### 2018-10-31 ttt.tex
ttt

\documentclass[a4,dvipdfmx,11pt]{article}

\usepackage{fancyhdr}
\usepackage{amsmath,amssymb}
\usepackage{fancybox,ascmac}
\usepackage[]{multicol}
\usepackage{caption}
\usepackage{mathtools}

\usepackage[dvipdfmx]{color}

\usepackage{float}
\usepackage[dvipdfmx]{graphicx}
\usepackage{tikz}
\usetikzlibrary{automata}
\usetikzlibrary{lindenmayersystems}
\usepackage{geometry}

\usepackage{amsthm}
\usepackage{amsmath}

\theoremstyle{definition}
\newtheorem{myth}{Theorem}[section]
\newtheorem{myproof}{Proof}[section]

\begin{document}

\section{Tunnel Troll Theorem}
\subsection{Introduction}
決定性Oritatami Systemでは転写されたbeadが固定される時、その位置は一意に定まる。
$\delta = 1$において転写されたbeadが一意に定まるためには、既に固定されている別のbeadとそのbeadがbondを結ぶか、あるいはトンネルを消費する必要がある。

ここで言う「トンネル」とは、ある三角格子上の点の周囲6点のうち、ちょうど4点が既に埋まっているような構造を指す。このトンネルの空いている頂点に直前のbeadが転写され、次のbeadがトンネルの中心に固定された時、そのbeadの周囲5点が埋まっていることになり、その次のbeadの位置は空いている1点に定まる。

この「トンネル」について以下が成り立つ。

\begin{myth}[Tunnel Troll Theorem]
  $|\Sigma| = 1, \delta = 1, \alpha = 2$を満たすOritatami Systemにおいて、トンネルを消費する時、Bondの数が減少する。
\end{myth}

\subsection{Proof}

この定理を示すには、トンネルを消費した際に増加するbondの数より減少するbondの数の方が多いことを示せば良い。

まず直前に固定されたbeadがトンネルの中にいるか外にいるかで場合分けを考える。トンネルの中にいる場合、次のbeadの固定される位置は既に決定されているが、次に固定される位置が再びトンネルの中であるかトンネルの外であるかでも場合分けを考える。また、トンネルの外にいる場合、そこがトンネルから離れた位置であるかトンネルの入り口であるかで場合分けをする(fig.\ref{TTT_position1})。パスは次のbeadが固定された時の状態遷移である。

\begin{figure}[h]
  \begin{center}
    \begin{tikzpicture}
      \draw[thick]
      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
      \node at(2.5,1) {トンネルの外};
      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {トンネルの入り口};
      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {トンネルから離れている};

      \draw[thick]
      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
      \node at(10.5,1) {トンネルの中};
      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {次もトンネル};
      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {次は外};

      \draw[->]
      (outside) edge [bend left] node[above] {} (enter)
                edge [loop left, transform canvas={xshift=-1cm}] node {} (outside)
      (enter)   edge [bend left] (next-tunnel)
                edge [bend left] (next-outside)
                edge [bend left] (outside)
      (next-tunnel) edge         (next-outside)
                edge [loop right]    (next-tunnel)
      (next-outside) edge[bend left] (outside)
                edge [bend left]     (enter)
      ;

    \end{tikzpicture}
    \caption{beadの位置による場合分け}
    \label{TTT_position1}
  \end{center}
\end{figure}

また、beadの位置とは別にトンネルの形状についても場合分けができる。三角格子上での対称性を考えるとトンネルの形状は以下の3つが考えられる(fig.\ref{TTT_tunnel})。この図において、バツが既にbeadが存在する頂点、白マルが空いている頂点である。また、トンネルの入口に注目すると、トンネルA,Bはどちらもトンネル内部に入る時のtranscriptのエッジに対して両側にbeadが存在する。一方でトンネルCは片側にのみbeadが存在する(fig.\ref{TTT_enterpoint})。出口についてはいずれのトンネルも同じ形になる(fig.\ref{TTT_exitpoint})。

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{ccc}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.1];

            \foreach \theta in {0,180}{
              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60,120,-120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

          \node at (2,-0.5) {Tunnel A};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.1];

            \foreach \theta in {-60,180}{
              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {0,60,120,-120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

          \node at (2,-0.5) {Tunnel B};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.1];

            \foreach \theta in {-120,180}{
              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {0,60,-60,120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }
          \end{scope}

          \node at (2,-0.5) {Tunnel C};
        \end{tikzpicture}
      \end{minipage}

    \end{tabular}
    \caption{トンネルの形状}
    \label{TTT_tunnel}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{cc}

      \begin{minipage}{0.45\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(2.5,0)--(2.5,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.1];
            \fill[transform canvas={shift=(180:1.5)}](0,0) circle [radius=0.1];

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (-1.4,0) -- (-0.1,0);
          \end{scope}

          \node at (1.25,-0.5) {Tunnel A,B};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.45\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(2.5,0)--(2.5,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \draw(0,0) circle [radius=0.1];

            \draw[transform canvas={shift=(-120:1.5)}](0,0) circle [radius=0.1];
            \fill[transform canvas={shift=(180:1.5)}](0,0) circle [radius=0.1];

            \foreach \theta in {120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (-1.4,0) -- (-0.1,0);
          \end{scope}

          \node at (1.25,-0.5) {Tunnel C};
        \end{tikzpicture}
      \end{minipage}

    \end{tabular}
    \caption{トンネルの入り口}
    \label{TTT_enterpoint}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \begin{tikzpicture}
      \draw[thick, rounded corners = 10pt]
      (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

      \begin{scope}[xshift=2cm, yshift=2cm]
        \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
        \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);

        \foreach \theta in {0}{
          \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
        }

        \foreach \theta in {60,-60,120,-120,180}{
          \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
          \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
        }
        \draw[->] (0.1,0) -- (1.4,0);
      \end{scope}
    \end{tikzpicture}
    \caption{トンネルの出口}
    \label{TTT_exitpoint}
  \end{center}
\end{figure}

今、トンネルAとトンネルBの場合だけを考える。Appendixより、各状態遷移においてbondの増加量の最大値をそれぞれのedgeに加えると以下のようになる(fig.\ref{TTT_position2})。ただし$a$は自然数とし、「次は外」の状態に遷移するたびに値が更新される。この図のように、トンネルの内と外を往来するとbondの数が減少する。

次にトンネルCについて考える。fig.\ref{TTT_enterpoint}とfig.\ref{TTT_exitpoint}よりトンネルCの入口にbeadが固定される時、トンネルの出口とトンネルCの入口は共存出来ないため、トンネルCは連続したトンネル構造の途中や出口に使用することはできない。これを考慮し、トンネルCが使用されるケースについて場合分けを考える(fig.\ref{TTT_tunnelC_graph})。この場合分けの内、上２つはトンネルA,Bの中へ入るためbondの数が減少する。そのため下２つについて考えれば良い。Appendixより、いずれの場合もbondの数が減少する。

以上より、トンネルA,B,Cいずれを消費した場合も増加するbondの数より減少するbondの数の方が多い。よってこの定理は示された。

\begin{figure}[h]
  \begin{center}
    \begin{tikzpicture}
      \draw[thick]
      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
      \node at(2.5,1) {トンネルの外};
      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {トンネルの入り口};
      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {トンネルから離れている};

      \draw[thick]
      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
      \node at(10.5,1) {トンネルの中};
      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {次もトンネル};
      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {次は外};

      \draw[->]
      (outside) edge [bend left] node[left] {$-1$} (enter)
                edge [loop left, transform canvas={xshift=-1cm}] node[left] {$0$} (outside)
      (enter)   edge [bend left] node[above] {$-1$} (next-tunnel)
                edge [bend left] node[above] {$-a$} (next-outside)
                edge [bend left] node[right] {$0$}  (outside)
      (next-tunnel) edge         node[right] {$-a$} (next-outside)
                edge [loop right]node[right] {$0$}    (next-tunnel)
      (next-outside) edge[bend left] node[above] {$a$}  (outside)
                edge [bend left]     node[above] {$a-1$}(enter)
      ;

    \end{tikzpicture}
    \caption{Tunnel A,Bにおけるbondの増加量}
    \label{TTT_position2}
  \end{center}
\end{figure}

\begin{figure}[h]
  \begin{center}
    \begin{tikzpicture}
      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {トンネルから離れている};
      \node at (4.5,4) [rectangle, draw,rounded corners] (enter1)   {トンネルの入り口};
      \node at (8,4)   [rectangle, draw, rounded corners] (inside1) {トンネルC};
      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {トンネルA,Bの中};
      \draw[->] (outside1)--(enter1);
      \draw[->] (enter1)  --(inside1);
      \draw[->] (inside1) --(exit1);

      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {トンネルの中};
      \node at (4.5,3) [rectangle, draw,rounded corners] (enter2)   {トンネルの入り口};
      \node at (8,3)   [rectangle, draw, rounded corners] (inside2) {トンネルC};
      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {トンネルA,Bの中};     
      \draw[->] (outside2)--(enter2);
      \draw[->] (enter2)  --(inside2);
      \draw[->] (inside2) --(exit2);

      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {トンネルから離れている};
      \node at (4.5,1) [rectangle, draw,rounded corners] (enter3)   {トンネルの入り口};
      \node at (8,1)   [rectangle, draw, rounded corners] (inside3) {トンネルC};
      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {トンネルの外};     
      \draw[->] (outside3)--(enter3);
      \draw[->] (enter3)  --(inside3);
      \draw[->] (inside3) --(exit3);

      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {トンネルの中};
      \node at (4.5,0) [rectangle, draw,rounded corners] (enter4)   {トンネルの入り口};
      \node at (8,0)   [rectangle, draw, rounded corners] (inside4) {トンネルC};
      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {トンネルの外};     
      \draw[->] (outside4)--(enter4);
      \draw[->] (enter4)  --(inside4);
      \draw[->] (inside4) --(exit4);
    \end{tikzpicture}
    \caption{Tunnel Cの場合分け}
    \label{TTT_tunnelC_graph}
  \end{center}
\end{figure}

\newpage

\subsection{Appendix of Tunnel Troll Theorem}
\subsubsection{Entrance of TunnelA,B}
Tunnelの入口に固定されたbeadが、どの方向から来たかで場合分けをする(fig.\ref{TTT_tunnel_direction})。
その結果３通りの場合分けが出来るが、以下のようにいずれの場合もbondの総数は減少する。

\begin{itemize}
\item{Pattern1の時}\\
  四角で表されてる2頂点が埋まっているかどうかで分けられる。もしどちらも埋まっているとすると、トンネルの入り口ではなくトンネルの中になってしまうので、必ず少なくとも一方は空いている。今、頂点cが空いているとする。すると頂点Aの周囲は3点以上空いている事になる。Aの周囲2頂点はback boneとしてつながっている。そのためもしBが既にbondを消費しているならば、残りの1頂点に存在するbeadとのみbondを結ぶ事となる。頂点Bの周囲は３点空いている事を考えるとBは1つ以上のbondを残している。そのため入口に固定されるbeadと必ずbondを結ぶ事になる。もし頂点dも空いている場合、固定されるbeadはbondを２つとも消費し、かつ既存のbondも２つ消費しbondの総数は減少する。頂点dが埋まっていたとしても、頂点Aとは同様にしてbondを結び、決定的に固定するために頂点Bかdとbondを結ぶ。故にいずれの場合もbondの総数は減少する。

\item{Pattern2の時}\\
  Pattern1と同様にして頂点c,dが埋まっているかどうかで分けられる。Pattern1の例よりどちらも埋まっていることはない。頂点cが空いている場合決定的にbeadを固定するためにA,B少なくとも一方のbondを消費する。一方、頂点cが埋まっていて頂点dが空いている場合、Pattern1のように、固定されるbeadと頂点Bはbondを結ぶためbondを消費する。

  Pattern2の場合、固定されるbeadはbondを１つ増やす可能性がある。もし仮にbondが増えたとするならば、そのbondを使用するためはに頂点cかdにbeadが固定される必要がある。しかし今頂点BとPはback boneによってつながっている。Jordan curve theoremより、これ以降に転写され得るbeadの領域に頂点c,dは含まれないため、このbondを消費することはできず、bondの数は増加しない。よって既存のbondを減少させ、かつ新たに有効なbondを増やさないことからbondの総数は減少する。

\item{Pattern3の時}\\
  頂点nは空いているため、決定的に固定するために頂点c,d,eのいずれかとbondを結ぶ必要がある、そのため既存のbondを消費する。一方、固定されるbeadはbondを１つ増やす可能性があるが、pattern2と同様に頂点AとPがback boneでつながっているため、これ以降に転写され得るbeadの領域に頂点c,d,eは含まれていないため、増やされるbondを使用できない。よって既存のbondを減少させ、かつ新たに有効なbondを増やさないことからbondの総数は減少する。

\end{itemize}

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{ccc}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60,180}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {120,-120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.4)--(180:0.1);
            \draw[->] (0:0.1)--(0:1.4);

            \node[transform canvas={shift=(60:1.5)},right] {A};
            \node[transform canvas={shift=(-60:1.5)},right] {B};

            \node[transform canvas={shift=(120:1.5)},left] {c};
            \node[transform canvas={shift=(-120:1.5)},left] {d};
          \end{scope}

          \node at (2,-0.5) {Pattern 1};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60,120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {180,-120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (120:1.4)--(120:0.1);
            \draw[->] (0:0.1)--(0:1.4);

            \node[transform canvas={shift=(60:1.5)},right] {A};
            \node[transform canvas={shift=(-60:1.5)},right] {B};
            \node[transform canvas={shift=(120:1.5)},left] {P};

            \node[transform canvas={shift=(180:1.5)},left] {c};
            \node[transform canvas={shift=(-120:1.5)},left] {d};
          \end{scope}

          \node at (2,-0.5) {Pattern 2};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.3\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];

            \foreach \theta in {0}{
              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
            }

            \foreach \theta in {60,-60}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {180,-120,120}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (60:1.4)--(60:0.1);
            \draw[->] (0:0.1)--(0:1.4);

            \node[transform canvas={shift=(-60:1.5)},right] {A};
            \node[transform canvas={shift=(60:1.5)},right] {P};

            \node[transform canvas={shift=(120:1.5)},left] {c};
            \node[transform canvas={shift=(180:1.5)},left] {d};
            \node[transform canvas={shift=(-120:1.5)},left] {e};
            \node[transform canvas={shift=(0:1.5)},below] {n};
          \end{scope}

          \node at (2,-0.5) {Pattern 3};
        \end{tikzpicture}
      \end{minipage}

    \end{tabular}
    \caption{入口へ至る方向}
    \label{TTT_tunnel_direction}
  \end{center}
\end{figure}

\subsubsection{Exit of Tunnel}

Tunnelの出口について場合分けを考える(fig.\ref{TTT_tunnel_exit})。この場合分けは頂点c,dについてその頂点が既に埋まっているか埋まっていないかで場合分けされている。なお、頂点c,dの両方とも埋まっている場合は、Tunnelの出口ではなくトンネルの中になるため場合分けに含めない。今、出口に固定されるbeadの1つ前のbeadが、$a$以下のbond消費したとする。すると以下で示されるようにTunnelの出口で増加するbondの数は高々$a$程度となる。つまり、Tunnelを出る事によって増加するbondの最大値は$0$となる。

\begin{itemize}
\item{Pattern1の時}\\
  頂点c,dが空いていたとする。入口の時と同様に考えると、頂点A,Bはbondを残しているため、頂点Pは頂点A,Bとbondを結ぶ。すなわち$a=2$となる。$\alpha = 2$を考えるとTunnel出口に固定されるbeadのよって増加するbondは高々$a=2$程度。
\item{Pattern2の時}\\
  頂点cのみが埋まっていたとする。頂点Bはbondを残しているため、頂点PとBはbondを結ぶ。よって$a \geq 1$また、Tunnel出口で固定されるbeadはbondを$2$増加させる可能性があるが、空いている頂点e,dについて一方はback boneとして消費されるため、このbeadが増加させたbondを使用できるのは後にbeadが頂点e,dのいずれかに来た時のみ。よってTunnel出口に固定されるbeadは有効なbondを高々$1$程度しか増やさない。よって増加するbondの数は高々$a$程度であることが言える。

\end{itemize}

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{cc}

      \begin{minipage}{0.48\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];

            \foreach \theta in {120,-120,180}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {0,60,-60}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.4)--(180:0.1);

            \node[transform canvas={shift=(120:1.5)},right] {A};
            \node[transform canvas={shift=(-120:1.5)},right] {B};
            \node[transform canvas={shift=(180:1.5)},left] {P};

            \node[transform canvas={shift=(60:1.5)},left] {c};
            \node[transform canvas={shift=(-60:1.5)},left] {d};
          \end{scope}

          \node at (2,-0.5) {Pattern 1};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.48\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;

          \begin{scope}[xshift=2cm, yshift=2cm]
            \fill(0,0) circle [radius=0.1];

            \foreach \theta in {120,-120,180,60}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \foreach \theta in {0,-60}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
            }

            \draw[->] (180:1.4)--(180:0.1);

            \node[transform canvas={shift=(120:1.5)},right] {A};
            \node[transform canvas={shift=(-120:1.5)},right] {B};
            \node[transform canvas={shift=(180:1.5)},left] {P};

            \node[transform canvas={shift=(-60:1.5)},right] {d};
            \node[transform canvas={shift=(60:1.5)},right] {c};
            \node[transform canvas={shift=(0:1.5)},right] {e};
          \end{scope}

          \node at (2,-0.5) {Pattern 2};
        \end{tikzpicture}
      \end{minipage}

    \end{tabular}
    \caption{出口のパターン}
    \label{TTT_tunnel_exit}
  \end{center}
\end{figure}

\subsubsection{Tunnel C}

Tunnel Cの入口に固定されるbeadについて、そのbeadがTunnelを消費して固定されたか、
そうでないかによって場合分けをする。

\subsubsection{Tunnel Cの入口のbeadがTunnelを消費して固定された場合}
Tunnel Cの構造を維持したまま入口にTunnel消費によるbeadを固定するパターンはfig.\ref{TTT_tunnelC_enter_usingTunnel}の２通りがある。

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{cc}

      \begin{minipage}{0.48\hsize}
        \begin{tikzpicture}
          \draw[thick, rounded corners = 10pt]
          (-2,2)--(5,2)--(5,-3)--(-2,-3)-- cycle;

          \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
          \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);

          \foreach \theta in {60,-60,120,-120,180}{
            \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
            \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
          }

          \fill(0:1.5) circle [radius=0.1];
          \draw[->] (0:0.1)--(0:1.4);

          \node[left] at (-60:1.5) {A};

          \begin{scope}[shift=(0:3)]
            \fill(0,0) circle [radius=0.1];

            \foreach \theta in {120,60,-60}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (180:1.4)--(180:0.1);
            \draw[->] (-120:0.1)--(-120:1.4);

            \node[below] at (180:1.5) {$t_1$};
            \node[right] at (0:0) {$t_2$};
            \node[right] at (-120:1.5) {$t_3$};

            \node[left] at (120:1.5) {B};
            \node[left] at (60:1.5) {C};
            \node[left] at (0:1.5) {D};

            \begin{scope}[shift=(-120:1.5)]
              \draw(0,0) circle [radius=0.1];
              \foreach \theta in {-120,-60}{
                \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
              }

              \node[right] at (-120:1.5) {e};
            \end{scope}

          \end{scope}

          \node at (1.5,-3.5) {Pattern 1};
        \end{tikzpicture}
      \end{minipage}

      \begin{minipage}{0.48\hsize}
        \begin{tikzpicture}
                    \draw[thick, rounded corners = 10pt]
          (-2,2)--(5,2)--(5,-3)--(-2,-3)-- cycle;

          \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
          \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);

          \foreach \theta in {60,-60,120,-120,180}{
            \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
            \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
          }

          \fill(0:1.5) circle [radius=0.1];
          \draw[->] (0:0.1)--(0:1.4);

          \node[left] at (-60:1.5) {A};

          \begin{scope}[shift=(0:3)]
            \fill(0,0) circle [radius=0.1];

            \foreach \theta in {120,60,-60}{
              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
            }

            \draw[->] (180:1.4)--(180:0.1);
            \draw[->] (-120:0.1)--(-120:1.4);

            \node[below] at (180:1.5) {$t_1$};
            \node[right] at (0:0) {$t_2$};
            \node[right] at (-120:1.5) {$t_3$};

            \node[left] at (120:1.5) {B};
            \node[left] at (60:1.5) {C};
            \node[left] at (0:1.5) {D};

            \begin{scope}[shift=(-120:1.5)]
              \draw(0,0) circle [radius=0.1];
              \foreach \theta in {-120,-60}{
                \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
              }

              \node[right] at (-120:1.5) {e};
            \end{scope}

          \end{scope}

          \node at (1.5,-3.5) {Pattern 2};
        \end{tikzpicture}
      \end{minipage}

    \end{tabular}
    \caption{Tunnelを消費して入口に固定されたbead}
    \label{TTT_tunnelC_enter_usingTunnel}
  \end{center}
\end{figure}

\end{document}

### 2018-10-31 ttt.tex
update ttt

@@
 Tunnel Cの入口に固定されるbeadについて、そのbeadがTunnelを消費して固定されたか、
-そうでないかによって場合分けをする。
+そうでないかによって場合分けをする。なお、Tunnel Cの出口はTunnelA,Bの中でないとする。
 
@@
 Tunnel Cの構造を維持したまま入口にTunnel消費によるbeadを固定するパターンはfig.\ref{TTT_tunnelC_enter_usingTunnel}の２通りがある。
+
+\begin{itemize}
+\item{Pattern1}\\
+  頂点$t_1$が転写される前では、$t_3$がトンネルの外であることから頂点Aの周囲3点は空いてる。よって頂点Aのbeadは1つ以上bondを持つため、頂点Aと$t_1$はbondを結ぶ。また、頂点$t_2$が決定的に固定されるためには頂点B,C,Dとの間とbondを結ぶ必要がある。一方で、頂点$t_1,t_2$は、たとえbondを増やしたとしても周囲6点が埋まっているため、それを使うことができない。つまり$t_2$が固定された時点でbondは$2$減少している。今、$t_3$が固定された時を考えると、このbeadはbondを最大で2つ増やす可能性がある。しかし今$t_3$の周囲で空いているのは頂点e,fで、このうち一方はback boneのために使われるため、$t_3$の増やしたbondは1つのみが有効なbondとなる。よって全体でbondの総数を1以上減少させる。
+
+\item{Pattern2}\\
+  頂点$t_1$が固定される時そのbeadが幾つ周囲のbondを消費するかで場合分けできる。
+  \begin{itemize}
+  \item[-]{$t_1$がbondを消費しない場合}\\
+    頂点$t_2$が決定的に固定される時、bondを1以上消費しかつ有効なbondを増やさない。頂点$t_3$が固定される時、頂点$t_1$はbondを持っているため、$t_3$,$t_1$の間でbondを結ぶ。よって$t_3$の固定で増加するbondの数は0以下。一方で、この時$t_1$はまだ有効なbondを一つ持っている。もし頂点eが埋まっているならこのbondは有効でなくなりbondの総数は減少する。そこで仮に頂点eが空いている場合を考える。今$t_3$の次に固定されるbeadを$t_4$とする。もし$t_4$が頂点eに固定されたなら、$t_1$のbondを消費しかつ$t_4$はbondを1つ消費し1つ増やす。よって$t_1$から$t_4$の固定においてbondの総数は減少する。次に$t_4$が頂点f,gのどちらかに固定される場合を考える。頂点eは空いているため、決定的に固定するに$t_4$は2つのbondを消費する必要がある。よって$t_1$が増やしたbondを加味してもbond$t_1$から$t_4$の固定でbondの総数を減らすことになる。よっていずれのケースを考えてもbondの総数は減少する。
+
+  \item[-]{$t_1$がbondを1つ消費する場合}\\
+    $t_2$は同様にしてbondの総数を1つ減少させ、$t_3$も増加させるbondの数は0以下。この時$t_1$はbondを増やさない。よってbondの総数は2以上減少する。
+  \item[-]{$t_1$がbondを2つ消費する場合}\\
+    $t_2$はbondを1つ以上減少させ、$t_3$はbondを2つ増加させる。よってbondの総数は減少する。
+  \end{itemize}
+\end{itemize}
 
@@
               \node[right] at (-120:1.5) {e};
+              \node[right] at (-60:1.5) {f};
             \end{scope}
@@
           \draw[thick, rounded corners = 10pt]
-          (-2,2)--(5,2)--(5,-3)--(-2,-3)-- cycle;
+          (-2,2)--(4.5,2)--(4.5,-4.5)--(-2,-4.5)-- cycle;
 
@@
 
-          \foreach \theta in {60,-60,120,-120,180}{
+          \foreach \theta in {60,0,120,-120,180}{
             \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
@@
 
-          \fill(0:1.5) circle [radius=0.1];
-          \draw[->] (0:0.1)--(0:1.4);
+          \draw[->] (-60:0.1)--(-60:1.4);
 
-          \node[left] at (-60:1.5) {A};
+          \begin{scope}[shift=(-60:1.5),shift=(0:1.5)]
+            \fill(0,0) circle [radius=0.1];
+            \fill(180:1.5) circle [radius=0.1];
 
-          \begin{scope}[shift=(0:3)]
-            \fill(0,0) circle [radius=0.1];
-
-            \foreach \theta in {120,60,-60}{
+            \foreach \theta in {120,60,0,-60}{
               \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
@@
 
-            \node[left] at (120:1.5) {B};
-            \node[left] at (60:1.5) {C};
-            \node[left] at (0:1.5) {D};
+            \node[left] at (120:1.5) {A};
+            \node[left] at (60:1.5) {B};
+            \node[left] at (0:1.5) {C};
 
@@
               \draw(0,0) circle [radius=0.1];
-              \foreach \theta in {-120,-60}{
+              \foreach \theta in {180,-120,-60}{
                 \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
@@
 
-              \node[right] at (-120:1.5) {e};
+              \node[right] at (180:1.5) {e};
+              \node[right] at (-120:1.5) {f};
+              \node[right] at (-60:1.5) {g};
             \end{scope}
@@
 
-          \node at (1.5,-3.5) {Pattern 2};
+          \node at (1.25,-5) {Pattern 2};
         \end{tikzpicture}

### 2018-11-01 ttt.tex
updating ttt

@@
 
+\subsubsection{TunnelCの入口のbeadがTunnelを使わずに固定された場合}
+TunnelCの入口のbeadがTunnelを使わずに固定される時、そのbeadは既存のbondを使うことによって固定される。fig.\ref{TTT_tunnelC_enter_usingBond}において$t_1$がいくつのbondを消費したかで場合分けを考える。
+
+\begin{itemize}
+\item{$t_1$が1つのbondを消費する場合}\\
+  この時$t_1$は1つの有効なbondを生み出す。$t_2$は頂点A,B,Cの少なくとも一つとbondを結ぶ必要があり、かつ有効なbondを増やさない。$t_3$について考えると、$t_1$がbondを残していることから$t_3$と$t_1$はbondで結ばれる。故にbondの総数は1以上減少する。
+
+\item{$t_1$が2つのbondを消費する場合}\\
+  この時$t_1$はbondを生み出さない。$t_2$については先程と同様bondの総数を1減らす。今、$t_3$はどのbeadともbondを結ばない可能性があるため、bondの総数を最大で2増加させる。故にbondの総数は1以上減少する。
+\end{itemize}
+
+\begin{figure}[h]
+  \begin{center}
+    \begin{tabular}{cc}
+
+      \begin{minipage}{0.48\hsize}
+        \begin{tikzpicture}
+          \draw[thick, rounded corners = 10pt]
+          (-3,2)--(2.5,2)--(2.5,-3)--(-3,-3)-- cycle;
+
+          \foreach \theta in {60,-60,120,0}{
+            \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+          }
+
+          \fill(180:1.5) circle [radius=0.1];
+          \fill(0:0) circle [radius=0.1];
+
+          \draw[transform canvas={shift=(180:1.5)}] (105:1.4) edge[bend right] (105:0.1);
+          \draw[->] (180:1.4) -- (180:0.1);
+          \draw[->] (-120:0.1) -- (-120:1.4);
+
+          \node[below] at (180:1.5) {$t_1$};
+          \node[right] at (0:0) {$t_2$};
+          \node[left] at (-120:1.5) {$t_3$};
+
+          \node[right] at (120:1.5) {A};
+          \node[right] at (60:1.5) {B};
+          \node[right] at (0:1.5) {C};
+
+          \begin{scope}[shift=(-120:1.5)]
+            \draw(0,0) circle [radius=0.1];
+            \foreach \theta in {-120,-60,180}{
+              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
+            }
+
+          \end{scope}
+
+          \node at (-0.25,-3.5) {Pattern 1};
+        \end{tikzpicture}
+      \end{minipage}
+
+    \end{tabular}
+    \caption{Tunnelを消費せずに入口に固定されたbead}
+    \label{TTT_tunnelC_enter_usingBond}
+  \end{center}
+\end{figure}
+
 \end{document}

### 2018-11-01 ttt.tex
11/1

@@
 
+We will show that there are more bonds in decreasing than in increasing.
+
+First, we divide cases of there is a bead in a tunnel and there is out of the tunnel.
+The bead have two cases which a next bead is in a tunnel or out of the tunnel if the bead in the tunnel.
+On the other hand if the bead out of the tunnel, the bead have two cases which it exists in far away of tunnels or at an entrance of a tunnel(fig.\ref{TTT_position1}).
+Paths are transition of dicided position of a next bead in this figure.
+
 この定理を示すには、トンネルを消費した際に増加するbondの数より減少するbondの数の方が多いことを示せば良い。
@@
       (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
-      \node at(2.5,1) {トンネルの外};
-      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {トンネルの入り口};
-      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {トンネルから離れている};
+      \node at(2.5,1) {Out of tunnels};
+      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
+      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Far away of tunnels};
 
@@
       (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
-      \node at(10.5,1) {トンネルの中};
-      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {次もトンネル};
-      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {次は外};
+      \node at(10.5,1) {Inside of tunnels};
+      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Next to a tunnel};
+      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Next to outside};
 
@@
     \end{tikzpicture}
-    \caption{beadの位置による場合分け}
+    \caption{Cases on position of a bead}
     \label{TTT_position1}
@@
 
-以上より、トンネルA,B,Cいずれを消費した場合も増加するbondの数より減少するbondの数の方が多い。よってこの定理は示された。
+以上より、トンネルA,B,Cのどれを消費した場合もbondの増加量は-1以下となる(fig.\ref{TTT_delta-1}は増加量が$-1$となる例)。よってこの定理は示された。
+
+\begin{figure}[h]
+  \begin{center}
+    \begin{tikzpicture}
+      \draw[thick, rounded corners = 10pt]
+      (-2,-2)--(5,-2)--(5,3)--(-2,3)-- cycle;
+
+      \fill(0,0) circle [radius=0.1];
+      \foreach \theta in {60,-60,120}{
+        \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
+        \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+      }
+      \foreach \theta in {180,-120}{
+        \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
+      }
+
+      \draw[->] (120:1.4) -- (120:0.1);
+      \draw[dashed] (-60:0.1) -- (-60:1.4);
+
+      \begin{scope}[shift=(60:1.5)]
+        \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
+        \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
+
+        \foreach \theta in {60,120,0}{
+          \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
+          \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+        }
+
+        \draw[->] (60:1.4)--(60:0.1);
+        \draw[->] (180:0.1)--(180:1.4);
+        \draw[dashed] (120:0.1)--(120:1.4);
+        \draw[dashed] (0:0.1)--(0:1.4);
+
+        \begin{scope}[shift=(0:1.5)]
+          \foreach \theta in {60,0}{
+            \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+          }
+          \draw[dashed] (120:0.1)--(120:1.4);
+          \draw (0:0.1)--(0:1.4);
+          \draw (60:0.1)--(60:1.4);
+        \end{scope}
+      \end{scope}
+      \begin{scope}[shift=(0:1.5)]
+        \fill(0,0) circle [radius=0.1];
+        \fill(0:1.5) circle [radius=0.1];
+        \draw(0:3) circle [radius=0.1];
+        \draw[shift=(0:1.5),shift=(-60:1.5)] circle [radius=0.1];
+        \foreach \theta in {-60}{
+          \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
+          \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+        }
+
+        \draw[->] (180:1.4)--(180:0.1);
+        \draw[->] (0:0.1)--(0:1.4);
+        \draw[->] (0:1.6)--(0:2.9);
+        \draw[dashed] (-60:0.1)--(-60:1.4);
+
+        \node[above] at (180:1.5) {$(-1)$};
+        \node[above] at (0:0) {$(-1)$};
+        \node[above] at (0:1.5) {$(+1)$};
+
+      \end{scope}
+    \end{tikzpicture}
+  \end{center}
+  \caption{増加量が$-1$となる例}
+  \label{TTT_delta-1}
+\end{figure}
 
@@
       \node at(10.5,1) {トンネルの中};
-      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {次もトンネル};
-      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {次は外};
+      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Next to a tunnel};
+      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Next to outside};
 
@@
       (outside) edge [bend left] node[left] {$-1$} (enter)
-                edge [loop left, transform canvas={xshift=-1cm}] node[left] {$0$} (outside)
+                edge [loop left, transform canvas={xshift=-1cm}] node[left] {$\pm 0$} (outside)
       (enter)   edge [bend left] node[above] {$-1$} (next-tunnel)
                 edge [bend left] node[above] {$-a$} (next-outside)
-                edge [bend left] node[right] {$0$}  (outside)
+                edge [bend left] node[right] {$\pm 0$}  (outside)
       (next-tunnel) edge         node[right] {$-a$} (next-outside)
-                edge [loop right]node[right] {$0$}    (next-tunnel)
-      (next-outside) edge[bend left] node[above] {$a$}  (outside)
-                edge [bend left]     node[above] {$a-1$}(enter)
+                edge [loop right]node[below] {$\pm 0$}    (next-tunnel)
+      (next-outside) edge[bend left] node[above] {$+a$}  (outside)
+                edge [bend left]     node[above] {$+(a-1)$}(enter)
       ;

### 2018-11-06 ttt.tex
11/6 en ver

@@
 \usepackage{tikz}
+\usepackage{calc}
 \usetikzlibrary{automata}
@@
 
-\section{Tunnel Troll Theorem}
-\subsection{Introduction}
-決定性Oritatami Systemでは転写されたbeadが固定される時、その位置は一意に定まる。
-$\delta = 1$において転写されたbeadが一意に定まるためには、既に固定されている別のbeadとそのbeadがbondを結ぶか、あるいはトンネルを消費する必要がある。
+\section{Infiniteness of delay-1, arity-2 unary deterministic oritatami system}
 
-ここで言う「トンネル」とは、ある三角格子上の点の周囲6点のうち、ちょうど4点が既に埋まっているような構造を指す。このトンネルの空いている頂点に直前のbeadが転写され、次のbeadがトンネルの中心に固定された時、そのbeadの周囲5点が埋まっていることになり、その次のbeadの位置は空いている1点に定まる。
-
-この「トンネル」について以下が成り立つ。
-
-\begin{myth}[Tunnel Troll Theorem]
-  $|\Sigma| = 1, \delta = 1, \alpha = 2$を満たすOritatami Systemにおいて、トンネルを消費する時、Bondの数が減少する。
-\end{myth}
-
-\subsection{Proof}
-
-We will show that there are more bonds in decreasing than in increasing.
-
-First, we divide cases of there is a bead in a tunnel and there is out of the tunnel.
-The bead have two cases which a next bead is in a tunnel or out of the tunnel if the bead in the tunnel.
-On the other hand if the bead out of the tunnel, the bead have two cases which it exists in far away of tunnels or at an entrance of a tunnel(fig.\ref{TTT_position1}).
-Paths are transition of dicided position of a next bead in this figure.
-
-この定理を示すには、トンネルを消費した際に増加するbondの数より減少するbondの数の方が多いことを示せば良い。
-
-まず直前に固定されたbeadがトンネルの中にいるか外にいるかで場合分けを考える。トンネルの中にいる場合、次のbeadの固定される位置は既に決定されているが、次に固定される位置が再びトンネルの中であるかトンネルの外であるかでも場合分けを考える。また、トンネルの外にいる場合、そこがトンネルから離れた位置であるかトンネルの入り口であるかで場合分けをする(fig.\ref{TTT_position1})。パスは次のbeadが固定された時の状態遷移である。
-
-\begin{figure}[h]
+\begin{figure}
   \begin{center}
     \begin{tikzpicture}
-      \draw[thick]
-      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
-      \node at(2.5,1) {Out of tunnels};
-      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
-      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Far away of tunnels};
+      \draw[thick, rounded corners = 10pt]
+      (-1,-1)--(7,-1)--(7,2)--(-1,2)-- cycle;
 
-      \draw[thick]
-      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
-      \node at(10.5,1) {Inside of tunnels};
-      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Next to a tunnel};
-      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Next to outside};
+      \fill (0,0) circle[radius = 0.1];
+      \fill (1.5,0) circle[radius = 0.1];
+      \fill (3,0) circle[radius = 0.1];
+      \fill (4.5,0) circle[radius = 0.1];
+      \fill (6,0) circle[radius = 0.1];
 
-      \draw[->]
-      (outside) edge [bend left] node[above] {} (enter)
-                edge [loop left, transform canvas={xshift=-1cm}] node {} (outside)
-      (enter)   edge [bend left] (next-tunnel)
-                edge [bend left] (next-outside)
-                edge [bend left] (outside)
-      (next-tunnel) edge         (next-outside)
-                edge [loop right]    (next-tunnel)
-      (next-outside) edge[bend left] (outside)
-                edge [bend left]     (enter)
-      ;
+      \draw[dashed] (0,0)--(1.5,0);
+      \draw[dashed] (1.5,0)--(3,0);
+      \draw[dashed] (3,0)--(4.5,0);
+      \draw[dashed] (4.5,0)--(6,0);
+      \draw[->] (0,0)--(60:1.3);
+      \draw[->] (1.5,0)--++(60:1.3);
+      \draw[->] (3,0)--++(60:1.3);
+      \draw[->] (4.5,0)--++(60:1.3);
+
+      \begin{scope}[shift=(60:1.5)]
+        \fill (0,0) circle[radius = 0.1];
+        \fill (1.5,0) circle[radius = 0.1];
+        \fill (3,0) circle[radius = 0.1];
+        \fill (4.5,0) circle[radius = 0.1];
+        \draw[dashed] (0,0)--(1.5,0);
+        \draw[dashed] (1.5,0)--(3,0);
+        \draw[dashed] (3,0)--(4.5,0);
+        \draw[->] (0,0)--(-60:1.3);
+        \draw[->] (1.5,0)--++(-60:1.3);
+        \draw[->] (3,0)--++(-60:1.3);
+        \draw[->] (4.5,0)--++(-60:1.3);
+      \end{scope}
 
     \end{tikzpicture}
-    \caption{Cases on position of a bead}
-    \label{TTT_position1}
+    \caption{zig-zag conformation}
+    \label{TTT_zigzag}
   \end{center}
@@
 
-また、beadの位置とは別にトンネルの形状についても場合分けができる。三角格子上での対称性を考えるとトンネルの形状は以下の3つが考えられる(fig.\ref{TTT_tunnel})。この図において、バツが既にbeadが存在する頂点、白マルが空いている頂点である。また、トンネルの入口に注目すると、トンネルA,Bはどちらもトンネル内部に入る時のtranscriptのエッジに対して両側にbeadが存在する。一方でトンネルCは片側にのみbeadが存在する(fig.\ref{TTT_enterpoint})。出口についてはいずれのトンネルも同じ形になる(fig.\ref{TTT_exitpoint})。
+\subsection{Introduction}
 
-\begin{figure}[h]
+In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 1 deterministically moreover the infinite terminal which its oritatami system can yield is only zig-zag conformations shown in Fig\ref{TTT_zigzag}.
+
+Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2.
+Assume its seed $\sigma$ consists of $n$ beads.
+Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
+For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$ that is foldable by $\Xi$.
+Hence $C_0 = \sigma$.
+
+Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$.
+The bead cannot collaborate with any succeeding bead $w_{i+1},w_{i+2},\cdots$ at delay 1.
+There are just two ways to get stabilized at delay 1.
+One way is to be bound to another bead.
+The other way is through a $tunnel\ section$.
+A tunnel section consists of four beads that occupt four neighbors of a point(Fig.\ref{TTT_tunnel_intro}).
+Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are not occupied.
+We call such beads as $p$ $inside\ of\ a\ tunnel$ and such beads as $p^\prime$ $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel.
+If the beads $a_{i-2}$ and $a_{i-1}$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $a_i$ cannot help but be stabilized at the other free neighbor.
+In this way, $a_i$ can get stabilized without being bound.
+
+%Tunnel sections and unbound beads, or more precisely, their some capabilities of binding, are the resources for beads to get stabilized deterministically at delay 1
+
+If a bead is stabilized through a tunnel section, then it can provide two binging capabilities and create tunnel sections.
+
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \fill (0:0) circle [radius=0.05];
+      \fill (0:1.5) circle [radius=0.05];
+      \fill (180:1.5) circle [radius=0.05];
+      \node[above] at (0:1.5) { $p^\prime$ };
+      \node[above] at (0:0) { $p$ };
+      \node[above] at (180:1.5) { $p^\prime$ };
+
+      \fill (60 : 1.5) circle [radius=0.1];
+      \fill (-60 : 1.5) circle [radius=0.1];
+      \fill (120 : 1.5) circle [radius=0.1];
+      \fill (-120 : 1.5) circle [radius=0.1];
+      \node[above] at (60 :1.5) { $a_{j_1}$ };
+      \node[above] at (-60 :1.5) { $a_{j_2}$ };
+      \node[above] at (120 :1.5) { $a_{j_3}$ };
+      \node[above] at (-120 :1.5) { $a_{j_4}$ };
+
+      \begin{scope}[shift=(0:5)]
+        \fill (0:0) circle [radius=0.1];
+        \fill (0:1.5) circle [radius=0.05];
+        \fill (180:1.5) circle [radius=0.1];
+        \node[above] at (180:1.5) { $a_{i-2}$ };
+        \node[above] at (0:0) { $a_{i-1}$ };
+        \draw[->] (180:1.4) -- (180:0.1);
+
+        \fill (60 : 1.5) circle [radius=0.1];
+        \fill (-60 : 1.5) circle [radius=0.1];
+        \fill (120 : 1.5) circle [radius=0.1];
+        \fill (-120 : 1.5) circle [radius=0.1];
+        \node[above] at (60 :1.5) { $a_{j_1}$ };
+        \node[above] at (-60 :1.5) { $a_{j_2}$ };
+        \node[above] at (120 :1.5) { $a_{j_3}$ };
+        \node[above] at (-120 :1.5) { $a_{j_4}$ };
+      \end{scope}
+      \begin{scope}[shift=(0:10)]
+        \fill (0:0) circle [radius=0.1];
+        \fill (0:1.5) circle [radius=0.1];
+        \fill (180:1.5) circle [radius=0.1];
+        \node[above] at (180:1.5) { $a_{i-2}$ };
+        \node[above] at (0:0) { $a_{i-1}$ };
+        \node[above] at (0:1.5) { $a_i$ };
+        \draw[->] (180:1.4) -- (180:0.1);
+        \draw[->] (0:0.1) -- (0:1.4);
+
+        \fill (60 : 1.5) circle [radius=0.1];
+        \fill (-60 : 1.5) circle [radius=0.1];
+        \fill (120 : 1.5) circle [radius=0.1];
+        \fill (-120 : 1.5) circle [radius=0.1];
+        \node[above] at (60 :1.5) { $a_{j_1}$ };
+        \node[above] at (-60 :1.5) { $a_{j_2}$ };
+        \node[above] at (120 :1.5) { $a_{j_3}$ };
+        \node[above] at (-120 :1.5) { $a_{j_4}$ };
+      \end{scope}
+    \end{tikzpicture} 
+    \caption{Through a tunnel section}
+    \label{TTT_tunnel_intro}
+  \end{center}
+\end{figure}
+
+%決定性Oritatami Systemでは転写されたbeadが固定される時、その位置は一意に定まる。
+%$\delta = 1$において転写されたbeadが一意に定まるためには、既に固定されている別のbeadとそのbeadがbondを結ぶか、あるいはトンネルを消費する必要がある。
+
+%ここで言う「トンネル」とは、ある三角格子上の点の周囲6点のうち、ちょうど4点が既に埋まっているような構造を指す。このトンネルの空いている頂点に直前のbeadが転写され、次のbeadがトンネルの中心に固定された時、そのbeadの周囲5点が埋まっていることになり、その次のbeadの位置は空いている1点に定まる。
+
+%この「トンネル」について以下が成り立つ。
+
+\begin{myth}[Tunnel Troll Theorem]
+  Let $\Xi$ be an unary oritatami system of delay 1 and arity 2. If a bead is stabilized through a tunnel section, then it consume some binging capabilities.
+\end{myth}
+
+\subsection{Proof of Tunnel Troll Theorem}
+Assume $\Xi$ is deterministic.
+Let us represent its transcript $w$ as $w = w_1 w_2 w_3 \cdots$ for beads $w_1 , w_2 , w_3 , \cdots \in \Sigma = \{e\}$.
+Each of these beads is stabilized either by being bound or through a tunnel section (or by both).
+How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
+On the other hand, each of beads are bound either inside of tunnel or outside (Fig.
+\ref{TTT_position1}).
+If a bead is stabilized at inside of tunnel, then its successor is already decided the position either inside of a tunnel or outside.
+Moreover, If a bead is stabilized at outside of a tunnel, then its position is an entrance of a tunnel or otherwise.
+
+Tunnel sections have three possible shape with considering symmetry such as acute turn, straight and obtuse turn (Figure \ref{TTT_tunnel}).
+Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Figure \ref{TTT_enterpoint}).
+
+Let us consider tunnel sections only tunnel A and B.
+See Figure \ref{TTT_position2}.
+According to appendix, we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successer\ in\ outside$.
+
+Next, we consider on tunnel C section.
+If $w[i]$ is stabilized by tunnel C and $S[i+1]$ is $t$, then $w[i+1]$ is stabilized by tunnel A or B because if $w[i+1]$ is stabilized by tunnel C, then $C_{i+1}$ is a terminal.
+Hence, tunnel C section is devided cases sush as Figure \ref{TTT_tunnelC_graph}.
+Cases of $S[i...] = bt^l (l \geq 2)$ are already considered (Upper).
+According to appendix, cases of $S[i..i+2] = btb$ also consume some binding capabilities.
+
+Thus, if a bead is stabilized through a tunnel section, then it consume some binging capabilities.
+
+%この定理を示すには、トンネルを消費した際に増加するbondの数より減少するbondの数の方が多いことを示せば良い。
+
+%まず直前に固定されたbeadがトンネルの中にいるか外にいるかで場合分けを考える。トンネルの中にいる場合、次のbeadの固定される位置は既に決定されているが、次に固定される位置が再びトンネルの中であるかトンネルの外であるかでも場合分けを考える。また、トンネルの外にいる場合、そこがトンネルから離れた位置であるかトンネルの入り口であるかで場合分けをする(fig.\ref{TTT_position1})。パスは次のbeadが固定された時の状態遷移である。
+
+%また、beadの位置とは別にトンネルの形状についても場合分けができる。三角格子上での対称性を考えるとトンネルの形状は以下の3つが考えられる(fig.\ref{TTT_tunnel})。この図において、バツが既にbeadが存在する頂点、白マルが空いている頂点である。また、トンネルの入口に注目すると、トンネルA,Bはどちらもトンネル内部に入る時のtranscriptのエッジに対して両側にbeadが存在する。一方でトンネルCは片側にのみbeadが存在する(fig.\ref{TTT_enterpoint})。出口についてはいずれのトンネルも同じ形になる(fig.\ref{TTT_exitpoint})。
+
+%今、トンネルAとトンネルBの場合だけを考える。Appendixより、各状態遷移においてbondの増加量の最大値をそれぞれのedgeに加えると以下のようになる(fig.\ref{TTT_position2})。ただし$a$は自然数とし、「次は外」の状態に遷移するたびに値が更新される。この図のように、トンネルの内と外を往来するとbondの数が減少する。
+
+%次にトンネルCについて考える。fig.\ref{TTT_enterpoint}とfig.\ref{TTT_exitpoint}よりトンネルCの入口にbeadが固定される時、トンネルの出口とトンネルCの入口は共存出来ないため、トンネルCは連続したトンネル構造の途中や出口に使用することはできない。これを考慮し、トンネルCが使用されるケースについて場合分けを考える(fig.\ref{TTT_tunnelC_graph})。この場合分けの内、上２つはトンネルA,Bの中へ入るためbondの数が減少する。そのため下２つについて考えれば良い。Appendixより、いずれの場合もbondの数が減少する。
+
+%以上より、トンネルA,B,Cのどれを消費した場合もbondの増加量は-1以下となる(fig.\ref{TTT_delta-1}は増加量が$-1$となる例)。よってこの定理は示された。
+
+\begin{figure}
   \begin{center}
@@
           \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.1];
+            \fill(0,0) circle [radius=0.05];
+            \node[above] at (180:1.5) {$p^\prime$};
+            \node[above] at (0:1.5) {$p^\prime$};
 
             \foreach \theta in {0,180}{
-              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
+              \fill[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.05];
             }
@@
           \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.1];
+            \fill(0,0) circle [radius=0.05];
+            \node[above] at (180:1.5) {$p^\prime$};
+            \node[above] at (-60:1.5) {$p^\prime$};
 
             \foreach \theta in {-60,180}{
-              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
+              \fill[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.05];
             }
@@
           \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.1];
+            \fill(0,0) circle [radius=0.05];
+            \node[above] at (180:1.5) {$p^\prime$};
+            \node[above] at (-1200:1.5) {$p^\prime$};
 
             \foreach \theta in {-120,180}{
-              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
+              \fill[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.05];
             }
@@
     \end{tabular}
-    \caption{トンネルの形状}
+    \caption{All possible tunnel sections}
     \label{TTT_tunnel}
@@
           \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.1];
+            \fill(0,0) circle [radius=0.1];
+            \node[above] at (180:1.5) {$p^\prime$};
+
             \fill[transform canvas={shift=(180:1.5)}](0,0) circle [radius=0.1];
@@
           \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.1];
+            \fill(0,0) circle [radius=0.1];
+            \node[above] at (180:1.5) {$p^\prime$};
 
@@
     \end{tabular}
-    \caption{トンネルの入り口}
+    \caption{Entrance of a tunnel}
     \label{TTT_enterpoint}
@@
 
-\begin{figure}[h]
-  \begin{center}
-    \begin{tikzpicture}
-      \draw[thick, rounded corners = 10pt]
-      (0,0)--(4,0)--(4,4)--(0,4)-- cycle;
+%\begin{figure}
+%  \begin{center}
+%    \begin{tikzpicture}
+%      \draw[thick, rounded corners = 10pt]
+%      (0,0)--(4,0)--(4,4)--(0,4)-- cycle;
+%
+%      \begin{scope}[xshift=2cm, yshift=2cm]
+%        \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
+%        \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
+%
+%        \foreach \theta in {0}{
+%          \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
+%        }
+%        
+%        \foreach \theta in {60,-60,120,-120,180}{
+%          \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
+%          \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+%        }
+%        \draw[->] (0.1,0) -- (1.4,0);
+%      \end{scope}
+%    \end{tikzpicture}
+%    \caption{トンネルの出口}
+%    \label{TTT_exitpoint}
+%  \end{center}
+%\end{figure}
 
-      \begin{scope}[xshift=2cm, yshift=2cm]
-        \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
-        \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
-
-        \foreach \theta in {0}{
-          \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
-        }
-
-        \foreach \theta in {60,-60,120,-120,180}{
-          \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-          \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
-        }
-        \draw[->] (0.1,0) -- (1.4,0);
-      \end{scope}
-    \end{tikzpicture}
-    \caption{トンネルの出口}
-    \label{TTT_exitpoint}
-  \end{center}
-\end{figure}
-
-今、トンネルAとトンネルBの場合だけを考える。Appendixより、各状態遷移においてbondの増加量の最大値をそれぞれのedgeに加えると以下のようになる(fig.\ref{TTT_position2})。ただし$a$は自然数とし、「次は外」の状態に遷移するたびに値が更新される。この図のように、トンネルの内と外を往来するとbondの数が減少する。
-
-次にトンネルCについて考える。fig.\ref{TTT_enterpoint}とfig.\ref{TTT_exitpoint}よりトンネルCの入口にbeadが固定される時、トンネルの出口とトンネルCの入口は共存出来ないため、トンネルCは連続したトンネル構造の途中や出口に使用することはできない。これを考慮し、トンネルCが使用されるケースについて場合分けを考える(fig.\ref{TTT_tunnelC_graph})。この場合分けの内、上２つはトンネルA,Bの中へ入るためbondの数が減少する。そのため下２つについて考えれば良い。Appendixより、いずれの場合もbondの数が減少する。
-
-以上より、トンネルA,B,Cのどれを消費した場合もbondの増加量は-1以下となる(fig.\ref{TTT_delta-1}は増加量が$-1$となる例)。よってこの定理は示された。
-
-\begin{figure}[h]
+\begin{figure}
   \begin{center}
@@
 
-\begin{figure}[h]
+\begin{figure}
   \begin{center}
@@
       (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
-      \node at(2.5,1) {Out of tunnels};
+      \node at(2.5,1) {Outside};
       \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
-      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Far away of tunnels};
+      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
 
@@
       (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
-      \node at(10.5,1) {トンネルの中};
-      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Next to a tunnel};
-      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Next to outside};
+      \node at(10.5,1) {Inside of a tunnel};
+      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
+      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
+
+      \draw[->]
+      (outside) edge [bend left] node[left] {$b$} (enter)
+                edge [loop left] node[left] {$b$} (outside)
+      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
+                edge [bend left] node[above] {$b$} (next-outside)
+                edge [bend left] node[right] {$b$}  (outside)
+      (next-tunnel) edge         node[right] {$t$} (next-outside)
+                edge [loop right]node[below] {$t$}    (next-tunnel)
+      (next-outside) edge[bend left] node[above] {$t$}  (outside)
+                edge [bend left]     node[above] {$t$}(enter)
+      ;
+
+    \end{tikzpicture}
+    \caption{Cases on position of a bead}
+    \label{TTT_position1}
+  \end{center}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \draw[thick]
+      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
+      \node at(2.5,1) {Outside};
+      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
+      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
+
+      \draw[thick]
+      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
+      \node at(10.5,1) {Inside of a tunnel};
+      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successer in inside};
+      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successer in outside};
 
@@
       (outside) edge [bend left] node[left] {$-1$} (enter)
-                edge [loop left, transform canvas={xshift=-1cm}] node[left] {$\pm 0$} (outside)
+                edge [loop left] node[left] {$\pm 0$} (outside)
       (enter)   edge [bend left] node[above] {$-1$} (next-tunnel)

### 2018-11-07 paper.tex
please write contents in this file

\documentclass[runningheads]{llncs}

\usepackage[dvipdfmx]{color}

\usepackage[dvipdfmx]{graphicx}
\usepackage{tikz}
\usepackage{calc}
\usetikzlibrary{automata}

\title{On finiteness of structures produced deterministically by co-transcriptional folding}
\author{}
\date{}

\begin{document}

\maketitle

\section{Introduction}

\section{Preliminary}

\section{Case of $\delta = 1$}

\section{Case of $\delta \geq 2$}

\end{document}

### 2018-11-08 paper.tex
Preliminaries writing started
I have just added a file "uos_preliminaries", which includes the tex
source for preliminaries. I will work on it so that please do not touch
it without any permission from me.
Title, Author, Institute
I added my name and institute. Please add your info by yourself.

@@
 
-\title{On finiteness of structures produced deterministically by co-transcriptional folding}
-\author{}
-\date{}
+\title{On finiteness of structures produced deterministically by oritatami co-transcriptional folding
+\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779}
+}
+\author{Shinnosuke Seki\inst{2}\thanks{Corresponding author (\email{s.seki@uec.ac.jp})}}
+\institute{Akita University 
+\and
+University of Electro-Communications, 1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan
+}
 
@@
 
+\begin{abstract}
+
+\end{abstract}
+
 \section{Introduction}
 
-\section{Preliminary}
+\section{Preliminaries}
+\input{uos_preliminaries.tex}
 

### 2018-11-08 uos_preliminaries.tex
Push before dinner
Nothing special to note.

Let $\Sigma$ be a set of types of abstract molecules, or \textit{beads}. 
By $\Sigma^*$ and $\Sigma^\omega$, we denote the set of finite sequences of beads and that of one-way infinite sequences of beads, respectively. 
A bead of type $a \in \Sigma$ is called an $a$-bead. 
Let $w = b_1 b_2 \cdots b_n \in \Sigma^*$ be a sequence of length $n$ for some integer $n$ and bead types $b_1, \ldots, b_n \in \Sigma$. 
The \textit{length} of $w$ is denoted by $|w|$, that is, $|w| = n$. 
For two indices $i, j$ with $1 \le i \le j \le n$, we let $w[i..j]$ refer to the subsequence $b_i b_{i+1} \cdots b_{j-1}b_j$; if $i = j$, then $w[i..i]$ is simplified as $w[i]$. 
For $k \ge 1$, $w[1..k]$ is called a \textit{prefix} of $w$.

Oritatami systems folds their transcript, which is a sequence of beads, over the triangular grid graph $\mathbb{T} = (V, E)$ cotranscriptionally. 
A directed path $P = p_1 p_2 \cdots p_n$ in $\mathbb{T}$ is a sequence of \textit{pairwise-distinct} points $p_1, p_2, \ldots, p_n \in V$ such that $\{p_i, p_{i+1}\} \in E$ for all $1 \le i < n$.

### 2018-11-08 ttt.tex

@@
-\documentclass[a4,dvipdfmx,11pt]{article}
-
-\usepackage{fancyhdr}
-\usepackage{amsmath,amssymb}
-\usepackage{fancybox,ascmac}
-\usepackage[]{multicol}
-\usepackage{caption}
-\usepackage{mathtools}
+\documentclass[runningheads]{llncs}
 
@@
 
-\usepackage{float}
 \usepackage[dvipdfmx]{graphicx}
@@
 \usetikzlibrary{automata}
-\usetikzlibrary{lindenmayersystems}
-\usepackage{geometry}
-
-\usepackage{amsthm}
-\usepackage{amsmath}
-
-\theoremstyle{definition}
-\newtheorem{myth}{Theorem}[section]
-\newtheorem{myproof}{Proof}[section]
 
 \begin{document}
+
+\title{On finiteness of structures produced deterministically by co-transcriptional folding}
 
@@
 
-%Tunnel sections and unbound beads, or more precisely, their some capabilities of binding, are the resources for beads to get stabilized deterministically at delay 1
-
 If a bead is stabilized through a tunnel section, then it can provide two binging capabilities and create tunnel sections.
@@
 
-%決定性Oritatami Systemでは転写されたbeadが固定される時、その位置は一意に定まる。
-%$\delta = 1$において転写されたbeadが一意に定まるためには、既に固定されている別のbeadとそのbeadがbondを結ぶか、あるいはトンネルを消費する必要がある。
-
-%ここで言う「トンネル」とは、ある三角格子上の点の周囲6点のうち、ちょうど4点が既に埋まっているような構造を指す。このトンネルの空いている頂点に直前のbeadが転写され、次のbeadがトンネルの中心に固定された時、そのbeadの周囲5点が埋まっていることになり、その次のbeadの位置は空いている1点に定まる。
-
-%この「トンネル」について以下が成り立つ。
-
-\begin{myth}[Tunnel Troll Theorem]
+\begin{theorem}[Tunnel Troll Theorem]
   Let $\Xi$ be an unary oritatami system of delay 1 and arity 2. If a bead is stabilized through a tunnel section, then it consume some binging capabilities.
-\end{myth}
+\end{theorem}
 
@@
 Let us consider tunnel sections only tunnel A and B.
-See Figure \ref{TTT_position2}.
-According to appendix, we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successer\ in\ outside$.
+See Fig.
+\ref{TTT_position2}.
+From appendix (Entrance of Tunnel A, B and Exit of Tunnel), we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successer\ in\ outside$.
 
@@
 Cases of $S[i...] = bt^l (l \geq 2)$ are already considered (Upper).
-According to appendix, cases of $S[i..i+2] = btb$ also consume some binding capabilities.
+According to appendix (Tunnel C), cases of $S[i..i+2] = btb$ also consume some binding capabilities (Lower).
 
 Thus, if a bead is stabilized through a tunnel section, then it consume some binging capabilities.
-
-%この定理を示すには、トンネルを消費した際に増加するbondの数より減少するbondの数の方が多いことを示せば良い。
-
-%まず直前に固定されたbeadがトンネルの中にいるか外にいるかで場合分けを考える。トンネルの中にいる場合、次のbeadの固定される位置は既に決定されているが、次に固定される位置が再びトンネルの中であるかトンネルの外であるかでも場合分けを考える。また、トンネルの外にいる場合、そこがトンネルから離れた位置であるかトンネルの入り口であるかで場合分けをする(fig.\ref{TTT_position1})。パスは次のbeadが固定された時の状態遷移である。
-
-%また、beadの位置とは別にトンネルの形状についても場合分けができる。三角格子上での対称性を考えるとトンネルの形状は以下の3つが考えられる(fig.\ref{TTT_tunnel})。この図において、バツが既にbeadが存在する頂点、白マルが空いている頂点である。また、トンネルの入口に注目すると、トンネルA,Bはどちらもトンネル内部に入る時のtranscriptのエッジに対して両側にbeadが存在する。一方でトンネルCは片側にのみbeadが存在する(fig.\ref{TTT_enterpoint})。出口についてはいずれのトンネルも同じ形になる(fig.\ref{TTT_exitpoint})。
-
-%今、トンネルAとトンネルBの場合だけを考える。Appendixより、各状態遷移においてbondの増加量の最大値をそれぞれのedgeに加えると以下のようになる(fig.\ref{TTT_position2})。ただし$a$は自然数とし、「次は外」の状態に遷移するたびに値が更新される。この図のように、トンネルの内と外を往来するとbondの数が減少する。
-
-%次にトンネルCについて考える。fig.\ref{TTT_enterpoint}とfig.\ref{TTT_exitpoint}よりトンネルCの入口にbeadが固定される時、トンネルの出口とトンネルCの入口は共存出来ないため、トンネルCは連続したトンネル構造の途中や出口に使用することはできない。これを考慮し、トンネルCが使用されるケースについて場合分けを考える(fig.\ref{TTT_tunnelC_graph})。この場合分けの内、上２つはトンネルA,Bの中へ入るためbondの数が減少する。そのため下２つについて考えれば良い。Appendixより、いずれの場合もbondの数が減少する。
-
-%以上より、トンネルA,B,Cのどれを消費した場合もbondの増加量は-1以下となる(fig.\ref{TTT_delta-1}は増加量が$-1$となる例)。よってこの定理は示された。
 
@@
 
-%\begin{figure}
-%  \begin{center}
-%    \begin{tikzpicture}
-%      \draw[thick, rounded corners = 10pt]
-%      (0,0)--(4,0)--(4,4)--(0,4)-- cycle;
-%
-%      \begin{scope}[xshift=2cm, yshift=2cm]
-%        \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
-%        \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
-%
-%        \foreach \theta in {0}{
-%          \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
-%        }
-%        
-%        \foreach \theta in {60,-60,120,-120,180}{
-%          \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-%          \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
-%        }
-%        \draw[->] (0.1,0) -- (1.4,0);
-%      \end{scope}
-%    \end{tikzpicture}
-%    \caption{トンネルの出口}
-%    \label{TTT_exitpoint}
-%  \end{center}
-%\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw[thick, rounded corners = 10pt]
-      (-2,-2)--(5,-2)--(5,3)--(-2,3)-- cycle;
-
-      \fill(0,0) circle [radius=0.1];
-      \foreach \theta in {60,-60,120}{
-        \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-        \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
-      }
-      \foreach \theta in {180,-120}{
-        \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
-      }
-
-      \draw[->] (120:1.4) -- (120:0.1);
-      \draw[dashed] (-60:0.1) -- (-60:1.4);
-
-      \begin{scope}[shift=(60:1.5)]
-        \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
-        \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
-
-        \foreach \theta in {60,120,0}{
-          \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-          \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
-        }
-
-        \draw[->] (60:1.4)--(60:0.1);
-        \draw[->] (180:0.1)--(180:1.4);
-        \draw[dashed] (120:0.1)--(120:1.4);
-        \draw[dashed] (0:0.1)--(0:1.4);
-
-        \begin{scope}[shift=(0:1.5)]
-          \foreach \theta in {60,0}{
-            \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-            \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
-          }
-          \draw[dashed] (120:0.1)--(120:1.4);
-          \draw (0:0.1)--(0:1.4);
-          \draw (60:0.1)--(60:1.4);
-        \end{scope}
-      \end{scope}
-      \begin{scope}[shift=(0:1.5)]
-        \fill(0,0) circle [radius=0.1];
-        \fill(0:1.5) circle [radius=0.1];
-        \draw(0:3) circle [radius=0.1];
-        \draw[shift=(0:1.5),shift=(-60:1.5)] circle [radius=0.1];
-        \foreach \theta in {-60}{
-          \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-          \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
-        }
-
-        \draw[->] (180:1.4)--(180:0.1);
-        \draw[->] (0:0.1)--(0:1.4);
-        \draw[->] (0:1.6)--(0:2.9);
-        \draw[dashed] (-60:0.1)--(-60:1.4);
-
-        \node[above] at (180:1.5) {$(-1)$};
-        \node[above] at (0:0) {$(-1)$};
-        \node[above] at (0:1.5) {$(+1)$};
-
-      \end{scope}
-    \end{tikzpicture}
-  \end{center}
-  \caption{増加量が$-1$となる例}
-  \label{TTT_delta-1}
-\end{figure}
-
 \begin{figure}
@@
     \begin{tikzpicture}
-      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {トンネルから離れている};
-      \node at (4.5,4) [rectangle, draw,rounded corners] (enter1)   {トンネルの入り口};
-      \node at (8,4)   [rectangle, draw, rounded corners] (inside1) {トンネルC};
-      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {トンネルA,Bの中};
+      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Otherwise};
+      \node at (4.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
+      \node at (8,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
+      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
       \draw[->] (outside1)--(enter1);
@@
 
-      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {トンネルの中};
-      \node at (4.5,3) [rectangle, draw,rounded corners] (enter2)   {トンネルの入り口};
-      \node at (8,3)   [rectangle, draw, rounded corners] (inside2) {トンネルC};
-      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {トンネルA,Bの中};     
+      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
+      \node at (4.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
+      \node at (8,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
+      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
       \draw[->] (outside2)--(enter2);
@@
 
-\newpage
-
 \subsection{Appendix of Tunnel Troll Theorem}
 \subsubsection{Entrance of TunnelA,B}
-Tunnelの入口に固定されたbeadが、どの方向から来たかで場合分けをする(fig.\ref{TTT_tunnel_direction})。
-その結果３通りの場合分けが出来るが、以下のようにいずれの場合もbondの総数は減少する。
+
+Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
+Any cases in $\delta = 1, \alpha = 2$ consume some binding capabilities into the follows.
 
 \begin{itemize}
-\item{Pattern1の時}\\
-  四角で表されてる2頂点が埋まっているかどうかで分けられる。もしどちらも埋まっているとすると、トンネルの入り口ではなくトンネルの中になってしまうので、必ず少なくとも一方は空いている。今、頂点cが空いているとする。すると頂点Aの周囲は3点以上空いている事になる。Aの周囲2頂点はback boneとしてつながっている。そのためもしBが既にbondを消費しているならば、残りの1頂点に存在するbeadとのみbondを結ぶ事となる。頂点Bの周囲は３点空いている事を考えるとBは1つ以上のbondを残している。そのため入口に固定されるbeadと必ずbondを結ぶ事になる。もし頂点dも空いている場合、固定されるbeadはbondを２つとも消費し、かつ既存のbondも２つ消費しbondの総数は減少する。頂点dが埋まっていたとしても、頂点Aとは同様にしてbondを結び、決定的に固定するために頂点Bかdとbondを結ぶ。故にいずれの場合もbondの総数は減少する。
+\item{Case of $t_0$}\\
+  Let us consider points of $c,d$ either occupied or not.
+A point $c$ or $d$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
+If $c$ is free, then $p^\prime$ has to be bound to a bead except $A$ due to deterministically stabilize.
+In this situation, at least three neighbors of A are free that is at most three neighbors of A are occupied.
+A leave at least one binging capability because beads of beighbors are predecessor and successor in addition A is able to consume itself binging capabilities only one-time.
+Hence, $p^\prime$ must be bound to A.
+Thus, a case of $t_0$ consumes some binding capabilities.
 
-\item{Pattern2の時}\\
-  Pattern1と同様にして頂点c,dが埋まっているかどうかで分けられる。Pattern1の例よりどちらも埋まっていることはない。頂点cが空いている場合決定的にbeadを固定するためにA,B少なくとも一方のbondを消費する。一方、頂点cが埋まっていて頂点dが空いている場合、Pattern1のように、固定されるbeadと頂点Bはbondを結ぶためbondを消費する。
+\item{Case of $t_{\pm 60}$}\\
+  In this case, a point $c$ or $d$ is free, too.
+If $c$ is free, $p^\prime$ has to be bound to A or B.
+If $c$ is occupied, then $d$ is free.
+This time, B has some binding capabilitie so $p^\prime$ has to be bound to B.
 
-  Pattern2の場合、固定されるbeadはbondを１つ増やす可能性がある。もし仮にbondが増えたとするならば、そのbondを使用するためはに頂点cかdにbeadが固定される必要がある。しかし今頂点BとPはback boneによってつながっている。Jordan curve theoremより、これ以降に転写され得るbeadの領域に頂点c,dは含まれないため、このbondを消費することはできず、bondの数は増加しない。よって既存のbondを減少させ、かつ新たに有効なbondを増やさないことからbondの総数は減少する。
+  In this situation, $p^\prime$ is able to supply a binding capability.
+if this capability is active, $p^\prime$ bind a bead into $c$ or $d$.
+However, B and P are exist in back bone.
+According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $c$ or $d$ so this capability is inactive.
+Thus, a case of $t_{\pm 60}$ consumes some binding capabilities.
 
-\item{Pattern3の時}\\
-  頂点nは空いているため、決定的に固定するために頂点c,d,eのいずれかとbondを結ぶ必要がある、そのため既存のbondを消費する。一方、固定されるbeadはbondを１つ増やす可能性があるが、pattern2と同様に頂点AとPがback boneでつながっているため、これ以降に転写され得るbeadの領域に頂点c,d,eは含まれていないため、増やされるbondを使用できない。よって既存のbondを減少させ、かつ新たに有効なbondを増やさないことからbondの総数は減少する。
+\item{Case of $t_{\pm 120}$}\\
+  Binding capabilities that $p^\prime$ supply are inactive according to Jordan curve theorem on A and P.
+Moreover, $p^\prime$ has to be bound to one of $c$, $d$,$e$ in order to deterministically stabilize.
+Thus, a case of $t_{\pm 120}$ consumes some binging capabilities.
 
@@
             \fill(0,0) circle [radius=0.1];
+            \node[above] at (0,0) {$p^\prime$};
 
@@
 
-          \node at (2,-0.5) {Pattern 1};
+          \node at (2,-0.5) {$t_0$};
         \end{tikzpicture}
@@
             \fill(0,0) circle [radius=0.1];
+            \node[below] at (0,0) {$p^\prime$};
 
@@
 
-          \node at (2,-0.5) {Pattern 2};
+          \node at (2,-0.5) {$t_{\pm 60}$};
         \end{tikzpicture}
@@
 
-          \node at (2,-0.5) {Pattern 3};
+          \node at (2,-0.5) {$t_{\pm 120}$};
         \end{tikzpicture}
@@
     \end{tabular}
-    \caption{入口へ至る方向}
+    \caption{Direction into a entrance}
     \label{TTT_tunnel_direction}
@@
 
-Tunnelの出口について場合分けを考える(fig.\ref{TTT_tunnel_exit})。この場合分けは頂点c,dについてその頂点が既に埋まっているか埋まっていないかで場合分けされている。なお、頂点c,dの両方とも埋まっている場合は、Tunnelの出口ではなくトンネルの中になるため場合分けに含めない。今、出口に固定されるbeadの1つ前のbeadが、$a$以下のbond消費したとする。すると以下で示されるようにTunnelの出口で増加するbondの数は高々$a$程度となる。つまり、Tunnelを出る事によって増加するbondの最大値は$0$となる。
+Fig.\ref{TTT_tunnel_exit} exhibits all the two kings of exit of tunnel. 
+At least one of point $c$ or $d$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
+
+\paragraph{$\delta = 1, \alpha = 2$}
+ Any cases of $\delta = 1, \alpha = 2$ supply at most $a$ binding capabilities into follows where $a$ is number of predecessor of $p^\prime$ consumes binging capabilities.
 
 \begin{itemize}
-\item{Pattern1の時}\\
-  頂点c,dが空いていたとする。入口の時と同様に考えると、頂点A,Bはbondを残しているため、頂点Pは頂点A,Bとbondを結ぶ。すなわち$a=2$となる。$\alpha = 2$を考えるとTunnel出口に固定されるbeadのよって増加するbondは高々$a=2$程度。
-\item{Pattern2の時}\\
-  頂点cのみが埋まっていたとする。頂点Bはbondを残しているため、頂点PとBはbondを結ぶ。よって$a \geq 1$また、Tunnel出口で固定されるbeadはbondを$2$増加させる可能性があるが、空いている頂点e,dについて一方はback boneとして消費されるため、このbeadが増加させたbondを使用できるのは後にbeadが頂点e,dのいずれかに来た時のみ。よってTunnel出口に固定されるbeadは有効なbondを高々$1$程度しか増やさない。よって増加するbondの数は高々$a$程度であることが言える。
+\item{Case of $c$ and $d$ are free}\\
+  This case can be regarded same situation as entrance.
+See Fig.\ref{TTT_tunnel_exit} (Left).
+Predecessor P has to be bound A and B because each of A and B leave binding capabilities.
+Hence, at least $a=2$.
+This time, $\alpha = 2$ that is this case supply at most only $a$ binding capabilities.
 
+\item{Case of $c$ is occupied}\\
+  See Fig.\ref{TTT_tunnel_exit} (Right).
+If $c$ is pccupied, then $d$ is free so that P has to be bound B.
+Hence, at least $a=1$.
+This case can supply two binding capabilities but $p^\prime$ can bind to only one of $e$ or $d$ because $e$ or $d$ will be occupied a successor of $p^\prime$.
+Therefore, this case supply at most only $a=1$ active binding capabiliry.
+
+\end{itemize}
+
+\paragraph{$\delta = 1, \alpha \geq 3$}
+Any cases of $\delta = 1, \alpha \geq 3$ consume some binding capabilities into follows.
+
+\begin{itemize}
+\item{Case of $c$ and $d$ are free}\\
+  In $\alpha \geq 3$, if three neighbors of a bead leave, then it can supply two binding capabilities.
+Therefore Predecessor P has to be bound A and B, and $p^\prime$, too.
+In this case, at least consumes four bindings and supplies at most two bindings.
+Thus, it consumes some binding capabilities, totally.
+
+\item{Case of $c$ is occupied}\\
+  In this case, B leave at least two bindings and A, $c$ also leave at least one binding.
+Therefore P has to be bound A and B, and $p^\prime$ also has to be bound B and $c$.
+In this case, at least consumes four bindings and supplies at most one binding.
+Thus, it consumes some binding capabiliries, totally.
 \end{itemize}
@@
 
-          \node at (2,-0.5) {Pattern 1};
+          \node at (2,-0.5) {Point $c$ and $d$ are free};
         \end{tikzpicture}
@@
 
-          \node at (2,-0.5) {Pattern 2};
+          \node at (2,-0.5) {Point $c$ is occupied};
         \end{tikzpicture}
@@
     \end{tabular}
-    \caption{出口のパターン}
+    \caption{Exit of Tunnel}
     \label{TTT_tunnel_exit}
@@
 
+By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
+
 \end{document}

### 2018-11-08 uos_preliminaries.tex
Push before going to bed
Still writing preliminaries

@@
 Let $\Sigma$ be a set of types of abstract molecules, or \textit{beads}. 
+A bead of type $a \in \Sigma$ is called an $a$-bead. 
 By $\Sigma^*$ and $\Sigma^\omega$, we denote the set of finite sequences of beads and that of one-way infinite sequences of beads, respectively. 
-A bead of type $a \in \Sigma$ is called an $a$-bead. 
+The empty sequence is denoted by $\lambda$. 
 Let $w = b_1 b_2 \cdots b_n \in \Sigma^*$ be a sequence of length $n$ for some integer $n$ and bead types $b_1, \ldots, b_n \in \Sigma$. 
@@
 Oritatami systems folds their transcript, which is a sequence of beads, over the triangular grid graph $\mathbb{T} = (V, E)$ cotranscriptionally. 
+We designate one point in $V$ as the origin $O$ of $\mathbb{T}$. 
 A directed path $P = p_1 p_2 \cdots p_n$ in $\mathbb{T}$ is a sequence of \textit{pairwise-distinct} points $p_1, p_2, \ldots, p_n \in V$ such that $\{p_i, p_{i+1}\} \in E$ for all $1 \le i < n$. 
+Its $i$-th point is referred to as $P[i]$. 
+Now we are ready to abstract RNA single-stranded structures in the name of conformation. 
+A \textit{conformation} $C$ is a triple $(P, w, H)$ of a directed path $P$ in $\mathbb{T}$, $w \in \Sigma^*$ of the same length as $P$, and a set of h-interactions $H \subseteq \bigl\{\{i, j\} \bigm| 1 \le i, i+2 \le j, \{P[i], P[j]\} \in E \bigr\}$.
+This is to be interpreted as the sequence $w$ being folded along the path $P$ in such a manner that its $i$-th bead $w[i]$ is placed at the $i$-th point $P[i]$ and the $i$-th and $j$-th beads are bound (by a hydrogen-bond-based interaction) if and only if $\{i, j\} \in H$.
+The condition $i+2 \le j$ represents the topological restriction that two consecutive beads along the path cannot be bound. 
+A \textit{rule set} $R \subseteq \Sigma \times \Sigma$ is a symmetric relation over $\Sigma$, that is, for all bead types $a, b \in \Sigma$, $(a, b) \in R$ implies $(b, a) \in R$. 
+A bond $\{i, j\} \in H$ is \textit{valid with respect to $R$}, or simply $R$-valid, if $(w[i], w[j]) \in R$. 
+This conformation $C$ is \textit{$R$-valid} if all of its bonds are $R$-valid. 
+For an integer $\alpha \ge 1$, $C$ is \textit{of arity $\alpha$} if it contains a bead that forms $\alpha$ bonds but none of its bead forms more. 
+By $\mathcal{C}_{\le \alpha}$, we denote the set of all conformations of arity at most $\alpha$.
+
+The oritatami system grows conformations by an operation called elongation. 
+Given a rule set $R$ and an $R$-valid conformation $C_1 = (P, w, H)$, we say that another conformation $C_2$ is an elongation of $C_1$ by a bead $b \in \Sigma$, written as $C_1 \xrightarrow{R}_b C_2$, if $C_2 = (P p, wb, H \cup H')$ for some point $p \in V$ not along the path $P$ and set $H' \subseteq \bigl\{ \{i, |w|+1\} \bigm| 1 \le i < |w|, \{P[i], p\} \in E, (w[i], b) \in R \bigr\}$ of bonds formed by the $b$-bead; this set $H'$ can be empty.
+Note that $C_2$ is also $R$-valid. 
+This operation is recursively extended to the elongation by a finite sequence of beads as: for any conformation $C$, $C \xrightarrow{R}_\lambda^* C$; and for a finite sequence of beads $w \in \Sigma^*$ and a bead $b \in \Sigma$, a conformation $C_1$ is elongated to a conformation $C_2$ by $wb$, written as $C_1 \xrightarrow{R}_{wb}^* C_2$, if there is a conformation $C'$ that satisfies $C_1 \xrightarrow{R}_w^* C'$ and $C' \xrightarrow{R}_b C_2$.
+
+An \textit{oritatami system} (OS) is a 6-tuple $\Xi = (\Sigma, R, \alpha, \delta, \sigma, w)$, where $R$ is a rule set, $\alpha$ is an arity, $\delta \ge 1$ is a parameter called the \textit{delay}, $\sigma$ is an initial $R$-valid conformation of arity at most $\alpha$ called the \textit{seed}, upon which its finite \textit{transcript} $w \in \Sigma^*$ is to be folded by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads.
+The energy of a conformation $C = (P, w, H)$, denoted by $\Delta G(C)$, is defined to be ${-}|H|$; the more bonds a conformation has, the more stable it gets. 
+The set $\mathcal{F}(\Xi)$ of conformations \textit{foldable} by the system $\Xi$ is recursively defined as: the seed $\sigma$ is in $\mathcal{F}(\Xi)$; and provided that an elongation $C_i$ of $\sigma$ by the prefix $w[1..i]$ be foldable (i.e., $C_0 = \sigma$), its further elongation $C_{i+1}$ by the next bead $w[i+1]$ is foldable if
+\begin{equation}\label{eq:folding}
+C_{i+1} \in \argmin_{
+\substack{
+C \in \mathcal{C}_{\le \alpha} s.t. \\
+C_i \xrightarrow{R}_{w[i+1]}C \\
+}
+}
+\min \Bigl\{ \Delta G(C') \Bigm|
+C \xrightarrow{R}^*_{w[i+2...i+k]}C', k\le \delta, C' \in \mathcal{C}_{\le \alpha}
+\Bigr\}.
+\end{equation}

### 2018-11-08 ttt.tex

@@
 
-Tunnel Cの入口に固定されるbeadについて、そのbeadがTunnelを消費して固定されたか、
-そうでないかによって場合分けをする。なお、Tunnel Cの出口はTunnelA,Bの中でないとする。
+Assume $w[i]$ is a bead which stabilized by tunnel C. Let us consider kinds of stabilization $S[i-2..i] = tbt$ or $S[i-2..i] = bbt$ except cases of $w[i]$ is inside of tunnel A, B.
 
-\subsubsection{Tunnel Cの入口のbeadがTunnelを消費して固定された場合}
-Tunnel Cの構造を維持したまま入口にTunnel消費によるbeadを固定するパターンはfig.\ref{TTT_tunnelC_enter_usingTunnel}の２通りがある。
+\subsubsection{Case of $S[i-2..i] = tbt$}
+Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
 
 \begin{itemize}
-\item{Pattern1}\\
-  頂点$t_1$が転写される前では、$t_3$がトンネルの外であることから頂点Aの周囲3点は空いてる。よって頂点Aのbeadは1つ以上bondを持つため、頂点Aと$t_1$はbondを結ぶ。また、頂点$t_2$が決定的に固定されるためには頂点B,C,Dとの間とbondを結ぶ必要がある。一方で、頂点$t_1,t_2$は、たとえbondを増やしたとしても周囲6点が埋まっているため、それを使うことができない。つまり$t_2$が固定された時点でbondは$2$減少している。今、$t_3$が固定された時を考えると、このbeadはbondを最大で2つ増やす可能性がある。しかし今$t_3$の周囲で空いているのは頂点e,fで、このうち一方はback boneのために使われるため、$t_3$の増やしたbondは1つのみが有効なbondとなる。よって全体でbondの総数を1以上減少させる。
+\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
+  In this figure, Bead A has at least one binding so that $w_{i-2}$ has to bound A.
+Moreover, $w_{i-1}$ has to bound one of B, C, D in order to stabilize deterministically.
+On the other hand, $w_i$ can supply two bindings but free neighbors of $w_i$ are two points.
+One of them is occupied a successor.
+Therefore $w_i$ can only bind one of $e,f$ that is $w_i$ supplies at most one binding.
+Thus, this case consumes some binding capabilities.
 
-\item{Pattern2}\\
-  頂点$t_1$が固定される時そのbeadが幾つ周囲のbondを消費するかで場合分けできる。
+\item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
+  This cases are divided on number of capabilities that $w_{i-2}$ consumes.
   \begin{itemize}
-  \item[-]{$t_1$がbondを消費しない場合}\\
-    頂点$t_2$が決定的に固定される時、bondを1以上消費しかつ有効なbondを増やさない。頂点$t_3$が固定される時、頂点$t_1$はbondを持っているため、$t_3$,$t_1$の間でbondを結ぶ。よって$t_3$の固定で増加するbondの数は0以下。一方で、この時$t_1$はまだ有効なbondを一つ持っている。もし頂点eが埋まっているならこのbondは有効でなくなりbondの総数は減少する。そこで仮に頂点eが空いている場合を考える。今$t_3$の次に固定されるbeadを$t_4$とする。もし$t_4$が頂点eに固定されたなら、$t_1$のbondを消費しかつ$t_4$はbondを1つ消費し1つ増やす。よって$t_1$から$t_4$の固定においてbondの総数は減少する。次に$t_4$が頂点f,gのどちらかに固定される場合を考える。頂点eは空いているため、決定的に固定するに$t_4$は2つのbondを消費する必要がある。よって$t_1$が増やしたbondを加味してもbond$t_1$から$t_4$の固定でbondの総数を減らすことになる。よっていずれのケースを考えてもbondの総数は減少する。
+  \item[-]{$w_i$ does not consume any bindings}\\
+    $w_{i-1}$ has to bound one of B, C, D in order to stabilize deterministically.
+$w_i$ has to be bound to $w_{i-2}$ because $w_{i-2}$ has bindings.
+This time, let us consider either $e$ is occupied or not.
+If $e$ is occupied, then $w_{i-2}$ has no active bindings that is this situation consumes some binding capabilities.
+If $e$ is free and $w_{i+1}$ is stabilized in $e$, then $w_{i-2}$ has to bind $w_{i+1}$.
+Therefore, In this case, stabilization of $w[i-2..i+1]$ consumes some bindings.
+If $e$ is free and $w_{i+1}$ is stabilized except $e$, then this oritatami system has to use two binding capabilities in order to bind $w_{i+1}$.
+Therefore, in this case consumes some bindings.
+Thus in this cases consume some binding capabilities.
 
-  \item[-]{$t_1$がbondを1つ消費する場合}\\
-    $t_2$は同様にしてbondの総数を1つ減少させ、$t_3$も増加させるbondの数は0以下。この時$t_1$はbondを増やさない。よってbondの総数は2以上減少する。
-  \item[-]{$t_1$がbondを2つ消費する場合}\\
-    $t_2$はbondを1つ以上減少させ、$t_3$はbondを2つ増加させる。よってbondの総数は減少する。
+  \item[-]{$w_i$ consumes one binding}\\
+    In this case, $w_{i-1}$ has to be bound one of B, C, D. In addition, $w_{i-2}$ and $w_i$ are not supply any bindings. Thus, in this cases consume some binding capabilities.。
+  \item[-]{$w_i$ consumes two bindings}\\
+    In this case, $w_{i-2}$ already consumes two binding. $w_{i-1}$ has to be bound. $w_i$ supplies two bindings. Thus, in this cases consume some binding capabilities.
+
   \end{itemize}
@@
 
-            \node[below] at (180:1.5) {$t_1$};
-            \node[right] at (0:0) {$t_2$};
-            \node[right] at (-120:1.5) {$t_3$};
+            \node[below] at (180:1.5) {$w_{i-2}$};
+            \node[right] at (0:0) {$w_{i-1}$};
+            \node[right] at (-120:1.5) {$w_i$};
 
@@
     \end{tabular}
-    \caption{Tunnelを消費して入口に固定されたbead}
+    \caption{Case of $S[i-2..i] = tbt$}
     \label{TTT_tunnelC_enter_usingTunnel}
@@
 
-\subsubsection{TunnelCの入口のbeadがTunnelを使わずに固定された場合}
-TunnelCの入口のbeadがTunnelを使わずに固定される時、そのbeadは既存のbondを使うことによって固定される。fig.\ref{TTT_tunnelC_enter_usingBond}において$t_1$がいくつのbondを消費したかで場合分けを考える。
+\subsubsection{Case of $S[i-2..i] = bbt$}
+Let us consider number of consumed by $w_{i-2}$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
 
 \begin{itemize}
-\item{$t_1$が1つのbondを消費する場合}\\
-  この時$t_1$は1つの有効なbondを生み出す。$t_2$は頂点A,B,Cの少なくとも一つとbondを結ぶ必要があり、かつ有効なbondを増やさない。$t_3$について考えると、$t_1$がbondを残していることから$t_3$と$t_1$はbondで結ばれる。故にbondの総数は1以上減少する。
+\item{$w_{i-2}$ consumes one binding}\\
+  In this situation, $w_{i-2}$ supplies one active binding whereas $w_{i}$ consumes this binding. In addtion, $w_{i-1}$ has to bound to one of A, B, C.
+  Thus, in this cases consume some binding capabilities.
 
-\item{$t_1$が2つのbondを消費する場合}\\
-  この時$t_1$はbondを生み出さない。$t_2$については先程と同様bondの総数を1減らす。今、$t_3$はどのbeadともbondを結ばない可能性があるため、bondの総数を最大で2増加させる。故にbondの総数は1以上減少する。
+\item{$w_{i-2}$ consumes two bindings}\\
+  In this case, $w_{i-2}$ already consumes two binding. $w_{i-1}$ has to be bound. $w_i$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
 \end{itemize}
@@
     \end{tabular}
-    \caption{Tunnelを消費せずに入口に固定されたbead}
+    \caption{Case of $S[i-2..i] = bbt$}
     \label{TTT_tunnelC_enter_usingBond}

### 2018-11-09 paper.tex
Push before dinner
Nothing special to note.
Push before going to bed
Still writing preliminaries
More grant info added
I added the info on my JST grant.

@@
 \usepackage{calc}
+
+\usepackage{amsmath, amssymb}
+\DeclareMathOperator*{\argmin}{arg\,min}
+
 \usetikzlibrary{automata}
@@
 \title{On finiteness of structures produced deterministically by oritatami co-transcriptional folding
-\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779}
+\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~S.}
 }
@@
 \and
-University of Electro-Communications, 1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan
+The University of Electro-Communications, 1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan
 }

### 2018-11-09 uos_preliminaries.tex
More grant info added
I added the info on my JST grant.

@@
 Now we are ready to abstract RNA single-stranded structures in the name of conformation. 
-A \textit{conformation} $C$ is a triple $(P, w, H)$ of a directed path $P$ in $\mathbb{T}$, $w \in \Sigma^*$ of the same length as $P$, and a set of h-interactions $H \subseteq \bigl\{\{i, j\} \bigm| 1 \le i, i+2 \le j, \{P[i], P[j]\} \in E \bigr\}$.
+A \textit{conformation} $C$ (over $\Sigma$) is a triple $(P, w, H)$ of a directed path $P$ in $\mathbb{T}$, $w \in \Sigma^*$ of the same length as $P$, and a set of h-interactions $H \subseteq \bigl\{\{i, j\} \bigm| 1 \le i, i+2 \le j, \{P[i], P[j]\} \in E \bigr\}$.
 This is to be interpreted as the sequence $w$ being folded along the path $P$ in such a manner that its $i$-th bead $w[i]$ is placed at the $i$-th point $P[i]$ and the $i$-th and $j$-th beads are bound (by a hydrogen-bond-based interaction) if and only if $\{i, j\} \in H$.
@@
 
-An \textit{oritatami system} (OS) is a 6-tuple $\Xi = (\Sigma, R, \alpha, \delta, \sigma, w)$, where $R$ is a rule set, $\alpha$ is an arity, $\delta \ge 1$ is a parameter called the \textit{delay}, $\sigma$ is an initial $R$-valid conformation of arity at most $\alpha$ called the \textit{seed}, upon which its finite \textit{transcript} $w \in \Sigma^*$ is to be folded by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads.
+An \textit{oritatami system} (OS) is a 6-tuple $\Xi = (\Sigma, R, \alpha, \delta, \sigma, w)$, where $\Sigma$ is a set of bead types, $R\subseteq \Sigma \times \Sigma$ is a rule set, $\alpha$ is an arity, $\delta \ge 1$ is a parameter called the \textit{delay}, $\sigma$ is an initial $R$-valid conformation of arity at most $\alpha$ over $\Sigma$ called the \textit{seed}, upon which its finite \textit{transcript} $w \in \Sigma^*$ is to be folded by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads.
 The energy of a conformation $C = (P, w, H)$, denoted by $\Delta G(C)$, is defined to be ${-}|H|$; the more bonds a conformation has, the more stable it gets. 
 The set $\mathcal{F}(\Xi)$ of conformations \textit{foldable} by the system $\Xi$ is recursively defined as: the seed $\sigma$ is in $\mathcal{F}(\Xi)$; and provided that an elongation $C_i$ of $\sigma$ by the prefix $w[1..i]$ be foldable (i.e., $C_0 = \sigma$), its further elongation $C_{i+1}$ by the next bead $w[i+1]$ is foldable if
-\begin{equation}\label{eq:folding}
+\begin{equation}\label{eq:OS_CF}
 C_{i+1} \in \argmin_{
@@
 \end{equation}
+%
+Then we say that the bead $w[i+1]$ and the bonds it forms are \textit{stabilized} according to $C_{i+1}$. 
+Note that an arity-$\alpha$ oritatami system cannot fold any conformation of arity larger than $\alpha$. 
+A conformation foldable by $\Xi$ is \textit{terminal} if none of its elongations is foldable by $\Xi$. 
+The OS $\Xi$ is \textit{deterministic} if for all $i \ge 0$, there exists at most one $C_{i+1}$ that satisfies \eqref{eq:OS_CF}. 
+A deterministic oritatami system folds into a unique terminal conformation.
+
+In this paper, we mainly consider the unary oritatami system. 
+An oritatami system is \textit{unary} if its bead type set $\Sigma$ is of size 1. 
+Its sole element is denoted by $a$, that is, $\Sigma = \{a\}$. 
+Its only possible rule is $(a, a)$ and without that, the system would not fold into anything meaningful but just into any elongation of its seed nondeterministically.

### 2018-11-09 uos_preliminaries.tex
Preliminaries almost done.
We should add anything, whenever the need arises.

@@
 A deterministic oritatami system folds into a unique terminal conformation. 
+An oritatami system with the empty rule set just folds into an arbitrary elongation of its seed nondeterministically. 
+Thus, the rule set is always assumed to be non-empty.
 
@@
 An oritatami system is \textit{unary} if its bead type set $\Sigma$ is of size 1. 
-Its sole element is denoted by $a$, that is, $\Sigma = \{a\}$. 
-Its only possible rule is $(a, a)$ and without that, the system would not fold into anything meaningful but just into any elongation of its seed nondeterministically.
+Its sole bead type is denoted by $a$, that is, $\Sigma = \{a\}$. 
+Its only possible rule is $(a, a)$ so that the non-empty rule set assumption implies that its rule set is $R = \{(a, a)\}$. 
+Its transcript is a sequence of $a$-beads. 
+That is to say, the behavior of a unary oritatami system is fully determined by the delay, arity, and seed.

### 2018-11-09 paper.tex
Update before lunch
Theorem 1 is added, but I'm still working on it.

@@
 
+\usepackage{wasysym}
+
 \usetikzlibrary{automata}
@@
 }
-\author{Shinnosuke Seki\inst{2}\thanks{Corresponding author (\email{s.seki@uec.ac.jp})}}
-\institute{Akita University 
+\author{
+Szil\'{a}rd Zsolt Fazekas\inst{1} \and
+Shinnosuke Seki\inst{2}\thanks{Corresponding author}}
+\institute{
+Akita University, 
+Graduate School of Engineering Science, 
+1-1 Tegate Gakuen-machi, Akita, 0108502, Japan \\
+\email{szilard.fazekas@ie.akita-u.ac.jp}
 \and
-The University of Electro-Communications, 1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan
+The University of Electro-Communications, 
+Graduate School of Informatics and Engineering, 
+1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan \\
+\email{s.seki@uec.ac.jp}
 }
@@
 
+\begin{theorem}\label{thm:OS_to_2dTM}
+	There exists a Turing machine with 2-dimensional tape that simulates any oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time $O(((|\sigma| + |w|)\delta)^\delta)$. 
+\end{theorem}
+\begin{proof}
+	Take any step in the computation, up to which some $i \ge 0$ first beads of $w$ have been stabilized, with the last bead at a point $p$. 
+	The number of all possible elongations of the current conformation by the next $\delta$-beads is $(6 \times 5^{\delta-1}) \times ((2^4)^{\delta-1} \times 2^5)$. 
+\end{proof}
+
 \section{Case of $\delta = 1$}

### 2018-11-09 uos_preliminaries.tex
Update before lunch
Theorem 1 is added, but I'm still working on it.

@@
 
-Oritatami systems folds their transcript, which is a sequence of beads, over the triangular grid graph $\mathbb{T} = (V, E)$ cotranscriptionally. 
+Oritatami systems fold their transcript, which is a sequence of beads, over the triangular grid graph $\mathbb{T} = (V, E)$ cotranscriptionally. 
 We designate one point in $V$ as the origin $O$ of $\mathbb{T}$. 
+For a point $p \in V$, let $\hexagon_p^d$ denote the set of points which lie in the regular hexagon of radius $d$ centered at the point $p$. 
 A directed path $P = p_1 p_2 \cdots p_n$ in $\mathbb{T}$ is a sequence of \textit{pairwise-distinct} points $p_1, p_2, \ldots, p_n \in V$ such that $\{p_i, p_{i+1}\} \in E$ for all $1 \le i < n$. 
@@
 For an integer $\alpha \ge 1$, $C$ is \textit{of arity $\alpha$} if it contains a bead that forms $\alpha$ bonds but none of its bead forms more. 
-By $\mathcal{C}_{\le \alpha}$, we denote the set of all conformations of arity at most $\alpha$.
+By $\mathcal{C}_{\le \alpha}(\Sigma)$, we denote the set of all conformations over $\Sigma$ whose arity is at most $\alpha$; its argument $\Sigma$ is omitted whenever $\Sigma$ is clear from the context.
 
@@
 
-An \textit{oritatami system} (OS) is a 6-tuple $\Xi = (\Sigma, R, \alpha, \delta, \sigma, w)$, where $\Sigma$ is a set of bead types, $R\subseteq \Sigma \times \Sigma$ is a rule set, $\alpha$ is an arity, $\delta \ge 1$ is a parameter called the \textit{delay}, $\sigma$ is an initial $R$-valid conformation of arity at most $\alpha$ over $\Sigma$ called the \textit{seed}, upon which its finite \textit{transcript} $w \in \Sigma^*$ is to be folded by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads.
+An \textit{oritatami system} (OS) $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ is composed of
+\begin{itemize}
+\item a set $\Sigma$ of bead types, 
+\item a rule set $R \subseteq \Sigma \times \Sigma$, 
+\item a positive integer $\delta$ called the \textit{delay}, 
+\item a positive integer $\alpha$ called the \textit{arity}, 
+\item an initial $R$-valid conformation $\sigma \in C_{\le \alpha}(\Sigma)$ called the \textit{seed}, upon which 
+\item its (possibly infinite) \textit{transcript} $w \in \Sigma^* \cup \Sigma^\omega$ is to be folded by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads.
+\end{itemize}
 The energy of a conformation $C = (P, w, H)$, denoted by $\Delta G(C)$, is defined to be ${-}|H|$; the more bonds a conformation has, the more stable it gets. 
@@
 A conformation foldable by $\Xi$ is \textit{terminal} if none of its elongations is foldable by $\Xi$. 
-The OS $\Xi$ is \textit{deterministic} if for all $i \ge 0$, there exists at most one $C_{i+1}$ that satisfies \eqref{eq:OS_CF}. 
+The oritatami system $\Xi$ is \textit{deterministic} if for all $i \ge 0$, there exists at most one $C_{i+1}$ that satisfies \eqref{eq:OS_CF}. 
 A deterministic oritatami system folds into a unique terminal conformation. 
@@
 
-In this paper, we mainly consider the unary oritatami system. 
+In the second half of this paper, we consider the unary oritatami system. 
 An oritatami system is \textit{unary} if its bead type set $\Sigma$ is of size 1. 

### 2018-11-09 ttt.tex
11/9 en

@@
 \usepackage{calc}
+\usepackage{amsmath,amssymb}
 \usetikzlibrary{automata}
@@
 By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
+If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$.
+Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities.
+Therefore formula \ref{TTT_only_hold} hold.
+
+\begin{eqnarray}
+  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
+  \label{TTT_only_bond}
+\end{eqnarray}
+
+Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
+
+Let us consider the case of $v_k$ is $o$.
+See Fig.\ref{TTT_case_of_o}.
+$v_{i-1}$ consumes some binding capabilities because $S[i-1]$ is $b$.
+If the number of $v_{i-1}$'s bindings is one binding, then $v_{i+1}$ has to be bound except A or B so that $v_{i+1}$ must consumes two bindings except the case of A and B are occupied and $v_i$ consumes at least one binding.
+If A and B are occupied, then $v_{i-1}$'s binginds are inactive that is $v_{i-1}$ consumes two binding capabilities.
+Therefore, this case consumes binding capabilities.
+If $v_{i-1}$ dose Not have any bindings, then $v_{i-1}$ already consumes two bindings.
+In addition, $v_i$ and $v_{i+1}$ consume at least one binding.
+Therefore this case consumes binding capabilities.
+Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.
+
+\begin{eqnarray}
+  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
+  \label{TTT_only_a}
+\end{eqnarray}
+
+\begin{eqnarray}
+  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
+  \label{TTT_structure}
+\end{eqnarray}
+
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \draw[thick, rounded corners = 10pt]
+      (-1.5,2)--(3,2)--(3,-2.5)--(-1.5,-2.5)-- cycle;
+
+      \draw[transform canvas={shift=(-120:1.5)}](-0.1,-0.1)--(0.1,0.1);
+      \draw[transform canvas={shift=(-120:1.5)}](0.1,-0.1)--(-0.1,0.1);
+
+      \fill(0:0) circle [radius=0.1];
+      \fill(0:1.5) circle [radius=0.1];
+      \fill[shift=(0:1.5)](40:1.5) circle [radius=0.1];
+
+      \draw[->] (-120:1.4) edge[bend left] (-120:0.1);
+      \draw[->] (0:0) -- (0:1.3);
+      \draw[->,transform canvas={shift=(0:1.5)}] (0:0.1) edge[bend right] (40:1.3);
+
+      \draw [shift=(60:1.5)] (-0.1,-0.1) rectangle (0.1,0.1);
+      \draw [shift=(-60:1.5)] (-0.1,-0.1) rectangle (0.1,0.1);
+
+      \node[below] at (-120:1.5) {$v_{i-2}$};
+      \node[above] at (0:0) {$v_{i-1}$};
+      \node[above] at (0:1.5) {$v_i$};
+      \node[left, shift=(0:1.5)] at (40:1.5) {$v_{i+1}$};
+
+      \node[right] at (60:1.5) {A};
+      \node[right] at (-60:1.5) {B};
+
+    \end{tikzpicture}
+    \caption{Case of $S[i$}
+    \label{TTT_case_of_o}
+  \end{center}
+\end{figure}
 

### 2018-11-09 paper.tex
Update
Theorem 1, more contents added.

@@
 \begin{theorem}\label{thm:OS_to_2dTM}
-	There exists a Turing machine with 2-dimensional tape that simulates any oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time $O(((|\sigma| + |w|)\delta)^\delta)$. 
+	There exists a Turing machine with 2-dimensional tape that simulates any oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time ??. 
 \end{theorem}
@@
 	Take any step in the computation, up to which some $i \ge 0$ first beads of $w$ have been stabilized, with the last bead at a point $p$. 
-	The number of all possible elongations of the current conformation by the next $\delta$-beads is $(6 \times 5^{\delta-1}) \times ((2^4)^{\delta-1} \times 2^5)$. 
+	The number of all possible elongations of the current conformation by the next $\delta$-beads is $(6 \times 5^{\delta-1}) \times ((2^4)^{\delta-1} \times 2^5) \in 2^{O(\delta)}$. 
+	We can check for each of these elongations whether its arity is at most $\alpha$ or not and whether it is $R$-valid or not in time $O(\delta)$. 
 \end{proof}

### 2018-11-09 paper.tex
Finished simulation Thm, added some explanation before and after
Added Proposition 1 (proof is simple, so can be moved to appendix). Finished proof of Theorem about simulation. Changed statement from 2D Turing machines to algorithms, because otherwise we may need to add many unnecessary details about how the input is given on the 2D tape, how we traverse it, etc.

@@
 
+\begin{proposition}\label{prop:check_validity}
+	For any rule set $R$, arity $\alpha$ and conformation $C = (P,w,H)$ it is possible to check whether $C$ is $R$-valid and whether $C\in \mathcal{C}_{\leq \alpha}$ in time $\mathcal{O}(|H|\cdot|w|\cdot|R|)$.
+\end{proposition}
+\begin{proof}
+	To check whether $C$ is $R$-valid:
+	\begin{enumerate}
+		\item FOR each $(i,j)\in H$:
+		\item \hspace{1cm} IF $(w[i],w[j])\notin R$ THEN answer NO and HALT
+		\item answer YES and HALT
+	\end{enumerate}	
+	Checking the condition in 2. can be done in $\mathcal{O}(|w|\cdot|R|)$ time for any reasonable representation of $w$ and $R$, hence the whole process takes $\mathcal{O}(|H|\cdot |w|\cdot|R|)$ time.	
+	To check the arity constraint $C\in \mathcal{C}_{\leq \alpha}$: 
+	\begin{enumerate}
+		\item FOR each $i\in \{1,\dots,|w|\}$:
+		\item \hspace{1cm} IF $\mathrm{degree}(i)=|\{j | (i,j)\in H \}|>\alpha$ THEN answer NO and HALT
+		\item answer YES and HALT
+	\end{enumerate}	
+	Checking the condition in 2. can be done in $\mathcal{O}(|H|)$ time for any reasonable representation of $H$, hence the whole process takes $\mathcal{O}(|w|\cdot|H|)$ time.
+\end{proof}
 \begin{theorem}\label{thm:OS_to_2dTM}
-	There exists a Turing machine with 2-dimensional tape that simulates any oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time ??. 
+	There is an algorithm that simulates any oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$. 
 \end{theorem}
@@
 	The number of all possible elongations of the current conformation by the next $\delta$-beads is $(6 \times 5^{\delta-1}) \times ((2^4)^{\delta-1} \times 2^5) \in 2^{O(\delta)}$. 
-	We can check for each of these elongations whether its arity is at most $\alpha$ or not and whether it is $R$-valid or not in time $O(\delta)$. 
+	By Proposition~\ref{prop:check_validity}, we can check for each of these elongations whether its arity is at most $\alpha$ or not and whether it is $R$-valid or not in time $\mathcal{O}((2^4)^{\delta-1}\cdot2^5\cdot \delta\cdot|R|)=2^{\mathcal{O}(\delta)}\cdot|R|$.
+Therefore, the total running time is $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$.
 \end{proof}
+
+\begin{corollary}
+	For fixed $\delta$ and $\alpha$, the class of problems solvable by oritatami systems $(\Sigma, R, \delta, \alpha, \sigma, w)$ is included in $\mathrm{DTIME}(n^3)$.
+\end{corollary}
+\begin{proof}
+	The claim follows from Theorem~\ref{thm:OS_to_2dTM} and the fact that $|R|$ is implicitly bounded by $|w|^2$.
+\end{proof}
+
+%\begin{corollary}\label{polytranscript}
+%	Let $k$ be a non-negative number.
+Let $\Sigma$, $H$, $\delta$, $\alpha$ be fixed and the transcript length bounded polynomially by the seed length, i.e., $|w|\in O(|\sigma|^k)$.
+Then, the language of seeds $\sigma$ accepted by an OS $(\Sigma, R, \delta, \alpha, \sigma, w)$ is in $\mathrm{DTIME}(|\sigma|^{2k})$.
+%\end{corollary}
+
+%If the transcript length is polynomially bounded by the seed length, than the accepted language is in $\mathrm{P}$.
+
+Because of the time hierarchy theorems, we know that $\mathrm{P}\subsetneq \mathrm{EXP}$, so we can conclude that OS which cannot deterministically fold transcripts of length exponential in the length of the seed are not computationally universal.
 

### 2018-11-11 oldManuscript.tex
Added unary, arity 1, delta 2 case +Figures
I added the proof for delta 2, arity 1, unary. It needs some polishing still, but the main points are in there.
I also added a Fig folder with svg and png figures in case it is useful.
For the same reason, uploaded the old manuscript which has the write up for my version of the Chichen Itza construction, in case it helps Reoto

\documentclass[]{llncs}

\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{txfonts}
\usepackage{xcolor}
\usepackage{graphbox}
%\usepackage{subcaption}

\newcommand{\red}{\color{red}}
\newcommand{\black}{\color{black}}

\newcommand{\ori}{\mathcal{O}}
\newcommand{\bond}{\mathcal{H}}

\newcommand{\pos}{\mathrm{\bf pos}}

\begin{document}

\title{ON THE POWER OF ORITATAMI SYSTEMS WITH UNARY BEAD SEQUENCE\thanks{Both authors were supported by JSPS Challenging Exploratory Research Grant no. 18K19779.}}

\titlerunning{Simple oritatami systems}

\author{Szil\'ard Zsolt Fazekas\inst{1} \and
Shinnosuke Seki\inst{2}}
%
\authorrunning{S.Z. Fazekas, S. Seki}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Akita University, Graduate School of Engineering Science\\ \email{szilard.fazekas@ie.akita-u.ac.jp} \and The University of Electro-Communications, Graduate School of Informatics and Engineering\\ \email{s.seki@uec.ac.jp}
%\url{http://www.springer.com/gp/computer-science/lncs} \and
%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
%\email{\{abc,lncs\}@uni-heidelberg.de}
}
%
\maketitle

\begin{abstract}
We investigate simple Oritatami Systems in an attempt to establish lower bounds on the size and complexity of computationally universal systems. In particular, we look at Oritatami Systems, where the folding sequence consists of a number of beads of the same type and show that under reasonable assumptions, these systems are not universal.
\end{abstract}

Transcription is the first essential step of gene expression, when DNA templates are copied into single stranded RNA by a `copy machine' called RNA polymerase. The RNA strand is synthesized letter by letter ($A\rightarrow U$, $T\rightarrow A$, $G\rightarrow C$, $C\rightarrow G$) and folds up during a process called co-transcriptional folding.

In a recent breakthrough in molecular engineering by Geary, Rothemund and Andersen~\cite{RNAorigami} the co-transcriptional folding of RNA is controlled by careful design of the DNA template. As demonstrated in laboratory, this method, called RNA Origami, makes it possible to build rectangles out of RNA strands. Geary, Meunier, Schabanel and Seki~\cite{Oritatami} proposed a mathematical model for this process, called Oritatami Systems (OS).
It has been shown~\cite{Simulator} that the model is computationally universal by simulating cyclic tag systems introduced by Matthew Cook~\cite{Cook110}. The simulation involves a very large and complex OS. One future direction of research is to find smaller universal OS.

Closely related is the question of where not to look for universal systems, i.e., what are the limitations of simple OS. When considering simple OS, there are a number of restrictions one can pose on them:
\begin{itemize}
\item bounds on the delay, the number of bead types or the arity;
\item bounds on the size of the primary structure or of the attraction rule set;
\item structural conditions on the primary structure or the attraction rule set.
\end{itemize}

Rogers and Seki~\cite{SimpleSim} showed that certain OS with small delays are not universal.

Han, Kim, Rogers and Seki\cite{SelfRemove} proved that it is possible to avoid self-attraction rules without changing the behavior of OS.

In this paper we start a new line of study which concerns the alphabet size for the primary structure, i.e., the number of bead types.
%One can show that the model is computationally universal by simulating cyclic tag systems introduced by Matthew Cook~\cite{Cook110}.

\pagebreak

\section{Oritatami Systems}
An \textbf{Oritatami System} $\ori = (B, p, \bond, \delta, \alpha)$ is composed of
\begin{enumerate}
\item a finite set $B$ of \textit{bead types},
\item a (possibly infinite) \textit{transcript} $p\in B^*\cup B^\omega$, which is a sequence of beads,
\item an \textit{attraction rule set} $\bond$, which is a symmetric relation $\bond\subseteq B^2$,
\item  a positive integer $\delta$ called the \textit{delay},
\item a positive integer $\alpha$ called the \textit{arity}.
%\item a conformation $\sigma$ called the \textit{seed}.
\end{enumerate}

Computation in OS consists of folding finite sequences of beads, each from a finite set $B$ of bead types, according to the set of attraction rules $\bond \subseteq B\times B$, on the triangular lattice graph $\mathbb{T} = (\mathbb{Z}^2,\sim)$
where $(x, y) \sim (u, v)$ if and only if $$(u, v) \in \{(x-1, y), (x+1, y), (x, y+1), (x+1, y+1), (x-1, y-1), (x, y-1)\}.$$

\noindent Sometimes we will refer to the relation above as $(x,y)$ is \textit{next to} $(u,v)$. For the illustrations, the indexing of the grid lines goes from bottom to top and from left to right, and the first coordinate refers to the horizontal axis.

A (self-avoiding) path of length $n\geq 1$ between points $(x,y)$ and $(z,t)$ is a sequence of distinct points $(x_1,y_1),\dots,(x_{n+1},y_{n+1})$ such that $(x,y)=(x_1,y_1)$, $(z,t)=(x_{n+1},y_{n+1})$ and $(x_i,y_i)\sim (x_{i+1},y_{i+1})$ for all $i\in\{1,\dots,n\}$. We denote this relation by $(x,y)\sim_n (z,t)$. This way, $\sim_1$ is $\sim$. We set $\sim_0$ to mean that the points are equal.

For a point $(x,y)$, let $N_{x,y}^d$ denote the set of points which are in a \textit{neighborhood} of size $d$ of $(x,y)$, that is,
$$N_{x,y}^d = \{ (z,t) \mid \exists n\leq d: (x,y)\sim_n (z,t) \}$$
Points $(x,y)$ and $(z,t)$ are at \textit{distance} $d\geq 0$ from each other if $(z,t)\in N_{x,y}^d\setminus N_{x,y}^{d-1}$. As we will repeatedly refer to neighborhoods in our arguments, we note that the points in $N_{x,y}^d$ form a regular hexagon centered at $(x,y)$, whose sides consist of $d$ points and the number of all points in this neighborhood is $3d^2+3d+1$.

\bigskip

A \textit{conformation} $c$ of a sequence of beads $w\in B^*$ is a path of length $n-1$ labeled by $w$ in $\mathbb{T}$, i.e., a sequence $c_1,\dots , c_n\in \mathbb{T}$ of distinct points, and a labeling $\ell: \mathbb{T}\rightarrow B$, such that $\ell(c_i)=w_i$, where $w=w_1\dots w_n$.
%\begin{itemize}
%\item $\forall i,j \in \{1,\dots, n\}$: $(x_i,y_i)=(x_j,y_j) \Rightarrow i=j$
%\item $\forall i\in \{1,\dots,n-1\}$: $(x_i,y_i)\sim (x_{i+1},y_{i+1})$
%\item $\forall i\in \{1,\dots, n\}$: $\ell(x_i,y_i)=w_i$, where $w=w_1\dots w_n$.
%\end{itemize}

The grid point occupied by bead $i$ in conformation $C$ is $\pos_C(i)=c_i$. We may omit the subscript when it is clear which conformation we refer to, or when we argue about all possible conformations.
%are pairwise distinct and labelled by the letters of $w$. A partial conformation of a sequence $w$ is a conformation of a prefix of $w$. For any partial conformation $c$ of some sequence $w$, an elongation of $c$ by $k$ beads is a partial conformation of $w$ of length $|c|+k$. We denote by $C_w$ the set of all partial conformations of $w$. We denote by $c^{\triangleright k}$ the set of all elongations by $k$ beads of a partial conformation $c$ of a sequence $w$ and by $c^{\triangleleft k}$ the singleton containing the prefix of length $|c|-k$ of $c$.
%\bigskip

Given a finite \textit{attraction rule} set $\bond\subseteq B^2$ and a conformation $c$ of a sequence $w$, a bond is a pair $(i,j)$, such that $c_i\sim c_j$ and $\ell(c_i) \bond \ell(c_j)$. The energy of a conformation $c$ of $w$, written $E(c)$, is the negation of the number of bonds within $c$: formally, $E(c) = -|\{(i, j) : c_i \sim c_j \textrm{, } j > i + 1, \textrm{ and } w_i \bond w_j \}|$.

\bigskip

The arity parameter controls the maximum number of bonds in which a given bead of a conformation can participate. For instance if $\alpha=1$, then any bead can form at most one bond, even if the attraction rule set is such that multiple neighbors could be paired with the bead. As we are embedding the conformations into $\mathbb{T}$, a bead cannot form more than $6$ bonds and that only if it is the only bead in the transcript. Similarly, $5$ bonds are only possible for the first and the last bead of a conformation, hence it generally makes sense to consider an arity parameter $\alpha\leq 4$.

In this paper we will consider OS as computing devices which start with an input conformation called the \textit{seed}, usually denoted by $\sigma$. Note that in previous papers on OS, the seed was part of the definition of the system.

The transcript folds into a conformation one bead at a time, by \textit{fixing} each bead at a point in $\mathbb{T}$. The first bead of the transcript has to be fixed next to the last bead of the seed. The position of the beads (letters of $p$) is fixed one-by-one. Suppose that beads of the seed and the first $i$ beads of the transcript have been fixed into a conformation $C_i$. Then the OS chooses among all \red TBC \black

Sometimes several conformations have the maximum number of bonds and the OS keeps track of those, while discarding the less stable ones. If more than one conformation of length $N+\delta$ has the maximum attainable number of bonds and the position of or the bonds formed by the $N+1$-th bead is not the same in all of them, then the system is nondeterministic.
In this paper we deal only with deterministic systems, and aim to show that certain simple OS are not capable of universal computation.

% so that each bead $i$, together with its $\delta-1$ successors attains a conformation which has the most bonds possible for the given $i+\delta$ long prefix of $p$.

\begin{figure}
\centering
\includegraphics[width=1\linewidth]{orisys3}
\caption{Four examples of the possible conformations (left) and the conformation with the most hydrogen bonds (1) fixes a vertex with label $C$ (right).}
\label{fig:orisys3}
\end{figure}

As a short illustration of how the model works, consider the following example (Fig.~\ref{fig:orisys3}). The OriSys is $\ori= (p, R, \delta)$, where

\begin{itemize}
\item the set of beads is $B=\{A, U, C, G\}$,
\item the transcript is $p=GCAAGCUCU$,
\item the attraction rule set is $\bond = \{A-U, C-G, G-U  \}$,
\item the delay is $\delta = 3$, and
\item the arity is $\alpha=3$.
\end{itemize}

 Suppose that the first 5 beads were fixed in place along the thick black path. At the beginning of step $N$(=5) the path is extended by one vertex labeled by the $N+\delta=8$-th letter of the primary structure (C). The position of vertices $1,\cdots, N$ is fixed ($GCAAG$) and the position of the next $\delta$ vertices is not ($CUC$). Out of all possible conformations (4 shown out of many) the not yet fixed part of the path folds up into the conformation (1) with the highest number of hydrogen-bonds (4). Bonds form according to the rules of attraction $\bond$. After the most stable conformation is found the position of vertex $N+1$ ($C$) is fixed and the next step follows.

\section{Preliminaries}
By simulating a deterministic (finite) OS with Turing machines, or indeed, with some other classical model of computation, we mean that for a suitably encoded input seed, the simulator can output the suitably encoded final conformation of the OS.

To simplify the argument, we treat the computations performed by OS as decision problems in the following sense. We can look at a deterministic Oritatami system $\ori$, with some polynomial time algorithm $\mathcal{A}_\ori$, as a computing device which takes the seed and the transcript as input and accepts the input if $\mathcal{A}_\ori$ accepts the final conformation of the OS. Assuming the existence of a polytime $\mathcal{A}_\ori$ is realistic, since if the interpretation of the output does not have to be tractable, then one can hide the real computation there.
%two dimensional array $S$ of size $w\times h$, where $w$ is the width and $h$ is the height of the final conformation of the OS. We require $S[i,j]=(n,\mathrm{prev},\mathrm{next})$

We will make repeated use of the fact that for a given delay OS can be efficiently simulated by classical algorithms, as shown in~\cite{simulation}. We present a simplified version of the argument which suffices for our results here.
\begin{theorem}
For any given $\Sigma$, $\bond$, $\delta$, $\alpha$ there exists a Turing machine with 2-dimensional tape which can simulate any OS $(\Sigma, p, \bond, \delta, \alpha)$ with any seed $\sigma$, in time $O(|\sigma|+|p|)$.
\end{theorem}
\begin{proof}
Take any step in the computation, when some $i\geq 0$ beads of the transcript have been fixed, with the last bead occupying position $(x,y)$. The delay $\delta$ is constant, and there are $|N_{x,y}^\delta|=3\delta^2+3\delta+1$ points in the neigborhood of size $\delta$. The next $\delta$ beads can only be placed within $N_{x,y}^\delta$, so the number of all possible placements (including ones which are not valid conformations) is ${|N_{x,y}^\delta|\choose \delta}\cdot \delta!\in O(1)$. For each such placement, the number of all possible bond sets formed is bounded by $2^{|N_{x,y}^\delta|\choose 2}\in O(1)$. Selecting the valid placement with the maximum number of bonds or deciding that there is no such placement, therefore, can be done in time $O(1)$.
\end{proof}

In turn, a Turing machine (TM) with two dimensional tape can be easily simulated by TM with a one dimensional tape with at most a quadratic blow up in time complexity.

\begin{corollary}
For fixed $\Sigma$, $\bond$, $\delta$, $\alpha$, the class of problems solvable by OS $(\Sigma, p, \bond, \delta, \alpha, \sigma)$ is included in $\mathrm{DTIME}((|\sigma|+|p|)^2)$.
\end{corollary}

\begin{corollary}\label{polytranscript}
Let $k$ be a non-negative number. Let $\Sigma$, $\bond$, $\delta$, $\alpha$ be fixed and the transcript length bounded polynomially by the seed length, i.e., $|p|\in O(|\sigma|^k)$. Then, the language of seeds $\sigma$ accepted by an OS $(\Sigma, p, \bond, \delta, \alpha, \sigma)$ is in $\mathrm{DTIME}(|\sigma|^{2k})$.
\end{corollary}

If the transcript length is polynomially bounded by the seed length, than the accepted language is in $\mathrm{P}$. Because of the time hierarchy theorems, we know that $\mathrm{P}\subsetneq \mathrm{EXP}$, so we can conclude that such deterministic OS are not computationally universal.

Going forward, for OS with various restrictions we will establish length bounds on the transcript $p$ in terms of $|\sigma|$, above which the OS does not behave deterministically. We also give a construction which demonstrates a lower bound for the longest transcript which can be deterministically folded by an OS with arity $1$ and delay $2$ for given input seed length.

\section{Arbitrary alphabets}
Let us first recall a result about OS with arity $1$ and delay $1$.
\begin{theorem}\cite{ARITY1D1}
For an OS with arity $1$, delay $1$ and seed length $n$, the maximum length of transcript which can be folded deterministically is $9n$.
\end{theorem}

This theorem, together with Corollary~\ref{polytranscript} means that such OS are not computationally universal.
\begin{corollary}
The languages accepted by deterministic OS with arity $1$, delay $1$ are in $\mathrm{DTIME}(n^2)$.
\end{corollary}

Keeping to arity $1$, but allowing delay $2$ increases the power of OS. We demonstrate this with an infinite family of OS, which fold deterministically a transcript of length $\frac{(n-1)^2}{4}$ when receiving a given seed of length $n$.

Consider a delay $2$, arity $1$ system with bead types $B_0$ to $B_4$ and attraction rules $\{B_1-B_1,B_2-B_2, B_3-B_3,B_4-B_4\}$. Let the seed be a conformation of a $4k+1$ long bead sequence of the form $(B_1B_0B_2B_0)^kB_0$. Bead $i$ of the seed is fixed at point $(i,0)$, for all $1\leq i\leq 4k-1$. Bead $4k$ is at $(4k-1,-1)$ and bead $4k+1$ is at $(4k,0)$.

\noindent The transcript is
\begin{center}
\begin{tabular}{llllll}
$p=$ & $(B_2B_4B_1B_3)^{k-1}$ & $B_2B_4(B_1B_4B_2B_3)^{k-1}$ & $B_1B_4(B_1B_3B_2B_4)^{k-2}$ & $B_1B_3(B_2B_3B_1B_4)^{k-2}$ & $B_2B_3$\\
     & $(B_2B_4B_1B_3)^{k-3}$ & $B_2B_4(B_1B_4B_2B_3)^{k-3}$ & $B_1B_4(B_1B_3B_2B_4)^{k-4}$ & $B_1B_3(B_2B_3B_1B_4)^{k-4}$ & $B_2B_3$\\
     & \vdots\\
     & $(B_2B_4B_1B_3)^{2}$ & $B_2B_4(B_1B_4B_2B_3)^{2}$ & $B_1B_4(B_1B_3B_2B_4)^{1}$ & $B_1B_3(B_2B_3B_1B_4)^{1}$ & $B_2B_3$\\
     & $B_2B_4B_1B_4$
\end{tabular}

\end{center}
if $k$ is odd, and
\begin{center}
\begin{tabular}{llllll}
$p=$ & $(B_2B_4B_1B_3)^{k-1}$ & $B_2B_4(B_1B_4B_2B_3)^{k-1}$ & $B_1B_4(B_1B_3B_2B_4)^{k-2}$ & $B_1B_3(B_2B_3B_1B_4)^{k-2}$ & $B_2B_3$\\
     & $(B_2B_4B_1B_3)^{k-3}$ & $B_2B_4(B_1B_4B_2B_3)^{k-3}$ & $B_1B_4(B_1B_3B_2B_4)^{k-4}$ & $B_1B_3(B_2B_3B_1B_4)^{k-4}$ & $B_2B_3$\\
     & \vdots\\
     & $(B_2B_4B_1B_3)^{2}$ & $B_2B_4(B_1B_4B_2B_3)^{2}$ & $B_1B_4$\\
     & $B_1B_3B_2B_3$
\end{tabular}

\end{center}
if $k$ is even. The length of the transcript is $4k^2$. One row of the formula above corresponds to four rows of the conformation (except for the last rows).

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{./chichenBig}
\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. Beads: '$B_0$' black, '$B_1$' red, '$B_2$' red with black contour, '$B_3$' green, '$B_4$' green with black contour.}
\label{fig:chichenBig}
\end{figure}

The first bead of the transcript is type $B_2$ and it has to be fixed next to $(4k,0)$. The second bead is type $B_4$, which cannot form a bond with anything in the conformation so far. The only possibility of forming a bond is if $B_2$ is placed at $(4k,1)$ and it bonds with the $B_2$ at $(4k-1,0)$. The next bead to be fixed is $B_4$, and since it cannot form a bond, the conformation with the highest number of bonds is when the next bead, $B_1$ is at $(4k-2,1)$, which fixes the previous bead, $B_4$ at $(4k-1,1)$.

\begin{figure}
\begin{minipage}{.35\textwidth}
	\centering
	\includegraphics[align=c,height=1in]{./CI_1}\\
	\bigskip

	(a) First transcript bead
\end{minipage}%
\begin{minipage}{.2\textwidth}
	\centering
	\includegraphics[align=c,height=0.7in]{./CI_2}\\
	\bigskip

	(b) Second bead
\end{minipage}
\begin{minipage}{.4\textwidth}
	\centering
	\includegraphics[align=c,height=0.5in]{./CI_3}
	\bigskip
	\vspace{0.1in}
	\includegraphics[align=c,height=0.5in]{./CI_4}
	\bigskip

	(c) Bead $i+1$, when bead $i$ is $B_{3,4}$ and $B_{1,2}$, respectively
\end{minipage}
\caption{Fixing transcript beads in odd rows}

\end{figure}

Let the last bead fixed be the $i$th one.
If it is $B_1$ or $B_2$ at some position $(4k+1-i,1)$, then the next two are $B_3B_2$ or $B_4B1$, respectively. The first beads in both cases cannot bind anywhere, whereas the second ones can bind with identical beads at $(4k+1-(i+3),0)$, fixing bead $i+1$ at $(4k+1-(i+1),1)$.
If bead $i$ was $B_3$ or $B_4$ at position $(4k+1-i,1)$ then the next two are $B_2B_4$ or $B_1B_3$,respectively. The first bead of those sequences can bind only to its identical counterpart at $(4k+1-(i+2),0)$, whereas the second cannot bind anywhere, fixing bead $i+1$ at $(4k+1-(i+1))$. The above hold as long as there is a bead already at $(4k+1-(i+3),0)$ or at $(4k+1-(i+3),0)$, respectively, so for all $i\in \{1,\dots, 4k-2\}$.

According to the above, bead $4k-1$ was fixed at $(4k+1-(4k-1),1)=(2,1)$. The next bead, $4k$ is of the same type as bead $4k-2$, so they can form a bond, and this is the only bond that can be formed by any conformation of beads $4k$ and $4k+1$ (see Fig.~\ref{fig:citurn}). A similar situation occurs when trying to fix bead $8k-2$: it can only bond to bead $8k-4$, so it will turn the path around.
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{CI_turn}
	\caption{}
	\label{fig:citurn}
\end{figure}

\section{Unary}
In what follows, the alphabet of the transcript is unary, that is, there is only one bead type, say $\{A\}$. One could consider an attraction rule set where $A$ forms bonds only with beads of the seed and not with itself, but here there is only one attraction rule, $A$ binds to itself $\{A-A\}$.
Therefore, to simplify notation for unary OS we dispense with the bead alphabet and the attraction rules and we define them as $(p, \delta, \alpha)$.

We will analyze cases when the OS reaches a conformation where there is enough ``open space'', i.e., unoccupied grid points around the last fixed bead.

\subsection{Arity 1}

\paragraph{Delay 2}
Let the coordinates where the first transcript bead was fixed be $(x,y)$ and let $n=|\mathrm{seed}|+1$. We will argue about the situation when the first bead is stabilized outside $N_{x,y}^n$ (a hexagon of radius $n$). Let this be the $i$th bead of the transcript. Without loss of generality, we can translate the origin $(0,0)$ to the coordinates of bead $i-1$ (still in $N_{x,y}^n$), and we can assume that the bead outside the hexagon is fixed at $(1,1)$ (see Fig.~\ref{fig:hexagonOut}). The only position with which $(1,1)$ can form a bond is $(1,0)$. This means that there is a bead at $(1,0)$, which bonds to bead $i$, otherwise there are other conformations in which beads $i$ and $i+1$ add one bond to the conformation, making the behavior nondeterministic.

The next bead, $i+1$, can be fixed at $(2,1)$ or at $(0,1)$ as all other possibilities result in nondeterministic behavior immediately, so we have two cases.

\begin{enumerate}
\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$. Now consider bead $i+2$. For $i+1$ to be fixed at $(2,1)$, $i+2$ needs to form a bond somewhere, otherwise $i+2$ could go to $(2,1)$ forming the bond with the bead at $(2,0)$ and there would be two conformations with the maximal $1$ bond. The only possibility is that there is a bead at $(3,0)$ and $i+2$ can bond with it when placed at $(3,1)$. We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by active beads, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$. Such an $m$ exists, and it is not greater than $n$. Then, bead $i+\ell$ is fixed at $(\ell+1,1)$ and bonds with $(\ell+1,0)$. 
\item bead $i+1$ is fixed at $(0,1)$. This is only possible if
\begin{enumerate}
\item there is an inactive bead at $(-1,0)$ and an active one at $(-2,0)$. This case is symmetrical to (1).
\item there is no bead at $(-1,0)$, bead $i+1$ can bond with bead $i-1$ at $(0,0)$ and the bead $i+2$ can be placed at $(-1,0)$ where it can bond with $(-2,0)$, $(-2,-1)$ or $(-1,-1)$. This leads to nondeterminism, because bead $i$ at $(-1,0)$ and bead $i+1$ at $(0,1)$ has two bonds, just as the original conformation.
\item there is a bead at $(-1,0)$ and bead $i+1$ can bond with that or with bead $i-1$ at $(0,0)$. However, this means that placing bead $i$ at $(0,1)$ at bead $i+1$ at $(1,1)$ creates the same number of hydrogen bonds, thus resulting in bead $i$ not being placed deterministically.

\end{enumerate}
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=0.3\linewidth]{./hexagonOut}
\hspace{10mm} %
\includegraphics[width=0.6\linewidth]{./hexOut}

\caption{LEFT: $N_{x,y}^n$ and the position $(1,1)$ of the first bead fixed outside of it. RIGHT: the three possible conformations with 2 bonds which would fix bead $i$ at $(1,1)$.}
\label{fig:hexagonOut}
\end{figure}

\red
At arity 1, delay 2, glider is impossible for any alphabet size
%\begin{figure}
%\centering
%\includegraphics[width=0.7\linewidth]{./IMG_20180714_113733073}
%\caption{}
%\label{fig:IMG_20180714_113733073}
%\end{figure}
%
\black
%Arity 1 delay 2:
%\begin{itemize}
%\item $m$ beads in seed
%\item $n$ transcript beads
%\item we can add 2 bonds/2 beads at most $m$ times
%\item when we first get out of the hexagon (center is the first transcript bead) of radius $m+i$, $i\geq 0$ we can only bond with transcript beads
%\item if we only add one bond/2 beads now, see figure for nondeterminism
%\item for higher delays $d$, try a similar argument, going out of a hexagon, the next $d$ beads form at most $\lfloor d/2\rfloor$ bonds, two different zigzags add enough bonds
%\end{itemize}

\section{Arity 2}
We need a lemma which gives an upper bound on the number of bonds for a (not necessarily unary) conformation of arity $2$.
\begin{lemma}
For any OS with arity $2$ and primary structure of length $n$, the maximum number of bonds is at most $n-1$.
\end{lemma}
\begin{proof}
As $\alpha=2$, if all beads realized the maximum $2$ bonds, that gives $n$ bonds, because of the handshaking lemma.

Suppose this is the case, i.e., there exists some conformation $C$ which has $n$ bonds. Consider $B$, the minimal convex bounding polygon of $C$ with all vertices in $\mathbb{T}$. Take, say, the topmost and leftmost vertex $(i,j)$ of $C$ which is on an edge of $B$. Then, $(i,j)$ being the topmost, $(i+1,x)\notin C$ for any $x$, and $(i,j)$ being the leftmost among the topmost, $(i,x)\notin C$ for any $x<j$. This excludes three neighbors of $(i,j)$ from $C$ and leaves us with the following possibilities:
\begin{enumerate}
\item $\{(i,j), (i-1,j), (i,j+1)\}\subset C$
\item $\{(i,j), (i-1,j-1), (i-1,j)\}\subset C$
\item $\{(i,j), (i-1,j-1), (i,j+1)\}\subset C$
\end{enumerate}
The first two form a sharp angle, while the third forms a wide angle. In all cases, three of the neighbors of $(i,j)$ are excluded from $C$, while two have the beads immediately preceding and succeeding the one at $(i,j)$, so there is only one neighbor left to form a bond with. This means that at least one of the beads has at most one bond, proving our claim.
\end{proof}

For arity $2$, consider an OS which can reach a conformation as shown in Fig.~\ref{fig:arity2}. Suppose the last two beads were fixed at grid points $(i-1,j-1)$ and $(i,j)$, in this order. If the following conditions hold, then the behavior of the OS is nondeterministic
\begin{itemize}
\item $\delta\geq 3$;
\item grid points $(i,j+x)$ and $(i+1,j+y)$, for all $x\in \{1,\dots,\lfloor \delta/2\rfloor\}$, $y\in \{0,\dots,\lceil\delta/2\rceil-1\}$ are not occupied;
\item the beads at $(i,j)$ and $i+1,j+1$ can both form one more bond.
\end{itemize}
Both conformations shown in the figure have the maximum $3$ bonds but the first not fixed bead has different position in the two. If the conditions above apply, the next $\delta$ beads of the primary structure can fold up into a zig-zag, adding the maximum possible $\delta$ bonds.

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{./arity2}
\caption{Nondeterministic behavior at arity 2. The two conformations have the same number of hydrogen bonds (2 dashed lines each) and the next bead to be fixed (filled circle) occupies different grid points in the two.}
\label{fig:arity2}
\end{figure}

\paragraph{Arity 3}

\paragraph{Arity 4}

\bibliographystyle{splncs04}
\bibliography{Oritatami}

\end{document}

### 2018-11-11 paper.tex
Dvipdfmx option has been causing an error
The option [dvipdfmx] causes an error so that we couldn't open paper.pdf
by Acrobat Reader. I removed them as you can see the log.
Added unary, arity 1, delta 2 case +Figures
I added the proof for delta 2, arity 1, unary. It needs some polishing still, but the main points are in there.
I also added a Fig folder with svg and png figures in case it is useful.
For the same reason, uploaded the old manuscript which has the write up for my version of the Chichen Itza construction, in case it helps Reoto

@@
 
-\usepackage[dvipdfmx]{color}
+\usepackage{color}
 
-\usepackage[dvipdfmx]{graphicx}
+\usepackage{graphicx}
 \usepackage{tikz}
@@
 
+\subsection{$\alpha = 1$, unary}
+
+Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|+1$.
+We will argue about the situation when the first bead is stabilized outside $\hexagon_p^n$ (a hexagon of radius $n$).
+Let this be the $i$th bead of the transcript.
+Without loss of generality, we can translate the origin $(0,0)$ to the coordinates of bead $i-1$ (which is still in $\hexagon_p^n$), and we can assume that the bead outside the hexagon is fixed at $(1,1)$ (see Fig.~\ref{fig:hexagonOut}).
+\begin{figure}
+	\centering
+	\includegraphics[width=0.3\linewidth]{./Fig/hexagonOut}
+	\caption{$N_p^n$ and the position $(1,1)$ of the first bead fixed outside of it.}
+	\label{fig:hexagonOut}
+\end{figure}
+
+In the elongation that places bead $i$ at $(1,1)$ there are two possibilities:
+\begin{itemize}
+	\item $i$ forms a bond with a bead at $(1,0)$.
+	\item  $i$ does not bond to anything and $i+1$ is at $(2,1)$ bonding with a bead at $(2,0)$.
+If there is no bead at $(1,0)$, then placing $i$ at $(1,0)$ instead of $(1,1)$ results in the same number of bonds, leading to nondeterminism.
+Therefore, there has to be a bead at $(1,0)$ and it is inert, otherwise it would bond to $i$.
+This is analogous to case 1.
+below.%as in Fig.~\ref{fig:hexagonOut1}.
+	\begin{figure}
+		\centering
+		\includegraphics[width=0.2\linewidth]{./Fig/hexagonOut1}
+		%\caption{}
+		\label{fig:hexagonOut1}
+	\end{figure}
+
+\end{itemize}
+
+%The only position with which $(1,1)$ can form a bond is $(1,0)$.
+This means that there is a bead at $(1,0)$, which bonds to bead $i$, otherwise there are other conformations in which beads $i$ and $i+1$ add one bond to the conformation, making the behavior nondeterministic.
+
+The next bead, $i+1$, can be fixed at $(2,1)$ or at $(0,1)$ as all other possibilities result in nondeterministic behavior immediately, so we have two cases.
+
+\begin{enumerate}
+	\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$.
+Now consider bead $i+2$.
+For $i+1$ to be fixed at $(2,1)$, $i+2$ needs to form a bond somewhere, otherwise $i+2$ could go to $(2,1)$ forming the bond with the bead at $(2,0)$ and there would be two conformations with the maximal $1$ bond.
+The only possibility is that there is a bead at $(3,0)$ and $i+2$ can bond with it when placed at $(3,1)$.
+We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by active beads, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$.
+Such an $m$ exists, and it is not greater than $n$.
+Then, bead $i+\ell$ is fixed at $(\ell+1,1)$ and bonds with $(\ell+1,0)$.
+However, bead $i+2+m$ cannot be fixed anywhere, because $i+2+m$ and $i+3+m$ can only add one bond to the conformation, and that is possible either with $i+2+m \rightarrow (2+m,1)$, $i+3+m \rightarrow (3+m,1)$ or with $i+2+m \rightarrow (2+m,2)$, $i+3+m \rightarrow (2+m,1)$.
+	\begin{figure}
+		\centering
+		\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut2}
+		\caption{}
+		\label{fig:hexagonout2}
+	\end{figure}
+
+	\item bead $i+1$ is fixed at $(0,1)$. This is only possible if
+	\begin{enumerate}
+		\item there is an inactive bead at $(-1,0)$ and an active one at $(-2,0)$. This case is symmetrical to (1).
+		\item there is no bead at $(-1,0)$, bead $i+1$ can bond with bead $i-1$ at $(0,0)$ and the bead $i+2$ can be placed at $(-1,0)$ where it can bond with $(-2,0)$, $(-2,-1)$ or $(-1,-1)$.
+This leads to nondeterminism, because bead $i$ at $(-1,0)$ and bead $i+1$ at $(0,1)$ has two bonds, just as the original conformation.
+		\item there is a bead at $(-1,0)$ and bead $i+1$ can bond with that or with bead $i-1$ at $(0,0)$.
+However, this means that placing bead $i$ at $(0,1)$ at bead $i+1$ at $(1,1)$ creates the same number of hydrogen bonds, thus resulting in bead $i$ not being placed deterministically.
+
+	\end{enumerate}
+\end{enumerate}
+
+\begin{figure}
+	\centering
+	%\includegraphics[width=0.3\linewidth]{./hexagonOut1}
+	%\hspace{10mm} %
+	\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut3}
+
+	\caption{}
+	\label{fig:hexagonOut2}
+\end{figure}
+
 \end{document}

### 2018-11-13 paper.tex
Introduction added
Thanks, Szilard. I borrowed the introduction and title with some
technical modifications.

@@
 
-\title{On finiteness of structures produced deterministically by oritatami co-transcriptional folding
-\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~S.}
+\title{On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F.
+and S.~S.}
 }
@@
 \begin{abstract}
-
+We investigate simple oritatami systems in an attempt to establish lower bounds on the size and complexity of computationally universal systems. 
+In particular, we look at oritatami systems, where the folding sequence consists of a number of beads of the same type and show that under reasonable assumptions, these systems are not universal.
 \end{abstract}
@@
 \section{Introduction}
+
+Transcription is the first essential step of gene expression, when a DNA template sequence is copied into a complementary single stranded RNA sequence by a `copy machine' called RNA polymerase. 
+The RNA strand is synthesized letter by letter according to the complimentarity relation ${\tt A} \rightarrow {\tt U}$, ${\tt G} \rightarrow {\tt C}$, ${\tt C} \rightarrow {\tt G}$, and ${\tt T} \rightarrow {\tt A}$ and folds up during a process called co-transcriptional folding.
+
+In a recent breakthrough in molecular engineering by Geary, Rothemund and Andersen~\cite{RNAorigami} the co-transcriptional folding of RNA is controlled by careful design of the DNA template.
+As demonstrated in laboratory, this method, called RNA Origami, makes it possible to build rectangles out of RNA strands.
+Geary et al.~\cite{Oritatami} proposed a mathematical model for this process, called oritatami system.
+It has been shown~\cite{Simulator} that the model is computationally universal by simulating cyclic tag systems introduced by Cook~\cite{Cook110}. 
+The simulation involves a very large and complex oritatami system. 
+One future direction of research is to find smaller universal oritatami system.
+
+Closely related is the question of where not to look for universal systems, i.e., what are the limitations of simple oritatami system. 
+In search for simple oritatami systems, there are a number of restrictions one can pose on them:
+\begin{itemize}
+\item bounds on the delay, the number of bead types or the arity;
+\item bounds on the size of the primary structure or of the attraction rule set;
+\item structural conditions on the primary structure or the attraction rule set.
+\end{itemize}
+
+%Rogers and Seki~\cite{SimpleSim} showed that certain OS with small delays are not universal.
+
+%Han, Kim, Rogers and Seki\cite{SelfRemove} proved that it is possible to avoid self-attraction rules without changing the behavior of OS.
+
+In this paper we start a new line of study which concerns the alphabet size for the primary structure, i.e., the number of bead types.
 

### 2018-11-13 ttt.tex
11/13 en

@@
 
-\usepackage[dvipdfmx]{color}
-
-\usepackage[dvipdfmx]{graphicx}
 \usepackage{tikz}
@@
     \begin{tikzpicture}
-      \draw[thick, rounded corners = 10pt]
-      (-1,-1)--(7,-1)--(7,2)--(-1,2)-- cycle;
-
       \fill (0,0) circle[radius = 0.1];
@@
 
-In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 1 deterministically moreover the infinite terminal which its oritatami system can yield is only zig-zag conformations shown in Fig\ref{TTT_zigzag}.
+In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 2 deterministically and moreover that the only infinite conformations which its oritatami system can yield is only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
 
-Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2.
-Assume its seed $\sigma$ consists of $n$ beads.
-Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
-For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$ that is foldable by $\Xi$.
-Hence $C_0 = \sigma$.
+Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
+%Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
+For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$ that is foldable by $\Xi$. Hence $C_0 = \sigma$.
 
 Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$.
-The bead cannot collaborate with any succeeding bead $w_{i+1},w_{i+2},\cdots$ at delay 1.
+The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1.
 There are just two ways to get stabilized at delay 1.
@@
 The other way is through a $tunnel\ section$.
-A tunnel section consists of four beads that occupt four neighbors of a point(Fig.\ref{TTT_tunnel_intro}).
-Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are not occupied.
+A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
+Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
 We call such beads as $p$ $inside\ of\ a\ tunnel$ and such beads as $p^\prime$ $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel.
-If the beads $a_{i-2}$ and $a_{i-1}$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $a_i$ cannot help but be stabilized at the other free neighbor.
-In this way, $a_i$ can get stabilized without being bound.
+If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor.
+In this way, $w[i]$ can get stabilized without being bound.
 
@@
       \fill (0:0) circle [radius=0.05];
-      \fill (0:1.5) circle [radius=0.05];
-      \fill (180:1.5) circle [radius=0.05];
-      \node[above] at (0:1.5) { $p^\prime$ };
+      \fill (0:1.2) circle [radius=0.05];
+      \fill (180:1.2) circle [radius=0.05];
+      \node[above] at (0:1.2) { $p^\prime$ };
       \node[above] at (0:0) { $p$ };
-      \node[above] at (180:1.5) { $p^\prime$ };
+      \node[above] at (180:1.2) { $p^\prime$ };
 
-      \fill (60 : 1.5) circle [radius=0.1];
-      \fill (-60 : 1.5) circle [radius=0.1];
-      \fill (120 : 1.5) circle [radius=0.1];
-      \fill (-120 : 1.5) circle [radius=0.1];
-      \node[above] at (60 :1.5) { $a_{j_1}$ };
-      \node[above] at (-60 :1.5) { $a_{j_2}$ };
-      \node[above] at (120 :1.5) { $a_{j_3}$ };
-      \node[above] at (-120 :1.5) { $a_{j_4}$ };
+      \fill (60 : 1.2) circle [radius=0.1];
+      \fill (-60 : 1.2) circle [radius=0.1];
+      \fill (120 : 1.2) circle [radius=0.1];
+      \fill (-120 : 1.2) circle [radius=0.1];
+      \node[above] at (60 :1.2) { $a_{j_1}$ };
+      \node[above] at (-60 :1.2) { $a_{j_2}$ };
+      \node[above] at (120 :1.2) { $a_{j_3}$ };
+      \node[above] at (-120 :1.2) { $a_{j_4}$ };
 
@@
         \fill (0:0) circle [radius=0.1];
-        \fill (0:1.5) circle [radius=0.05];
-        \fill (180:1.5) circle [radius=0.1];
-        \node[above] at (180:1.5) { $a_{i-2}$ };
+        \fill (0:1.2) circle [radius=0.05];
+        \fill (180:1.2) circle [radius=0.1];
+        \node[above] at (180:1.2) { $a_{i-2}$ };
         \node[above] at (0:0) { $a_{i-1}$ };
-        \draw[->] (180:1.4) -- (180:0.1);
+        \draw[->] (180:1.1) -- (180:0.1);
 
-        \fill (60 : 1.5) circle [radius=0.1];
-        \fill (-60 : 1.5) circle [radius=0.1];
-        \fill (120 : 1.5) circle [radius=0.1];
-        \fill (-120 : 1.5) circle [radius=0.1];
-        \node[above] at (60 :1.5) { $a_{j_1}$ };
-        \node[above] at (-60 :1.5) { $a_{j_2}$ };
-        \node[above] at (120 :1.5) { $a_{j_3}$ };
-        \node[above] at (-120 :1.5) { $a_{j_4}$ };
+        \fill (60 : 1.2) circle [radius=0.1];
+        \fill (-60 : 1.2) circle [radius=0.1];
+        \fill (120 : 1.2) circle [radius=0.1];
+        \fill (-120 : 1.2) circle [radius=0.1];
+        \node[above] at (60 :1.2) { $a_{j_1}$ };
+        \node[above] at (-60 :1.2) { $a_{j_2}$ };
+        \node[above] at (120 :1.2) { $a_{j_3}$ };
+        \node[above] at (-120 :1.2) { $a_{j_4}$ };
       \end{scope}
@@
         \fill (0:0) circle [radius=0.1];
-        \fill (0:1.5) circle [radius=0.1];
-        \fill (180:1.5) circle [radius=0.1];
-        \node[above] at (180:1.5) { $a_{i-2}$ };
+        \fill (0:1.2) circle [radius=0.1];
+        \fill (180:1.2) circle [radius=0.1];
+        \node[above] at (180:1.2) { $a_{i-2}$ };
         \node[above] at (0:0) { $a_{i-1}$ };
-        \node[above] at (0:1.5) { $a_i$ };
-        \draw[->] (180:1.4) -- (180:0.1);
-        \draw[->] (0:0.1) -- (0:1.4);
+        \node[above] at (0:1.2) { $a_i$ };
+        \draw[->] (180:1.1) -- (180:0.1);
+        \draw[->] (0:0.1) -- (0:1.1);
 
-        \fill (60 : 1.5) circle [radius=0.1];
-        \fill (-60 : 1.5) circle [radius=0.1];
-        \fill (120 : 1.5) circle [radius=0.1];
-        \fill (-120 : 1.5) circle [radius=0.1];
-        \node[above] at (60 :1.5) { $a_{j_1}$ };
-        \node[above] at (-60 :1.5) { $a_{j_2}$ };
-        \node[above] at (120 :1.5) { $a_{j_3}$ };
-        \node[above] at (-120 :1.5) { $a_{j_4}$ };
+        \fill (60 : 1.2) circle [radius=0.1];
+        \fill (-60 : 1.2) circle [radius=0.1];
+        \fill (120 : 1.2) circle [radius=0.1];
+        \fill (-120 : 1.2) circle [radius=0.1];
+        \node[above] at (60 :1.2) { $a_{j_1}$ };
+        \node[above] at (-60 :1.2) { $a_{j_2}$ };
+        \node[above] at (120 :1.2) { $a_{j_3}$ };
+        \node[above] at (-120 :1.2) { $a_{j_4}$ };
       \end{scope}
@@
         \begin{tikzpicture}
-          \draw[thick, rounded corners = 10pt]
-          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;
-
           \begin{scope}[xshift=2cm, yshift=2cm]
             \fill(0,0) circle [radius=0.05];
-            \node[above] at (180:1.5) {$p^\prime$};
-            \node[above] at (0:1.5) {$p^\prime$};
+            \node[above] at (180:1.2) {$p^\prime$};
+            \node[above] at (0:1.2) {$p^\prime$};
 
             \foreach \theta in {0,180}{
-              \fill[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.05];
+              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
             }
@@
             \foreach \theta in {60,-60,120,-120}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
@@
 
-          \node at (2,-0.5) {Tunnel A};
+          \node at (2,0) {Tunnel A};
         \end{tikzpicture}
@@
         \begin{tikzpicture}
-          \draw[thick, rounded corners = 10pt]
-          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;
 
@@
             \fill(0,0) circle [radius=0.05];
-            \node[above] at (180:1.5) {$p^\prime$};
-            \node[above] at (-60:1.5) {$p^\prime$};
+            \node[above] at (180:1.2) {$p^\prime$};
+            \node[above] at (-60:1.2) {$p^\prime$};
 
             \foreach \theta in {-60,180}{
-              \fill[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.05];
+              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
             }
@@
             \foreach \theta in {0,60,120,-120}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
@@
 
-          \node at (2,-0.5) {Tunnel B};
+          \node at (2,0) {Tunnel B};
         \end{tikzpicture}
@@
             \fill(0,0) circle [radius=0.05];
-            \node[above] at (180:1.5) {$p^\prime$};
-            \node[above] at (-1200:1.5) {$p^\prime$};
+            \node[above] at (180:1.2) {$p^\prime$};
+            \node[above] at (-1200:1.2) {$p^\prime$};
 
             \foreach \theta in {-120,180}{
-              \fill[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.05];
+              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
             }
@@
             \foreach \theta in {0,60,-60,120}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
@@
 
-          \node at (2,-0.5) {Tunnel C};
+          \node at (2,0) {Tunnel C};
         \end{tikzpicture}
@@
 
-\begin{figure}[h]
+\begin{figure}
   \begin{center}
-    \begin{tabular}{cc}
+    \begin{tabular}{lr}
 
-      \begin{minipage}{0.45\hsize}
+      \begin{minipage}{0.2\hsize}
         \begin{tikzpicture}
-          \draw[thick, rounded corners = 10pt]
-          (0,0)--(2.5,0)--(2.5,4)--(0,4)-- cycle;
 
-          \begin{scope}[xshift=2cm, yshift=2cm]
+          \begin{scope}[xshift=1cm, yshift=2cm]
             \fill(0,0) circle [radius=0.1];
-            \node[above] at (180:1.5) {$p^\prime$};
+            \node[above] at (180:1.2) {$p^\prime$};
 
-            \fill[transform canvas={shift=(180:1.5)}](0,0) circle [radius=0.1];
+            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
 
             \foreach \theta in {120,-120}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
 
-            \draw[->] (-1.4,0) -- (-0.1,0);
+            \draw[->] (-1.1,0) -- (-0.1,0);
           \end{scope}
 
-          \node at (1.25,-0.5) {Tunnel A,B};
+          \node at (0.25,0) {Tunnel A,B};
         \end{tikzpicture}
@@
 
-      \begin{minipage}{0.45\hsize}
+      \begin{minipage}{0.2\hsize}
         \begin{tikzpicture}
-          \draw[thick, rounded corners = 10pt]
-          (0,0)--(2.5,0)--(2.5,4)--(0,4)-- cycle;
 
-          \begin{scope}[xshift=2cm, yshift=2cm]
+          \begin{scope}[xshift=1cm, yshift=2cm]
             \fill(0,0) circle [radius=0.1];
-            \node[above] at (180:1.5) {$p^\prime$};
+            \node[above] at (180:1.2) {$p^\prime$};
 
-            \draw[transform canvas={shift=(-120:1.5)}](0,0) circle [radius=0.1];
-            \fill[transform canvas={shift=(180:1.5)}](0,0) circle [radius=0.1];
+            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
+            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
 
             \foreach \theta in {120}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
 
-            \draw[->] (-1.4,0) -- (-0.1,0);
+            \draw[->] (-1.1,0) -- (-0.1,0);
           \end{scope}
 
-          \node at (1.25,-0.5) {Tunnel C};
+          \node at (0.25,0) {Tunnel C};
         \end{tikzpicture}
@@
     \end{tikzpicture}
-    \caption{Tunnel A,Bにおけるbondの増加量}
+    \caption{Increment on Tunnel A,B}
     \label{TTT_position2}
@@
 
-\begin{figure}[h]
+\begin{figure}
   \begin{center}
     \begin{tikzpicture}
-      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Otherwise};
-      \node at (4.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
-      \node at (8,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
+      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
+      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
+      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
       \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
@@
       \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
-      \node at (4.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
-      \node at (8,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
+      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
+      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
       \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
@@
 
-      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {トンネルから離れている};
-      \node at (4.5,1) [rectangle, draw,rounded corners] (enter3)   {トンネルの入り口};
-      \node at (8,1)   [rectangle, draw, rounded corners] (inside3) {トンネルC};
-      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {トンネルの外};     
+      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
+      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
+      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
+      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
       \draw[->] (outside3)--(enter3);
@@
 
-      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {トンネルの中};
-      \node at (4.5,0) [rectangle, draw,rounded corners] (enter4)   {トンネルの入り口};
-      \node at (8,0)   [rectangle, draw, rounded corners] (inside4) {トンネルC};
-      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {トンネルの外};     
+      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
+      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
+      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
+      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
       \draw[->] (outside4)--(enter4);
@@
     \end{tikzpicture}
-    \caption{Tunnel Cの場合分け}
+    \caption{Case of Tunnel C}
     \label{TTT_tunnelC_graph}
@@
             \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1.5)}](0,0) circle [radius=0.1];
+              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
             }
@@
             \foreach \theta in {60,-60,180}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
@@
             \foreach \theta in {120,-120}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
             }
 
-            \draw[->] (180:1.4)--(180:0.1);
-            \draw[->] (0:0.1)--(0:1.4);
+            \draw[->] (180:1.1)--(180:0.1);
+            \draw[->] (0:0.1)--(0:1.1);
 
-            \node[transform canvas={shift=(60:1.5)},right] {A};
-            \node[transform canvas={shift=(-60:1.5)},right] {B};
+            \node[transform canvas={shift=(60:1.2)},right] {A};
+            \node[transform canvas={shift=(-60:1.2)},right] {B};
 
-            \node[transform canvas={shift=(120:1.5)},left] {c};
-            \node[transform canvas={shift=(-120:1.5)},left] {d};
+            \node[transform canvas={shift=(120:1.2)},left] {c};
+            \node[transform canvas={shift=(-120:1.2)},left] {d};
           \end{scope}
@@
             \foreach \theta in {60,-60,120}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
@@
             \foreach \theta in {180,-120}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
             }
 
-            \draw[->] (120:1.4)--(120:0.1);
-            \draw[->] (0:0.1)--(0:1.4);
+            \draw[->] (120:1.1)--(120:0.1);
+            \draw[->] (0:0.1)--(0:1.1);
 
-            \node[transform canvas={shift=(60:1.5)},right] {A};
-            \node[transform canvas={shift=(-60:1.5)},right] {B};
-            \node[transform canvas={shift=(120:1.5)},left] {P};
+            \node[transform canvas={shift=(60:1.2)},right] {A};
+            \node[transform canvas={shift=(-60:1.2)},right] {B};
+            \node[transform canvas={shift=(120:1.2)},left] {P};
 
-            \node[transform canvas={shift=(180:1.5)},left] {c};
-            \node[transform canvas={shift=(-120:1.5)},left] {d};
+            \node[transform canvas={shift=(180:1.2)},left] {c};
+            \node[transform canvas={shift=(-120:1.2)},left] {d};
           \end{scope}
@@
             \foreach \theta in {60,-60}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
@@
             \foreach \theta in {180,-120,120}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
             }
 
-            \draw[->] (60:1.4)--(60:0.1);
-            \draw[->] (0:0.1)--(0:1.4);
+            \draw[->] (60:1.1)--(60:0.1);
+            \draw[->] (0:0.1)--(0:1.1);
 
-            \node[transform canvas={shift=(-60:1.5)},right] {A};
-            \node[transform canvas={shift=(60:1.5)},right] {P};
+            \node[transform canvas={shift=(-60:1.2)},right] {A};
+            \node[transform canvas={shift=(60:1.2)},right] {P};
 
-            \node[transform canvas={shift=(120:1.5)},left] {c};
-            \node[transform canvas={shift=(180:1.5)},left] {d};
-            \node[transform canvas={shift=(-120:1.5)},left] {e};
-            \node[transform canvas={shift=(0:1.5)},below] {n};
+            \node[transform canvas={shift=(120:1.2)},left] {c};
+            \node[transform canvas={shift=(180:1.2)},left] {d};
+            \node[transform canvas={shift=(-120:1.2)},left] {e};
+            \node[transform canvas={shift=(0:1.2)},below] {n};
           \end{scope}
@@
 
-\begin{figure}[h]
-  \begin{center}
+\begin{figure}
+  \centering
     \begin{tabular}{cc}
 
-      \begin{minipage}{0.48\hsize}
+      \begin{minipage}{0.48\linewidth}
+      \centering
         \begin{tikzpicture}
-          \draw[thick, rounded corners = 10pt]
-          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;
 
-          \begin{scope}[xshift=2cm, yshift=2cm]
             \fill(0,0) circle [radius=0.1];
@@
             \foreach \theta in {120,-120,180}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
@@
             \foreach \theta in {0,60,-60}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
             }
 
-            \draw[->] (180:1.4)--(180:0.1);
+            \draw[->] (180:1.1)--(180:0.1);
 
-            \node[transform canvas={shift=(120:1.5)},right] {A};
-            \node[transform canvas={shift=(-120:1.5)},right] {B};
-            \node[transform canvas={shift=(180:1.5)},left] {P};
+            \node[transform canvas={shift=(120:1.2)},right] {A};
+            \node[transform canvas={shift=(-120:1.2)},right] {B};
+            \node[transform canvas={shift=(180:1.2)},left] {P};
 
-            \node[transform canvas={shift=(60:1.5)},left] {c};
-            \node[transform canvas={shift=(-60:1.5)},left] {d};
-          \end{scope}
+            \node[transform canvas={shift=(60:1.2)},left] {c};
+            \node[transform canvas={shift=(-60:1.2)},left] {d};
 
-          \node at (2,-0.5) {Point $c$ and $d$ are free};
+          \node at (0,-2) {Point $c$ and $d$ are free};
         \end{tikzpicture}
@@
 
-      \begin{minipage}{0.48\hsize}
+      \begin{minipage}{0.48\linewidth}
+      \centering
         \begin{tikzpicture}
-          \draw[thick, rounded corners = 10pt]
-          (0,0)--(4,0)--(4,4)--(0,4)-- cycle;
 
-          \begin{scope}[xshift=2cm, yshift=2cm]
             \fill(0,0) circle [radius=0.1];
@@
             \foreach \theta in {120,-120,180,60}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
@@
             \foreach \theta in {0,-60}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
             }
 
-            \draw[->] (180:1.4)--(180:0.1);
+            \draw[->] (180:1.1)--(180:0.1);
 
-            \node[transform canvas={shift=(120:1.5)},right] {A};
-            \node[transform canvas={shift=(-120:1.5)},right] {B};
-            \node[transform canvas={shift=(180:1.5)},left] {P};
+            \node[transform canvas={shift=(120:1.2)},right] {A};
+            \node[transform canvas={shift=(-120:1.2)},right] {B};
+            \node[transform canvas={shift=(180:1.2)},left] {P};
 
-            \node[transform canvas={shift=(-60:1.5)},right] {d};
-            \node[transform canvas={shift=(60:1.5)},right] {c};
-            \node[transform canvas={shift=(0:1.5)},right] {e};
-          \end{scope}
+            \node[transform canvas={shift=(-60:1.2)},right] {d};
+            \node[transform canvas={shift=(60:1.2)},right] {c};
+            \node[transform canvas={shift=(0:1.2)},right] {e};
 
-          \node at (2,-0.5) {Point $c$ is occupied};
+          \node at (0,-2) {Point $c$ is occupied};
         \end{tikzpicture}
@@
     \label{TTT_tunnel_exit}
-  \end{center}
 \end{figure}

### 2018-11-13 paper.tex
Fig 1 added (summary)
In Fig. 1, I summarized the results obtained so far.

@@
 
+%------------------------------------------------------
 	\section{Introduction}
+%------------------------------------------------------
 
@@
 
+\begin{figure}[tb]
+\begin{tikzpicture}
+
+\node (origin) at (0, 0) {};
+
+\draw[-latex] (origin) -- ++(0:3) node[below] {$\delta$}; 
+\node at (1, -0.2) {1};
+\node at (2, -0.2) {2};
+\draw[-latex] (origin) -- ++(90:5) node[left] {$\alpha$}; 
+\node at (-0.2, 1) {1};
+\node at (-0.2, 2) {2};
+\node at (-0.2, 3) {3};
+\node at (-0.2, 4) {4};
+
+%Results
+\node at (1, 4) {$O(n^2)$};
+\node at (1, 3) {$O(n)$};
+\node at (1, 2) {$O(n^2)$};
+\node at (1, 1) {$O(n)$ \cite{DemaineDNA24}};
+
+\node at (2, 1) {$O(n^2)$};
+
+\end{tikzpicture}
+\caption{Summary of the results.}
+\label{fig:summary}
+\end{figure}
+
+%------------------------------------------------------
 	\section{Preliminaries}
+%------------------------------------------------------
 \input{uos_preliminaries.tex}
@@
 Because of the time hierarchy theorems, we know that $\mathrm{P}\subsetneq \mathrm{EXP}$, so we can conclude that OS which cannot deterministically fold transcripts of length exponential in the length of the seed are not computationally universal.
+
+\section{Problem description}
+
+In \cite{DemaineDNA24}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
+We consider this finiteness problem under various settings of the values of delay and arity. 
+Results on this problem are summarized in Fig.~\ref{fig:summary}.
 

### 2018-11-14 ttt.tex
11/14 en

@@
 
-In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 2 deterministically and moreover that the only infinite conformations which its oritatami system can yield is only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
+In this section, we consider on finiteness of structures produced deterministically at delay 1.
+In result, cases of arity 1 and 3 can only yield finite structures which is size of $\mathcal{O} (n)$, and cases of arity 4 and more can only yield finite structures which is size of $mathcal{O} (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
+
+%In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 2 deterministically and moreover that the only infinite conformations which its oritatami system can yield is only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
 
@@
 A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
+How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
 Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
-We call such beads as $p$ $inside\ of\ a\ tunnel$ and such beads as $p^\prime$ $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel.
+We call such a bead $p$ as $inside\ of\ a\ tunnel$ and such beads $p^\prime$ as $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel.
 If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor.
@@
 
-If a bead is stabilized through a tunnel section, then it can provide two binging capabilities and create tunnel sections.
+If a bead is stabilized through a tunnel section, then it can provide some bonds.
+Let us consider on bonds of $C_i$.
+$C_i$ is represented $C = (W,P,H)$ where $|W| = i + n$ $C_i$ contains $\alpha \cdot (i + n) - 2|H|$ bonds because $C_i$ consists of $i + n$ beads and a bead has just $\alpha$ bonds and then $2 |H|$ of the those bonds are already used.
+However, even if a bead has an available bond, $w[j]$ $(j > i)$ might not be able to use this bond because the bond has possibility that it is blocked by transcripts $w[i+1..j-1]$.
+Number of $binding\ capabilities$ does not contain that case so that it is at most $\alpha \cdot (i + n) - 2|H|$.
 
@@
 \begin{theorem}[Tunnel Troll Theorem]
-  Let $\Xi$ be an unary oritatami system of delay 1 and arity 2. If a bead is stabilized through a tunnel section, then it consume some binging capabilities.
+  Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$.
+If there is a part of transcript $w[i-1..j+1] = btt...tb$, then $C_i$'s binding capabilities is more than $C_j$'s binding capabilities.
 \end{theorem}
@@
 Assume $\Xi$ is deterministic.
-Let us represent its transcript $w$ as $w = w_1 w_2 w_3 \cdots$ for beads $w_1 , w_2 , w_3 , \cdots \in \Sigma = \{e\}$.
-Each of these beads is stabilized either by being bound or through a tunnel section (or by both).
-How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
-On the other hand, each of beads are bound either inside of tunnel or outside (Fig.
+%How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
+Each of beads in transcript are bound either inside of tunnel or outside (Fig.
 \ref{TTT_position1}).
@@
 
-Tunnel sections have three possible shape with considering symmetry such as acute turn, straight and obtuse turn (Figure \ref{TTT_tunnel}).
-Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Figure \ref{TTT_enterpoint}).
+Tunnel sections have three possible shape with considering symmetry such as straight, acute turn and obtuse turn (Fig.
+\ref{TTT_tunnel}).
+Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Fig.
+\ref{TTT_enterpoint}).
 
@@
   \begin{center}
-    \begin{tabular}{lr}
+    \begin{tabular}{cc}
 
       \begin{minipage}{0.2\hsize}
+      \centering
         \begin{tikzpicture}
@@
       \begin{minipage}{0.2\hsize}
+      \centering
         \begin{tikzpicture}
@@
       \begin{minipage}{0.3\hsize}
+      \centering
         \begin{tikzpicture}
+	 \draw[->,white] (120:1.1)--(120:0.1);%for adjustment
 
-          \begin{scope}[xshift=2cm, yshift=2cm]
             \fill(0,0) circle [radius=0.1];
-            \node[above] at (0,0) {$p^\prime$};
+            \node[below] at (0,0) {$p^\prime$};
 
@@
             \node[transform canvas={shift=(-60:1.2)},right] {B};
-
             \node[transform canvas={shift=(120:1.2)},left] {c};
             \node[transform canvas={shift=(-120:1.2)},left] {d};
-          \end{scope}
 
-          \node at (2,-0.5) {$t_0$};
+          \node at (0,-2) {$t_{0}$};
         \end{tikzpicture}
@@
       \begin{minipage}{0.3\hsize}
+      \centering
         \begin{tikzpicture}
 
-          \begin{scope}[xshift=2cm, yshift=2cm]
             \fill(0,0) circle [radius=0.1];
@@
             \node[transform canvas={shift=(-120:1.2)},left] {d};
-          \end{scope}
 
-          \node at (2,-0.5) {$t_{\pm 60}$};
+          \node at (0,-2) {$t_{\pm 60}$};
         \end{tikzpicture}
@@
       \begin{minipage}{0.3\hsize}
+      \centering
         \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
             \fill(0,0) circle [radius=0.1];
@@
             \node[transform canvas={shift=(0:1.2)},below] {n};
-          \end{scope}
 
-          \node at (2,-0.5) {$t_{\pm 120}$};
+          \node at (0,-2) {$t_{\pm 120}$};
         \end{tikzpicture}
@@
 \end{itemize}
-
-\begin{figure}[h]
-  \begin{center}
+\begin{figure}
+  \centering
     \begin{tabular}{cc}
@@
       \begin{minipage}{0.48\hsize}
+      \centering
         \begin{tikzpicture}
-          \draw[thick, rounded corners = 10pt]
-          (-2,2)--(5,2)--(5,-3)--(-2,-3)-- cycle;
 
@@
           \foreach \theta in {60,-60,120,-120,180}{
-            \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-            \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
           }
 
-          \fill(0:1.5) circle [radius=0.1];
-          \draw[->] (0:0.1)--(0:1.4);
+          \fill(0:1.2) circle [radius=0.1];
+          \draw[->] (0:0.1)--(0:1.1);
 
-          \node[left] at (-60:1.5) {A};
+          \node[left] at (-60:1.2) {A};
 
-          \begin{scope}[shift=(0:3)]
+          \begin{scope}[shift=(0:2.4)]
             \fill(0,0) circle [radius=0.1];
@@
             \foreach \theta in {120,60,-60}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
 
-            \draw[->] (180:1.4)--(180:0.1);
-            \draw[->] (-120:0.1)--(-120:1.4);
+            \draw[->] (180:1.1)--(180:0.1);
+            \draw[->] (-120:0.1)--(-120:1.1);
 
-            \node[below] at (180:1.5) {$w_{i-2}$};
+            \node[below] at (180:1.2) {$w_{i-2}$};
             \node[right] at (0:0) {$w_{i-1}$};
-            \node[right] at (-120:1.5) {$w_i$};
+            \node[right] at (-120:1.2) {$w_i$};
 
-            \node[left] at (120:1.5) {B};
-            \node[left] at (60:1.5) {C};
-            \node[left] at (0:1.5) {D};
+            \node[left] at (120:1.2) {B};
+            \node[left] at (60:1.2) {C};
+            \node[left] at (0:1.2) {D};
 
-            \begin{scope}[shift=(-120:1.5)]
+            \begin{scope}[shift=(-120:1.2)]
               \draw(0,0) circle [radius=0.1];
               \foreach \theta in {-120,-60}{
-                \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
+                \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
               }
 
-              \node[right] at (-120:1.5) {e};
-              \node[right] at (-60:1.5) {f};
+              \node[right] at (-120:1.2) {e};
+              \node[right] at (-60:1.2) {f};
             \end{scope}
@@
 
-          \node at (1.5,-3.5) {Pattern 1};
+          \node at (1.2,-2.5) {Pattern 1};
         \end{tikzpicture}
@@
       \begin{minipage}{0.48\hsize}
+      \centering
         \begin{tikzpicture}
-          \draw[thick, rounded corners = 10pt]
-          (-2,2)--(4.5,2)--(4.5,-4.5)--(-2,-4.5)-- cycle;
 
@@
           \foreach \theta in {60,0,120,-120,180}{
-            \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-            \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
           }
 
-          \draw[->] (-60:0.1)--(-60:1.4);
+          \draw[->] (-60:0.1)--(-60:1.1);
 
-          \begin{scope}[shift=(-60:1.5),shift=(0:1.5)]
+          \begin{scope}[shift=(-60:1.2),shift=(0:1.2)]
             \fill(0,0) circle [radius=0.1];
-            \fill(180:1.5) circle [radius=0.1];
+            \fill(180:1.2) circle [radius=0.1];
 
             \foreach \theta in {120,60,0,-60}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
             }
 
-            \draw[->] (180:1.4)--(180:0.1);
-            \draw[->] (-120:0.1)--(-120:1.4);
+            \draw[->] (180:1.1)--(180:0.1);
+            \draw[->] (-120:0.1)--(-120:1.1);
 
-            \node[below] at (180:1.5) {$w_{i-2}$};
+            \node[below] at (180:1.2) {$w_{i-2}$};
             \node[right] at (0:0) {$w_{i-1}$};
-            \node[right] at (-120:1.5) {$w_i$};
+            \node[right] at (-120:1.2) {$w_i$};
 
-            \node[left] at (120:1.5) {A};
-            \node[left] at (60:1.5) {B};
-            \node[left] at (0:1.5) {C};
+            \node[left] at (120:1.2) {A};
+            \node[left] at (60:1.2) {B};
+            \node[left] at (0:1.2) {C};
 
-            \begin{scope}[shift=(-120:1.5)]
+            \begin{scope}[shift=(-120:1.2)]
               \draw(0,0) circle [radius=0.1];
               \foreach \theta in {180,-120,-60}{
-                \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
+                \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
               }
 
-              \node[right] at (180:1.5) {e};
-              \node[right] at (-120:1.5) {f};
-              \node[right] at (-60:1.5) {g};
+              \node[right] at (180:1.2) {e};
+              \node[right] at (-120:1.2) {f};
+              \node[right] at (-60:1.2) {g};
             \end{scope}
@@
 
-          \node at (1.25,-5) {Pattern 2};
+          \node at (1.25,-4) {Pattern 2};
         \end{tikzpicture}
@@
     \label{TTT_tunnelC_enter_usingTunnel}
-  \end{center}
 \end{figure}
@@
   \begin{center}
-    \begin{tabular}{cc}
-
-      \begin{minipage}{0.48\hsize}
         \begin{tikzpicture}
-          \draw[thick, rounded corners = 10pt]
-          (-3,2)--(2.5,2)--(2.5,-3)--(-3,-3)-- cycle;
-
+        \draw[->,white] (-70:0.1) -- (-70:3);
           \foreach \theta in {60,-60,120,0}{
-            \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1)--(0.1,0.1);
-            \draw[transform canvas={shift=(\theta:1.5)}](0.1,-0.1)--(-0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
           }
 
-          \fill(180:1.5) circle [radius=0.1];
+          \fill(180:1.2) circle [radius=0.1];
           \fill(0:0) circle [radius=0.1];
 
-          \draw[transform canvas={shift=(180:1.5)}] (105:1.4) edge[bend right] (105:0.1);
-          \draw[->] (180:1.4) -- (180:0.1);
-          \draw[->] (-120:0.1) -- (-120:1.4);
+          \draw[transform canvas={shift=(180:1.2)}] (105:1.1) edge[bend right] (105:0.1);
+          \draw[->] (180:1.1) -- (180:0.1);
+          \draw[->] (-120:0.1) -- (-120:1.1);
 
-          \node[below] at (180:1.5) {$t_1$};
+          \node[below] at (180:1.2) {$t_1$};
           \node[right] at (0:0) {$t_2$};
-          \node[left] at (-120:1.5) {$t_3$};
+          \node[left] at (-120:1.2) {$t_3$};
 
-          \node[right] at (120:1.5) {A};
-          \node[right] at (60:1.5) {B};
-          \node[right] at (0:1.5) {C};
+          \node[right] at (120:1.2) {A};
+          \node[right] at (60:1.2) {B};
+          \node[right] at (0:1.2) {C};
 
-          \begin{scope}[shift=(-120:1.5)]
+          \begin{scope}[shift=(-120:1.2)]
             \draw(0,0) circle [radius=0.1];
             \foreach \theta in {-120,-60,180}{
-              \draw[transform canvas={shift=(\theta:1.5)}](-0.1,-0.1) rectangle (0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
             }
@@
           \end{scope}
-
-          \node at (-0.25,-3.5) {Pattern 1};
         \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
     \caption{Case of $S[i-2..i] = bbt$}
@@
     \begin{tikzpicture}
-      \draw[thick, rounded corners = 10pt]
-      (-1.5,2)--(3,2)--(3,-2.5)--(-1.5,-2.5)-- cycle;
 
-      \draw[transform canvas={shift=(-120:1.5)}](-0.1,-0.1)--(0.1,0.1);
-      \draw[transform canvas={shift=(-120:1.5)}](0.1,-0.1)--(-0.1,0.1);
+      \draw[transform canvas={shift=(-120:1.2)}](-0.1,-0.1)--(0.1,0.1);
+      \draw[transform canvas={shift=(-120:1.2)}](0.1,-0.1)--(-0.1,0.1);
 
@@
       \fill(0:1.5) circle [radius=0.1];
-      \fill[shift=(0:1.5)](40:1.5) circle [radius=0.1];
+      \fill[shift=(0:1.2)](40:1.2) circle [radius=0.1];
 
-      \draw[->] (-120:1.4) edge[bend left] (-120:0.1);
+      \draw[->] (-120:1.1) edge[bend left] (-120:0.1);
       \draw[->] (0:0) -- (0:1.3);
-      \draw[->,transform canvas={shift=(0:1.5)}] (0:0.1) edge[bend right] (40:1.3);
+      \draw[->,transform canvas={shift=(0:1.2)}] (0:0.1) edge[bend right] (40:1.3);
 
-      \draw [shift=(60:1.5)] (-0.1,-0.1) rectangle (0.1,0.1);
-      \draw [shift=(-60:1.5)] (-0.1,-0.1) rectangle (0.1,0.1);
+      \draw [shift=(60:1.2)] (-0.1,-0.1) rectangle (0.1,0.1);
+      \draw [shift=(-60:1.2)] (-0.1,-0.1) rectangle (0.1,0.1);
 
-      \node[below] at (-120:1.5) {$v_{i-2}$};
+      \node[below] at (-120:1.2) {$v_{i-2}$};
       \node[above] at (0:0) {$v_{i-1}$};
-      \node[above] at (0:1.5) {$v_i$};
-      \node[left, shift=(0:1.5)] at (40:1.5) {$v_{i+1}$};
+      \node[above] at (0:1.2) {$v_i$};
+      \node[left, shift=(0:1.2)] at (40:1.2) {$v_{i+1}$};
 
-      \node[right] at (60:1.5) {A};
-      \node[right] at (-60:1.5) {B};
+      \node[right] at (60:1.2) {A};
+      \node[right] at (-60:1.2) {B};
 
     \end{tikzpicture}
-    \caption{Case of $S[i$}
+    \caption{Case of $S[i]$}
     \label{TTT_case_of_o}

### 2018-11-14 ttt.tex
11/14 before dinner

@@
 A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
-How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
+Accordingly, how they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
+
 Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
@@
   Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$.
-If there is a part of transcript $w[i-1..j+1] = btt...tb$, then $C_i$'s binding capabilities is more than $C_j$'s binding capabilities.
+If there is a part of transcript $w[i..j+1] = bttt...tb$, then $C_i$'s binding capabilities is more than $C_j$'s binding capabilities.
 \end{theorem}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Each of beads in transcript are bound either inside of tunnel or outside (Fig.
-\ref{TTT_position1}).
+\ref{TTT_position}).
 If a bead is stabilized at inside of tunnel, then its successor is already decided the position either inside of a tunnel or outside.
@@
 \ref{TTT_tunnel}).
-Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Fig.
+%Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Fig.
 \ref{TTT_enterpoint}).
 
+Let us consider each of cases of tunnel A, B, and C. Accordingly, We use lemma \ref{TTT_neighbor_lemma}
+
+\begin{lemma}
+\label{TTT_neighbor_lemma}
+If a bead does not have any bond, then neighbors of it must be occupied by $\alpha + 2$ beads at $\delta = 1$ and unary except first and last beads.
+\end{lemma}
+
+A bead in transcript needs predecessor and successor except first and last beads.
+If the bead does not have ant bond, then it use hand with $\alpha$ neighbors.
+Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
+
+\paragraph{}
 Let us consider tunnel sections only tunnel A and B.
 See Fig.
-\ref{TTT_position2}.
-From appendix (Entrance of Tunnel A, B and Exit of Tunnel), we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successer\ in\ outside$.
+\ref{TTT_position}.
+From appendix (Entrance of Tunnel A, B and Exit of Tunnel), we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successor\ in\ outside$.
+
+%The sequence $S$ can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+ \cup bt^+bt^+$.
 
@@
 If $w[i]$ is stabilized by tunnel C and $S[i+1]$ is $t$, then $w[i+1]$ is stabilized by tunnel A or B because if $w[i+1]$ is stabilized by tunnel C, then $C_{i+1}$ is a terminal.
-Hence, tunnel C section is devided cases sush as Figure \ref{TTT_tunnelC_graph}.
+Hence, tunnel C section is divided cases such as Figure \ref{TTT_tunnelC_graph}.
 Cases of $S[i...] = bt^l (l \geq 2)$ are already considered (Upper).
@@
     \end{tabular}
-    \caption{All possible tunnel sections}
+    \caption{All possible tunnel sections: straight, acute turn, and obtuse turn}
     \label{TTT_tunnel}
@@
 
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{cc}
+%\begin{figure}
+%  \begin{center}
+%    \begin{tabular}{cc}
+%      
+%      \begin{minipage}{0.2\hsize}
+%      \centering
+%        \begin{tikzpicture}
+%
+%          \begin{scope}[xshift=1cm, yshift=2cm]
+%            \fill(0,0) circle [radius=0.1];
+%            \node[above] at (180:1.2) {$p^\prime$};
+%            
+%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
+%            
+%            
+%            \foreach \theta in {120,-120}{
+%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+%            }
+%
+%            \draw[->] (-1.1,0) -- (-0.1,0);
+%          \end{scope}
+%
+%          \node at (0.25,0) {Tunnel A,B};
+%        \end{tikzpicture}
+%      \end{minipage}
+%
+%      \begin{minipage}{0.2\hsize}
+%      \centering
+%        \begin{tikzpicture}
+%
+%          \begin{scope}[xshift=1cm, yshift=2cm]
+%            \fill(0,0) circle [radius=0.1];
+%            \node[above] at (180:1.2) {$p^\prime$};
+%
+%            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
+%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
+%            
+%            
+%            \foreach \theta in {120}{
+%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+%            }
+%
+%            \draw[->] (-1.1,0) -- (-0.1,0);
+%          \end{scope}
+%
+%          \node at (0.25,0) {Tunnel C};
+%        \end{tikzpicture}
+%      \end{minipage}
+%
+%    \end{tabular}
+%    \caption{Entrance of a tunnel}
+%    \label{TTT_enterpoint}
+%  \end{center}
+%\end{figure}
 
-      \begin{minipage}{0.2\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=1cm, yshift=2cm]
-            \fill(0,0) circle [radius=0.1];
-            \node[above] at (180:1.2) {$p^\prime$};
-
-            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
-
-            \foreach \theta in {120,-120}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-            }
-
-            \draw[->] (-1.1,0) -- (-0.1,0);
-          \end{scope}
-
-          \node at (0.25,0) {Tunnel A,B};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.2\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=1cm, yshift=2cm]
-            \fill(0,0) circle [radius=0.1];
-            \node[above] at (180:1.2) {$p^\prime$};
-
-            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
-            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
-
-            \foreach \theta in {120}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-            }
-
-            \draw[->] (-1.1,0) -- (-0.1,0);
-          \end{scope}
-
-          \node at (0.25,0) {Tunnel C};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Entrance of a tunnel}
-    \label{TTT_enterpoint}
-  \end{center}
-\end{figure}
+%\begin{figure}
+%  \begin{center}
+%    \begin{tikzpicture}
+%      \draw[thick]
+%      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
+%      \node at(2.5,1) {Outside};
+%      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
+%      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
+%
+%      
+%      
+%      \draw[thick]
+%      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
+%      \node at(10.5,1) {Inside of a tunnel};
+%      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
+%      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
+%
+%      \draw[->]
+%      (outside) edge [bend left] node[left] {$b$} (enter)
+%                edge [loop left] node[left] {$b$} (outside)
+%      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
+%                edge [bend left] node[above] {$b$} (next-outside)
+%                edge [bend left] node[right] {$b$}  (outside)
+%      (next-tunnel) edge         node[right] {$t$} (next-outside)
+%                edge [loop right]node[below] {$t$}    (next-tunnel)
+%      (next-outside) edge[bend left] node[above] {$t$}  (outside)
+%                edge [bend left]     node[above] {$t$}(enter)
+%      ;
+%      
+%    \end{tikzpicture}
+%    \caption{Cases on position of a bead}
+%    \label{TTT_position1}
+%  \end{center}
+%\end{figure}
 
@@
     \begin{tikzpicture}
-      \draw[thick]
-      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
-      \node at(2.5,1) {Outside};
-      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
-      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
+      \draw[thick, gray]
+      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
+      \node at(2,1) {Outside};
+      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
+      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
 
-      \draw[thick]
-      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
-      \node at(10.5,1) {Inside of a tunnel};
-      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
+      \draw[thick, gray]
+      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
+      \node at(9,1) {Inside of a tunnel};
+      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
+      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
 
       \draw[->]
-      (outside) edge [bend left] node[left] {$b$} (enter)
-                edge [loop left] node[left] {$b$} (outside)
-      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
-                edge [bend left] node[above] {$b$} (next-outside)
-                edge [bend left] node[right] {$b$}  (outside)
-      (next-tunnel) edge         node[right] {$t$} (next-outside)
-                edge [loop right]node[below] {$t$}    (next-tunnel)
-      (next-outside) edge[bend left] node[above] {$t$}  (outside)
-                edge [bend left]     node[above] {$t$}(enter)
-      ;
-
-    \end{tikzpicture}
-    \caption{Cases on position of a bead}
-    \label{TTT_position1}
-  \end{center}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw[thick]
-      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
-      \node at(2.5,1) {Outside};
-      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
-      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
-
-      \draw[thick]
-      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
-      \node at(10.5,1) {Inside of a tunnel};
-      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successer in inside};
-      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successer in outside};
-
-      \draw[->]
-      (outside) edge [bend left] node[left] {$-1$} (enter)
-                edge [loop left] node[left] {$\pm 0$} (outside)
-      (enter)   edge [bend left] node[above] {$-1$} (next-tunnel)
-                edge [bend left] node[above] {$-a$} (next-outside)
-                edge [bend left] node[right] {$\pm 0$}  (outside)
-      (next-tunnel) edge         node[right] {$-a$} (next-outside)
-                edge [loop right]node[below] {$\pm 0$}    (next-tunnel)
-      (next-outside) edge[bend left] node[above] {$+a$}  (outside)
-                edge [bend left]     node[above] {$+(a-1)$}(enter)
+      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
+                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
+      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
+                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
+                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
+      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
+                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
+      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
+                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
       ;
@@
     \caption{Increment on Tunnel A,B}
-    \label{TTT_position2}
+    \label{TTT_position}
   \end{center}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%/////////////////////////////////////////////////
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Appendix of Tunnel Troll Theorem}
@@
 \item{Case of $t_0$}\\
-  Let us consider points of $c,d$ either occupied or not.
-A point $c$ or $d$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-If $c$ is free, then $p^\prime$ has to be bound to a bead except $A$ due to deterministically stabilize.
-In this situation, at least three neighbors of A are free that is at most three neighbors of A are occupied.
-A leave at least one binging capability because beads of beighbors are predecessor and successor in addition A is able to consume itself binging capabilities only one-time.
-Hence, $p^\prime$ must be bound to A.
-Thus, a case of $t_0$ consumes some binding capabilities.
+  Let us consider points of $n_3,n_4$ either occupied or not.
+A point $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
+If $n_3$ is free, then $p^\prime$ has to be bound to a bead except $n_1$ due to deterministically stabilize.
+In this situation, at least three neighbors of $n_1$ are free that is $n_1$ leave at least one bond from lemma \ref{TTT_neighbor_lemma}.
+Hence, $p^\prime$ must be bound to $n_1$.
+Thus, a case of $t_0$ consumes two binding capabilities and it does not supply any binding capabilities.
 
 \item{Case of $t_{\pm 60}$}\\
-  In this case, a point $c$ or $d$ is free, too.
-If $c$ is free, $p^\prime$ has to be bound to A or B.
-If $c$ is occupied, then $d$ is free.
-This time, B has some binding capabilitie so $p^\prime$ has to be bound to B.
+  In this case, a point $n_4$ or $n_5$ is free, too.
+If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$.
+If $n_5$ is occupied, then $n_4$ is free.
+This time, $n_2$ has some binding capabilities so $p^\prime$ has to be bound to $n_2$.
 
   In this situation, $p^\prime$ is able to supply a binding capability.
-if this capability is active, $p^\prime$ bind a bead into $c$ or $d$.
-However, B and P are exist in back bone.
-According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $c$ or $d$ so this capability is inactive.
+if this capability is active, $p^\prime$ bind a bead into $n_4$ or $n_5$.
+However, $n_2$ and $n_3$ are exist in back bone.
+According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive.
 Thus, a case of $t_{\pm 60}$ consumes some binding capabilities.
@@
 \item{Case of $t_{\pm 120}$}\\
-  Binding capabilities that $p^\prime$ supply are inactive according to Jordan curve theorem on A and P.
-Moreover, $p^\prime$ has to be bound to one of $c$, $d$,$e$ in order to deterministically stabilize.
+  Binding capabilities that $p^\prime$ supply are inactive according to Jordan curve theorem on $n_1$ and $n_2$.
+Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
 Thus, a case of $t_{\pm 120}$ consumes some binging capabilities.
@@
 
-            \node[transform canvas={shift=(60:1.2)},right] {A};
-            \node[transform canvas={shift=(-60:1.2)},right] {B};
-            \node[transform canvas={shift=(120:1.2)},left] {c};
-            \node[transform canvas={shift=(-120:1.2)},left] {d};
+            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
 
@@
 
-            \node[transform canvas={shift=(60:1.2)},right] {A};
-            \node[transform canvas={shift=(-60:1.2)},right] {B};
-            \node[transform canvas={shift=(120:1.2)},left] {P};
-
-            \node[transform canvas={shift=(180:1.2)},left] {c};
-            \node[transform canvas={shift=(-120:1.2)},left] {d};
+            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
 
@@
 
-            \node[transform canvas={shift=(-60:1.2)},right] {A};
-            \node[transform canvas={shift=(60:1.2)},right] {P};
-
-            \node[transform canvas={shift=(120:1.2)},left] {c};
-            \node[transform canvas={shift=(180:1.2)},left] {d};
-            \node[transform canvas={shift=(-120:1.2)},left] {e};
-            \node[transform canvas={shift=(0:1.2)},below] {n};
+            \node[transform canvas={shift=(0:1.2)},below] {$n_0$};
+            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
 
@@
 Fig.\ref{TTT_tunnel_exit} exhibits all the two kings of exit of tunnel. 
-At least one of point $c$ or $d$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
+At least one of point $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
 
@@
 \begin{itemize}
-\item{Case of $c$ and $d$ are free}\\
+\item{Case of $n_1$ and $n_2$ are free}\\
   This case can be regarded same situation as entrance.
 See Fig.\ref{TTT_tunnel_exit} (Left).
-Predecessor P has to be bound A and B because each of A and B leave binding capabilities.
+Predecessor $n_5$ has to be bound $n_4$ and $n_5$ because each of $n_3$ and $n_4$ leave binding capabilities.
 Hence, at least $a=2$.
@@
   See Fig.\ref{TTT_tunnel_exit} (Right).
-If $c$ is pccupied, then $d$ is free so that P has to be bound B.
+If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$.
 Hence, at least $a=1$.
-This case can supply two binding capabilities but $p^\prime$ can bind to only one of $e$ or $d$ because $e$ or $d$ will be occupied a successor of $p^\prime$.
-Therefore, this case supply at most only $a=1$ active binding capabiliry.
+This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied a successor of $p^\prime$.
+Therefore, this case supply at most only $a=1$ active binding capability.
 
@@
 \begin{itemize}
-\item{Case of $c$ and $d$ are free}\\
+\item{Case of $n_1$ and $n_2$ are free}\\
   In $\alpha \geq 3$, if three neighbors of a bead leave, then it can supply two binding capabilities.
-Therefore Predecessor P has to be bound A and B, and $p^\prime$, too.
+Therefore Predecessor $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$, too.
 In this case, at least consumes four bindings and supplies at most two bindings.
@@
 \item{Case of $c$ is occupied}\\
-  In this case, B leave at least two bindings and A, $c$ also leave at least one binding.
-Therefore P has to be bound A and B, and $p^\prime$ also has to be bound B and $c$.
+  In this case, $n_4$ leave at least two bindings and $n_3$, $n_1$ also leave at least one binding.
+Therefore $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$ also has to be bound $n_1$ and $n_4$.
 In this case, at least consumes four bindings and supplies at most one binding.
-Thus, it consumes some binding capabiliries, totally.
+Thus, it consumes some binding capabilities, totally.
 \end{itemize}
@@
 
-            \node[transform canvas={shift=(120:1.2)},right] {A};
-            \node[transform canvas={shift=(-120:1.2)},right] {B};
-            \node[transform canvas={shift=(180:1.2)},left] {P};
+            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
 
-            \node[transform canvas={shift=(60:1.2)},left] {c};
-            \node[transform canvas={shift=(-60:1.2)},left] {d};
-
-          \node at (0,-2) {Point $c$ and $d$ are free};
+          \node at (0,-2) {Point $n_1$ and $n_2$ are free};
         \end{tikzpicture}
@@
 
-            \node[transform canvas={shift=(120:1.2)},right] {A};
-            \node[transform canvas={shift=(-120:1.2)},right] {B};
-            \node[transform canvas={shift=(180:1.2)},left] {P};
+            \node[transform canvas={shift=(0:1.2)},right] {$n_0$};
+            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
 
-            \node[transform canvas={shift=(-60:1.2)},right] {d};
-            \node[transform canvas={shift=(60:1.2)},right] {c};
-            \node[transform canvas={shift=(0:1.2)},right] {e};
-
-          \node at (0,-2) {Point $c$ is occupied};
+          \node at (0,-2) {Point $n_1$ is occupied};
         \end{tikzpicture}
@@
 \item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  In this figure, Bead A has at least one binding so that $w_{i-2}$ has to bound A.
-Moreover, $w_{i-1}$ has to bound one of B, C, D in order to stabilize deterministically.
-On the other hand, $w_i$ can supply two bindings but free neighbors of $w_i$ are two points.
-One of them is occupied a successor.
-Therefore $w_i$ can only bind one of $e,f$ that is $w_i$ supplies at most one binding.
+  In this figure, Bead $n_4$ has at least one binding so that $w[i-2]$ has to bound $n_4$.
+Moreover, $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
+On the other hand, $w[i]$ can supply two bindings but free neighbors of $w[i]$ are two points.
+One of them is occupied by a successor.
+Therefore $w[i]$ can only bind one of $n_5, n_6$ that is $w[i]$ supplies at most one binding.
 Thus, this case consumes some binding capabilities.
@@
 \item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  This cases are divided on number of capabilities that $w_{i-2}$ consumes.
+  This cases are divided on number of capabilities that $w[i-2]$ consumes.
   \begin{itemize}
-  \item[-]{$w_i$ does not consume any bindings}\\
-    $w_{i-1}$ has to bound one of B, C, D in order to stabilize deterministically.
-$w_i$ has to be bound to $w_{i-2}$ because $w_{i-2}$ has bindings.
-This time, let us consider either $e$ is occupied or not.
-If $e$ is occupied, then $w_{i-2}$ has no active bindings that is this situation consumes some binding capabilities.
-If $e$ is free and $w_{i+1}$ is stabilized in $e$, then $w_{i-2}$ has to bind $w_{i+1}$.
+  \item[-]{$w[i]$ does not consume any bindings}\\
+    $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
+$w[i]$ has to be bound to $w[i-2]$ because $w[i-2]$ has bindings.
+This time, let us consider either $n_4$ is occupied or not.
+If $n_4$ is occupied, then $w[i-2]$ has no active bindings that is this situation consumes some binding capabilities.
+If $n_4$ is free and $w[i+1]$ is stabilized in $n_4$, then $w[i-2]$ has to bind $w[i+1]$.
 Therefore, In this case, stabilization of $w[i-2..i+1]$ consumes some bindings.
-If $e$ is free and $w_{i+1}$ is stabilized except $e$, then this oritatami system has to use two binding capabilities in order to bind $w_{i+1}$.
+If $n_4$ is free and $w[i+1]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[i+1]$.
 Therefore, in this case consumes some bindings.
@@
   \item[-]{$w_i$ consumes one binding}\\
-    In this case, $w_{i-1}$ has to be bound one of B, C, D. In addition, $w_{i-2}$ and $w_i$ are not supply any bindings. Thus, in this cases consume some binding capabilities.。
+    In this case, $w_{i-1}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[i-2]$ and $w[i]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
   \item[-]{$w_i$ consumes two bindings}\\
-    In this case, $w_{i-2}$ already consumes two binding. $w_{i-1}$ has to be bound. $w_i$ supplies two bindings. Thus, in this cases consume some binding capabilities.
+    In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies two bindings. Thus, in this cases consume some binding capabilities.
 
@@
 
-          \node[left] at (-60:1.2) {A};
+          \node[left] at (-60:1.2) {$n_4$};
 
@@
 
-            \foreach \theta in {120,60,-60}{
+            \foreach \theta in {120,60,-60,0}{
               \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
@@
 
-            \node[below] at (180:1.2) {$w_{i-2}$};
-            \node[right] at (0:0) {$w_{i-1}$};
-            \node[right] at (-120:1.2) {$w_i$};
+            \node[below] at (180:1.2) {$w[i-2]$};
+            \node[above] at (0:0) {$w[i-1]$};
+            \node[right] at (-120:1.2) {$w[i]$};
 
-            \node[left] at (120:1.2) {B};
-            \node[left] at (60:1.2) {C};
-            \node[left] at (0:1.2) {D};
+            \node[left] at (120:1.2) {$n_3$};
+            \node[left] at (60:1.2) {$n_2$};
+            \node[left] at (0:1.2) {$n_1$};
 
@@
 
-              \node[right] at (-120:1.2) {e};
-              \node[right] at (-60:1.2) {f};
+              \node[right] at (-120:1.2) {$n_5$};
+              \node[right] at (-60:1.2) {$n_6$};
             \end{scope}
@@
 
-            \node[below] at (180:1.2) {$w_{i-2}$};
-            \node[right] at (0:0) {$w_{i-1}$};
-            \node[right] at (-120:1.2) {$w_i$};
+            \node[below] at (180:1.2) {$w[i-2]$};
+            \node[above] at (0:0) {$w[i-1]$};
+            \node[right] at (-120:1.2) {$w[i]$};
 
-            \node[left] at (120:1.2) {A};
-            \node[left] at (60:1.2) {B};
-            \node[left] at (0:1.2) {C};
+            \node[left] at (120:1.2) {$n_3$};
+            \node[left] at (60:1.2) {$n_2$};
+            \node[left] at (0:1.2) {$n_1$};
 
@@
 
-              \node[right] at (180:1.2) {e};
-              \node[right] at (-120:1.2) {f};
-              \node[right] at (-60:1.2) {g};
+              \node[right] at (180:1.2) {$n_4$};
+              \node[right] at (-120:1.2) {$n_5$};
+              \node[right] at (-60:1.2) {$n_6$};
             \end{scope}
@@
 \subsubsection{Case of $S[i-2..i] = bbt$}
-Let us consider number of consumed by $w_{i-2}$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
+Let us consider number of consumed by $w[i-2]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
 
 \begin{itemize}
-\item{$w_{i-2}$ consumes one binding}\\
-  In this situation, $w_{i-2}$ supplies one active binding whereas $w_{i}$ consumes this binding. In addtion, $w_{i-1}$ has to bound to one of A, B, C.
+\item{$w[i-2]$ consumes one binding}\\
+  In this situation, $w[i-2]$ supplies one active binding whereas $w[i]$ consumes this binding. In addition, $w[i-1]$ has to bound to one of $n_1, n_2, n_3$.
   Thus, in this cases consume some binding capabilities.
 
-\item{$w_{i-2}$ consumes two bindings}\\
-  In this case, $w_{i-2}$ already consumes two binding. $w_{i-1}$ has to be bound. $w_i$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
+\item{$w[i-2]$ consumes two bindings}\\
+  In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
 \end{itemize}
@@
 
-          \node[below] at (180:1.2) {$t_1$};
-          \node[right] at (0:0) {$t_2$};
-          \node[left] at (-120:1.2) {$t_3$};
+          \node[below] at (180:1.2) {$w[i-2]$};
+          \node[above] at (0:0) {$w[i-1]$};
+          \node[left] at (-120:1.2) {$w[i]$};
 
-          \node[right] at (120:1.2) {A};
-          \node[right] at (60:1.2) {B};
-          \node[right] at (0:1.2) {C};
+          \node[right] at (120:1.2) {$n_3$};
+          \node[right] at (60:1.2) {$n_2$};
+          \node[right] at (0:1.2) {$n_1$};
 
@@
 Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities.
-Therefore formula \ref{TTT_only_hold} hold.
+Therefore formula \ref{TTT_only_bond} hold.
 

### 2018-11-18 ttt.tex
11/18 en

@@
 
+\DeclareMathOperator*{\argmin}{arg\,min}
+
+\usepackage{wasysym}
+
 \begin{document}
@@
 
-\section{Infiniteness of delay-1, arity-2 unary deterministic oritatami system}
+\section{Infiniteness of delay-1 unary deterministic oritatami system}
 
@@
 If a bead is stabilized through a tunnel section, then it can provide some bonds.
-Let us consider on bonds of $C_i$.
+Let us consider bonds of $C_i$.
 $C_i$ is represented $C = (W,P,H)$ where $|W| = i + n$ $C_i$ contains $\alpha \cdot (i + n) - 2|H|$ bonds because $C_i$ consists of $i + n$ beads and a bead has just $\alpha$ bonds and then $2 |H|$ of the those bonds are already used.
@@
 Number of $binding\ capabilities$ does not contain that case so that it is at most $\alpha \cdot (i + n) - 2|H|$.
+
+\begin{definition}[binding capability]
+We say that $p$ is $reachable$ if there exists directed path $P^\prime$ from $q$ to $p$ such that the path of $P^\prime$ does not cross the path of $P$ where $q_0$ is a bead which is latest stabilized, and $q_m$ is a reachable point.
+Let $B_i$ be $( \{ (h, i) | {}^\forall h < i \} \cup \{ (i, j) | {}^\forall j > i \}) \cap H$.
+Moreover, let $R_i$ be a set of inside $\hexagon_{w_i}^1$ that are free and reachable.
+ We represent the number of binding capabilities of a conformation $C_j$ as $\#bc(C_j)$. $\#bc(C_j)$ is defined by $\sum^{j}_{k=-n+1} \min \{ |B_k|, |R_k|  \}$.
+\end{definition}
 
@@
 \begin{theorem}[Tunnel Troll Theorem]
-  Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$.
-If there is a part of transcript $w[i..j+1] = bttt...tb$, then $C_i$'s binding capabilities is more than $C_j$'s binding capabilities.
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there is a part of transcript $w[i..j+1] = bttt...tb$, then $\#bc(C_i)$ is more than $\#bc(C_j)$.
 \end{theorem}
@@
 
-\subsection{Proof of Tunnel Troll Theorem}
+\proof%{Proof of Tunnel Troll Theorem}
 Assume $\Xi$ is deterministic.
@@
 
+\begin{proof}[lemma \ref{TTT_neighbor_lemma}]
 A bead in transcript needs predecessor and successor except first and last beads.
@@
 Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
+\end{proof}
 
-\paragraph{}
 Let us consider tunnel sections only tunnel A and B.
@@
 See Fig.\ref{TTT_case_of_o}.
-$v_{i-1}$ consumes some binding capabilities because $S[i-1]$ is $b$.
-If the number of $v_{i-1}$'s bindings is one binding, then $v_{i+1}$ has to be bound except A or B so that $v_{i+1}$ must consumes two bindings except the case of A and B are occupied and $v_i$ consumes at least one binding.
-If A and B are occupied, then $v_{i-1}$'s binginds are inactive that is $v_{i-1}$ consumes two binding capabilities.
+$w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$.
+If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding.
+If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s binginds are inactive that is $w[i-1]$ consumes two binding capabilities.
 Therefore, this case consumes binding capabilities.
-If $v_{i-1}$ dose Not have any bindings, then $v_{i-1}$ already consumes two bindings.
-In addition, $v_i$ and $v_{i+1}$ consume at least one binding.
+If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings.
+In addition, $w[i]$ and $w[i+1]$ consume at least one binding.
 Therefore this case consumes binding capabilities.
@@
 
-      \node[below] at (-120:1.2) {$v_{i-2}$};
-      \node[above] at (0:0) {$v_{i-1}$};
-      \node[above] at (0:1.2) {$v_i$};
-      \node[left, shift=(0:1.2)] at (40:1.2) {$v_{i+1}$};
+      \node[below] at (-120:1.2) {$w[i-2]$};
+      \node[above] at (0:0) {$w[i-1]$};
+      \node[below] at (0:1.2) {$w[i]$};
+      \node[right, shift=(0:1.2)] at (40:1.2) {$w[i+1]$};
 
-      \node[right] at (60:1.2) {A};
-      \node[right] at (-60:1.2) {B};
+      \node[right] at (60:1.2) {$n_1$};
+      \node[right] at (-60:1.2) {$n_2$};
 

### 2018-11-19 paper.tex
adding d=1,d=3

@@
 \section{Case of $\delta = 1$}
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \fill (0,0) circle[radius = 0.1];
+      \fill (1.5,0) circle[radius = 0.1];
+      \fill (3,0) circle[radius = 0.1];
+      \fill (4.5,0) circle[radius = 0.1];
+      \fill (6,0) circle[radius = 0.1];
+
+      \draw[dashed] (0,0)--(1.5,0);
+      \draw[dashed] (1.5,0)--(3,0);
+      \draw[dashed] (3,0)--(4.5,0);
+      \draw[dashed] (4.5,0)--(6,0);
+      \draw[->] (0,0)--(60:1.3);
+      \draw[->] (1.5,0)--++(60:1.3);
+      \draw[->] (3,0)--++(60:1.3);
+      \draw[->] (4.5,0)--++(60:1.3);
+
+      \begin{scope}[shift=(60:1.5)]
+        \fill (0,0) circle[radius = 0.1];
+        \fill (1.5,0) circle[radius = 0.1];
+        \fill (3,0) circle[radius = 0.1];
+        \fill (4.5,0) circle[radius = 0.1];
+        \draw[dashed] (0,0)--(1.5,0);
+        \draw[dashed] (1.5,0)--(3,0);
+        \draw[dashed] (3,0)--(4.5,0);
+        \draw[->] (0,0)--(-60:1.3);
+        \draw[->] (1.5,0)--++(-60:1.3);
+        \draw[->] (3,0)--++(-60:1.3);
+        \draw[->] (4.5,0)--++(-60:1.3);
+      \end{scope}
+
+    \end{tikzpicture}
+    \caption{zig-zag conformation}
+    \label{TTT_zigzag}
+  \end{center}
+\end{figure}
+
+\subsection{Introduction}
+
+In this section, we consider on finiteness of structures produced deterministically at delay 1.
+In result, cases of arity 1 and 3 can only yield finite structures which is size of $\mathcal{O} (n)$, and cases of arity 4 and more can only yield finite structures which is size of $mathcal{O} (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
+
+%In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 2 deterministically and moreover that the only infinite conformations which its oritatami system can yield is only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
+
+Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
+%Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
+For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$ that is foldable by $\Xi$. Hence $C_0 = \sigma$.
+
+Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$.
+The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1.
+There are just two ways to get stabilized at delay 1.
+One way is to be bound to another bead.
+The other way is through a $tunnel\ section$.
+A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
+Accordingly, how they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
+
+Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
+We call such a bead $p$ as $inside\ of\ a\ tunnel$ and such beads $p^\prime$ as $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel.
+If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor.
+In this way, $w[i]$ can get stabilized without being bound.
+
+If a bead is stabilized through a tunnel section, then it can provide some bonds.
+Let us consider bonds of $C_i$.
+$C_i$ is represented $C = (W,P,H)$ where $|W| = i + n$ $C_i$ contains $\alpha \cdot (i + n) - 2|H|$ bonds because $C_i$ consists of $i + n$ beads and a bead has just $\alpha$ bonds and then $2 |H|$ of the those bonds are already used.
+However, even if a bead has an available bond, $w[j]$ $(j > i)$ might not be able to use this bond because the bond has possibility that it is blocked by transcripts $w[i+1..j-1]$.
+Number of $binding\ capabilities$ does not contain that case so that it is at most $\alpha \cdot (i + n) - 2|H|$.
+
+\begin{definition}[binding capability]
+We say that $p$ is $reachable$ if there exists directed path $P^\prime$ from $q$ to $p$ such that the path of $P^\prime$ does not cross the path of $P$ where $q_0$ is a bead which is latest stabilized, and $q_m$ is a reachable point.
+Let $B_i$ be $( \{ (h, i) | {}^\forall h < i \} \cup \{ (i, j) | {}^\forall j > i \}) \cap H$.
+Moreover, let $R_i$ be a set of inside $\hexagon_{w_i}^1$ that are free and reachable.
+ We represent the number of binding capabilities of a conformation $C_j$ as $\#bc(C_j)$. $\#bc(C_j)$ is defined by $\sum^{j}_{k=-n+1} \min \{ |B_k|, |R_k|  \}$.
+\end{definition}
+
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \fill (0:0) circle [radius=0.05];
+      \fill (0:1.2) circle [radius=0.05];
+      \fill (180:1.2) circle [radius=0.05];
+      \node[above] at (0:1.2) { $p^\prime$ };
+      \node[above] at (0:0) { $p$ };
+      \node[above] at (180:1.2) { $p^\prime$ };
+
+      \fill (60 : 1.2) circle [radius=0.1];
+      \fill (-60 : 1.2) circle [radius=0.1];
+      \fill (120 : 1.2) circle [radius=0.1];
+      \fill (-120 : 1.2) circle [radius=0.1];
+      \node[above] at (60 :1.2) { $a_{j_1}$ };
+      \node[above] at (-60 :1.2) { $a_{j_2}$ };
+      \node[above] at (120 :1.2) { $a_{j_3}$ };
+      \node[above] at (-120 :1.2) { $a_{j_4}$ };
+
+      \begin{scope}[shift=(0:5)]
+        \fill (0:0) circle [radius=0.1];
+        \fill (0:1.2) circle [radius=0.05];
+        \fill (180:1.2) circle [radius=0.1];
+        \node[above] at (180:1.2) { $a_{i-2}$ };
+        \node[above] at (0:0) { $a_{i-1}$ };
+        \draw[->] (180:1.1) -- (180:0.1);
+
+        \fill (60 : 1.2) circle [radius=0.1];
+        \fill (-60 : 1.2) circle [radius=0.1];
+        \fill (120 : 1.2) circle [radius=0.1];
+        \fill (-120 : 1.2) circle [radius=0.1];
+        \node[above] at (60 :1.2) { $a_{j_1}$ };
+        \node[above] at (-60 :1.2) { $a_{j_2}$ };
+        \node[above] at (120 :1.2) { $a_{j_3}$ };
+        \node[above] at (-120 :1.2) { $a_{j_4}$ };
+      \end{scope}
+      \begin{scope}[shift=(0:10)]
+        \fill (0:0) circle [radius=0.1];
+        \fill (0:1.2) circle [radius=0.1];
+        \fill (180:1.2) circle [radius=0.1];
+        \node[above] at (180:1.2) { $a_{i-2}$ };
+        \node[above] at (0:0) { $a_{i-1}$ };
+        \node[above] at (0:1.2) { $a_i$ };
+        \draw[->] (180:1.1) -- (180:0.1);
+        \draw[->] (0:0.1) -- (0:1.1);
+
+        \fill (60 : 1.2) circle [radius=0.1];
+        \fill (-60 : 1.2) circle [radius=0.1];
+        \fill (120 : 1.2) circle [radius=0.1];
+        \fill (-120 : 1.2) circle [radius=0.1];
+        \node[above] at (60 :1.2) { $a_{j_1}$ };
+        \node[above] at (-60 :1.2) { $a_{j_2}$ };
+        \node[above] at (120 :1.2) { $a_{j_3}$ };
+        \node[above] at (-120 :1.2) { $a_{j_4}$ };
+      \end{scope}
+    \end{tikzpicture} 
+    \caption{Through a tunnel section}
+    \label{TTT_tunnel_intro}
+  \end{center}
+\end{figure}
+
+\begin{theorem}[Tunnel Troll Theorem]
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there is a part of transcript $w[i..j+1] = bttt...tb$, then $\#bc(C_i)$ is more than $\#bc(C_j)$.
+\end{theorem}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\proof%{Proof of Tunnel Troll Theorem}
+Assume $\Xi$ is deterministic.
+%How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
+Each of beads in transcript are bound either inside of tunnel or outside (Fig.
+\ref{TTT_position}).
+If a bead is stabilized at inside of tunnel, then its successor is already decided the position either inside of a tunnel or outside.
+Moreover, If a bead is stabilized at outside of a tunnel, then its position is an entrance of a tunnel or otherwise.
+
+Tunnel sections have three possible shape with considering symmetry such as straight, acute turn and obtuse turn (Fig.
+\ref{TTT_tunnel}).
+%Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Fig.
+\ref{TTT_enterpoint}).
+
+Let us consider each of cases of tunnel A, B, and C. Accordingly, We use lemma \ref{TTT_neighbor_lemma}
+
+\begin{lemma}
+\label{TTT_neighbor_lemma}
+If a bead does not have any bond, then neighbors of it must be occupied by $\alpha + 2$ beads at $\delta = 1$ and unary except first and last beads.
+\end{lemma}
+
+\begin{proof}[lemma \ref{TTT_neighbor_lemma}]
+A bead in transcript needs predecessor and successor except first and last beads.
+If the bead does not have ant bond, then it use hand with $\alpha$ neighbors.
+Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
+\end{proof}
+
+Let us consider tunnel sections only tunnel A and B.
+See Fig.
+\ref{TTT_position}.
+From appendix (Entrance of Tunnel A, B and Exit of Tunnel), we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successor\ in\ outside$.
+
+%The sequence $S$ can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+ \cup bt^+bt^+$.
+
+Next, we consider on tunnel C section.
+If $w[i]$ is stabilized by tunnel C and $S[i+1]$ is $t$, then $w[i+1]$ is stabilized by tunnel A or B because if $w[i+1]$ is stabilized by tunnel C, then $C_{i+1}$ is a terminal.
+Hence, tunnel C section is divided cases such as Figure \ref{TTT_tunnelC_graph}.
+Cases of $S[i...] = bt^l (l \geq 2)$ are already considered (Upper).
+According to appendix (Tunnel C), cases of $S[i..i+2] = btb$ also consume some binding capabilities (Lower).
+
+Thus, if a bead is stabilized through a tunnel section, then it consume some binging capabilities.
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{ccc}
+
+      \begin{minipage}{0.3\hsize}
+        \begin{tikzpicture}
+          \begin{scope}[xshift=2cm, yshift=2cm]
+            \fill(0,0) circle [radius=0.05];
+            \node[above] at (180:1.2) {$p^\prime$};
+            \node[above] at (0:1.2) {$p^\prime$};
+
+            \foreach \theta in {0,180}{
+              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {60,-60,120,-120}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+            }
+          \end{scope}
+
+          \node at (2,0) {Tunnel A};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.3\hsize}
+        \begin{tikzpicture}
+
+          \begin{scope}[xshift=2cm, yshift=2cm]
+            \fill(0,0) circle [radius=0.05];
+            \node[above] at (180:1.2) {$p^\prime$};
+            \node[above] at (-60:1.2) {$p^\prime$};
+
+            \foreach \theta in {-60,180}{
+              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {0,60,120,-120}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+            }
+          \end{scope}
+
+          \node at (2,0) {Tunnel B};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.3\hsize}
+        \begin{tikzpicture}
+
+          \begin{scope}[xshift=2cm, yshift=2cm]
+            \fill(0,0) circle [radius=0.05];
+            \node[above] at (180:1.2) {$p^\prime$};
+            \node[above] at (-1200:1.2) {$p^\prime$};
+
+            \foreach \theta in {-120,180}{
+              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {0,60,-60,120}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+            }
+          \end{scope}
+
+          \node at (2,0) {Tunnel C};
+        \end{tikzpicture}
+      \end{minipage}
+
+    \end{tabular}
+    \caption{All possible tunnel sections: straight, acute turn, and obtuse turn}
+    \label{TTT_tunnel}
+  \end{center}
+\end{figure}
+
+%\begin{figure}
+%  \begin{center}
+%    \begin{tabular}{cc}
+%      
+%      \begin{minipage}{0.2\hsize}
+%      \centering
+%        \begin{tikzpicture}
+%
+%          \begin{scope}[xshift=1cm, yshift=2cm]
+%            \fill(0,0) circle [radius=0.1];
+%            \node[above] at (180:1.2) {$p^\prime$};
+%            
+%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
+%            
+%            
+%            \foreach \theta in {120,-120}{
+%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+%            }
+%
+%            \draw[->] (-1.1,0) -- (-0.1,0);
+%          \end{scope}
+%
+%          \node at (0.25,0) {Tunnel A,B};
+%        \end{tikzpicture}
+%      \end{minipage}
+%
+%      \begin{minipage}{0.2\hsize}
+%      \centering
+%        \begin{tikzpicture}
+%
+%          \begin{scope}[xshift=1cm, yshift=2cm]
+%            \fill(0,0) circle [radius=0.1];
+%            \node[above] at (180:1.2) {$p^\prime$};
+%
+%            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
+%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
+%            
+%            
+%            \foreach \theta in {120}{
+%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+%            }
+%
+%            \draw[->] (-1.1,0) -- (-0.1,0);
+%          \end{scope}
+%
+%          \node at (0.25,0) {Tunnel C};
+%        \end{tikzpicture}
+%      \end{minipage}
+%
+%    \end{tabular}
+%    \caption{Entrance of a tunnel}
+%    \label{TTT_enterpoint}
+%  \end{center}
+%\end{figure}
+
+%\begin{figure}
+%  \begin{center}
+%    \begin{tikzpicture}
+%      \draw[thick]
+%      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
+%      \node at(2.5,1) {Outside};
+%      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
+%      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
+%
+%      
+%      
+%      \draw[thick]
+%      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
+%      \node at(10.5,1) {Inside of a tunnel};
+%      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
+%      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
+%
+%      \draw[->]
+%      (outside) edge [bend left] node[left] {$b$} (enter)
+%                edge [loop left] node[left] {$b$} (outside)
+%      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
+%                edge [bend left] node[above] {$b$} (next-outside)
+%                edge [bend left] node[right] {$b$}  (outside)
+%      (next-tunnel) edge         node[right] {$t$} (next-outside)
+%                edge [loop right]node[below] {$t$}    (next-tunnel)
+%      (next-outside) edge[bend left] node[above] {$t$}  (outside)
+%                edge [bend left]     node[above] {$t$}(enter)
+%      ;
+%      
+%    \end{tikzpicture}
+%    \caption{Cases on position of a bead}
+%    \label{TTT_position1}
+%  \end{center}
+%\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \draw[thick, gray]
+      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
+      \node at(2,1) {Outside};
+      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
+      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
+
+      \draw[thick, gray]
+      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
+      \node at(9,1) {Inside of a tunnel};
+      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
+      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
+
+      \draw[->]
+      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
+                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
+      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
+                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
+                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
+      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
+                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
+      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
+                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
+      ;
+
+    \end{tikzpicture}
+    \caption{Increment on Tunnel A,B}
+    \label{TTT_position}
+  \end{center}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
+      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
+      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
+      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
+      \draw[->] (outside1)--(enter1);
+      \draw[->] (enter1)  --(inside1);
+      \draw[->] (inside1) --(exit1);
+
+      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
+      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
+      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
+      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
+      \draw[->] (outside2)--(enter2);
+      \draw[->] (enter2)  --(inside2);
+      \draw[->] (inside2) --(exit2);
+
+      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
+      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
+      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
+      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
+      \draw[->] (outside3)--(enter3);
+      \draw[->] (enter3)  --(inside3);
+      \draw[->] (inside3) --(exit3);
+
+      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
+      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
+      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
+      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
+      \draw[->] (outside4)--(enter4);
+      \draw[->] (enter4)  --(inside4);
+      \draw[->] (inside4) --(exit4);
+    \end{tikzpicture}
+    \caption{Case of Tunnel C}
+    \label{TTT_tunnelC_graph}
+  \end{center}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%/////////////////////////////////////////////////
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Appendix of Tunnel Troll Theorem}
+\subsubsection{Entrance of TunnelA,B}
+
+Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
+Any cases in $\delta = 1, \alpha = 2$ consume some binding capabilities into the follows.
+
+\begin{itemize}
+\item{Case of $t_0$}\\
+  Let us consider points of $n_3,n_4$ either occupied or not.
+A point $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
+If $n_3$ is free, then $p^\prime$ has to be bound to a bead except $n_1$ due to deterministically stabilize.
+In this situation, at least three neighbors of $n_1$ are free that is $n_1$ leave at least one bond from lemma \ref{TTT_neighbor_lemma}.
+Hence, $p^\prime$ must be bound to $n_1$.
+Thus, a case of $t_0$ consumes two binding capabilities and it does not supply any binding capabilities.
+
+\item{Case of $t_{\pm 60}$}\\
+  In this case, a point $n_4$ or $n_5$ is free, too.
+If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$.
+If $n_5$ is occupied, then $n_4$ is free.
+This time, $n_2$ has some binding capabilities so $p^\prime$ has to be bound to $n_2$.
+
+  In this situation, $p^\prime$ is able to supply a binding capability.
+if this capability is active, $p^\prime$ bind a bead into $n_4$ or $n_5$.
+However, $n_2$ and $n_3$ are exist in back bone.
+According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive.
+Thus, a case of $t_{\pm 60}$ consumes some binding capabilities.
+
+\item{Case of $t_{\pm 120}$}\\
+  Binding capabilities that $p^\prime$ supply are inactive according to Jordan curve theorem on $n_1$ and $n_2$.
+Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
+Thus, a case of $t_{\pm 120}$ consumes some binging capabilities.
+
+\end{itemize}
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{ccc}
+
+      \begin{minipage}{0.3\hsize}
+      \centering
+        \begin{tikzpicture}
+	 \draw[->,white] (120:1.1)--(120:0.1);%for adjustment
+
+            \fill(0,0) circle [radius=0.1];
+            \node[below] at (0,0) {$p^\prime$};
+
+            \foreach \theta in {0}{
+              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
+            }
+
+            \foreach \theta in {60,-60,180}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+            }
+
+            \foreach \theta in {120,-120}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
+            }
+
+            \draw[->] (180:1.1)--(180:0.1);
+            \draw[->] (0:0.1)--(0:1.1);
+
+            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
+
+          \node at (0,-2) {$t_{0}$};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.3\hsize}
+      \centering
+        \begin{tikzpicture}
+
+            \fill(0,0) circle [radius=0.1];
+            \node[below] at (0,0) {$p^\prime$};
+
+            \foreach \theta in {0}{
+              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
+            }
+
+            \foreach \theta in {60,-60,120}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+            }
+
+            \foreach \theta in {180,-120}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
+            }
+
+            \draw[->] (120:1.1)--(120:0.1);
+            \draw[->] (0:0.1)--(0:1.1);
+
+            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
+
+          \node at (0,-2) {$t_{\pm 60}$};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.3\hsize}
+      \centering
+        \begin{tikzpicture}
+            \fill(0,0) circle [radius=0.1];
+            \node[above] at (0,0) {$p^\prime$};
+
+            \foreach \theta in {0}{
+              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
+            }
+
+            \foreach \theta in {60,-60}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+            }
+
+            \foreach \theta in {180,-120,120}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
+            }
+
+            \draw[->] (60:1.1)--(60:0.1);
+            \draw[->] (0:0.1)--(0:1.1);
+
+            \node[transform canvas={shift=(0:1.2)},below] {$n_0$};
+            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
+
+          \node at (0,-2) {$t_{\pm 120}$};
+        \end{tikzpicture}
+      \end{minipage}
+
+    \end{tabular}
+    \caption{Direction into a entrance}
+    \label{TTT_tunnel_direction}
+  \end{center}
+\end{figure}
+
+\subsubsection{Exit of Tunnel}
+
+Fig.\ref{TTT_tunnel_exit} exhibits all the two kings of exit of tunnel. 
+At least one of point $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
+
+\paragraph{$\delta = 1, \alpha = 2$}
+ Any cases of $\delta = 1, \alpha = 2$ supply at most $a$ binding capabilities into follows where $a$ is number of predecessor of $p^\prime$ consumes binging capabilities.
+
+\begin{itemize}
+\item{Case of $n_1$ and $n_2$ are free}\\
+  This case can be regarded same situation as entrance.
+See Fig.\ref{TTT_tunnel_exit} (Left).
+Predecessor $n_5$ has to be bound $n_4$ and $n_5$ because each of $n_3$ and $n_4$ leave binding capabilities.
+Hence, at least $a=2$.
+This time, $\alpha = 2$ that is this case supply at most only $a$ binding capabilities.
+
+\item{Case of $c$ is occupied}\\
+  See Fig.\ref{TTT_tunnel_exit} (Right).
+If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$.
+Hence, at least $a=1$.
+This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied a successor of $p^\prime$.
+Therefore, this case supply at most only $a=1$ active binding capability.
+
+\end{itemize}
+
+\paragraph{$\delta = 1, \alpha \geq 3$}
+Any cases of $\delta = 1, \alpha \geq 3$ consume some binding capabilities into follows.
+
+\begin{itemize}
+\item{Case of $n_1$ and $n_2$ are free}\\
+  In $\alpha \geq 3$, if three neighbors of a bead leave, then it can supply two binding capabilities.
+Therefore Predecessor $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$, too.
+In this case, at least consumes four bindings and supplies at most two bindings.
+Thus, it consumes some binding capabilities, totally.
+
+\item{Case of $c$ is occupied}\\
+  In this case, $n_4$ leave at least two bindings and $n_3$, $n_1$ also leave at least one binding.
+Therefore $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$ also has to be bound $n_1$ and $n_4$.
+In this case, at least consumes four bindings and supplies at most one binding.
+Thus, it consumes some binding capabilities, totally.
+\end{itemize}
+
+\begin{figure}
+  \centering
+    \begin{tabular}{cc}
+
+      \begin{minipage}{0.48\linewidth}
+      \centering
+        \begin{tikzpicture}
+
+            \fill(0,0) circle [radius=0.1];
+            \node[above] at (0,0) {$p^\prime$};
+
+            \foreach \theta in {120,-120,180}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+            }
+
+            \foreach \theta in {0,60,-60}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
+            }
+
+            \draw[->] (180:1.1)--(180:0.1);
+
+            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
+
+          \node at (0,-2) {Point $n_1$ and $n_2$ are free};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.48\linewidth}
+      \centering
+        \begin{tikzpicture}
+
+            \fill(0,0) circle [radius=0.1];
+            \node[above] at (0,0) {$p^\prime$};
+
+            \foreach \theta in {120,-120,180,60}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+            }
+
+            \foreach \theta in {0,-60}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
+            }
+
+            \draw[->] (180:1.1)--(180:0.1);
+
+            \node[transform canvas={shift=(0:1.2)},right] {$n_0$};
+            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
+
+          \node at (0,-2) {Point $n_1$ is occupied};
+        \end{tikzpicture}
+      \end{minipage}
+
+    \end{tabular}
+    \caption{Exit of Tunnel}
+    \label{TTT_tunnel_exit}
+\end{figure}
+
+\subsubsection{Tunnel C}
+
+Assume $w[i]$ is a bead which stabilized by tunnel C. Let us consider kinds of stabilization $S[i-2..i] = tbt$ or $S[i-2..i] = bbt$ except cases of $w[i]$ is inside of tunnel A, B.
+
+\subsubsection{Case of $S[i-2..i] = tbt$}
+Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
+
+\begin{itemize}
+\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
+  In this figure, Bead $n_4$ has at least one binding so that $w[i-2]$ has to bound $n_4$.
+Moreover, $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
+On the other hand, $w[i]$ can supply two bindings but free neighbors of $w[i]$ are two points.
+One of them is occupied by a successor.
+Therefore $w[i]$ can only bind one of $n_5, n_6$ that is $w[i]$ supplies at most one binding.
+Thus, this case consumes some binding capabilities.
+
+\item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
+  This cases are divided on number of capabilities that $w[i-2]$ consumes.
+  \begin{itemize}
+  \item[-]{$w[i]$ does not consume any bindings}\\
+    $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
+$w[i]$ has to be bound to $w[i-2]$ because $w[i-2]$ has bindings.
+This time, let us consider either $n_4$ is occupied or not.
+If $n_4$ is occupied, then $w[i-2]$ has no active bindings that is this situation consumes some binding capabilities.
+If $n_4$ is free and $w[i+1]$ is stabilized in $n_4$, then $w[i-2]$ has to bind $w[i+1]$.
+Therefore, In this case, stabilization of $w[i-2..i+1]$ consumes some bindings.
+If $n_4$ is free and $w[i+1]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[i+1]$.
+Therefore, in this case consumes some bindings.
+Thus in this cases consume some binding capabilities.
+
+  \item[-]{$w_i$ consumes one binding}\\
+    In this case, $w_{i-1}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[i-2]$ and $w[i]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
+  \item[-]{$w_i$ consumes two bindings}\\
+    In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies two bindings. Thus, in this cases consume some binding capabilities.
+
+  \end{itemize}
+\end{itemize}
+\begin{figure}
+  \centering
+    \begin{tabular}{cc}
+
+      \begin{minipage}{0.48\hsize}
+      \centering
+        \begin{tikzpicture}
+
+          \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
+          \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
+
+          \foreach \theta in {60,-60,120,-120,180}{
+            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+          }
+
+          \fill(0:1.2) circle [radius=0.1];
+          \draw[->] (0:0.1)--(0:1.1);
+
+          \node[left] at (-60:1.2) {$n_4$};
+
+          \begin{scope}[shift=(0:2.4)]
+            \fill(0,0) circle [radius=0.1];
+
+            \foreach \theta in {120,60,-60,0}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+            }
+
+            \draw[->] (180:1.1)--(180:0.1);
+            \draw[->] (-120:0.1)--(-120:1.1);
+
+            \node[below] at (180:1.2) {$w[i-2]$};
+            \node[above] at (0:0) {$w[i-1]$};
+            \node[right] at (-120:1.2) {$w[i]$};
+
+            \node[left] at (120:1.2) {$n_3$};
+            \node[left] at (60:1.2) {$n_2$};
+            \node[left] at (0:1.2) {$n_1$};
+
+            \begin{scope}[shift=(-120:1.2)]
+              \draw(0,0) circle [radius=0.1];
+              \foreach \theta in {-120,-60}{
+                \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
+              }
+
+              \node[right] at (-120:1.2) {$n_5$};
+              \node[right] at (-60:1.2) {$n_6$};
+            \end{scope}
+
+          \end{scope}
+
+          \node at (1.2,-2.5) {Pattern 1};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.48\hsize}
+      \centering
+        \begin{tikzpicture}
+
+          \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
+          \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
+
+          \foreach \theta in {60,0,120,-120,180}{
+            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+          }
+
+          \draw[->] (-60:0.1)--(-60:1.1);
+
+          \begin{scope}[shift=(-60:1.2),shift=(0:1.2)]
+            \fill(0,0) circle [radius=0.1];
+            \fill(180:1.2) circle [radius=0.1];
+
+            \foreach \theta in {120,60,0,-60}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+            }
+
+            \draw[->] (180:1.1)--(180:0.1);
+            \draw[->] (-120:0.1)--(-120:1.1);
+
+            \node[below] at (180:1.2) {$w[i-2]$};
+            \node[above] at (0:0) {$w[i-1]$};
+            \node[right] at (-120:1.2) {$w[i]$};
+
+            \node[left] at (120:1.2) {$n_3$};
+            \node[left] at (60:1.2) {$n_2$};
+            \node[left] at (0:1.2) {$n_1$};
+
+            \begin{scope}[shift=(-120:1.2)]
+              \draw(0,0) circle [radius=0.1];
+              \foreach \theta in {180,-120,-60}{
+                \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
+              }
+
+              \node[right] at (180:1.2) {$n_4$};
+              \node[right] at (-120:1.2) {$n_5$};
+              \node[right] at (-60:1.2) {$n_6$};
+            \end{scope}
+
+          \end{scope}
+
+          \node at (1.25,-4) {Pattern 2};
+        \end{tikzpicture}
+      \end{minipage}
+
+    \end{tabular}
+    \caption{Case of $S[i-2..i] = tbt$}
+    \label{TTT_tunnelC_enter_usingTunnel}
+\end{figure}
+
+\subsubsection{Case of $S[i-2..i] = bbt$}
+Let us consider number of consumed by $w[i-2]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
+
+\begin{itemize}
+\item{$w[i-2]$ consumes one binding}\\
+  In this situation, $w[i-2]$ supplies one active binding whereas $w[i]$ consumes this binding. In addition, $w[i-1]$ has to bound to one of $n_1, n_2, n_3$.
+  Thus, in this cases consume some binding capabilities.
+
+\item{$w[i-2]$ consumes two bindings}\\
+  In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
+\end{itemize}
+
+\begin{figure}
+  \begin{center}
+        \begin{tikzpicture}
+        \draw[->,white] (-70:0.1) -- (-70:3);
+          \foreach \theta in {60,-60,120,0}{
+            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
+            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+          }
+
+          \fill(180:1.2) circle [radius=0.1];
+          \fill(0:0) circle [radius=0.1];
+
+          \draw[transform canvas={shift=(180:1.2)}] (105:1.1) edge[bend right] (105:0.1);
+          \draw[->] (180:1.1) -- (180:0.1);
+          \draw[->] (-120:0.1) -- (-120:1.1);
+
+          \node[below] at (180:1.2) {$w[i-2]$};
+          \node[above] at (0:0) {$w[i-1]$};
+          \node[left] at (-120:1.2) {$w[i]$};
+
+          \node[right] at (120:1.2) {$n_3$};
+          \node[right] at (60:1.2) {$n_2$};
+          \node[right] at (0:1.2) {$n_1$};
+
+          \begin{scope}[shift=(-120:1.2)]
+            \draw(0,0) circle [radius=0.1];
+            \foreach \theta in {-120,-60,180}{
+              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
+            }
+
+          \end{scope}
+        \end{tikzpicture}
+    \caption{Case of $S[i-2..i] = bbt$}
+    \label{TTT_tunnelC_enter_usingBond}
+  \end{center}
+\end{figure}
+
+By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
+If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$.
+Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities.
+Therefore formula \ref{TTT_only_bond} hold.
+
+\begin{eqnarray}
+  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
+  \label{TTT_only_bond}
+\end{eqnarray}
+
+Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
+
+Let us consider the case of $v_k$ is $o$.
+See Fig.\ref{TTT_case_of_o}.
+$w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$.
+If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding.
+If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s binginds are inactive that is $w[i-1]$ consumes two binding capabilities.
+Therefore, this case consumes binding capabilities.
+If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings.
+In addition, $w[i]$ and $w[i+1]$ consume at least one binding.
+Therefore this case consumes binding capabilities.
+Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.
+
+\begin{eqnarray}
+  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
+  \label{TTT_only_a}
+\end{eqnarray}
+
+\begin{eqnarray}
+  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
+  \label{TTT_structure}
+\end{eqnarray}
+
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+
+      \draw[transform canvas={shift=(-120:1.2)}](-0.1,-0.1)--(0.1,0.1);
+      \draw[transform canvas={shift=(-120:1.2)}](0.1,-0.1)--(-0.1,0.1);
+
+      \fill(0:0) circle [radius=0.1];
+      \fill(0:1.5) circle [radius=0.1];
+      \fill[shift=(0:1.2)](40:1.2) circle [radius=0.1];
+
+      \draw[->] (-120:1.1) edge[bend left] (-120:0.1);
+      \draw[->] (0:0) -- (0:1.3);
+      \draw[->,transform canvas={shift=(0:1.2)}] (0:0.1) edge[bend right] (40:1.3);
+
+      \draw [shift=(60:1.2)] (-0.1,-0.1) rectangle (0.1,0.1);
+      \draw [shift=(-60:1.2)] (-0.1,-0.1) rectangle (0.1,0.1);
+
+      \node[below] at (-120:1.2) {$w[i-2]$};
+      \node[above] at (0:0) {$w[i-1]$};
+      \node[below] at (0:1.2) {$w[i]$};
+      \node[right, shift=(0:1.2)] at (40:1.2) {$w[i+1]$};
+
+      \node[right] at (60:1.2) {$n_1$};
+      \node[right] at (-60:1.2) {$n_2$};
+
+    \end{tikzpicture}
+    \caption{Case of $S[i]$}
+    \label{TTT_case_of_o}
+  \end{center}
+\end{figure}
 
@@
 
+\subsection{In the case of $\delta = 3$}
+
+We discuss when the length of seed is $n$.
+If the length of seed is $n$, the seed will be in an equilateral hexagon with a radius of $n$ when it is given.
+We will begin our disscussion by considering the moment when a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$.
+Let us assume that a fixed bead on a side of an equilateral hexagon with a radius of $n$ is able to make a hydrogen bond.
+If it is able to make only two hydrogen bonds, it will be nondeterministic because there are two possibilities that it makes two structures in Fig.5.
+Therefore, it needs to make three hydrogen bonds to determine the only structure.\\
+
+\begin{figure}
+  \begin{center}
+  \begin{tabular}{cc}
+    \begin{tikzpicture}
+      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
+      \fill (2.0, 0.0) node [right] {$n$};
+      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
+      \fill (2.0, 0.866) node [right] {$n+1$};
+      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
+      \fill (2.0, 1.732) node [right] {$n+2$};
+      \fill (0,0) circle [radius = 0.05];
+      \begin{scope}[shift = (0 : 0.0)]
+        \foreach \theta in {60, 120}{
+          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw (0 : 0.0) -- (60 : 1.0);
+        \draw (60 : 1.0) -- (120 : 1.0);
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (60 : 1.0)]
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (120 : 1.0)]
+        \foreach \theta in {60}{
+        \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw (0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+    \end{tikzpicture}
+
+    \begin{tikzpicture}
+      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
+      \fill (2.0, 0.0) node [right] {$n$};
+      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
+      \fill (2.0, 0.866) node [right] {$n+1$};
+      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
+      \fill (2.0, 1.732) node [right] {$n+2$};
+      \fill (0,0) circle [radius = 0.05];
+      \begin{scope}[shift = (0 : 0.0)]
+        \foreach \theta in {60, 120}{
+          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
+        \draw (60 : 1.0) -- (120 : 1.0);
+        \draw (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (60 : 1.0)]
+        \draw (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (120 : 1.0)]
+        \foreach \theta in {60}{
+        \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw [dotted](0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+    \end{tikzpicture}
+    \end{tabular}
+    \caption{}
+  \end{center}
+\end{figure}
+
+There are the two cases in which a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$ and it makes three hydrogen bonds in Fig.6.
+If it makes three hydrogen bonds once such as Fig6., it will make three hyrogen bonds forever to be deterministic.
+This becomes nondeterministic finally, such as in Fig.7., when it reaches a corner of an equilateral hexagon.
+Thus, the fixed bead on a side of an equilateral hexagon with a radius of $n$ has to make a hydrogen bond with a bead in an equilateral hexagon.
+
+\begin{figure}
+  \begin{center}
+  \begin{tabular}{cc}
+    \begin{tikzpicture}
+      \draw [dashed] (-0.5, 0.0) -- (3.5, 0.0);
+      \fill (3.5, 0.0) node [right] {$n$};
+      \draw [dashed] (-0.5, 0.866) -- (3.5, 0.866);
+      \fill (3.5, 0.866) node [right] {$n+1$};
+      \fill (0,0) circle [radius = 0.05];
+      \begin{scope}[shift = (0 : 0.0)]
+        \foreach \theta in {0, 60}{
+          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw (0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 2.0)]
+        \fill (0,0) circle [radius = 0.05];
+        \foreach \theta in {0, 60, 120}{
+          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (60 : 1.0)]
+          \draw (0 : 0.0) -- (0 : 2.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 1.0)]
+          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 3.0)]
+          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+    \end{tikzpicture}
+
+    \begin{tikzpicture}
+      \draw [dashed] (-1.5, 0.0) -- (2.5, 0.0);
+      \fill (2.5, 0.0) node [right] {$n$};
+      \draw [dashed] (-1.5, 0.866) -- (2.5, 0.866);
+      \fill (2.5, 0.866) node [right] {$n+1$};
+      \fill (0,0) circle [radius = 0.05];
+      \begin{scope}[shift = (0 : 0.0)]
+        \foreach \theta in {0, 60, 120, 180}{
+          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 2.0)]
+        \fill (0,0) circle [radius = 0.05];
+        \foreach \theta in {120}{
+          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (120 : 1.0)]
+          \draw (0 : 0.0) -- (0 : 2.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 1.0)]
+          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (180 : 1.0)]
+          \draw [dotted] (0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+    \end{tikzpicture}
+    \end{tabular}
+    \caption{}
+  \end{center}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \begin{tabular}{cc}
+    \begin{tikzpicture}
+      \draw [dashed] (-0.5, 0.0) -- (2.0, 0.0);
+      \fill (3.0, 0.0) node [right] {$n$};
+      \draw [dashed] (-0.5, 0.866) -- (2.5, 0.866);
+      \fill (3.0, 0.866) node [right] {$n+1$};
+      \draw [dashed] (-0.5, 1.732) -- (3.0, 1.732);
+      \fill (3.0, 1.732) node [right] {$n+2$};
+      \fill (60 : 1.0) circle [radius = 0.05];
+      \draw (-0.1,-0.1) -- (0.1,0.1);
+      \draw (0.1,-0.1) -- (-0.1,0.1);
+      \begin{scope}[shift = (120 : 1.0)]
+        \draw (-0.1,-0.1) -- (0.1,0.1);
+        \draw (0.1,-0.1) -- (-0.1,0.1);
+      \end{scope}
+      \begin{scope}[shift = (120 : 1.0)]
+        \draw [dotted] (0 : 0.0) -- (300 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (60 : 1.0)]
+        \draw (0.0, 0.0) -- (2.0, 0.0);
+        \fill (2.0, 0.0) circle [radius = 0.05];
+      \end{scope}
+      \begin{scope}[shift = (0 : 2.0)]
+        \draw [dashed] (0 : 0.0) -- (300 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 1.0)]
+      \fill (0.0, 0.0) circle [radius = 0.05];
+        \foreach \theta in {0, 60}{
+          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 2.0)]
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (60 : 1.0)]
+        \begin{scope}[shift = (120 : 1.0)]
+          \fill (0.0, 0.0) circle [radius = 0.05];
+          \draw (0 : 0.0) -- (240 : 1.0);
+          \draw (0 : 0.0) -- (300 : 1.0);
+        \end{scope}
+      \end{scope}
+    \end{tikzpicture}
+
+    \begin{tikzpicture}
+      \draw [dashed] (-0.5, 0.0) -- (2.0, 0.0);
+      \fill (3.0, 0.0) node [right] {$n$};
+      \draw [dashed] (-0.5, 0.866) -- (2.5, 0.866);
+      \fill (3.0, 0.866) node [right] {$n+1$};
+      \draw (-0.1,-0.1) -- (0.1,0.1);
+      \draw (0.1,-0.1) -- (-0.1,0.1);
+      \fill (60 : 1.0) circle [radius = 0.05];
+      \begin{scope}[shift = (120 : 1.0)]
+        \draw (-0.1,-0.1) -- (0.1,0.1);
+        \draw (0.1,-0.1) -- (-0.1,0.1);
+      \end{scope}
+      \begin{scope}[shift = (120 : 1.0)]
+        \draw [dotted] (0 : 0.0) -- (300 : 1.0);
+        \draw (0.0, 0.0) -- (3.0, 0.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 2.0)]
+        \draw [dashed] (0 : 0.0) -- (300 : 1.0);
+        \fill (60 : 1.0) circle [radius = 0.05];
+      \end{scope}
+      \begin{scope}[shift = (0 : 1.0)]
+        \fill (0.0, 0.0) circle [radius = 0.05];
+        \foreach \theta in {0, 60}{
+          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 2.0)]
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+    \end{tikzpicture}
+    \end{tabular}
+    \caption{}
+  \end{center}
+\end{figure}
+
+Then, we will discuss the moment after the first the is fixed on a side of an equilateral hexagon with a radius of $n+1$.
+Let us assume that the bead is able to make a hydrogen bond.
+If it is able to make only two hydrogen bonds, it will be nondeterministic because there are possibilities that it makes two structures in Fig.8.
+Hence, it needs to make three hydrogen bonds to determine the only structure.
+It needs to be a right or left figure in Fig.9.
+to make three hydrogen bonds.\\
+
+\begin{figure}
+  \begin{center}
+  \begin{tabular}{cc}
+    \begin{tikzpicture}
+        \begin{scope}[shift=(0 : 0.0)]
+          \draw (-0.1,-0.1) -- (0.1,0.1);
+          \draw (0.1,-0.1) -- (-0.1,0.1);
+          \draw (0 : 0.0) -- (60 : 1.0);
+        \end{scope}
+      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
+      \fill (2.0, 0.0) node [right] {$n$};
+      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
+      \fill (2.0, 0.866) node [right] {$n+1$};
+      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
+      \fill (2.0, 1.732) node [right] {$n+2$};
+      \draw [dashed] (-1.0, 2.598) -- (2.0, 2.598);
+      \fill (2.0, 2.598) node [right] {$n+3$};
+      \fill (0,0) circle [radius = 0.05];
+      \begin{scope}[shift = (60 : 2.0)]
+        \fill(0.0, 0.0) circle [radius = 0.05];
+        \foreach \theta in {120, 180, 240}{
+          \fill (0.0, 0.0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+        \draw (0 : 0.0) -- (180 : 1.0);
+        \draw (0 : 0.0) -- (240 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (60 : 1.0)]
+        \begin{scope}[shift = (120 : 1.0)]
+          \draw (0.0, 0.0) -- (60 : 1.0);
+          \draw [dotted] (0.0, 0.0) -- (300 : 1.0);
+        \end{scope}
+      \end{scope}
+    \end{tikzpicture}
+
+    \begin{tikzpicture}
+        \begin{scope}[shift=(0 : 0.0)]
+          \draw (-0.1,-0.1) -- (0.1,0.1);
+          \draw (0.1,-0.1) -- (-0.1,0.1);
+          \draw (0 : 0.0) -- (60 : 1.0);
+        \end{scope}
+      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
+      \fill (2.0, 0.0) node [right] {$n$};
+      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
+      \fill (2.0, 0.866) node [right] {$n+1$};
+      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
+      \fill (2.0, 1.732) node [right] {$n+2$};
+      \draw [dashed] (-1.0, 2.598) -- (2.0, 2.598);
+      \fill (2.0, 2.598) node [right] {$n+3$};
+      \fill (0,0) circle [radius = 0.05];
+      \begin{scope}[shift = (60 : 2.0)]
+        \fill(0.0, 0.0) circle [radius = 0.05];
+        \foreach \theta in {120, 180, 240}{
+          \fill (0.0, 0.0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
+        }
+        \draw (0 : 0.0) -- (120 : 1.0);
+        \draw (0 : 0.0) -- (180 : 1.0);
+        \draw [dotted] (0 : 0.0) -- (240 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (60 : 1.0)]
+        \begin{scope}[shift = (120 : 1.0)]
+          \draw [dotted] (0.0, 0.0) -- (60 : 1.0);
+          \draw (0.0, 0.0) -- (300 : 1.0);
+        \end{scope}
+      \end{scope}
+    \end{tikzpicture}
+    \end{tabular}
+    \caption{}
+  \end{center}
+\end{figure}
+
+ If it makes three hydrogen bonds once such as Fig.9., it will make three hyrogen bonds forever to be deterministic.
+This becomes nondeterministic finally, such as in Fig.7., when it reaches a corner of an equilateral hexagon.
+Therefore, the first fixed bead on a side of an equilateral hexagon with a radius of $n+1$ has to make a hydrogen bond with a molecule on a side of an equilateral hexagon with a radius of $n$.
+
+\begin{figure}
+  \begin{center}
+  \begin{tabular}{cc}
+    \begin{tikzpicture}
+      \begin{scope}[shift=(0 : 0.0)]
+        \draw (-0.1,-0.1) -- (0.1,0.1);
+        \draw (0.1,-0.1) -- (-0.1,0.1);
+        \draw (0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+      \draw [dashed] (-0.5, 0.0) -- (4.5, 0.0);
+      \fill (4.5, 0.0) node [right] {$n$};
+      \draw [dashed] (-0.5, 0.866) -- (4.5, 0.866);
+      \fill (4.5, 0.866) node [right] {$n+1$};
+      \fill (2.0, 0.0) circle [radius = 0.05];
+      \fill (3.0, 0.0) circle [radius = 0.05];
+      \fill (4.0, 0.0) circle [radius = 0.05];
+      \begin{scope}[shift = (60 : 1.0)]
+        \fill (0.0, 0.0) circle [radius = 0.05];
+        \fill (1.0, 0.0) circle [radius = 0.05];
+        \fill (2.0, 0.0) circle [radius = 0.05];
+        \fill (3.0, 0.0) circle [radius = 0.05];
+        \draw (0.0, 0.0) -- (3.0, 0.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 2.0)]
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 3.0)]
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : 4.0)]
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+    \end{tikzpicture}
+
+    \begin{tikzpicture}
+      \begin{scope}[shift=(0 : 0.0)]
+        \draw (-0.1,-0.1) -- (0.1,0.1);
+        \draw (0.1,-0.1) -- (-0.1,0.1);
+        \draw (0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+      \draw [dashed] (-3.5, 0.0) -- (1.0, 0.0);
+      \fill (1.0, 0.0) node [right] {$n$};
+      \draw [dashed] (-3.5, 0.866) -- (1.0, 0.866);
+      \fill (1.0, 0.866) node [right] {$n+1$};
+      \fill (-1.0, 0.0) circle [radius = 0.05];
+      \fill (-2.0, 0.0) circle [radius = 0.05];
+      \fill (-3.0, 0.0) circle [radius = 0.05];
+      \begin{scope}[shift = (60 : 1.0)]
+        \fill (0.0, 0.0) circle [radius = 0.05];
+        \fill (-1.0, 0.0) circle [radius = 0.05];
+        \fill (-2.0, 0.0) circle [radius = 0.05];
+        \fill (-3.0, 0.0) circle [radius = 0.05];
+        \draw (0.0, 0.0) -- (-3.0, 0.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : -1.0)]
+        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : -2.0)]
+        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+      \begin{scope}[shift = (0 : -3.0)]
+        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+    \end{tikzpicture}
+    \end{tabular}
+    \caption{}
+  \end{center}
+\end{figure}
+
+Accordingly, it is Fig.10. when a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$.
+
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
+      \fill (2.0, 0.0) node [right] {$n$};
+      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
+      \fill (2.0, 0.866) node [right] {$n+1$};
+      \begin{scope}[shift=(0 : 0.0)]
+        \draw (-0.1,-0.1) -- (0.1,0.1);
+        \draw (0.1,-0.1) -- (-0.1,0.1);
+        \draw (0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+      \begin{scope}[shift=(60 : 1.0)]
+        \draw (-0.1,-0.1) -- (0.1,0.1);
+        \draw (0.1,-0.1) -- (-0.1,0.1);
+      \end{scope}
+      \begin{scope}[shift=(0 : 1.0)]
+        \draw (-0.1,-0.1) -- (0.1,0.1);
+        \draw (0.1,-0.1) -- (-0.1,0.1);
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+    \end{tikzpicture}
+    \caption{}
+  \end{center}
+\end{figure}
+
+It has to be a right or left figure in Fig.6.
+when the first bead fixed on a side of an equilateral hexagon with a radius of $n+1$ make a hydrogen bond with a bead on a side of an equilateral hexagon with a radius of $n$.
+Fig.6.
+becomes nondeterministic finally, such as in Fig.7., when it reaches a corner of an equilateral hexagon.
+It is clear that all beads on a side of an equilateral hexagon with a radius of $n+1$ has to make a hydrogen bond with a bead on a side of an equilateral hexagon with a radius of $n$.
+It is impossible to fix molecules on a side of an equilateral hexagon with a radius of $n+2$ and determine the only structure when there are only beads which are able to make a hydrogen bond in an equilateral hexagon with a radius of $n$.
+
 \end{document}

### 2018-11-19 paper.tex
update delay 1

@@
 \section{Case of $\delta = 1$}
+
+%//////////////////////////////////////////////////////%
+%//////////////////////////////////////////////////////%
+%Kohei
+%//////////////////////////////////////////////////////%
+%//////////////////////////////////////////////////////%
+
 \begin{figure}
@@
 
-If a bead is stabilized through a tunnel section, then it can provide some bonds.
+%If a bead is stabilized through a tunnel section, then it can provide some bonds.
 Let us consider bonds of $C_i$.
@@
 
+We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$.
+We define $binding\ capability$ with reachable.
+
 \begin{definition}[binding capability]
-We say that $p$ is $reachable$ if there exists directed path $P^\prime$ from $q$ to $p$ such that the path of $P^\prime$ does not cross the path of $P$ where $q_0$ is a bead which is latest stabilized, and $q_m$ is a reachable point.
 Let $B_i$ be $( \{ (h, i) | {}^\forall h < i \} \cup \{ (i, j) | {}^\forall j > i \}) \cap H$.
-Moreover, let $R_i$ be a set of inside $\hexagon_{w_i}^1$ that are free and reachable.
+Moreover, let $R_i$ be a set of neighbors of $w[i]$ that are free and reachable from $C_j$ where $C_j$ is a conformation which stabilized until $w[j]$.
  We represent the number of binding capabilities of a conformation $C_j$ as $\#bc(C_j)$. $\#bc(C_j)$ is defined by $\sum^{j}_{k=-n+1} \min \{ |B_k|, |R_k|  \}$.
@@
 \begin{theorem}[Tunnel Troll Theorem]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there is a part of transcript $w[i..j+1] = bttt...tb$, then $\#bc(C_i)$ is more than $\#bc(C_j)$.
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there are indices $i$ and $j$ such that $S[i..j+1] = bt^{j-i}b$, then $\#bc(C_i)$ > $\#bc(C_j)$.
 \end{theorem}
@@
 
+%end of d = 1
+%//////////////////////////////////////////////////////%
+%//////////////////////////////////////////////////////%
+
 \section{Case of $\delta \geq 2$}

### 2018-11-22 paper.tex
update 11/22 in tokyo

@@
 %//////////////////////////////////////////////////////%
-%//////////////////////////////////////////////////////%
+%//////////////////////////////////////////////////////%l.168 - 1324
 
@@
       \draw[dashed] (4.5,0)--(6,0);
-      \draw[->] (0,0)--(60:1.3);
-      \draw[->] (1.5,0)--++(60:1.3);
-      \draw[->] (3,0)--++(60:1.3);
-      \draw[->] (4.5,0)--++(60:1.3);
+      \draw[->] (0,0)--(60:0.75);
+      \draw[->] (1.5,0)--++(60:0.75);
+      \draw[->] (3,0)--++(60:0.75);
+      \draw[->] (4.5,0)--++(60:0.75);
+      \draw (0,0)--(60:1.5);
+      \draw (1.5,0)--++(60:1.5);
+      \draw (3,0)--++(60:1.5);
+      \draw (4.5,0)--++(60:1.5);
 
@@
         \draw[dashed] (3,0)--(4.5,0);
-        \draw[->] (0,0)--(-60:1.3);
-        \draw[->] (1.5,0)--++(-60:1.3);
-        \draw[->] (3,0)--++(-60:1.3);
-        \draw[->] (4.5,0)--++(-60:1.3);
+        \draw[->] (0,0)--(-60:0.75);
+        \draw[->] (1.5,0)--++(-60:0.75);
+        \draw[->] (3,0)--++(-60:0.75);
+        \draw[->] (4.5,0)--++(-60:0.75);
+
+        \draw (0,0)--(-60:1.5);
+        \draw (1.5,0)--++(-60:1.5);
+        \draw (3,0)--++(-60:1.5);
+        \draw (4.5,0)--++(-60:1.5);
       \end{scope}
@@
     \begin{tikzpicture}
-      \fill (0:0) circle [radius=0.05];
-      \fill (0:1.2) circle [radius=0.05];
-      \fill (180:1.2) circle [radius=0.05];
-      \node[above] at (0:1.2) { $p^\prime$ };
+      \draw (0:0) circle [radius=0.05];
+      \draw (0:1) circle [radius=0.05];
+      \draw (180:1) circle [radius=0.05];
+      \node[above] at (0:1) { $p^\prime$ };
       \node[above] at (0:0) { $p$ };
-      \node[above] at (180:1.2) { $p^\prime$ };
-
-      \fill (60 : 1.2) circle [radius=0.1];
-      \fill (-60 : 1.2) circle [radius=0.1];
-      \fill (120 : 1.2) circle [radius=0.1];
-      \fill (-120 : 1.2) circle [radius=0.1];
-      \node[above] at (60 :1.2) { $a_{j_1}$ };
-      \node[above] at (-60 :1.2) { $a_{j_2}$ };
-      \node[above] at (120 :1.2) { $a_{j_3}$ };
-      \node[above] at (-120 :1.2) { $a_{j_4}$ };
+      \node[above] at (180:1) { $p^\prime$ };
+
+      \fill (60 : 1) circle [radius=0.1];
+      \fill (-60 : 1) circle [radius=0.1];
+      \fill (120 : 1) circle [radius=0.1];
+      \fill (-120 : 1) circle [radius=0.1];
+      \node[above] at (60 :1) { $a_{j_1}$ };
+      \node[above] at (-60 :1) { $a_{j_2}$ };
+      \node[above] at (120 :1) { $a_{j_3}$ };
+      \node[above] at (-120 :1) { $a_{j_4}$ };
 
       \begin{scope}[shift=(0:5)]
-        \fill (0:0) circle [radius=0.1];
-        \fill (0:1.2) circle [radius=0.05];
-        \fill (180:1.2) circle [radius=0.1];
+        \fill[blue] (0:0) circle [radius=0.1];
+        \draw (0:1) circle [radius=0.05];
+        \fill (180:1) circle [radius=0.1];
         \node[above] at (180:1.2) { $a_{i-2}$ };
         \node[above] at (0:0) { $a_{i-1}$ };
-        \draw[->] (180:1.1) -- (180:0.1);
-
-        \fill (60 : 1.2) circle [radius=0.1];
-        \fill (-60 : 1.2) circle [radius=0.1];
-        \fill (120 : 1.2) circle [radius=0.1];
-        \fill (-120 : 1.2) circle [radius=0.1];
-        \node[above] at (60 :1.2) { $a_{j_1}$ };
-        \node[above] at (-60 :1.2) { $a_{j_2}$ };
-        \node[above] at (120 :1.2) { $a_{j_3}$ };
-        \node[above] at (-120 :1.2) { $a_{j_4}$ };
+        \draw[->, blue] (180:0.9) -- (180:0.1);
+
+        \fill (60 : 1) circle [radius=0.1];
+        \fill (-60 : 1) circle [radius=0.1];
+        \fill (120 : 1) circle [radius=0.1];
+        \fill (-120 : 1) circle [radius=0.1];
+        \node[above] at (60 :1) { $a_{j_1}$ };
+        \node[above] at (-60 :1) { $a_{j_2}$ };
+        \node[above] at (120 :1) { $a_{j_3}$ };
+        \node[above] at (-120 :1) { $a_{j_4}$ };
       \end{scope}
@@
         \fill (0:0) circle [radius=0.1];
-        \fill (0:1.2) circle [radius=0.1];
-        \fill (180:1.2) circle [radius=0.1];
-        \node[above] at (180:1.2) { $a_{i-2}$ };
+        \fill[blue] (0:1) circle [radius=0.1];
+        \fill (180:1) circle [radius=0.1];
+        \node[above] at (180:1) { $a_{i-2}$ };
         \node[above] at (0:0) { $a_{i-1}$ };
-        \node[above] at (0:1.2) { $a_i$ };
-        \draw[->] (180:1.1) -- (180:0.1);
-        \draw[->] (0:0.1) -- (0:1.1);
-
-        \fill (60 : 1.2) circle [radius=0.1];
-        \fill (-60 : 1.2) circle [radius=0.1];
-        \fill (120 : 1.2) circle [radius=0.1];
-        \fill (-120 : 1.2) circle [radius=0.1];
-        \node[above] at (60 :1.2) { $a_{j_1}$ };
-        \node[above] at (-60 :1.2) { $a_{j_2}$ };
-        \node[above] at (120 :1.2) { $a_{j_3}$ };
-        \node[above] at (-120 :1.2) { $a_{j_4}$ };
+        \node[above] at (0:1) { $a_i$ };
+        \draw[->] (180:0.9) -- (180:0.1);
+        \draw[->,blue] (0:0.1) -- (0:0.9);
+
+        \fill (60 : 1) circle [radius=0.1];
+        \fill (-60 : 1) circle [radius=0.1];
+        \fill (120 : 1) circle [radius=0.1];
+        \fill (-120 : 1) circle [radius=0.1];
+        \node[above] at (60 :1) { $a_{j_1}$ };
+        \node[above] at (-60 :1) { $a_{j_2}$ };
+        \node[above] at (120 :1) { $a_{j_3}$ };
+        \node[above] at (-120 :1) { $a_{j_4}$ };
       \end{scope}
@@
           \begin{scope}[xshift=2cm, yshift=2cm]
-            \fill(0,0) circle [radius=0.05];
-            \node[above] at (180:1.2) {$p^\prime$};
-            \node[above] at (0:1.2) {$p^\prime$};
+            \draw(0,0) circle [radius=0.05];
+            \node[above] at (180:1) {$p^\prime$};
+            \node[above] at (0:1) {$p^\prime$};
 
             \foreach \theta in {0,180}{
-              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
             }
@@
             \foreach \theta in {60,-60,120,-120}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
             }
@@
           \begin{scope}[xshift=2cm, yshift=2cm]
-            \fill(0,0) circle [radius=0.05];
-            \node[above] at (180:1.2) {$p^\prime$};
-            \node[above] at (-60:1.2) {$p^\prime$};
+            \draw(0,0) circle [radius=0.05];
+            \node[above] at (180:1) {$p^\prime$};
+            \node[above] at (-60:1) {$p^\prime$};
 
             \foreach \theta in {-60,180}{
-              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
             }
@@
             \foreach \theta in {0,60,120,-120}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+ 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
             }
@@
           \begin{scope}[xshift=2cm, yshift=2cm]
-            \fill(0,0) circle [radius=0.05];
-            \node[above] at (180:1.2) {$p^\prime$};
-            \node[above] at (-1200:1.2) {$p^\prime$};
+            \draw(0,0) circle [radius=0.05];
+            \node[above] at (180:1) {$p^\prime$};
+            \node[above] at (-1200:1) {$p^\prime$};
 
             \foreach \theta in {-120,180}{
-              \fill[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.05];
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
             }
@@
             \foreach \theta in {0,60,-60,120}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
             }
@@
         \begin{tikzpicture}
-	 \draw[->,white] (120:1.1)--(120:0.1);%for adjustment
-
-            \fill(0,0) circle [radius=0.1];
+	 \draw[->,white] (120:0.8)--(120:0.1);%for adjustment
+
+            \fill[blue] (0,0) circle [radius=0.05];
             \node[below] at (0,0) {$p^\prime$};
@@
             \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
+              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
             }
@@
             \foreach \theta in {60,-60,180}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
             }
@@
             \foreach \theta in {120,-120}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
-            }
-
-            \draw[->] (180:1.1)--(180:0.1);
-            \draw[->] (0:0.1)--(0:1.1);
-
-            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+            }
+
+            \draw[->, blue] (180:0.9)--(180:0.1);
+            \draw[->, blue] (0:0.1)--(0:0.9);
+
+            \node[transform canvas={shift=(60:1)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
 
@@
 
-            \fill(0,0) circle [radius=0.1];
+            \fill(0,0) circle [radius=0.05];
             \node[below] at (0,0) {$p^\prime$};
@@
             \foreach \theta in {60,-60,120}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
             }
@@
             \foreach \theta in {180,-120}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
-            }
-
-            \draw[->] (120:1.1)--(120:0.1);
-            \draw[->] (0:0.1)--(0:1.1);
-
-            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+            }
+
+            \draw[->, blue] (120:0.9)--(120:0.1);
+            \draw[->, blue] (0:0.1)--(0:0.9);
+
+            \node[transform canvas={shift=(60:1)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1)},left] {$n_5$};
 
@@
         \begin{tikzpicture}
-            \fill(0,0) circle [radius=0.1];
+            \fill[blue](0,0) circle [radius=0.05];
             \node[above] at (0,0) {$p^\prime$};
@@
             \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1.2)}](0,0) circle [radius=0.1];
+              \fill[transform canvas={shift=(\theta:1)}, blue](0,0) circle [radius=0.05];
             }
@@
             \foreach \theta in {60,-60}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
             }
@@
             \foreach \theta in {180,-120,120}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
-            }
-
-            \draw[->] (60:1.1)--(60:0.1);
-            \draw[->] (0:0.1)--(0:1.1);
-
-            \node[transform canvas={shift=(0:1.2)},below] {$n_0$};
-            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+            }
+
+            \draw[->, blue] (60:1.1)--(60:0.1);
+            \draw[->, blue] (0:0.1)--(0:1.1);
+
+            \node[transform canvas={shift=(0:1)},below] {$n_0$};
+            \node[transform canvas={shift=(60:1)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1)},left] {$n_5$};
 
@@
 
-Fig.\ref{TTT_tunnel_exit} exhibits all the two kings of exit of tunnel. 
+Fig.\ref{TTT_tunnel_exit} exhibits all the two kinds of exit of tunnel. 
 At least one of point $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
@@
 
-            \fill(0,0) circle [radius=0.1];
+            \fill[blue](0,0) circle [radius=0.05];
             \node[above] at (0,0) {$p^\prime$};
@@
             \foreach \theta in {120,-120,180}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-            }
-
-            \foreach \theta in {0,60,-60}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
-            }
-
-            \draw[->] (180:1.1)--(180:0.1);
-
-            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+
+            \foreach \theta in {0}{
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+            }
+            \draw (-60:1) circle [radius=0.05];
+            \draw (60:1) circle [radius=0.05];
+
+            \draw[->, blue] (180:0.9)--(180:0.1);
+
+            \node[transform canvas={shift=(60:1)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1)},left] {$n_5$};
 
@@
             \foreach \theta in {120,-120,180,60}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-            }
-
-            \foreach \theta in {0,-60}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
-            }
-
-            \draw[->] (180:1.1)--(180:0.1);
-
-            \node[transform canvas={shift=(0:1.2)},right] {$n_0$};
-            \node[transform canvas={shift=(60:1.2)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1.2)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1.2)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1.2)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1.2)},left] {$n_5$};
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+
+            \foreach \theta in {0}{
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+            }
+            \draw (-60:1) circle [radius=0.05];
+
+            \draw[->, blue] (180:0.9)--(180:0.1);
+
+            \node[transform canvas={shift=(0:1)},right] {$n_0$};
+            \node[transform canvas={shift=(60:1)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1)},left] {$n_5$};
 
@@
 
-          \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
-          \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
+          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];
 
           \foreach \theta in {60,-60,120,-120,180}{
-            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-          }
-
-          \fill(0:1.2) circle [radius=0.1];
-          \draw[->] (0:0.1)--(0:1.1);
-
-          \node[left] at (-60:1.2) {$n_4$};
-
-          \begin{scope}[shift=(0:2.4)]
-            \fill(0,0) circle [radius=0.1];
+            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+          }
+
+          \fill[blue](0:1) circle [radius=0.05];
+          \draw[->, blue] (0:0.1)--(0:0.9);
+
+          \node[below] at (-60:1) {$n_4$};
+
+          \begin{scope}[shift=(0:2)]
+            \fill[blue](0,0) circle [radius=0.05];
 
             \foreach \theta in {120,60,-60,0}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-            }
-
-            \draw[->] (180:1.1)--(180:0.1);
-            \draw[->] (-120:0.1)--(-120:1.1);
-
-            \node[below] at (180:1.2) {$w[i-2]$};
+             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+
+            \draw[->, blue] (180:0.9)--(180:0.1);
+            \draw[->, blue] (-120:0.1)--(-120:0.9);
+
+            \node[below] at (180:1) {$w[i-2]$};
             \node[above] at (0:0) {$w[i-1]$};
-            \node[right] at (-120:1.2) {$w[i]$};
-
-            \node[left] at (120:1.2) {$n_3$};
-            \node[left] at (60:1.2) {$n_2$};
-            \node[left] at (0:1.2) {$n_1$};
-
-            \begin{scope}[shift=(-120:1.2)]
-              \draw(0,0) circle [radius=0.1];
+            \node[right] at (-120:1) {$w[i]$};
+
+            \node[above] at (120:1) {$n_3$};
+            \node[above] at (60:1) {$n_2$};
+            \node[right] at (0:1) {$n_1$};
+
+            \begin{scope}[shift=(-120:1)]
+              \fill[blue](0,0) circle [radius=0.05];
               \foreach \theta in {-120,-60}{
-                \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
-              }
-
-              \node[right] at (-120:1.2) {$n_5$};
-              \node[right] at (-60:1.2) {$n_6$};
+                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+              }
+
+              \node[right] at (-120:1) {$n_5$};
+              \node[right] at (-60:1) {$n_6$};
             \end{scope}
@@
 
-          \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
-          \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
+          \fill(0,0) circle [radius=0.1];
 
           \foreach \theta in {60,0,120,-120,180}{
-            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-          }
-
-          \draw[->] (-60:0.1)--(-60:1.1);
-
-          \begin{scope}[shift=(-60:1.2),shift=(0:1.2)]
-            \fill(0,0) circle [radius=0.1];
-            \fill(180:1.2) circle [radius=0.1];
+            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+          }
+
+          \draw[->, blue] (-60:0.1)--(-60:0.9);
+
+          \begin{scope}[shift=(-60:1),shift=(0:1)]
+            \fill[blue](0,0) circle [radius=0.05];
+            \fill[blue](180:1) circle [radius=0.05];
 
             \foreach \theta in {120,60,0,-60}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-            }
-
-            \draw[->] (180:1.1)--(180:0.1);
-            \draw[->] (-120:0.1)--(-120:1.1);
-
-            \node[below] at (180:1.2) {$w[i-2]$};
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+
+            \draw[->, blue] (180:0.9)--(180:0.1);
+            \draw[->, blue] (-120:0.1)--(-120:0.9);
+
+            \node[below] at (180:1) {$w[i-2]$};
             \node[above] at (0:0) {$w[i-1]$};
-            \node[right] at (-120:1.2) {$w[i]$};
-
-            \node[left] at (120:1.2) {$n_3$};
-            \node[left] at (60:1.2) {$n_2$};
-            \node[left] at (0:1.2) {$n_1$};
-
-            \begin{scope}[shift=(-120:1.2)]
-              \draw(0,0) circle [radius=0.1];
+            \node[right] at (-120:1) {$w[i]$};
+
+            \node[above right] at (120:1) {$n_3$};
+            \node[right] at (60:1) {$n_2$};
+            \node[right] at (0:1) {$n_1$};
+
+            \begin{scope}[shift=(-120:1)]
+              \fill(0,0) circle [radius=0.05];
               \foreach \theta in {180,-120,-60}{
-                \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
-              }
-
-              \node[right] at (180:1.2) {$n_4$};
-              \node[right] at (-120:1.2) {$n_5$};
-              \node[right] at (-60:1.2) {$n_6$};
+                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+              }
+
+              \node[right] at (180:1) {$n_4$};
+              \node[right] at (-120:1) {$n_5$};
+              \node[right] at (-60:1) {$n_6$};
             \end{scope}
@@
           \foreach \theta in {60,-60,120,0}{
-            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-          }
-
-          \fill(180:1.2) circle [radius=0.1];
-          \fill(0:0) circle [radius=0.1];
-
-          \draw[transform canvas={shift=(180:1.2)}] (105:1.1) edge[bend right] (105:0.1);
-          \draw[->] (180:1.1) -- (180:0.1);
-          \draw[->] (-120:0.1) -- (-120:1.1);
-
-          \node[below] at (180:1.2) {$w[i-2]$};
+            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+          }
+
+          \fill[blue](180:1) circle [radius=0.05];
+          \fill[blue](0:0) circle [radius=0.05];
+
+          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
+          \draw[->, blue] (180:0.9) -- (180:0.1);
+          \draw[->, blue] (-120:0.1) -- (-120:0.9);
+
+          \node[below left] at (180:1) {$w[i-2]$};
           \node[above] at (0:0) {$w[i-1]$};
-          \node[left] at (-120:1.2) {$w[i]$};
-
-          \node[right] at (120:1.2) {$n_3$};
-          \node[right] at (60:1.2) {$n_2$};
-          \node[right] at (0:1.2) {$n_1$};
-
-          \begin{scope}[shift=(-120:1.2)]
-            \draw(0,0) circle [radius=0.1];
+          \node[below] at (-120:1) {$w[i]$};
+
+          \node[right] at (120:1) {$n_3$};
+          \node[right] at (60:1) {$n_2$};
+          \node[right] at (0:1) {$n_1$};
+
+          \begin{scope}[shift=(-120:1)]
+            \fill[blue](0,0) circle [radius=0.05];
             \foreach \theta in {-120,-60,180}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
             }
@@
 If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding.
-If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s binginds are inactive that is $w[i-1]$ consumes two binding capabilities.
+If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive that is $w[i-1]$ consumes two binding capabilities.
 Therefore, this case consumes binding capabilities.
@@
 
-      \draw[transform canvas={shift=(-120:1.2)}](-0.1,-0.1)--(0.1,0.1);
-      \draw[transform canvas={shift=(-120:1.2)}](0.1,-0.1)--(-0.1,0.1);
-
-      \fill(0:0) circle [radius=0.1];
-      \fill(0:1.5) circle [radius=0.1];
-      \fill[shift=(0:1.2)](40:1.2) circle [radius=0.1];
-
-      \draw[->] (-120:1.1) edge[bend left] (-120:0.1);
-      \draw[->] (0:0) -- (0:1.3);
-      \draw[->,transform canvas={shift=(0:1.2)}] (0:0.1) edge[bend right] (40:1.3);
-
-      \draw [shift=(60:1.2)] (-0.1,-0.1) rectangle (0.1,0.1);
-      \draw [shift=(-60:1.2)] (-0.1,-0.1) rectangle (0.1,0.1);
-
-      \node[below] at (-120:1.2) {$w[i-2]$};
+      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
+
+      \fill[blue](0:0) circle [radius=0.05];
+      \fill[blue](0:1) circle [radius=0.05];
+      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
+
+      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
+      \draw[->, blue] (0:0.1) -- (0:0.9);
+      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
+
+      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
+      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
+
+      \node[below] at (-120:1) {$w[i-2]$};
       \node[above] at (0:0) {$w[i-1]$};
-      \node[below] at (0:1.2) {$w[i]$};
-      \node[right, shift=(0:1.2)] at (40:1.2) {$w[i+1]$};
-
-      \node[right] at (60:1.2) {$n_1$};
-      \node[right] at (-60:1.2) {$n_2$};
+      \node[below] at (0:1) {$w[i]$};
+      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
+
+      \node[above] at (60:1) {$n_1$};
+      \node[below] at (-60:1) {$n_2$};
 
@@
 
+\subsubsection{$\alpha = 3$}
+
+\begin{theorem}[$\delta = 1, \alpha = 3$]
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only a finite structure whose size is $\mathcal{O}(n)$.
+\end{theorem}
+
+\begin{lemma}
+\label{TTT_a3_2b_lemma}
+ Let $p$ be a point whose neighbors is occupied at least two point.
+If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
+\end{lemma}
+
+\begin{proof}[proof of lemma]
+Assume the transcript is stabilized until $w[i-1]$.
+One of neighbors of $p$ is not $w[i-1]$ where this bead regards $n_1$.
+If $w[i-1]$ include neighbors of $p$ and $w[i]$ is stabilized at another point of $p$ with one bond.
+Then, any neighbors do not have bond without $w[i-1]$.
+Neighbors of $n_1$ have to be occupied at least five according to lemma \ref{TTT_neighbor_lemma} and two of them include neighbors of $p$ where each of them regards $n_2, n_3$.
+In the same way, five neighbors of $n_2$ and $n_3$ are occupied and each of one of them includes neighbors of $p$ where they regard $n_4, n_5$.
+one of $n_5$'s neighbors includes neighbors of $p$ where it regards $n_6$.
+Then, any neighbors of $p$ are occupied.
+That is if some neighbors of $p$ are free, then there exists a bead which has bonds in neighbors.
+\end{proof}
+
+\begin{proof}
+Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
+Let us assume $w[i]$ is able to be stabilized with using one hand. Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$. Then, $w[i]$ can be also stabilized at $n_3$.
+
+\begin{paragraph}{Case of straight}
+\begin{itemize}
+\item[-] Case of $n_3$ is free\\
+According to assumption, $w[i]$ uses only one hand.
+Therefore, any neighbors of $n_3$ are occupied according to the lemma\ref{TTT_a3_2b_lemma}.
+$n_3$ and the point which is stabilized $w[i]$ are free so that $n_1$ has some bond by lemma\ref{TTT_neighbor_lemma}.
+Accordingly, this situation is non-deterministic.
+Thus, $n_3$ and $n_4$ have to be occupied because of symmetry.
+
+\item[-] Otherwise\\
+Because of  $S[i] = b$, at least one of $n_1$ and $n_2$ have to be free.
+Let us regard that $n_1$ is free.
+Neighbors of $n_1$ have to be occupied and at least two neighbors of $n_{-1}$ have to be free for $n_1$ and $w[i]$.
+According to lemma\ref{TTT_neighbor_lemma}, $n_{-1}$ have some hand.
+Therefore $w[i]$ can be also stabilized $n_1$ that is this situation is non-deterministic.
+Thus, one of $n_3$ and $n_4$ has to be free.
+\end{itemize}
+
+Therefore, this case is false.
+\end{paragraph}
+
+\begin{paragraph}{Case of obtuse}
+\begin{itemize}
+\item[-] Case of $n_3$ is free\\
+Any neighbors of $n_3$ have to be occupied but the point which is stabilized $w[i]$ is free. Thus $n_3$ has to be occupied.
+\item[-] Case of $n_4$ is free\\
+%n4??????????lemma2??n2???????lemma???n0??????????????w[i]???????????????????????bead?????????????1?????
+%??n0?????????????n3???????????lemma1??n-3????????n-3???????????n-2??????????n-1???????????????w[i]???????????????????w[i]????????????
+%??n3?????????????n0????????????lemma1??n-1???????????n-2?n-3???????w[i]?????????????
+%???n0 n3???beead???????????n0 n3 ????????????lemma1??n-1 n-3????????n-1,n-3????????????n-3???????????
+%???n-4????????????in order to provide inifinite structures?
+\item[-] Case of $n_2$ is free\\
+Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied.
+Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_2$ has to be occupied.
+\item[-] Case of $n_0$ is free\\
+Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied.
+Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_0$ has to be occupied.
+\end{itemize}
+
+Therefore, any situations contradict $S[i] = b$.
+
+\end{paragraph}
+
+\begin{paragraph}{Case of acute}
+\begin{itemize}
+\item[-] Case of $n_4$ is free\\
+$n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some hands according to lemma\ref{TTT_neighbor_lemma}.
+However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
+\item[-] Case of $n_2$ is free\\
+According to lemma\ref{TTT_a3_2b_lemma}, $n_0$ has to be occupied. $n_1$ has to be also occupied because of lemma\ref{TTT_neighbor_lemma}.
+We consider this case just like case of obtuse and that $n_4$ is free.
+Then if $w[i-2]$ binds $w[i]$, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
+If $n_1$ binds $w[i]$, this case is same.
+Also if $n_1$ and $w[i-2]$ do not have any hand, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
+Therefore, $w[i+1]$ cannot be provided.
+\item[-] Case of $n_0$ is free\\
+Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied.
+Any neighbors of $n_{1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_0$ has to be occupied.
+\item[-] Case of $n_1$ is free\\
+Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied.
+Any neighbors of $n_{-1}$ except $n_1$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_1$ has to be occupied.
+\end{itemize}
+
+Therefore, any situations contradict $S[i] = b$.
+\end{paragraph}\\
+
+Hence, assumption that w[i] is able to be stabilized with using one hand is false.
+Therefore, when w[i] is stabilized, w[i] uses at least two hands.
+\end{proof}
+
+\begin{figure}
+  \begin{center}
+  \begin{tabular}{c c c}
+ \begin{minipage}{0.3\hsize}
+ \centering
+    \begin{tikzpicture}
+
+      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \fill[blue](0:1) circle [radius=0.05];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+      \draw[->, blue] (0:0.1) -- (0:0.9);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (0:1) {$w_{[i]}$};
+
+	\foreach \theta in {60,-60,120,-120}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+	 \draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
+ 	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[below] at (-120:1) {$n_4$};
+	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
+    \end{tikzpicture}
+    \end{minipage}
+
+    \begin{minipage}{0.3\hsize}
+    \centering
+     \begin{tikzpicture}
+
+      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \fill[blue](60:1) circle [radius=0.05];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+      \draw[->, blue] (60:0.1) -- (60:0.9);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (60:1) {$w_{[i]}$};
+
+	\foreach \theta in {0,-60,120,-120}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+	\draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
+	\draw [shift=(60:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+	\draw [shift=(60:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+
+ 	\node[right] at (0:1) {$n_0$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[below] at (-120:1) {$n_4$};
+	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
+	\node[above, shift=(60:1)] at (60:1) {$n_{-2}$};
+	\node[above, shift=(60:1)] at (120:1) {$n_{-3}$};
+    \end{tikzpicture}
+    \end{minipage}
+
+    \begin{minipage}{0.3\hsize}
+        \centering
+     \begin{tikzpicture}
+
+      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \fill[blue](120:1) circle [radius=0.05];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+      \draw[->, blue] (120:0.1) -- (120:0.9);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (120:1) {$w_{[i]}$};
+
+	\foreach \theta in {0,60,-60,-120}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+	\draw [shift=(120:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+	\draw [shift=(120:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+	\draw [shift=(120:1), shift=(180:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+
+ 	\node[right] at (0:1) {$n_0$};
+	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[below] at (-120:1) {$n_4$};
+	\node[above, shift=(120:1)] at (60:1) {$n_{-1}$};
+	\node[above, shift=(120:1)] at (120:1) {$n_{-2}$};
+	\node[above, shift=(120:1)] at (180:1) {$n_{-3}$};
+    \end{tikzpicture}
+    \end{minipage}
+    \end{tabular}
+    \caption{All possible directions of $w[i]$: straight, obtuse, acute.}
+    \label{TTT_a3_w}
+  \end{center}
+\end{figure}
+
+\subsubsection{$\alpha = 4$}
+\begin{theorem}[$\delta = 1, \alpha = 4$]
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only a finite structure whose size is $\mathcal{O}(n^2)$.
+\end{theorem}
+
+\begin{lemma}
+\label{TTT_a4_2b_lemma}
+Any beads which are already stabilized by some bonds use at least two bonds.
+\end{lemma}
+
+\begin{proof}[proof of lemma]
+Let us consider when $w[i]$ is stabilized by only one bond.
+See Fig.\ref{TTT_a4_lemma_fig}.
+According to lemma\ref{TTT_neighbor_lemma}, if $n_3$ is free, $w[i-2]$ has some hands.
+Thus, $n_4$ has to be occupied in order to stabilize deterministically.
+Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$.
+$n_1$ has some hands because $n_3$ is free.
+Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands.
+It contradict assumption.
+\end{proof}
+
+\begin{proof}
+According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds.
+Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized.
+See Fig.\ref{TTT_a4_first}.
+any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$.
+At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind.
+In this case, a point which is able to put a bead is only $n_2$.
+Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$.
+Hence oritatami system can yield only a finite structure whose size is $\mathcal{O}(n^2)$ in $\delta =1, \alpha = 4$.
+%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
+\end{proof}
+
+\begin{figure}
+ \centering
+    \begin{tikzpicture}
+	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (0:1) {$n_0$};
+
+	\foreach \theta in {0,60,-60,120,-120}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+ 	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[below] at (-120:1) {$n_4$};
+    \end{tikzpicture}
+    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
+    \label{TTT_a4_lemma_fig}
+\end{figure}
+
+\begin{figure}
+ \centering
+    \begin{tikzpicture}
+	\fill[shift=(-120:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0), blue] (0,0) circle [radius=0.05];
+
+      \draw[dashed] (180:2) -- (0:2);
+      \draw[->, blue] (-120:0.9) -- (-120:0.1);
+
+	\node[below] at (-120:1) {$w_{[i-1]}$};
+	\node[above] at (180:0) {$w_{[i]}$};
+	\node[above] at (0:1) {$n_0$};
+
+	\foreach \theta in {0,60,-60,120,180}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+
+ 	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[above] at (180:1) {$n_5$};
+
+	\node at (0:2.5) {$n+1$};
+    \end{tikzpicture}
+    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
+    \label{TTT_a4_first}
+\end{figure}
+
 %end of d = 1
-%//////////////////////////////////////////////////////%
+%//////////////////////////////////////////////////////% l.168 - 1324
 %//////////////////////////////////////////////////////%

### 2018-11-22 ttt.tex
update 11/22 in tokyo

@@
 
-          \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
-          \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
+          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];
 
           \foreach \theta in {60,-60,120,-120,180}{
-            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-          }
-
-          \fill(0:1.2) circle [radius=0.1];
-          \draw[->] (0:0.1)--(0:1.1);
-
-          \node[left] at (-60:1.2) {$n_4$};
-
-          \begin{scope}[shift=(0:2.4)]
+            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+          }
+
+          \fill[blue](0:1) circle [radius=0.05];
+          \draw[->, blue] (0:0.1)--(0:0.9);
+
+          \node[below] at (-60:1) {$n_4$};
+
+          \begin{scope}[shift=(0:2)]
+            \fill[blue](0,0) circle [radius=0.05];
+
+            \foreach \theta in {120,60,-60,0}{
+             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+
+            \draw[->, blue] (180:0.9)--(180:0.1);
+            \draw[->, blue] (-120:0.1)--(-120:0.9);
+
+            \node[below] at (180:1) {$w[i-2]$};
+            \node[above] at (0:0) {$w[i-1]$};
+            \node[right] at (-120:1) {$w[i]$};
+
+            \node[above] at (120:1) {$n_3$};
+            \node[above] at (60:1) {$n_2$};
+            \node[right] at (0:1) {$n_1$};
+
+            \begin{scope}[shift=(-120:1)]
+              \fill[blue](0,0) circle [radius=0.05];
+              \foreach \theta in {-120,-60}{
+                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+              }
+
+              \node[right] at (-120:1) {$n_5$};
+              \node[right] at (-60:1) {$n_6$};
+            \end{scope}
+
+          \end{scope}
+
+          \node at (1.2,-2.5) {Pattern 1};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.48\hsize}
+      \centering
+        \begin{tikzpicture}
+
           \fill(0,0) circle [radius=0.1];
 
-            \foreach \theta in {120,60,-60,0}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-            }
-
-            \draw[->] (180:1.1)--(180:0.1);
-            \draw[->] (-120:0.1)--(-120:1.1);
-
-            \node[below] at (180:1.2) {$w[i-2]$};
+          \foreach \theta in {60,0,120,-120,180}{
+            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+          }
+
+          \draw[->, blue] (-60:0.1)--(-60:0.9);
+
+          \begin{scope}[shift=(-60:1),shift=(0:1)]
+            \fill[blue](0,0) circle [radius=0.05];
+            \fill[blue](180:1) circle [radius=0.05];
+
+            \foreach \theta in {120,60,0,-60}{
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+
+            \draw[->, blue] (180:0.9)--(180:0.1);
+            \draw[->, blue] (-120:0.1)--(-120:0.9);
+
+            \node[below] at (180:1) {$w[i-2]$};
             \node[above] at (0:0) {$w[i-1]$};
-            \node[right] at (-120:1.2) {$w[i]$};
-
-            \node[left] at (120:1.2) {$n_3$};
-            \node[left] at (60:1.2) {$n_2$};
-            \node[left] at (0:1.2) {$n_1$};
-
-            \begin{scope}[shift=(-120:1.2)]
-              \draw(0,0) circle [radius=0.1];
-              \foreach \theta in {-120,-60}{
-                \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
-              }
-
-              \node[right] at (-120:1.2) {$n_5$};
-              \node[right] at (-60:1.2) {$n_6$};
-            \end{scope}
-
-          \end{scope}
-
-          \node at (1.2,-2.5) {Pattern 1};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.48\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \draw[transform canvas={shift=(0:0)}](-0.1,-0.1)--(0.1,0.1);
-          \draw[transform canvas={shift=(0:0)}](0.1,-0.1)--(-0.1,0.1);
-
-          \foreach \theta in {60,0,120,-120,180}{
-            \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-            \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-          }
-
-          \draw[->] (-60:0.1)--(-60:1.1);
-
-          \begin{scope}[shift=(-60:1.2),shift=(0:1.2)]
-            \fill(0,0) circle [radius=0.1];
-            \fill(180:1.2) circle [radius=0.1];
-
-            \foreach \theta in {120,60,0,-60}{
-              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-            }
-
-            \draw[->] (180:1.1)--(180:0.1);
-            \draw[->] (-120:0.1)--(-120:1.1);
-
-            \node[below] at (180:1.2) {$w[i-2]$};
-            \node[above] at (0:0) {$w[i-1]$};
-            \node[right] at (-120:1.2) {$w[i]$};
-
-            \node[left] at (120:1.2) {$n_3$};
-            \node[left] at (60:1.2) {$n_2$};
-            \node[left] at (0:1.2) {$n_1$};
-
-            \begin{scope}[shift=(-120:1.2)]
-              \draw(0,0) circle [radius=0.1];
+            \node[right] at (-120:1) {$w[i]$};
+
+            \node[above right] at (120:1) {$n_3$};
+            \node[right] at (60:1) {$n_2$};
+            \node[right] at (0:1) {$n_1$};
+
+            \begin{scope}[shift=(-120:1)]
+              \fill(0,0) circle [radius=0.05];
               \foreach \theta in {180,-120,-60}{
-                \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1) rectangle (0.1,0.1);
-              }
-
-              \node[right] at (180:1.2) {$n_4$};
-              \node[right] at (-120:1.2) {$n_5$};
-              \node[right] at (-60:1.2) {$n_6$};
+                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+              }
+
+              \node[right] at (180:1) {$n_4$};
+              \node[right] at (-120:1) {$n_5$};
+              \node[right] at (-60:1) {$n_6$};
             \end{scope}
@@
 
+\subsubsection{$\alpha = 3$}
+
+\begin{theorem}[$\delta = 1, \alpha = 3$]
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only a finite structure whose size is $\mathcal{O}(n)$.
+\end{theorem}
+
+\begin{lemma}
+\label{TTT_a3_2b_lemma}
+ Let $p$ be a point whose neighbors is occupied at least two point.
+If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
+\end{lemma}
+
+\begin{proof}[proof of lemma]
+Assume the transcript is stabilized until $w[i-1]$.
+One of neighbors of $p$ is not $w[i-1]$ where this bead regards $n_1$.
+If $w[i-1]$ include neighbors of $p$ and $w[i]$ is stabilized at another point of $p$ with one bond.
+Then, any neighbors do not have bond without $w[i-1]$.
+Neighbors of $n_1$ have to be occupied at least five according to lemma \ref{TTT_neighbor_lemma} and two of them include neighbors of $p$ where each of them regards $n_2, n_3$.
+In the same way, five neighbors of $n_2$ and $n_3$ are occupied and each of one of them includes neighbors of $p$ where they regard $n_4, n_5$.
+one of $n_5$'s neighbors includes neighbors of $p$ where it regards $n_6$.
+Then, any neighbors of $p$ are occupied.
+That is if some neighbors of $p$ are free, then there exists a bead which has bonds in neighbors.
+\end{proof}
+
+\begin{proof}
+Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
+Let us assume $w[i]$ is able to be stabilized with using one hand. Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$. Then, $w[i]$ can be also stabilized at $n_3$.
+
+\begin{paragraph}{Case of straight}
+\begin{itemize}
+\item[-] Case of $n_3$ is free\\
+According to assumption, $w[i]$ uses only one hand.
+Therefore, any neighbors of $n_3$ are occupied according to the lemma\ref{TTT_a3_2b_lemma}.
+$n_3$ and the point which is stabilized $w[i]$ are free so that $n_1$ has some bond by lemma\ref{TTT_neighbor_lemma}.
+Accordingly, this situation is non-deterministic.
+Thus, $n_3$ and $n_4$ have to be occupied because of symmetry.
+
+\item[-] Otherwise\\
+Because of  $S[i] = b$, at least one of $n_1$ and $n_2$ have to be free.
+Let us regard that $n_1$ is free.
+Neighbors of $n_1$ have to be occupied and at least two neighbors of $n_{-1}$ have to be free for $n_1$ and $w[i]$.
+According to lemma\ref{TTT_neighbor_lemma}, $n_{-1}$ have some hand.
+Therefore $w[i]$ can be also stabilized $n_1$ that is this situation is non-deterministic.
+Thus, one of $n_3$ and $n_4$ has to be free.
+\end{itemize}
+
+Therefore, this case is false.
+\end{paragraph}
+
+\begin{paragraph}{Case of obtuse}
+\begin{itemize}
+\item[-] Case of $n_3$ is free\\
+Any neighbors of $n_3$ have to be occupied but the point which is stabilized $w[i]$ is free. Thus $n_3$ has to be occupied.
+\item[-] Case of $n_4$ is free\\
+%n4??????????lemma2??n2???????lemma???n0??????????????w[i]???????????????????????bead?????????????1?????
+%??n0?????????????n3???????????lemma1??n-3????????n-3???????????n-2??????????n-1???????????????w[i]???????????????????w[i]????????????
+%??n3?????????????n0????????????lemma1??n-1???????????n-2?n-3???????w[i]?????????????
+%???n0 n3???beead???????????n0 n3 ????????????lemma1??n-1 n-3????????n-1,n-3????????????n-3???????????
+%???n-4????????????in order to provide inifinite structures?
+\item[-] Case of $n_2$ is free\\
+Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied.
+Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_2$ has to be occupied.
+\item[-] Case of $n_0$ is free\\
+Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied.
+Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_0$ has to be occupied.
+\end{itemize}
+
+Therefore, any situations contradict $S[i] = b$.
+
+\end{paragraph}
+
+\begin{paragraph}{Case of acute}
+\begin{itemize}
+\item[-] Case of $n_4$ is free\\
+$n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some hands according to lemma\ref{TTT_neighbor_lemma}.
+However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
+\item[-] Case of $n_2$ is free\\
+According to lemma\ref{TTT_a3_2b_lemma}, $n_0$ has to be occupied. $n_1$ has to be also occupied because of lemma\ref{TTT_neighbor_lemma}.
+We consider this case just like case of obtuse and that $n_4$ is free.
+Then if $w[i-2]$ binds $w[i]$, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
+If $n_1$ binds $w[i]$, this case is same.
+Also if $n_1$ and $w[i-2]$ do not have any hand, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
+Therefore, $w[i+1]$ cannot be provided.
+\item[-] Case of $n_0$ is free\\
+Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied.
+Any neighbors of $n_{1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_0$ has to be occupied.
+\item[-] Case of $n_1$ is free\\
+Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied.
+Any neighbors of $n_{-1}$ except $n_1$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_1$ has to be occupied.
+\end{itemize}
+
+Therefore, any situations contradict $S[i] = b$.
+\end{paragraph}\\
+
+Hence, assumption that w[i] is able to be stabilized with using one hand is false.
+Therefore, when w[i] is stabilized, w[i] uses at least two hands.
+\end{proof}
+
+\begin{figure}
+  \begin{center}
+  \begin{tabular}{c c c}
+ \begin{minipage}{0.3\hsize}
+ \centering
+    \begin{tikzpicture}
+
+      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \fill[blue](0:1) circle [radius=0.05];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+      \draw[->, blue] (0:0.1) -- (0:0.9);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (0:1) {$w_{[i]}$};
+
+	\foreach \theta in {60,-60,120,-120}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+	 \draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
+ 	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[below] at (-120:1) {$n_4$};
+	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
+    \end{tikzpicture}
+    \end{minipage}
+
+    \begin{minipage}{0.3\hsize}
+    \centering
+     \begin{tikzpicture}
+
+      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \fill[blue](60:1) circle [radius=0.05];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+      \draw[->, blue] (60:0.1) -- (60:0.9);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (60:1) {$w_{[i]}$};
+
+	\foreach \theta in {0,-60,120,-120}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+	\draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
+	\draw [shift=(60:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+	\draw [shift=(60:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+
+ 	\node[right] at (0:1) {$n_0$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[below] at (-120:1) {$n_4$};
+	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
+	\node[above, shift=(60:1)] at (60:1) {$n_{-2}$};
+	\node[above, shift=(60:1)] at (120:1) {$n_{-3}$};
+    \end{tikzpicture}
+    \end{minipage}
+
+    \begin{minipage}{0.3\hsize}
+        \centering
+     \begin{tikzpicture}
+
+      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \fill[blue](120:1) circle [radius=0.05];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+      \draw[->, blue] (120:0.1) -- (120:0.9);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (120:1) {$w_{[i]}$};
+
+	\foreach \theta in {0,60,-60,-120}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+	\draw [shift=(120:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+	\draw [shift=(120:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+	\draw [shift=(120:1), shift=(180:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+
+ 	\node[right] at (0:1) {$n_0$};
+	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[below] at (-120:1) {$n_4$};
+	\node[above, shift=(120:1)] at (60:1) {$n_{-1}$};
+	\node[above, shift=(120:1)] at (120:1) {$n_{-2}$};
+	\node[above, shift=(120:1)] at (180:1) {$n_{-3}$};
+    \end{tikzpicture}
+    \end{minipage}
+    \end{tabular}
+    \caption{All possible directions of $w[i]$: straight, obtuse, acute.}
+    \label{TTT_a3_w}
+  \end{center}
+\end{figure}
+
+\subsubsection{$\alpha = 4$}
+\begin{theorem}[$\delta = 1, \alpha = 4$]
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only a finite structure whose size is $\mathcal{O}(n^2)$.
+\end{theorem}
+
+\begin{lemma}
+\label{TTT_a4_2b_lemma}
+Any beads which are already stabilized by some bonds use at least two bonds.
+\end{lemma}
+
+\begin{proof}[proof of lemma]
+Let us consider when $w[i]$ is stabilized by only one bond.
+See Fig.\ref{TTT_a4_lemma_fig}.
+According to lemma\ref{TTT_neighbor_lemma}, if $n_3$ is free, $w[i-2]$ has some hands.
+Thus, $n_4$ has to be occupied in order to stabilize deterministically.
+Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$.
+$n_1$ has some hands because $n_3$ is free.
+Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands.
+It contradict assumption.
+\end{proof}
+
+\begin{proof}
+According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds.
+Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized.
+See Fig.\ref{TTT_a4_first}.
+any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$.
+At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind.
+In this case, a point which is able to put a bead is only $n_2$.
+Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$.
+Hence oritatami system can yield only a finite structure whose size is $\mathcal{O}(n^2)$ in $\delta =1, \alpha = 4$.
+%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
+\end{proof}
+
+\begin{figure}
+ \centering
+    \begin{tikzpicture}
+	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (0:1) {$n_0$};
+
+	\foreach \theta in {0,60,-60,120,-120}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+ 	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[below] at (-120:1) {$n_4$};
+    \end{tikzpicture}
+    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
+    \label{TTT_a4_lemma_fig}
+\end{figure}
+
+\begin{figure}
+ \centering
+    \begin{tikzpicture}
+	\fill[shift=(-120:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0), blue] (0,0) circle [radius=0.05];
+
+      \draw[dashed] (180:2) -- (0:2);
+      \draw[->, blue] (-120:0.9) -- (-120:0.1);
+
+	\node[below] at (-120:1) {$w_{[i-1]}$};
+	\node[above] at (180:0) {$w_{[i]}$};
+	\node[above] at (0:1) {$n_0$};
+
+	\foreach \theta in {0,60,-60,120,180}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+
+ 	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[above] at (180:1) {$n_5$};
+
+	\node at (0:2.5) {$n+1$};
+    \end{tikzpicture}
+    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
+    \label{TTT_a4_first}
+\end{figure}
+
 \end{document}

### 2018-11-23 paper.tex
update 11/23 in Tokyo

@@
 %//////////////////////////////////////////////////////%
-%//////////////////////////////////////////////////////%l.168 - 1324
+%//////////////////////////////////////////////////////%l.168 - 1326
 
@@
 
+\subsubsection{$\alpha = 2$}
+
 By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
@@
 \item[-] Case of $n_4$ is free\\
-%n4??????????lemma2??n2???????lemma???n0??????????????w[i]???????????????????????bead?????????????1?????
-%??n0?????????????n3???????????lemma1??n-3????????n-3???????????n-2??????????n-1???????????????w[i]???????????????????w[i]????????????
-%??n3?????????????n0????????????lemma1??n-1???????????n-2?n-3???????w[i]?????????????
-%???n0 n3???beead???????????n0 n3 ????????????lemma1??n-1 n-3????????n-1,n-3????????????n-3???????????
-%???n-4????????????in order to provide inifinite structures?
+According to lemma\ref{TTT_a3_2b_lemma}, $n_2$ has to be occupied because $n_4$ is free.
+Also $n_0$ has to be occupied from lemma\ref{TTT_neighbor_lemma}.
+Thus, only one of $n_0, n_3$ leave some hands or both of them do not leave any hands because $w[i]$ use only one bond.\\
+If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied.
+Also $n_{-3}$ must not have any hands so that $n_{-2}$ is occupied and also $n_{-1}$ is occupied.
+Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
+If $n_3$ has some hands, then $n_0$ does not have any hands so that $n_{-1}$ is occupied.
+In the same previous way, any $n_{-2}, n_{-3}$ are occupied.
+Therefore any neighbors of $w[i]$ are occupied.\\
+If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied.
+If one of $n_{-1}, n_{-3}$ has some hands, the other does not have any hands so that $n_{-2}$ is occupied.
+If both of $n_{-1}, n_{-3}$ do not have any hands, $n_{-2}$ has to be occupied and $n_{-2}$ has some hands.Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
+Thus $n_3$ has to be occupied in order to yield infinite structures.
 \item[-] Case of $n_2$ is free\\
@@
 %end of d = 1
-%//////////////////////////////////////////////////////% l.168 - 1324
+%//////////////////////////////////////////////////////% l.168 - 1326
 %//////////////////////////////////////////////////////%

### 2018-11-24 paper.tex
Section 3 done
Problem 1 was added to Section 3.

@@
 In \cite{DemaineDNA24}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
-We consider this finiteness problem under various settings of the values of delay and arity. 
+We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.
+
+\begin{problem}\label{prob:det_unary_length}
+Give an upper bound on the length of a transcript of a delay-$\delta$, arity-$\alpha$ deterministic unary oritatami system whose seed is of length $n$ by a function in $\delta$, $\alpha$, and $n$. 
+\end{problem}
+
 Results on this problem are summarized in Fig.~\ref{fig:summary}.

### 2018-11-24 paper.tex
Bibliography
I have just added bibliography file and solve the citation in the paper.

@@
 
-In a recent breakthrough in molecular engineering by Geary, Rothemund and Andersen~\cite{RNAorigami} the co-transcriptional folding of RNA is controlled by careful design of the DNA template.
+In a recent breakthrough in molecular engineering by Geary, Rothemund and Andersen~\cite{GearyRothemundAndersen2014} the co-transcriptional folding of RNA is controlled by careful design of the DNA template.
 As demonstrated in laboratory, this method, called RNA Origami, makes it possible to build rectangles out of RNA strands.
-Geary et al.~\cite{Oritatami} proposed a mathematical model for this process, called oritatami system.
-It has been shown~\cite{Simulator} that the model is computationally universal by simulating cyclic tag systems introduced by Cook~\cite{Cook110}. 
+Geary et al.~\cite{GeMeScSe2016} proposed a mathematical model for this process, called oritatami system.
+It has been just shown in \cite{GeMeScSe2018} that the model is efficiently Turing universal by simulating cyclic tag systems introduced by Cook~\cite{Cook2004}. 
 The simulation involves a very large and complex oritatami system. 
@@
 
+%-------------------------------------------------------
 	\section{Problem description}
-
-In \cite{DemaineDNA24}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
+%-------------------------------------------------------
+
+In \cite{DHOPRSST2018}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
 We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.
@@
 
+\bibliographystyle{splncs03}
+\bibliography{tamc2019.bib}
+
 \end{document}

### 2018-11-28 paper.tex
update 11/28 in Tokyo

@@
 %//////////////////////////////////////////////////////%
-%//////////////////////////////////////////////////////%l.168 - 1326
+%//////////////////////////////////////////////////////%l.177 - 1312
 
@@
 %Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
-For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$ that is foldable by $\Xi$. Hence $C_0 = \sigma$.
+For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$, that is, foldable by $\Xi$. Hence $C_0 = \sigma$.
 
@@
 \begin{theorem}[Tunnel Troll Theorem]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there are indices $i$ and $j$ such that $S[i..j+1] = bt^{j-i}b$, then $\#bc(C_i)$ > $\#bc(C_j)$.
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$.
+If there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$, then $\#bc(C_{i-1}) > \#bc(C_j)$ and if $S[i..j+1] = bt^lbt^mb \quad (l + m = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
+On the other hand, at $\delta = 1$ and $\alpha \geq 3$, if S$[k] = t$, then $\#bc(C_{k-1}) > \#bc(C_k)$.
 \end{theorem}
@@
 Assume $\Xi$ is deterministic.
-%How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
-Each of beads in transcript are bound either inside of tunnel or outside (Fig.
-\ref{TTT_position}).
-If a bead is stabilized at inside of tunnel, then its successor is already decided the position either inside of a tunnel or outside.
-Moreover, If a bead is stabilized at outside of a tunnel, then its position is an entrance of a tunnel or otherwise.
-
-Tunnel sections have three possible shape with considering symmetry such as straight, acute turn and obtuse turn (Fig.
-\ref{TTT_tunnel}).
-%Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Fig.
-\ref{TTT_enterpoint}).
-
-Let us consider each of cases of tunnel A, B, and C. Accordingly, We use lemma \ref{TTT_neighbor_lemma}
+Each bead in the transcript is bound either inside a tunnel or outside.
+If a bead is stabilized inside a tunnel, then its successor is already decided the position either inside of a tunnel or outside.
+Moreover, If a bead is stabilized outside a tunnel, then its position is an entrance of a tunnel or otherwise.
+
+Tunnel sections have three possible shapes up to symmetry : straight($A$), obtuse($B$) and acute($C$) turn (Fig. \ref{TTT_tunnel}), and we will consider each of those.
 
@@
 \label{TTT_neighbor_lemma}
-If a bead does not have any bond, then neighbors of it must be occupied by $\alpha + 2$ beads at $\delta = 1$ and unary except first and last beads.
+For unary transcripts at $\delta = 1$, If a bead has no free hand, then at least $\alpha + 2$ of its neighbors have to be occpied.
 \end{lemma}
 
-\begin{proof}[lemma \ref{TTT_neighbor_lemma}]
-A bead in transcript needs predecessor and successor except first and last beads.
-If the bead does not have ant bond, then it use hand with $\alpha$ neighbors.
-Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
-\end{proof}
-
-Let us consider tunnel sections only tunnel A and B.
-See Fig.
-\ref{TTT_position}.
-From appendix (Entrance of Tunnel A, B and Exit of Tunnel), we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successor\ in\ outside$.
-
-%The sequence $S$ can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+ \cup bt^+bt^+$.
-
-Next, we consider on tunnel C section.
-If $w[i]$ is stabilized by tunnel C and $S[i+1]$ is $t$, then $w[i+1]$ is stabilized by tunnel A or B because if $w[i+1]$ is stabilized by tunnel C, then $C_{i+1}$ is a terminal.
-Hence, tunnel C section is divided cases such as Figure \ref{TTT_tunnelC_graph}.
-Cases of $S[i...] = bt^l (l \geq 2)$ are already considered (Upper).
-According to appendix (Tunnel C), cases of $S[i..i+2] = btb$ also consume some binding capabilities (Lower).
-
-Thus, if a bead is stabilized through a tunnel section, then it consume some binging capabilities.
+\begin{lemma}
+\label{TTT_entrance_Tab}
+Let $\Xi$ be an oritatami system at $\delta = 1, \alpha =2$ 
+Assume $\Xi$ stabilizes transcript until $w[i-1]$. If $w[i]$ is stabilized at an entrance point of tunnel $A$ or $B$, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
+\end{lemma}
+
+\begin{lemma}
+\label{TTT_exit}
+Let $w[i]$ be a bead which is stabilized in exit of a tunnel.
+At $\delta = 1, \alpha =2$, If we assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$, then $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
+%if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
+On the other hand, if we assume $S[k] = t (k \leq i)$ at $\delta =1, \alpha \geq 3$, then $\#bc(C_{k-1}) > \#bc(C_{k})$.
+\end{lemma}
+
+\begin{lemma}
+\label{TTT_tunnelC_lemma}
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$.
+We assume $S[h..i+1] = bt^{(i-h)}b \quad (1<h<i)$.
+If at least one of $w[h+1..i]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_i)$.
+\end{lemma}
+
+Let us first consider cases of $\delta \geq 3, \alpha = 1$. These cases are clearly true because we use lemma\ref{TTT_exit}.
+
+Next, we consider the case of $\delta = 2, \alpha = 1$.
+We assume there is index $h$ such that $S[h-1..h+1] = bbt$ or $S[h-1..h+1] = tbt$.
+According to lemma\ref{TTT_entrance_Tab}, if $w[h+1]$ is stabilized by tunnel $A$ or $B$, then $\#bc(C_{h-1}) > \#bc(C_{h})$.
+Also,  According to lemma\ref{TTT_exit}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-1}) > \#bc(C_{h})$, too.
+On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$.
+Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.
+
+\qed
 
@@
             \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-1200:1) {$p^\prime$};
+            \node[above] at (-120:1) {$p^\prime$};
 
@@
     \end{tabular}
-    \caption{All possible tunnel sections: straight, acute turn, and obtuse turn}
+    \caption{All possible tunnel sections: straight, obtuse turn, and acute turn}
     \label{TTT_tunnel}
@@
 \end{figure}
-
-%\begin{figure}
-%  \begin{center}
-%    \begin{tabular}{cc}
-%      
-%      \begin{minipage}{0.2\hsize}
-%      \centering
-%        \begin{tikzpicture}
-%
-%          \begin{scope}[xshift=1cm, yshift=2cm]
-%            \fill(0,0) circle [radius=0.1];
-%            \node[above] at (180:1.2) {$p^\prime$};
-%            
-%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
-%            
-%            
-%            \foreach \theta in {120,-120}{
-%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-%            }
-%
-%            \draw[->] (-1.1,0) -- (-0.1,0);
-%          \end{scope}
-%
-%          \node at (0.25,0) {Tunnel A,B};
-%        \end{tikzpicture}
-%      \end{minipage}
-%
-%      \begin{minipage}{0.2\hsize}
-%      \centering
-%        \begin{tikzpicture}
-%
-%          \begin{scope}[xshift=1cm, yshift=2cm]
-%            \fill(0,0) circle [radius=0.1];
-%            \node[above] at (180:1.2) {$p^\prime$};
-%
-%            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
-%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
-%            
-%            
-%            \foreach \theta in {120}{
-%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-%            }
-%
-%            \draw[->] (-1.1,0) -- (-0.1,0);
-%          \end{scope}
-%
-%          \node at (0.25,0) {Tunnel C};
-%        \end{tikzpicture}
-%      \end{minipage}
-%
-%    \end{tabular}
-%    \caption{Entrance of a tunnel}
-%    \label{TTT_enterpoint}
-%  \end{center}
-%\end{figure}
 
@@
 %    \begin{tikzpicture}
-%      \draw[thick]
-%      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
-%      \node at(2.5,1) {Outside};
-%      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
-%      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
+%      \draw[thick, gray]
+%      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
+%      \node at(2,1) {Outside};
+%      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
+%      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
 %
@@
 %      
-%      \draw[thick]
-%      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
-%      \node at(10.5,1) {Inside of a tunnel};
-%      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-%      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
+%      \draw[thick, gray]
+%      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
+%      \node at(9,1) {Inside of a tunnel};
+%      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
+%      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
 %
 %      \draw[->]
-%      (outside) edge [bend left] node[left] {$b$} (enter)
-%                edge [loop left] node[left] {$b$} (outside)
-%      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
-%                edge [bend left] node[above] {$b$} (next-outside)
-%                edge [bend left] node[right] {$b$}  (outside)
-%      (next-tunnel) edge         node[right] {$t$} (next-outside)
-%                edge [loop right]node[below] {$t$}    (next-tunnel)
-%      (next-outside) edge[bend left] node[above] {$t$}  (outside)
-%                edge [bend left]     node[above] {$t$}(enter)
+%      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
+%                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
+%      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
+%                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
+%                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
+%      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
+%                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
+%      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
+%                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
 %      ;
@@
 %    \end{tikzpicture}
-%    \caption{Cases on position of a bead}
-%    \label{TTT_position1}
+%    \caption{Increment on Tunnel A,B}
+%    \label{TTT_position}
 %  \end{center}
@@
 
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw[thick, gray]
-      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
-      \node at(2,1) {Outside};
-      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
-      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
-
-      \draw[thick, gray]
-      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
-      \node at(9,1) {Inside of a tunnel};
-      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
-
-      \draw[->]
-      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
-                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
-      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
-                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
-                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
-      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
-                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
-      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
-                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
-      ;
-
-    \end{tikzpicture}
-    \caption{Increment on Tunnel A,B}
-    \label{TTT_position}
-  \end{center}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
-      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
-      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
-      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
-      \draw[->] (outside1)--(enter1);
-      \draw[->] (enter1)  --(inside1);
-      \draw[->] (inside1) --(exit1);
-
-      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
-      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
-      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
-      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
-      \draw[->] (outside2)--(enter2);
-      \draw[->] (enter2)  --(inside2);
-      \draw[->] (inside2) --(exit2);
-
-      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
-      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
-      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
-      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
-      \draw[->] (outside3)--(enter3);
-      \draw[->] (enter3)  --(inside3);
-      \draw[->] (inside3) --(exit3);
-
-      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
-      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
-      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
-      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
-      \draw[->] (outside4)--(enter4);
-      \draw[->] (enter4)  --(inside4);
-      \draw[->] (inside4) --(exit4);
-    \end{tikzpicture}
-    \caption{Case of Tunnel C}
-    \label{TTT_tunnelC_graph}
-  \end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%/////////////////////////////////////////////////
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Appendix of Tunnel Troll Theorem}
-\subsubsection{Entrance of TunnelA,B}
-
+%\begin{figure}
+%  \begin{center}
+%    \begin{tikzpicture}
+%      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
+%      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
+%      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
+%      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
+%      \draw[->] (outside1)--(enter1);
+%      \draw[->] (enter1)  --(inside1);
+%      \draw[->] (inside1) --(exit1);
+%      
+%      
+%      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
+%      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
+%      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
+%      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
+%      \draw[->] (outside2)--(enter2);
+%      \draw[->] (enter2)  --(inside2);
+%      \draw[->] (inside2) --(exit2);
+%
+%      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
+%      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
+%      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
+%      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
+%      \draw[->] (outside3)--(enter3);
+%      \draw[->] (enter3)  --(inside3);
+%      \draw[->] (inside3) --(exit3);
+%
+%      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
+%      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
+%      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
+%      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
+%      \draw[->] (outside4)--(enter4);
+%      \draw[->] (enter4)  --(inside4);
+%      \draw[->] (inside4) --(exit4);
+%    \end{tikzpicture}
+%    \caption{Case of Tunnel C}
+%    \label{TTT_tunnelC_graph}
+%  \end{center}
+%\end{figure}
+
+\begin{proof}[lemma \ref{TTT_neighbor_lemma}]
+A transcript bead in has predecessor and successor except the first and last beads.
+If the bead does not have any free hand, then it uses hands with $\alpha$ neighbors.
+Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
+\end{proof}
+
+\begin{proof}[lemma \ref{TTT_entrance_Tab}]
 Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
-Any cases in $\delta = 1, \alpha = 2$ consume some binding capabilities into the follows.
+Let $w[i]$ be stabilized at an entrance point of Tunnel $A$ or $B$.
+All cases are $\#bc(C_{i-1}) > \#bc(C_{i})$ as follows.
 
@@
 \item{Case of $t_0$}\\
-  Let us consider points of $n_3,n_4$ either occupied or not.
-A point $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-If $n_3$ is free, then $p^\prime$ has to be bound to a bead except $n_1$ due to deterministically stabilize.
-In this situation, at least three neighbors of $n_1$ are free that is $n_1$ leave at least one bond from lemma \ref{TTT_neighbor_lemma}.
+  Let us consider points $n_3,n_4$.
+At least one of the points $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
+If $n_3$ is free, then $p^\prime$ has to be bound to a bead other than $n_1$ due to deterministically stabilize.
+In this situation, at least three neighbors of $n_1$ are free, that is, $n_1$ has at least one free hand from lemma \ref{TTT_neighbor_lemma}.
 Hence, $p^\prime$ must be bound to $n_1$.
-Thus, a case of $t_0$ consumes two binding capabilities and it does not supply any binding capabilities.
+Thus, a case of $t_0$ consumes two hands and it does not supply any binding capabilities.
 
@@
 If $n_5$ is occupied, then $n_4$ is free.
-This time, $n_2$ has some binding capabilities so $p^\prime$ has to be bound to $n_2$.
-
-  In this situation, $p^\prime$ is able to supply a binding capability.
-if this capability is active, $p^\prime$ bind a bead into $n_4$ or $n_5$.
-However, $n_2$ and $n_3$ are exist in back bone.
+This time, $n_2$ has some free hands so $p^\prime$ has to be bound to $n_2$.
+
+  In this situation, $p^\prime$ is able to supply a binding capabilities which could $p^\prime$ bind a bead into $n_4$ or $n_5$.
+However, $n_2$ and $n_3$ are part of a contiguous conformation.
 According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive.
-Thus, a case of $t_{\pm 60}$ consumes some binding capabilities.
+Thus, a case of $t_{\pm 60}$ is$\#bc(C_{i-1}) > \#bc(C_{i})$.
 
 \item{Case of $t_{\pm 120}$}\\
-  Binding capabilities that $p^\prime$ supply are inactive according to Jordan curve theorem on $n_1$ and $n_2$.
+  Binding capabilities that $p^\prime$ supplies are inactive according to Jordan curve theorem on $n_1$ and $n_2$.
 Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
-Thus, a case of $t_{\pm 120}$ consumes some binging capabilities.
+Thus, a case of $t_{\pm 120}$ is $\#bc(C_{i-1}) > \#bc(C_{i})$.
 
@@
 
-\subsubsection{Exit of Tunnel}
-
+\end{proof}
+
+\begin{proof}[lemma \ref{TTT_exit}]
 Fig.\ref{TTT_tunnel_exit} exhibits all the two kinds of exit of tunnel. 
-At least one of point $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-
-\paragraph{$\delta = 1, \alpha = 2$}
- Any cases of $\delta = 1, \alpha = 2$ supply at most $a$ binding capabilities into follows where $a$ is number of predecessor of $p^\prime$ consumes binging capabilities.
+At least one of points $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
+
+\begin{paragraph}{}
+$\delta = 1, \alpha = 2$\\
+Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$. We assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$.
+If let $a$ be $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$ as follows.
+Also, if $h - i > 1$ and let $j$ be $h<j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because any neighbors of $w[j]$ are occupied by beads of tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$.
+Thus, $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
+\end{paragraph}
 
 \begin{itemize}
-\item{Case of $n_1$ and $n_2$ are free}\\
-  This case can be regarded same situation as entrance.
+\item{Case of $n_1$ and $n_2$ being free}\\
+  This case can be regarded the same as entrance.
 See Fig.\ref{TTT_tunnel_exit} (Left).
-Predecessor $n_5$ has to be bound $n_4$ and $n_5$ because each of $n_3$ and $n_4$ leave binding capabilities.
-Hence, at least $a=2$.
-This time, $\alpha = 2$ that is this case supply at most only $a$ binding capabilities.
-
-\item{Case of $c$ is occupied}\\
+Predecessor $n_5$ has to be bound to $n_4$ and $n_5$ because both of $n_3$ and $n_4$ have binding capabilities.
+Hence, $a \geq 2$.
+This time, $\alpha = 2$, that is, this case $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
+
+\item{Case of $n_1$ is occupied}\\
   See Fig.\ref{TTT_tunnel_exit} (Right).
 If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$.
-Hence, at least $a=1$.
-This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied a successor of $p^\prime$.
-Therefore, this case supply at most only $a=1$ active binding capability.
+Hence,  $a \geq 1$.
+This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied by the successor of $p^\prime$.
+Therefore, this case $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
 
@@
 
-\paragraph{$\delta = 1, \alpha \geq 3$}
-Any cases of $\delta = 1, \alpha \geq 3$ consume some binding capabilities into follows.
+\begin{paragraph}{}
+$\delta = 1, \alpha \geq 3$\\
+Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha \geq 3$. We assume $w[i]$ is stabilized at exit of tunnel.
+Any cases $\#bc(C_{i-1}) > \#bc(C_{i})$.
+Moreover, if $S[k] = t (k \leq i)$, then $\#bc(C_{k-1}) > \#bc(C_{k})$ because both of sides of the path $p$ in Fig.\ref{TTT_inside_tunnel} ($n_1, n_2$) have two free points and one of $n_1, n_2$ is not the predecessor so that it has hand and moreover that $w[k]$ supplies any binding capabilities because its neighbors are occupied by beads of tunnel.
+\end{paragraph}
 
@@
     \begin{tabular}{cc}
-
-      \begin{minipage}{0.48\linewidth}
-      \centering
-        \begin{tikzpicture}
+    \begin{minipage}{0.66\hsize}
+    \centering
+      \begin{tabular}{cc}
+      \begin{minipage}{0.45\linewidth}
+      \centering
+        \begin{tikzpicture}
+	\draw[white] (0:0) -- (120:1);
+	\draw[white] (0:0) -- (-60:1);
+	\draw[white] (0:0) -- (0:1);
 
@@
 
-      \begin{minipage}{0.48\linewidth}
-      \centering
-        \begin{tikzpicture}
+      \begin{minipage}{0.45\linewidth}
+      \centering
+        \begin{tikzpicture}
+	\draw[white] (0:0) -- (0:1);
+	\draw[white] (0:0) -- (120:1);
+	\draw[white] (0:0) -- (-90:2);
 
@@
       \end{minipage}
-
     \end{tabular}
@@
     \label{TTT_tunnel_exit}
-\end{figure}
-
-\subsubsection{Tunnel C}
-
-Assume $w[i]$ is a bead which stabilized by tunnel C. Let us consider kinds of stabilization $S[i-2..i] = tbt$ or $S[i-2..i] = bbt$ except cases of $w[i]$ is inside of tunnel A, B.
-
-\subsubsection{Case of $S[i-2..i] = tbt$}
+    \end{minipage}
+
+    \begin{minipage}{0.33\hsize}
+    \centering
+     \begin{tikzpicture}
+	\draw[white] (0:0) -- (120:1);
+	\draw[white] (0:0) -- (-60:1);
+            \fill[blue](0,0) circle [radius=0.05];
+            \draw[blue] (0:1) circle [radius = 0.05];
+            \draw[->] (0:0.1) -- node[above]{$p$} (0:0.9);
+
+            \foreach \theta in {60, -60, 120,-120,180}{
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+            \node[transform canvas={shift=(60:1)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
+                \end{tikzpicture}
+
+    \caption{Inside tunnel}
+    \label{TTT_inside_tunnel}
+    \end{minipage}
+
+    \end{tabular}
+\end{figure}
+\end{proof}
+
+\begin{proof}[lemma \ref{TTT_tunnelC_lemma}]
+Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
+Assume $S[h..i+1] = bt^{i-h}b (h<i)$.
+If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$ is stabilized by tunnel $C$, $C_g$ is a terminal.
+
+Let us consider kinds of stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ into follows.
+In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
+In addition according to lemma\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$.
+Thus, $\#bc(C_{h-3}) > \#bc(C_{i})$.
+\\
+
+\subsubsection{Case of $S[h-1..h+1] = tbt$}
 Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
@@
 \item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  In this figure, Bead $n_4$ has at least one binding so that $w[i-2]$ has to bound $n_4$.
-Moreover, $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
-On the other hand, $w[i]$ can supply two bindings but free neighbors of $w[i]$ are two points.
+  In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$.
+Moreover, $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
+On the other hand, $w[h+1]$ can supply two bindings but free neighbors of $w[h+1]$ are two points.
 One of them is occupied by a successor.
-Therefore $w[i]$ can only bind one of $n_5, n_6$ that is $w[i]$ supplies at most one binding.
-Thus, this case consumes some binding capabilities.
+Therefore $w[h+1]$ can only bind one of $n_5, n_6$, that is, $w[h+1]$ supplies at most one binding.
+Thus, this case $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
 
 \item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  This cases are divided on number of capabilities that $w[i-2]$ consumes.
+  This cases are divided on number of capabilities that $w[h-1]$ consumes.
   \begin{itemize}
   \item[-]{$w[i]$ does not consume any bindings}\\
-    $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
-$w[i]$ has to be bound to $w[i-2]$ because $w[i-2]$ has bindings.
-This time, let us consider either $n_4$ is occupied or not.
-If $n_4$ is occupied, then $w[i-2]$ has no active bindings that is this situation consumes some binding capabilities.
-If $n_4$ is free and $w[i+1]$ is stabilized in $n_4$, then $w[i-2]$ has to bind $w[i+1]$.
-Therefore, In this case, stabilization of $w[i-2..i+1]$ consumes some bindings.
-If $n_4$ is free and $w[i+1]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[i+1]$.
+  According to lemma\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
+    $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
+    $w[h+1]$ has to be bound to $w[h-1]$ because $w[h-1]$ has bindings, that is, $w[h+1]$ consumes at least one hand and supplies at most one hand so that $\#bc(C_{h}) \geq \#bc(C_{h+1})$.
+Thus, in this cases $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
+%     This time, let us consider either $n_4$ is occupied or not.
+If $n_4$ is occupied, then $w[h-1]$ has no active bindings that is this situation consumes some binding capabilities.
+If $n_4$ is free and $w[h+2]$ is stabilized in $n_4$, then $w[h-1]$ has to bind $w[h+2]$.
+Therefore, In this case, stabilization of $w[h-1..h+2]$ consumes some bindings.
+If $n_4$ is free and $w[h+2]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[h+2]$.
 Therefore, in this case consumes some bindings.
-Thus in this cases consume some binding capabilities.
-
-  \item[-]{$w_i$ consumes one binding}\\
-    In this case, $w_{i-1}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[i-2]$ and $w[i]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
+Thus in this cases $\#bc(C_{h-1}) > \#bc(C_{h+2})$.
+
+  \item[-]{$w_{h+1}$ consumes one binding}\\
+    In this case, $w_{h}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[h-1]$ and $w[h+1]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
   \item[-]{$w_i$ consumes two bindings}\\
-    In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies two bindings. Thus, in this cases consume some binding capabilities.
+    In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies two bindings. Thus, in this cases $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
 
@@
 
-            \node[below] at (180:1) {$w[i-2]$};
-            \node[above] at (0:0) {$w[i-1]$};
-            \node[right] at (-120:1) {$w[i]$};
+            \node[below] at (180:1) {$w[h-1]$};
+            \node[above] at (0:0) {$w[h]$};
+            \node[right] at (-120:1) {$w[h+1]$};
 
@@
     \end{tabular}
-    \caption{Case of $S[i-2..i] = tbt$}
+    \caption{Case of $S[h-1..h+1] = tbt$}
     \label{TTT_tunnelC_enter_usingTunnel}
@@
 
-\subsubsection{Case of $S[i-2..i] = bbt$}
-Let us consider number of consumed by $w[i-2]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
+\subsubsection{Case of $S[h-1..h+1] = bbt$}
+Let us consider number of consumed by $w[h-1]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
 
 \begin{itemize}
-\item{$w[i-2]$ consumes one binding}\\
-  In this situation, $w[i-2]$ supplies one active binding whereas $w[i]$ consumes this binding. In addition, $w[i-1]$ has to bound to one of $n_1, n_2, n_3$.
+\item{$w[h-1]$ consumes one binding}\\
+  In this situation, $w[h-1]$ supplies one active binding whereas $w[h+1]$ consumes this binding. In addition, $w[h]$ has to bound to one of $n_1, n_2, n_3$.
   Thus, in this cases consume some binding capabilities.
 
-\item{$w[i-2]$ consumes two bindings}\\
-  In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
+\item{$w[h-1]$ consumes two bindings}\\
+  In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
 \end{itemize}
@@
 
-          \node[below left] at (180:1) {$w[i-2]$};
-          \node[above] at (0:0) {$w[i-1]$};
-          \node[below] at (-120:1) {$w[i]$};
+          \node[below left] at (180:1) {$w[h-1]$};
+          \node[above] at (0:0) {$w[h]$};
+          \node[below] at (-120:1) {$w[h+1]$};
 
@@
         \end{tikzpicture}
-    \caption{Case of $S[i-2..i] = bbt$}
+    \caption{Case of $S[h-1..h+1] = bbt$}
     \label{TTT_tunnelC_enter_usingBond}
@@
 
-\subsubsection{$\alpha = 2$}
-
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%/////////////////////////////////////////////////
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{On structures provided by a unary and $\delta = 1$ oritatami system}
+\begin{theorem}[$\delta= 1, \alpha=2$]
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation.
+\end{theorem}
+
+\begin{proof}
 By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
@@
 If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding.
-If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive that is $w[i-1]$ consumes two binding capabilities.
+If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive, that is, $w[i-1]$ consumes two binding capabilities.
 Therefore, this case consumes binding capabilities.
@@
 Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.
+Thus, in this case, oritatami system can yield infinite structures but they are only zig-zag conformation.
+
+\end{proof}
 
@@
 
-\subsubsection{$\alpha = 3$}
-
 \begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only a finite structure whose size is $\mathcal{O}(n)$.
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite structures whose size is $\mathcal{O}(n)$.
 \end{theorem}
@@
 Then, any neighbors of $p$ are occupied.
-That is if some neighbors of $p$ are free, then there exists a bead which has bonds in neighbors.
+That is, if some neighbors of $p$ are free, then there exists a bead which has bonds in neighbors.
 \end{proof}
@@
 \begin{proof}
-Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
+Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is, when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
 Let us assume $w[i]$ is able to be stabilized with using one hand. Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$. Then, $w[i]$ can be also stabilized at $n_3$.
@@
 According to lemma\ref{TTT_neighbor_lemma}, $n_{-1}$ have some hand.
-Therefore $w[i]$ can be also stabilized $n_1$ that is this situation is non-deterministic.
+Therefore $w[i]$ can be also stabilized $n_1$, that is, this situation is non-deterministic.
 Thus, one of $n_3$ and $n_4$ has to be free.
@@
 
-\subsubsection{$\alpha = 4$}
 \begin{theorem}[$\delta = 1, \alpha = 4$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only a finite structure whose size is $\mathcal{O}(n^2)$.
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite structures whose size is $\mathcal{O}(n^2)$.
 \end{theorem}
@@
       \draw[dashed] (180:2) -- (0:2);
+      \draw[dashed, shift=(-60:1)] (180:2.5) -- (0:1.5);
       \draw[->, blue] (-120:0.9) -- (-120:0.1);
@@
 	\node at (0:2.5) {$n+1$};
+	\node[shift=(-60:1)] at (0:2) {$n$};
     \end{tikzpicture}
@@
 %end of d = 1
-%//////////////////////////////////////////////////////% l.168 - 1326
+%//////////////////////////////////////////////////////% l.177 - 1312
 %//////////////////////////////////////////////////////%

### 2018-11-28 ttt.tex
update 11/28 in Tokyo

@@
 %  \begin{center}
-%    \begin{tabular}{cc}
-%      
-%      \begin{minipage}{0.2\hsize}
-%      \centering
 %    \begin{tikzpicture}
-%
-%          \begin{scope}[xshift=1cm, yshift=2cm]
-%            \fill(0,0) circle [radius=0.1];
-%            \node[above] at (180:1.2) {$p^\prime$};
-%            
-%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
+%      \draw[thick, gray]
+%      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
+%      \node at(2,1) {Outside};
+%      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
+%      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
 %
 %      
-%            \foreach \theta in {120,-120}{
-%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-%            }
 %      
-%            \draw[->] (-1.1,0) -- (-0.1,0);
-%          \end{scope}
+%      \draw[thick, gray]
+%      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
+%      \node at(9,1) {Inside of a tunnel};
+%      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
+%      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
 %
-%          \node at (0.25,0) {Tunnel A,B};
+%      \draw[->]
+%      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
+%                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
+%      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
+%                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
+%                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
+%      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
+%                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
+%      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
+%                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
+%      ;
+%      
 %    \end{tikzpicture}
-%      \end{minipage}
-%
-%      \begin{minipage}{0.2\hsize}
-%      \centering
-%        \begin{tikzpicture}
-%
-%          \begin{scope}[xshift=1cm, yshift=2cm]
-%            \fill(0,0) circle [radius=0.1];
-%            \node[above] at (180:1.2) {$p^\prime$};
-%
-%            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
-%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
-%            
-%            
-%            \foreach \theta in {120}{
-%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-%            }
-%
-%            \draw[->] (-1.1,0) -- (-0.1,0);
-%          \end{scope}
-%
-%          \node at (0.25,0) {Tunnel C};
-%        \end{tikzpicture}
-%      \end{minipage}
-%
-%    \end{tabular}
-%    \caption{Entrance of a tunnel}
-%    \label{TTT_enterpoint}
+%    \caption{Increment on Tunnel A,B}
+%    \label{TTT_position}
 %  \end{center}
@@
 %    \begin{tikzpicture}
-%      \draw[thick]
-%      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
-%      \node at(2.5,1) {Outside};
-%      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
-%      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
+%      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
+%      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
+%      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
+%      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
+%      \draw[->] (outside1)--(enter1);
+%      \draw[->] (enter1)  --(inside1);
+%      \draw[->] (inside1) --(exit1);
 %      
 %      
+%      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
+%      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
+%      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
+%      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
+%      \draw[->] (outside2)--(enter2);
+%      \draw[->] (enter2)  --(inside2);
+%      \draw[->] (inside2) --(exit2);
 %
-%      \draw[thick]
-%      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
-%      \node at(10.5,1) {Inside of a tunnel};
-%      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-%      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
+%      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
+%      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
+%      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
+%      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
+%      \draw[->] (outside3)--(enter3);
+%      \draw[->] (enter3)  --(inside3);
+%      \draw[->] (inside3) --(exit3);
 %
-%      \draw[->]
-%      (outside) edge [bend left] node[left] {$b$} (enter)
-%                edge [loop left] node[left] {$b$} (outside)
-%      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
-%                edge [bend left] node[above] {$b$} (next-outside)
-%                edge [bend left] node[right] {$b$}  (outside)
-%      (next-tunnel) edge         node[right] {$t$} (next-outside)
-%                edge [loop right]node[below] {$t$}    (next-tunnel)
-%      (next-outside) edge[bend left] node[above] {$t$}  (outside)
-%                edge [bend left]     node[above] {$t$}(enter)
-%      ;
-%      
+%      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
+%      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
+%      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
+%      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
+%      \draw[->] (outside4)--(enter4);
+%      \draw[->] (enter4)  --(inside4);
+%      \draw[->] (inside4) --(exit4);
 %    \end{tikzpicture}
-%    \caption{Cases on position of a bead}
-%    \label{TTT_position1}
+%    \caption{Case of Tunnel C}
+%    \label{TTT_tunnelC_graph}
 %  \end{center}
@@
 
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw[thick, gray]
-      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
-      \node at(2,1) {Outside};
-      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
-      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
-
-      \draw[thick, gray]
-      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
-      \node at(9,1) {Inside of a tunnel};
-      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
-
-      \draw[->]
-      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
-                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
-      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
-                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
-                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
-      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
-                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
-      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
-                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
-      ;
-
-    \end{tikzpicture}
-    \caption{Increment on Tunnel A,B}
-    \label{TTT_position}
-  \end{center}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
-      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
-      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
-      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
-      \draw[->] (outside1)--(enter1);
-      \draw[->] (enter1)  --(inside1);
-      \draw[->] (inside1) --(exit1);
-
-      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
-      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
-      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
-      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
-      \draw[->] (outside2)--(enter2);
-      \draw[->] (enter2)  --(inside2);
-      \draw[->] (inside2) --(exit2);
-
-      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
-      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
-      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
-      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
-      \draw[->] (outside3)--(enter3);
-      \draw[->] (enter3)  --(inside3);
-      \draw[->] (inside3) --(exit3);
-
-      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
-      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
-      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
-      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
-      \draw[->] (outside4)--(enter4);
-      \draw[->] (enter4)  --(inside4);
-      \draw[->] (inside4) --(exit4);
-    \end{tikzpicture}
-    \caption{Case of Tunnel C}
-    \label{TTT_tunnelC_graph}
-  \end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%/////////////////////////////////////////////////
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Appendix of Tunnel Troll Theorem}
-\subsubsection{Entrance of TunnelA,B}
-
+\begin{proof}[lemma \ref{TTT_neighbor_lemma}]
+A transcript bead in has predecessor and successor except the first and last beads.
+If the bead does not have any free hand, then it uses hands with $\alpha$ neighbors.
+Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
+\end{proof}
+
+\begin{proof}[lemma \ref{TTT_entrance_Tab}]
 Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
-Any cases in $\delta = 1, \alpha = 2$ consume some binding capabilities into the follows.
+Let $w[i]$ be stabilized at an entrance point of Tunnel $A$ or $B$.
+All cases are $\#bc(C_{i-1}) > \#bc(C_{i})$ as follows.
 
@@
     \label{TTT_tunnel_exit}
+    \end{minipage}
+
+    \begin{minipage}{0.33\hsize}
+    \centering
+     \begin{tikzpicture}
+	\draw[white] (0:0) -- (120:1);
+	\draw[white] (0:0) -- (-60:1);
+            \fill[blue](0,0) circle [radius=0.05];
+            \draw[blue] (0:1) circle [radius = 0.05];
+            \draw[->] (0:0.1) -- node[above]{$p$} (0:0.9);
+
+            \foreach \theta in {60, -60, 120,-120,180}{
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+            \node[transform canvas={shift=(60:1)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
+                \end{tikzpicture}
+
+    \caption{Inside tunnel}
+    \label{TTT_inside_tunnel}
+    \end{minipage}
+
+    \end{tabular}
 \end{figure}
-
-\subsubsection{Tunnel C}
-
-Assume $w[i]$ is a bead which stabilized by tunnel C. Let us consider kinds of stabilization $S[i-2..i] = tbt$ or $S[i-2..i] = bbt$ except cases of $w[i]$ is inside of tunnel A, B.
-
-\subsubsection{Case of $S[i-2..i] = tbt$}
+\end{proof}
+
+\begin{proof}[lemma \ref{TTT_tunnelC_lemma}]
+Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
+Assume $S[h..i+1] = bt^{i-h}b (h<i)$.
+If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$ is stabilized by tunnel $C$, $C_g$ is a terminal.
+
+Let us consider kinds of stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ into follows.
+In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
+In addition according to lemma\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$.
+Thus, $\#bc(C_{h-3}) > \#bc(C_{i})$.
+\\
+
+\subsubsection{Case of $S[h-1..h+1] = tbt$}
 Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.

### 2018-11-30 ttt.tex
update after noon

@@
 
-In this section, we consider on finiteness of structures produced deterministically at delay 1.
-In result, cases of arity 1 and 3 can only yield finite structures which is size of $\mathcal{O} (n)$, and cases of arity 4 and more can only yield finite structures which is size of $mathcal{O} (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
+In this section, we consider the finiteness of structures produced deterministically at delay 1.
+Our result, cases of arity 1 and 3 can only yield finite structures of size $\mathcal{O} (n)$, and cases of arity 4 and more can only yield finite structures which is size of $mathcal{O} (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
 
@@
 Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
-We call such a bead $p$ as $inside\ of\ a\ tunnel$ and such beads $p^\prime$ as $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel.
+We call such a point $p$ the $inside\ of\ a\ tunnel$ and points $p^\prime$ the $entrance\ of\ a\ tunnel$ except when $p^\prime$ is inside of a tunnel.
 If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor.
@@
 Moreover, let $R_i$ be a set of neighbors of $w[i]$ that are free and reachable from $C_j$ where $C_j$ is a conformation which stabilized until $w[j]$.
- We represent the number of binding capabilities of a conformation $C_j$ as $\#bc(C_j)$. $\#bc(C_j)$ is defined by $\sum^{j}_{k=-n+1} \min \{ |B_k|, |R_k|  \}$.
+ The number of binding capabilities of a conformation $C_j$ is denoted $\#bc(C_j)$ and is defined by $\sum^{j}_{k=-n+1} \min \{ |B_k|, |R_k|  \}$.
 \end{definition}
@@
 Each bead in the transcript is bound either inside a tunnel or outside.
-If a bead is stabilized inside a tunnel, then its successor is already decided the position either inside of a tunnel or outside.
-Moreover, If a bead is stabilized outside a tunnel, then its position is an entrance of a tunnel or otherwise.
+If a bead is stabilized inside a tunnel, then the position of successor is already decided either inside of a tunnel or outside.
+Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.
 
@@
 \label{TTT_neighbor_lemma}
-For unary transcripts at $\delta = 1$, If a bead has no free hand, then at least $\alpha + 2$ of its neighbors have to be occpied.
+For unary transcripts at $\delta = 1$, if a bead has no free hand, then at least $\alpha + 2$ of its neighbors have to be occpied.
 \end{lemma}
@@
 \label{TTT_entrance_Tab}
-Let $\Xi$ be an oritatami system at $\delta = 1, \alpha =2$ 
-Assume $\Xi$ stabilizes transcript until $w[i-1]$. If $w[i]$ is stabilized at an entrance point of tunnel $A$ or $B$, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
+Let $\Xi$ be an oritatami system at $\delta = 1, \alpha =2$. 
+Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $w[i]$ is stabilized at an entrance point of tunnel $A$ or $B$, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
 \end{lemma}
@@
 \label{TTT_exit}
-Let $w[i]$ be a bead which is stabilized in exit of a tunnel.
-At $\delta = 1, \alpha =2$, If we assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$, then $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
+Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
+At $\delta = 1, \alpha =2$, if we assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$, then $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
 %if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
@@
 We assume $S[h..i+1] = bt^{(i-h)}b \quad (1<h<i)$.
-If at least one of $w[h+1..i]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_i)$.
+If at least one of $w[h+1..i]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_i)$.
 \end{lemma}
 
-Let us first consider cases of $\delta \geq 3, \alpha = 1$. These cases are clearly true because we use lemma\ref{TTT_exit}.
+Let us first consider cases of $\delta \geq 3, \alpha = 1$. These cases are clearly true because of lemma\ref{TTT_exit}.
 
 Next, we consider the case of $\delta = 2, \alpha = 1$.
-We assume there is index $h$ such that $S[h-1..h+1] = bbt$ or $S[h-1..h+1] = tbt$.
+We assume there is an index $h$ such that $S[h-1..h+1] = bbt$ or $S[h-1..h+1] = tbt$.
 According to lemma\ref{TTT_entrance_Tab}, if $w[h+1]$ is stabilized by tunnel $A$ or $B$, then $\#bc(C_{h-1}) > \#bc(C_{h})$.
-Also,  According to lemma\ref{TTT_exit}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-1}) > \#bc(C_{h})$, too.
-On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$.
+Also,  According to lemma\ref{TTT_tunnelC_lemma}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
+On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of lemma\ref{TTT_exit}.
 Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.
@@
 \begin{proof}[lemma \ref{TTT_neighbor_lemma}]
-A transcript bead in has predecessor and successor except the first and last beads.
+Any transcript bead has predecessor and successor except for the first and last beads.
 If the bead does not have any free hand, then it uses hands with $\alpha$ neighbors.
@@
 At least one of the points $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-If $n_3$ is free, then $p^\prime$ has to be bound to a bead other than $n_1$ due to deterministically stabilize.
+If $n_3$ is free, then $p^\prime$ has to be bound to a bead other than $n_1$ to deterministically stabilize.
 In this situation, at least three neighbors of $n_1$ are free, that is, $n_1$ has at least one free hand from lemma \ref{TTT_neighbor_lemma}.
@@
 \item{Case of $t_{\pm 60}$}\\
-  In this case, a point $n_4$ or $n_5$ is free, too.
+  In this case, too, $n_4$ or $n_5$ is free.
 If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$.
 If $n_5$ is occupied, then $n_4$ is free.
-This time, $n_2$ has some free hands so $p^\prime$ has to be bound to $n_2$.
-
-  In this situation, $p^\prime$ is able to supply a binding capabilities which could $p^\prime$ bind a bead into $n_4$ or $n_5$.
+This time, by $n_2$ has some free hands so $p^\prime$ has to be bound to $n_2$.
+
+  In this situation, $p^\prime$ is able to supply a binding capabilities which could bind a bead into $n_4$ or $n_5$.
 However, $n_2$ and $n_3$ are part of a contiguous conformation.
 According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive.
-Thus, a case of $t_{\pm 60}$ is$\#bc(C_{i-1}) > \#bc(C_{i})$.
+Thus, in the case of $t_{\pm 60}$ $\#bc(C_{i-1}) > \#bc(C_{i})$.
 
@@
 Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
-Thus, a case of $t_{\pm 120}$ is $\#bc(C_{i-1}) > \#bc(C_{i})$.
+Thus, in the case of $t_{\pm 120}$ is $\#bc(C_{i-1}) > \#bc(C_{i})$.
 
@@
 Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$. We assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$.
-If let $a$ be $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$ as follows.
-Also, if $h - i > 1$ and let $j$ be $h<j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because any neighbors of $w[j]$ are occupied by beads of tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$.
+Let $a$ be $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$.
+Then, $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$ as follows.
+Also, if $i - h > 1$ and $j$ is such that $h<j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because all neighbors of $w[j]$ are occupied by beads forming the tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$.
 Thus, $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
@@
 \begin{itemize}
-\item{Case of $n_1$ and $n_2$ being free}\\
+\item{Case of both $n_1$ and $n_2$ being free}\\
   This case can be regarded the same as entrance.
@@
 Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha \geq 3$. We assume $w[i]$ is stabilized at exit of tunnel.
-Any cases $\#bc(C_{i-1}) > \#bc(C_{i})$.
-Moreover, if $S[k] = t (k \leq i)$, then $\#bc(C_{k-1}) > \#bc(C_{k})$ because both of sides of the path $p$ in Fig.\ref{TTT_inside_tunnel} ($n_1, n_2$) have two free points and one of $n_1, n_2$ is not the predecessor so that it has hand and moreover that $w[k]$ supplies any binding capabilities because its neighbors are occupied by beads of tunnel.
+In all cases $\#bc(C_{i-1}) > \#bc(C_{i})$.
+Moreover, if $S[k] = t (k \leq i)$, then $\#bc(C_{k-1}) > \#bc(C_{k})$ because both sides of the path $p$ in Fig.\ref{TTT_inside_tunnel} ($n_1, n_2$) have two free points and one of $n_1, n_2$ is not the predecessor so that it has hand and moreover that $w[k]$ supplies any binding capabilities because its neighbors are occupied by beads of tunnel.
 \end{paragraph}
@@
   In $\alpha \geq 3$, if three neighbors of a bead leave, then it can supply two binding capabilities.
-Therefore Predecessor $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$, too.
-In this case, at least consumes four bindings and supplies at most two bindings.
-Thus, it consumes some binding capabilities, totally.
-
-\item{Case of $c$ is occupied}\\
+Therefore predecessor $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$, too.
+In this case, at least four bindings are consumed and at most two are added.
+Thus, it consumes some binding capabilities, overall.
+
+\item{Case of $n_1$ is occupied}\\
   In this case, $n_4$ leave at least two bindings and $n_3$, $n_1$ also leave at least one binding.
 Therefore $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$ also has to be bound $n_1$ and $n_4$.
-In this case, at least consumes four bindings and supplies at most one binding.
+In this case, at least four bindings are consumed and at most two are added.
 Thus, it consumes some binding capabilities, totally.
@@
 Assume $S[h..i+1] = bt^{i-h}b (h<i)$.
-If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$ is stabilized by tunnel $C$, $C_g$ is a terminal.
-
-Let us consider kinds of stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ into follows.
+If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$, with $h+2 \leq g \leq i$ is stabilized by tunnel $C$, $C_g$ is a terminal.
+
+Let us consider stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ as follows.
 In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
 In addition according to lemma\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$.
-Thus, $\#bc(C_{h-3}) > \#bc(C_{i})$.
+Thus, $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_{i})$.
 \\
@@
   In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$.
-Moreover, $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
-On the other hand, $w[h+1]$ can supply two bindings but free neighbors of $w[h+1]$ are two points.
+Moreover, $w[h]$ has to bind to one of $n_1, n_2, n_3$ in order to stabilize deterministically.
+On the other hand, $w[h+1]$ can supply two bindings but has only two free neighbors.
 One of them is occupied by a successor.
@@
 \item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  This cases are divided on number of capabilities that $w[h-1]$ consumes.
+  These cases are divided on number of capabilities that $w[h-1]$ consumes.
   \begin{itemize}
-  \item[-]{$w[i]$ does not consume any bindings}\\
+  \item[-]{$w[h-1]$ does not consume any bindings}\\
   According to lemma\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
@@
 
-  \item[-]{$w_{h+1}$ consumes one binding}\\
+  \item[-]{$w[h-1]$ consumes one binding}\\
     In this case, $w_{h}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[h-1]$ and $w[h+1]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
-  \item[-]{$w_i$ consumes two bindings}\\
+  \item[-]{$w[h-1]$ consumes two bindings}\\
     In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies two bindings. Thus, in this cases $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
@@
 
-            \node[below] at (180:1) {$w[h-1]$};
-            \node[above] at (0:0) {$w[h]$};
-            \node[right] at (-120:1) {$w[h+1]$};
+            \node[below] at (180:1) {$w_{[h-1]}$};
+            \node[above] at (0:0) {$w_{[h]}$};
+            \node[below] at (-120:1) {$w_{[h+1]}$};
 
@@
 
-              \node[right] at (180:1) {$n_4$};
+              \node[left] at (180:1) {$n_4$};
               \node[right] at (-120:1) {$n_5$};
@@
 \subsubsection{Case of $S[h-1..h+1] = bbt$}
-Let us consider number of consumed by $w[h-1]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
+Let us consider number of consumed bindings by $w[h-1]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
 

### 2018-11-30 arity1.tex
separate in subfiles

--- 2018-11-24 paper.tex
@@
-\documentclass[runningheads]{llncs}
-
-\usepackage{color}
-
-\usepackage{graphicx}
-\usepackage{tikz}
-\usepackage{calc}
-
-\usepackage{amsmath, amssymb}
-\DeclareMathOperator*{\argmin}{arg\,min}
-
-\usepackage{wasysym}
-
-\usetikzlibrary{automata}
-
-\title{On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F.
-and S.~S.}
-}
-\author{
-Szil\'{a}rd Zsolt Fazekas\inst{1} \and
-Shinnosuke Seki\inst{2}\thanks{Corresponding author}}
-\institute{
-Akita University, 
-Graduate School of Engineering Science, 
-1-1 Tegate Gakuen-machi, Akita, 0108502, Japan \\
-\email{szilard.fazekas@ie.akita-u.ac.jp}
-\and
-The University of Electro-Communications, 
-Graduate School of Informatics and Engineering, 
-1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan \\
-\email{s.seki@uec.ac.jp}
-}
-
-\begin{document}
-
-\maketitle
-
-\begin{abstract}
-We investigate simple oritatami systems in an attempt to establish lower bounds on the size and complexity of computationally universal systems. 
-In particular, we look at oritatami systems, where the folding sequence consists of a number of beads of the same type and show that under reasonable assumptions, these systems are not universal.
-\end{abstract}
-
-%------------------------------------------------------
-	\section{Introduction}
-%------------------------------------------------------
-
-Transcription is the first essential step of gene expression, when a DNA template sequence is copied into a complementary single stranded RNA sequence by a `copy machine' called RNA polymerase. 
-The RNA strand is synthesized letter by letter according to the complimentarity relation ${\tt A} \rightarrow {\tt U}$, ${\tt G} \rightarrow {\tt C}$, ${\tt C} \rightarrow {\tt G}$, and ${\tt T} \rightarrow {\tt A}$ and folds up during a process called co-transcriptional folding.
-
-In a recent breakthrough in molecular engineering by Geary, Rothemund and Andersen~\cite{RNAorigami} the co-transcriptional folding of RNA is controlled by careful design of the DNA template.
-As demonstrated in laboratory, this method, called RNA Origami, makes it possible to build rectangles out of RNA strands.
-Geary et al.~\cite{Oritatami} proposed a mathematical model for this process, called oritatami system.
-It has been shown~\cite{Simulator} that the model is computationally universal by simulating cyclic tag systems introduced by Cook~\cite{Cook110}. 
-The simulation involves a very large and complex oritatami system. 
-One future direction of research is to find smaller universal oritatami system.
-
-Closely related is the question of where not to look for universal systems, i.e., what are the limitations of simple oritatami system. 
-In search for simple oritatami systems, there are a number of restrictions one can pose on them:
-\begin{itemize}
-\item bounds on the delay, the number of bead types or the arity;
-\item bounds on the size of the primary structure or of the attraction rule set;
-\item structural conditions on the primary structure or the attraction rule set.
-\end{itemize}
-
-%Rogers and Seki~\cite{SimpleSim} showed that certain OS with small delays are not universal.
-
-%Han, Kim, Rogers and Seki\cite{SelfRemove} proved that it is possible to avoid self-attraction rules without changing the behavior of OS.
-
-In this paper we start a new line of study which concerns the alphabet size for the primary structure, i.e., the number of bead types.
-
-\begin{figure}[tb]
-\begin{tikzpicture}
-
-\node (origin) at (0, 0) {};
-
-\draw[-latex] (origin) -- ++(0:3) node[below] {$\delta$}; 
-\node at (1, -0.2) {1};
-\node at (2, -0.2) {2};
-\draw[-latex] (origin) -- ++(90:5) node[left] {$\alpha$}; 
-\node at (-0.2, 1) {1};
-\node at (-0.2, 2) {2};
-\node at (-0.2, 3) {3};
-\node at (-0.2, 4) {4};
-
-%Results
-\node at (1, 4) {$O(n^2)$};
-\node at (1, 3) {$O(n)$};
-\node at (1, 2) {$O(n^2)$};
-\node at (1, 1) {$O(n)$ \cite{DemaineDNA24}};
-
-\node at (2, 1) {$O(n^2)$};
-
-\end{tikzpicture}
-\caption{Summary of the results.}
-\label{fig:summary}
-\end{figure}
-
-%------------------------------------------------------
-	\section{Preliminaries}
-%------------------------------------------------------
-\input{uos_preliminaries.tex}
-
-\begin{proposition}\label{prop:check_validity}
-	For any rule set $R$, arity $\alpha$ and conformation $C = (P,w,H)$ it is possible to check whether $C$ is $R$-valid and whether $C\in \mathcal{C}_{\leq \alpha}$ in time $\mathcal{O}(|H|\cdot|w|\cdot|R|)$.
-\end{proposition}
-\begin{proof}
-	To check whether $C$ is $R$-valid:
-	\begin{enumerate}
-		\item FOR each $(i,j)\in H$:
-		\item \hspace{1cm} IF $(w[i],w[j])\notin R$ THEN answer NO and HALT
-		\item answer YES and HALT
-	\end{enumerate}	
-	Checking the condition in 2. can be done in $\mathcal{O}(|w|\cdot|R|)$ time for any reasonable representation of $w$ and $R$, hence the whole process takes $\mathcal{O}(|H|\cdot |w|\cdot|R|)$ time.	
-	To check the arity constraint $C\in \mathcal{C}_{\leq \alpha}$: 
-	\begin{enumerate}
-		\item FOR each $i\in \{1,\dots,|w|\}$:
-		\item \hspace{1cm} IF $\mathrm{degree}(i)=|\{j | (i,j)\in H \}|>\alpha$ THEN answer NO and HALT
-		\item answer YES and HALT
-	\end{enumerate}	
-	Checking the condition in 2. can be done in $\mathcal{O}(|H|)$ time for any reasonable representation of $H$, hence the whole process takes $\mathcal{O}(|w|\cdot|H|)$ time.
-\end{proof}
-\begin{theorem}\label{thm:OS_to_2dTM}
-	There is an algorithm that simulates any oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$. 
-\end{theorem}
-\begin{proof}
-	Take any step in the computation, up to which some $i \ge 0$ first beads of $w$ have been stabilized, with the last bead at a point $p$. 
-	The number of all possible elongations of the current conformation by the next $\delta$-beads is $(6 \times 5^{\delta-1}) \times ((2^4)^{\delta-1} \times 2^5) \in 2^{O(\delta)}$. 
-	By Proposition~\ref{prop:check_validity}, we can check for each of these elongations whether its arity is at most $\alpha$ or not and whether it is $R$-valid or not in time $\mathcal{O}((2^4)^{\delta-1}\cdot2^5\cdot \delta\cdot|R|)=2^{\mathcal{O}(\delta)}\cdot|R|$.
-Therefore, the total running time is $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$.
-\end{proof}
-
-\begin{corollary}
-	For fixed $\delta$ and $\alpha$, the class of problems solvable by oritatami systems $(\Sigma, R, \delta, \alpha, \sigma, w)$ is included in $\mathrm{DTIME}(n^3)$.
-\end{corollary}
-\begin{proof}
-	The claim follows from Theorem~\ref{thm:OS_to_2dTM} and the fact that $|R|$ is implicitly bounded by $|w|^2$.
-\end{proof}
-
-%\begin{corollary}\label{polytranscript}
-%	Let $k$ be a non-negative number.
-Let $\Sigma$, $H$, $\delta$, $\alpha$ be fixed and the transcript length bounded polynomially by the seed length, i.e., $|w|\in O(|\sigma|^k)$.
-Then, the language of seeds $\sigma$ accepted by an OS $(\Sigma, R, \delta, \alpha, \sigma, w)$ is in $\mathrm{DTIME}(|\sigma|^{2k})$.
-%\end{corollary}
-
-%If the transcript length is polynomially bounded by the seed length, than the accepted language is in $\mathrm{P}$.
-
-Because of the time hierarchy theorems, we know that $\mathrm{P}\subsetneq \mathrm{EXP}$, so we can conclude that OS which cannot deterministically fold transcripts of length exponential in the length of the seed are not computationally universal.
-
-\section{Problem description}
-
-In \cite{DemaineDNA24}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
-We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.
-
-\begin{problem}\label{prob:det_unary_length}
-Give an upper bound on the length of a transcript of a delay-$\delta$, arity-$\alpha$ deterministic unary oritatami system whose seed is of length $n$ by a function in $\delta$, $\alpha$, and $n$. 
-\end{problem}
-
-Results on this problem are summarized in Fig.~\ref{fig:summary}.
-
-\section{Case of $\delta = 1$}
-
-%//////////////////////////////////////////////////////%
-%//////////////////////////////////////////////////////%
-%Kohei
-%//////////////////////////////////////////////////////%
-%//////////////////////////////////////////////////////%l.168 - 1326
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \fill (0,0) circle[radius = 0.1];
-      \fill (1.5,0) circle[radius = 0.1];
-      \fill (3,0) circle[radius = 0.1];
-      \fill (4.5,0) circle[radius = 0.1];
-      \fill (6,0) circle[radius = 0.1];
-
-      \draw[dashed] (0,0)--(1.5,0);
-      \draw[dashed] (1.5,0)--(3,0);
-      \draw[dashed] (3,0)--(4.5,0);
-      \draw[dashed] (4.5,0)--(6,0);
-      \draw[->] (0,0)--(60:0.75);
-      \draw[->] (1.5,0)--++(60:0.75);
-      \draw[->] (3,0)--++(60:0.75);
-      \draw[->] (4.5,0)--++(60:0.75);
-      \draw (0,0)--(60:1.5);
-      \draw (1.5,0)--++(60:1.5);
-      \draw (3,0)--++(60:1.5);
-      \draw (4.5,0)--++(60:1.5);
-
-      \begin{scope}[shift=(60:1.5)]
-        \fill (0,0) circle[radius = 0.1];
-        \fill (1.5,0) circle[radius = 0.1];
-        \fill (3,0) circle[radius = 0.1];
-        \fill (4.5,0) circle[radius = 0.1];
-        \draw[dashed] (0,0)--(1.5,0);
-        \draw[dashed] (1.5,0)--(3,0);
-        \draw[dashed] (3,0)--(4.5,0);
-        \draw[->] (0,0)--(-60:0.75);
-        \draw[->] (1.5,0)--++(-60:0.75);
-        \draw[->] (3,0)--++(-60:0.75);
-        \draw[->] (4.5,0)--++(-60:0.75);
-
-        \draw (0,0)--(-60:1.5);
-        \draw (1.5,0)--++(-60:1.5);
-        \draw (3,0)--++(-60:1.5);
-        \draw (4.5,0)--++(-60:1.5);
-      \end{scope}
-
-    \end{tikzpicture}
-    \caption{zig-zag conformation}
-    \label{TTT_zigzag}
-  \end{center}
-\end{figure}
-
-\subsection{Introduction}
-
-In this section, we consider on finiteness of structures produced deterministically at delay 1.
-In result, cases of arity 1 and 3 can only yield finite structures which is size of $\mathcal{O} (n)$, and cases of arity 4 and more can only yield finite structures which is size of $mathcal{O} (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
-
-%In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 2 deterministically and moreover that the only infinite conformations which its oritatami system can yield is only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
-
-Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
-%Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
-For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$ that is foldable by $\Xi$. Hence $C_0 = \sigma$.
-
-Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$.
-The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1.
-There are just two ways to get stabilized at delay 1.
-One way is to be bound to another bead.
-The other way is through a $tunnel\ section$.
-A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
-Accordingly, how they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
-
-Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
-We call such a bead $p$ as $inside\ of\ a\ tunnel$ and such beads $p^\prime$ as $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel.
-If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor.
-In this way, $w[i]$ can get stabilized without being bound.
-
-%If a bead is stabilized through a tunnel section, then it can provide some bonds.
-Let us consider bonds of $C_i$.
-$C_i$ is represented $C = (W,P,H)$ where $|W| = i + n$ $C_i$ contains $\alpha \cdot (i + n) - 2|H|$ bonds because $C_i$ consists of $i + n$ beads and a bead has just $\alpha$ bonds and then $2 |H|$ of the those bonds are already used.
-However, even if a bead has an available bond, $w[j]$ $(j > i)$ might not be able to use this bond because the bond has possibility that it is blocked by transcripts $w[i+1..j-1]$.
-Number of $binding\ capabilities$ does not contain that case so that it is at most $\alpha \cdot (i + n) - 2|H|$.
-
-We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$.
-We define $binding\ capability$ with reachable.
-
-\begin{definition}[binding capability]
-Let $B_i$ be $( \{ (h, i) | {}^\forall h < i \} \cup \{ (i, j) | {}^\forall j > i \}) \cap H$.
-Moreover, let $R_i$ be a set of neighbors of $w[i]$ that are free and reachable from $C_j$ where $C_j$ is a conformation which stabilized until $w[j]$.
- We represent the number of binding capabilities of a conformation $C_j$ as $\#bc(C_j)$. $\#bc(C_j)$ is defined by $\sum^{j}_{k=-n+1} \min \{ |B_k|, |R_k|  \}$.
-\end{definition}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw (0:0) circle [radius=0.05];
-      \draw (0:1) circle [radius=0.05];
-      \draw (180:1) circle [radius=0.05];
-      \node[above] at (0:1) { $p^\prime$ };
-      \node[above] at (0:0) { $p$ };
-      \node[above] at (180:1) { $p^\prime$ };
-
-      \fill (60 : 1) circle [radius=0.1];
-      \fill (-60 : 1) circle [radius=0.1];
-      \fill (120 : 1) circle [radius=0.1];
-      \fill (-120 : 1) circle [radius=0.1];
-      \node[above] at (60 :1) { $a_{j_1}$ };
-      \node[above] at (-60 :1) { $a_{j_2}$ };
-      \node[above] at (120 :1) { $a_{j_3}$ };
-      \node[above] at (-120 :1) { $a_{j_4}$ };
-
-      \begin{scope}[shift=(0:5)]
-        \fill[blue] (0:0) circle [radius=0.1];
-        \draw (0:1) circle [radius=0.05];
-        \fill (180:1) circle [radius=0.1];
-        \node[above] at (180:1.2) { $a_{i-2}$ };
-        \node[above] at (0:0) { $a_{i-1}$ };
-        \draw[->, blue] (180:0.9) -- (180:0.1);
-
-        \fill (60 : 1) circle [radius=0.1];
-        \fill (-60 : 1) circle [radius=0.1];
-        \fill (120 : 1) circle [radius=0.1];
-        \fill (-120 : 1) circle [radius=0.1];
-        \node[above] at (60 :1) { $a_{j_1}$ };
-        \node[above] at (-60 :1) { $a_{j_2}$ };
-        \node[above] at (120 :1) { $a_{j_3}$ };
-        \node[above] at (-120 :1) { $a_{j_4}$ };
-      \end{scope}
-      \begin{scope}[shift=(0:10)]
-        \fill (0:0) circle [radius=0.1];
-        \fill[blue] (0:1) circle [radius=0.1];
-        \fill (180:1) circle [radius=0.1];
-        \node[above] at (180:1) { $a_{i-2}$ };
-        \node[above] at (0:0) { $a_{i-1}$ };
-        \node[above] at (0:1) { $a_i$ };
-        \draw[->] (180:0.9) -- (180:0.1);
-        \draw[->,blue] (0:0.1) -- (0:0.9);
-
-        \fill (60 : 1) circle [radius=0.1];
-        \fill (-60 : 1) circle [radius=0.1];
-        \fill (120 : 1) circle [radius=0.1];
-        \fill (-120 : 1) circle [radius=0.1];
-        \node[above] at (60 :1) { $a_{j_1}$ };
-        \node[above] at (-60 :1) { $a_{j_2}$ };
-        \node[above] at (120 :1) { $a_{j_3}$ };
-        \node[above] at (-120 :1) { $a_{j_4}$ };
-      \end{scope}
-    \end{tikzpicture} 
-    \caption{Through a tunnel section}
-    \label{TTT_tunnel_intro}
-  \end{center}
-\end{figure}
-
-\begin{theorem}[Tunnel Troll Theorem]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there are indices $i$ and $j$ such that $S[i..j+1] = bt^{j-i}b$, then $\#bc(C_i)$ > $\#bc(C_j)$.
-\end{theorem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\proof%{Proof of Tunnel Troll Theorem}
-Assume $\Xi$ is deterministic.
-%How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
-Each of beads in transcript are bound either inside of tunnel or outside (Fig.
-\ref{TTT_position}).
-If a bead is stabilized at inside of tunnel, then its successor is already decided the position either inside of a tunnel or outside.
-Moreover, If a bead is stabilized at outside of a tunnel, then its position is an entrance of a tunnel or otherwise.
-
-Tunnel sections have three possible shape with considering symmetry such as straight, acute turn and obtuse turn (Fig.
-\ref{TTT_tunnel}).
-%Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Fig.
-\ref{TTT_enterpoint}).
-
-Let us consider each of cases of tunnel A, B, and C. Accordingly, We use lemma \ref{TTT_neighbor_lemma}
-
-\begin{lemma}
-\label{TTT_neighbor_lemma}
-If a bead does not have any bond, then neighbors of it must be occupied by $\alpha + 2$ beads at $\delta = 1$ and unary except first and last beads.
-\end{lemma}
-
-\begin{proof}[lemma \ref{TTT_neighbor_lemma}]
-A bead in transcript needs predecessor and successor except first and last beads.
-If the bead does not have ant bond, then it use hand with $\alpha$ neighbors.
-Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
-\end{proof}
-
-Let us consider tunnel sections only tunnel A and B.
-See Fig.
-\ref{TTT_position}.
-From appendix (Entrance of Tunnel A, B and Exit of Tunnel), we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successor\ in\ outside$.
-
-%The sequence $S$ can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+ \cup bt^+bt^+$.
-
-Next, we consider on tunnel C section.
-If $w[i]$ is stabilized by tunnel C and $S[i+1]$ is $t$, then $w[i+1]$ is stabilized by tunnel A or B because if $w[i+1]$ is stabilized by tunnel C, then $C_{i+1}$ is a terminal.
-Hence, tunnel C section is divided cases such as Figure \ref{TTT_tunnelC_graph}.
-Cases of $S[i...] = bt^l (l \geq 2)$ are already considered (Upper).
-According to appendix (Tunnel C), cases of $S[i..i+2] = btb$ also consume some binding capabilities (Lower).
-
-Thus, if a bead is stabilized through a tunnel section, then it consume some binging capabilities.
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{ccc}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (0:1) {$p^\prime$};
-
-            \foreach \theta in {0,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,120,-120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel A};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-60:1) {$p^\prime$};
-
-            \foreach \theta in {-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {0,60,120,-120}{
- 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel B};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-1200:1) {$p^\prime$};
-
-            \foreach \theta in {-120,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {0,60,-60,120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel C};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{All possible tunnel sections: straight, acute turn, and obtuse turn}
-    \label{TTT_tunnel}
-  \end{center}
-\end{figure}
-
-%\begin{figure}
-%  \begin{center}
-%    \begin{tabular}{cc}
-%      
-%      \begin{minipage}{0.2\hsize}
-%      \centering
-%        \begin{tikzpicture}
-%
-%          \begin{scope}[xshift=1cm, yshift=2cm]
-%            \fill(0,0) circle [radius=0.1];
-%            \node[above] at (180:1.2) {$p^\prime$};
-%            
-%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
-%            
-%            
-%            \foreach \theta in {120,-120}{
-%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-%            }
-%
-%            \draw[->] (-1.1,0) -- (-0.1,0);
-%          \end{scope}
-%
-%          \node at (0.25,0) {Tunnel A,B};
-%        \end{tikzpicture}
-%      \end{minipage}
-%
-%      \begin{minipage}{0.2\hsize}
-%      \centering
-%        \begin{tikzpicture}
-%
-%          \begin{scope}[xshift=1cm, yshift=2cm]
-%            \fill(0,0) circle [radius=0.1];
-%            \node[above] at (180:1.2) {$p^\prime$};
-%
-%            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
-%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
-%            
-%            
-%            \foreach \theta in {120}{
-%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-%            }
-%
-%            \draw[->] (-1.1,0) -- (-0.1,0);
-%          \end{scope}
-%
-%          \node at (0.25,0) {Tunnel C};
-%        \end{tikzpicture}
-%      \end{minipage}
-%
-%    \end{tabular}
-%    \caption{Entrance of a tunnel}
-%    \label{TTT_enterpoint}
-%  \end{center}
-%\end{figure}
-
-%\begin{figure}
-%  \begin{center}
-%    \begin{tikzpicture}
-%      \draw[thick]
-%      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
-%      \node at(2.5,1) {Outside};
-%      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
-%      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
-%
-%      
-%      
-%      \draw[thick]
-%      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
-%      \node at(10.5,1) {Inside of a tunnel};
-%      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-%      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
-%
-%      \draw[->]
-%      (outside) edge [bend left] node[left] {$b$} (enter)
-%                edge [loop left] node[left] {$b$} (outside)
-%      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
-%                edge [bend left] node[above] {$b$} (next-outside)
-%                edge [bend left] node[right] {$b$}  (outside)
-%      (next-tunnel) edge         node[right] {$t$} (next-outside)
-%                edge [loop right]node[below] {$t$}    (next-tunnel)
-%      (next-outside) edge[bend left] node[above] {$t$}  (outside)
-%                edge [bend left]     node[above] {$t$}(enter)
-%      ;
-%      
-%    \end{tikzpicture}
-%    \caption{Cases on position of a bead}
-%    \label{TTT_position1}
-%  \end{center}
-%\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw[thick, gray]
-      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
-      \node at(2,1) {Outside};
-      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
-      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
-
-      \draw[thick, gray]
-      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
-      \node at(9,1) {Inside of a tunnel};
-      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
-
-      \draw[->]
-      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
-                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
-      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
-                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
-                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
-      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
-                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
-      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
-                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
-      ;
-
-    \end{tikzpicture}
-    \caption{Increment on Tunnel A,B}
-    \label{TTT_position}
-  \end{center}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
-      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
-      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
-      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
-      \draw[->] (outside1)--(enter1);
-      \draw[->] (enter1)  --(inside1);
-      \draw[->] (inside1) --(exit1);
-
-      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
-      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
-      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
-      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
-      \draw[->] (outside2)--(enter2);
-      \draw[->] (enter2)  --(inside2);
-      \draw[->] (inside2) --(exit2);
-
-      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
-      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
-      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
-      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
-      \draw[->] (outside3)--(enter3);
-      \draw[->] (enter3)  --(inside3);
-      \draw[->] (inside3) --(exit3);
-
-      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
-      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
-      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
-      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
-      \draw[->] (outside4)--(enter4);
-      \draw[->] (enter4)  --(inside4);
-      \draw[->] (inside4) --(exit4);
-    \end{tikzpicture}
-    \caption{Case of Tunnel C}
-    \label{TTT_tunnelC_graph}
-  \end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%/////////////////////////////////////////////////
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Appendix of Tunnel Troll Theorem}
-\subsubsection{Entrance of TunnelA,B}
-
-Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
-Any cases in $\delta = 1, \alpha = 2$ consume some binding capabilities into the follows.
-
-\begin{itemize}
-\item{Case of $t_0$}\\
-  Let us consider points of $n_3,n_4$ either occupied or not.
-A point $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-If $n_3$ is free, then $p^\prime$ has to be bound to a bead except $n_1$ due to deterministically stabilize.
-In this situation, at least three neighbors of $n_1$ are free that is $n_1$ leave at least one bond from lemma \ref{TTT_neighbor_lemma}.
-Hence, $p^\prime$ must be bound to $n_1$.
-Thus, a case of $t_0$ consumes two binding capabilities and it does not supply any binding capabilities.
-
-\item{Case of $t_{\pm 60}$}\\
-  In this case, a point $n_4$ or $n_5$ is free, too.
-If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$.
-If $n_5$ is occupied, then $n_4$ is free.
-This time, $n_2$ has some binding capabilities so $p^\prime$ has to be bound to $n_2$.
-
-  In this situation, $p^\prime$ is able to supply a binding capability.
-if this capability is active, $p^\prime$ bind a bead into $n_4$ or $n_5$.
-However, $n_2$ and $n_3$ are exist in back bone.
-According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive.
-Thus, a case of $t_{\pm 60}$ consumes some binding capabilities.
-
-\item{Case of $t_{\pm 120}$}\\
-  Binding capabilities that $p^\prime$ supply are inactive according to Jordan curve theorem on $n_1$ and $n_2$.
-Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
-Thus, a case of $t_{\pm 120}$ consumes some binging capabilities.
-
-\end{itemize}
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{ccc}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-	 \draw[->,white] (120:0.8)--(120:0.1);%for adjustment
-
-            \fill[blue] (0,0) circle [radius=0.05];
-            \node[below] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,180}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {120,-120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (0:0.1)--(0:0.9);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-
-          \node at (0,-2) {$t_{0}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-
-            \fill(0,0) circle [radius=0.05];
-            \node[below] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {180,-120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (120:0.9)--(120:0.1);
-            \draw[->, blue] (0:0.1)--(0:0.9);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {$t_{\pm 60}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-            \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)}, blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {180,-120,120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (60:1.1)--(60:0.1);
-            \draw[->, blue] (0:0.1)--(0:1.1);
-
-            \node[transform canvas={shift=(0:1)},below] {$n_0$};
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {$t_{\pm 120}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Direction into a entrance}
-    \label{TTT_tunnel_direction}
-  \end{center}
-\end{figure}
-
-\subsubsection{Exit of Tunnel}
-
-Fig.\ref{TTT_tunnel_exit} exhibits all the two kinds of exit of tunnel. 
-At least one of point $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-
-\paragraph{$\delta = 1, \alpha = 2$}
- Any cases of $\delta = 1, \alpha = 2$ supply at most $a$ binding capabilities into follows where $a$ is number of predecessor of $p^\prime$ consumes binging capabilities.
-
-\begin{itemize}
-\item{Case of $n_1$ and $n_2$ are free}\\
-  This case can be regarded same situation as entrance.
-See Fig.\ref{TTT_tunnel_exit} (Left).
-Predecessor $n_5$ has to be bound $n_4$ and $n_5$ because each of $n_3$ and $n_4$ leave binding capabilities.
-Hence, at least $a=2$.
-This time, $\alpha = 2$ that is this case supply at most only $a$ binding capabilities.
-
-\item{Case of $c$ is occupied}\\
-  See Fig.\ref{TTT_tunnel_exit} (Right).
-If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$.
-Hence, at least $a=1$.
-This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied a successor of $p^\prime$.
-Therefore, this case supply at most only $a=1$ active binding capability.
-
-\end{itemize}
-
-\paragraph{$\delta = 1, \alpha \geq 3$}
-Any cases of $\delta = 1, \alpha \geq 3$ consume some binding capabilities into follows.
-
-\begin{itemize}
-\item{Case of $n_1$ and $n_2$ are free}\\
-  In $\alpha \geq 3$, if three neighbors of a bead leave, then it can supply two binding capabilities.
-Therefore Predecessor $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$, too.
-In this case, at least consumes four bindings and supplies at most two bindings.
-Thus, it consumes some binding capabilities, totally.
-
-\item{Case of $c$ is occupied}\\
-  In this case, $n_4$ leave at least two bindings and $n_3$, $n_1$ also leave at least one binding.
-Therefore $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$ also has to be bound $n_1$ and $n_4$.
-In this case, at least consumes four bindings and supplies at most one binding.
-Thus, it consumes some binding capabilities, totally.
-\end{itemize}
-
-\begin{figure}
-  \centering
-    \begin{tabular}{cc}
-
-      \begin{minipage}{0.48\linewidth}
-      \centering
-        \begin{tikzpicture}
-
-            \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {120,-120,180}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-            \draw (-60:1) circle [radius=0.05];
-            \draw (60:1) circle [radius=0.05];
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {Point $n_1$ and $n_2$ are free};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.48\linewidth}
-      \centering
-        \begin{tikzpicture}
-
-            \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {120,-120,180,60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-            \draw (-60:1) circle [radius=0.05];
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-
-            \node[transform canvas={shift=(0:1)},right] {$n_0$};
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {Point $n_1$ is occupied};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Exit of Tunnel}
-    \label{TTT_tunnel_exit}
-\end{figure}
-
-\subsubsection{Tunnel C}
-
-Assume $w[i]$ is a bead which stabilized by tunnel C. Let us consider kinds of stabilization $S[i-2..i] = tbt$ or $S[i-2..i] = bbt$ except cases of $w[i]$ is inside of tunnel A, B.
-
-\subsubsection{Case of $S[i-2..i] = tbt$}
-Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
-
-\begin{itemize}
-\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  In this figure, Bead $n_4$ has at least one binding so that $w[i-2]$ has to bound $n_4$.
-Moreover, $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
-On the other hand, $w[i]$ can supply two bindings but free neighbors of $w[i]$ are two points.
-One of them is occupied by a successor.
-Therefore $w[i]$ can only bind one of $n_5, n_6$ that is $w[i]$ supplies at most one binding.
-Thus, this case consumes some binding capabilities.
-
-\item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  This cases are divided on number of capabilities that $w[i-2]$ consumes.
-  \begin{itemize}
-  \item[-]{$w[i]$ does not consume any bindings}\\
-    $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
-$w[i]$ has to be bound to $w[i-2]$ because $w[i-2]$ has bindings.
-This time, let us consider either $n_4$ is occupied or not.
-If $n_4$ is occupied, then $w[i-2]$ has no active bindings that is this situation consumes some binding capabilities.
-If $n_4$ is free and $w[i+1]$ is stabilized in $n_4$, then $w[i-2]$ has to bind $w[i+1]$.
-Therefore, In this case, stabilization of $w[i-2..i+1]$ consumes some bindings.
-If $n_4$ is free and $w[i+1]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[i+1]$.
-Therefore, in this case consumes some bindings.
-Thus in this cases consume some binding capabilities.
-
-  \item[-]{$w_i$ consumes one binding}\\
-    In this case, $w_{i-1}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[i-2]$ and $w[i]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
-  \item[-]{$w_i$ consumes two bindings}\\
-    In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies two bindings. Thus, in this cases consume some binding capabilities.
-
-  \end{itemize}
-\end{itemize}
-\begin{figure}
-  \centering
-    \begin{tabular}{cc}
-
-      \begin{minipage}{0.48\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];
-
-          \foreach \theta in {60,-60,120,-120,180}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \fill[blue](0:1) circle [radius=0.05];
-          \draw[->, blue] (0:0.1)--(0:0.9);
-
-          \node[below] at (-60:1) {$n_4$};
-
-          \begin{scope}[shift=(0:2)]
-            \fill[blue](0,0) circle [radius=0.05];
-
-            \foreach \theta in {120,60,-60,0}{
-             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (-120:0.1)--(-120:0.9);
-
-            \node[below] at (180:1) {$w[i-2]$};
-            \node[above] at (0:0) {$w[i-1]$};
-            \node[right] at (-120:1) {$w[i]$};
-
-            \node[above] at (120:1) {$n_3$};
-            \node[above] at (60:1) {$n_2$};
-            \node[right] at (0:1) {$n_1$};
-
-            \begin{scope}[shift=(-120:1)]
-              \fill[blue](0,0) circle [radius=0.05];
-              \foreach \theta in {-120,-60}{
-                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-              }
-
-              \node[right] at (-120:1) {$n_5$};
-              \node[right] at (-60:1) {$n_6$};
-            \end{scope}
-
-          \end{scope}
-
-          \node at (1.2,-2.5) {Pattern 1};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.48\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \fill(0,0) circle [radius=0.1];
-
-          \foreach \theta in {60,0,120,-120,180}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \draw[->, blue] (-60:0.1)--(-60:0.9);
-
-          \begin{scope}[shift=(-60:1),shift=(0:1)]
-            \fill[blue](0,0) circle [radius=0.05];
-            \fill[blue](180:1) circle [radius=0.05];
-
-            \foreach \theta in {120,60,0,-60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (-120:0.1)--(-120:0.9);
-
-            \node[below] at (180:1) {$w[i-2]$};
-            \node[above] at (0:0) {$w[i-1]$};
-            \node[right] at (-120:1) {$w[i]$};
-
-            \node[above right] at (120:1) {$n_3$};
-            \node[right] at (60:1) {$n_2$};
-            \node[right] at (0:1) {$n_1$};
-
-            \begin{scope}[shift=(-120:1)]
-              \fill(0,0) circle [radius=0.05];
-              \foreach \theta in {180,-120,-60}{
-                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-              }
-
-              \node[right] at (180:1) {$n_4$};
-              \node[right] at (-120:1) {$n_5$};
-              \node[right] at (-60:1) {$n_6$};
-            \end{scope}
-
-          \end{scope}
-
-          \node at (1.25,-4) {Pattern 2};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Case of $S[i-2..i] = tbt$}
-    \label{TTT_tunnelC_enter_usingTunnel}
-\end{figure}
-
-\subsubsection{Case of $S[i-2..i] = bbt$}
-Let us consider number of consumed by $w[i-2]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
-
-\begin{itemize}
-\item{$w[i-2]$ consumes one binding}\\
-  In this situation, $w[i-2]$ supplies one active binding whereas $w[i]$ consumes this binding. In addition, $w[i-1]$ has to bound to one of $n_1, n_2, n_3$.
-  Thus, in this cases consume some binding capabilities.
-
-\item{$w[i-2]$ consumes two bindings}\\
-  In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
-\end{itemize}
-
-\begin{figure}
-  \begin{center}
-        \begin{tikzpicture}
-        \draw[->,white] (-70:0.1) -- (-70:3);
-          \foreach \theta in {60,-60,120,0}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \fill[blue](180:1) circle [radius=0.05];
-          \fill[blue](0:0) circle [radius=0.05];
-
-          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
-          \draw[->, blue] (180:0.9) -- (180:0.1);
-          \draw[->, blue] (-120:0.1) -- (-120:0.9);
-
-          \node[below left] at (180:1) {$w[i-2]$};
-          \node[above] at (0:0) {$w[i-1]$};
-          \node[below] at (-120:1) {$w[i]$};
-
-          \node[right] at (120:1) {$n_3$};
-          \node[right] at (60:1) {$n_2$};
-          \node[right] at (0:1) {$n_1$};
-
-          \begin{scope}[shift=(-120:1)]
-            \fill[blue](0,0) circle [radius=0.05];
-            \foreach \theta in {-120,-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-          \end{scope}
-        \end{tikzpicture}
-    \caption{Case of $S[i-2..i] = bbt$}
-    \label{TTT_tunnelC_enter_usingBond}
-  \end{center}
-\end{figure}
-
-\subsubsection{$\alpha = 2$}
-
-By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
-If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$.
-Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities.
-Therefore formula \ref{TTT_only_bond} hold.
-
-\begin{eqnarray}
-  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
-  \label{TTT_only_bond}
-\end{eqnarray}
-
-Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
-
-Let us consider the case of $v_k$ is $o$.
-See Fig.\ref{TTT_case_of_o}.
-$w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$.
-If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding.
-If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive that is $w[i-1]$ consumes two binding capabilities.
-Therefore, this case consumes binding capabilities.
-If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings.
-In addition, $w[i]$ and $w[i+1]$ consume at least one binding.
-Therefore this case consumes binding capabilities.
-Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.
-
-\begin{eqnarray}
-  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
-  \label{TTT_only_a}
-\end{eqnarray}
-
-\begin{eqnarray}
-  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
-  \label{TTT_structure}
-\end{eqnarray}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-
-      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
-
-      \fill[blue](0:0) circle [radius=0.05];
-      \fill[blue](0:1) circle [radius=0.05];
-      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
-
-      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
-      \draw[->, blue] (0:0.1) -- (0:0.9);
-      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
-
-      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-
-      \node[below] at (-120:1) {$w[i-2]$};
-      \node[above] at (0:0) {$w[i-1]$};
-      \node[below] at (0:1) {$w[i]$};
-      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
-
-      \node[above] at (60:1) {$n_1$};
-      \node[below] at (-60:1) {$n_2$};
-
-    \end{tikzpicture}
-    \caption{Case of $S[i]$}
-    \label{TTT_case_of_o}
-  \end{center}
-\end{figure}
-
-\subsubsection{$\alpha = 3$}
-
-\begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only a finite structure whose size is $\mathcal{O}(n)$.
-\end{theorem}
-
-\begin{lemma}
-\label{TTT_a3_2b_lemma}
- Let $p$ be a point whose neighbors is occupied at least two point.
-If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
-\end{lemma}
-
-\begin{proof}[proof of lemma]
-Assume the transcript is stabilized until $w[i-1]$.
-One of neighbors of $p$ is not $w[i-1]$ where this bead regards $n_1$.
-If $w[i-1]$ include neighbors of $p$ and $w[i]$ is stabilized at another point of $p$ with one bond.
-Then, any neighbors do not have bond without $w[i-1]$.
-Neighbors of $n_1$ have to be occupied at least five according to lemma \ref{TTT_neighbor_lemma} and two of them include neighbors of $p$ where each of them regards $n_2, n_3$.
-In the same way, five neighbors of $n_2$ and $n_3$ are occupied and each of one of them includes neighbors of $p$ where they regard $n_4, n_5$.
-one of $n_5$'s neighbors includes neighbors of $p$ where it regards $n_6$.
-Then, any neighbors of $p$ are occupied.
-That is if some neighbors of $p$ are free, then there exists a bead which has bonds in neighbors.
-\end{proof}
-
-\begin{proof}
-Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
-Let us assume $w[i]$ is able to be stabilized with using one hand. Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$. Then, $w[i]$ can be also stabilized at $n_3$.
-
-\begin{paragraph}{Case of straight}
-\begin{itemize}
-\item[-] Case of $n_3$ is free\\
-According to assumption, $w[i]$ uses only one hand.
-Therefore, any neighbors of $n_3$ are occupied according to the lemma\ref{TTT_a3_2b_lemma}.
-$n_3$ and the point which is stabilized $w[i]$ are free so that $n_1$ has some bond by lemma\ref{TTT_neighbor_lemma}.
-Accordingly, this situation is non-deterministic.
-Thus, $n_3$ and $n_4$ have to be occupied because of symmetry.
-
-\item[-] Otherwise\\
-Because of  $S[i] = b$, at least one of $n_1$ and $n_2$ have to be free.
-Let us regard that $n_1$ is free.
-Neighbors of $n_1$ have to be occupied and at least two neighbors of $n_{-1}$ have to be free for $n_1$ and $w[i]$.
-According to lemma\ref{TTT_neighbor_lemma}, $n_{-1}$ have some hand.
-Therefore $w[i]$ can be also stabilized $n_1$ that is this situation is non-deterministic.
-Thus, one of $n_3$ and $n_4$ has to be free.
-\end{itemize}
-
-Therefore, this case is false.
-\end{paragraph}
-
-\begin{paragraph}{Case of obtuse}
-\begin{itemize}
-\item[-] Case of $n_3$ is free\\
-Any neighbors of $n_3$ have to be occupied but the point which is stabilized $w[i]$ is free. Thus $n_3$ has to be occupied.
-\item[-] Case of $n_4$ is free\\
-According to lemma\ref{TTT_a3_2b_lemma}, $n_2$ has to be occupied because $n_4$ is free.
-Also $n_0$ has to be occupied from lemma\ref{TTT_neighbor_lemma}.
-Thus, only one of $n_0, n_3$ leave some hands or both of them do not leave any hands because $w[i]$ use only one bond.\\
-If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied.
-Also $n_{-3}$ must not have any hands so that $n_{-2}$ is occupied and also $n_{-1}$ is occupied.
-Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
-If $n_3$ has some hands, then $n_0$ does not have any hands so that $n_{-1}$ is occupied.
-In the same previous way, any $n_{-2}, n_{-3}$ are occupied.
-Therefore any neighbors of $w[i]$ are occupied.\\
-If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied.
-If one of $n_{-1}, n_{-3}$ has some hands, the other does not have any hands so that $n_{-2}$ is occupied.
-If both of $n_{-1}, n_{-3}$ do not have any hands, $n_{-2}$ has to be occupied and $n_{-2}$ has some hands.Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
-Thus $n_3$ has to be occupied in order to yield infinite structures.
-\item[-] Case of $n_2$ is free\\
-Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied.
-Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_2$ has to be occupied.
-\item[-] Case of $n_0$ is free\\
-Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied.
-Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_0$ has to be occupied.
-\end{itemize}
-
-Therefore, any situations contradict $S[i] = b$.
-
-\end{paragraph}
-
-\begin{paragraph}{Case of acute}
-\begin{itemize}
-\item[-] Case of $n_4$ is free\\
-$n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some hands according to lemma\ref{TTT_neighbor_lemma}.
-However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
-\item[-] Case of $n_2$ is free\\
-According to lemma\ref{TTT_a3_2b_lemma}, $n_0$ has to be occupied. $n_1$ has to be also occupied because of lemma\ref{TTT_neighbor_lemma}.
-We consider this case just like case of obtuse and that $n_4$ is free.
-Then if $w[i-2]$ binds $w[i]$, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
-If $n_1$ binds $w[i]$, this case is same.
-Also if $n_1$ and $w[i-2]$ do not have any hand, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
-Therefore, $w[i+1]$ cannot be provided.
-\item[-] Case of $n_0$ is free\\
-Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied.
-Any neighbors of $n_{1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_0$ has to be occupied.
-\item[-] Case of $n_1$ is free\\
-Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied.
-Any neighbors of $n_{-1}$ except $n_1$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_1$ has to be occupied.
-\end{itemize}
-
-Therefore, any situations contradict $S[i] = b$.
-\end{paragraph}\\
-
-Hence, assumption that w[i] is able to be stabilized with using one hand is false.
-Therefore, when w[i] is stabilized, w[i] uses at least two hands.
-\end{proof}
-
-\begin{figure}
-  \begin{center}
-  \begin{tabular}{c c c}
- \begin{minipage}{0.3\hsize}
- \centering
-    \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](0:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (0:0.1) -- (0:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (0:1) {$w_{[i]}$};
-
-	\foreach \theta in {60,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	 \draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
-    \end{tikzpicture}
-    \end{minipage}
-
-    \begin{minipage}{0.3\hsize}
-    \centering
-     \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](60:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (60:0.1) -- (60:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (60:1) {$w_{[i]}$};
-
-	\foreach \theta in {0,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	\draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
-	\draw [shift=(60:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(60:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-
- 	\node[right] at (0:1) {$n_0$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
-	\node[above, shift=(60:1)] at (60:1) {$n_{-2}$};
-	\node[above, shift=(60:1)] at (120:1) {$n_{-3}$};
-    \end{tikzpicture}
-    \end{minipage}
-
-    \begin{minipage}{0.3\hsize}
-        \centering
-     \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](120:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (120:0.1) -- (120:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (120:1) {$w_{[i]}$};
-
-	\foreach \theta in {0,60,-60,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	\draw [shift=(120:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(120:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(120:1), shift=(180:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-
- 	\node[right] at (0:1) {$n_0$};
-	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(120:1)] at (60:1) {$n_{-1}$};
-	\node[above, shift=(120:1)] at (120:1) {$n_{-2}$};
-	\node[above, shift=(120:1)] at (180:1) {$n_{-3}$};
-    \end{tikzpicture}
-    \end{minipage}
-    \end{tabular}
-    \caption{All possible directions of $w[i]$: straight, obtuse, acute.}
-    \label{TTT_a3_w}
-  \end{center}
-\end{figure}
-
-\subsubsection{$\alpha = 4$}
-\begin{theorem}[$\delta = 1, \alpha = 4$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only a finite structure whose size is $\mathcal{O}(n^2)$.
-\end{theorem}
-
-\begin{lemma}
-\label{TTT_a4_2b_lemma}
-Any beads which are already stabilized by some bonds use at least two bonds.
-\end{lemma}
-
-\begin{proof}[proof of lemma]
-Let us consider when $w[i]$ is stabilized by only one bond.
-See Fig.\ref{TTT_a4_lemma_fig}.
-According to lemma\ref{TTT_neighbor_lemma}, if $n_3$ is free, $w[i-2]$ has some hands.
-Thus, $n_4$ has to be occupied in order to stabilize deterministically.
-Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$.
-$n_1$ has some hands because $n_3$ is free.
-Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands.
-It contradict assumption.
-\end{proof}
-
-\begin{proof}
-According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds.
-Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized.
-See Fig.\ref{TTT_a4_first}.
-any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$.
-At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind.
-In this case, a point which is able to put a bead is only $n_2$.
-Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$.
-Hence oritatami system can yield only a finite structure whose size is $\mathcal{O}(n^2)$ in $\delta =1, \alpha = 4$.
-%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
-\end{proof}
-
-\begin{figure}
- \centering
-    \begin{tikzpicture}
-	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (0:1) {$n_0$};
-
-	\foreach \theta in {0,60,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-    \end{tikzpicture}
-    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
-    \label{TTT_a4_lemma_fig}
-\end{figure}
-
-\begin{figure}
- \centering
-    \begin{tikzpicture}
-	\fill[shift=(-120:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0), blue] (0,0) circle [radius=0.05];
-
-      \draw[dashed] (180:2) -- (0:2);
-      \draw[->, blue] (-120:0.9) -- (-120:0.1);
-
-	\node[below] at (-120:1) {$w_{[i-1]}$};
-	\node[above] at (180:0) {$w_{[i]}$};
-	\node[above] at (0:1) {$n_0$};
-
-	\foreach \theta in {0,60,-60,120,180}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[above] at (180:1) {$n_5$};
-
-	\node at (0:2.5) {$n+1$};
-    \end{tikzpicture}
-    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
-    \label{TTT_a4_first}
-\end{figure}
-
-%end of d = 1
-%//////////////////////////////////////////////////////% l.168 - 1326
-%//////////////////////////////////////////////////////%
-
-\section{Case of $\delta \geq 2$}
-
 \subsection{$\alpha = 1$, unary}
@@
 It is impossible to fix molecules on a side of an equilateral hexagon with a radius of $n+2$ and determine the only structure when there are only beads which are able to make a hydrogen bond in an equilateral hexagon with a radius of $n$.
-
-\end{document}

### 2018-11-30 paper.tex
separate in subfiles

--- 2018-11-24 paper.tex
@@
 
-\section{Case of $\delta = 1$}
+\section{Case of arity $1$}
 
-%//////////////////////////////////////////////////////%
-%//////////////////////////////////////////////////////%
-%Kohei
-%//////////////////////////////////////////////////////%
-%//////////////////////////////////////////////////////%l.168 - 1326
+\input{arity1}
 
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \fill (0,0) circle[radius = 0.1];
-      \fill (1.5,0) circle[radius = 0.1];
-      \fill (3,0) circle[radius = 0.1];
-      \fill (4.5,0) circle[radius = 0.1];
-      \fill (6,0) circle[radius = 0.1];
+\section{Case of delay $1$}
 
-      \draw[dashed] (0,0)--(1.5,0);
-      \draw[dashed] (1.5,0)--(3,0);
-      \draw[dashed] (3,0)--(4.5,0);
-      \draw[dashed] (4.5,0)--(6,0);
-      \draw[->] (0,0)--(60:0.75);
-      \draw[->] (1.5,0)--++(60:0.75);
-      \draw[->] (3,0)--++(60:0.75);
-      \draw[->] (4.5,0)--++(60:0.75);
-      \draw (0,0)--(60:1.5);
-      \draw (1.5,0)--++(60:1.5);
-      \draw (3,0)--++(60:1.5);
-      \draw (4.5,0)--++(60:1.5);
-
-      \begin{scope}[shift=(60:1.5)]
-        \fill (0,0) circle[radius = 0.1];
-        \fill (1.5,0) circle[radius = 0.1];
-        \fill (3,0) circle[radius = 0.1];
-        \fill (4.5,0) circle[radius = 0.1];
-        \draw[dashed] (0,0)--(1.5,0);
-        \draw[dashed] (1.5,0)--(3,0);
-        \draw[dashed] (3,0)--(4.5,0);
-        \draw[->] (0,0)--(-60:0.75);
-        \draw[->] (1.5,0)--++(-60:0.75);
-        \draw[->] (3,0)--++(-60:0.75);
-        \draw[->] (4.5,0)--++(-60:0.75);
-
-        \draw (0,0)--(-60:1.5);
-        \draw (1.5,0)--++(-60:1.5);
-        \draw (3,0)--++(-60:1.5);
-        \draw (4.5,0)--++(-60:1.5);
-      \end{scope}
-
-    \end{tikzpicture}
-    \caption{zig-zag conformation}
-    \label{TTT_zigzag}
-  \end{center}
-\end{figure}
-
-\subsection{Introduction}
-
-In this section, we consider on finiteness of structures produced deterministically at delay 1.
-In result, cases of arity 1 and 3 can only yield finite structures which is size of $\mathcal{O} (n)$, and cases of arity 4 and more can only yield finite structures which is size of $mathcal{O} (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
-
-%In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 2 deterministically and moreover that the only infinite conformations which its oritatami system can yield is only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
-
-Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
-%Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
-For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$ that is foldable by $\Xi$. Hence $C_0 = \sigma$.
-
-Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$.
-The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1.
-There are just two ways to get stabilized at delay 1.
-One way is to be bound to another bead.
-The other way is through a $tunnel\ section$.
-A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
-Accordingly, how they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
-
-Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
-We call such a bead $p$ as $inside\ of\ a\ tunnel$ and such beads $p^\prime$ as $entrance\ of\ a\ tunnel$ without a case that $p^\prime$ is inside of a tunnel.
-If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor.
-In this way, $w[i]$ can get stabilized without being bound.
-
-%If a bead is stabilized through a tunnel section, then it can provide some bonds.
-Let us consider bonds of $C_i$.
-$C_i$ is represented $C = (W,P,H)$ where $|W| = i + n$ $C_i$ contains $\alpha \cdot (i + n) - 2|H|$ bonds because $C_i$ consists of $i + n$ beads and a bead has just $\alpha$ bonds and then $2 |H|$ of the those bonds are already used.
-However, even if a bead has an available bond, $w[j]$ $(j > i)$ might not be able to use this bond because the bond has possibility that it is blocked by transcripts $w[i+1..j-1]$.
-Number of $binding\ capabilities$ does not contain that case so that it is at most $\alpha \cdot (i + n) - 2|H|$.
-
-We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$.
-We define $binding\ capability$ with reachable.
-
-\begin{definition}[binding capability]
-Let $B_i$ be $( \{ (h, i) | {}^\forall h < i \} \cup \{ (i, j) | {}^\forall j > i \}) \cap H$.
-Moreover, let $R_i$ be a set of neighbors of $w[i]$ that are free and reachable from $C_j$ where $C_j$ is a conformation which stabilized until $w[j]$.
- We represent the number of binding capabilities of a conformation $C_j$ as $\#bc(C_j)$. $\#bc(C_j)$ is defined by $\sum^{j}_{k=-n+1} \min \{ |B_k|, |R_k|  \}$.
-\end{definition}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw (0:0) circle [radius=0.05];
-      \draw (0:1) circle [radius=0.05];
-      \draw (180:1) circle [radius=0.05];
-      \node[above] at (0:1) { $p^\prime$ };
-      \node[above] at (0:0) { $p$ };
-      \node[above] at (180:1) { $p^\prime$ };
-
-      \fill (60 : 1) circle [radius=0.1];
-      \fill (-60 : 1) circle [radius=0.1];
-      \fill (120 : 1) circle [radius=0.1];
-      \fill (-120 : 1) circle [radius=0.1];
-      \node[above] at (60 :1) { $a_{j_1}$ };
-      \node[above] at (-60 :1) { $a_{j_2}$ };
-      \node[above] at (120 :1) { $a_{j_3}$ };
-      \node[above] at (-120 :1) { $a_{j_4}$ };
-
-      \begin{scope}[shift=(0:5)]
-        \fill[blue] (0:0) circle [radius=0.1];
-        \draw (0:1) circle [radius=0.05];
-        \fill (180:1) circle [radius=0.1];
-        \node[above] at (180:1.2) { $a_{i-2}$ };
-        \node[above] at (0:0) { $a_{i-1}$ };
-        \draw[->, blue] (180:0.9) -- (180:0.1);
-
-        \fill (60 : 1) circle [radius=0.1];
-        \fill (-60 : 1) circle [radius=0.1];
-        \fill (120 : 1) circle [radius=0.1];
-        \fill (-120 : 1) circle [radius=0.1];
-        \node[above] at (60 :1) { $a_{j_1}$ };
-        \node[above] at (-60 :1) { $a_{j_2}$ };
-        \node[above] at (120 :1) { $a_{j_3}$ };
-        \node[above] at (-120 :1) { $a_{j_4}$ };
-      \end{scope}
-      \begin{scope}[shift=(0:10)]
-        \fill (0:0) circle [radius=0.1];
-        \fill[blue] (0:1) circle [radius=0.1];
-        \fill (180:1) circle [radius=0.1];
-        \node[above] at (180:1) { $a_{i-2}$ };
-        \node[above] at (0:0) { $a_{i-1}$ };
-        \node[above] at (0:1) { $a_i$ };
-        \draw[->] (180:0.9) -- (180:0.1);
-        \draw[->,blue] (0:0.1) -- (0:0.9);
-
-        \fill (60 : 1) circle [radius=0.1];
-        \fill (-60 : 1) circle [radius=0.1];
-        \fill (120 : 1) circle [radius=0.1];
-        \fill (-120 : 1) circle [radius=0.1];
-        \node[above] at (60 :1) { $a_{j_1}$ };
-        \node[above] at (-60 :1) { $a_{j_2}$ };
-        \node[above] at (120 :1) { $a_{j_3}$ };
-        \node[above] at (-120 :1) { $a_{j_4}$ };
-      \end{scope}
-    \end{tikzpicture} 
-    \caption{Through a tunnel section}
-    \label{TTT_tunnel_intro}
-  \end{center}
-\end{figure}
-
-\begin{theorem}[Tunnel Troll Theorem]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha \geq 2$. If there are indices $i$ and $j$ such that $S[i..j+1] = bt^{j-i}b$, then $\#bc(C_i)$ > $\#bc(C_j)$.
-\end{theorem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\proof%{Proof of Tunnel Troll Theorem}
-Assume $\Xi$ is deterministic.
-%How they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
-Each of beads in transcript are bound either inside of tunnel or outside (Fig.
-\ref{TTT_position}).
-If a bead is stabilized at inside of tunnel, then its successor is already decided the position either inside of a tunnel or outside.
-Moreover, If a bead is stabilized at outside of a tunnel, then its position is an entrance of a tunnel or otherwise.
-
-Tunnel sections have three possible shape with considering symmetry such as straight, acute turn and obtuse turn (Fig.
-\ref{TTT_tunnel}).
-%Let us focus entrances of a tunnel such as $p^\prime$, then Entrances have two possible shape (Fig.
-\ref{TTT_enterpoint}).
-
-Let us consider each of cases of tunnel A, B, and C. Accordingly, We use lemma \ref{TTT_neighbor_lemma}
-
-\begin{lemma}
-\label{TTT_neighbor_lemma}
-If a bead does not have any bond, then neighbors of it must be occupied by $\alpha + 2$ beads at $\delta = 1$ and unary except first and last beads.
-\end{lemma}
-
-\begin{proof}[lemma \ref{TTT_neighbor_lemma}]
-A bead in transcript needs predecessor and successor except first and last beads.
-If the bead does not have ant bond, then it use hand with $\alpha$ neighbors.
-Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
-\end{proof}
-
-Let us consider tunnel sections only tunnel A and B.
-See Fig.
-\ref{TTT_position}.
-From appendix (Entrance of Tunnel A, B and Exit of Tunnel), we add maximum number which each transitions provide binding capabilities for each edge where $a$ is number of consuming binding capabilities when the bead is stabilized at position of $successor\ in\ outside$.
-
-%The sequence $S$ can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+ \cup bt^+bt^+$.
-
-Next, we consider on tunnel C section.
-If $w[i]$ is stabilized by tunnel C and $S[i+1]$ is $t$, then $w[i+1]$ is stabilized by tunnel A or B because if $w[i+1]$ is stabilized by tunnel C, then $C_{i+1}$ is a terminal.
-Hence, tunnel C section is divided cases such as Figure \ref{TTT_tunnelC_graph}.
-Cases of $S[i...] = bt^l (l \geq 2)$ are already considered (Upper).
-According to appendix (Tunnel C), cases of $S[i..i+2] = btb$ also consume some binding capabilities (Lower).
-
-Thus, if a bead is stabilized through a tunnel section, then it consume some binging capabilities.
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{ccc}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (0:1) {$p^\prime$};
-
-            \foreach \theta in {0,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,120,-120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel A};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-60:1) {$p^\prime$};
-
-            \foreach \theta in {-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {0,60,120,-120}{
- 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel B};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-1200:1) {$p^\prime$};
-
-            \foreach \theta in {-120,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {0,60,-60,120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel C};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{All possible tunnel sections: straight, acute turn, and obtuse turn}
-    \label{TTT_tunnel}
-  \end{center}
-\end{figure}
-
-%\begin{figure}
-%  \begin{center}
-%    \begin{tabular}{cc}
-%      
-%      \begin{minipage}{0.2\hsize}
-%      \centering
-%        \begin{tikzpicture}
-%
-%          \begin{scope}[xshift=1cm, yshift=2cm]
-%            \fill(0,0) circle [radius=0.1];
-%            \node[above] at (180:1.2) {$p^\prime$};
-%            
-%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
-%            
-%            
-%            \foreach \theta in {120,-120}{
-%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-%            }
-%
-%            \draw[->] (-1.1,0) -- (-0.1,0);
-%          \end{scope}
-%
-%          \node at (0.25,0) {Tunnel A,B};
-%        \end{tikzpicture}
-%      \end{minipage}
-%
-%      \begin{minipage}{0.2\hsize}
-%      \centering
-%        \begin{tikzpicture}
-%
-%          \begin{scope}[xshift=1cm, yshift=2cm]
-%            \fill(0,0) circle [radius=0.1];
-%            \node[above] at (180:1.2) {$p^\prime$};
-%
-%            \draw[transform canvas={shift=(-120:1.2)}](0,0) circle [radius=0.1];
-%            \fill[transform canvas={shift=(180:1.2)}](0,0) circle [radius=0.1];
-%            
-%            
-%            \foreach \theta in {120}{
-%              \draw[transform canvas={shift=(\theta:1.2)}](-0.1,-0.1)--(0.1,0.1);
-%              \draw[transform canvas={shift=(\theta:1.2)}](0.1,-0.1)--(-0.1,0.1);
-%            }
-%
-%            \draw[->] (-1.1,0) -- (-0.1,0);
-%          \end{scope}
-%
-%          \node at (0.25,0) {Tunnel C};
-%        \end{tikzpicture}
-%      \end{minipage}
-%
-%    \end{tabular}
-%    \caption{Entrance of a tunnel}
-%    \label{TTT_enterpoint}
-%  \end{center}
-%\end{figure}
-
-%\begin{figure}
-%  \begin{center}
-%    \begin{tikzpicture}
-%      \draw[thick]
-%      (1.3,1)--(0,1)--(0,5)--(5,5)--(5,1)--(3.7,1);
-%      \node at(2.5,1) {Outside};
-%      \node at (2.5,4) [rectangle, draw,rounded corners] (enter) {Entrance of a tunnel};
-%      \node at(2.5,2) [rectangle, draw, rounded corners] (outside) {Otherwise};
-%
-%      
-%      
-%      \draw[thick]
-%      (9.3,1)--(8,1)--(8,5)--(13,5)--(13,1)--(11.7,1);
-%      \node at(10.5,1) {Inside of a tunnel};
-%      \node at(10.5,4) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-%      \node at(10.5,2) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
-%
-%      \draw[->]
-%      (outside) edge [bend left] node[left] {$b$} (enter)
-%                edge [loop left] node[left] {$b$} (outside)
-%      (enter)   edge [bend left] node[above] {$b$} (next-tunnel)
-%                edge [bend left] node[above] {$b$} (next-outside)
-%                edge [bend left] node[right] {$b$}  (outside)
-%      (next-tunnel) edge         node[right] {$t$} (next-outside)
-%                edge [loop right]node[below] {$t$}    (next-tunnel)
-%      (next-outside) edge[bend left] node[above] {$t$}  (outside)
-%                edge [bend left]     node[above] {$t$}(enter)
-%      ;
-%      
-%    \end{tikzpicture}
-%    \caption{Cases on position of a bead}
-%    \label{TTT_position1}
-%  \end{center}
-%\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw[thick, gray]
-      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
-      \node at(2,1) {Outside};
-      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
-      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
-
-      \draw[thick, gray]
-      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
-      \node at(9,1) {Inside of a tunnel};
-      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
-
-      \draw[->]
-      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
-                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
-      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
-                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
-                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
-      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
-                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
-      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
-                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
-      ;
-
-    \end{tikzpicture}
-    \caption{Increment on Tunnel A,B}
-    \label{TTT_position}
-  \end{center}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
-      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
-      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
-      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
-      \draw[->] (outside1)--(enter1);
-      \draw[->] (enter1)  --(inside1);
-      \draw[->] (inside1) --(exit1);
-
-      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
-      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
-      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
-      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
-      \draw[->] (outside2)--(enter2);
-      \draw[->] (enter2)  --(inside2);
-      \draw[->] (inside2) --(exit2);
-
-      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
-      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
-      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
-      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
-      \draw[->] (outside3)--(enter3);
-      \draw[->] (enter3)  --(inside3);
-      \draw[->] (inside3) --(exit3);
-
-      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
-      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
-      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
-      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
-      \draw[->] (outside4)--(enter4);
-      \draw[->] (enter4)  --(inside4);
-      \draw[->] (inside4) --(exit4);
-    \end{tikzpicture}
-    \caption{Case of Tunnel C}
-    \label{TTT_tunnelC_graph}
-  \end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%/////////////////////////////////////////////////
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Appendix of Tunnel Troll Theorem}
-\subsubsection{Entrance of TunnelA,B}
-
-Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
-Any cases in $\delta = 1, \alpha = 2$ consume some binding capabilities into the follows.
-
-\begin{itemize}
-\item{Case of $t_0$}\\
-  Let us consider points of $n_3,n_4$ either occupied or not.
-A point $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-If $n_3$ is free, then $p^\prime$ has to be bound to a bead except $n_1$ due to deterministically stabilize.
-In this situation, at least three neighbors of $n_1$ are free that is $n_1$ leave at least one bond from lemma \ref{TTT_neighbor_lemma}.
-Hence, $p^\prime$ must be bound to $n_1$.
-Thus, a case of $t_0$ consumes two binding capabilities and it does not supply any binding capabilities.
-
-\item{Case of $t_{\pm 60}$}\\
-  In this case, a point $n_4$ or $n_5$ is free, too.
-If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$.
-If $n_5$ is occupied, then $n_4$ is free.
-This time, $n_2$ has some binding capabilities so $p^\prime$ has to be bound to $n_2$.
-
-  In this situation, $p^\prime$ is able to supply a binding capability.
-if this capability is active, $p^\prime$ bind a bead into $n_4$ or $n_5$.
-However, $n_2$ and $n_3$ are exist in back bone.
-According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive.
-Thus, a case of $t_{\pm 60}$ consumes some binding capabilities.
-
-\item{Case of $t_{\pm 120}$}\\
-  Binding capabilities that $p^\prime$ supply are inactive according to Jordan curve theorem on $n_1$ and $n_2$.
-Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
-Thus, a case of $t_{\pm 120}$ consumes some binging capabilities.
-
-\end{itemize}
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{ccc}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-	 \draw[->,white] (120:0.8)--(120:0.1);%for adjustment
-
-            \fill[blue] (0,0) circle [radius=0.05];
-            \node[below] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,180}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {120,-120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (0:0.1)--(0:0.9);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-
-          \node at (0,-2) {$t_{0}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-
-            \fill(0,0) circle [radius=0.05];
-            \node[below] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {180,-120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (120:0.9)--(120:0.1);
-            \draw[->, blue] (0:0.1)--(0:0.9);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {$t_{\pm 60}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-            \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)}, blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {180,-120,120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (60:1.1)--(60:0.1);
-            \draw[->, blue] (0:0.1)--(0:1.1);
-
-            \node[transform canvas={shift=(0:1)},below] {$n_0$};
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {$t_{\pm 120}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Direction into a entrance}
-    \label{TTT_tunnel_direction}
-  \end{center}
-\end{figure}
-
-\subsubsection{Exit of Tunnel}
-
-Fig.\ref{TTT_tunnel_exit} exhibits all the two kinds of exit of tunnel. 
-At least one of point $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-
-\paragraph{$\delta = 1, \alpha = 2$}
- Any cases of $\delta = 1, \alpha = 2$ supply at most $a$ binding capabilities into follows where $a$ is number of predecessor of $p^\prime$ consumes binging capabilities.
-
-\begin{itemize}
-\item{Case of $n_1$ and $n_2$ are free}\\
-  This case can be regarded same situation as entrance.
-See Fig.\ref{TTT_tunnel_exit} (Left).
-Predecessor $n_5$ has to be bound $n_4$ and $n_5$ because each of $n_3$ and $n_4$ leave binding capabilities.
-Hence, at least $a=2$.
-This time, $\alpha = 2$ that is this case supply at most only $a$ binding capabilities.
-
-\item{Case of $c$ is occupied}\\
-  See Fig.\ref{TTT_tunnel_exit} (Right).
-If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$.
-Hence, at least $a=1$.
-This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied a successor of $p^\prime$.
-Therefore, this case supply at most only $a=1$ active binding capability.
-
-\end{itemize}
-
-\paragraph{$\delta = 1, \alpha \geq 3$}
-Any cases of $\delta = 1, \alpha \geq 3$ consume some binding capabilities into follows.
-
-\begin{itemize}
-\item{Case of $n_1$ and $n_2$ are free}\\
-  In $\alpha \geq 3$, if three neighbors of a bead leave, then it can supply two binding capabilities.
-Therefore Predecessor $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$, too.
-In this case, at least consumes four bindings and supplies at most two bindings.
-Thus, it consumes some binding capabilities, totally.
-
-\item{Case of $c$ is occupied}\\
-  In this case, $n_4$ leave at least two bindings and $n_3$, $n_1$ also leave at least one binding.
-Therefore $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$ also has to be bound $n_1$ and $n_4$.
-In this case, at least consumes four bindings and supplies at most one binding.
-Thus, it consumes some binding capabilities, totally.
-\end{itemize}
-
-\begin{figure}
-  \centering
-    \begin{tabular}{cc}
-
-      \begin{minipage}{0.48\linewidth}
-      \centering
-        \begin{tikzpicture}
-
-            \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {120,-120,180}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-            \draw (-60:1) circle [radius=0.05];
-            \draw (60:1) circle [radius=0.05];
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {Point $n_1$ and $n_2$ are free};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.48\linewidth}
-      \centering
-        \begin{tikzpicture}
-
-            \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {120,-120,180,60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-            \draw (-60:1) circle [radius=0.05];
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-
-            \node[transform canvas={shift=(0:1)},right] {$n_0$};
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {Point $n_1$ is occupied};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Exit of Tunnel}
-    \label{TTT_tunnel_exit}
-\end{figure}
-
-\subsubsection{Tunnel C}
-
-Assume $w[i]$ is a bead which stabilized by tunnel C. Let us consider kinds of stabilization $S[i-2..i] = tbt$ or $S[i-2..i] = bbt$ except cases of $w[i]$ is inside of tunnel A, B.
-
-\subsubsection{Case of $S[i-2..i] = tbt$}
-Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
-
-\begin{itemize}
-\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  In this figure, Bead $n_4$ has at least one binding so that $w[i-2]$ has to bound $n_4$.
-Moreover, $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
-On the other hand, $w[i]$ can supply two bindings but free neighbors of $w[i]$ are two points.
-One of them is occupied by a successor.
-Therefore $w[i]$ can only bind one of $n_5, n_6$ that is $w[i]$ supplies at most one binding.
-Thus, this case consumes some binding capabilities.
-
-\item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  This cases are divided on number of capabilities that $w[i-2]$ consumes.
-  \begin{itemize}
-  \item[-]{$w[i]$ does not consume any bindings}\\
-    $w[i-1]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically.
-$w[i]$ has to be bound to $w[i-2]$ because $w[i-2]$ has bindings.
-This time, let us consider either $n_4$ is occupied or not.
-If $n_4$ is occupied, then $w[i-2]$ has no active bindings that is this situation consumes some binding capabilities.
-If $n_4$ is free and $w[i+1]$ is stabilized in $n_4$, then $w[i-2]$ has to bind $w[i+1]$.
-Therefore, In this case, stabilization of $w[i-2..i+1]$ consumes some bindings.
-If $n_4$ is free and $w[i+1]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[i+1]$.
-Therefore, in this case consumes some bindings.
-Thus in this cases consume some binding capabilities.
-
-  \item[-]{$w_i$ consumes one binding}\\
-    In this case, $w_{i-1}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[i-2]$ and $w[i]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
-  \item[-]{$w_i$ consumes two bindings}\\
-    In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies two bindings. Thus, in this cases consume some binding capabilities.
-
-  \end{itemize}
-\end{itemize}
-\begin{figure}
-  \centering
-    \begin{tabular}{cc}
-
-      \begin{minipage}{0.48\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];
-
-          \foreach \theta in {60,-60,120,-120,180}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \fill[blue](0:1) circle [radius=0.05];
-          \draw[->, blue] (0:0.1)--(0:0.9);
-
-          \node[below] at (-60:1) {$n_4$};
-
-          \begin{scope}[shift=(0:2)]
-            \fill[blue](0,0) circle [radius=0.05];
-
-            \foreach \theta in {120,60,-60,0}{
-             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (-120:0.1)--(-120:0.9);
-
-            \node[below] at (180:1) {$w[i-2]$};
-            \node[above] at (0:0) {$w[i-1]$};
-            \node[right] at (-120:1) {$w[i]$};
-
-            \node[above] at (120:1) {$n_3$};
-            \node[above] at (60:1) {$n_2$};
-            \node[right] at (0:1) {$n_1$};
-
-            \begin{scope}[shift=(-120:1)]
-              \fill[blue](0,0) circle [radius=0.05];
-              \foreach \theta in {-120,-60}{
-                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-              }
-
-              \node[right] at (-120:1) {$n_5$};
-              \node[right] at (-60:1) {$n_6$};
-            \end{scope}
-
-          \end{scope}
-
-          \node at (1.2,-2.5) {Pattern 1};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.48\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \fill(0,0) circle [radius=0.1];
-
-          \foreach \theta in {60,0,120,-120,180}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \draw[->, blue] (-60:0.1)--(-60:0.9);
-
-          \begin{scope}[shift=(-60:1),shift=(0:1)]
-            \fill[blue](0,0) circle [radius=0.05];
-            \fill[blue](180:1) circle [radius=0.05];
-
-            \foreach \theta in {120,60,0,-60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (-120:0.1)--(-120:0.9);
-
-            \node[below] at (180:1) {$w[i-2]$};
-            \node[above] at (0:0) {$w[i-1]$};
-            \node[right] at (-120:1) {$w[i]$};
-
-            \node[above right] at (120:1) {$n_3$};
-            \node[right] at (60:1) {$n_2$};
-            \node[right] at (0:1) {$n_1$};
-
-            \begin{scope}[shift=(-120:1)]
-              \fill(0,0) circle [radius=0.05];
-              \foreach \theta in {180,-120,-60}{
-                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-              }
-
-              \node[right] at (180:1) {$n_4$};
-              \node[right] at (-120:1) {$n_5$};
-              \node[right] at (-60:1) {$n_6$};
-            \end{scope}
-
-          \end{scope}
-
-          \node at (1.25,-4) {Pattern 2};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Case of $S[i-2..i] = tbt$}
-    \label{TTT_tunnelC_enter_usingTunnel}
-\end{figure}
-
-\subsubsection{Case of $S[i-2..i] = bbt$}
-Let us consider number of consumed by $w[i-2]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
-
-\begin{itemize}
-\item{$w[i-2]$ consumes one binding}\\
-  In this situation, $w[i-2]$ supplies one active binding whereas $w[i]$ consumes this binding. In addition, $w[i-1]$ has to bound to one of $n_1, n_2, n_3$.
-  Thus, in this cases consume some binding capabilities.
-
-\item{$w[i-2]$ consumes two bindings}\\
-  In this case, $w[i-2]$ already consumes two binding. $w[i-1]$ has to be bound. $w[i]$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
-\end{itemize}
-
-\begin{figure}
-  \begin{center}
-        \begin{tikzpicture}
-        \draw[->,white] (-70:0.1) -- (-70:3);
-          \foreach \theta in {60,-60,120,0}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \fill[blue](180:1) circle [radius=0.05];
-          \fill[blue](0:0) circle [radius=0.05];
-
-          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
-          \draw[->, blue] (180:0.9) -- (180:0.1);
-          \draw[->, blue] (-120:0.1) -- (-120:0.9);
-
-          \node[below left] at (180:1) {$w[i-2]$};
-          \node[above] at (0:0) {$w[i-1]$};
-          \node[below] at (-120:1) {$w[i]$};
-
-          \node[right] at (120:1) {$n_3$};
-          \node[right] at (60:1) {$n_2$};
-          \node[right] at (0:1) {$n_1$};
-
-          \begin{scope}[shift=(-120:1)]
-            \fill[blue](0,0) circle [radius=0.05];
-            \foreach \theta in {-120,-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-          \end{scope}
-        \end{tikzpicture}
-    \caption{Case of $S[i-2..i] = bbt$}
-    \label{TTT_tunnelC_enter_usingBond}
-  \end{center}
-\end{figure}
-
-\subsubsection{$\alpha = 2$}
-
-By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
-If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$.
-Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities.
-Therefore formula \ref{TTT_only_bond} hold.
-
-\begin{eqnarray}
-  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
-  \label{TTT_only_bond}
-\end{eqnarray}
-
-Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
-
-Let us consider the case of $v_k$ is $o$.
-See Fig.\ref{TTT_case_of_o}.
-$w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$.
-If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding.
-If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive that is $w[i-1]$ consumes two binding capabilities.
-Therefore, this case consumes binding capabilities.
-If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings.
-In addition, $w[i]$ and $w[i+1]$ consume at least one binding.
-Therefore this case consumes binding capabilities.
-Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.
-
-\begin{eqnarray}
-  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
-  \label{TTT_only_a}
-\end{eqnarray}
-
-\begin{eqnarray}
-  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
-  \label{TTT_structure}
-\end{eqnarray}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-
-      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
-
-      \fill[blue](0:0) circle [radius=0.05];
-      \fill[blue](0:1) circle [radius=0.05];
-      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
-
-      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
-      \draw[->, blue] (0:0.1) -- (0:0.9);
-      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
-
-      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-
-      \node[below] at (-120:1) {$w[i-2]$};
-      \node[above] at (0:0) {$w[i-1]$};
-      \node[below] at (0:1) {$w[i]$};
-      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
-
-      \node[above] at (60:1) {$n_1$};
-      \node[below] at (-60:1) {$n_2$};
-
-    \end{tikzpicture}
-    \caption{Case of $S[i]$}
-    \label{TTT_case_of_o}
-  \end{center}
-\end{figure}
-
-\subsubsection{$\alpha = 3$}
-
-\begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only a finite structure whose size is $\mathcal{O}(n)$.
-\end{theorem}
-
-\begin{lemma}
-\label{TTT_a3_2b_lemma}
- Let $p$ be a point whose neighbors is occupied at least two point.
-If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
-\end{lemma}
-
-\begin{proof}[proof of lemma]
-Assume the transcript is stabilized until $w[i-1]$.
-One of neighbors of $p$ is not $w[i-1]$ where this bead regards $n_1$.
-If $w[i-1]$ include neighbors of $p$ and $w[i]$ is stabilized at another point of $p$ with one bond.
-Then, any neighbors do not have bond without $w[i-1]$.
-Neighbors of $n_1$ have to be occupied at least five according to lemma \ref{TTT_neighbor_lemma} and two of them include neighbors of $p$ where each of them regards $n_2, n_3$.
-In the same way, five neighbors of $n_2$ and $n_3$ are occupied and each of one of them includes neighbors of $p$ where they regard $n_4, n_5$.
-one of $n_5$'s neighbors includes neighbors of $p$ where it regards $n_6$.
-Then, any neighbors of $p$ are occupied.
-That is if some neighbors of $p$ are free, then there exists a bead which has bonds in neighbors.
-\end{proof}
-
-\begin{proof}
-Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
-Let us assume $w[i]$ is able to be stabilized with using one hand. Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$. Then, $w[i]$ can be also stabilized at $n_3$.
-
-\begin{paragraph}{Case of straight}
-\begin{itemize}
-\item[-] Case of $n_3$ is free\\
-According to assumption, $w[i]$ uses only one hand.
-Therefore, any neighbors of $n_3$ are occupied according to the lemma\ref{TTT_a3_2b_lemma}.
-$n_3$ and the point which is stabilized $w[i]$ are free so that $n_1$ has some bond by lemma\ref{TTT_neighbor_lemma}.
-Accordingly, this situation is non-deterministic.
-Thus, $n_3$ and $n_4$ have to be occupied because of symmetry.
-
-\item[-] Otherwise\\
-Because of  $S[i] = b$, at least one of $n_1$ and $n_2$ have to be free.
-Let us regard that $n_1$ is free.
-Neighbors of $n_1$ have to be occupied and at least two neighbors of $n_{-1}$ have to be free for $n_1$ and $w[i]$.
-According to lemma\ref{TTT_neighbor_lemma}, $n_{-1}$ have some hand.
-Therefore $w[i]$ can be also stabilized $n_1$ that is this situation is non-deterministic.
-Thus, one of $n_3$ and $n_4$ has to be free.
-\end{itemize}
-
-Therefore, this case is false.
-\end{paragraph}
-
-\begin{paragraph}{Case of obtuse}
-\begin{itemize}
-\item[-] Case of $n_3$ is free\\
-Any neighbors of $n_3$ have to be occupied but the point which is stabilized $w[i]$ is free. Thus $n_3$ has to be occupied.
-\item[-] Case of $n_4$ is free\\
-According to lemma\ref{TTT_a3_2b_lemma}, $n_2$ has to be occupied because $n_4$ is free.
-Also $n_0$ has to be occupied from lemma\ref{TTT_neighbor_lemma}.
-Thus, only one of $n_0, n_3$ leave some hands or both of them do not leave any hands because $w[i]$ use only one bond.\\
-If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied.
-Also $n_{-3}$ must not have any hands so that $n_{-2}$ is occupied and also $n_{-1}$ is occupied.
-Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
-If $n_3$ has some hands, then $n_0$ does not have any hands so that $n_{-1}$ is occupied.
-In the same previous way, any $n_{-2}, n_{-3}$ are occupied.
-Therefore any neighbors of $w[i]$ are occupied.\\
-If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied.
-If one of $n_{-1}, n_{-3}$ has some hands, the other does not have any hands so that $n_{-2}$ is occupied.
-If both of $n_{-1}, n_{-3}$ do not have any hands, $n_{-2}$ has to be occupied and $n_{-2}$ has some hands.Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
-Thus $n_3$ has to be occupied in order to yield infinite structures.
-\item[-] Case of $n_2$ is free\\
-Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied.
-Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_2$ has to be occupied.
-\item[-] Case of $n_0$ is free\\
-Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied.
-Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_0$ has to be occupied.
-\end{itemize}
-
-Therefore, any situations contradict $S[i] = b$.
-
-\end{paragraph}
-
-\begin{paragraph}{Case of acute}
-\begin{itemize}
-\item[-] Case of $n_4$ is free\\
-$n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some hands according to lemma\ref{TTT_neighbor_lemma}.
-However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
-\item[-] Case of $n_2$ is free\\
-According to lemma\ref{TTT_a3_2b_lemma}, $n_0$ has to be occupied. $n_1$ has to be also occupied because of lemma\ref{TTT_neighbor_lemma}.
-We consider this case just like case of obtuse and that $n_4$ is free.
-Then if $w[i-2]$ binds $w[i]$, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
-If $n_1$ binds $w[i]$, this case is same.
-Also if $n_1$ and $w[i-2]$ do not have any hand, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
-Therefore, $w[i+1]$ cannot be provided.
-\item[-] Case of $n_0$ is free\\
-Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied.
-Any neighbors of $n_{1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_0$ has to be occupied.
-\item[-] Case of $n_1$ is free\\
-Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied.
-Any neighbors of $n_{-1}$ except $n_1$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_1$ has to be occupied.
-\end{itemize}
-
-Therefore, any situations contradict $S[i] = b$.
-\end{paragraph}\\
-
-Hence, assumption that w[i] is able to be stabilized with using one hand is false.
-Therefore, when w[i] is stabilized, w[i] uses at least two hands.
-\end{proof}
-
-\begin{figure}
-  \begin{center}
-  \begin{tabular}{c c c}
- \begin{minipage}{0.3\hsize}
- \centering
-    \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](0:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (0:0.1) -- (0:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (0:1) {$w_{[i]}$};
-
-	\foreach \theta in {60,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	 \draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
-    \end{tikzpicture}
-    \end{minipage}
-
-    \begin{minipage}{0.3\hsize}
-    \centering
-     \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](60:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (60:0.1) -- (60:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (60:1) {$w_{[i]}$};
-
-	\foreach \theta in {0,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	\draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
-	\draw [shift=(60:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(60:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-
- 	\node[right] at (0:1) {$n_0$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
-	\node[above, shift=(60:1)] at (60:1) {$n_{-2}$};
-	\node[above, shift=(60:1)] at (120:1) {$n_{-3}$};
-    \end{tikzpicture}
-    \end{minipage}
-
-    \begin{minipage}{0.3\hsize}
-        \centering
-     \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](120:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (120:0.1) -- (120:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (120:1) {$w_{[i]}$};
-
-	\foreach \theta in {0,60,-60,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	\draw [shift=(120:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(120:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(120:1), shift=(180:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-
- 	\node[right] at (0:1) {$n_0$};
-	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(120:1)] at (60:1) {$n_{-1}$};
-	\node[above, shift=(120:1)] at (120:1) {$n_{-2}$};
-	\node[above, shift=(120:1)] at (180:1) {$n_{-3}$};
-    \end{tikzpicture}
-    \end{minipage}
-    \end{tabular}
-    \caption{All possible directions of $w[i]$: straight, obtuse, acute.}
-    \label{TTT_a3_w}
-  \end{center}
-\end{figure}
-
-\subsubsection{$\alpha = 4$}
-\begin{theorem}[$\delta = 1, \alpha = 4$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only a finite structure whose size is $\mathcal{O}(n^2)$.
-\end{theorem}
-
-\begin{lemma}
-\label{TTT_a4_2b_lemma}
-Any beads which are already stabilized by some bonds use at least two bonds.
-\end{lemma}
-
-\begin{proof}[proof of lemma]
-Let us consider when $w[i]$ is stabilized by only one bond.
-See Fig.\ref{TTT_a4_lemma_fig}.
-According to lemma\ref{TTT_neighbor_lemma}, if $n_3$ is free, $w[i-2]$ has some hands.
-Thus, $n_4$ has to be occupied in order to stabilize deterministically.
-Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$.
-$n_1$ has some hands because $n_3$ is free.
-Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands.
-It contradict assumption.
-\end{proof}
-
-\begin{proof}
-According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds.
-Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized.
-See Fig.\ref{TTT_a4_first}.
-any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$.
-At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind.
-In this case, a point which is able to put a bead is only $n_2$.
-Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$.
-Hence oritatami system can yield only a finite structure whose size is $\mathcal{O}(n^2)$ in $\delta =1, \alpha = 4$.
-%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
-\end{proof}
-
-\begin{figure}
- \centering
-    \begin{tikzpicture}
-	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (0:1) {$n_0$};
-
-	\foreach \theta in {0,60,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-    \end{tikzpicture}
-    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
-    \label{TTT_a4_lemma_fig}
-\end{figure}
-
-\begin{figure}
- \centering
-    \begin{tikzpicture}
-	\fill[shift=(-120:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0), blue] (0,0) circle [radius=0.05];
-
-      \draw[dashed] (180:2) -- (0:2);
-      \draw[->, blue] (-120:0.9) -- (-120:0.1);
-
-	\node[below] at (-120:1) {$w_{[i-1]}$};
-	\node[above] at (180:0) {$w_{[i]}$};
-	\node[above] at (0:1) {$n_0$};
-
-	\foreach \theta in {0,60,-60,120,180}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[above] at (180:1) {$n_5$};
-
-	\node at (0:2.5) {$n+1$};
-    \end{tikzpicture}
-    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
-    \label{TTT_a4_first}
-\end{figure}
-
-%end of d = 1
-%//////////////////////////////////////////////////////% l.168 - 1326
-%//////////////////////////////////////////////////////%
-
-\section{Case of $\delta \geq 2$}
-
-\subsection{$\alpha = 1$, unary}
-
-Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|+1$.
-We will argue about the situation when the first bead is stabilized outside $\hexagon_p^n$ (a hexagon of radius $n$).
-Let this be the $i$th bead of the transcript.
-Without loss of generality, we can translate the origin $(0,0)$ to the coordinates of bead $i-1$ (which is still in $\hexagon_p^n$), and we can assume that the bead outside the hexagon is fixed at $(1,1)$ (see Fig.~\ref{fig:hexagonOut}).
-\begin{figure}
-	\centering
-	\includegraphics[width=0.3\linewidth]{./Fig/hexagonOut}
-	\caption{$N_p^n$ and the position $(1,1)$ of the first bead fixed outside of it.}
-	\label{fig:hexagonOut}
-\end{figure}
-
-In the elongation that places bead $i$ at $(1,1)$ there are two possibilities:
-\begin{itemize}
-	\item $i$ forms a bond with a bead at $(1,0)$.
-	\item  $i$ does not bond to anything and $i+1$ is at $(2,1)$ bonding with a bead at $(2,0)$.
-If there is no bead at $(1,0)$, then placing $i$ at $(1,0)$ instead of $(1,1)$ results in the same number of bonds, leading to nondeterminism.
-Therefore, there has to be a bead at $(1,0)$ and it is inert, otherwise it would bond to $i$.
-This is analogous to case 1.
-below.%as in Fig.~\ref{fig:hexagonOut1}.
-	\begin{figure}
-		\centering
-		\includegraphics[width=0.2\linewidth]{./Fig/hexagonOut1}
-		%\caption{}
-		\label{fig:hexagonOut1}
-	\end{figure}
-
-\end{itemize}
-
-%The only position with which $(1,1)$ can form a bond is $(1,0)$.
-This means that there is a bead at $(1,0)$, which bonds to bead $i$, otherwise there are other conformations in which beads $i$ and $i+1$ add one bond to the conformation, making the behavior nondeterministic.
-
-The next bead, $i+1$, can be fixed at $(2,1)$ or at $(0,1)$ as all other possibilities result in nondeterministic behavior immediately, so we have two cases.
-
-\begin{enumerate}
-	\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$.
-Now consider bead $i+2$.
-For $i+1$ to be fixed at $(2,1)$, $i+2$ needs to form a bond somewhere, otherwise $i+2$ could go to $(2,1)$ forming the bond with the bead at $(2,0)$ and there would be two conformations with the maximal $1$ bond.
-The only possibility is that there is a bead at $(3,0)$ and $i+2$ can bond with it when placed at $(3,1)$.
-We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by active beads, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$.
-Such an $m$ exists, and it is not greater than $n$.
-Then, bead $i+\ell$ is fixed at $(\ell+1,1)$ and bonds with $(\ell+1,0)$.
-However, bead $i+2+m$ cannot be fixed anywhere, because $i+2+m$ and $i+3+m$ can only add one bond to the conformation, and that is possible either with $i+2+m \rightarrow (2+m,1)$, $i+3+m \rightarrow (3+m,1)$ or with $i+2+m \rightarrow (2+m,2)$, $i+3+m \rightarrow (2+m,1)$.
-	\begin{figure}
-		\centering
-		\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut2}
-		\caption{}
-		\label{fig:hexagonout2}
-	\end{figure}
-
-	\item bead $i+1$ is fixed at $(0,1)$. This is only possible if
-	\begin{enumerate}
-		\item there is an inactive bead at $(-1,0)$ and an active one at $(-2,0)$. This case is symmetrical to (1).
-		\item there is no bead at $(-1,0)$, bead $i+1$ can bond with bead $i-1$ at $(0,0)$ and the bead $i+2$ can be placed at $(-1,0)$ where it can bond with $(-2,0)$, $(-2,-1)$ or $(-1,-1)$.
-This leads to nondeterminism, because bead $i$ at $(-1,0)$ and bead $i+1$ at $(0,1)$ has two bonds, just as the original conformation.
-		\item there is a bead at $(-1,0)$ and bead $i+1$ can bond with that or with bead $i-1$ at $(0,0)$.
-However, this means that placing bead $i$ at $(0,1)$ at bead $i+1$ at $(1,1)$ creates the same number of hydrogen bonds, thus resulting in bead $i$ not being placed deterministically.
-
-	\end{enumerate}
-\end{enumerate}
-
-\begin{figure}
-	\centering
-	%\includegraphics[width=0.3\linewidth]{./hexagonOut1}
-	%\hspace{10mm} %
-	\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut3}
-
-	\caption{}
-	\label{fig:hexagonOut2}
-\end{figure}
-
-\subsection{In the case of $\delta = 3$}
-
-We discuss when the length of seed is $n$.
-If the length of seed is $n$, the seed will be in an equilateral hexagon with a radius of $n$ when it is given.
-We will begin our disscussion by considering the moment when a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$.
-Let us assume that a fixed bead on a side of an equilateral hexagon with a radius of $n$ is able to make a hydrogen bond.
-If it is able to make only two hydrogen bonds, it will be nondeterministic because there are two possibilities that it makes two structures in Fig.5.
-Therefore, it needs to make three hydrogen bonds to determine the only structure.\\
-
-\begin{figure}
-  \begin{center}
-  \begin{tabular}{cc}
-    \begin{tikzpicture}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
-      \fill (2.0, 1.732) node [right] {$n+2$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (0 : 0.0)]
-        \foreach \theta in {60, 120}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw (0 : 0.0) -- (60 : 1.0);
-        \draw (60 : 1.0) -- (120 : 1.0);
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (120 : 1.0)]
-        \foreach \theta in {60}{
-        \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-    \end{tikzpicture}
-
-    \begin{tikzpicture}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
-      \fill (2.0, 1.732) node [right] {$n+2$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (0 : 0.0)]
-        \foreach \theta in {60, 120}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
-        \draw (60 : 1.0) -- (120 : 1.0);
-        \draw (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \draw (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (120 : 1.0)]
-        \foreach \theta in {60}{
-        \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted](0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-    \end{tikzpicture}
-    \end{tabular}
-    \caption{}
-  \end{center}
-\end{figure}
-
-There are the two cases in which a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$ and it makes three hydrogen bonds in Fig.6.
-If it makes three hydrogen bonds once such as Fig6., it will make three hyrogen bonds forever to be deterministic.
-This becomes nondeterministic finally, such as in Fig.7., when it reaches a corner of an equilateral hexagon.
-Thus, the fixed bead on a side of an equilateral hexagon with a radius of $n$ has to make a hydrogen bond with a bead in an equilateral hexagon.
-
-\begin{figure}
-  \begin{center}
-  \begin{tabular}{cc}
-    \begin{tikzpicture}
-      \draw [dashed] (-0.5, 0.0) -- (3.5, 0.0);
-      \fill (3.5, 0.0) node [right] {$n$};
-      \draw [dashed] (-0.5, 0.866) -- (3.5, 0.866);
-      \fill (3.5, 0.866) node [right] {$n+1$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (0 : 0.0)]
-        \foreach \theta in {0, 60}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \fill (0,0) circle [radius = 0.05];
-        \foreach \theta in {0, 60, 120}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-          \draw (0 : 0.0) -- (0 : 2.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 1.0)]
-          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 3.0)]
-          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-    \end{tikzpicture}
-
-    \begin{tikzpicture}
-      \draw [dashed] (-1.5, 0.0) -- (2.5, 0.0);
-      \fill (2.5, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.5, 0.866) -- (2.5, 0.866);
-      \fill (2.5, 0.866) node [right] {$n+1$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (0 : 0.0)]
-        \foreach \theta in {0, 60, 120, 180}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \fill (0,0) circle [radius = 0.05];
-        \foreach \theta in {120}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (120 : 1.0)]
-          \draw (0 : 0.0) -- (0 : 2.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 1.0)]
-          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (180 : 1.0)]
-          \draw [dotted] (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-    \end{tikzpicture}
-    \end{tabular}
-    \caption{}
-  \end{center}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \begin{tabular}{cc}
-    \begin{tikzpicture}
-      \draw [dashed] (-0.5, 0.0) -- (2.0, 0.0);
-      \fill (3.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-0.5, 0.866) -- (2.5, 0.866);
-      \fill (3.0, 0.866) node [right] {$n+1$};
-      \draw [dashed] (-0.5, 1.732) -- (3.0, 1.732);
-      \fill (3.0, 1.732) node [right] {$n+2$};
-      \fill (60 : 1.0) circle [radius = 0.05];
-      \draw (-0.1,-0.1) -- (0.1,0.1);
-      \draw (0.1,-0.1) -- (-0.1,0.1);
-      \begin{scope}[shift = (120 : 1.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-      \end{scope}
-      \begin{scope}[shift = (120 : 1.0)]
-        \draw [dotted] (0 : 0.0) -- (300 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \draw (0.0, 0.0) -- (2.0, 0.0);
-        \fill (2.0, 0.0) circle [radius = 0.05];
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \draw [dashed] (0 : 0.0) -- (300 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 1.0)]
-      \fill (0.0, 0.0) circle [radius = 0.05];
-        \foreach \theta in {0, 60}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \begin{scope}[shift = (120 : 1.0)]
-          \fill (0.0, 0.0) circle [radius = 0.05];
-          \draw (0 : 0.0) -- (240 : 1.0);
-          \draw (0 : 0.0) -- (300 : 1.0);
-        \end{scope}
-      \end{scope}
-    \end{tikzpicture}
-
-    \begin{tikzpicture}
-      \draw [dashed] (-0.5, 0.0) -- (2.0, 0.0);
-      \fill (3.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-0.5, 0.866) -- (2.5, 0.866);
-      \fill (3.0, 0.866) node [right] {$n+1$};
-      \draw (-0.1,-0.1) -- (0.1,0.1);
-      \draw (0.1,-0.1) -- (-0.1,0.1);
-      \fill (60 : 1.0) circle [radius = 0.05];
-      \begin{scope}[shift = (120 : 1.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-      \end{scope}
-      \begin{scope}[shift = (120 : 1.0)]
-        \draw [dotted] (0 : 0.0) -- (300 : 1.0);
-        \draw (0.0, 0.0) -- (3.0, 0.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \draw [dashed] (0 : 0.0) -- (300 : 1.0);
-        \fill (60 : 1.0) circle [radius = 0.05];
-      \end{scope}
-      \begin{scope}[shift = (0 : 1.0)]
-        \fill (0.0, 0.0) circle [radius = 0.05];
-        \foreach \theta in {0, 60}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-    \end{tikzpicture}
-    \end{tabular}
-    \caption{}
-  \end{center}
-\end{figure}
-
-Then, we will discuss the moment after the first the is fixed on a side of an equilateral hexagon with a radius of $n+1$.
-Let us assume that the bead is able to make a hydrogen bond.
-If it is able to make only two hydrogen bonds, it will be nondeterministic because there are possibilities that it makes two structures in Fig.8.
-Hence, it needs to make three hydrogen bonds to determine the only structure.
-It needs to be a right or left figure in Fig.9.
-to make three hydrogen bonds.\\
-
-\begin{figure}
-  \begin{center}
-  \begin{tabular}{cc}
-    \begin{tikzpicture}
-        \begin{scope}[shift=(0 : 0.0)]
-          \draw (-0.1,-0.1) -- (0.1,0.1);
-          \draw (0.1,-0.1) -- (-0.1,0.1);
-          \draw (0 : 0.0) -- (60 : 1.0);
-        \end{scope}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
-      \fill (2.0, 1.732) node [right] {$n+2$};
-      \draw [dashed] (-1.0, 2.598) -- (2.0, 2.598);
-      \fill (2.0, 2.598) node [right] {$n+3$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (60 : 2.0)]
-        \fill(0.0, 0.0) circle [radius = 0.05];
-        \foreach \theta in {120, 180, 240}{
-          \fill (0.0, 0.0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-        \draw (0 : 0.0) -- (180 : 1.0);
-        \draw (0 : 0.0) -- (240 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \begin{scope}[shift = (120 : 1.0)]
-          \draw (0.0, 0.0) -- (60 : 1.0);
-          \draw [dotted] (0.0, 0.0) -- (300 : 1.0);
-        \end{scope}
-      \end{scope}
-    \end{tikzpicture}
-
-    \begin{tikzpicture}
-        \begin{scope}[shift=(0 : 0.0)]
-          \draw (-0.1,-0.1) -- (0.1,0.1);
-          \draw (0.1,-0.1) -- (-0.1,0.1);
-          \draw (0 : 0.0) -- (60 : 1.0);
-        \end{scope}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
-      \fill (2.0, 1.732) node [right] {$n+2$};
-      \draw [dashed] (-1.0, 2.598) -- (2.0, 2.598);
-      \fill (2.0, 2.598) node [right] {$n+3$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (60 : 2.0)]
-        \fill(0.0, 0.0) circle [radius = 0.05];
-        \foreach \theta in {120, 180, 240}{
-          \fill (0.0, 0.0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw (0 : 0.0) -- (120 : 1.0);
-        \draw (0 : 0.0) -- (180 : 1.0);
-        \draw [dotted] (0 : 0.0) -- (240 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \begin{scope}[shift = (120 : 1.0)]
-          \draw [dotted] (0.0, 0.0) -- (60 : 1.0);
-          \draw (0.0, 0.0) -- (300 : 1.0);
-        \end{scope}
-      \end{scope}
-    \end{tikzpicture}
-    \end{tabular}
-    \caption{}
-  \end{center}
-\end{figure}
-
- If it makes three hydrogen bonds once such as Fig.9., it will make three hyrogen bonds forever to be deterministic.
-This becomes nondeterministic finally, such as in Fig.7., when it reaches a corner of an equilateral hexagon.
-Therefore, the first fixed bead on a side of an equilateral hexagon with a radius of $n+1$ has to make a hydrogen bond with a molecule on a side of an equilateral hexagon with a radius of $n$.
-
-\begin{figure}
-  \begin{center}
-  \begin{tabular}{cc}
-    \begin{tikzpicture}
-      \begin{scope}[shift=(0 : 0.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \draw [dashed] (-0.5, 0.0) -- (4.5, 0.0);
-      \fill (4.5, 0.0) node [right] {$n$};
-      \draw [dashed] (-0.5, 0.866) -- (4.5, 0.866);
-      \fill (4.5, 0.866) node [right] {$n+1$};
-      \fill (2.0, 0.0) circle [radius = 0.05];
-      \fill (3.0, 0.0) circle [radius = 0.05];
-      \fill (4.0, 0.0) circle [radius = 0.05];
-      \begin{scope}[shift = (60 : 1.0)]
-        \fill (0.0, 0.0) circle [radius = 0.05];
-        \fill (1.0, 0.0) circle [radius = 0.05];
-        \fill (2.0, 0.0) circle [radius = 0.05];
-        \fill (3.0, 0.0) circle [radius = 0.05];
-        \draw (0.0, 0.0) -- (3.0, 0.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 3.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 4.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-    \end{tikzpicture}
-
-    \begin{tikzpicture}
-      \begin{scope}[shift=(0 : 0.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \draw [dashed] (-3.5, 0.0) -- (1.0, 0.0);
-      \fill (1.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-3.5, 0.866) -- (1.0, 0.866);
-      \fill (1.0, 0.866) node [right] {$n+1$};
-      \fill (-1.0, 0.0) circle [radius = 0.05];
-      \fill (-2.0, 0.0) circle [radius = 0.05];
-      \fill (-3.0, 0.0) circle [radius = 0.05];
-      \begin{scope}[shift = (60 : 1.0)]
-        \fill (0.0, 0.0) circle [radius = 0.05];
-        \fill (-1.0, 0.0) circle [radius = 0.05];
-        \fill (-2.0, 0.0) circle [radius = 0.05];
-        \fill (-3.0, 0.0) circle [radius = 0.05];
-        \draw (0.0, 0.0) -- (-3.0, 0.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : -1.0)]
-        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : -2.0)]
-        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : -3.0)]
-        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-    \end{tikzpicture}
-    \end{tabular}
-    \caption{}
-  \end{center}
-\end{figure}
-
-Accordingly, it is Fig.10. when a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$.
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \begin{scope}[shift=(0 : 0.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \begin{scope}[shift=(60 : 1.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-      \end{scope}
-      \begin{scope}[shift=(0 : 1.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-    \end{tikzpicture}
-    \caption{}
-  \end{center}
-\end{figure}
-
-It has to be a right or left figure in Fig.6.
-when the first bead fixed on a side of an equilateral hexagon with a radius of $n+1$ make a hydrogen bond with a bead on a side of an equilateral hexagon with a radius of $n$.
-Fig.6.
-becomes nondeterministic finally, such as in Fig.7., when it reaches a corner of an equilateral hexagon.
-It is clear that all beads on a side of an equilateral hexagon with a radius of $n+1$ has to make a hydrogen bond with a bead on a side of an equilateral hexagon with a radius of $n$.
-It is impossible to fix molecules on a side of an equilateral hexagon with a radius of $n+2$ and determine the only structure when there are only beads which are able to make a hydrogen bond in an equilateral hexagon with a radius of $n$.
+\input{ttt}
 

### 2018-11-30 paper.tex
including preliminaries

@@
 %------------------------------------------------------
-\input{uos_preliminaries.tex}
+Let $\Sigma$ be a set of types of abstract molecules, or \textit{beads}. 
+A bead of type $a \in \Sigma$ is called an $a$-bead. 
+By $\Sigma^*$ and $\Sigma^\omega$, we denote the set of finite sequences of beads and that of one-way infinite sequences of beads, respectively. 
+The empty sequence is denoted by $\lambda$. 
+Let $w = b_1 b_2 \cdots b_n \in \Sigma^*$ be a sequence of length $n$ for some integer $n$ and bead types $b_1, \ldots, b_n \in \Sigma$. 
+The \textit{length} of $w$ is denoted by $|w|$, that is, $|w| = n$. 
+For two indices $i, j$ with $1 \le i \le j \le n$, we let $w[i..j]$ refer to the subsequence $b_i b_{i+1} \cdots b_{j-1}b_j$; if $i = j$, then $w[i..i]$ is simplified as $w[i]$. 
+For $k \ge 1$, $w[1..k]$ is called a \textit{prefix} of $w$.
+
+Oritatami systems fold their transcript, which is a sequence of beads, over the triangular grid graph $\mathbb{T} = (V, E)$ cotranscriptionally. 
+We designate one point in $V$ as the origin $O$ of $\mathbb{T}$. 
+For a point $p \in V$, let $N_p^d$ denote the set of points which lie in the regular hexagon of radius $d$ centered at the point $p$. 
+A directed path $P = p_1 p_2 \cdots p_n$ in $\mathbb{T}$ is a sequence of \textit{pairwise-distinct} points $p_1, p_2, \ldots, p_n \in V$ such that $\{p_i, p_{i+1}\} \in E$ for all $1 \le i < n$. 
+Its $i$-th point is referred to as $P[i]$. 
+Now we are ready to abstract RNA single-stranded structures in the name of conformation. 
+A \textit{conformation} $C$ (over $\Sigma$) is a triple $(P, w, H)$ of a directed path $P$ in $\mathbb{T}$, $w \in \Sigma^*$ of the same length as $P$, and a set of h-interactions $H \subseteq \bigl\{\{i, j\} \bigm| 1 \le i, i+2 \le j, \{P[i], P[j]\} \in E \bigr\}$.
+This is to be interpreted as the sequence $w$ being folded along the path $P$ in such a manner that its $i$-th bead $w[i]$ is placed at the $i$-th point $P[i]$ and the $i$-th and $j$-th beads are bound (by a hydrogen-bond-based interaction) if and only if $\{i, j\} \in H$.
+The condition $i+2 \le j$ represents the topological restriction that two consecutive beads along the path cannot be bound. 
+A \textit{rule set} $R \subseteq \Sigma \times \Sigma$ is a symmetric relation over $\Sigma$, that is, for all bead types $a, b \in \Sigma$, $(a, b) \in R$ implies $(b, a) \in R$. 
+A bond $\{i, j\} \in H$ is \textit{valid with respect to $R$}, or simply $R$-valid, if $(w[i], w[j]) \in R$. 
+This conformation $C$ is \textit{$R$-valid} if all of its bonds are $R$-valid. 
+For an integer $\alpha \ge 1$, $C$ is \textit{of arity $\alpha$} if it contains a bead that forms $\alpha$ bonds but none of its bead forms more. 
+By $\mathcal{C}_{\le \alpha}(\Sigma)$, we denote the set of all conformations over $\Sigma$ whose arity is at most $\alpha$; its argument $\Sigma$ is omitted whenever $\Sigma$ is clear from the context.
+
+The oritatami system grows conformations by an operation called elongation. 
+Given a rule set $R$ and an $R$-valid conformation $C_1 = (P, w, H)$, we say that another conformation $C_2$ is an elongation of $C_1$ by a bead $b \in \Sigma$, written as $C_1 \xrightarrow{R}_b C_2$, if $C_2 = (P p, wb, H \cup H')$ for some point $p \in V$ not along the path $P$ and set $H' \subseteq \bigl\{ \{i, |w|+1\} \bigm| 1 \le i < |w|, \{P[i], p\} \in E, (w[i], b) \in R \bigr\}$ of bonds formed by the $b$-bead; this set $H'$ can be empty.
+Note that $C_2$ is also $R$-valid. 
+This operation is recursively extended to the elongation by a finite sequence of beads as: for any conformation $C$, $C \xrightarrow{R}_\lambda^* C$; and for a finite sequence of beads $w \in \Sigma^*$ and a bead $b \in \Sigma$, a conformation $C_1$ is elongated to a conformation $C_2$ by $wb$, written as $C_1 \xrightarrow{R}_{wb}^* C_2$, if there is a conformation $C'$ that satisfies $C_1 \xrightarrow{R}_w^* C'$ and $C' \xrightarrow{R}_b C_2$.
+
+An \textit{oritatami system} (OS) $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ is composed of
+\begin{itemize}
+\item a set $\Sigma$ of bead types, 
+\item a rule set $R \subseteq \Sigma \times \Sigma$, 
+\item a positive integer $\delta$ called the \textit{delay}, 
+\item a positive integer $\alpha$ called the \textit{arity}, 
+\item an initial $R$-valid conformation $\sigma \in C_{\le \alpha}(\Sigma)$ called the \textit{seed}, upon which 
+\item its (possibly infinite) \textit{transcript} $w \in \Sigma^* \cup \Sigma^\omega$ is to be folded by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads.
+\end{itemize}
+The energy of a conformation $C = (P, w, H)$, denoted by $\Delta G(C)$, is defined to be ${-}|H|$; the more bonds a conformation has, the more stable it gets. 
+The set $\mathcal{F}(\Xi)$ of conformations \textit{foldable} by the system $\Xi$ is recursively defined as: the seed $\sigma$ is in $\mathcal{F}(\Xi)$; and provided that an elongation $C_i$ of $\sigma$ by the prefix $w[1..i]$ be foldable (i.e., $C_0 = \sigma$), its further elongation $C_{i+1}$ by the next bead $w[i+1]$ is foldable if
+\begin{equation}\label{eq:OS_CF}
+C_{i+1} \in \argmin_{
+\substack{
+C \in \mathcal{C}_{\le \alpha} s.t. \\
+C_i \xrightarrow{R}_{w[i+1]}C \\
+}
+}
+\min \Bigl\{ \Delta G(C') \Bigm|
+C \xrightarrow{R}^*_{w[i+2...i+k]}C', k\le \delta, C' \in \mathcal{C}_{\le \alpha}
+\Bigr\}.
+\end{equation}
+%
+Then we say that the bead $w[i+1]$ and the bonds it forms are \textit{stabilized} according to $C_{i+1}$. 
+Note that an arity-$\alpha$ oritatami system cannot fold any conformation of arity larger than $\alpha$. 
+A conformation foldable by $\Xi$ is \textit{terminal} if none of its elongations is foldable by $\Xi$. 
+The oritatami system $\Xi$ is \textit{deterministic} if for all $i \ge 0$, there exists at most one $C_{i+1}$ that satisfies \eqref{eq:OS_CF}. 
+A deterministic oritatami system folds into a unique terminal conformation. 
+An oritatami system with the empty rule set just folds into an arbitrary elongation of its seed nondeterministically. 
+Thus, the rule set is always assumed to be non-empty.
+
+In the second half of this paper, we consider the unary oritatami system. 
+An oritatami system is \textit{unary} if its bead type set $\Sigma$ is of size 1. 
+Its sole bead type is denoted by $a$, that is, $\Sigma = \{a\}$. 
+Its only possible rule is $(a, a)$ so that the non-empty rule set assumption implies that its rule set is $R = \{(a, a)\}$. 
+Its transcript is a sequence of $a$-beads. 
+That is to say, the behavior of a unary oritatami system is fully determined by the delay, arity, and seed.
 

### 2018-11-30 paper.tex
Grant info
Grant info modified

@@
 
-\title{On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F.
-and S.~S.}
+\title{On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 granted to S.~Z.~F.
+and S.~S.
+and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~S.}
 }

### 2018-11-30 ttt.tex
update after noon
separate in subfiles
update 11/30

@@
-\documentclass[runningheads]{llncs}
-
-\usepackage{tikz}
-\usepackage{calc}
-\usepackage{amsmath,amssymb}
-\usetikzlibrary{automata}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-
-\usepackage{wasysym}
-
-\begin{document}
-
-\title{On finiteness of structures produced deterministically by co-transcriptional folding}
-
-\section{Infiniteness of delay-1 unary deterministic oritatami system}
-
 \begin{figure}
@@
 
-\subsection{Introduction}
-
-In this section, we consider the finiteness of structures produced deterministically at delay 1.
-Our result, cases of arity 1 and 3 can only yield finite structures of size $\mathcal{O} (n)$, and cases of arity 4 and more can only yield finite structures which is size of $mathcal{O} (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
+In this section, we consider Problem~\ref{prob:det_unary_length} at delay 1.
+Our result, cases of arity 1 and 3 can only yield finite structures of size $O (n)$, and cases of arity 4 and more can only yield finite structures which is size of $O (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.~\ref{TTT_zigzag}.
 
@@
 
-Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
-%Let us denote its transcript by $w = w_1 w_2 w_3 \cdots$ for some $w_1,w_2,w_3 \in \Sigma = \{e\}$.
+%Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
 For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$, that is, foldable by $\Xi$. Hence $C_0 = \sigma$.
@@
 A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
-Accordingly, how they are stabilized can be described by a binary sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
+Accordingly, how they are stabilized can be described by a sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
+We let $S$ take the value $\blacksquare$ for halt.
 
@@
 \begin{definition}[binding capability]
-Let $B_i$ be $( \{ (h, i) | {}^\forall h < i \} \cup \{ (i, j) | {}^\forall j > i \}) \cap H$.
-Moreover, let $R_i$ be a set of neighbors of $w[i]$ that are free and reachable from $C_j$ where $C_j$ is a conformation which stabilized until $w[j]$.
- The number of binding capabilities of a conformation $C_j$ is denoted $\#bc(C_j)$ and is defined by $\sum^{j}_{k=-n+1} \min \{ |B_k|, |R_k|  \}$.
+Let $C = (P,w,H)$ be a conformation.
+Let $B_k$ be $H \cap \{ (i,j) \mid \mbox{$i=k$ or $j=k$} \}$. Moreover, let $R_k$ be a set of neighbors of the point $P[k]$ that are free and reachable from $C$.
+ The binding capability of $C$, denoted by $\#bc(C)$, is defined by $\sum^{|w|}_{k=1} \min \{ |B_k|, |R_k|  \}$.
 \end{definition}
@@
 
+%remark
+
 \begin{theorem}[Tunnel Troll Theorem]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$.
-If there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$, then $\#bc(C_{i-1}) > \#bc(C_j)$ and if $S[i..j+1] = bt^lbt^mb \quad (l + m = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
-On the other hand, at $\delta = 1$ and $\alpha \geq 3$, if S$[k] = t$, then $\#bc(C_{k-1}) > \#bc(C_k)$.
+Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. 
+At arity $\alpha \geq 3$, if $S[k] = t$ and $S[k+1] \neq \blacksquare$, then $\#bc(C_{k-1}) > \#bc(C_k)$.
+On the other hand, at arity $\alpha = 2$, if there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
 \end{theorem}
@@
 \proof%{Proof of Tunnel Troll Theorem}
-Assume $\Xi$ is deterministic.
-Each bead in the transcript is bound either inside a tunnel or outside.
-If a bead is stabilized inside a tunnel, then the position of successor is already decided either inside of a tunnel or outside.
+Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
+then it has at most one free neighbor, and hence its successor it to be stabilized there.
 Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.
 
-Tunnel sections have three possible shapes up to symmetry : straight($A$), obtuse($B$) and acute($C$) turn (Fig. \ref{TTT_tunnel}), and we will consider each of those.
-
-\begin{lemma}
-\label{TTT_neighbor_lemma}
-For unary transcripts at $\delta = 1$, if a bead has no free hand, then at least $\alpha + 2$ of its neighbors have to be occpied.
-\end{lemma}
+Tunnel sections have three possible shapes up to symmetry : straight($S$), obtuse($O$) and acute($A$) turn (Fig. \ref{TTT_tunnel}), and we will consider each of those.
+
+%\begin{lemma}
+%\label{TTT_neighbor_lemma}
+%For unary transcripts at $\delta = 1$, if a bead has no free hand, then at least $\alpha + 2$ of its neighbors have to be occpied.
+%\end{lemma}
 
@@
 \label{TTT_entrance_Tab}
-Let $\Xi$ be an oritatami system at $\delta = 1, \alpha =2$. 
+Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$, arity $\alpha =2$. 
 Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $w[i]$ is stabilized at an entrance point of tunnel $A$ or $B$, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
@@
 \label{TTT_exit}
+Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. 
 Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
@@
 \label{TTT_tunnelC_lemma}
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$.
+Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
 We assume $S[h..i+1] = bt^{(i-h)}b \quad (1<h<i)$.
@@
 
-Let us first consider cases of $\delta \geq 3, \alpha = 1$. These cases are clearly true because of lemma\ref{TTT_exit}.
+Let us first consider cases of $\delta \geq 3, \alpha = 1$. These cases are clearly true because of Lemma~\ref{TTT_exit}.
 
@@
 We assume there is an index $h$ such that $S[h-1..h+1] = bbt$ or $S[h-1..h+1] = tbt$.
-According to lemma\ref{TTT_entrance_Tab}, if $w[h+1]$ is stabilized by tunnel $A$ or $B$, then $\#bc(C_{h-1}) > \#bc(C_{h})$.
-Also,  According to lemma\ref{TTT_tunnelC_lemma}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
-On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of lemma\ref{TTT_exit}.
+According to Lemma~\ref{TTT_entrance_Tab}, if $w[h+1]$ is stabilized by tunnel $A$ or $B$, then $\#bc(C_{h-1}) > \#bc(C_{h})$.
+Also,  According to Lemma~\ref{TTT_tunnelC_lemma}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
+On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of Lemma~\ref{TTT_exit}.
 Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.
@@
 
-          \node at (2,0) {Tunnel A};
+          \node at (2,0) {Tunnel $S$};
         \end{tikzpicture}
@@
 
-          \node at (2,0) {Tunnel B};
+          \node at (2,0) {Tunnel $O$};
         \end{tikzpicture}
@@
 
-          \node at (2,0) {Tunnel C};
+          \node at (2,0) {Tunnel $A$};
         \end{tikzpicture}
@@
 
-\begin{proof}[lemma \ref{TTT_neighbor_lemma}]
-Any transcript bead has predecessor and successor except for the first and last beads.
-If the bead does not have any free hand, then it uses hands with $\alpha$ neighbors.
-Thus, lemma \ref{TTT_neighbor_lemma} is clearly true.
-\end{proof}
-
 \begin{proof}[lemma \ref{TTT_entrance_Tab}]
@@
 If $n_3$ is free, then $p^\prime$ has to be bound to a bead other than $n_1$ to deterministically stabilize.
-In this situation, at least three neighbors of $n_1$ are free, that is, $n_1$ has at least one free hand from lemma \ref{TTT_neighbor_lemma}.
+In this situation, at least three neighbors of $n_1$ are free, that is, $n_1$ has at least one free hand from Lemma~ \ref{TTT_neighbor_lemma}.
 Hence, $p^\prime$ must be bound to $n_1$.
@@
 
-\begin{proof}[lemma \ref{TTT_exit}]
+\begin{proof}[Lemma~ \ref{TTT_exit}]
 Fig.\ref{TTT_tunnel_exit} exhibits all the two kinds of exit of tunnel. 
@@
 $\delta = 1, \alpha = 2$\\
-Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$. We assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$.
-Let $a$ be $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$.
+Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$. We assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$ and
+let $a$ be $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$.
 Then, $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$ as follows.
@@
 
-\begin{proof}[lemma \ref{TTT_tunnelC_lemma}]
+\begin{proof}[Lemma~ \ref{TTT_tunnelC_lemma}]
 Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
@@
 In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
-In addition according to lemma\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$.
+In addition according to Lemma~\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$.
 Thus, $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_{i})$.
@@
   \item[-]{$w[h-1]$ does not consume any bindings}\\
-  According to lemma\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
+  According to Lemma~\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
     $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
@@
 \end{figure}
-
-\end{document}

### 2018-11-30 arity1.tex
Added pyramid part, polished arity 1, delay 3, unary
The pyramid part still needs some work, as does the arity 1, delay 2.

I went over Reoto's arity 1, delay 3 and made some changes to make it more readable. For now I commented out the last 2 paragraphs, as they are not necessary for the proof, I think. However, here we need to add some conclusion to the arguments of the previous two subsections.

@@
+\subsection{$\alpha = 1$, arbitrary alphabets}
+
+At arity $1$, allowing delay $2$ increases the power of OS compared with $\delta=1$, if at least four bead types are allowed.
+We demonstrate this with an infinite family of OS, which fold deterministically a transcript of length $\frac{(n-1)^2}{4}$ when receiving a given seed of length $n$.
+
+Consider a delay $2$, arity $1$ system with bead types $B_0$ to $B_4$ and attraction rules $\{B_1-B_1,B_2-B_2, B_3-B_3,B_4-B_4\}$.
+Let the seed be a conformation of a $4k+1$ long bead sequence of the form $(B_1B_0B_2B_0)^kB_0$.
+Bead $i$ of the seed is fixed at point $(i,0)$, for all $1\leq i\leq 4k-1$.
+Bead $4k$ is at $(4k-1,-1)$ and bead $4k+1$ is at $(4k,0)$.
+
+\noindent The transcript is
+\begin{center}
+	\scriptsize
+	\begin{tabular}{llllll}
+		$p=$ & $(B_2B_4B_1B_3)^{k-1}$ & $B_2B_4(B_1B_4B_2B_3)^{k-1}$ & $B_1B_4(B_1B_3B_2B_4)^{k-2}$ & $B_1B_3(B_2B_3B_1B_4)^{k-2}$ & $B_2B_3$\\
+		& $(B_2B_4B_1B_3)^{k-3}$ & $B_2B_4(B_1B_4B_2B_3)^{k-3}$ & $B_1B_4(B_1B_3B_2B_4)^{k-4}$ & $B_1B_3(B_2B_3B_1B_4)^{k-4}$ & $B_2B_3$\\
+		& \vdots\\
+		& $(B_2B_4B_1B_3)^{2}$ & $B_2B_4(B_1B_4B_2B_3)^{2}$ & $B_1B_4(B_1B_3B_2B_4)^{1}$ & $B_1B_3(B_2B_3B_1B_4)^{1}$ & $B_2B_3$\\
+		& $B_2B_4B_1B_4$
+	\end{tabular}
+
+\end{center}
+if $k$ is odd, and
+\begin{center}
+	\scriptsize
+	\begin{tabular}{llllll}
+		$p=$ & $(B_2B_4B_1B_3)^{k-1}$ & $B_2B_4(B_1B_4B_2B_3)^{k-1}$ & $B_1B_4(B_1B_3B_2B_4)^{k-2}$ & $B_1B_3(B_2B_3B_1B_4)^{k-2}$ & $B_2B_3$\\
+		& $(B_2B_4B_1B_3)^{k-3}$ & $B_2B_4(B_1B_4B_2B_3)^{k-3}$ & $B_1B_4(B_1B_3B_2B_4)^{k-4}$ & $B_1B_3(B_2B_3B_1B_4)^{k-4}$ & $B_2B_3$\\
+		& \vdots\\
+		& $(B_2B_4B_1B_3)^{2}$ & $B_2B_4(B_1B_4B_2B_3)^{2}$ & $B_1B_4$\\
+		& $B_1B_3B_2B_3$
+	\end{tabular}
+
+\end{center}
+if $k$ is even. The length of the transcript is $4k^2$. One row of the formula above corresponds to four rows of the conformation (except for the last rows).
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{./Fig/chichenBig}
+	\caption{Quadratic length transcript folding deterministically into pyramid shape.
+Seed: thick black path.
+Transcript: thin blue path.
+Bonds: dashed red lines.
+Beads: '$B_0$' black, '$B_1$' red, '$B_2$' red with black contour, '$B_3$' green, '$B_4$' green with black contour.}
+	\label{CI:big}
+\end{figure}
+
+The first bead of the transcript is type $B_2$ and it has to be fixed next to $(4k,0)$.
+The second bead is type $B_4$, which cannot form a bond with anything in the conformation so far.
+The only possibility of forming a bond is if $B_2$ is placed at $(4k,1)$ and it bonds with the $B_2$ at $(4k-1,0)$.
+The next bead to be fixed is $B_4$, and since it cannot form a bond, the conformation with the highest number of bonds is when the next bead, $B_1$ is at $(4k-2,1)$, which fixes the previous bead, $B_4$ at $(4k-1,1)$.
+
+\begin{figure}
+	\begin{minipage}{.35\textwidth}
+		\centering
+		\includegraphics[align=c,height=1in]{./Fig/CI_1}\\
+		\bigskip
+
+		(a) First transcript bead
+	\end{minipage}%
+	\begin{minipage}{.2\textwidth}
+		\centering
+		\includegraphics[align=c,height=0.7in]{./Fig/CI_2}\\
+		\bigskip
+
+		(b) Second bead
+	\end{minipage}
+	\begin{minipage}{.4\textwidth}
+		\centering
+		\includegraphics[align=c,height=0.5in]{./Fig/CI_3}
+		\bigskip
+		\vspace{0.1in}
+		\includegraphics[align=c,height=0.5in]{./Fig/CI_4}
+		\bigskip
+
+		(c) Bead $i+1$, when bead $i$ is $B_{3,4}$ and $B_{1,2}$, respectively
+	\end{minipage}
+	\caption{Fixing transcript beads in odd rows}
+	\label{CI:1-4}
+\end{figure}
+
+Let the last bead fixed be the $i$th one.
+If it is $B_1$ or $B_2$ at some position $(4k+1-i,1)$, then the next two are $B_3B_2$ or $B_4B1$, respectively.
+The first beads in both cases cannot bind anywhere, whereas the second ones can bind with identical beads at $(4k+1-(i+3),0)$, fixing bead $i+1$ at $(4k+1-(i+1),1)$.
+If bead $i$ was $B_3$ or $B_4$ at position $(4k+1-i,1)$ then the next two are $B_2B_4$ or $B_1B_3$,respectively.
+The first bead of those sequences can bind only to its identical counterpart at $(4k+1-(i+2),0)$, whereas the second cannot bind anywhere, fixing bead $i+1$ at $(4k+1-(i+1))$.
+The above hold as long as there is a bead already at $(4k+1-(i+3),0)$ or at $(4k+1-(i+3),0)$, respectively, so for all $i\in \{1,\dots, 4k-2\}$.
+
+According to the above, bead $4k-1$ was fixed at $(4k+1-(4k-1),1)=(2,1)$.
+The next bead, $4k$ is of the same type as bead $4k-2$, so they can form a bond, and this is the only bond that can be formed by any conformation of beads $4k$ and $4k+1$ (see Fig.~\ref{CI:turn}).
+A similar situation occurs when trying to fix bead $8k-2$: it can only bond to bead $8k-4$, so it will turn the path around.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{./Fig/CI_turn}
+	\caption{Beads $4k, 8k-2, \dots$ stabilize at turning points because the bead two positions before is the same type and has a free hand.}
+	\label{CI:turn}
+\end{figure}
+
 \subsection{$\alpha = 1$, unary}
@@
 	\includegraphics[width=0.3\linewidth]{./Fig/hexagonOut}
-	\caption{$N_p^n$ and the position $(1,1)$ of the first bead fixed outside of it.}
+	\caption{$\hexagon_p^n$ and the position $(1,1)$ of the first bead fixed outside of it.}
 	\label{fig:hexagonOut}
@@
 If there is no bead at $(1,0)$, then placing $i$ at $(1,0)$ instead of $(1,1)$ results in the same number of bonds, leading to nondeterminism.
-Therefore, there has to be a bead at $(1,0)$ and it is inert, otherwise it would bond to $i$.
+Therefore, there has to be a bead at $(1,0)$ and it is inactive, otherwise it would bond to $i$.
 This is analogous to case 1.
@@
 
-We discuss when the length of seed is $n$.
-If the length of seed is $n$, the seed will be in an equilateral hexagon with a radius of $n$ when it is given.
-We will begin our disscussion by considering the moment when a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$.
-Let us assume that a fixed bead on a side of an equilateral hexagon with a radius of $n$ is able to make a hydrogen bond.
-If it is able to make only two hydrogen bonds, it will be nondeterministic because there are two possibilities that it makes two structures in Fig.5.
-Therefore, it needs to make three hydrogen bonds to determine the only structure.\\
+As before, the length of seed is $n$ and the seed will be inside $\hexagon_p^n$, the equilateral hexagon with a radius of $n$ and center $p$, the point where the first bead of the seed is fixed.
+We will begin our discussion by considering the moment when the first bead is fixed outside $\hexagon_p^n$.
+Let this bead be the $i$th one.
+
+\textbf{A.} First, let us assume that a fixed bead on a side of $\hexagon_p^n$ has a free hand, and bead $i$ binds to it.
+If the most stable conformation formed by beads $i, i+1, i+2$ has only two hydrogen bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}.
+Therefore, it needs to make three hydrogen bonds to deterministically stabilize $i$.\\
 
@@
     \caption{}
+    \label{fig:beadi}
   \end{center}
@@
 
-There are the two cases in which a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$ and it makes three hydrogen bonds in Fig.6.
-If it makes three hydrogen bonds once such as Fig6., it will make three hyrogen bonds forever to be deterministic.
-This becomes nondeterministic finally, such as in Fig.7., when it reaches a corner of an equilateral hexagon.
-Thus, the fixed bead on a side of an equilateral hexagon with a radius of $n$ has to make a hydrogen bond with a bead in an equilateral hexagon.
+There are the two cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}.
+However, if it makes three bonds once, such as in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
+Similarly to case 1.
+in the previous section, this becomes nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a corner of $\hexagon_p^n$.
+Thus, the fixed bead on the side of an equilateral hexagon with a radius of $n$ has to make a hydrogen bond with a bead in an equilateral hexagon.
 
@@
     \caption{}
+    \label{fig:3bonds}
   \end{center}
+
 \end{figure}
@@
     \caption{}
+    \label{fig:hexcorner}
   \end{center}
@@
 
-Then, we will discuss the moment after the first the is fixed on a side of an equilateral hexagon with a radius of $n+1$.
-Let us assume that the bead is able to make a hydrogen bond.
-If it is able to make only two hydrogen bonds, it will be nondeterministic because there are possibilities that it makes two structures in Fig.8.
-Hence, it needs to make three hydrogen bonds to determine the only structure.
-It needs to be a right or left figure in Fig.9.
-to make three hydrogen bonds.\\
+\textbf{B.} Next, assume that bead $i$ could not bind to anything and let us discuss the moment after bead $i$ is fixed outside $\hexagon_p^n$.
+Now bead $i$ has a free hand.
+If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such structures, as in Fig.~\ref{fig:afterzigzag}.
+Hence, they need to form three bonds to deterministically stabilize, such as in the right or left side of Fig.~\ref{fig:afterline}.\\
 
@@
     \caption{}
+    \label{fig:afterzigzag}
   \end{center}
@@
 
- If it makes three hydrogen bonds once such as Fig.9., it will make three hyrogen bonds forever to be deterministic.
-This becomes nondeterministic finally, such as in Fig.7., when it reaches a corner of an equilateral hexagon.
-Therefore, the first fixed bead on a side of an equilateral hexagon with a radius of $n+1$ has to make a hydrogen bond with a molecule on a side of an equilateral hexagon with a radius of $n$.
+ If they form three bonds once, such as Fig.~\ref{fig:afterline}, the system would need three bonds forever to be deterministic.
+This becomes nondeterministic finally, such as in Fig.~\ref{fig:hexcorner}, when it reaches a corner of $\hexagon_p^n$.
+ %Therefore, the first fixed bead on a side of an equilateral hexagon with a radius of $n+1$ has to make a hydrogen bond with a molecule on a side of an equilateral hexagon with a radius of $n$.
 
@@
     \caption{}
+    \label{fig:afterline}
   \end{center}
@@
 
-Accordingly, it is Fig.10. when a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$.
+%Accordingly, it is Fig.~\ref{fig:firstout} when a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$.
 
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \begin{scope}[shift=(0 : 0.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \begin{scope}[shift=(60 : 1.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-      \end{scope}
-      \begin{scope}[shift=(0 : 1.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-    \end{tikzpicture}
-    \caption{}
-  \end{center}
-\end{figure}
+%\begin{figure}
+%  \begin{center}
+%    \begin{tikzpicture}
+%      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
+%      \fill (2.0, 0.0) node [right] {$n$};
+%      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
+%      \fill (2.0, 0.866) node [right] {$n+1$};
+%      \begin{scope}[shift=(0 : 0.0)]
+%        \draw (-0.1,-0.1) -- (0.1,0.1);
+%        \draw (0.1,-0.1) -- (-0.1,0.1);
+%        \draw (0 : 0.0) -- (60 : 1.0);
+%      \end{scope}
+%      \begin{scope}[shift=(60 : 1.0)]
+%        \draw (-0.1,-0.1) -- (0.1,0.1);
+%        \draw (0.1,-0.1) -- (-0.1,0.1);
+%      \end{scope}
+%      \begin{scope}[shift=(0 : 1.0)]
+%        \draw (-0.1,-0.1) -- (0.1,0.1);
+%        \draw (0.1,-0.1) -- (-0.1,0.1);
+%        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+%      \end{scope}
+%    \end{tikzpicture}
+%    \caption{}
+%    \label{fig:firstout}
+%  \end{center}
+%\end{figure}
 
-It has to be a right or left figure in Fig.6.
+%It has to be a right or left figure in Fig.6.
 when the first bead fixed on a side of an equilateral hexagon with a radius of $n+1$ make a hydrogen bond with a bead on a side of an equilateral hexagon with a radius of $n$.

### 2018-12-01 tt_intro.tex
12/1

--- 2018-11-30 ttt.tex
@@
 \end{figure}
-
-%remark
-
-\begin{theorem}[Tunnel Troll Theorem]
-Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. 
-At arity $\alpha \geq 3$, if $S[k] = t$ and $S[k+1] \neq \blacksquare$, then $\#bc(C_{k-1}) > \#bc(C_k)$.
-On the other hand, at arity $\alpha = 2$, if there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
-\end{theorem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\proof%{Proof of Tunnel Troll Theorem}
-Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
-then it has at most one free neighbor, and hence its successor it to be stabilized there.
-Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.
-
-Tunnel sections have three possible shapes up to symmetry : straight($S$), obtuse($O$) and acute($A$) turn (Fig. \ref{TTT_tunnel}), and we will consider each of those.
-
-%\begin{lemma}
-%\label{TTT_neighbor_lemma}
-%For unary transcripts at $\delta = 1$, if a bead has no free hand, then at least $\alpha + 2$ of its neighbors have to be occpied.
-%\end{lemma}
-
-\begin{lemma}
-\label{TTT_entrance_Tab}
-Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$, arity $\alpha =2$. 
-Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $w[i]$ is stabilized at an entrance point of tunnel $A$ or $B$, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
-\end{lemma}
-
-\begin{lemma}
-\label{TTT_exit}
-Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. 
-Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
-At $\delta = 1, \alpha =2$, if we assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$, then $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
-%if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
-On the other hand, if we assume $S[k] = t (k \leq i)$ at $\delta =1, \alpha \geq 3$, then $\#bc(C_{k-1}) > \#bc(C_{k})$.
-\end{lemma}
-
-\begin{lemma}
-\label{TTT_tunnelC_lemma}
-Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
-We assume $S[h..i+1] = bt^{(i-h)}b \quad (1<h<i)$.
-If at least one of $w[h+1..i]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_i)$.
-\end{lemma}
-
-Let us first consider cases of $\delta \geq 3, \alpha = 1$. These cases are clearly true because of Lemma~\ref{TTT_exit}.
-
-Next, we consider the case of $\delta = 2, \alpha = 1$.
-We assume there is an index $h$ such that $S[h-1..h+1] = bbt$ or $S[h-1..h+1] = tbt$.
-According to Lemma~\ref{TTT_entrance_Tab}, if $w[h+1]$ is stabilized by tunnel $A$ or $B$, then $\#bc(C_{h-1}) > \#bc(C_{h})$.
-Also,  According to Lemma~\ref{TTT_tunnelC_lemma}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
-On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of Lemma~\ref{TTT_exit}.
-Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.
-
-\qed
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{ccc}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (0:1) {$p^\prime$};
-
-            \foreach \theta in {0,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,120,-120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel $S$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-60:1) {$p^\prime$};
-
-            \foreach \theta in {-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {0,60,120,-120}{
- 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel $O$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-120:1) {$p^\prime$};
-
-            \foreach \theta in {-120,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {0,60,-60,120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel $A$};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{All possible tunnel sections: straight, obtuse turn, and acute turn}
-    \label{TTT_tunnel}
-  \end{center}
-\end{figure}
-
-%\begin{figure}
-%  \begin{center}
-%    \begin{tikzpicture}
-%      \draw[thick, gray]
-%      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
-%      \node at(2,1) {Outside};
-%      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
-%      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
-%
-%      
-%      
-%      \draw[thick, gray]
-%      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
-%      \node at(9,1) {Inside of a tunnel};
-%      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-%      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
-%
-%      \draw[->]
-%      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
-%                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
-%      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
-%                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
-%                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
-%      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
-%                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
-%      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
-%                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
-%      ;
-%      
-%    \end{tikzpicture}
-%    \caption{Increment on Tunnel A,B}
-%    \label{TTT_position}
-%  \end{center}
-%\end{figure}
-
-%\begin{figure}
-%  \begin{center}
-%    \begin{tikzpicture}
-%      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
-%      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
-%      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
-%      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
-%      \draw[->] (outside1)--(enter1);
-%      \draw[->] (enter1)  --(inside1);
-%      \draw[->] (inside1) --(exit1);
-%      
-%      
-%      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
-%      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
-%      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
-%      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
-%      \draw[->] (outside2)--(enter2);
-%      \draw[->] (enter2)  --(inside2);
-%      \draw[->] (inside2) --(exit2);
-%
-%      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
-%      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
-%      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
-%      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
-%      \draw[->] (outside3)--(enter3);
-%      \draw[->] (enter3)  --(inside3);
-%      \draw[->] (inside3) --(exit3);
-%
-%      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
-%      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
-%      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
-%      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
-%      \draw[->] (outside4)--(enter4);
-%      \draw[->] (enter4)  --(inside4);
-%      \draw[->] (inside4) --(exit4);
-%    \end{tikzpicture}
-%    \caption{Case of Tunnel C}
-%    \label{TTT_tunnelC_graph}
-%  \end{center}
-%\end{figure}
-
-\begin{proof}[lemma \ref{TTT_entrance_Tab}]
-Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
-Let $w[i]$ be stabilized at an entrance point of Tunnel $A$ or $B$.
-All cases are $\#bc(C_{i-1}) > \#bc(C_{i})$ as follows.
-
-\begin{itemize}
-\item{Case of $t_0$}\\
-  Let us consider points $n_3,n_4$.
-At least one of the points $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-If $n_3$ is free, then $p^\prime$ has to be bound to a bead other than $n_1$ to deterministically stabilize.
-In this situation, at least three neighbors of $n_1$ are free, that is, $n_1$ has at least one free hand from Lemma~ \ref{TTT_neighbor_lemma}.
-Hence, $p^\prime$ must be bound to $n_1$.
-Thus, a case of $t_0$ consumes two hands and it does not supply any binding capabilities.
-
-\item{Case of $t_{\pm 60}$}\\
-  In this case, too, $n_4$ or $n_5$ is free.
-If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$.
-If $n_5$ is occupied, then $n_4$ is free.
-This time, by $n_2$ has some free hands so $p^\prime$ has to be bound to $n_2$.
-
-  In this situation, $p^\prime$ is able to supply a binding capabilities which could bind a bead into $n_4$ or $n_5$.
-However, $n_2$ and $n_3$ are part of a contiguous conformation.
-According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive.
-Thus, in the case of $t_{\pm 60}$ $\#bc(C_{i-1}) > \#bc(C_{i})$.
-
-\item{Case of $t_{\pm 120}$}\\
-  Binding capabilities that $p^\prime$ supplies are inactive according to Jordan curve theorem on $n_1$ and $n_2$.
-Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
-Thus, in the case of $t_{\pm 120}$ is $\#bc(C_{i-1}) > \#bc(C_{i})$.
-
-\end{itemize}
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{ccc}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-	 \draw[->,white] (120:0.8)--(120:0.1);%for adjustment
-
-            \fill[blue] (0,0) circle [radius=0.05];
-            \node[below] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,180}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {120,-120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (0:0.1)--(0:0.9);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-
-          \node at (0,-2) {$t_{0}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-
-            \fill(0,0) circle [radius=0.05];
-            \node[below] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {180,-120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (120:0.9)--(120:0.1);
-            \draw[->, blue] (0:0.1)--(0:0.9);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {$t_{\pm 60}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-            \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)}, blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {180,-120,120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (60:1.1)--(60:0.1);
-            \draw[->, blue] (0:0.1)--(0:1.1);
-
-            \node[transform canvas={shift=(0:1)},below] {$n_0$};
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {$t_{\pm 120}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Direction into a entrance}
-    \label{TTT_tunnel_direction}
-  \end{center}
-\end{figure}
-
-\end{proof}
-
-\begin{proof}[Lemma~ \ref{TTT_exit}]
-Fig.\ref{TTT_tunnel_exit} exhibits all the two kinds of exit of tunnel. 
-At least one of points $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-
-\begin{paragraph}{}
-$\delta = 1, \alpha = 2$\\
-Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$. We assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$ and
-let $a$ be $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$.
-Then, $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$ as follows.
-Also, if $i - h > 1$ and $j$ is such that $h<j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because all neighbors of $w[j]$ are occupied by beads forming the tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$.
-Thus, $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
-\end{paragraph}
-
-\begin{itemize}
-\item{Case of both $n_1$ and $n_2$ being free}\\
-  This case can be regarded the same as entrance.
-See Fig.\ref{TTT_tunnel_exit} (Left).
-Predecessor $n_5$ has to be bound to $n_4$ and $n_5$ because both of $n_3$ and $n_4$ have binding capabilities.
-Hence, $a \geq 2$.
-This time, $\alpha = 2$, that is, this case $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
-
-\item{Case of $n_1$ is occupied}\\
-  See Fig.\ref{TTT_tunnel_exit} (Right).
-If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$.
-Hence,  $a \geq 1$.
-This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied by the successor of $p^\prime$.
-Therefore, this case $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
-
-\end{itemize}
-
-\begin{paragraph}{}
-$\delta = 1, \alpha \geq 3$\\
-Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha \geq 3$. We assume $w[i]$ is stabilized at exit of tunnel.
-In all cases $\#bc(C_{i-1}) > \#bc(C_{i})$.
-Moreover, if $S[k] = t (k \leq i)$, then $\#bc(C_{k-1}) > \#bc(C_{k})$ because both sides of the path $p$ in Fig.\ref{TTT_inside_tunnel} ($n_1, n_2$) have two free points and one of $n_1, n_2$ is not the predecessor so that it has hand and moreover that $w[k]$ supplies any binding capabilities because its neighbors are occupied by beads of tunnel.
-\end{paragraph}
-
-\begin{itemize}
-\item{Case of $n_1$ and $n_2$ are free}\\
-  In $\alpha \geq 3$, if three neighbors of a bead leave, then it can supply two binding capabilities.
-Therefore predecessor $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$, too.
-In this case, at least four bindings are consumed and at most two are added.
-Thus, it consumes some binding capabilities, overall.
-
-\item{Case of $n_1$ is occupied}\\
-  In this case, $n_4$ leave at least two bindings and $n_3$, $n_1$ also leave at least one binding.
-Therefore $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$ also has to be bound $n_1$ and $n_4$.
-In this case, at least four bindings are consumed and at most two are added.
-Thus, it consumes some binding capabilities, totally.
-\end{itemize}
-
-\begin{figure}
-  \centering
-    \begin{tabular}{cc}
-    \begin{minipage}{0.66\hsize}
-    \centering
-      \begin{tabular}{cc}
-      \begin{minipage}{0.45\linewidth}
-      \centering
-        \begin{tikzpicture}
-	\draw[white] (0:0) -- (120:1);
-	\draw[white] (0:0) -- (-60:1);
-	\draw[white] (0:0) -- (0:1);
-
-            \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {120,-120,180}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-            \draw (-60:1) circle [radius=0.05];
-            \draw (60:1) circle [radius=0.05];
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {Point $n_1$ and $n_2$ are free};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.45\linewidth}
-      \centering
-        \begin{tikzpicture}
-	\draw[white] (0:0) -- (0:1);
-	\draw[white] (0:0) -- (120:1);
-	\draw[white] (0:0) -- (-90:2);
-
-            \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {120,-120,180,60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-            \draw (-60:1) circle [radius=0.05];
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-
-            \node[transform canvas={shift=(0:1)},right] {$n_0$};
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {Point $n_1$ is occupied};
-        \end{tikzpicture}
-      \end{minipage}
-    \end{tabular}
-    \caption{Exit of Tunnel}
-    \label{TTT_tunnel_exit}
-    \end{minipage}
-
-    \begin{minipage}{0.33\hsize}
-    \centering
-     \begin{tikzpicture}
-	\draw[white] (0:0) -- (120:1);
-	\draw[white] (0:0) -- (-60:1);
-            \fill[blue](0,0) circle [radius=0.05];
-            \draw[blue] (0:1) circle [radius = 0.05];
-            \draw[->] (0:0.1) -- node[above]{$p$} (0:0.9);
-
-            \foreach \theta in {60, -60, 120,-120,180}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-                \end{tikzpicture}
-
-    \caption{Inside tunnel}
-    \label{TTT_inside_tunnel}
-    \end{minipage}
-
-    \end{tabular}
-\end{figure}
-\end{proof}
-
-\begin{proof}[Lemma~ \ref{TTT_tunnelC_lemma}]
-Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
-Assume $S[h..i+1] = bt^{i-h}b (h<i)$.
-If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$, with $h+2 \leq g \leq i$ is stabilized by tunnel $C$, $C_g$ is a terminal.
-
-Let us consider stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ as follows.
-In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
-In addition according to Lemma~\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$.
-Thus, $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_{i})$.
-\\
-
-\subsubsection{Case of $S[h-1..h+1] = tbt$}
-Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
-
-\begin{itemize}
-\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$.
-Moreover, $w[h]$ has to bind to one of $n_1, n_2, n_3$ in order to stabilize deterministically.
-On the other hand, $w[h+1]$ can supply two bindings but has only two free neighbors.
-One of them is occupied by a successor.
-Therefore $w[h+1]$ can only bind one of $n_5, n_6$, that is, $w[h+1]$ supplies at most one binding.
-Thus, this case $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
-
-\item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  These cases are divided on number of capabilities that $w[h-1]$ consumes.
-  \begin{itemize}
-  \item[-]{$w[h-1]$ does not consume any bindings}\\
-  According to Lemma~\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
-    $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
-    $w[h+1]$ has to be bound to $w[h-1]$ because $w[h-1]$ has bindings, that is, $w[h+1]$ consumes at least one hand and supplies at most one hand so that $\#bc(C_{h}) \geq \#bc(C_{h+1})$.
-Thus, in this cases $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
-%     This time, let us consider either $n_4$ is occupied or not.
-If $n_4$ is occupied, then $w[h-1]$ has no active bindings that is this situation consumes some binding capabilities.
-If $n_4$ is free and $w[h+2]$ is stabilized in $n_4$, then $w[h-1]$ has to bind $w[h+2]$.
-Therefore, In this case, stabilization of $w[h-1..h+2]$ consumes some bindings.
-If $n_4$ is free and $w[h+2]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[h+2]$.
-Therefore, in this case consumes some bindings.
-Thus in this cases $\#bc(C_{h-1}) > \#bc(C_{h+2})$.
-
-  \item[-]{$w[h-1]$ consumes one binding}\\
-    In this case, $w_{h}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[h-1]$ and $w[h+1]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
-  \item[-]{$w[h-1]$ consumes two bindings}\\
-    In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies two bindings. Thus, in this cases $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
-
-  \end{itemize}
-\end{itemize}
-\begin{figure}
-  \centering
-    \begin{tabular}{cc}
-
-      \begin{minipage}{0.48\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];
-
-          \foreach \theta in {60,-60,120,-120,180}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \fill[blue](0:1) circle [radius=0.05];
-          \draw[->, blue] (0:0.1)--(0:0.9);
-
-          \node[below] at (-60:1) {$n_4$};
-
-          \begin{scope}[shift=(0:2)]
-            \fill[blue](0,0) circle [radius=0.05];
-
-            \foreach \theta in {120,60,-60,0}{
-             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (-120:0.1)--(-120:0.9);
-
-            \node[below] at (180:1) {$w_{[h-1]}$};
-            \node[above] at (0:0) {$w_{[h]}$};
-            \node[below] at (-120:1) {$w_{[h+1]}$};
-
-            \node[above] at (120:1) {$n_3$};
-            \node[above] at (60:1) {$n_2$};
-            \node[right] at (0:1) {$n_1$};
-
-            \begin{scope}[shift=(-120:1)]
-              \fill[blue](0,0) circle [radius=0.05];
-              \foreach \theta in {-120,-60}{
-                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-              }
-
-              \node[right] at (-120:1) {$n_5$};
-              \node[right] at (-60:1) {$n_6$};
-            \end{scope}
-
-          \end{scope}
-
-          \node at (1.2,-2.5) {Pattern 1};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.48\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \fill(0,0) circle [radius=0.1];
-
-          \foreach \theta in {60,0,120,-120,180}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \draw[->, blue] (-60:0.1)--(-60:0.9);
-
-          \begin{scope}[shift=(-60:1),shift=(0:1)]
-            \fill[blue](0,0) circle [radius=0.05];
-            \fill[blue](180:1) circle [radius=0.05];
-
-            \foreach \theta in {120,60,0,-60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (-120:0.1)--(-120:0.9);
-
-            \node[below] at (180:1) {$w_{[h-1]}$};
-            \node[above] at (0:0) {$w_{[h]}$};
-            \node[below] at (-120:1) {$w_{[h+1]}$};
-
-            \node[above right] at (120:1) {$n_3$};
-            \node[right] at (60:1) {$n_2$};
-            \node[right] at (0:1) {$n_1$};
-
-            \begin{scope}[shift=(-120:1)]
-              \fill(0,0) circle [radius=0.05];
-              \foreach \theta in {180,-120,-60}{
-                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-              }
-
-              \node[left] at (180:1) {$n_4$};
-              \node[right] at (-120:1) {$n_5$};
-              \node[right] at (-60:1) {$n_6$};
-            \end{scope}
-
-          \end{scope}
-
-          \node at (1.25,-4) {Pattern 2};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Case of $S[h-1..h+1] = tbt$}
-    \label{TTT_tunnelC_enter_usingTunnel}
-\end{figure}
-
-\subsubsection{Case of $S[h-1..h+1] = bbt$}
-Let us consider number of consumed bindings by $w[h-1]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
-
-\begin{itemize}
-\item{$w[h-1]$ consumes one binding}\\
-  In this situation, $w[h-1]$ supplies one active binding whereas $w[h+1]$ consumes this binding. In addition, $w[h]$ has to bound to one of $n_1, n_2, n_3$.
-  Thus, in this cases consume some binding capabilities.
-
-\item{$w[h-1]$ consumes two bindings}\\
-  In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
-\end{itemize}
-
-\begin{figure}
-  \begin{center}
-        \begin{tikzpicture}
-        \draw[->,white] (-70:0.1) -- (-70:3);
-          \foreach \theta in {60,-60,120,0}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \fill[blue](180:1) circle [radius=0.05];
-          \fill[blue](0:0) circle [radius=0.05];
-
-          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
-          \draw[->, blue] (180:0.9) -- (180:0.1);
-          \draw[->, blue] (-120:0.1) -- (-120:0.9);
-
-          \node[below left] at (180:1) {$w[h-1]$};
-          \node[above] at (0:0) {$w[h]$};
-          \node[below] at (-120:1) {$w[h+1]$};
-
-          \node[right] at (120:1) {$n_3$};
-          \node[right] at (60:1) {$n_2$};
-          \node[right] at (0:1) {$n_1$};
-
-          \begin{scope}[shift=(-120:1)]
-            \fill[blue](0,0) circle [radius=0.05];
-            \foreach \theta in {-120,-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-          \end{scope}
-        \end{tikzpicture}
-    \caption{Case of $S[h-1..h+1] = bbt$}
-    \label{TTT_tunnelC_enter_usingBond}
-  \end{center}
-\end{figure}
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%/////////////////////////////////////////////////
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{On structures provided by a unary and $\delta = 1$ oritatami system}
-\begin{theorem}[$\delta= 1, \alpha=2$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation.
-\end{theorem}
-
-\begin{proof}
-By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
-If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$.
-Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities.
-Therefore formula \ref{TTT_only_bond} hold.
-
-\begin{eqnarray}
-  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
-  \label{TTT_only_bond}
-\end{eqnarray}
-
-Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
-
-Let us consider the case of $v_k$ is $o$.
-See Fig.\ref{TTT_case_of_o}.
-$w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$.
-If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding.
-If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive, that is, $w[i-1]$ consumes two binding capabilities.
-Therefore, this case consumes binding capabilities.
-If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings.
-In addition, $w[i]$ and $w[i+1]$ consume at least one binding.
-Therefore this case consumes binding capabilities.
-Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.
-Thus, in this case, oritatami system can yield infinite structures but they are only zig-zag conformation.
-
-\end{proof}
-
-\begin{eqnarray}
-  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
-  \label{TTT_only_a}
-\end{eqnarray}
-
-\begin{eqnarray}
-  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
-  \label{TTT_structure}
-\end{eqnarray}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-
-      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
-
-      \fill[blue](0:0) circle [radius=0.05];
-      \fill[blue](0:1) circle [radius=0.05];
-      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
-
-      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
-      \draw[->, blue] (0:0.1) -- (0:0.9);
-      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
-
-      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-
-      \node[below] at (-120:1) {$w[i-2]$};
-      \node[above] at (0:0) {$w[i-1]$};
-      \node[below] at (0:1) {$w[i]$};
-      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
-
-      \node[above] at (60:1) {$n_1$};
-      \node[below] at (-60:1) {$n_2$};
-
-    \end{tikzpicture}
-    \caption{Case of $S[i]$}
-    \label{TTT_case_of_o}
-  \end{center}
-\end{figure}
-
-\begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite structures whose size is $\mathcal{O}(n)$.
-\end{theorem}
-
-\begin{lemma}
-\label{TTT_a3_2b_lemma}
- Let $p$ be a point whose neighbors is occupied at least two point.
-If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
-\end{lemma}
-
-\begin{proof}[proof of lemma]
-Assume the transcript is stabilized until $w[i-1]$.
-One of neighbors of $p$ is not $w[i-1]$ where this bead regards $n_1$.
-If $w[i-1]$ include neighbors of $p$ and $w[i]$ is stabilized at another point of $p$ with one bond.
-Then, any neighbors do not have bond without $w[i-1]$.
-Neighbors of $n_1$ have to be occupied at least five according to lemma \ref{TTT_neighbor_lemma} and two of them include neighbors of $p$ where each of them regards $n_2, n_3$.
-In the same way, five neighbors of $n_2$ and $n_3$ are occupied and each of one of them includes neighbors of $p$ where they regard $n_4, n_5$.
-one of $n_5$'s neighbors includes neighbors of $p$ where it regards $n_6$.
-Then, any neighbors of $p$ are occupied.
-That is, if some neighbors of $p$ are free, then there exists a bead which has bonds in neighbors.
-\end{proof}
-
-\begin{proof}
-Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is, when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
-Let us assume $w[i]$ is able to be stabilized with using one hand. Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$. Then, $w[i]$ can be also stabilized at $n_3$.
-
-\begin{paragraph}{Case of straight}
-\begin{itemize}
-\item[-] Case of $n_3$ is free\\
-According to assumption, $w[i]$ uses only one hand.
-Therefore, any neighbors of $n_3$ are occupied according to the lemma\ref{TTT_a3_2b_lemma}.
-$n_3$ and the point which is stabilized $w[i]$ are free so that $n_1$ has some bond by lemma\ref{TTT_neighbor_lemma}.
-Accordingly, this situation is non-deterministic.
-Thus, $n_3$ and $n_4$ have to be occupied because of symmetry.
-
-\item[-] Otherwise\\
-Because of  $S[i] = b$, at least one of $n_1$ and $n_2$ have to be free.
-Let us regard that $n_1$ is free.
-Neighbors of $n_1$ have to be occupied and at least two neighbors of $n_{-1}$ have to be free for $n_1$ and $w[i]$.
-According to lemma\ref{TTT_neighbor_lemma}, $n_{-1}$ have some hand.
-Therefore $w[i]$ can be also stabilized $n_1$, that is, this situation is non-deterministic.
-Thus, one of $n_3$ and $n_4$ has to be free.
-\end{itemize}
-
-Therefore, this case is false.
-\end{paragraph}
-
-\begin{paragraph}{Case of obtuse}
-\begin{itemize}
-\item[-] Case of $n_3$ is free\\
-Any neighbors of $n_3$ have to be occupied but the point which is stabilized $w[i]$ is free. Thus $n_3$ has to be occupied.
-\item[-] Case of $n_4$ is free\\
-According to lemma\ref{TTT_a3_2b_lemma}, $n_2$ has to be occupied because $n_4$ is free.
-Also $n_0$ has to be occupied from lemma\ref{TTT_neighbor_lemma}.
-Thus, only one of $n_0, n_3$ leave some hands or both of them do not leave any hands because $w[i]$ use only one bond.\\
-If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied.
-Also $n_{-3}$ must not have any hands so that $n_{-2}$ is occupied and also $n_{-1}$ is occupied.
-Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
-If $n_3$ has some hands, then $n_0$ does not have any hands so that $n_{-1}$ is occupied.
-In the same previous way, any $n_{-2}, n_{-3}$ are occupied.
-Therefore any neighbors of $w[i]$ are occupied.\\
-If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied.
-If one of $n_{-1}, n_{-3}$ has some hands, the other does not have any hands so that $n_{-2}$ is occupied.
-If both of $n_{-1}, n_{-3}$ do not have any hands, $n_{-2}$ has to be occupied and $n_{-2}$ has some hands.Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
-Thus $n_3$ has to be occupied in order to yield infinite structures.
-\item[-] Case of $n_2$ is free\\
-Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied.
-Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_2$ has to be occupied.
-\item[-] Case of $n_0$ is free\\
-Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied.
-Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_0$ has to be occupied.
-\end{itemize}
-
-Therefore, any situations contradict $S[i] = b$.
-
-\end{paragraph}
-
-\begin{paragraph}{Case of acute}
-\begin{itemize}
-\item[-] Case of $n_4$ is free\\
-$n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some hands according to lemma\ref{TTT_neighbor_lemma}.
-However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
-\item[-] Case of $n_2$ is free\\
-According to lemma\ref{TTT_a3_2b_lemma}, $n_0$ has to be occupied. $n_1$ has to be also occupied because of lemma\ref{TTT_neighbor_lemma}.
-We consider this case just like case of obtuse and that $n_4$ is free.
-Then if $w[i-2]$ binds $w[i]$, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
-If $n_1$ binds $w[i]$, this case is same.
-Also if $n_1$ and $w[i-2]$ do not have any hand, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
-Therefore, $w[i+1]$ cannot be provided.
-\item[-] Case of $n_0$ is free\\
-Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied.
-Any neighbors of $n_{1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_0$ has to be occupied.
-\item[-] Case of $n_1$ is free\\
-Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied.
-Any neighbors of $n_{-1}$ except $n_1$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_1$ has to be occupied.
-\end{itemize}
-
-Therefore, any situations contradict $S[i] = b$.
-\end{paragraph}\\
-
-Hence, assumption that w[i] is able to be stabilized with using one hand is false.
-Therefore, when w[i] is stabilized, w[i] uses at least two hands.
-\end{proof}
-
-\begin{figure}
-  \begin{center}
-  \begin{tabular}{c c c}
- \begin{minipage}{0.3\hsize}
- \centering
-    \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](0:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (0:0.1) -- (0:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (0:1) {$w_{[i]}$};
-
-	\foreach \theta in {60,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	 \draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
-    \end{tikzpicture}
-    \end{minipage}
-
-    \begin{minipage}{0.3\hsize}
-    \centering
-     \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](60:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (60:0.1) -- (60:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (60:1) {$w_{[i]}$};
-
-	\foreach \theta in {0,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	\draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
-	\draw [shift=(60:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(60:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-
- 	\node[right] at (0:1) {$n_0$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
-	\node[above, shift=(60:1)] at (60:1) {$n_{-2}$};
-	\node[above, shift=(60:1)] at (120:1) {$n_{-3}$};
-    \end{tikzpicture}
-    \end{minipage}
-
-    \begin{minipage}{0.3\hsize}
-        \centering
-     \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](120:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (120:0.1) -- (120:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (120:1) {$w_{[i]}$};
-
-	\foreach \theta in {0,60,-60,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	\draw [shift=(120:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(120:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(120:1), shift=(180:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-
- 	\node[right] at (0:1) {$n_0$};
-	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(120:1)] at (60:1) {$n_{-1}$};
-	\node[above, shift=(120:1)] at (120:1) {$n_{-2}$};
-	\node[above, shift=(120:1)] at (180:1) {$n_{-3}$};
-    \end{tikzpicture}
-    \end{minipage}
-    \end{tabular}
-    \caption{All possible directions of $w[i]$: straight, obtuse, acute.}
-    \label{TTT_a3_w}
-  \end{center}
-\end{figure}
-
-\begin{theorem}[$\delta = 1, \alpha = 4$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite structures whose size is $\mathcal{O}(n^2)$.
-\end{theorem}
-
-\begin{lemma}
-\label{TTT_a4_2b_lemma}
-Any beads which are already stabilized by some bonds use at least two bonds.
-\end{lemma}
-
-\begin{proof}[proof of lemma]
-Let us consider when $w[i]$ is stabilized by only one bond.
-See Fig.\ref{TTT_a4_lemma_fig}.
-According to lemma\ref{TTT_neighbor_lemma}, if $n_3$ is free, $w[i-2]$ has some hands.
-Thus, $n_4$ has to be occupied in order to stabilize deterministically.
-Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$.
-$n_1$ has some hands because $n_3$ is free.
-Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands.
-It contradict assumption.
-\end{proof}
-
-\begin{proof}
-According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds.
-Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized.
-See Fig.\ref{TTT_a4_first}.
-any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$.
-At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind.
-In this case, a point which is able to put a bead is only $n_2$.
-Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$.
-Hence oritatami system can yield only a finite structure whose size is $\mathcal{O}(n^2)$ in $\delta =1, \alpha = 4$.
-%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
-\end{proof}
-
-\begin{figure}
- \centering
-    \begin{tikzpicture}
-	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (0:1) {$n_0$};
-
-	\foreach \theta in {0,60,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-    \end{tikzpicture}
-    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
-    \label{TTT_a4_lemma_fig}
-\end{figure}
-
-\begin{figure}
- \centering
-    \begin{tikzpicture}
-	\fill[shift=(-120:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0), blue] (0,0) circle [radius=0.05];
-
-      \draw[dashed] (180:2) -- (0:2);
-      \draw[dashed, shift=(-60:1)] (180:2.5) -- (0:1.5);
-      \draw[->, blue] (-120:0.9) -- (-120:0.1);
-
-	\node[below] at (-120:1) {$w_{[i-1]}$};
-	\node[above] at (180:0) {$w_{[i]}$};
-	\node[above] at (0:1) {$n_0$};
-
-	\foreach \theta in {0,60,-60,120,180}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[above] at (180:1) {$n_5$};
-
-	\node at (0:2.5) {$n+1$};
-	\node[shift=(-60:1)] at (0:2) {$n$};
-    \end{tikzpicture}
-    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
-    \label{TTT_a4_first}
-\end{figure}

### 2018-12-01 tt_theorem.tex
12/1

--- 2018-11-30 ttt.tex
@@
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \fill (0,0) circle[radius = 0.1];
-      \fill (1.5,0) circle[radius = 0.1];
-      \fill (3,0) circle[radius = 0.1];
-      \fill (4.5,0) circle[radius = 0.1];
-      \fill (6,0) circle[radius = 0.1];
-
-      \draw[dashed] (0,0)--(1.5,0);
-      \draw[dashed] (1.5,0)--(3,0);
-      \draw[dashed] (3,0)--(4.5,0);
-      \draw[dashed] (4.5,0)--(6,0);
-      \draw[->] (0,0)--(60:0.75);
-      \draw[->] (1.5,0)--++(60:0.75);
-      \draw[->] (3,0)--++(60:0.75);
-      \draw[->] (4.5,0)--++(60:0.75);
-      \draw (0,0)--(60:1.5);
-      \draw (1.5,0)--++(60:1.5);
-      \draw (3,0)--++(60:1.5);
-      \draw (4.5,0)--++(60:1.5);
-
-      \begin{scope}[shift=(60:1.5)]
-        \fill (0,0) circle[radius = 0.1];
-        \fill (1.5,0) circle[radius = 0.1];
-        \fill (3,0) circle[radius = 0.1];
-        \fill (4.5,0) circle[radius = 0.1];
-        \draw[dashed] (0,0)--(1.5,0);
-        \draw[dashed] (1.5,0)--(3,0);
-        \draw[dashed] (3,0)--(4.5,0);
-        \draw[->] (0,0)--(-60:0.75);
-        \draw[->] (1.5,0)--++(-60:0.75);
-        \draw[->] (3,0)--++(-60:0.75);
-        \draw[->] (4.5,0)--++(-60:0.75);
-
-        \draw (0,0)--(-60:1.5);
-        \draw (1.5,0)--++(-60:1.5);
-        \draw (3,0)--++(-60:1.5);
-        \draw (4.5,0)--++(-60:1.5);
-      \end{scope}
-
-    \end{tikzpicture}
-    \caption{zig-zag conformation}
-    \label{TTT_zigzag}
-  \end{center}
-\end{figure}
-
-In this section, we consider Problem~\ref{prob:det_unary_length} at delay 1.
-Our result, cases of arity 1 and 3 can only yield finite structures of size $O (n)$, and cases of arity 4 and more can only yield finite structures which is size of $O (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.~\ref{TTT_zigzag}.
-
-%In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 2 deterministically and moreover that the only infinite conformations which its oritatami system can yield is only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
-
-%Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
-For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$, that is, foldable by $\Xi$. Hence $C_0 = \sigma$.
-
-Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$.
-The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1.
-There are just two ways to get stabilized at delay 1.
-One way is to be bound to another bead.
-The other way is through a $tunnel\ section$.
-A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
-Accordingly, how they are stabilized can be described by a sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
-We let $S$ take the value $\blacksquare$ for halt.
-
-Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
-We call such a point $p$ the $inside\ of\ a\ tunnel$ and points $p^\prime$ the $entrance\ of\ a\ tunnel$ except when $p^\prime$ is inside of a tunnel.
-If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor.
-In this way, $w[i]$ can get stabilized without being bound.
-
-%If a bead is stabilized through a tunnel section, then it can provide some bonds.
-Let us consider bonds of $C_i$.
-$C_i$ is represented $C = (W,P,H)$ where $|W| = i + n$ $C_i$ contains $\alpha \cdot (i + n) - 2|H|$ bonds because $C_i$ consists of $i + n$ beads and a bead has just $\alpha$ bonds and then $2 |H|$ of the those bonds are already used.
-However, even if a bead has an available bond, $w[j]$ $(j > i)$ might not be able to use this bond because the bond has possibility that it is blocked by transcripts $w[i+1..j-1]$.
-Number of $binding\ capabilities$ does not contain that case so that it is at most $\alpha \cdot (i + n) - 2|H|$.
-
-We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$.
-We define $binding\ capability$ with reachable.
-
-\begin{definition}[binding capability]
-Let $C = (P,w,H)$ be a conformation.
-Let $B_k$ be $H \cap \{ (i,j) \mid \mbox{$i=k$ or $j=k$} \}$. Moreover, let $R_k$ be a set of neighbors of the point $P[k]$ that are free and reachable from $C$.
- The binding capability of $C$, denoted by $\#bc(C)$, is defined by $\sum^{|w|}_{k=1} \min \{ |B_k|, |R_k|  \}$.
-\end{definition}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \draw (0:0) circle [radius=0.05];
-      \draw (0:1) circle [radius=0.05];
-      \draw (180:1) circle [radius=0.05];
-      \node[above] at (0:1) { $p^\prime$ };
-      \node[above] at (0:0) { $p$ };
-      \node[above] at (180:1) { $p^\prime$ };
-
-      \fill (60 : 1) circle [radius=0.1];
-      \fill (-60 : 1) circle [radius=0.1];
-      \fill (120 : 1) circle [radius=0.1];
-      \fill (-120 : 1) circle [radius=0.1];
-      \node[above] at (60 :1) { $a_{j_1}$ };
-      \node[above] at (-60 :1) { $a_{j_2}$ };
-      \node[above] at (120 :1) { $a_{j_3}$ };
-      \node[above] at (-120 :1) { $a_{j_4}$ };
-
-      \begin{scope}[shift=(0:5)]
-        \fill[blue] (0:0) circle [radius=0.1];
-        \draw (0:1) circle [radius=0.05];
-        \fill (180:1) circle [radius=0.1];
-        \node[above] at (180:1.2) { $a_{i-2}$ };
-        \node[above] at (0:0) { $a_{i-1}$ };
-        \draw[->, blue] (180:0.9) -- (180:0.1);
-
-        \fill (60 : 1) circle [radius=0.1];
-        \fill (-60 : 1) circle [radius=0.1];
-        \fill (120 : 1) circle [radius=0.1];
-        \fill (-120 : 1) circle [radius=0.1];
-        \node[above] at (60 :1) { $a_{j_1}$ };
-        \node[above] at (-60 :1) { $a_{j_2}$ };
-        \node[above] at (120 :1) { $a_{j_3}$ };
-        \node[above] at (-120 :1) { $a_{j_4}$ };
-      \end{scope}
-      \begin{scope}[shift=(0:10)]
-        \fill (0:0) circle [radius=0.1];
-        \fill[blue] (0:1) circle [radius=0.1];
-        \fill (180:1) circle [radius=0.1];
-        \node[above] at (180:1) { $a_{i-2}$ };
-        \node[above] at (0:0) { $a_{i-1}$ };
-        \node[above] at (0:1) { $a_i$ };
-        \draw[->] (180:0.9) -- (180:0.1);
-        \draw[->,blue] (0:0.1) -- (0:0.9);
-
-        \fill (60 : 1) circle [radius=0.1];
-        \fill (-60 : 1) circle [radius=0.1];
-        \fill (120 : 1) circle [radius=0.1];
-        \fill (-120 : 1) circle [radius=0.1];
-        \node[above] at (60 :1) { $a_{j_1}$ };
-        \node[above] at (-60 :1) { $a_{j_2}$ };
-        \node[above] at (120 :1) { $a_{j_3}$ };
-        \node[above] at (-120 :1) { $a_{j_4}$ };
-      \end{scope}
-    \end{tikzpicture} 
-    \caption{Through a tunnel section}
-    \label{TTT_tunnel_intro}
-  \end{center}
-\end{figure}
-
 %remark

### 2018-12-01 tt_theorem.tex
12/1 before lunch

@@
 
-\proof%{Proof of Tunnel Troll Theorem}
-Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
-then it has at most one free neighbor, and hence its successor it to be stabilized there.
-Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.
-
-Tunnel sections have three possible shapes up to symmetry : straight($S$), obtuse($O$) and acute($A$) turn (Fig. \ref{TTT_tunnel}), and we will consider each of those.
-
-%\begin{lemma}
-%\label{TTT_neighbor_lemma}
-%For unary transcripts at $\delta = 1$, if a bead has no free hand, then at least $\alpha + 2$ of its neighbors have to be occpied.
-%\end{lemma}
-
 \begin{lemma}
@@
 Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$, arity $\alpha =2$. 
-Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $w[i]$ is stabilized at an entrance point of tunnel $A$ or $B$, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
+Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $S[i] = b$ and $S[i+1] \in \{ t_s, t_o \} $, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
 \end{lemma}
+
+\begin{proof}[lemma \ref{TTT_entrance_Tab}]
+Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
+Let $w[i]$ be stabilized at an entrance point of Tunnel $A$ or $B$.
+All cases are $\#bc(C_{i-1}) > \#bc(C_{i})$ as follows.
+
+\begin{itemize}
+\item{Case of $t_0$}\\
+  Let us consider points $n_3,n_4$.
+At least one of the points $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
+If $n_3$ is free, then $p^\prime$ has to be bound to a bead other than $n_1$ to deterministically stabilize.
+In this situation, at least three neighbors of $n_1$ are free, that is, $n_1$ has at least one free hand from Lemma~ \ref{TTT_neighbor_lemma}.
+Hence, $p^\prime$ must be bound to $n_1$.
+Thus, a case of $t_0$ consumes two hands and it does not supply any binding capabilities.
+
+\item{Case of $t_{\pm 60}$}\\
+  In this case, too, $n_4$ or $n_5$ is free.
+If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$.
+If $n_5$ is occupied, then $n_4$ is free.
+This time, by $n_2$ has some free hands so $p^\prime$ has to be bound to $n_2$.
+
+  In this situation, $p^\prime$ is able to supply a binding capabilities which could bind a bead into $n_4$ or $n_5$.
+However, $n_2$ and $n_3$ are part of a contiguous conformation.
+According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive.
+Thus, in the case of $t_{\pm 60}$ $\#bc(C_{i-1}) > \#bc(C_{i})$.
+
+\item{Case of $t_{\pm 120}$}\\
+  Binding capabilities that $p^\prime$ supplies are inactive according to Jordan curve theorem on $n_1$ and $n_2$.
+Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
+Thus, in the case of $t_{\pm 120}$ is $\#bc(C_{i-1}) > \#bc(C_{i})$.
+
+\end{itemize}
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{ccc}
+
+      \begin{minipage}{0.3\hsize}
+      \centering
+        \begin{tikzpicture}
+	 \draw[->,white] (120:0.8)--(120:0.1);%for adjustment
+
+            \fill[blue] (0,0) circle [radius=0.05];
+            \node[below] at (0,0) {$w[i]$};
+
+            \foreach \theta in {0}{
+              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {60,-60,180}{
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+
+            \foreach \theta in {120,-120}{
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+            }
+
+            \draw[->, blue] (180:0.9)--(180:0.1);
+            \draw[->, blue] (0:0.1)--(0:0.9);
+
+            \node[transform canvas={shift=(60:1)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
+
+          \node at (0,-2) {$t_{0}$};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.3\hsize}
+      \centering
+        \begin{tikzpicture}
+
+            \fill(0,0) circle [radius=0.05];
+            \node[below] at (0,0) {$w[i]$};
+
+            \foreach \theta in {0}{
+              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {60,-60,120}{
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+
+            \foreach \theta in {180,-120}{
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+            }
+
+            \draw[->, blue] (120:0.9)--(120:0.1);
+            \draw[->, blue] (0:0.1)--(0:0.9);
+
+            \node[transform canvas={shift=(60:1)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1)},left] {$n_5$};
+
+          \node at (0,-2) {$t_{\pm 60}$};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.3\hsize}
+      \centering
+        \begin{tikzpicture}
+            \fill[blue](0,0) circle [radius=0.05];
+            \node[below] at (0,0) {$w[i]$};
+
+            \foreach \theta in {0}{
+              \fill[transform canvas={shift=(\theta:1)}, blue](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {60,-60}{
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+
+            \foreach \theta in {180,-120,120}{
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+            }
+
+            \draw[->, blue] (60:1.1)--(60:0.1);
+            \draw[->, blue] (0:0.1)--(0:1.1);
+
+            \node[transform canvas={shift=(0:1)},below] {$n_0$};
+            \node[transform canvas={shift=(60:1)},right] {$n_1$};
+            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
+            \node[transform canvas={shift=(120:1)},left] {$n_3$};
+            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
+            \node[transform canvas={shift=(180:1)},left] {$n_5$};
+
+          \node at (0,-2) {$t_{\pm 120}$};
+        \end{tikzpicture}
+      \end{minipage}
+
+    \end{tabular}
+    \caption{Direction into a entrance}
+    \label{TTT_tunnel_direction}
+  \end{center}
+\end{figure}
+
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{lemma}
-\label{TTT_tunnelC_lemma}
-Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
-We assume $S[h..i+1] = bt^{(i-h)}b \quad (1<h<i)$.
-If at least one of $w[h+1..i]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_i)$.
-\end{lemma}
-
-Let us first consider cases of $\delta \geq 3, \alpha = 1$. These cases are clearly true because of Lemma~\ref{TTT_exit}.
-
-Next, we consider the case of $\delta = 2, \alpha = 1$.
-We assume there is an index $h$ such that $S[h-1..h+1] = bbt$ or $S[h-1..h+1] = tbt$.
-According to Lemma~\ref{TTT_entrance_Tab}, if $w[h+1]$ is stabilized by tunnel $A$ or $B$, then $\#bc(C_{h-1}) > \#bc(C_{h})$.
-Also,  According to Lemma~\ref{TTT_tunnelC_lemma}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
-On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of Lemma~\ref{TTT_exit}.
-Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.
-
-\qed
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{ccc}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (0:1) {$p^\prime$};
-
-            \foreach \theta in {0,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,120,-120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel $S$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-60:1) {$p^\prime$};
-
-            \foreach \theta in {-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {0,60,120,-120}{
- 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel $O$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-120:1) {$p^\prime$};
-
-            \foreach \theta in {-120,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {0,60,-60,120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel $A$};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{All possible tunnel sections: straight, obtuse turn, and acute turn}
-    \label{TTT_tunnel}
-  \end{center}
-\end{figure}
-
-%\begin{figure}
-%  \begin{center}
-%    \begin{tikzpicture}
-%      \draw[thick, gray]
-%      (0.5,1)--(0,1)--(0,4)--(4,4)--(4,1)--(3.5,1);
-%      \node at(2,1) {Outside};
-%      \node at (2,3.2) [rectangle, draw, rounded corners] (enter) {Entrance of a tunnel};
-%      \node at(2,1.8) [rectangle, draw, rounded corners] (outside) {Otherwise};
-%
-%      
-%      
-%      \draw[thick, gray]
-%      (7.5,1)--(7,1)--(7,4)--(11,4)--(11,1)--(10.5,1);
-%      \node at(9,1) {Inside of a tunnel};
-%      \node at(9,3.2) [rectangle, draw, rounded corners] (next-tunnel) {Successor in inside};
-%      \node at(9,1.8) [rectangle, draw, rounded corners] (next-outside) {Successor in outside};
-%
-%      \draw[->]
-%      (outside) edge [bend left, blue] node[left] {$s=b,\Delta=-1$} (enter)
-%                   edge [loop left, blue] node[below left] {$s=b,\Delta=\pm 0$} (outside)
-%      (enter)   edge [bend left, blue] node[above] {$s=b,\Delta=-1$} (next-tunnel)
-%                edge [bend left, blue] node[above] {$s=b,\Delta=-a$} (next-outside)
-%                edge [bend left, blue] node[right] {$s=b,\Delta=\pm 0$}  (outside)
-%      (next-tunnel) edge[teal]         node[right] {$s=t,\Delta=-a$} (next-outside)
-%                edge [loop right, teal]node[right] {$s=t,\Delta=\pm 0$}    (next-tunnel)
-%      (next-outside) edge[bend left, teal] node[above] {$s=t,\Delta=+a$}  (outside)
-%                edge [bend left, teal]     node[above] {$s=t,\Delta=+(a-1)$}(enter)
-%      ;
-%      
-%    \end{tikzpicture}
-%    \caption{Increment on Tunnel A,B}
-%    \label{TTT_position}
-%  \end{center}
-%\end{figure}
-
-%\begin{figure}
-%  \begin{center}
-%    \begin{tikzpicture}
-%      \node at (0,4)   [rectangle, draw,rounded corners] (outside1) {Outside of tunnels};
-%      \node at (3.5,4) [rectangle, draw,rounded corners] (enter1)   {Entrance of a tunnel};
-%      \node at (7,4)   [rectangle, draw, rounded corners] (inside1) {Inside of a tunnel C};
-%      \node at (11,4)  [rectangle, draw, rounded corners] (exit1)   {Inside of a tunnel A or B};
-%      \draw[->] (outside1)--(enter1);
-%      \draw[->] (enter1)  --(inside1);
-%      \draw[->] (inside1) --(exit1);
-%      
-%      
-%      \node at (0,3)   [rectangle, draw,rounded corners] (outside2) {Inside of a tunnel};
-%      \node at (3.5,3) [rectangle, draw,rounded corners] (enter2)   {Entrance of a tunnel};
-%      \node at (7,3)   [rectangle, draw, rounded corners] (inside2) {Inside of a tunnel C};
-%      \node at (11,3)  [rectangle, draw, rounded corners] (exit2)   {Inside of a tunnel A or B};     
-%      \draw[->] (outside2)--(enter2);
-%      \draw[->] (enter2)  --(inside2);
-%      \draw[->] (inside2) --(exit2);
-%
-%      \node at (0,1)   [rectangle, draw,rounded corners] (outside3) {Outside of tunnels};
-%      \node at (3.5,1) [rectangle, draw,rounded corners] (enter3)   {Entrance of a tunnel};
-%      \node at (7,1)   [rectangle, draw, rounded corners] (inside3) {Inside of a tunnel C};
-%      \node at (11,1)  [rectangle, draw, rounded corners] (exit3)   {Outside of tunnels};     
-%      \draw[->] (outside3)--(enter3);
-%      \draw[->] (enter3)  --(inside3);
-%      \draw[->] (inside3) --(exit3);
-%
-%      \node at (0,0)   [rectangle, draw,rounded corners] (outside4) {Inside of atunnel};
-%      \node at (3.5,0) [rectangle, draw,rounded corners] (enter4)   {Entrance of a tunnel};
-%      \node at (7,0)   [rectangle, draw, rounded corners] (inside4) {Inside of a tunnel C};
-%      \node at (11,0)  [rectangle, draw, rounded corners] (exit4)   {Outside of tunnels};     
-%      \draw[->] (outside4)--(enter4);
-%      \draw[->] (enter4)  --(inside4);
-%      \draw[->] (inside4) --(exit4);
-%    \end{tikzpicture}
-%    \caption{Case of Tunnel C}
-%    \label{TTT_tunnelC_graph}
-%  \end{center}
-%\end{figure}
-
-\begin{proof}[lemma \ref{TTT_entrance_Tab}]
-Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
-Let $w[i]$ be stabilized at an entrance point of Tunnel $A$ or $B$.
-All cases are $\#bc(C_{i-1}) > \#bc(C_{i})$ as follows.
-
-\begin{itemize}
-\item{Case of $t_0$}\\
-  Let us consider points $n_3,n_4$.
-At least one of the points $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-If $n_3$ is free, then $p^\prime$ has to be bound to a bead other than $n_1$ to deterministically stabilize.
-In this situation, at least three neighbors of $n_1$ are free, that is, $n_1$ has at least one free hand from Lemma~ \ref{TTT_neighbor_lemma}.
-Hence, $p^\prime$ must be bound to $n_1$.
-Thus, a case of $t_0$ consumes two hands and it does not supply any binding capabilities.
-
-\item{Case of $t_{\pm 60}$}\\
-  In this case, too, $n_4$ or $n_5$ is free.
-If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$.
-If $n_5$ is occupied, then $n_4$ is free.
-This time, by $n_2$ has some free hands so $p^\prime$ has to be bound to $n_2$.
-
-  In this situation, $p^\prime$ is able to supply a binding capabilities which could bind a bead into $n_4$ or $n_5$.
-However, $n_2$ and $n_3$ are part of a contiguous conformation.
-According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive.
-Thus, in the case of $t_{\pm 60}$ $\#bc(C_{i-1}) > \#bc(C_{i})$.
-
-\item{Case of $t_{\pm 120}$}\\
-  Binding capabilities that $p^\prime$ supplies are inactive according to Jordan curve theorem on $n_1$ and $n_2$.
-Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
-Thus, in the case of $t_{\pm 120}$ is $\#bc(C_{i-1}) > \#bc(C_{i})$.
-
-\end{itemize}
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{ccc}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-	 \draw[->,white] (120:0.8)--(120:0.1);%for adjustment
-
-            \fill[blue] (0,0) circle [radius=0.05];
-            \node[below] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,180}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {120,-120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (0:0.1)--(0:0.9);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-
-          \node at (0,-2) {$t_{0}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-
-            \fill(0,0) circle [radius=0.05];
-            \node[below] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)},blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {180,-120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (120:0.9)--(120:0.1);
-            \draw[->, blue] (0:0.1)--(0:0.9);
-
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {$t_{\pm 60}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-      \centering
-        \begin{tikzpicture}
-            \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
-
-            \foreach \theta in {0}{
-              \fill[transform canvas={shift=(\theta:1)}, blue](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \foreach \theta in {180,-120,120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-            \draw[->, blue] (60:1.1)--(60:0.1);
-            \draw[->, blue] (0:0.1)--(0:1.1);
-
-            \node[transform canvas={shift=(0:1)},below] {$n_0$};
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-            \node[transform canvas={shift=(120:1)},left] {$n_3$};
-            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
-
-          \node at (0,-2) {$t_{\pm 120}$};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Direction into a entrance}
-    \label{TTT_tunnel_direction}
-  \end{center}
-\end{figure}
-
-\end{proof}
-
 \begin{proof}[Lemma~ \ref{TTT_exit}]
@@
 
-\begin{paragraph}{}
-$\delta = 1, \alpha = 2$\\
 Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$. We assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$ and
@@
 Thus, $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
-\end{paragraph}
 
@@
 
-\begin{paragraph}{}
-$\delta = 1, \alpha \geq 3$\\
-Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha \geq 3$. We assume $w[i]$ is stabilized at exit of tunnel.
-In all cases $\#bc(C_{i-1}) > \#bc(C_{i})$.
-Moreover, if $S[k] = t (k \leq i)$, then $\#bc(C_{k-1}) > \#bc(C_{k})$ because both sides of the path $p$ in Fig.\ref{TTT_inside_tunnel} ($n_1, n_2$) have two free points and one of $n_1, n_2$ is not the predecessor so that it has hand and moreover that $w[k]$ supplies any binding capabilities because its neighbors are occupied by beads of tunnel.
-\end{paragraph}
-
-\begin{itemize}
-\item{Case of $n_1$ and $n_2$ are free}\\
-  In $\alpha \geq 3$, if three neighbors of a bead leave, then it can supply two binding capabilities.
-Therefore predecessor $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$, too.
-In this case, at least four bindings are consumed and at most two are added.
-Thus, it consumes some binding capabilities, overall.
-
-\item{Case of $n_1$ is occupied}\\
-  In this case, $n_4$ leave at least two bindings and $n_3$, $n_1$ also leave at least one binding.
-Therefore $n_5$ has to be bound $n_3$ and $n_4$, and $p^\prime$ also has to be bound $n_1$ and $n_4$.
-In this case, at least four bindings are consumed and at most two are added.
-Thus, it consumes some binding capabilities, totally.
-\end{itemize}
-
 \begin{figure}
@@
     \begin{tabular}{cc}
-    \begin{minipage}{0.66\hsize}
-    \centering
-      \begin{tabular}{cc}
+    \centering
       \begin{minipage}{0.45\linewidth}
@@
             \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$p^\prime$};
+            \node[above] at (0,0) {$w[i]$};
 
@@
             \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
+            \node[transform canvas={shift=(180:1)},left] {$w[i-1]$};
 
@@
             \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$n_5$};
+            \node[transform canvas={shift=(180:1)},above] {$w[i-1]$};
 
@@
     \label{TTT_tunnel_exit}
-    \end{minipage}
-
-    \begin{minipage}{0.33\hsize}
-    \centering
-     \begin{tikzpicture}
-	\draw[white] (0:0) -- (120:1);
-	\draw[white] (0:0) -- (-60:1);
-            \fill[blue](0,0) circle [radius=0.05];
-            \draw[blue] (0:1) circle [radius = 0.05];
-            \draw[->] (0:0.1) -- node[above]{$p$} (0:0.9);
-
-            \foreach \theta in {60, -60, 120,-120,180}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-            \node[transform canvas={shift=(60:1)},right] {$n_1$};
-            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
-                \end{tikzpicture}
-
-    \caption{Inside tunnel}
-    \label{TTT_inside_tunnel}
-    \end{minipage}
-
-    \end{tabular}
 \end{figure}
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{lemma}
+\label{TTT_tunnelC_lemma}
+Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
+We assume $S[h..i+1] = bt^{(i-h)}b \quad (1<h<i)$.
+If at least one of $w[h+1..i]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_i)$.
+\end{lemma}
 
@@
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%%%
+%%%%%%
+%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\proof%{Proof of Tunnel Troll Theorem}
+Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
+then it has at most one free neighbor, and hence its successor it to be stabilized there.
+Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.
+
+Tunnel sections have three possible shapes up to symmetry : straight($S$), obtuse($O$) and acute($A$) turn (Fig. \ref{TTT_tunnel}), and we will consider each of those.
+
+%\begin{lemma}
+%\label{TTT_neighbor_lemma}
+%For unary transcripts at $\delta = 1$, if a bead has no free hand, then at least $\alpha + 2$ of its neighbors have to be occpied.
+%\end{lemma}
+
+Let us first consider cases of $\delta \geq 3, \alpha = 1$. 
+See Fig.~\ref{TTT_tunnel_exit}. Consider the stabilization of $w[i]$. 
+This bead $w[i]$, once stabilized, shares two neighbors with its predecessor $w[i-1]$, which are denoted by $n_3, n_4$. 
+Both of them have been already occupied because $S[i] = t$.
+
+Since $S[i+1] \neq \blacksquare$, at least one of the other three neighbors, denoted by $n_0, n_1, n_2$, must be free. 
+Assume that in the neighborhood of $w[i]$, there are two beads with one free neighbor even after $w[i]$ is stabilized. 
+Before the stabilization of $w[i]$, such a bead had two free neighbors, and hence, is provided with at least one free bond. 
+Thus, $w[i]$ is to be bonded to these two beads, and it decreases the binding capability by at least 1. 
+It now suffices to check that this assumption holds no matter how $n_0, n_1, n_2$ are occupied as long as at least one of them is left free.
+
+Next, we consider the case of $\delta = 2, \alpha = 1$.
+We assume there is an index $h$ such that $S[h-1..h+1] = bbt$ or $S[h-1..h+1] = tbt$.
+According to Lemma~\ref{TTT_entrance_Tab}, if $w[h+1]$ is stabilized by tunnel $A$ or $B$, then $\#bc(C_{h-1}) > \#bc(C_{h})$.
+Also,  According to Lemma~\ref{TTT_tunnelC_lemma}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
+On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of Lemma~\ref{TTT_exit}.
+Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.
+
+\qed
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{ccc}
+
+      \begin{minipage}{0.3\hsize}
+        \begin{tikzpicture}
+          \begin{scope}[xshift=2cm, yshift=2cm]
+            \draw(0,0) circle [radius=0.05];
+            \node[above] at (180:1) {$p^\prime$};
+            \node[above] at (0:1) {$p^\prime$};
+
+            \foreach \theta in {0,180}{
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {60,-60,120,-120}{
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+          \end{scope}
+
+          \node at (2,0) {Tunnel $S$};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.3\hsize}
+        \begin{tikzpicture}
+
+          \begin{scope}[xshift=2cm, yshift=2cm]
+            \draw(0,0) circle [radius=0.05];
+            \node[above] at (180:1) {$p^\prime$};
+            \node[above] at (-60:1) {$p^\prime$};
+
+            \foreach \theta in {-60,180}{
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {0,60,120,-120}{
+ 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+          \end{scope}
+
+          \node at (2,0) {Tunnel $O$};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.3\hsize}
+        \begin{tikzpicture}
+
+          \begin{scope}[xshift=2cm, yshift=2cm]
+            \draw(0,0) circle [radius=0.05];
+            \node[above] at (180:1) {$p^\prime$};
+            \node[above] at (-120:1) {$p^\prime$};
+
+            \foreach \theta in {-120,180}{
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {0,60,-60,120}{
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+          \end{scope}
+
+          \node at (2,0) {Tunnel $A$};
+        \end{tikzpicture}
+      \end{minipage}
+
+    \end{tabular}
+    \caption{All possible tunnel sections: straight, obtuse turn, and acute turn}
+    \label{TTT_tunnel}
+  \end{center}
+\end{figure}
 

### 2018-12-01 tt_theorem.tex
12/1

@@
 Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$, arity $\alpha =2$. 
-Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $S[i] = b$ and $S[i+1] \in \{ t_s, t_o \} $, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
+Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $S[i+1] = b$ and $S[i+2] \in \{ t_s, t_o \} $, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
 \end{lemma}
@@
 \begin{proof}[lemma \ref{TTT_entrance_Tab}]
-Fig.\ref{TTT_tunnel_direction} exhibits all the three kinds of entrance of tunnel A, B.
-Let $w[i]$ be stabilized at an entrance point of Tunnel $A$ or $B$.
-All cases are $\#bc(C_{i-1}) > \#bc(C_{i})$ as follows.
+See Fig.\ref{TTT_tunnel_direction}.
+$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section type of $S$ or $O$.
+Thus,  its predecessor $w[i+1]$ must be inside the tunnel section, that is, $n_1$ and $n_2$ must be occupied.
+Free bonds of $w[i]$, if any, cannot be used in future by another bead $w[j]$ because otherwise the part of transcript $w[i..j]$ and the bond between $w[i]$ and $w[j]$ would form a closed curve and the curve would cross the path of $C_{i-1}$ between $n_1$ and $n_2$, contradiction.
+%Binding capabilities that $w[i]$ supplies are inactive according to Jordan curve theorem on $n_1$, $n_2$, and $w[i]$.
+Therefore, if $w[i]$ forms a bond at its stabilization $\#bc(C_{i-1}) > \#bc(C_{i})$ holds.
+Hence, assume $w[i]$ does not form any bond at stabilization.
+Then $w[i-1]$ is not on $n_1$ or $n_2$.
 
-\begin{itemize}
-\item{Case of $t_0$}\\
-  Let us consider points $n_3,n_4$.
-At least one of the points $n_3$ or $n_4$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
-If $n_3$ is free, then $p^\prime$ has to be bound to a bead other than $n_1$ to deterministically stabilize.
-In this situation, at least three neighbors of $n_1$ are free, that is, $n_1$ has at least one free hand from Lemma~ \ref{TTT_neighbor_lemma}.
-Hence, $p^\prime$ must be bound to $n_1$.
-Thus, a case of $t_0$ consumes two hands and it does not supply any binding capabilities.
+On the other hand, let us consider $S[i] = t$.
+Beads which are shared by neighbors of $w[i-1]$ and $w[i]$ are occupied so that we consider only Fig.~\ref{TTT_tunnel_direction} (Left) and (Middle) case because (Right) case is not occupied them.
+In the (Left) case, if $S[i] = t$, points $n_3$ and $n_4$ are occupied. Then, $S[i+1] = t$, contradiction.
+In the (Middle) case, if $S[i] = t$, $n_4$ is free and $n_5$ is occupied because of $S[i+1] = b$.
+This time, by $n_4$ has some free hands because at least three neighbors of $n_4$ are free so $w[i]$ has to be bound to $n_2$. Thus, $\#bc(C_{i-1}) > \#bc(C_{i})$.
 
-\item{Case of $t_{\pm 60}$}\\
-  In this case, too, $n_4$ or $n_5$ is free.
-If $n_5$ is free, $p^\prime$ has to be bound to $n_1$ or $n_2$.
-If $n_5$ is occupied, then $n_4$ is free.
-This time, by $n_2$ has some free hands so $p^\prime$ has to be bound to $n_2$.
-
-  In this situation, $p^\prime$ is able to supply a binding capabilities which could bind a bead into $n_4$ or $n_5$.
-However, $n_2$ and $n_3$ are part of a contiguous conformation.
-According to Jordan curve theorem, any successors of $p^\prime$ cannot reach a point $n_4$ or $n_5$ so this capability is inactive.
-Thus, in the case of $t_{\pm 60}$ $\#bc(C_{i-1}) > \#bc(C_{i})$.
-
-\item{Case of $t_{\pm 120}$}\\
-  Binding capabilities that $p^\prime$ supplies are inactive according to Jordan curve theorem on $n_1$ and $n_2$.
-Moreover, $p^\prime$ has to be bound to one of $n_3, n_4, n_5$ in order to deterministically stabilize.
-Thus, in the case of $t_{\pm 120}$ is $\#bc(C_{i-1}) > \#bc(C_{i})$.
-
-\end{itemize}
+%In the case of $t_0$, one of $n_3$ and $n_4$ is free because of $S[i+1] = b$. Thus, this case is only $S[i] = b$.
+%
+%
+%In the case of $t_{\pm 60}$, if $S[i] = t$, the point $n_4$ is free and $n_5$ is occupied.
+This time, by $n_2$ has some free hands because at least three neighbors of $n_2$ are free so $w[i]$ has to be bound to $n_2$.
+Thus, $\#bc(C_{i-1}) > \#bc(C_{i})$.
+%
+%In the case of $t_{\pm120}$, the point of $w[i+1]$ is free before $w[i+1]$ is stabilized. Thus, this case is only $S[i] = b$.
+%
 
@@
         \begin{tikzpicture}
+        \draw[->, white] (0:0)--(-120:1);
 	 \draw[->,white] (120:0.8)--(120:0.1);%for adjustment
@@
             \node[below] at (0,0) {$w[i]$};
+            \node[below] at (0:1) {$w[i+1]$};
 
@@
 
-          \node at (0,-2) {$t_{0}$};
+         % \node at (0,-2) {$t_{0}$};
         \end{tikzpicture}
@@
         \begin{tikzpicture}
-
+	\draw[->, white] (0:0)--(-120:1);
             \fill(0,0) circle [radius=0.05];
             \node[below] at (0,0) {$w[i]$};
+            \node[below] at (0:1) {$w[i+1]$};
 
@@
 
-          \node at (0,-2) {$t_{\pm 60}$};
+          %\node at (0,-2) {$t_{\pm 60}$};
         \end{tikzpicture}
@@
         \begin{tikzpicture}
+        \draw[->, white] (0:0)--(-120:1);
             \fill[blue](0,0) circle [radius=0.05];
             \node[below] at (0,0) {$w[i]$};
+            \node[below] at (0:1) {$w[i+1]$};
 
@@
 
-            \node[transform canvas={shift=(0:1)},below] {$n_0$};
+            %\node[transform canvas={shift=(0:1)},below] {$n_0$};
             \node[transform canvas={shift=(60:1)},right] {$n_1$};
@@
 
-          \node at (0,-2) {$t_{\pm 120}$};
+         % \node at (0,-2) {$t_{\pm 120}$};
         \end{tikzpicture}
@@
             \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},left] {$w[i-1]$};
+            \node[transform canvas={shift=(180:1)},above] {$w[i-1]$};
 
@@
 
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{ccc}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (0:1) {$p^\prime$};
-
-            \foreach \theta in {0,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {60,-60,120,-120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel $S$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-60:1) {$p^\prime$};
-
-            \foreach \theta in {-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {0,60,120,-120}{
- 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel $O$};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.3\hsize}
-        \begin{tikzpicture}
-
-          \begin{scope}[xshift=2cm, yshift=2cm]
-            \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-120:1) {$p^\prime$};
-
-            \foreach \theta in {-120,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
-
-            \foreach \theta in {0,60,-60,120}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-          \end{scope}
-
-          \node at (2,0) {Tunnel $A$};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{All possible tunnel sections: straight, obtuse turn, and acute turn}
-    \label{TTT_tunnel}
-  \end{center}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite structures whose size is $\mathcal{O}(n)$.
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite structures whose size is $O(n)$.
 \end{theorem}
@@
 \begin{theorem}[$\delta = 1, \alpha = 4$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite structures whose size is $\mathcal{O}(n^2)$.
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite structures whose size is $O(n^2)$.
 \end{theorem}
@@
 Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$.
-Hence oritatami system can yield only a finite structure whose size is $\mathcal{O}(n^2)$ in $\delta =1, \alpha = 4$.
+Hence oritatami system can yield only a finite structure whose size is $O(n^2)$ in $\delta =1, \alpha = 4$.
 %lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left

### 2018-12-01 paper.tex
Added pyramid part, polished arity 1, delay 3, unary
The pyramid part still needs some work, as does the arity 1, delay 2.

I went over Reoto's arity 1, delay 3 and made some changes to make it more readable. For now I commented out the last 2 paragraphs, as they are not necessary for the proof, I think. However, here we need to add some conclusion to the arguments of the previous two subsections.
12/1
Afternoon commit
S.S. started writing an intro for TT theorem.

@@
 
+\usepackage{graphbox}
 \usepackage{wasysym}
@@
 Szil\'{a}rd Zsolt Fazekas\inst{1} \and
-Shinnosuke Seki\inst{2}\thanks{Corresponding author}}
+Shinnosuke Seki\inst{2}\thanks{Corresponding author (\email{s.seki@uec.ac.jp})}}
 \institute{
@@
 1-1 Tegate Gakuen-machi, Akita, 0108502, Japan \\
-\email{szilard.fazekas@ie.akita-u.ac.jp}
+%\email{szilard.fazekas@ie.akita-u.ac.jp}
 \and
@@
 1-5-1 Chofugaoka, Chofu, Tokyo, 1828585, Japan \\
-\email{s.seki@uec.ac.jp}
 }
@@
 \section{Case of delay $1$}
-
-\input{ttt}
+\input{tt_intro}
+\input{tt_theorem}
 

### 2018-12-01 tt_intro.tex
12/1 after lunch
Afternoon commit
S.S. started writing an intro for TT theorem.

@@
 
-%Let $\Xi$ be a deterministic oritatami system of delay 1 and arity 2. Assume its seed $\sigma$ consists of $n$ beads.
+Let $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ be a deterministic oritatami system of delay 1. 
 For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$, that is, foldable by $\Xi$. Hence $C_0 = \sigma$.
-
-Let us consider the stabilization of the $i$-th bead $a_i$ upon $C_{i-1}$.
-The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1.
-There are just two ways to get stabilized at delay 1.
-One way is to be bound to another bead.
-The other way is through a $tunnel\ section$.
-A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
-Accordingly, how they are stabilized can be described by a sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
-We let $S$ take the value $\blacksquare$ for halt.
-
-Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
-We call such a point $p$ the $inside\ of\ a\ tunnel$ and points $p^\prime$ the $entrance\ of\ a\ tunnel$ except when $p^\prime$ is inside of a tunnel.
-If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor.
-In this way, $w[i]$ can get stabilized without being bound.
-
-%If a bead is stabilized through a tunnel section, then it can provide some bonds.
-Let us consider bonds of $C_i$.
-$C_i$ is represented $C = (W,P,H)$ where $|W| = i + n$ $C_i$ contains $\alpha \cdot (i + n) - 2|H|$ bonds because $C_i$ consists of $i + n$ beads and a bead has just $\alpha$ bonds and then $2 |H|$ of the those bonds are already used.
-However, even if a bead has an available bond, $w[j]$ $(j > i)$ might not be able to use this bond because the bond has possibility that it is blocked by transcripts $w[i+1..j-1]$.
-Number of $binding\ capabilities$ does not contain that case so that it is at most $\alpha \cdot (i + n) - 2|H|$.
-
-We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$.
-We define $binding\ capability$ with reachable.
-
-\begin{definition}[binding capability]
-Let $C = (P,w,H)$ be a conformation.
-Let $B_k$ be $H \cap \{ (i,j) \mid \mbox{$i=k$ or $j=k$} \}$. Moreover, let $R_k$ be a set of neighbors of the point $P[k]$ that are free and reachable from $C$.
- The binding capability of $C$, denoted by $\#bc(C)$, is defined by $\sum^{|w|}_{k=1} \min \{ |B_k|, |R_k|  \}$.
-\end{definition}
 
@@
 \end{figure}
+
+\begin{figure}
+  \begin{center}
+    \begin{tabular}{ccc}
+
+      \begin{minipage}{0.3\hsize}
+        \begin{tikzpicture}
+          \begin{scope}[xshift=2cm, yshift=2cm]
+            \draw(0,0) circle [radius=0.05];
+            \node[above] at (180:1) {$p^\prime$};
+            \node[above] at (0:1) {$p^\prime$};
+
+            \foreach \theta in {0,180}{
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {60,-60,120,-120}{
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+          \end{scope}
+
+          \node at (2,0) {Type S};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.3\hsize}
+        \begin{tikzpicture}
+
+          \begin{scope}[xshift=2cm, yshift=2cm]
+            \draw(0,0) circle [radius=0.05];
+            \node[above] at (180:1) {$p^\prime$};
+            \node[above] at (-60:1) {$p^\prime$};
+
+            \foreach \theta in {-60,180}{
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {0,60,120,-120}{
+ 	            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+          \end{scope}
+
+          \node at (2,0) {Type O};
+        \end{tikzpicture}
+      \end{minipage}
+
+      \begin{minipage}{0.3\hsize}
+        \begin{tikzpicture}
+
+          \begin{scope}[xshift=2cm, yshift=2cm]
+            \draw(0,0) circle [radius=0.05];
+            \node[above] at (180:1) {$p^\prime$};
+            \node[above] at (-120:1) {$p^\prime$};
+
+            \foreach \theta in {-120,180}{
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
+            }
+
+            \foreach \theta in {0,60,-60,120}{
+              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+            }
+          \end{scope}
+
+          \node at (2,0) {Type A};
+        \end{tikzpicture}
+      \end{minipage}
+
+    \end{tabular}
+    \caption{Tunnel sections of all possible three types: straight (Type S), obtuse turn (Type O), and acute turn (Type A).}
+    \label{fig:TTT_tunnel}
+  \end{center}
+\end{figure}
+
+At delay 1, a bead cannot collaborate with its successors in order to stabilize itself. 
+In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts). 
+One is to be bound and the other is through a 1-in-1-out structure called the tunnel section. 
+See Fig.~\ref{fig:TTT_tunnel}. 
+A \textit{tunnel section} consists of four beads that occupy four neighbors of one point.
+
+Let us consider the stabilization of the $i$-th bead $w[i]$ of the transcript $w$ upon $C_{i-1}$. 
+The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1.
+There are just two ways to get stabilized at delay 1.
+One way is to be bound to another bead.
+The other way is through a $tunnel\ section$.
+A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
+Accordingly, how they are stabilized can be described by a sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
+We let $S$ take the value $\blacksquare$ for halt.
+
+Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
+We call such a point $p$ the $inside\ of\ a\ tunnel$ and points $p^\prime$ the $entrance\ of\ a\ tunnel$ except when $p^\prime$ is inside of a tunnel.
+If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor.
+In this way, $w[i]$ can get stabilized without being bound.
+
+%If a bead is stabilized through a tunnel section, then it can provide some bonds.
+Let us consider bonds of $C_i$.
+$C_i$ is represented $C = (W,P,H)$ where $|W| = i + n$ $C_i$ contains $\alpha \cdot (i + n) - 2|H|$ bonds because $C_i$ consists of $i + n$ beads and a bead has just $\alpha$ bonds and then $2 |H|$ of the those bonds are already used.
+However, even if a bead has an available bond, $w[j]$ $(j > i)$ might not be able to use this bond because the bond has possibility that it is blocked by transcripts $w[i+1..j-1]$.
+Number of $binding\ capabilities$ does not contain that case so that it is at most $\alpha \cdot (i + n) - 2|H|$.
+
+We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$.
+We define $binding\ capability$ with reachable.
+
+\begin{definition}[binding capability]
+Let $C = (P,w,H)$ be a conformation.
+Let $B_k$ be $H \cap \{ (i,j) \mid \mbox{$i=k$ or $j=k$} \}$. Moreover, let $R_k$ be a set of neighbors of the point $P[k]$ that are free and reachable from $C$.
+ The binding capability of $C$, denoted by $\#bc(C)$, is defined by $\sum^{|w|}_{k=1} \min \{ |B_k|, |R_k|  \}$.
+\end{definition}

### 2018-12-01 tt_theorem.tex
finished proof of lemma 1,2

@@
 Therefore, if $w[i]$ forms a bond at its stabilization $\#bc(C_{i-1}) > \#bc(C_{i})$ holds.
-Hence, assume $w[i]$ does not form any bond at stabilization.
-Then $w[i-1]$ is not on $n_1$ or $n_2$.
+We now prove that $w[i]$ must form a bond.
 
-On the other hand, let us consider $S[i] = t$.
-Beads which are shared by neighbors of $w[i-1]$ and $w[i]$ are occupied so that we consider only Fig.~\ref{TTT_tunnel_direction} (Left) and (Middle) case because (Right) case is not occupied them.
-In the (Left) case, if $S[i] = t$, points $n_3$ and $n_4$ are occupied. Then, $S[i+1] = t$, contradiction.
-In the (Middle) case, if $S[i] = t$, $n_4$ is free and $n_5$ is occupied because of $S[i+1] = b$.
-This time, by $n_4$ has some free hands because at least three neighbors of $n_4$ are free so $w[i]$ has to be bound to $n_2$. Thus, $\#bc(C_{i-1}) > \#bc(C_{i})$.
-
-%In the case of $t_0$, one of $n_3$ and $n_4$ is free because of $S[i+1] = b$. Thus, this case is only $S[i] = b$.
-%
-%
-%In the case of $t_{\pm 60}$, if $S[i] = t$, the point $n_4$ is free and $n_5$ is occupied.
-This time, by $n_2$ has some free hands because at least three neighbors of $n_2$ are free so $w[i]$ has to be bound to $n_2$.
-Thus, $\#bc(C_{i-1}) > \#bc(C_{i})$.
-%
-%In the case of $t_{\pm120}$, the point of $w[i+1]$ is free before $w[i+1]$ is stabilized. Thus, this case is only $S[i] = b$.
-%
+Suppose $w[i]$ ware stabilized without any bond, that is, by a tunnel.
+For that the two points that are a neighbor of both $w[i-1]$ and $w[i]$ must be occupied already.
+In addition, at least one of the neighbors of $w[i]$ must be free because $S[i+1] = b$.
+Thus, only the case to be considered is Fig.~\ref{TTT_tunnel_direction} (middle) with $n_5$ being occupied (that is, $n_4$ is free).
+In this case, before $w[i]$ is stabilized, at lest three neighbors of $n_2$ ware free and hence, a bead at $n_2$ was provided with one free bond and could form a bond with $w[i]$. \qed
 
@@
 \label{TTT_exit}
-Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. 
-Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
-At $\delta = 1, \alpha =2$, if we assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$, then $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
+Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$ and arity $\alpha =2$.
+%Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
+If $S[h..i+1] = bt^{(i-h)}b$ for some $h<i-1$, then $\#bc(C_{i-2}) \geq \#bc(C_i)$, and hence, $\#bc(C_{h-1}) \geq \#bc(C_i)$.
+If $h < i-1$, then the second inequality is strengthened as $\#bc(C_{h-1}) > \#bc(C_{i})$.
 %if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
-On the other hand, if we assume $S[k] = t (k \leq i)$ at $\delta =1, \alpha \geq 3$, then $\#bc(C_{k-1}) > \#bc(C_{k})$.
 \end{lemma}
 
-\begin{proof}[Lemma~ \ref{TTT_exit}]
-Fig.\ref{TTT_tunnel_exit} exhibits all the two kinds of exit of tunnel. 
-At least one of points $n_1$ or $n_2$ is free because if both of them are occupied, $p^\prime$ is inside of tunnel.
+\begin{proof}%[Lemma~ \ref{TTT_exit}]
+Since the binding capability never increases inside a tunnel, we just need to consider the exit of a tunnel.
+See Fig.\ref{TTT_tunnel_exit}. 
+At least one of points $n_1$ or $n_2$ must be free because otherwise $w[i]$ would be inside of a tunnel, that is, $S[i+1]$ would not be $b$.
 
-Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$. We assume $S[h..i+1] = bt^{(i-h)}b \quad (h<i)$ and
-let $a$ be $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$.
-Then, $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$ as follows.
-Also, if $i - h > 1$ and $j$ is such that $h<j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because all neighbors of $w[j]$ are occupied by beads forming the tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$.
-Thus, $\#bc(C_{h-1}) \geq \#bc(C_i)$ and $\#bc(C_{i-2}) \geq \#bc(C_i)$.
+%If $i - h > 1$ and $j$ is such that $h \leq j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because all neighbors of $w[j]$ are occupied by beads forming the tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$.
+%Thus, inside this tunnel, binding capabilities never increased.
+
+Let $a$ be the number of bonds $w[i-1]$ forms, that is, $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$. Then, $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$ as follows.
 
@@
 \end{itemize}
+
+Thus,$\#bc(C_{i-2}) \geq \#bc(C_i)$ , and hence, $\#bc(C_{h-1}) \geq \#bc(C_i)$.
+If $h < i-1$, then the second inequality is strengthened as $\#bc(C_{h-1}) > \#bc(C_{i})$ because $S[h] = b$, that is, $\#bc(C_{h-1}) > \#bc(C_h)$ and $\#bc(C_{h}) \geq \#bc(C_i)$. \qed
 
@@
 Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
+If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $t_a \in S[h+1..i]$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
+\end{lemma}
+
+%\begin{lemma}
+%\label{TTT_tunnelC_lemma}
+%Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
 We assume $S[h..i+1] = bt^{(i-h)}b \quad (1<h<i)$.
 If at least one of $w[h+1..i]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_i)$.
-\end{lemma}
+%\end{lemma}
 

### 2018-12-01 tt_theorem.tex
12/1 before dinner

@@
 
-\begin{proof}[lemma \ref{TTT_entrance_Tab}]
+\begin{proof}%[lemma \ref{TTT_entrance_Tab}]
 See Fig.\ref{TTT_tunnel_direction}.
-$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section type of $S$ or $O$.
+$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section of type $S$ or $O$.
 Thus,  its predecessor $w[i+1]$ must be inside the tunnel section, that is, $n_1$ and $n_2$ must be occupied.
@@
 Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
-If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $t_a \in S[h+1..i]$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
+If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ and $S[i+2] = t_a$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $S[i+l+2] = t_a$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
 \end{lemma}
@@
 \\
+
+\subsubsection{Case of $S[h-1..h+1] = bbt$}
+See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
+If $w[h-1]$ forms one bond, then it leaves one free bond, but it is consumed by $w[h+1]$.
+In addition, $w[h]$ has to bound.
+Thus, in this cases, binding capability decreases by 1.
+If $w[h-1]$ forms two bonds, then it does not leave any bond.
+In addition, $w[h]$ has to be bound.
+Thus, in this case, even if $w[h+1]$ supplies two free bonds, binding capability decreases by 1.
+
+\begin{figure}
+  \begin{center}
+        \begin{tikzpicture}
+        \draw[->,white] (-70:0.1) -- (-70:3);
+          \foreach \theta in {60,-60,120,0}{
+            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+          }
+
+          \fill[blue](180:1) circle [radius=0.05];
+          \fill[blue](0:0) circle [radius=0.05];
+
+          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
+          \draw[->, blue] (180:0.9) -- (180:0.1);
+          \draw[->, blue] (-120:0.1) -- (-120:0.9);
+
+          \node[below left] at (180:1) {$w[h-1]$};
+          \node[above] at (0:0) {$w[h]$};
+          \node[below] at (-120:1) {$w[h+1]$};
+
+          \node[right] at (120:1) {$n_3$};
+          \node[right] at (60:1) {$n_2$};
+          \node[right] at (0:1) {$n_1$};
+
+          \begin{scope}[shift=(-120:1)]
+            \fill[blue](0,0) circle [radius=0.05];
+            \foreach \theta in {-120,-60,180}{
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+            }
+
+          \end{scope}
+        \end{tikzpicture}
+    \caption{Case of $S[h-1..h+1] = bbt$}
+    \label{TTT_tunnelC_enter_usingBond}
+  \end{center}
+\end{figure}
 
@@
     \label{TTT_tunnelC_enter_usingTunnel}
-\end{figure}
-
-\subsubsection{Case of $S[h-1..h+1] = bbt$}
-Let us consider number of consumed bindings by $w[h-1]$ (Fig.\ref{TTT_tunnelC_enter_usingBond}).
-
-\begin{itemize}
-\item{$w[h-1]$ consumes one binding}\\
-  In this situation, $w[h-1]$ supplies one active binding whereas $w[h+1]$ consumes this binding. In addition, $w[h]$ has to bound to one of $n_1, n_2, n_3$.
-  Thus, in this cases consume some binding capabilities.
-
-\item{$w[h-1]$ consumes two bindings}\\
-  In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies at most two bindings. Thus, in this cases consume some binding capabilities.
-\end{itemize}
-
-\begin{figure}
-  \begin{center}
-        \begin{tikzpicture}
-        \draw[->,white] (-70:0.1) -- (-70:3);
-          \foreach \theta in {60,-60,120,0}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \fill[blue](180:1) circle [radius=0.05];
-          \fill[blue](0:0) circle [radius=0.05];
-
-          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
-          \draw[->, blue] (180:0.9) -- (180:0.1);
-          \draw[->, blue] (-120:0.1) -- (-120:0.9);
-
-          \node[below left] at (180:1) {$w[h-1]$};
-          \node[above] at (0:0) {$w[h]$};
-          \node[below] at (-120:1) {$w[h+1]$};
-
-          \node[right] at (120:1) {$n_3$};
-          \node[right] at (60:1) {$n_2$};
-          \node[right] at (0:1) {$n_1$};
-
-          \begin{scope}[shift=(-120:1)]
-            \fill[blue](0,0) circle [radius=0.05];
-            \foreach \theta in {-120,-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-          \end{scope}
-        \end{tikzpicture}
-    \caption{Case of $S[h-1..h+1] = bbt$}
-    \label{TTT_tunnelC_enter_usingBond}
-  \end{center}
 \end{figure}

### 2018-12-01 tt_intro.tex
S.S. commit before dinner
I'm still working on the intro for TTT.

@@
 See Fig.~\ref{fig:TTT_tunnel}. 
-A \textit{tunnel section} consists of four beads that occupy four neighbors of one point.
-
-Let us consider the stabilization of the $i$-th bead $w[i]$ of the transcript $w$ upon $C_{i-1}$. 
-The bead cannot collaborate with any succeeding bead $w[i+1],w[i+2],\cdots$ at delay 1.
-There are just two ways to get stabilized at delay 1.
-One way is to be bound to another bead.
-The other way is through a $tunnel\ section$.
-A tunnel section consists of four beads that occupy four neighbors of a point (Fig.\ref{TTT_tunnel_intro}).
-Accordingly, how they are stabilized can be described by a sequence $S$ of $b$'s (bound) and $t$'s (tunnel section); priority is given to $t$, that is, $S[i] = t$ if the $i$-th bead $w_i$ is stabilized not only by being bound but also through a tunnel section.
-We let $S$ take the value $\blacksquare$ for halt.
+A \textit{tunnel section} consists of four beads that occupy four neighbors of one free point. 
+The behavior of a deterministic oritatami system at delay 1 can be described by a sequence of $S$ of $b$ (bound), $t_s$ (straight tunnel section), $t_o$ (obtuse-turn tunnel section), and $t_a$ (acute-turn tunnel section); priority is given to tunnel, that is, $S[i]$ is $t_s$ (resp.~$t_o$, $t_a$) if the $i$-th bead of the system is stabilized not only by being bonded but also through a straight (resp.
+obtuse-turn, acute-turn) tunnel section.
+We let $S$ take the value $\blacksquare$ for halt (due to the lack of free neighbors).
 
@@
 We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. 
-We define $binding\ capability$ with reachable.
+Taking this reachability into account, we define the \textit{binding capability} of a conformation as the number of free bonds of its beads available geometrically for elongations of $C$.
+It is defined formally as follows:
 

### 2018-12-02 arity1.tex
Rewrote the Chichen Itza part
The previous version was hard to follow, because one got lost in the details. I think now it is much more readable and looks more organized.

The only modification to the main file, paper.tex are some package declarations.

@@
 \subsection{$\alpha = 1$, arbitrary alphabets}
+First we present a lower bound construction for arity $\alpha=1$ systems.
+At $\alpha=1$, allowing delay $\delta=2$ increases the power of OS compared with $\delta=1$, if at least four bead types are allowed.
+We demonstrate this with an infinite family of OS, which fold deterministically a transcript of length $\frac{(n-1)^2}{4}$ starting from a given seed of length $n$.
 
-At arity $1$, allowing delay $2$ increases the power of OS compared with $\delta=1$, if at least four bead types are allowed.
-We demonstrate this with an infinite family of OS, which fold deterministically a transcript of length $\frac{(n-1)^2}{4}$ when receiving a given seed of length $n$.
-
-Consider a delay $2$, arity $1$ system with bead types $B_0$ to $B_4$ and attraction rules $\{B_1-B_1,B_2-B_2, B_3-B_3,B_4-B_4\}$.
-Let the seed be a conformation of a $4k+1$ long bead sequence of the form $(B_1B_0B_2B_0)^kB_0$.
-Bead $i$ of the seed is fixed at point $(i,0)$, for all $1\leq i\leq 4k-1$.
+Consider the following $\delta=2$, $\alpha=1$ system with bead types $\{0,1,2,3,4\}$ and attraction rules $\{(1,1),(2,2), (3,3),(4,4)\}$.
+Let the seed $\sigma$ be a conformation of a $4k+1$ long bead sequence of the form $(1020)^k0$, such that bead $\sigma[i]$ of the seed is stabilized at point $(i,0)$, for all $1\leq i\leq 4k-1$.
 Bead $4k$ is at $(4k-1,-1)$ and bead $4k+1$ is at $(4k,0)$.
@@
 \begin{center}
-	\scriptsize
-	\begin{tabular}{llllll}
-		$p=$ & $(B_2B_4B_1B_3)^{k-1}$ & $B_2B_4(B_1B_4B_2B_3)^{k-1}$ & $B_1B_4(B_1B_3B_2B_4)^{k-2}$ & $B_1B_3(B_2B_3B_1B_4)^{k-2}$ & $B_2B_3$\\
-		& $(B_2B_4B_1B_3)^{k-3}$ & $B_2B_4(B_1B_4B_2B_3)^{k-3}$ & $B_1B_4(B_1B_3B_2B_4)^{k-4}$ & $B_1B_3(B_2B_3B_1B_4)^{k-4}$ & $B_2B_3$\\
-		& \vdots\\
-		& $(B_2B_4B_1B_3)^{2}$ & $B_2B_4(B_1B_4B_2B_3)^{2}$ & $B_1B_4(B_1B_3B_2B_4)^{1}$ & $B_1B_3(B_2B_3B_1B_4)^{1}$ & $B_2B_3$\\
-		& $B_2B_4B_1B_4$
+
+	%\scriptsize
+	\begin{tabular}{llll}
+		& $k$ odd &  & $k$ even\\
+		$w=$\hspace{1cm} & $(2413)^{k-1}241$ & \hspace{1cm} &  $(2413)^{k-1}241$\\
+		     & $(4231)^{k-1}4$   & &  $(4231)^{k-1}4$  \\
+		     & $(1324)^{k-2}132$ & &  $(1324)^{k-2}132$\\
+		     & $(3142)^{k-2}3$   & &  $(3142)^{k-2}3$ \vspace{5pt}\\
+
+		     & $(2413)^{k-3}241$ & &  $(2413)^{k-3}241$\\
+		     & $(4231)^{k-3}4$   & &  $(4231)^{k-3}4$  \\
+		     & $(1324)^{k-4}132$ & &  $(1324)^{k-4}132$\\
+		     & $(3142)^{k-4}3$   & &  $(3142)^{k-4}3$\\
+			 & \vdots			 & &  \vdots\\
+			 & $(2413)^{2} 241$	 & &  $(2413)^{1} 241$\\
+			 & $(4231)^2 4$		 & &  $(4231)^1 4$\\
+			 & $(1324)^1 132$	 & &  $(1324)^0 132$\\
+			 & $(3142)^1 3$		 & &  $(3142)^0 3$\\
+			 & $(2413)^0 241$	 & & \\
+			 & $(4231)^0 4$  	 & 
 	\end{tabular}
@@
 \end{center}
-if $k$ is odd, and
+The transcript above is written in rows which correspond to beads in the conformation stabilized along the same row on the grid.
+To simplify the argument we will use \textit{row} both for the transcript above and for the conformation it stabilizes in.
+In line with this, row $\ell\in \{1,\dots, 2k\}$ is as follows:
 \begin{center}
-	\scriptsize
-	\begin{tabular}{llllll}
-		$p=$ & $(B_2B_4B_1B_3)^{k-1}$ & $B_2B_4(B_1B_4B_2B_3)^{k-1}$ & $B_1B_4(B_1B_3B_2B_4)^{k-2}$ & $B_1B_3(B_2B_3B_1B_4)^{k-2}$ & $B_2B_3$\\
-		& $(B_2B_4B_1B_3)^{k-3}$ & $B_2B_4(B_1B_4B_2B_3)^{k-3}$ & $B_1B_4(B_1B_3B_2B_4)^{k-4}$ & $B_1B_3(B_2B_3B_1B_4)^{k-4}$ & $B_2B_3$\\
-		& \vdots\\
-		& $(B_2B_4B_1B_3)^{2}$ & $B_2B_4(B_1B_4B_2B_3)^{2}$ & $B_1B_4$\\
-		& $B_1B_3B_2B_3$
+	\begin{tabular}{llll}
+							& row $\ell$ & 			& $\ell\mod 4$ \\
+			& $(2413)^{k-\lfloor (\ell+1)/2\rfloor}241$ & \hspace{1cm} &  $\ell\equiv 1\mod 4$\\
+							& $(4231)^{k-\lfloor (\ell+1)/2\rfloor}4$   & &  $\ell\equiv 2 \mod 4$ \\
+							& $(1324)^{k-\lfloor (\ell+1)/2\rfloor}132$ & &  $\ell\equiv 3 \mod 4$\\
+							& $(3142)^{k-\lfloor (\ell+1)/2\rfloor}3$   & &  $\ell\equiv 4 \mod 4$ 
 	\end{tabular}
-
 \end{center}
-if $k$ is even. The length of the transcript is $4k^2$. One row of the formula above corresponds to four rows of the conformation (except for the last rows).
+so $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$.
+Row $1$ is of length $4k-1$ and row $\ell+1$ is two beads shorter than row $\ell$, so the length of the whole transcript is $|w|=4k^2=\frac{(4k+1-1)^2}{4}=\frac{(|\sigma|-1)^2}{4}$.
+As an example, see Fig.~\ref{CI:big}, where $k=5$, so the length of the seed is $4k+1=21$ and the transcript is $4k^2 = 100$ beads long.
 
@@
 Bonds: dashed red lines.
-Beads: '$B_0$' black, '$B_1$' red, '$B_2$' red with black contour, '$B_3$' green, '$B_4$' green with black contour.}
+Beads: '$0$' black, '$1$' red, '$2$' red with black contour, '$3$' green, '$4$' green with black contour.}
 	\label{CI:big}
@@
 
-The first bead of the transcript is type $B_2$ and it has to be fixed next to $(4k,0)$.
-The second bead is type $B_4$, which cannot form a bond with anything in the conformation so far.
-The only possibility of forming a bond is if $B_2$ is placed at $(4k,1)$ and it bonds with the $B_2$ at $(4k-1,0)$.
-The next bead to be fixed is $B_4$, and since it cannot form a bond, the conformation with the highest number of bonds is when the next bead, $B_1$ is at $(4k-2,1)$, which fixes the previous bead, $B_4$ at $(4k-1,1)$.
+Stabilizing the first bead of row $j$ goes as follows (see Fig.~\ref{CI:turn}):
+%\begin{itemize}
+%	\item $\bf j\equiv 1\mod 4$: the first two beads are $24$, and the preceding bead is stabilized at $(4k-\frac{j-1}{2}, j-1)$.
+The $2$ can only bind to the $2$ which occurred two beads before at $(4k-\frac{j+1}{2}, j-1)$, and $4$ cannot bind anywhere, so the $2$ is stabilized at $(4k-\frac{j-1}{2},j)$.
+%\end{itemize}
+
+\begin{center}
+	\begin{tabular}{|c|c|c|c|c|@{}m{0pt}@{}}
+		%\renewcommand{\arraystretch}{2}
+	$j\mod 4$					& first bead 	& predecessor at		& first bead binds to		& first stabilizes at\\
+						\hline
+	$\equiv 1$	& 2		& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$& $\mathrm{ }$\newline $\mathrm{ }$\\
+	\hline
+	$\equiv 2$	& 4				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$\\
+	\hline
+	$\equiv 3$	& 1				& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
+	\hline
+	$\equiv 4$	& 3				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
+	\hline		
+	\end{tabular}
+\end{center}
+
+%The first bead of the transcript is type $2$ and it has to be fixed next to $(4k,0)$.
+The second bead is type $4$, which cannot form a bond with anything in the conformation so far.
+The only possibility of forming a bond is if the $2$-bead is placed at $(4k,1)$ and it bonds with the $2$-bead of the seed at $(4k-1,0)$.
+The next to be stabilized is a $4$-bead, and since it cannot form any bond, the conformation with the highest number of bonds is when the one after, a $1$-bead, is at $(4k-2,1)$ bonding with $(4k-3,0)$, which stabilizes the preceding $4$-bead at $(4k-1,1)$ (see Fig.~\ref{CI:1-4}, (a)-(b)).
 
@@
 
-Let the last bead fixed be the $i$th one.
-If it is $B_1$ or $B_2$ at some position $(4k+1-i,1)$, then the next two are $B_3B_2$ or $B_4B1$, respectively.
-The first beads in both cases cannot bind anywhere, whereas the second ones can bind with identical beads at $(4k+1-(i+3),0)$, fixing bead $i+1$ at $(4k+1-(i+1),1)$.
-If bead $i$ was $B_3$ or $B_4$ at position $(4k+1-i,1)$ then the next two are $B_2B_4$ or $B_1B_3$,respectively.
-The first bead of those sequences can bind only to its identical counterpart at $(4k+1-(i+2),0)$, whereas the second cannot bind anywhere, fixing bead $i+1$ at $(4k+1-(i+1))$.
-The above hold as long as there is a bead already at $(4k+1-(i+3),0)$ or at $(4k+1-(i+3),0)$, respectively, so for all $i\in \{1,\dots, 4k-2\}$.
+As for the other beads, in rows $j\equiv 1,3\mod 4$, beads of type $1$ and $3$ bind to a bead in row $j-1$.
+In rows $j\equiv 2,4\mod 4$ beads of type $2$ and $4$ can bind to a bead in row $j-1$.
+This is true for row $1$, because beads of type $1$ and $3$ from row $1$ can only bind to every second bead of the seed, whereas beads of type $2$ and $4$ from row $1$ cannot bind to anything (Fig.~\ref{CI:1-4}, (c)).
+Once this dynamic holds for a row, it holds inductively for the next, as a bead that binds to another loses its only free hand at arity $1$.
 
-According to the above, bead $4k-1$ was fixed at $(4k+1-(4k-1),1)=(2,1)$.
-The next bead, $4k$ is of the same type as bead $4k-2$, so they can form a bond, and this is the only bond that can be formed by any conformation of beads $4k$ and $4k+1$ (see Fig.~\ref{CI:turn}).
-A similar situation occurs when trying to fix bead $8k-2$: it can only bond to bead $8k-4$, so it will turn the path around.
+Within one row of the transcript, no bead can bind to a preceding bead, because if there is a previous bead of the same type in that row, it is stabilized at a distance of four and the system has delay $2$.
+
+By the arguments above, the beads in row $i$ of the transcript are stabilized along row $i$ on the grid, forming the pyramid-like conformation from Fig.~\ref{CI:big}.
+
 \begin{figure}
@@
 
-%Accordingly, it is Fig.~\ref{fig:firstout} when a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$.
+Accordingly, it is Fig.~\ref{fig:firstout} when a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$.
 
-%\begin{figure}
-%  \begin{center}
-%    \begin{tikzpicture}
-%      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-%      \fill (2.0, 0.0) node [right] {$n$};
-%      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-%      \fill (2.0, 0.866) node [right] {$n+1$};
-%      \begin{scope}[shift=(0 : 0.0)]
-%        \draw (-0.1,-0.1) -- (0.1,0.1);
-%        \draw (0.1,-0.1) -- (-0.1,0.1);
-%        \draw (0 : 0.0) -- (60 : 1.0);
-%      \end{scope}
-%      \begin{scope}[shift=(60 : 1.0)]
-%        \draw (-0.1,-0.1) -- (0.1,0.1);
-%        \draw (0.1,-0.1) -- (-0.1,0.1);
-%      \end{scope}
-%      \begin{scope}[shift=(0 : 1.0)]
-%        \draw (-0.1,-0.1) -- (0.1,0.1);
-%        \draw (0.1,-0.1) -- (-0.1,0.1);
-%        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-%      \end{scope}
-%    \end{tikzpicture}
-%    \caption{}
-%    \label{fig:firstout}
-%  \end{center}
-%\end{figure}
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
+      \fill (2.0, 0.0) node [right] {$n$};
+      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
+      \fill (2.0, 0.866) node [right] {$n+1$};
+      \begin{scope}[shift=(0 : 0.0)]
+        \draw (-0.1,-0.1) -- (0.1,0.1);
+        \draw (0.1,-0.1) -- (-0.1,0.1);
+        \draw (0 : 0.0) -- (60 : 1.0);
+      \end{scope}
+      \begin{scope}[shift=(60 : 1.0)]
+        \draw (-0.1,-0.1) -- (0.1,0.1);
+        \draw (0.1,-0.1) -- (-0.1,0.1);
+      \end{scope}
+      \begin{scope}[shift=(0 : 1.0)]
+        \draw (-0.1,-0.1) -- (0.1,0.1);
+        \draw (0.1,-0.1) -- (-0.1,0.1);
+        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
+      \end{scope}
+    \end{tikzpicture}
+    \caption{}
+    \label{fig:firstout}
+  \end{center}
+\end{figure}
 

### 2018-12-02 tt_intro.tex
Binding capability
The definition of bc was not correct so that I fixed it.

@@
 
+\begin{comment}
 \begin{figure}
@@
 \end{figure}
+\end{comment}
 
@@
 At delay 1, a bead cannot collaborate with its successors in order to stabilize itself. 
-In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts). 
+In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts), as observed in \cite{DHOPRSST2018}. 
 One is to be bound and the other is through a 1-in-1-out structure called the tunnel section. 
@@
 A \textit{tunnel section} consists of four beads that occupy four neighbors of one free point. 
-The behavior of a deterministic oritatami system at delay 1 can be described by a sequence of $S$ of $b$ (bound), $t_s$ (straight tunnel section), $t_o$ (obtuse-turn tunnel section), and $t_a$ (acute-turn tunnel section); priority is given to tunnel, that is, $S[i]$ is $t_s$ (resp.~$t_o$, $t_a$) if the $i$-th bead of the system is stabilized not only by being bonded but also through a straight (resp.
+In order for an oritatam system to stabilize the bead $w[i]$ at the central point $p$ of a tunnel section, its predecessor $w[i-1]$ must be put at one of the two free neighbors of $p$. 
+Thus, at the stabilization of $w[i]$, only one neighbor of $p$ is left free so that the successor $w[i+1]$ is to be stabilized there, even without being bound. 
+In this case, the point where $w[i-1]$ is stabilized is considered to be an \textit{entrance of the tunnel} and the point where $w[i+1]$ is stabilized is considered as an \textit{exit of the tunnel}.
+
+The behavior of an oritatami system at delay 1 can be described by a sequence of $S$ of $b$ (bound), $t_s$ (straight tunnel section), $t_o$ (obtuse-turn tunnel section), and $t_a$ (acute-turn tunnel section); priority is given to tunnel, that is, $S[i]$ is $t_s$ (resp.~$t_o$, $t_a$) if the $i$-th bead of the system is stabilized not only by being bonded but also through a straight (resp.
 obtuse-turn, acute-turn) tunnel section.
@@
 
-Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
+%Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
 We call such a point $p$ the $inside\ of\ a\ tunnel$ and points $p^\prime$ the $entrance\ of\ a\ tunnel$ except when $p^\prime$ is inside of a tunnel.
@@
 
-We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. 
+%We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. 
+We say that a neighbor of a point $p$ is reachable from a conformation $C$ if there exists an elongation of $C$ in which a bead occupies the neighbor and it binds with a bead at $p$. 
 Taking this reachability into account, we define the \textit{binding capability} of a conformation as the number of free bonds of its beads available geometrically for elongations of $C$.
@@
 
-\begin{definition}[binding capability]
-Let $C = (P,w,H)$ be a conformation.
-Let $B_k$ be $H \cap \{ (i,j) \mid \mbox{$i=k$ or $j=k$} \}$. Moreover, let $R_k$ be a set of neighbors of the point $P[k]$ that are free and reachable from $C$.
- The binding capability of $C$, denoted by $\#bc(C)$, is defined by $\sum^{|w|}_{k=1} \min \{ |B_k|, |R_k|  \}$.
+\begin{definition}[Binding Capability]
+Let $\alpha$ be an arity and $C = (P,w,H)$ be a conformation of arity at most $\alpha$.
+Let $H_k = H \cap \{ (i,j) \mid \mbox{$i=k$ or $j=k$} \}$. 
+Moreover, let $R_k$ be a set of neighbors of the point $P[k]$ that are free and reachable from $C$.
+The binding capability of $C$ at arity $\alpha$, denoted by $\#bc_\alpha(C)$, is defined by $\sum^{|w|}_{k=1} \min \{\alpha-|H_k|, |R_k|\}$.
+Whenever the arity is clear from context, we omit the subscript $\alpha$. 
 \end{definition}

### 2018-12-03 paper.tex
Rewrote the Chichen Itza part
The previous version was hard to follow, because one got lost in the details. I think now it is much more readable and looks more organized.

The only modification to the main file, paper.tex are some package declarations.
Forgot to uncomment the includes I commented before for faster compilation
Binding capability
The definition of bc was not correct so that I fixed it.
Lenght of conformation defined
As stated in the title.

@@
 \usepackage{calc}
+\usepackage{array}
 
@@
 \usetikzlibrary{automata}
+
+\usepackage{comment}
 
@@
 \node at (1, 2) {$O(n^2)$};
-\node at (1, 1) {$O(n)$ \cite{DemaineDNA24}};
+\node at (1, 1) {$9n$ \cite{DHOPRSST2018}};
 
@@
 We designate one point in $V$ as the origin $O$ of $\mathbb{T}$. 
-For a point $p \in V$, let $N_p^d$ denote the set of points which lie in the regular hexagon of radius $d$ centered at the point $p$. 
+For a point $p \in V$, let $\hexagon_p^d$ denote the set of points which lie in the regular hexagon of radius $d$ centered at the point $p$. 
+Note that $\hexagon_p^d$ consists of $3d(d+1)+1$ points. 
 A directed path $P = p_1 p_2 \cdots p_n$ in $\mathbb{T}$ is a sequence of \textit{pairwise-distinct} points $p_1, p_2, \ldots, p_n \in V$ such that $\{p_i, p_{i+1}\} \in E$ for all $1 \le i < n$. 
@@
 The condition $i+2 \le j$ represents the topological restriction that two consecutive beads along the path cannot be bound. 
+The \textit{length} of $C$ is defined to be the length of its transcript $w$ (that is, equal to the length of the path $P$). 
 A \textit{rule set} $R \subseteq \Sigma \times \Sigma$ is a symmetric relation over $\Sigma$, that is, for all bead types $a, b \in \Sigma$, $(a, b) \in R$ implies $(b, a) \in R$. 
@@
 
-In the second half of this paper, we consider the unary oritatami system. 
+In this paper, we considerably focus on the unary oritatami system. 
 An oritatami system is \textit{unary} if its bead type set $\Sigma$ is of size 1. 
@@
 \bibliographystyle{splncs03}
-\bibliography{tamc2019.bib}
+\bibliography{tamc2019}
 

### 2018-12-03 tt_theorem.tex
before lunch 12/3

@@
 \begin{theorem}[Tunnel Troll Theorem]
-Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. 
-At arity $\alpha \geq 3$, if $S[k] = t$ and $S[k+1] \neq \blacksquare$, then $\#bc(C_{k-1}) > \#bc(C_k)$.
-On the other hand, at arity $\alpha = 2$, if there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
+Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. The following statements hold.
+\begin{enumerate}
+\item At arity $\alpha \geq 3$, if $S[k] = t$ (i.e. the tunnel that stabilizes $w[k]$ is not singular) and $S[k+1] \neq \blacksquare$, then $\#bc(C_{k-1}) > \#bc(C_k)$.
+\item At arity $\alpha = 2$, if there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
+\end{enumerate}
 \end{theorem}

### 2018-12-03 tt_theorem.tex
12/3 16pm

@@
 
-\subsubsection{Case of $S[h-1..h+1] = tbt$}
+\subsubsection{Case of $S[h-1..h+1] = tbt_a$}
 Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
 
-\begin{itemize}
-\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
+%\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
   In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$.
@@
 
-\item{Right of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
   These cases are divided on number of capabilities that $w[h-1]$ consumes.
@@
   \end{itemize}
-\end{itemize}
+
 \begin{figure}
@@
 \subsection{On structures provided by a unary and $\delta = 1$ oritatami system}
+
+\begin{figure}[tb]
+ \centering
+    \begin{tikzpicture}
+	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (0:1) {$n_0$};
+
+	\foreach \theta in {0,60,-60,120,-120}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+ 	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[below] at (-120:1) {$n_4$};
+    \end{tikzpicture}
+    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
+    \label{TTT_a4_lemma_fig}
+\end{figure}
+
+\begin{lemma}
+\label{TTT_a4_2b_lemma}
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$.
+When a bead is stabilized by bond, it forms at least two bonds.
+\end{lemma}
+
+\begin{proof}%[proof of lemma]
+Suppose $w[i]$ were stabilized by only one bond.
+See Fig.~\ref{TTT_a4_lemma_fig}.
+If $n_3$ is free, $w[i-2]$ still has some bonds because of arity $\alpha = 4$.
+Thus, $n_4$ must be occupied; otherwise, $w[i]$ would be stabilized nondeterministically at $n_3$ and $n_4$.
+Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$.
+$n_1$ has some hands because $n_3$ is free.
+Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands.
+It contradict assumption.
+\end{proof}
+
+\begin{theorem}[$\delta = 1, \alpha = 4$]
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite conformation of length is $3n^2  + 3n + 1$.
+\end{theorem}
+
+\begin{proof}
+According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds.
+Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized.
+See Fig.\ref{TTT_a4_first}.
+any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$.
+At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind.
+In this case, a point which is able to put a bead is only $n_2$.
+Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$.
+Hence oritatami system can yield only a finite structure whose size is $O(n^2)$ in $\delta =1, \alpha = 4$.
+%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
+\end{proof}
+
+\begin{figure}
+ \centering
+    \begin{tikzpicture}
+	\fill[shift=(-120:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0), blue] (0,0) circle [radius=0.05];
+
+      \draw[dashed] (180:2) -- (0:2);
+      \draw[dashed, shift=(-60:1)] (180:2.5) -- (0:1.5);
+      \draw[->, blue] (-120:0.9) -- (-120:0.1);
+
+	\node[below] at (-120:1) {$w_{[i-1]}$};
+	\node[above] at (180:0) {$w_{[i]}$};
+	\node[above] at (0:1) {$n_0$};
+
+	\foreach \theta in {0,60,-60,120,180}{
+   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+  	}
+
+ 	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[above] at (180:1) {$n_5$};
+
+	\node at (0:2.5) {$n+1$};
+	\node[shift=(-60:1)] at (0:2) {$n$};
+    \end{tikzpicture}
+    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
+    \label{TTT_a4_first}
+\end{figure}
+
 \begin{theorem}[$\delta= 1, \alpha=2$]
@@
 \begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite structures whose size is $O(n)$.
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $O(n)$.
 \end{theorem}
@@
 \end{figure}
-
-\begin{theorem}[$\delta = 1, \alpha = 4$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite structures whose size is $O(n^2)$.
-\end{theorem}
-
-\begin{lemma}
-\label{TTT_a4_2b_lemma}
-Any beads which are already stabilized by some bonds use at least two bonds.
-\end{lemma}
-
-\begin{proof}[proof of lemma]
-Let us consider when $w[i]$ is stabilized by only one bond.
-See Fig.\ref{TTT_a4_lemma_fig}.
-According to lemma\ref{TTT_neighbor_lemma}, if $n_3$ is free, $w[i-2]$ has some hands.
-Thus, $n_4$ has to be occupied in order to stabilize deterministically.
-Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$.
-$n_1$ has some hands because $n_3$ is free.
-Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands.
-It contradict assumption.
-\end{proof}
-
-\begin{proof}
-According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds.
-Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized.
-See Fig.\ref{TTT_a4_first}.
-any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$.
-At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind.
-In this case, a point which is able to put a bead is only $n_2$.
-Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$.
-Hence oritatami system can yield only a finite structure whose size is $O(n^2)$ in $\delta =1, \alpha = 4$.
-%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
-\end{proof}
-
-\begin{figure}
- \centering
-    \begin{tikzpicture}
-	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (0:1) {$n_0$};
-
-	\foreach \theta in {0,60,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-    \end{tikzpicture}
-    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
-    \label{TTT_a4_lemma_fig}
-\end{figure}
-
-\begin{figure}
- \centering
-    \begin{tikzpicture}
-	\fill[shift=(-120:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0), blue] (0,0) circle [radius=0.05];
-
-      \draw[dashed] (180:2) -- (0:2);
-      \draw[dashed, shift=(-60:1)] (180:2.5) -- (0:1.5);
-      \draw[->, blue] (-120:0.9) -- (-120:0.1);
-
-	\node[below] at (-120:1) {$w_{[i-1]}$};
-	\node[above] at (180:0) {$w_{[i]}$};
-	\node[above] at (0:1) {$n_0$};
-
-	\foreach \theta in {0,60,-60,120,180}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[above] at (180:1) {$n_5$};
-
-	\node at (0:2.5) {$n+1$};
-	\node[shift=(-60:1)] at (0:2) {$n$};
-    \end{tikzpicture}
-    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
-    \label{TTT_a4_first}
-\end{figure}

### 2018-12-03 tt_theorem.tex
12/3 d=3 cont.

@@
 
-\begin{lemma}
-\label{TTT_a4_2b_lemma}
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$.
-When a bead is stabilized by bond, it forms at least two bonds.
-\end{lemma}
-
-\begin{proof}%[proof of lemma]
-Suppose $w[i]$ were stabilized by only one bond.
+%\begin{lemma}
+%\label{TTT_a4_2b_lemma}
+%Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$.
+%When a bead is stabilized by bond, it forms at least two bonds.
+%\end{lemma}
+%
+%\begin{proof}%[proof of lemma]
+%Suppose $w[i]$ were stabilized by only one bond.
 See Fig.~\ref{TTT_a4_lemma_fig}.
@@
 It contradict assumption.
-\end{proof}
+%\end{proof}
 
@@
 \begin{proof}
-According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds.
+%According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds.
 Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized.
@@
 Hence oritatami system can yield only a finite structure whose size is $O(n^2)$ in $\delta =1, \alpha = 4$.
-%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
+%%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
+seki sensei.
 \end{proof}
@@
 
-\begin{theorem}[$\delta= 1, \alpha=2$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation.
-\end{theorem}
-
-\begin{proof}
-By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
-If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$.
-Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities.
-Therefore formula \ref{TTT_only_bond} hold.
-
-\begin{eqnarray}
-  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
-  \label{TTT_only_bond}
-\end{eqnarray}
-
-Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
-
-Let us consider the case of $v_k$ is $o$.
-See Fig.\ref{TTT_case_of_o}.
-$w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$.
-If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding.
-If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive, that is, $w[i-1]$ consumes two binding capabilities.
-Therefore, this case consumes binding capabilities.
-If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings.
-In addition, $w[i]$ and $w[i+1]$ consume at least one binding.
-Therefore this case consumes binding capabilities.
-Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.
-Thus, in this case, oritatami system can yield infinite structures but they are only zig-zag conformation.
-
-\end{proof}
-
-\begin{eqnarray}
-  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
-  \label{TTT_only_a}
-\end{eqnarray}
-
-\begin{eqnarray}
-  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
-  \label{TTT_structure}
-\end{eqnarray}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-
-      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
-
-      \fill[blue](0:0) circle [radius=0.05];
-      \fill[blue](0:1) circle [radius=0.05];
-      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
-
-      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
-      \draw[->, blue] (0:0.1) -- (0:0.9);
-      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
-
-      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-
-      \node[below] at (-120:1) {$w[i-2]$};
-      \node[above] at (0:0) {$w[i-1]$};
-      \node[below] at (0:1) {$w[i]$};
-      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
-
-      \node[above] at (60:1) {$n_1$};
-      \node[below] at (-60:1) {$n_2$};
-
-    \end{tikzpicture}
-    \caption{Case of $S[i]$}
-    \label{TTT_case_of_o}
-  \end{center}
-\end{figure}
-
-\begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $O(n)$.
-\end{theorem}
-
 \begin{lemma}
 \label{TTT_a3_2b_lemma}
- Let $p$ be a point whose neighbors is occupied at least two point.
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. 
+If $S[i] = t$ or $t^\times$ and $S[i+1] \neq \blacksquare$, then the bead $w[i]$ consumes also at least one bond. 
+% Let $p$ be a point whose neighbors is occupied at least two point.
 If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
@@
 
-\begin{proof}[proof of lemma]
-Assume the transcript is stabilized until $w[i-1]$.
-One of neighbors of $p$ is not $w[i-1]$ where this bead regards $n_1$.
+\begin{proof}%[proof of lemma]
+Both $n_3$ and $n_4$ are occupied because $S[i] = t$ or $t^\times$.
+Suppose $w[i]$ were stabilized without any bond.
+Then, all neighbors of $n_3$ must be occupied as long as the bead at $n_3$ is not singular; otherwise, a bead at $n_3$ would be capable of forming a bond with $w[i]$.
+That is, $n_1$ is occupied.
+We can continue this argument in clockwise manner to fill the neighbors of $w[i]$ until a singular bead is encountered, if any.
+If needed, the same argument is applied starting from $n_4$ in counter-clockwise manner.
+Thus, all neighbors of $w[i]$ must be occupied but then $S[i+1] = \blacksquare$, contradiction. \qed
+
+%One of neighbors of $p$ is not $w[i-1]$ where this bead regards $n_1$.
 If $w[i-1]$ include neighbors of $p$ and $w[i]$ is stabilized at another point of $p$ with one bond.
@@
 \end{proof}
+
+\begin{theorem}[$\delta = 1, \alpha = 3$]
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $O(n)$.
+\end{theorem}
 
@@
 \end{figure}
+
+\begin{theorem}[$\delta= 1, \alpha=2$]
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation.
+\end{theorem}
+
+\begin{proof}
+By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
+If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$.
+Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities.
+Therefore formula \ref{TTT_only_bond} hold.
+
+\begin{eqnarray}
+  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
+  \label{TTT_only_bond}
+\end{eqnarray}
+
+Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
+
+Let us consider the case of $v_k$ is $o$.
+See Fig.\ref{TTT_case_of_o}.
+$w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$.
+If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding.
+If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive, that is, $w[i-1]$ consumes two binding capabilities.
+Therefore, this case consumes binding capabilities.
+If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings.
+In addition, $w[i]$ and $w[i+1]$ consume at least one binding.
+Therefore this case consumes binding capabilities.
+Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.
+Thus, in this case, oritatami system can yield infinite structures but they are only zig-zag conformation.
+
+\end{proof}
+
+\begin{eqnarray}
+  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
+  \label{TTT_only_a}
+\end{eqnarray}
+
+\begin{eqnarray}
+  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
+  \label{TTT_structure}
+\end{eqnarray}
+
+\begin{figure}
+  \begin{center}
+    \begin{tikzpicture}
+
+      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
+
+      \fill[blue](0:0) circle [radius=0.05];
+      \fill[blue](0:1) circle [radius=0.05];
+      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
+
+      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
+      \draw[->, blue] (0:0.1) -- (0:0.9);
+      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
+
+      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
+      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
+
+      \node[below] at (-120:1) {$w[i-2]$};
+      \node[above] at (0:0) {$w[i-1]$};
+      \node[below] at (0:1) {$w[i]$};
+      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
+
+      \node[above] at (60:1) {$n_1$};
+      \node[below] at (-60:1) {$n_2$};
+
+    \end{tikzpicture}
+    \caption{Case of $S[i]$}
+    \label{TTT_case_of_o}
+  \end{center}
+\end{figure}

### 2018-12-03 paper.tex
Commit before going home
We have been working on the finiteness of \delta=1, arity being at least
3.

@@
 }
+\titlerunning{Power of unary oritatami cotranscriptional folding}
 \author{
 Szil\'{a}rd Zsolt Fazekas\inst{1} \and 
+Kohei Maruyama \and
+Reoto Morita \and \\
 Shinnosuke Seki\inst{2}\thanks{Corresponding author (\email{s.seki@uec.ac.jp})}}
@@
 
-Transcription is the first essential step of gene expression, when a DNA template sequence is copied into a complementary single stranded RNA sequence by a `copy machine' called RNA polymerase. 
+Transcription is the first essential step of gene expression, in which a DNA template sequence is copied into a complementary single stranded RNA sequence by a `copy machine' called RNA polymerase. 
 The RNA strand is synthesized letter by letter according to the complimentarity relation ${\tt A} \rightarrow {\tt U}$, ${\tt G} \rightarrow {\tt C}$, ${\tt C} \rightarrow {\tt G}$, and ${\tt T} \rightarrow {\tt A}$ and folds up during a process called co-transcriptional folding.
@@
 
-\draw[-latex] (origin) -- ++(0:3) node[below] {$\delta$}; 
-\node at (1, -0.2) {1};
-\node at (2, -0.2) {2};
+\draw[-latex] (origin) -- ++(0:5) node[below] {$\delta$}; 
+\node at (2, -0.2) {1};
+\node at (4, -0.2) {2 and 3};
 \draw[-latex] (origin) -- ++(90:5) node[left] {$\alpha$}; 
@@
 %Results
-\node at (1, 4) {$O(n^2)$};
-\node at (1, 3) {$O(n)$};
-\node at (1, 2) {$O(n^2)$};
-\node at (1, 1) {$9n$ \cite{DHOPRSST2018}};
+\node at (2, 4) {$3n(n+1)+1$};
+\node at (2, 3) {$O(n)$};
+\node at (2, 2) {$O(n^2)$};
+\node at (2, 1) {$10n$ \cite{DHOPRSST2018}};
 
-\node at (2, 1) {$O(n^2)$};
+\node at (4, 1) {$O(n^2)$};
 
@@
 
-In \cite{DHOPRSST2018}, Demaine et al. proved that at delay 1 and arity 1, an oritatami system can fold upon the seed of size $n$ only the first $9n$ beads of a transcript deterministically. 
+In \cite{DHOPRSST2018}, Demaine et al. proved that at delay 1 and arity 1, upon the seed of length $n$, a deterministic oritatami system cannot fold into any conformation strictly longer than $10n$. 
 We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.

### 2018-12-03 arity1.tex
Changes to pyramid
I am working on the drawing now to change the colors to numbers.

@@
 \subsection{$\alpha = 1$, arbitrary alphabets}
-First we present a lower bound construction for arity $\alpha=1$ systems.
-At $\alpha=1$, allowing delay $\delta=2$ increases the power of OS compared with $\delta=1$, if at least four bead types are allowed.
+First we present a lower bound construction for arity $1$ systems.
+At $\alpha=1$, having delay $\delta=2$ allows the deterministic folding of quadratic length transcripts compared with $\delta=1$, where, as stated before, the maximum length is linear in the length of the seed.
 We demonstrate this with an infinite family of OS, which fold deterministically a transcript of length $\frac{(n-1)^2}{4}$ starting from a given seed of length $n$.
@@
 
-\noindent The transcript is
-\begin{center}
+The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where $\mathrm{row}_\ell$, for $\ell\in \{1,\dots, 2k\}$ is given in the table below.
 
+\begin{figure}
+	\begin{minipage}{.49\textwidth}
+		%\centering
+		\begin{tabular}{l|l}
+			\multicolumn{2}{c}{Transcript $w$}\\
+			\multicolumn{2}{c}{}  \\
+			$k$ odd & \hspace{0.3cm} $k$ even\\\hline
+			& \\
+			$(2413)^{k-1}241$\hspace{0.3cm} & \hspace{0.3cm} $(2413)^{k-1}241$\\
+			$(4231)^{k-1}4$   &  \hspace{0.3cm} $(4231)^{k-1}4$  \\
+			$(1324)^{k-2}132$ &  \hspace{0.3cm} $(1324)^{k-2}132$\\
+			$(3142)^{k-2}3$   &  \hspace{0.3cm} $(3142)^{k-2}3$ \\
+			\vdots			 &  \hspace{0.3cm} \vdots\\
+			$(1324)^1 132$	 &  \hspace{0.3cm} $(2413)^{1} 241$\\
+			$(3142)^1 3$		 & \hspace{0.3cm} $(4231)^1 4$\\
+			$(2413)^0 241$	 &  \hspace{0.3cm} $(1324)^0 132$\\
+			$(4231)^0 4$		 & \hspace{0.3cm} $(3142)^0 3$\\
+		\end{tabular}
+	\end{minipage}
 	%\scriptsize
-	\begin{tabular}{llll}
-		& $k$ odd &  & $k$ even\\
-		$w=$\hspace{1cm} & $(2413)^{k-1}241$ & \hspace{1cm} &  $(2413)^{k-1}241$\\
-		     & $(4231)^{k-1}4$   & &  $(4231)^{k-1}4$  \\
-		     & $(1324)^{k-2}132$ & &  $(1324)^{k-2}132$\\
-		     & $(3142)^{k-2}3$   & &  $(3142)^{k-2}3$ \vspace{5pt}\\
-
-		     & $(2413)^{k-3}241$ & &  $(2413)^{k-3}241$\\
-		     & $(4231)^{k-3}4$   & &  $(4231)^{k-3}4$  \\
-		     & $(1324)^{k-4}132$ & &  $(1324)^{k-4}132$\\
-		     & $(3142)^{k-4}3$   & &  $(3142)^{k-4}3$\\
-			 & \vdots			 & &  \vdots\\
-			 & $(2413)^{2} 241$	 & &  $(2413)^{1} 241$\\
-			 & $(4231)^2 4$		 & &  $(4231)^1 4$\\
-			 & $(1324)^1 132$	 & &  $(1324)^0 132$\\
-			 & $(3142)^1 3$		 & &  $(3142)^0 3$\\
-			 & $(2413)^0 241$	 & & \\
-			 & $(4231)^0 4$  	 & 
+	\begin{minipage}{.49\textwidth}
+		%\centering
+		\begin{tabular}{|l|c|}
+			\hline
+			\hspace{1.2cm}row $\ell$ & $\ell\mod 4$ \\\hline
+			 & \\
+			\hspace{0.1cm}$(2413)^{k-\lfloor (\ell+1)/2\rfloor}241$ \hspace{0.1cm} &  $\textrm{ }\ell\equiv 1\mod 4\textrm{ }$\\
+			\hspace{0.1cm}$(4231)^{k-\lfloor (\ell+1)/2\rfloor}4$   &  $\textrm{ }\ell\equiv 2 \mod 4\textrm{ }$ \\
+			\hspace{0.1cm}$(1324)^{k-\lfloor (\ell+1)/2\rfloor}132$ &  $\textrm{ }\ell\equiv 3 \mod 4\textrm{ }$ \\
+			\hspace{0.1cm}$(3142)^{k-\lfloor (\ell+1)/2\rfloor}3$   &  $\textrm{ }\ell\equiv 4 \mod 4\textrm{ }$ \\\hline
 		\end{tabular}
 
-\end{center}
+	\end{minipage}
+
+\end{figure}
+
+%\begin{center}
+%	
+%	%\scriptsize
+%	\begin{tabular}{llll}
+%		& $k$ odd &  & $k$ even\\
+%		$w=$\hspace{1cm} & $(2413)^{k-1}241$ & \hspace{1cm} &  $(2413)^{k-1}241$\\
+%		     & $(4231)^{k-1}4$   & &  $(4231)^{k-1}4$  \\
+%		     & $(1324)^{k-2}132$ & &  $(1324)^{k-2}132$\\
+%		     & $(3142)^{k-2}3$   & &  $(3142)^{k-2}3$ \vspace{5pt}\\
+%		     
+%		     & $(2413)^{k-3}241$ & &  $(2413)^{k-3}241$\\
+%		     & $(4231)^{k-3}4$   & &  $(4231)^{k-3}4$  \\
+%		     & $(1324)^{k-4}132$ & &  $(1324)^{k-4}132$\\
+%		     & $(3142)^{k-4}3$   & &  $(3142)^{k-4}3$\\
+%			 & \vdots			 & &  \vdots\\
+%			 & $(2413)^{2} 241$	 & &  $(2413)^{1} 241$\\
+%			 & $(4231)^2 4$		 & &  $(4231)^1 4$\\
+%			 & $(1324)^1 132$	 & &  $(1324)^0 132$\\
+%			 & $(3142)^1 3$		 & &  $(3142)^0 3$\\
+%			 & $(2413)^0 241$	 & & \\
+%			 & $(4231)^0 4$  	 & 
+%	\end{tabular}
+%	
+%\end{center}
+
 The transcript above is written in rows which correspond to beads in the conformation stabilized along the same row on the grid.
-To simplify the argument we will use \textit{row} both for the transcript above and for the conformation it stabilizes in.
-In line with this, row $\ell\in \{1,\dots, 2k\}$ is as follows:
-\begin{center}
-	\begin{tabular}{llll}
-							& row $\ell$ & 			& $\ell\mod 4$ \\
-			& $(2413)^{k-\lfloor (\ell+1)/2\rfloor}241$ & \hspace{1cm} &  $\ell\equiv 1\mod 4$\\
-							& $(4231)^{k-\lfloor (\ell+1)/2\rfloor}4$   & &  $\ell\equiv 2 \mod 4$ \\
-							& $(1324)^{k-\lfloor (\ell+1)/2\rfloor}132$ & &  $\ell\equiv 3 \mod 4$\\
-							& $(3142)^{k-\lfloor (\ell+1)/2\rfloor}3$   & &  $\ell\equiv 4 \mod 4$ 
-	\end{tabular}
-\end{center}
-so $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$.
+To simplify the argument we will use \textit{row} both for the transcript above and for the conformation it stabilizes in (note that in the figure the row index grows from bottom to top).
+
 Row $1$ is of length $4k-1$ and row $\ell+1$ is two beads shorter than row $\ell$, so the length of the whole transcript is $|w|=4k^2=\frac{(4k+1-1)^2}{4}=\frac{(|\sigma|-1)^2}{4}$.

### 2018-12-03 tt_intro.tex

@@
 
-\begin{figure}
+\begin{figure}[tb]
   \begin{center}
@@
 Thus, at the stabilization of $w[i]$, only one neighbor of $p$ is left free so that the successor $w[i+1]$ is to be stabilized there, even without being bound. 
-In this case, the point where $w[i-1]$ is stabilized is considered to be an \textit{entrance of the tunnel} and the point where $w[i+1]$ is stabilized is considered as an \textit{exit of the tunnel}.
+In this case, the point where $w[i-1]$ is stabilized is considered to be an \textit{entrance of the tunnel section} and the point where $w[i+1]$ is stabilized is considered as its \textit{exit}.
 
@@
 obtuse-turn, acute-turn) tunnel section.
-We let $S$ take the value $\blacksquare$ for halt (due to the lack of free neighbors).
-
-%Assume that four of the six neighbors of a point $p$ are occupied by beads $a_{j_1},a_{j_2},a_{j_3},a_{j_4}$ while the other two are free.
-We call such a point $p$ the $inside\ of\ a\ tunnel$ and points $p^\prime$ the $entrance\ of\ a\ tunnel$ except when $p^\prime$ is inside of a tunnel.
-If the beads $w[i-2]$ and $w[i-1]$ are stabilized respectively at one of the two free neighbors and at $p$ one after another, then the next bead $w[i]$ cannot help but be stabilized at the other free neighbor.
-In this way, $w[i]$ can get stabilized without being bound.
+Let us introduce $t$ as a wildcard for $t_s$, $t_o$, and $t_a$. 
+We also let $S$ take the value $\blacksquare$ for halt (due to the lack of free neighbors). 
+A tunnel is a set of
 
@@
 The binding capability of $C$ at arity $\alpha$, denoted by $\#bc_\alpha(C)$, is defined by $\sum^{|w|}_{k=1} \min \{\alpha-|H_k|, |R_k|\}$.
-Whenever the arity is clear from context, we omit the subscript $\alpha$. 
+The subscript $\alpha$ is omitted whenever it is clear from context. 
 \end{definition}
+
+We now prove that in ``almost all'' tunnels is a troll domiciled and robs the transcript of binding capability (the original story is from \cite{Pratchett1992}). 
+Originally, we tried to find a troll in every tunnel but failed; a troll seems to dislike the very first bead $w[1]$, or its property that only $\alpha$+1 beads around may take all hands of $w[1]$ thanks to the absence of its predecessor; any other bead must be surrounded by at least $\alpha+2$ beads in order to be free from free hand because a bead cannot bind with its predecessor or successor.
+We call the bead $w[1]$ \textit{singular}. 
+A tunnel is \textit{singular} if its entrance or exit is next to $w[1]$. 
+There can be at most 3 tunnels around one bead so that no more than 3 tunnels can be singular. 
+A singular tunnel will be denoted with the superscript $\times$ like $t_s^\times$ or $t^\times$. 
+In contrast, the notation without $\times$ such as $t_s$ and $t$ shall imply their non-singularity.

### 2018-12-03 tt_intro.tex
Def Tunnel
Tunnel is now defined properly.

@@
             \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (0:1) {$p^\prime$};
+            \node[above] at (0,0) {$p_c$};
+            \node[above] at (180:1) {$p_e$};
+            \node[above] at (0:1) {$p_s$};
 
@@
             }
+          \draw[->, blue] (-0.9, 0) -- (-0.1, 0);
+          \draw[->, blue] (0.1, 0) -- (0.9, 0);
           \end{scope}
@@
             \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-60:1) {$p^\prime$};
+            \node[above] at (0,0) {$p_c$};
+            \node[above] at (180:1) {$p_e$};
+            \node[right] at (-60:1) {$p_s$};
 
@@
             }
+          \draw[->, blue] (-0.9, 0) -- (-0.1, 0);
+          \draw[->, blue] (0,0)++(300:0.1) -- (300:0.8);
           \end{scope}
@@
             \draw(0,0) circle [radius=0.05];
-            \node[above] at (180:1) {$p^\prime$};
-            \node[above] at (-120:1) {$p^\prime$};
+            \node[above] at (0,0) {$p_c$};
+            \node[above] at (180:1) {$p_e$};
+            \node[left] at (-120:1) {$p_s$};
 
@@
             }
+          \draw[->, blue] (-0.9, 0) -- (-0.1, 0);
+          \draw[->, blue] (0,0)++(240:0.1) -- (240:0.8);
           \end{scope}
@@
 In fact, there are just two ways for a bead to get stabilized at delay 1 (or the bead has no place to be stabilized around so that the system halts), as observed in \cite{DHOPRSST2018}. 
-One is to be bound and the other is through a 1-in-1-out structure called the tunnel section. 
+One is to be bound to another bead and the other is through a 1-in-1-out structure called the tunnel section. 
 See Fig.~\ref{fig:TTT_tunnel}. 
-A \textit{tunnel section} consists of four beads that occupy four neighbors of one free point. 
-In order for an oritatam system to stabilize the bead $w[i]$ at the central point $p$ of a tunnel section, its predecessor $w[i-1]$ must be put at one of the two free neighbors of $p$. 
+A \textit{tunnel section} consists of one free point $p_c$ and four beads that occupy four neighbors of $p_c$. 
+In order for an oritatami system to stabilize the bead $w[i]$ at the central point $p_c$, its predecessor $w[i-1]$ must be put at one of the two free neighbors of $p$. 
 Thus, at the stabilization of $w[i]$, only one neighbor of $p$ is left free so that the successor $w[i+1]$ is to be stabilized there, even without being bound. 
-In this case, the point where $w[i-1]$ is stabilized is considered to be an \textit{entrance of the tunnel section} and the point where $w[i+1]$ is stabilized is considered as its \textit{exit}.
+In this case, the point $p_e$ where $w[i-1]$ is stabilized is considered to be an \textit{entrance of the tunnel section} and the point $p_s$ where $w[i+1]$ is stabilized is considered as its \textit{exit}.
+A \textit{tunnel} is a maximal set of tunnel sections whose central points form a path.
 
@@
 \end{definition}
+%
+Observe one almost-trivial but important fact that a bead inside a tunnel does not increase the binding capability. 
+This is because for such a bead $w[k]$, $|R_k| = 0$.
 

### 2018-12-04 tt_theorem.tex
12/3

@@
 \begin{enumerate}
-\item At arity $\alpha \geq 3$, if $S[k] = t$ (i.e. the tunnel that stabilizes $w[k]$ is not singular) and $S[k+1] \neq \blacksquare$, then $\#bc(C_{k-1}) > \#bc(C_k)$.
-\item At arity $\alpha = 2$, if there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
+\item At arity $\alpha \geq 3$, if $S[i] = t$ (i.e. the tunnel that stabilizes $w[i]$ is not singular) and $S[i+1] \neq \blacksquare$, then $\#bc(C_{i-1}) > \#bc(C_i)$.
+\item At arity $\alpha = 2$, if $n$ is the number of $bt$ in $S[i..j]$ for some $i,j$ such that $S[i] = b$ and $i < j$, then $\#bc(C_{i-2}) - \#bc(C_{j}) \geq n$.
 \end{enumerate}
@@
 %Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
-If $S[h..i+1] = bt^{(i-h)}b$ for some $h<i-1$, then $\#bc(C_{i-2}) \geq \#bc(C_i)$, and hence, $\#bc(C_{h-1}) \geq \#bc(C_i)$.
+If $S[h..i+1] = bt^{(i-h)}b$ for some $h<i-1$ and $S[i] = t_s$ or $t_o$, then $\#bc(C_{i-2}) \geq \#bc(C_i)$, and hence, $\#bc(C_{h-1}) \geq \#bc(C_i)$.
 If $h < i-1$, then the second inequality is strengthened as $\#bc(C_{h-1}) > \#bc(C_{i})$.
@@
 
-\begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $O(n)$.
-\end{theorem}
-
-\begin{proof}
-Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is, when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
-Let us assume $w[i]$ is able to be stabilized with using one hand. Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$. Then, $w[i]$ can be also stabilized at $n_3$.
-
-\begin{paragraph}{Case of straight}
-\begin{itemize}
-\item[-] Case of $n_3$ is free\\
-According to assumption, $w[i]$ uses only one hand.
-Therefore, any neighbors of $n_3$ are occupied according to the lemma\ref{TTT_a3_2b_lemma}.
-$n_3$ and the point which is stabilized $w[i]$ are free so that $n_1$ has some bond by lemma\ref{TTT_neighbor_lemma}.
-Accordingly, this situation is non-deterministic.
-Thus, $n_3$ and $n_4$ have to be occupied because of symmetry.
-
-\item[-] Otherwise\\
-Because of  $S[i] = b$, at least one of $n_1$ and $n_2$ have to be free.
-Let us regard that $n_1$ is free.
-Neighbors of $n_1$ have to be occupied and at least two neighbors of $n_{-1}$ have to be free for $n_1$ and $w[i]$.
-According to lemma\ref{TTT_neighbor_lemma}, $n_{-1}$ have some hand.
-Therefore $w[i]$ can be also stabilized $n_1$, that is, this situation is non-deterministic.
-Thus, one of $n_3$ and $n_4$ has to be free.
-\end{itemize}
-
-Therefore, this case is false.
-\end{paragraph}
-
-\begin{paragraph}{Case of obtuse}
-\begin{itemize}
-\item[-] Case of $n_3$ is free\\
-Any neighbors of $n_3$ have to be occupied but the point which is stabilized $w[i]$ is free. Thus $n_3$ has to be occupied.
-\item[-] Case of $n_4$ is free\\
-According to lemma\ref{TTT_a3_2b_lemma}, $n_2$ has to be occupied because $n_4$ is free.
-Also $n_0$ has to be occupied from lemma\ref{TTT_neighbor_lemma}.
-Thus, only one of $n_0, n_3$ leave some hands or both of them do not leave any hands because $w[i]$ use only one bond.\\
-If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied.
-Also $n_{-3}$ must not have any hands so that $n_{-2}$ is occupied and also $n_{-1}$ is occupied.
-Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
-If $n_3$ has some hands, then $n_0$ does not have any hands so that $n_{-1}$ is occupied.
-In the same previous way, any $n_{-2}, n_{-3}$ are occupied.
-Therefore any neighbors of $w[i]$ are occupied.\\
-If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied.
-If one of $n_{-1}, n_{-3}$ has some hands, the other does not have any hands so that $n_{-2}$ is occupied.
-If both of $n_{-1}, n_{-3}$ do not have any hands, $n_{-2}$ has to be occupied and $n_{-2}$ has some hands.Therefore any neighbors of $w[i]$ are occupied so that $w[i+1]$ cannot provide.\\
-Thus $n_3$ has to be occupied in order to yield infinite structures.
-\item[-] Case of $n_2$ is free\\
-Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied.
-Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_2$ has to be occupied.
-\item[-] Case of $n_0$ is free\\
-Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied.
-Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_0$ has to be occupied.
-\end{itemize}
-
-Therefore, any situations contradict $S[i] = b$.
-
-\end{paragraph}
-
-\begin{paragraph}{Case of acute}
-\begin{itemize}
-\item[-] Case of $n_4$ is free\\
-$n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some hands according to lemma\ref{TTT_neighbor_lemma}.
-However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
-\item[-] Case of $n_2$ is free\\
-According to lemma\ref{TTT_a3_2b_lemma}, $n_0$ has to be occupied. $n_1$ has to be also occupied because of lemma\ref{TTT_neighbor_lemma}.
-We consider this case just like case of obtuse and that $n_4$ is free.
-Then if $w[i-2]$ binds $w[i]$, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
-If $n_1$ binds $w[i]$, this case is same.
-Also if $n_1$ and $w[i-2]$ do not have any hand, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
-Therefore, $w[i+1]$ cannot be provided.
-\item[-] Case of $n_0$ is free\\
-Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied.
-Any neighbors of $n_{1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_0$ has to be occupied.
-\item[-] Case of $n_1$ is free\\
-Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied.
-Any neighbors of $n_{-1}$ except $n_1$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_1$ has to be occupied.
-\end{itemize}
-
-Therefore, any situations contradict $S[i] = b$.
-\end{paragraph}\\
-
-Hence, assumption that w[i] is able to be stabilized with using one hand is false.
-Therefore, when w[i] is stabilized, w[i] uses at least two hands.
-\end{proof}
-
-\begin{figure}
+\begin{figure} [tb]
   \begin{center}
@@
 	 \draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
+	  \draw [shift=(180:1),shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
  	\node[above] at (60:1) {$n_1$};
@@
 	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
+	\node[above, shift=(180:1)] at (120:1) {$n_5$};
     \end{tikzpicture}
@@
 	\draw [shift=(60:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+	  \draw [shift=(180:1),shift=(-120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
 
@@
 	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
+	\node[above, shift=(60:1)] at (0:1) {$n_{-1}$};
 	\node[above, shift=(60:1)] at (60:1) {$n_{-2}$};
 	\node[above, shift=(60:1)] at (120:1) {$n_{-3}$};
+	\node[below, shift=(180:1)] at (-120:1) {$n_5$};
     \end{tikzpicture}
@@
 \end{figure}
+
+\begin{theorem}[$\delta = 1, \alpha = 3$]
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $O(n)$.
+\end{theorem}
+
+%Both $n_3$ and $n_4$ are occupied because $S[i] = t$ or $t^\times$.
+%Suppose $w[i]$ were stabilized without any bond.
+%Then, all neighbors of $n_3$ must be occupied as long as the bead at $n_3$ is not singular; otherwise, a bead at $n_3$ would be capable of forming a bond with $w[i]$.
+%That is, $n_1$ is occupied.
+%We can continue this argument in clockwise manner to fill the neighbors of $w[i]$ until a singular bead is encountered, if any.
+%If needed, the same argument is applied starting from $n_4$ in counter-clockwise manner.
+%Thus, all neighbors of $w[i]$ must be occupied but then $S[i+1] = \blacksquare$, contradiction. \qed
+
+\begin{proof}
+We consider cases which $w[i-1]$ is two distances away from the singular point.
+Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is, when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
+Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$.
+Suppose $w[i]$ were able to be stabilized with using one hand in each cases.
+
+% Then, $w[i]$ can be also stabilized at $n_3$.
+
+\begin{paragraph}{Case of straight}
+\begin{itemize}
+\item[-] Case of $n_3$ is free\\
+The bead $w[i-2]$ must not have bonds because $w[i]$ is stabilized deterministically so that five neighbors of $w[i-2]$ must be occupied.
+Therefore $n_5$ must be occupied.
+We can continue this argument in clockwise manner to fill the neighbors of $n_3$ until $n_1$.
+However, two neighbors of $n_1$ must be free because they are $n_3$ and the point of $w[i]$, contradict.
+
+\item[-] Otherwise\\
+Both $n_3$ and $n_4$ are occupied.
+One of $n_1$ and $n_2$ must be free because $S[i] = b$.
+We assume $n_1$ is free, then all neighbors of $n_1$ must be occupied because $n_3$ is occupied.
+However, one of neighbors $n_1$ is a point which $w[i]$ is stabilized, contradict.
+\end{itemize}
+
+Therefore, this case contradict assumption.
+\end{paragraph}
+
+\begin{paragraph}{Case of obtuse}
+\begin{itemize}
+\item[-] Case of $n_3$ is free\\
+Any neighbors of $n_3$ have to be occupied but the point which $w[i]$ is stabilized is free. Thus $n_3$ has to be occupied.
+\item[-] Case of $n_4$ is free\\
+The point $n_2$ must be occupied because $n_4$ is free and $n_5$ must be occupied.
+Therefore $n_0$ is occupied.
+The bead $w[i]$ forms just one bond so that one of $n_0, n_3$ leave some hands or both of them do not leave any bonds.\\
+If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied. 
+We can continue this argument in clockwise manner to fill the neighbors of $w[i]$.
+That is, $S[i] = \blacksquare$, contradict.
+
+If $n_3$ has some hands, then $n_0$ does not have any hands so that neighbors of $w[i]$ are occupied. In the same previous way, contradict.\\
+If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied.
+If one of $n_{-1}, n_{-3}$ has some hands, the other does not have any hands so that $n_{-2}$ is occupied.
+If both of $n_{-1}, n_{-3}$ do not have any hands, $n_{-2}$ has to be occupied and $n_{-2}$ has some hands, contradict.
+\item[-] Case of $n_2$ is free\\
+Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied.
+Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_2$ has to be occupied.
+\item[-] Case of $n_0$ is free\\
+Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied.
+Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_0$ has to be occupied.
+\end{itemize}
+\end{paragraph}
+
+\begin{paragraph}{Case of acute}
+\begin{itemize}
+\item[-] Case of $n_4$ is free\\
+The point $n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some bonds.
+However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
+\item[-] Case of $n_2$ is free\\
+The point $n_0$ has to be occupied. The point $n_1$ has to be also occupied because five neighbors of $n_0$ must be occupied.
+We consider this case just like case of obtuse and that $n_4$ is free.
+Then if $w[i-2]$ binds $w[i]$, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
+If $n_1$ binds $w[i]$, this case is same.
+Also if $n_1$ and $w[i-2]$ do not have any hand, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
+Therefore, $w[i+1]$ cannot be provided.
+\item[-] Case of $n_0$ is free\\
+Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied.
+Any neighbors of $n_{1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_0$ has to be occupied.
+\item[-] Case of $n_1$ is free\\
+Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied.
+Any neighbors of $n_{-1}$ except $n_1$ have to be also occupied but the point which is stabilized $w[i]$ is free.
+Thus $n_1$ has to be occupied.
+\end{itemize}
+
+Therefore, any situations contradict $S[i] = b$.
+\end{paragraph}\\
+
+Hence, $w[i]$ uses at least two bonds if $w[i-1]$ is at least two distances away the singular point.
+The size of $ \hexagon^2_0 = 19$ and this number contain the singular point, its successor and its three neighbors which is it binds to.
+Therefore 14 times  $w[i]$ can be stabilized by forming one bond.
+Therefore, a deterministic unary oritatami system at $\delta = 1$ and $\alpha = 3$ can yield only finite conformation of length is $2n + 14$.
+\end{proof}
 

### 2018-12-04 tt_theorem.tex

@@
 
-\begin{lemma}
-\label{TTT_a3_2b_lemma}
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. 
-If $S[i] = t$ or $t^\times$ and $S[i+1] \neq \blacksquare$, then the bead $w[i]$ consumes also at least one bond. 
-% Let $p$ be a point whose neighbors is occupied at least two point.
+%\begin{lemma}
+%\label{TTT_a3_2b_lemma}
+%Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. 
+%If $S[i] = t$ or $t^\times$ and $S[i+1] \neq \blacksquare$, then the bead $w[i]$ consumes also at least one bond. 
+%% Let $p$ be a point whose neighbors is occupied at least two point.
 If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
-\end{lemma}
-
-\begin{proof}%[proof of lemma]
-Both $n_3$ and $n_4$ are occupied because $S[i] = t$ or $t^\times$.
-Suppose $w[i]$ were stabilized without any bond.
-Then, all neighbors of $n_3$ must be occupied as long as the bead at $n_3$ is not singular; otherwise, a bead at $n_3$ would be capable of forming a bond with $w[i]$.
-That is, $n_1$ is occupied.
-We can continue this argument in clockwise manner to fill the neighbors of $w[i]$ until a singular bead is encountered, if any.
-If needed, the same argument is applied starting from $n_4$ in counter-clockwise manner.
-Thus, all neighbors of $w[i]$ must be occupied but then $S[i+1] = \blacksquare$, contradiction. \qed
-
-%One of neighbors of $p$ is not $w[i-1]$ where this bead regards $n_1$.
-If $w[i-1]$ include neighbors of $p$ and $w[i]$ is stabilized at another point of $p$ with one bond.
-Then, any neighbors do not have bond without $w[i-1]$.
-Neighbors of $n_1$ have to be occupied at least five according to lemma \ref{TTT_neighbor_lemma} and two of them include neighbors of $p$ where each of them regards $n_2, n_3$.
-In the same way, five neighbors of $n_2$ and $n_3$ are occupied and each of one of them includes neighbors of $p$ where they regard $n_4, n_5$.
-one of $n_5$'s neighbors includes neighbors of $p$ where it regards $n_6$.
-Then, any neighbors of $p$ are occupied.
-That is, if some neighbors of $p$ are free, then there exists a bead which has bonds in neighbors.
-\end{proof}
+%\end{lemma}
+%
+%\begin{proof}%[proof of lemma]
+%Both $n_3$ and $n_4$ are occupied because $S[i] = t$ or $t^\times$.
+%Suppose $w[i]$ were stabilized without any bond.
+%Then, all neighbors of $n_3$ must be occupied as long as the bead at $n_3$ is not singular; otherwise, a bead at $n_3$ would be capable of forming a bond with $w[i]$.
+%That is, $n_1$ is occupied.
+%We can continue this argument in clockwise manner to fill the neighbors of $w[i]$ until a singular bead is encountered, if any.
+%If needed, the same argument is applied starting from $n_4$ in counter-clockwise manner.
+%Thus, all neighbors of $w[i]$ must be occupied but then $S[i+1] = \blacksquare$, contradiction. \qed
+%\end{proof}
 

### 2018-12-04 tt_theorem.tex
12/4 before lunch

@@
 
-\begin{lemma}
-\label{TTT_entrance_Tab}
-Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$, arity $\alpha =2$. 
-Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $S[i+1] = b$ and $S[i+2] \in \{ t_s, t_o \} $, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
-\end{lemma}
-
-\begin{proof}%[lemma \ref{TTT_entrance_Tab}]
-See Fig.\ref{TTT_tunnel_direction}.
-$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section of type $S$ or $O$.
-Thus,  its predecessor $w[i+1]$ must be inside the tunnel section, that is, $n_1$ and $n_2$ must be occupied.
-Free bonds of $w[i]$, if any, cannot be used in future by another bead $w[j]$ because otherwise the part of transcript $w[i..j]$ and the bond between $w[i]$ and $w[j]$ would form a closed curve and the curve would cross the path of $C_{i-1}$ between $n_1$ and $n_2$, contradiction.
-%Binding capabilities that $w[i]$ supplies are inactive according to Jordan curve theorem on $n_1$, $n_2$, and $w[i]$.
-Therefore, if $w[i]$ forms a bond at its stabilization $\#bc(C_{i-1}) > \#bc(C_{i})$ holds.
-We now prove that $w[i]$ must form a bond.
-
-Suppose $w[i]$ ware stabilized without any bond, that is, by a tunnel.
-For that the two points that are a neighbor of both $w[i-1]$ and $w[i]$ must be occupied already.
-In addition, at least one of the neighbors of $w[i]$ must be free because $S[i+1] = b$.
-Thus, only the case to be considered is Fig.~\ref{TTT_tunnel_direction} (middle) with $n_5$ being occupied (that is, $n_4$ is free).
-In this case, before $w[i]$ is stabilized, at lest three neighbors of $n_2$ ware free and hence, a bead at $n_2$ was provided with one free bond and could form a bond with $w[i]$. \qed
-
-\begin{figure}
+\begin{figure}[tb]
   \begin{center}
@@
 
+\begin{lemma}
+\label{TTT_entrance_Tab}
+Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$, arity $\alpha =2$. 
+Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $S[i+1] = b$ and $S[i+2] \in \{ t_s, t_o \} $, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
+\end{lemma}
+
+\begin{proof}%[lemma \ref{TTT_entrance_Tab}]
+See Fig.\ref{TTT_tunnel_direction}.
+$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section of type $S$ or $O$.
+Thus,  its predecessor $w[i+1]$ must be inside the tunnel section, that is, $n_1$ and $n_2$ must be occupied.
+Free bonds of $w[i]$, if any, cannot be used in future by another bead $w[j]$ because otherwise the part of transcript $w[i..j]$ and the bond between $w[i]$ and $w[j]$ would form a closed curve and the curve would cross the path of $C_{i-1}$ between $n_1$ and $n_2$, contradiction.
+%Binding capabilities that $w[i]$ supplies are inactive according to Jordan curve theorem on $n_1$, $n_2$, and $w[i]$.
+Therefore, if $w[i]$ forms a bond at its stabilization $\#bc(C_{i-1}) > \#bc(C_{i})$ holds.
+We now prove that $w[i]$ must form a bond.
+
+Suppose $w[i]$ were stabilized without any bond, that is, by a tunnel.
+For that the two points that are a neighbor of both $w[i-1]$ and $w[i]$ must be occupied already.
+In addition, at least one of the neighbors of $w[i]$ must be free because $S[i+1] = b$.
+Thus, only the case to be considered is Fig.~\ref{TTT_tunnel_direction} (middle) with $n_5$ being occupied (that is, $n_4$ is free).
+In this case, before $w[i]$ is stabilized, at lest three neighbors of $n_2$ were free and hence, a bead at $n_2$ was provided with one free bond and could form a bond with $w[i]$. \qed
+
 \end{proof}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{lemma}
-\label{TTT_exit}
-Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$ and arity $\alpha =2$.
-%Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
-If $S[h..i+1] = bt^{(i-h)}b$ for some $h<i-1$ and $S[i] = t_s$ or $t_o$, then $\#bc(C_{i-2}) \geq \#bc(C_i)$, and hence, $\#bc(C_{h-1}) \geq \#bc(C_i)$.
-If $h < i-1$, then the second inequality is strengthened as $\#bc(C_{h-1}) > \#bc(C_{i})$.
-%if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
-\end{lemma}
-
-\begin{proof}%[Lemma~ \ref{TTT_exit}]
-Since the binding capability never increases inside a tunnel, we just need to consider the exit of a tunnel.
-See Fig.\ref{TTT_tunnel_exit}. 
-At least one of points $n_1$ or $n_2$ must be free because otherwise $w[i]$ would be inside of a tunnel, that is, $S[i+1]$ would not be $b$.
-
-%If $i - h > 1$ and $j$ is such that $h \leq j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because all neighbors of $w[j]$ are occupied by beads forming the tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$.
-%Thus, inside this tunnel, binding capabilities never increased.
-
-Let $a$ be the number of bonds $w[i-1]$ forms, that is, $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$. Then, $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$ as follows.
-
-\begin{itemize}
-\item{Case of both $n_1$ and $n_2$ being free}\\
-  This case can be regarded the same as entrance.
-See Fig.\ref{TTT_tunnel_exit} (Left).
-Predecessor $n_5$ has to be bound to $n_4$ and $n_5$ because both of $n_3$ and $n_4$ have binding capabilities.
-Hence, $a \geq 2$.
-This time, $\alpha = 2$, that is, this case $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
-
-\item{Case of $n_1$ is occupied}\\
-  See Fig.\ref{TTT_tunnel_exit} (Right).
-If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$.
-Hence,  $a \geq 1$.
-This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied by the successor of $p^\prime$.
-Therefore, this case $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
-
-\end{itemize}
-
-Thus,$\#bc(C_{i-2}) \geq \#bc(C_i)$ , and hence, $\#bc(C_{h-1}) \geq \#bc(C_i)$.
-If $h < i-1$, then the second inequality is strengthened as $\#bc(C_{h-1}) > \#bc(C_{i})$ because $S[h] = b$, that is, $\#bc(C_{h-1}) > \#bc(C_h)$ and $\#bc(C_{h}) \geq \#bc(C_i)$. \qed
-
-\begin{figure}
+\begin{figure}[tb]
   \centering
@@
             \fill[blue](0,0) circle [radius=0.05];
-            \node[above] at (0,0) {$w[i]$};
+            \node[above] at (0,0) {$w[j]$};
 
@@
             \node[transform canvas={shift=(-120:1)},left] {$n_4$};
-            \node[transform canvas={shift=(180:1)},above] {$w[i-1]$};
+            \node[transform canvas={shift=(180:1)},above] {$w[j-1]$};
 
@@
 \end{figure}
+
+\begin{lemma}
+\label{TTT_exit}
+Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$ and arity $\alpha =2$.
+%Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
+If $S[i+1..j+1] = bt^{(j-i-1)}b$ for some $i,j$ with $i \leq j-2$ and $S[j] \in \{ t_s, t_o\}$, then $\#bc(C_{j-2}) \geq \#bc(C_j)$, and hence, $\#bc(C_{i}) \geq \#bc(C_j)$.
+If $i \leq j-3$, then the second inequality is strengthened as $\#bc(C_{i}) > \#bc(C_{j})$.
+%if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
+\end{lemma}
+
+\begin{proof}%[Lemma~ \ref{TTT_exit}]
+Since the binding capability never increases inside a tunnel, we just need to consider the exit of a tunnel.
+See Fig.\ref{TTT_tunnel_exit}. 
+At least one of points $n_1$ or $n_2$ must be free because otherwise $w[j]$ would be inside of a tunnel, that is, $S[j+1]$ would not be $b$.
+
+%If $i - h > 1$ and $j$ is such that $h \leq j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because all neighbors of $w[j]$ are occupied by beads forming the tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$.
+%Thus, inside this tunnel, binding capabilities never increased.
+
+Let $m$ be the number of bonds $w[j-1]$ forms, that is, $\#bc(C_{j-2}) - \#bc(C_{j-1}) = m$.
+We claim $\#bc(C_{j}) - \#bc(C_{j-1}) \leq m$.
+Indeed, if both $n_1$ and $n_2$ are free (see Fig.~\ref{TTT_tunnel_exit}), the predecessor $w[j-1]$ must be bound to both beads at $n_3$ and at $n_4$ because both of them still have a free hand.
+Hence, $m \geq 2$.
+Since $\#bc(C_{j}) - \#bc(C_{j-1})$ is less than the arity, this difference is at most $m$.
+
+If $n_1$ is occupied, then $n_2$ is free.
+The predecessor $w[j-1]$ must be bound $n_4$.
+Hence,  $m \geq 1$.
+The bead $w[j]$ can increase the binding capability at most by 1 because one of its free neighbors would, $n_0$ or $n_2$, is to be occupied by the successor $w[j+1]$.
+Therefore, $\#bc(C_{j}) - \#bc(C_{j-1}) \leq m$.
+
+Thus,$\#bc(C_{j-2}) \geq \#bc(C_j)$ , and hence, $\#bc(C_{i}) \geq \#bc(C_j)$.
+If $i \leq j-3$, then the second inequality is strengthened as $\#bc(C_{i}) > \#bc(C_{j})$ because $S[i+1] = b$, that is, $\#bc(C_{i}) > \#bc(C_{i+1})$ and $\#bc(C_{i+1}) \geq \#bc(C_j)$. \qed
+
 \end{proof}
@@
 Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
-If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ and $S[i+2] = t_a$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $S[i+l+2] = t_a$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
+If $S[i+2] = t_a$, the following statements hold.
+\begin{enumerate}
+\item If $S[i] = b$, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
+\item If $S[i] \in \{t_s, t_o \}$, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
+\item If $S[i] = t_a$, $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
+\end{enumerate}
+%If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ and $S[i+2] = t_a$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $S[i+l+2] = t_a$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
 \end{lemma}
@@
 
-\begin{proof}[Lemma~ \ref{TTT_tunnelC_lemma}]
-Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
-Assume $S[h..i+1] = bt^{i-h}b (h<i)$.
+%\begin{proof}[Lemma~ \ref{TTT_tunnelC_lemma}]
+%Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
+%Assume $S[h..i+1] = bt^{i-h}b (h<i)$.
 If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$, with $h+2 \leq g \leq i$ is stabilized by tunnel $C$, $C_g$ is a terminal.
-
-Let us consider stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ as follows.
+%
+%
+%Let us consider stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ as follows.
 In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
@@
 Thus, $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_{i})$.
-\\
-
-\subsubsection{Case of $S[h-1..h+1] = bbt$}
-See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
-If $w[h-1]$ forms one bond, then it leaves one free bond, but it is consumed by $w[h+1]$.
-In addition, $w[h]$ has to bound.
-Thus, in this cases, binding capability decreases by 1.
-If $w[h-1]$ forms two bonds, then it does not leave any bond.
-In addition, $w[h]$ has to be bound.
-Thus, in this case, even if $w[h+1]$ supplies two free bonds, binding capability decreases by 1.
+%\\
+%
+%\subsubsection{Case of $S[h-1..h+1] = bbt$}
+%See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
+%If $w[h-1]$ forms one bond, then it leaves one free bond, but it is consumed by $w[h+1]$.
+%In addition, $w[h]$ has to bound.
+%Thus, in this cases, binding capability decreases by 1.
+%If $w[h-1]$ forms two bonds, then it does not leave any bond.
+%In addition, $w[h]$ has to be bound.
+%Thus, in this case, even if $w[h+1]$ supplies two free bonds, binding capability decreases by 1.
 
@@
 
-\subsubsection{Case of $S[h-1..h+1] = tbt_a$}
-Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
-
-%\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-  In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$.
+%\subsubsection{Case of $S[h-1..h+1] = tbt_a$}
+%Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
+%
+%%\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
+%  In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$.
 Moreover, $w[h]$ has to bind to one of $n_1, n_2, n_3$ in order to stabilize deterministically.
@@
 Thus, this case $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
-
-  These cases are divided on number of capabilities that $w[h-1]$ consumes.
-  \begin{itemize}
-  \item[-]{$w[h-1]$ does not consume any bindings}\\
-  According to Lemma~\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
-    $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
-    $w[h+1]$ has to be bound to $w[h-1]$ because $w[h-1]$ has bindings, that is, $w[h+1]$ consumes at least one hand and supplies at most one hand so that $\#bc(C_{h}) \geq \#bc(C_{h+1})$.
+%
+%  These cases are divided on number of capabilities that $w[h-1]$ consumes.
+%  \begin{itemize}
+%  \item[-]{$w[h-1]$ does not consume any bindings}\\
+%  According to Lemma~\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
+%    $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
+%    $w[h+1]$ has to be bound to $w[h-1]$ because $w[h-1]$ has bindings, that is, $w[h+1]$ consumes at least one hand and supplies at most one hand so that $\#bc(C_{h}) \geq \#bc(C_{h+1})$.
 Thus, in this cases $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
-%     This time, let us consider either $n_4$ is occupied or not.
+%%     This time, let us consider either $n_4$ is occupied or not.
 If $n_4$ is occupied, then $w[h-1]$ has no active bindings that is this situation consumes some binding capabilities.
@@
 Thus in this cases $\#bc(C_{h-1}) > \#bc(C_{h+2})$.
-
-  \item[-]{$w[h-1]$ consumes one binding}\\
-    In this case, $w_{h}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[h-1]$ and $w[h+1]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
-  \item[-]{$w[h-1]$ consumes two bindings}\\
-    In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies two bindings. Thus, in this cases $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
-
-  \end{itemize}
+%
+%  \item[-]{$w[h-1]$ consumes one binding}\\
+%    In this case, $w_{h}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[h-1]$ and $w[h+1]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
+%  \item[-]{$w[h-1]$ consumes two bindings}\\
+%    In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies two bindings. Thus, in this cases $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
+%   
+%  \end{itemize}
 
@@
 
-\end{proof}
+%\end{proof}
 
@@
 
-\proof%{Proof of Tunnel Troll Theorem}
-Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
-then it has at most one free neighbor, and hence its successor it to be stabilized there.
-Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.
-
-Tunnel sections have three possible shapes up to symmetry : straight($S$), obtuse($O$) and acute($A$) turn (Fig. \ref{TTT_tunnel}), and we will consider each of those.
+\proof{Proof of Tunnel Troll Theorem}
+%Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
+%then it has at most one free neighbor, and hence its successor it to be stabilized there.
+%Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.
+%
+%Tunnel sections have three possible shapes up to symmetry : straight($S$), obtuse($O$) and acute($A$) turn (Fig. \ref{fig:TTT_tunnel}), and we will consider each of those.
 
@@
 
-Next, we consider the case of $\delta = 2, \alpha = 1$.
-We assume there is an index $h$ such that $S[h-1..h+1] = bbt$ or $S[h-1..h+1] = tbt$.
-According to Lemma~\ref{TTT_entrance_Tab}, if $w[h+1]$ is stabilized by tunnel $A$ or $B$, then $\#bc(C_{h-1}) > \#bc(C_{h})$.
-Also,  According to Lemma~\ref{TTT_tunnelC_lemma}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
-On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of Lemma~\ref{TTT_exit}.
+Next, we consider the case of $\delta = 2, \alpha = 1$. We assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and $S[i+2] \in \{ t_s, t_o \} $.
+Then, all $S[i+1..j]$ do not contain $t_o$; otherwise $S[i+1..j]$ contain $\blacksquare$.
+Therefore according to Lemma~\ref{TTT_entrance_Tab}, $\#bc(C_{i-1}) > \#bc(C_{i})$ and moreover that, according to Lemma~\ref{TTT_exit}, $\#bc(C_{i}) \geq \#bc(C_{j})$.
+
+On the other hand, we assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and $S[i+2] = t_a$.
+
+Let us consider that $w[i]$ supplies two bonds (that is, $S[i] = t$).
+If $S[i] \in \{ t_s, t_o \}$, $\#bc(C_{i-2}) \geq \#bc(C_{i})$ because of Lemma~\ref{TTT_exit}.
+Therefore,
+
+if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of Lemma~\ref{TTT_exit}.
 Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.
@@
 
+\begin{figure}[tb]
+ \centering
+    \begin{tikzpicture}
+
+	\fill (0,0) circle [radius=0.1];
+        \fill[blue] (60:1) circle [radius=0.05];
+        \fill (0:1) circle [radius=0.1];
+
+      \draw[dashed] (180:2) -- (0:2);
+      \draw[dashed, shift=(60:1)] (180:2.5) -- (0:1.5);
+      \draw[->, blue] (60:0.1) -- (60:0.9);
+
+	\node[above] at (180:1) {$p_1$};
+	\node[left] at (-120:1) {$p_2$};
+	\node[left] at (-60:1) {$p_3$};
+	\node[left, shift=(-120:1)] at (-60:1) {$p_3$};
+
+	\draw (180:1) circle [radius=0.05];
+	\draw (-120:1) circle [radius=0.05];
+	\draw (-60:1) circle [radius=0.05];
+	\draw[shift=(-120:1)] (-60:1) circle [radius=0.05];
+
+	\node at (0:2.5) {$n$};
+	\node[shift=(60:1)] at (0:2) {$n+1$};
+    \end{tikzpicture}
+    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
+    \label{TTT_a4_first}
+\end{figure}
+
 \begin{theorem}[$\delta = 1, \alpha = 4$]
@@
 \begin{proof}
-%According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds.
-Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized.
-See Fig.\ref{TTT_a4_first}.
-any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$.
-At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind.
-In this case, a point which is able to put a bead is only $n_2$.
-Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$.
-Hence oritatami system can yield only a finite structure whose size is $O(n^2)$ in $\delta =1, \alpha = 4$.
-%%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
-seki sensei.
+Consider the moment when a bead $b$ is stabilized outside $\hexagon_O^n$ for the first time. 
+See Fig.~\ref{TTT_a4_first}
+There is only one bead available to stabilize $b$ there, which is $b_1$. 
+In order for $b$ to avoid nondeterminism, hence, none of the beads around should not attract $b$.
+
+The point $p_1$ must be empty because a bead there would have at least two free neighbors and hence is provided with a free hand. 
+If there is a bead at $p_2$, $n$ must be at least 2 so that the bead is not singular. 
+Since $p_1$ is empty, this bead has at least one free hand, a contradiction. 
+Thus, $p_2$ must be also empty. 
+In the same way, we can easily show that the point $p_3$ must not be occupied by a non-singular bead. 
+Suppose $p_3 = O$. 
+The point $p_4$ must not be empty; otherwise the singular bead, at $O$, would have a free hand. 
+However, then a bead at $p_4$ would be provided with a free hand, a contradiction. 
+\qed
 \end{proof}
-
-\begin{figure}
- \centering
-    \begin{tikzpicture}
-	\fill[shift=(-120:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0), blue] (0,0) circle [radius=0.05];
-
-      \draw[dashed] (180:2) -- (0:2);
-      \draw[dashed, shift=(-60:1)] (180:2.5) -- (0:1.5);
-      \draw[->, blue] (-120:0.9) -- (-120:0.1);
-
-	\node[below] at (-120:1) {$w_{[i-1]}$};
-	\node[above] at (180:0) {$w_{[i]}$};
-	\node[above] at (0:1) {$n_0$};
-
-	\foreach \theta in {0,60,-60,120,180}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[above] at (180:1) {$n_5$};
-
-	\node at (0:2.5) {$n+1$};
-	\node[shift=(-60:1)] at (0:2) {$n$};
-    \end{tikzpicture}
-    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
-    \label{TTT_a4_first}
-\end{figure}
 

### 2018-12-04 arity1.tex
Fixed pyramid drawing from red-green to numbered
Fixed small drawings for pyramid
I must have made a mistake with the commit for the big pyramid last
night. I will commit again when I get home
Update arity1.tex

@@
 		\centering
-		\includegraphics[align=c,height=1in]{./Fig/CI_1}\\
+		\includegraphics[align=c,height=1in]{./Fig/CI_1n}\\
 		\bigskip
@@
 		\centering
-		\includegraphics[align=c,height=0.7in]{./Fig/CI_2}\\
+		\includegraphics[align=c,height=0.7in]{./Fig/CI_2n}\\
 		\bigskip
@@
 		\centering
-		\includegraphics[align=c,height=0.5in]{./Fig/CI_3}
+		\includegraphics[align=c,height=0.5in]{./Fig/CI_3n}
 		\bigskip
 		\vspace{0.1in}
-		\includegraphics[align=c,height=0.5in]{./Fig/CI_4}
+		\includegraphics[align=c,height=0.5in]{./Fig/CI_4n}
 		\bigskip
 
-		(c) Bead $i+1$, when bead $i$ is $B_{3,4}$ and $B_{1,2}$, respectively
+		(c) Portions of row $1$
 	\end{minipage}
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{./Fig/CI_turn}
+	\includegraphics[width=0.7\linewidth]{./Fig/CI_turnn}
 	\caption{Beads $4k, 8k-2, \dots$ stabilize at turning points because the bead two positions before is the same type and has a free hand.}
@@
 \end{figure}
+
+\subsubsection{3.2.1 \ \ $\delta = 2$\\}
 
@@
 	%\hspace{10mm} %
-	\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut3}
+	\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut3n}
 
@@
 
-\subsection{In the case of $\delta = 3$}
+\subsubsection{3.2.2 \ \ $\delta = 3$\\}
 
-As before, the length of seed is $n$ and the seed will be inside $\hexagon_p^n$, the equilateral hexagon with a radius of $n$ and center $p$, the point where the first bead of the seed is fixed.
-We will begin our discussion by considering the moment when the first bead is fixed outside $\hexagon_p^n$.
-Let this bead be the $i$th one.
-
-\textbf{A.} First, let us assume that a fixed bead on a side of $\hexagon_p^n$ has a free hand, and bead $i$ binds to it.
+\textbf{A.} First, let us assume that a fixed bead on a side of $hexagon_p^n$ has a free hand, and bead $i$ binds to it.
 If the most stable conformation formed by beads $i, i+1, i+2$ has only two hydrogen bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}.
@@
     \begin{tabular}{cc}
-    \begin{tikzpicture}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
-      \fill (2.0, 1.732) node [right] {$n+2$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (0 : 0.0)]
-        \foreach \theta in {60, 120}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw (0 : 0.0) -- (60 : 1.0);
-        \draw (60 : 1.0) -- (120 : 1.0);
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (120 : 1.0)]
-        \foreach \theta in {60}{
-        \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 1.732) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (-0.5, 0.866);
+        \draw (0.0, 1.732) -- (-0.5, 0.866);
+        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
+        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
       \end{tikzpicture}
 
-    \begin{tikzpicture}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
-      \fill (2.0, 1.732) node [right] {$n+2$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (0 : 0.0)]
-        \foreach \theta in {60, 120}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
-        \draw (60 : 1.0) -- (120 : 1.0);
-        \draw (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \draw (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (120 : 1.0)]
-        \foreach \theta in {60}{
-        \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted](0 : 0.0) -- (60 : 1.0);
-      \end{scope}
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 1.732) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \draw (0.0, 0.0) -- (-0.5, 0.866);
+        \draw (-0.5, 0.866) -- (0.5, 0.866);
+        \draw (0.0, 1.732) -- (0.5, 0.866);
+        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
+        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
       \end{tikzpicture}
+
     \end{tabular}
@@
 
-There are the two cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}.
+There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}.
 However, if it makes three bonds once, such as in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
 Similarly to case 1.
-in the previous section, this becomes nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a corner of $\hexagon_p^n$.
+in the previous section, (a), (b) and (c)in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a first corner of $hexagon_p^n$ and  (e) in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a second corner of $hexagon_p^n$.
+(d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
 Thus, the fixed bead on the side of an equilateral hexagon with a radius of $n$ has to make a hydrogen bond with a bead in an equilateral hexagon.
@@
   \begin{center}
-  \begin{tabular}{cc}
-    \begin{tikzpicture}
-      \draw [dashed] (-0.5, 0.0) -- (3.5, 0.0);
-      \fill (3.5, 0.0) node [right] {$n$};
-      \draw [dashed] (-0.5, 0.866) -- (3.5, 0.866);
-      \fill (3.5, 0.866) node [right] {$n+1$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (0 : 0.0)]
-        \foreach \theta in {0, 60}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \fill (0,0) circle [radius = 0.05];
-        \foreach \theta in {0, 60, 120}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-          \draw (0 : 0.0) -- (0 : 2.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 1.0)]
-          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 3.0)]
-          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
+    \begin{tabular}{ccc}
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (1.0, 0.0) circle [radius = 0.1];
+        \fill (2.0, 0.0) circle [radius = 0.1];
+        \fill (3.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (1.5, 0.866) circle [radius = 0.1];
+        \fill (2.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (0.5, 0.866) node [above] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (1.5, 0.866);
+        \draw (1.5, 0.866) -- (2.5, 0.866);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \fill (1.5, -0.5) node [below] {(a)};
       \end{tikzpicture}
 
-    \begin{tikzpicture}
-      \draw [dashed] (-1.5, 0.0) -- (2.5, 0.0);
-      \fill (2.5, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.5, 0.866) -- (2.5, 0.866);
-      \fill (2.5, 0.866) node [right] {$n+1$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (0 : 0.0)]
-        \foreach \theta in {0, 60, 120, 180}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \fill (0,0) circle [radius = 0.05];
-        \foreach \theta in {120}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (120 : 1.0)]
-          \draw (0 : 0.0) -- (0 : 2.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 1.0)]
-          \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (180 : 1.0)]
-          \draw [dotted] (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (1.0, 0.0) circle [radius = 0.1];
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (-1.0, 0.0) circle [radius = 0.1];
+        \fill (-2.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (-1.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (0.5, 0.866) node [above] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (-0.5, 0.866);
+        \draw (-0.5, 0.866) -- (-1.5, 0.866);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (-0.5, 0.866) -- (-1.0, 0.0);
+        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
+        \fill (-0.5, -0.5) node [below] {(b)};
+      \end{tikzpicture}\\
+
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (1.0, 0.0) circle [radius = 0.1];
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (-1.0, 0.0) circle [radius = 0.1];
+        \fill (-2.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (-1.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (0.5, 0.866) node [above] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (-0.5, 0.866);
+        \draw (-0.5, 0.866) -- (-1.5, 0.866);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
+        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
+        \fill (-0.5, -0.5) node [below] {(c)};
       \end{tikzpicture}
+
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (1.0, 0.0) circle [radius = 0.1];
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (-2.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (-1.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (0.5, 0.866) node [above] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (-0.5, 0.866);
+        \draw (-0.5, 0.866) -- (-1.5, 0.866);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
+        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
+        \fill (-0.5, -0.5) node [below] {(d)};
+      \end{tikzpicture}
+
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (1.0, 0.0) circle [radius = 0.1];
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (-1.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (-1.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (0.5, 0.866) node [above] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (-0.5, 0.866);
+        \draw (-0.5, 0.866) -- (-1.5, 0.866);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
+        \draw [dashed] [red] (-1.5, 0.866) -- (-1.0, 0.0);
+        \fill (-0.5, -0.5) node [below] {(e)};
+      \end{tikzpicture}\\
+
+      (c) there is an inactive bead at (-1,0).\\
+      (d) there is no bead at (-1,0).
+
     \end{tabular}
@@
   \end{center}
-
 \end{figure}
@@
   \begin{center}
-  \begin{tabular}{cc}
-    \begin{tikzpicture}
-      \draw [dashed] (-0.5, 0.0) -- (2.0, 0.0);
-      \fill (3.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-0.5, 0.866) -- (2.5, 0.866);
-      \fill (3.0, 0.866) node [right] {$n+1$};
-      \draw [dashed] (-0.5, 1.732) -- (3.0, 1.732);
-      \fill (3.0, 1.732) node [right] {$n+2$};
-      \fill (60 : 1.0) circle [radius = 0.05];
-      \draw (-0.1,-0.1) -- (0.1,0.1);
-      \draw (0.1,-0.1) -- (-0.1,0.1);
-      \begin{scope}[shift = (120 : 1.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-      \end{scope}
-      \begin{scope}[shift = (120 : 1.0)]
-        \draw [dotted] (0 : 0.0) -- (300 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \draw (0.0, 0.0) -- (2.0, 0.0);
-        \fill (2.0, 0.0) circle [radius = 0.05];
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \draw [dashed] (0 : 0.0) -- (300 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 1.0)]
-      \fill (0.0, 0.0) circle [radius = 0.05];
-        \foreach \theta in {0, 60}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \begin{scope}[shift = (120 : 1.0)]
-          \fill (0.0, 0.0) circle [radius = 0.05];
-          \draw (0 : 0.0) -- (240 : 1.0);
-          \draw (0 : 0.0) -- (300 : 1.0);
-        \end{scope}
-      \end{scope}
+    \begin{tabular}{ccc}
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (1.0, 0.0) circle [radius = 0.1];
+        \fill (2.0, 0.0) circle [radius = 0.1];
+        \fill (3.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
+        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
+        \fill [blue] (3.5, 0.866) circle [radius = 0.1];
+        \draw [blue] (0.5, 0.866) -- (1.5, 0.866);
+        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
+        \draw [blue] (2.5, 0.866) -- (3.5, 0.866);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
+        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
       \end{tikzpicture}
 
-    \begin{tikzpicture}
-      \draw [dashed] (-0.5, 0.0) -- (2.0, 0.0);
-      \fill (3.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-0.5, 0.866) -- (2.5, 0.866);
-      \fill (3.0, 0.866) node [right] {$n+1$};
-      \draw (-0.1,-0.1) -- (0.1,0.1);
-      \draw (0.1,-0.1) -- (-0.1,0.1);
-      \fill (60 : 1.0) circle [radius = 0.05];
-      \begin{scope}[shift = (120 : 1.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-      \end{scope}
-      \begin{scope}[shift = (120 : 1.0)]
-        \draw [dotted] (0 : 0.0) -- (300 : 1.0);
-        \draw (0.0, 0.0) -- (3.0, 0.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \draw [dashed] (0 : 0.0) -- (300 : 1.0);
-        \fill (60 : 1.0) circle [radius = 0.05];
-      \end{scope}
-      \begin{scope}[shift = (0 : 1.0)]
-        \fill (0.0, 0.0) circle [radius = 0.05];
-        \foreach \theta in {0, 60}{
-          \fill (0,0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (1.0, 0.0) circle [radius = 0.1];
+        \fill (2.0, 0.0) circle [radius = 0.1];
+        \fill (3.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
+        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
+        \fill [blue] (1.0, 1.732) circle [radius = 0.1];
+        \draw [blue] (0.5, 0.866) -- (1.0, 1.732);
+        \draw [blue] (1.5, 0.866) -- (1.0, 1.732);
+        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
+        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
       \end{tikzpicture}
+
     \end{tabular}
@@
 
-\textbf{B.} Next, assume that bead $i$ could not bind to anything and let us discuss the moment after bead $i$ is fixed outside $\hexagon_p^n$.
+\textbf{B.} Next, let us assume that a fixed bead on a side of $hexagon_p^n$ does not have any free hands.
+And then assume that there is a bead having a free hand at (1,0).
+If there is a bead at (1,0) and beads $i, i+1, i+2$ make only two hydrogen bonds, it will become nondeterministic such as in Fig.~\ref{fig:beadat(1,0)}.
+That is, bead $i, i+1, i+2$ need to make three bonds to place a bead.
+If they make three hydrogen bonds, it will become \textbf{A}.
+There should not be any bead having a free hand at (1,0) or (-1,0) to prevent from becoming \textbf{A}.
+Let us discuss the moment after bead $i$ is fixed outside $hexagon_p^n$.
 Now bead $i$ has a free hand.
-If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such structures, as in Fig.~\ref{fig:afterzigzag}.
-Hence, they need to form three bonds to deterministically stabilize, such as in the right or left side of Fig.~\ref{fig:afterline}.\\
+If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such structures, as in Fig.~\ref{fig:beadi2}.
+Hence, they need to form three bonds to deterministically stabilize, such as in Fig.~\ref{fig:3bonds2}.
+(a) in Fig~\ref{fig:3bonds2} becomes \textbf{A} because it makes three hydrogen bonds.
+(b) in Fig.~\ref{fig:3bonds2} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (1,0).\\
 
@@
     \begin{tabular}{cc}
-    \begin{tikzpicture}
-        \begin{scope}[shift=(0 : 0.0)]
-          \draw (-0.1,-0.1) -- (0.1,0.1);
-          \draw (0.1,-0.1) -- (-0.1,0.1);
-          \draw (0 : 0.0) -- (60 : 1.0);
-        \end{scope}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
-      \fill (2.0, 1.732) node [right] {$n+2$};
-      \draw [dashed] (-1.0, 2.598) -- (2.0, 2.598);
-      \fill (2.0, 2.598) node [right] {$n+3$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (60 : 2.0)]
-        \fill(0.0, 0.0) circle [radius = 0.05];
-        \foreach \theta in {120, 180, 240}{
-          \fill (0.0, 0.0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-        \draw (0 : 0.0) -- (180 : 1.0);
-        \draw (0 : 0.0) -- (240 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \begin{scope}[shift = (120 : 1.0)]
-          \draw (0.0, 0.0) -- (60 : 1.0);
-          \draw [dotted] (0.0, 0.0) -- (300 : 1.0);
-        \end{scope}
-      \end{scope}
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (1.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (1.5, 0.866) circle [radius = 0.1];
+        \fill (1.0, 1.732) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (0.5, 0.866) node [left] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (1.5, 0.866);
+        \draw (1.0, 1.732) -- (1.5, 0.866);
+        \draw [dashed] [red] (1.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
+        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
       \end{tikzpicture}
 
-    \begin{tikzpicture}
-        \begin{scope}[shift=(0 : 0.0)]
-          \draw (-0.1,-0.1) -- (0.1,0.1);
-          \draw (0.1,-0.1) -- (-0.1,0.1);
-          \draw (0 : 0.0) -- (60 : 1.0);
-        \end{scope}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \draw [dashed] (-1.0, 1.732) -- (2.0, 1.732);
-      \fill (2.0, 1.732) node [right] {$n+2$};
-      \draw [dashed] (-1.0, 2.598) -- (2.0, 2.598);
-      \fill (2.0, 2.598) node [right] {$n+3$};
-      \fill (0,0) circle [radius = 0.05];
-      \begin{scope}[shift = (60 : 2.0)]
-        \fill(0.0, 0.0) circle [radius = 0.05];
-        \foreach \theta in {120, 180, 240}{
-          \fill (0.0, 0.0) [transform canvas = {shift = (\theta : 1.0)}] circle [radius = 0.05];
-        }
-        \draw (0 : 0.0) -- (120 : 1.0);
-        \draw (0 : 0.0) -- (180 : 1.0);
-        \draw [dotted] (0 : 0.0) -- (240 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (60 : 1.0)]
-        \begin{scope}[shift = (120 : 1.0)]
-          \draw [dotted] (0.0, 0.0) -- (60 : 1.0);
-          \draw (0.0, 0.0) -- (300 : 1.0);
-        \end{scope}
-      \end{scope}
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (1.0, 0.0) circle [radius = 0.1];
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 1.732) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (-0.5, 0.866) node [left] {$(0, 1)$};
+        \draw (0.0, 0.0) -- (-0.5, 0.866);
+        \draw (-0.5, 0.866) -- (0.5, 0.866);
+        \draw (0.0, 1.732) -- (0.5, 0.866);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
       \end{tikzpicture}
+
     \end{tabular}
     \caption{}
-    \label{fig:afterzigzag}
+    \label{fig:beadat(1,0)}
   \end{center}
 \end{figure}
-
- If they form three bonds once, such as Fig.~\ref{fig:afterline}, the system would need three bonds forever to be deterministic.
-This becomes nondeterministic finally, such as in Fig.~\ref{fig:hexcorner}, when it reaches a corner of $\hexagon_p^n$.
- %Therefore, the first fixed bead on a side of an equilateral hexagon with a radius of $n+1$ has to make a hydrogen bond with a molecule on a side of an equilateral hexagon with a radius of $n$.
 
@@
     \begin{tabular}{cc}
-    \begin{tikzpicture}
-      \begin{scope}[shift=(0 : 0.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \draw [dashed] (-0.5, 0.0) -- (4.5, 0.0);
-      \fill (4.5, 0.0) node [right] {$n$};
-      \draw [dashed] (-0.5, 0.866) -- (4.5, 0.866);
-      \fill (4.5, 0.866) node [right] {$n+1$};
-      \fill (2.0, 0.0) circle [radius = 0.05];
-      \fill (3.0, 0.0) circle [radius = 0.05];
-      \fill (4.0, 0.0) circle [radius = 0.05];
-      \begin{scope}[shift = (60 : 1.0)]
-        \fill (0.0, 0.0) circle [radius = 0.05];
-        \fill (1.0, 0.0) circle [radius = 0.05];
-        \fill (2.0, 0.0) circle [radius = 0.05];
-        \fill (3.0, 0.0) circle [radius = 0.05];
-        \draw (0.0, 0.0) -- (3.0, 0.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 2.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 3.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : 4.0)]
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 1.732) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (-0.5, 0.866);
+        \draw (0.0, 1.732) -- (-0.5, 0.866);
+        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
+        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
       \end{tikzpicture}
 
-    \begin{tikzpicture}
-      \begin{scope}[shift=(0 : 0.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \draw [dashed] (-3.5, 0.0) -- (1.0, 0.0);
-      \fill (1.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-3.5, 0.866) -- (1.0, 0.866);
-      \fill (1.0, 0.866) node [right] {$n+1$};
-      \fill (-1.0, 0.0) circle [radius = 0.05];
-      \fill (-2.0, 0.0) circle [radius = 0.05];
-      \fill (-3.0, 0.0) circle [radius = 0.05];
-      \begin{scope}[shift = (60 : 1.0)]
-        \fill (0.0, 0.0) circle [radius = 0.05];
-        \fill (-1.0, 0.0) circle [radius = 0.05];
-        \fill (-2.0, 0.0) circle [radius = 0.05];
-        \fill (-3.0, 0.0) circle [radius = 0.05];
-        \draw (0.0, 0.0) -- (-3.0, 0.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : -1.0)]
-        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : -2.0)]
-        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \begin{scope}[shift = (0 : -3.0)]
-        \draw [dotted] (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 1.732) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (-0.5, 0.866);
+        \draw (-0.5, 0.866) -- (0.5, 0.866);
+        \draw (0.0, 1.732) -- (0.5, 0.866);
+        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
+        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
       \end{tikzpicture}
+
     \end{tabular}
     \caption{}
-    \label{fig:afterline}
+    \label{fig:beadi2}
   \end{center}
@@
 
-Accordingly, it is Fig.~\ref{fig:firstout} when a first bead is fixed on a side of an equilateral hexagon with a radius of $n+1$.
-
 \begin{figure}
   \begin{center}
-    \begin{tikzpicture}
-      \draw [dashed] (-1.0, 0.0) -- (2.0, 0.0);
-      \fill (2.0, 0.0) node [right] {$n$};
-      \draw [dashed] (-1.0, 0.866) -- (2.0, 0.866);
-      \fill (2.0, 0.866) node [right] {$n+1$};
-      \begin{scope}[shift=(0 : 0.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-        \draw (0 : 0.0) -- (60 : 1.0);
-      \end{scope}
-      \begin{scope}[shift=(60 : 1.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-      \end{scope}
-      \begin{scope}[shift=(0 : 1.0)]
-        \draw (-0.1,-0.1) -- (0.1,0.1);
-        \draw (0.1,-0.1) -- (-0.1,0.1);
-        \draw [dotted] (0 : 0.0) -- (120 : 1.0);
-      \end{scope}
+    \begin{tabular}{ccc}
+
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (1.0, 0.0) circle [radius = 0.1];
+        \fill (2.0, 0.0) circle [radius = 0.1];
+        \fill (3.0, 0.0) circle [radius = 0.1];
+        \fill (4.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (1.5, 0.866) circle [radius = 0.1];
+        \fill (2.5, 0.866) circle [radius = 0.1];
+        \fill (3.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (0.5, 0.866) node [above] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (1.5, 0.866);
+        \draw (1.5, 0.866) -- (2.5, 0.866);
+        \draw (2.5, 0.866) -- (3.5, 0.866);
+        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
+        \fill (1.5, -0.5) node [below] {(a)};
       \end{tikzpicture}
+
+      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (2.0, 0.0) circle [radius = 0.1];
+        \fill (3.0, 0.0) circle [radius = 0.1];
+        \fill (4.0, 0.0) circle [radius = 0.1];
+        \fill (0.5, 0.866) circle [radius = 0.1];
+        \fill (1.5, 0.866) circle [radius = 0.1];
+        \fill (2.5, 0.866) circle [radius = 0.1];
+        \fill (3.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (0.5, 0.866) node [above] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (1.5, 0.866);
+        \draw (1.5, 0.866) -- (2.5, 0.866);
+        \draw (2.5, 0.866) -- (3.5, 0.866);
+        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
+        \fill (1.5, -0.5) node [below] {(b)};
+      \end{tikzpicture}\\
+
+      (a) there is an inactive bead at (1,0).\\
+      (b) there is no bead at (1,0).
+
+    \end{tabular}
     \caption{}
-    \label{fig:firstout}
+    \label{fig:3bonds2}
   \end{center}
 \end{figure}
-
-%It has to be a right or left figure in Fig.6.
-when the first bead fixed on a side of an equilateral hexagon with a radius of $n+1$ make a hydrogen bond with a bead on a side of an equilateral hexagon with a radius of $n$.
-Fig.6.
-becomes nondeterministic finally, such as in Fig.7., when it reaches a corner of an equilateral hexagon.
-It is clear that all beads on a side of an equilateral hexagon with a radius of $n+1$ has to make a hydrogen bond with a bead on a side of an equilateral hexagon with a radius of $n$.
-It is impossible to fix molecules on a side of an equilateral hexagon with a radius of $n+2$ and determine the only structure when there are only beads which are able to make a hydrogen bond in an equilateral hexagon with a radius of $n$.

### 2018-12-04 arity1.tex
Update arity1.tex

@@
 
-\subsubsection{3.2.1 \ \ $\delta = 2$\\}
+\subsubsection{$\delta = 2$\\}
 
@@
 
-\subsubsection{3.2.2 \ \ $\delta = 3$\\}
+\subsubsection{$\delta = 3$\\}
 
-\textbf{A.} First, let us assume that a fixed bead on a side of $hexagon_p^n$ has a free hand, and bead $i$ binds to it.
+\textbf{A.} First, let us assume that a fixed bead on a side of $\hexagon_p^n$ has a free hand, and bead $i$ binds to it.
 If the most stable conformation formed by beads $i, i+1, i+2$ has only two hydrogen bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}.
@@
 Similarly to case 1.
-in the previous section, (a), (b) and (c)in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a first corner of $hexagon_p^n$ and  (e) in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a second corner of $hexagon_p^n$.
+in the previous section, (a), (b) and (c)in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a first corner of $\hexagon_p^n$ and  (e) in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a second corner of $\hexagon_p^n$.
 (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
-Thus, the fixed bead on the side of an equilateral hexagon with a radius of $n$ has to make a hydrogen bond with a bead in an equilateral hexagon.
 
@@
 
-\textbf{B.} Next, let us assume that a fixed bead on a side of $hexagon_p^n$ does not have any free hands.
-And then assume that there is a bead having a free hand at (1,0).
-If there is a bead at (1,0) and beads $i, i+1, i+2$ make only two hydrogen bonds, it will become nondeterministic such as in Fig.~\ref{fig:beadat(1,0)}.
-That is, bead $i, i+1, i+2$ need to make three bonds to place a bead.
-If they make three hydrogen bonds, it will become \textbf{A}.
+\textbf{B.} Next, let us assume that bead $i$'s predecessor at (0,0) has no free hand and that there is a bead at (1,0) which has a free hand.
+If there is a bead at (1,0) and beads $i, i+1, i+2$ make only two hydrogen bonds, it will become nondeterministic as in Fig.~\ref{fig:beadat(1,0)}.
+That is, beads $i, i+1, i+2$ need to make three bonds to stabilize $i$.
+If they make three hydrogen bonds, the situation is analogous to \textbf{A}.
 There should not be any bead having a free hand at (1,0) or (-1,0) to prevent from becoming \textbf{A}.
-Let us discuss the moment after bead $i$ is fixed outside $hexagon_p^n$.
+Let us discuss the moment after bead $i$ is fixed outside $\hexagon_p^n$.
 Now bead $i$ has a free hand.

### 2018-12-04 arity1.tex

@@
 		\centering
-		\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut2}
+		\includegraphics[width=0.9\linewidth]{./Fig/hexagonOut2}
 		\caption{}
@@
 	%\hspace{10mm} %
-	\includegraphics[width=0.6\linewidth]{./Fig/hexagonOut3n}
+	\includegraphics[width=0.8\linewidth]{./Fig/hexagonOut3n}
 
@@
     \begin{tabular}{cc}
-      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
         \fill (0.0, 0.0) circle [radius = 0.1];
@@
         \draw (0.0, 1.732) -- (-0.5, 0.866);
-        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
-        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
+        \draw [dotted] [red] (0.0, 1.732) -- (0.5, 0.866);
+        \draw [dotted] [red] (0.0, 0.0) -- (-0.5, 0.866);
       \end{tikzpicture}
 
-      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
         \fill (0.0, 0.0) circle [radius = 0.1];
@@
         \draw (0.0, 1.732) -- (0.5, 0.866);
-        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
-        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
+        \draw [dotted] [red] (0.0, 0.0) -- (0.5, 0.866);
+        \draw [dotted] [red] (0.0, 1.732) -- (-0.5, 0.866);
       \end{tikzpicture}
@@
     \end{tabular}
-    \caption{}
+    \caption{Two conformations when a bead $i-1$ at (0,0) has a free hand}
     \label{fig:beadi}
@@
     \begin{tabular}{ccc}
-      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
         \fill (0.0, 0.0) circle [radius = 0.1];
@@
         \draw (1.5, 0.866) -- (2.5, 0.866);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
         \fill (1.5, -0.5) node [below] {(a)};
@@
 
-      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
         \fill (1.0, 0.0) circle [radius = 0.1];
@@
         \draw (-0.5, 0.866) -- (-1.5, 0.866);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (-0.5, 0.866) -- (-1.0, 0.0);
-        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
+        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dotted] [red] (-0.5, 0.866) -- (-1.0, 0.0);
+        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
         \fill (-0.5, -0.5) node [below] {(b)};
@@
         \draw (-0.5, 0.866) -- (-1.5, 0.866);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
-        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
+        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
+        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
         \fill (-0.5, -0.5) node [below] {(c)};
@@
         \draw (-0.5, 0.866) -- (-1.5, 0.866);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
-        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
+        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
+        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
         \fill (-0.5, -0.5) node [below] {(d)};
@@
         \draw (-0.5, 0.866) -- (-1.5, 0.866);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
-        \draw [dashed] [red] (-1.5, 0.866) -- (-1.0, 0.0);
+        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
+        \draw [dotted] [red] (-1.5, 0.866) -- (-1.0, 0.0);
         \fill (-0.5, -0.5) node [below] {(e)};
@@
 
-      (c) there is an inactive bead at (-1,0).\\
-      (d) there is no bead at (-1,0).
-
     \end{tabular}
-    \caption{}
+    \caption{When beads $i, i+1, i+2$ make three hydrogen bonds \newline (c) there is an inactive bead at (-1,0). \newline (d) there is no bead at (-1,0).}
     \label{fig:3bonds}
@@
     \begin{tabular}{ccc}
-      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
         \fill (1.0, 0.0) circle [radius = 0.1];
@@
         \draw [blue] (2.5, 0.866) -- (3.5, 0.866);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
         \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
@@
         \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
         \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
@@
     \end{tabular}
-    \caption{}
+    \caption{Being nondeterministic when reaching a corner of $\hexagon_p^n$}
     \label{fig:hexcorner}
@@
         \draw (1.0, 1.732) -- (1.5, 0.866);
-        \draw [dashed] [red] (1.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
-        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
+        \draw [dotted] [red] (1.5, 0.866) -- (1.0, 0.0);
+        \draw [dotted] [red] (1.0, 1.732) -- (0.5, 0.866);
+        \draw [dotted] [red] (1.0, 1.732) -- (0.5, 0.866);
       \end{tikzpicture}
 
-      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
         \fill (0.0, 0.0) circle [radius = 0.1];
@@
         \draw (0.0, 1.732) -- (0.5, 0.866);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
+        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dotted] [red] (0.0, 1.732) -- (-0.5, 0.866);
       \end{tikzpicture}
@@
     \end{tabular}
-    \caption{}
+    \caption{Two conformations when a bead at (1,0) has a free hand}
     \label{fig:beadat(1,0)}
@@
     \end{tabular}
-    \caption{}
+    \caption{Two conformations when a bead $i$ at (1,1) has a free hand}
     \label{fig:beadi2}
@@
 
-      \begin{tikzpicture}[thick,scale=0.6, every node/.style={scale=0.6}]
+      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
         \fill (0.0, 0.0) circle [radius = 0.1];
@@
         \draw (2.5, 0.866) -- (3.5, 0.866);
-        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
-        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
+        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dotted] [red] (3.5, 0.866) -- (4.0, 0.0);
         \fill (1.5, -0.5) node [below] {(a)};
@@
         \draw (2.5, 0.866) -- (3.5, 0.866);
-        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
-        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
+        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dotted] [red] (3.5, 0.866) -- (4.0, 0.0);
         \fill (1.5, -0.5) node [below] {(b)};
@@
 
-      (a) there is an inactive bead at (1,0).\\
-      (b) there is no bead at (1,0).
-
     \end{tabular}
-    \caption{}
+    \caption{When beads $i+1, i+2, i+3$ make three hydrogen bonds \newline (a) there is an inactive bead at (1,0). \newline (b) there is no bead at (1,0).}
     \label{fig:3bonds2}

### 2018-12-04 arity1.tex
Small correction to image and forcing transcipt table in place

@@
 Bead $4k$ is at $(4k-1,-1)$ and bead $4k+1$ is at $(4k,0)$.
+\vspace{0.1cm}
 
-The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where $\mathrm{row}_\ell$, for $\ell\in \{1,\dots, 2k\}$ is given in the table below.
-
-\begin{figure}
+The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where $\mathrm{row}_\ell$, for $\ell\in \{1,\dots, 2k\}$ is given in the table of Fig.~\ref{table:transcript}.
+\begin{figure}[h]
 	\begin{minipage}{.49\textwidth}
@@
 	\end{minipage}
-
+	\caption{}
+	\label{table:transcript}
 \end{figure}
-
-%\begin{center}
-%	
-%	%\scriptsize
-%	\begin{tabular}{llll}
-%		& $k$ odd &  & $k$ even\\
-%		$w=$\hspace{1cm} & $(2413)^{k-1}241$ & \hspace{1cm} &  $(2413)^{k-1}241$\\
-%		     & $(4231)^{k-1}4$   & &  $(4231)^{k-1}4$  \\
-%		     & $(1324)^{k-2}132$ & &  $(1324)^{k-2}132$\\
-%		     & $(3142)^{k-2}3$   & &  $(3142)^{k-2}3$ \vspace{5pt}\\
-%		     
-%		     & $(2413)^{k-3}241$ & &  $(2413)^{k-3}241$\\
-%		     & $(4231)^{k-3}4$   & &  $(4231)^{k-3}4$  \\
-%		     & $(1324)^{k-4}132$ & &  $(1324)^{k-4}132$\\
-%		     & $(3142)^{k-4}3$   & &  $(3142)^{k-4}3$\\
-%			 & \vdots			 & &  \vdots\\
-%			 & $(2413)^{2} 241$	 & &  $(2413)^{1} 241$\\
-%			 & $(4231)^2 4$		 & &  $(4231)^1 4$\\
-%			 & $(1324)^1 132$	 & &  $(1324)^0 132$\\
-%			 & $(3142)^1 3$		 & &  $(3142)^0 3$\\
-%			 & $(2413)^0 241$	 & & \\
-%			 & $(4231)^0 4$  	 & 
-%	\end{tabular}
-%	
-%\end{center}
 

### 2018-12-04 paper.tex

@@
 
-\usetikzlibrary{automata}
+\usetikzlibrary{automata,arrows}
 
@@
 
-Transcription is the first essential step of gene expression, in which a DNA template sequence is copied into a complementary single stranded RNA sequence by a `copy machine' called RNA polymerase. 
-The RNA strand is synthesized letter by letter according to the complimentarity relation ${\tt A} \rightarrow {\tt U}$, ${\tt G} \rightarrow {\tt C}$, ${\tt C} \rightarrow {\tt G}$, and ${\tt T} \rightarrow {\tt A}$ and folds up during a process called co-transcriptional folding.
+\begin{figure}[htb]
+\centering
+\begin{minipage}{0.6\linewidth}
+\includegraphics[width=\linewidth]{Fig/rna_origami.pdf}
+\end{minipage}
+\begin{minipage}{0.05\linewidth}
+\centering
+{\Large $\Rightarrow$}
+\end{minipage}
+\begin{minipage}{0.3\linewidth}
+\scalebox{0.3}{\begin{tikzpicture}
+\tikzstyle{mol} = [fill,circle,inner sep=2pt]
+
+\draw[-triangle 90, very thick] (3, 0) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(60:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(60:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(60:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(60:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(60:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(240:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(240:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(240:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(240:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(60:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(60:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(60:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(60:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(240:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(240:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(240:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(240:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(0:1) node[mol] {}
+-- ++(240:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1) node[mol] {}
+-- ++(180:1)
+;
+
+\draw[dashed, very thick]
+(-5, 0) -- ++(120:1)
+(-4, 0) -- ++(120:1)
+(-3, 0) -- ++(120:3)
+(-2, 0) -- ++(120:3)
+(-1, 0) -- ++(120:5)
+(0, 0) -- ++(120:1) ++(120:1) -- ++(120:3)
+(1, 0) -- ++(120:1) ++(120:1) -- ++(120:3)
+(2, 0) -- ++(120:1) ++(120:1) -- ++(120:1) ++(120:1) -- ++(120:1)
+(3, 0) -- ++(120:1) ++(120:3) -- ++(120:1)
+(4, 0) -- ++(120:1) ++(120:1) -- ++(120:1) ++(120:1) -- ++(120:1)
+(5, 0) -- ++(120:3)
+(6, 0) -- ++(120:3) ++(120:1) -- ++(120:1)
+(7, 0) -- ++(120:5)
+(8, 0) ++(120:2) -- ++(120:3)
+(9, 0) ++(120:2) -- ++(120:3)
+(10, 0) ++(120:4) -- ++(120:1)
+(11, 0) ++(120:4) -- ++(120:1)
+(3, 0) -- ++(0:1)
+;
+
+\foreach \y in {3, 5} {
+\draw[dashed,very thick] (0, 0)++(60:\y) -- ++(300:1);	
+}
+
+\end{tikzpicture}}
+
+\end{minipage}
+\caption{
+(Left) RNA origami. 
+(Right) an abstraction of its product, i.e., an RNA tile, as a configuration of an oritatami system.
+A dot $\bullet$ in the figure on the right represents a sequence of 3-4 nucleotides, and the solid arrow and dashed lines represent its RNA transcript and interactions (respectively) based on hydrogen bonds between nucleotides.
+}
+\label{fig:rna_origami}
+\end{figure}
+
+Transcription is the first essential step of gene expression, in which a DNA template sequence is copied into a single stranded RNA sequence by a `molecular Xerox' called RNA polymerase, letter by letter according to the complimentarity relation ${\tt A} \rightarrow {\tt U}$, ${\tt G} \rightarrow {\tt C}$, ${\tt C} \rightarrow {\tt G}$, and ${\tt T} \rightarrow {\tt A}$.
+The copied RNA sequence is called \textit{transcript}. 
+The transcript starts folding upon itself into intricate structures immediately after it emerges from the polymerase, as illustrated in Fig.~\ref{fig:rna_origami} (Left).
 
 In a recent breakthrough in molecular engineering by Geary, Rothemund and Andersen~\cite{GearyRothemundAndersen2014} the co-transcriptional folding of RNA is controlled by careful design of the DNA template.
-As demonstrated in laboratory, this method, called RNA Origami, makes it possible to build rectangles out of RNA strands.
+As demonstrated in laboratory, this method, called RNA Origami, makes it possible to cotranscriptionally self-assemble a unique RNA rectangular tile highly probably (see Fig.~\ref{fig:rna_origami} (Left)).
 Geary et al.~\cite{GeMeScSe2016} proposed a mathematical model for this process, called oritatami system. 
-It has been just shown in \cite{GeMeScSe2018} that the model is efficiently Turing universal by simulating cyclic tag systems introduced by Cook~\cite{Cook2004}. 
+In this model, an RNA structure is abstracted as a directed path with information on hydrogen-based interaction (bonds) over the triangular grid graph $\mathbb{T}$ as illustrated in Fig.~\ref{fig:rna_origami}.
+An oritatami system folds a transcript of abstract molecules (beads) of finite number of types over $\mathbb{T}$. 
+This model has been just proved efficiently Turing universal in \cite{GeMeScSe2018} by simulating cyclic tag systems introduced by Cook~\cite{Cook2004}. 
 The simulation involves a very large and complex oritatami system. 
-One future direction of research is to find smaller universal oritatami system.
-
-Closely related is the question of where not to look for universal systems, i.e., what are the limitations of simple oritatami system. 
-In search for simple oritatami systems, there are a number of restrictions one can pose on them:
-\begin{itemize}
-\item bounds on the delay, the number of bead types or the arity;
-\item bounds on the size of the primary structure or of the attraction rule set;
-\item structural conditions on the primary structure or the attraction rule set.
-\end{itemize}
-
-%Rogers and Seki~\cite{SimpleSim} showed that certain OS with small delays are not universal.
-
-%Han, Kim, Rogers and Seki\cite{SelfRemove} proved that it is possible to avoid self-attraction rules without changing the behavior of OS.
-
-In this paper we start a new line of study which concerns the alphabet size for the primary structure, i.e., the number of bead types.
+This system is deterministic in the sense that every bead is stabilized uniquely point-wise as well as interaction-wise (for the formal definition, see Sect.~\ref{sec:preliminaries}). 
+One future direction of research is to quest for a smaller Turing-universal oritatami system.
 
@@
 \node at (2, 4) {$3n(n+1)+1$};
-\node at (2, 3) {$O(n)$};
-\node at (2, 2) {$O(n^2)$};
+\node at (2, 3) {$4n+14$};
+\node at (2, 2) {$9n(3n+1)+1$};
 \node at (2, 1) {$10n$ \cite{DHOPRSST2018}};
@@
 
+Closely related is the question of where not to look for universal systems, i.e., what are the limitations of simple oritatami system. 
+In search for simple oritatami systems, there are a number of restrictions one can pose on them:
+\begin{itemize}
+\item bounds on the relative speed of transcription to folding (delay), the number of bead types, or the number of hydrogen bonds per bead (arity);
+\item bounds on the length of the transcript or on the complexity of rules to decide what types of beads interact with each other (attraction rules);
+\item structural conditions on the transcript or the attraction rules.
+\end{itemize}
+%
+In \cite{DHOPRSST2018}, Demaine et al.
+proved that at delay 1 and arity 1, upon an initial structure of $n$ beads, a deterministic oritatami system cannot fold into any conformation of more than $10n$ beads, no matter how many bead types are available.
+We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.
+
+\begin{problem}\label{prob:det_unary_length}
+Give an upper bound on the length of a transcript of a delay-$\delta$, arity-$\alpha$ deterministic unary oritatami system whose seed is of length $n$ by a function in $\delta$, $\alpha$, and $n$. 
+\end{problem}
+
+Results on this problem are summarized in Fig.~\ref{fig:summary}.
+
 %------------------------------------------------------
-	\section{Preliminaries}
+	\section{Preliminaries}\label{sec:preliminaries}
 %------------------------------------------------------
-Let $\Sigma$ be a set of types of abstract molecules, or \textit{beads}. 
+
+Let $\Sigma$ be a finite set of types of abstract molecules, or \textit{beads}. 
 A bead of type $a \in \Sigma$ is called an $a$-bead. 
@@
 \item a positive integer $\alpha$ called the \textit{arity}, 
-\item an initial $R$-valid conformation $\sigma \in C_{\le \alpha}(\Sigma)$ called the \textit{seed}, upon which 
-\item its (possibly infinite) \textit{transcript} $w \in \Sigma^* \cup \Sigma^\omega$ is to be folded by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads.
+\item an initial $R$-valid conformation $\sigma \in C_{\le \alpha}(\Sigma)$ called the \textit{seed}, whose first bead is assumed to be at the origin $O$ without loss of generality, 
+\item a (possibly infinite) \textit{transcript} $w \in \Sigma^* \cup \Sigma^\omega$, which is to be folded upon the seed by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads.
 \end{itemize}
@@
 An oritatami system with the empty rule set just folds into an arbitrary elongation of its seed nondeterministically. 
-Thus, the rule set is always assumed to be non-empty.
+Thus, the rule set is reasonably assumed non-empty.
 
 In this paper, we considerably focus on the unary oritatami system. 
-An oritatami system is \textit{unary} if its bead type set $\Sigma$ is of size 1. 
-Its sole bead type is denoted by $a$, that is, $\Sigma = \{a\}$. 
-Its only possible rule is $(a, a)$ so that the non-empty rule set assumption implies that its rule set is $R = \{(a, a)\}$. 
-Its transcript is a sequence of $a$-beads. 
-That is to say, the behavior of a unary oritatami system is fully determined by the delay, arity, and seed.
+An oritatami system is \textit{unary} if it involves only one type of bead, say $a$, that is, $\Sigma = \{a\}$. 
+Its rule set is $R = \{(a, a)\}$. 
+Its transcript is a sequence of $a$-beads so that nothing can be hardcoded on it.
 
@@
 
-%-------------------------------------------------------
-	\section{Problem description}
-%-------------------------------------------------------
-
-In \cite{DHOPRSST2018}, Demaine et al. proved that at delay 1 and arity 1, upon the seed of length $n$, a deterministic oritatami system cannot fold into any conformation strictly longer than $10n$. 
-We consider this finiteness problem for unary oritatami systems under various settings of the values of delay and arity, which is formalized as follows.
-
-\begin{problem}\label{prob:det_unary_length}
-Give an upper bound on the length of a transcript of a delay-$\delta$, arity-$\alpha$ deterministic unary oritatami system whose seed is of length $n$ by a function in $\delta$, $\alpha$, and $n$. 
-\end{problem}
-
-Results on this problem are summarized in Fig.~\ref{fig:summary}.
-
 \section{Case of arity $1$}

### 2018-12-04 tt_intro.tex
Commit before going to bed
Since I don't feel well, let me go to bed now.

@@
 We also let $S$ take the value $\blacksquare$ for halt (due to the lack of free neighbors).
-A tunnel is a set of
 
@@
 Originally, we tried to find a troll in every tunnel but failed; a troll seems to dislike the very first bead $w[1]$, or its property that only $\alpha$+1 beads around may take all hands of $w[1]$ thanks to the absence of its predecessor; any other bead must be surrounded by at least $\alpha+2$ beads in order to be free from free hand because a bead cannot bind with its predecessor or successor.
-We call the bead $w[1]$ \textit{singular}. 
-A tunnel is \textit{singular} if its entrance or exit is next to $w[1]$. 
+We call a bead \textit{singular} if it is surrounded by only $\alpha+1$ beads but forms $\alpha$ bonds. 
+Any bead but $w[1]$ can be singular because of their predecessor and successor. 
+A tunnel is \textit{singular} if its entrance or exit is next to $w[1]$ that is singular. 
 There can be at most 3 tunnels around one bead so that no more than 3 tunnels can be singular. 

### 2018-12-04 tt_theorem.tex
12/4 after lunch

@@
 \begin{theorem}[Tunnel Troll Theorem]
+\label{TTT}
 Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$. The following statements hold.
@@
 
+\begin{figure}
+  \begin{center}
+        \begin{tikzpicture}
+        \draw[->,white] (-70:0.1) -- (-70:3);
+          \foreach \theta in {60,-60,120,0}{
+            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+          }
+
+          \fill[blue](180:1) circle [radius=0.05];
+          \fill[blue](0:0) circle [radius=0.05];
+
+          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
+          \draw[->, blue] (180:0.9) -- (180:0.1);
+          \draw[->, blue] (-120:0.1) -- (-120:0.9);
+
+          \node[below left] at (180:1) {$w[i]$};
+          \node[above] at (0:0) {$w[i+1]$};
+          \node[below] at (-120:1) {$w[i+2]$};
+
+          \node[right] at (120:1) {$n_3$};
+          \node[right] at (60:1) {$n_2$};
+          \node[right] at (0:1) {$n_1$};
+
+          \begin{scope}[shift=(-120:1)]
+            \fill[blue](0,0) circle [radius=0.05];
+            \foreach \theta in {-120,-60,180}{
+              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+            }
+
+          \end{scope}
+        \end{tikzpicture}
+    \caption{Case of $S[h-1..h+1] = bbt$}
+    \label{TTT_tunnelC_enter_usingBond}
+  \end{center}
+\end{figure}
+
 \begin{lemma}
@@
 \begin{enumerate}
-\item If $S[i] = b$, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
-\item If $S[i] \in \{t_s, t_o \}$, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
-\item If $S[i] = t_a$, $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
+\item If $w[i]$ forms at least one bond, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
+\item If $w[i]$ does not consumes any bond and $S[i] \in \{t_s, t_o \}$, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
+\item If $w[i]$ does not consumes any bond and $S[i] = t_a$, $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
 \end{enumerate}
@@
 \end{lemma}
+
+\begin{proof}
+%	The bead $w[i+1]$ consumes one hand and provide nothing, that is, $\#bc(C_{i}) \geq \#bc(C_{i+1})$.
+%	The bead $w[i]$ consumes bond because $S[i] = b$.
+%	See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
+%	The bead $w[i+2]$ is stabilized at a point of neighbors of $w[i]$.
+%	If $w[i]$ consumes just one hand, $w[i]$ leaves a hand, that is, $\#bc(C_{i-1}) \geq \#bc(C_{i})$.
+%	Then, $w[i+2]$ consumes $w[i]$'s hand.
+%	Thus, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
+%	On the other hand, if $w[i]$ forms two bonds, then even if $w[i+2]$ provides two free hands, $\#bc(C_{i-1}) - \#bc(C_{i}) = \#bc(C_{i+1}) - \#bc(C_{i+2})$.
+%	Thus, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
+%	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.
+
+	We consider each statements. First we prove statement 1.
+	The bead $w[i+1]$ consumes one hand and provide nothing.
+	If $w[i]$ forms two bonds, then even if $w[i+2]$ provides two free hands, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
+	On the other hand, if it leaves a free hand, it will be used by $w[i+2]$, and hence, $w[i+2]$ does not increase the binding capability.
+	Thus, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
+	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.
+
+	Next we prove statement 2.
+	See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
+	Consider the case when $w[i]$ is stabilized by a tunnel section of type $S$ or $O$.
+	As prove in Lemma~\ref{TTT_exit}, $\#bc(C_{i-2}) \geq \#bc(C_{i})$.%the increase of binding capability by $w[i-1]$ and $w[i]$ is at most 0.
+	The bead $w[i]$ leaves two free hand, it will be used by $w[i+2]$, and hence, $w[i+2]$ does not increase the binding capability.
+	Thus, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
+	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.
+
+	Finally, we prove statement 3.
+	Consider the case when $w[i]$ is stabilized by a tunnel section of type $A$ and $w[i]$ does not consumes any bond.
+	Then, $w[i-2]$ must consume two bonds; otherwise $w[i-2]$'s hands is used by $w[i]$.
+	The bead $w[i-1]$ consumes one hand and provide nothing.
+	Thus,  $\#bc(C_{i-3}) - 1 \geq \#bc(C_{i})$.
+	Moreover, the bead $w[i+1]$ consumes one hand and provide nothing and $w[i]$'s hands is used by $w[i+2]$, and hence, $w[i+2]$ does not increase the binding capability.
+	Therefore, $\#bc(C_{i-3}) > \#bc(C_{i+2})$.
+	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.
+\end{proof}
 
@@
 %Thus, in this case, even if $w[h+1]$ supplies two free bonds, binding capability decreases by 1.
-
-\begin{figure}
-  \begin{center}
-        \begin{tikzpicture}
-        \draw[->,white] (-70:0.1) -- (-70:3);
-          \foreach \theta in {60,-60,120,0}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \fill[blue](180:1) circle [radius=0.05];
-          \fill[blue](0:0) circle [radius=0.05];
-
-          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
-          \draw[->, blue] (180:0.9) -- (180:0.1);
-          \draw[->, blue] (-120:0.1) -- (-120:0.9);
-
-          \node[below left] at (180:1) {$w[h-1]$};
-          \node[above] at (0:0) {$w[h]$};
-          \node[below] at (-120:1) {$w[h+1]$};
-
-          \node[right] at (120:1) {$n_3$};
-          \node[right] at (60:1) {$n_2$};
-          \node[right] at (0:1) {$n_1$};
-
-          \begin{scope}[shift=(-120:1)]
-            \fill[blue](0,0) circle [radius=0.05];
-            \foreach \theta in {-120,-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-          \end{scope}
-        \end{tikzpicture}
-    \caption{Case of $S[h-1..h+1] = bbt$}
-    \label{TTT_tunnelC_enter_usingBond}
-  \end{center}
-\end{figure}
 
@@
 
-\begin{figure}
-  \centering
-    \begin{tabular}{cc}
-
-      \begin{minipage}{0.48\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];
-
-          \foreach \theta in {60,-60,120,-120,180}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \fill[blue](0:1) circle [radius=0.05];
-          \draw[->, blue] (0:0.1)--(0:0.9);
-
-          \node[below] at (-60:1) {$n_4$};
-
-          \begin{scope}[shift=(0:2)]
-            \fill[blue](0,0) circle [radius=0.05];
-
-            \foreach \theta in {120,60,-60,0}{
-             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (-120:0.1)--(-120:0.9);
-
-            \node[below] at (180:1) {$w_{[h-1]}$};
-            \node[above] at (0:0) {$w_{[h]}$};
-            \node[below] at (-120:1) {$w_{[h+1]}$};
-
-            \node[above] at (120:1) {$n_3$};
-            \node[above] at (60:1) {$n_2$};
-            \node[right] at (0:1) {$n_1$};
-
-            \begin{scope}[shift=(-120:1)]
-              \fill[blue](0,0) circle [radius=0.05];
-              \foreach \theta in {-120,-60}{
-                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-              }
-
-              \node[right] at (-120:1) {$n_5$};
-              \node[right] at (-60:1) {$n_6$};
-            \end{scope}
-
-          \end{scope}
-
-          \node at (1.2,-2.5) {Pattern 1};
-        \end{tikzpicture}
-      \end{minipage}
-
-      \begin{minipage}{0.48\hsize}
-      \centering
-        \begin{tikzpicture}
-
-          \fill(0,0) circle [radius=0.1];
-
-          \foreach \theta in {60,0,120,-120,180}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \draw[->, blue] (-60:0.1)--(-60:0.9);
-
-          \begin{scope}[shift=(-60:1),shift=(0:1)]
-            \fill[blue](0,0) circle [radius=0.05];
-            \fill[blue](180:1) circle [radius=0.05];
-
-            \foreach \theta in {120,60,0,-60}{
-              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-            }
-
-            \draw[->, blue] (180:0.9)--(180:0.1);
-            \draw[->, blue] (-120:0.1)--(-120:0.9);
-
-            \node[below] at (180:1) {$w_{[h-1]}$};
-            \node[above] at (0:0) {$w_{[h]}$};
-            \node[below] at (-120:1) {$w_{[h+1]}$};
-
-            \node[above right] at (120:1) {$n_3$};
-            \node[right] at (60:1) {$n_2$};
-            \node[right] at (0:1) {$n_1$};
-
-            \begin{scope}[shift=(-120:1)]
-              \fill(0,0) circle [radius=0.05];
-              \foreach \theta in {180,-120,-60}{
-                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-              }
-
-              \node[left] at (180:1) {$n_4$};
-              \node[right] at (-120:1) {$n_5$};
-              \node[right] at (-60:1) {$n_6$};
-            \end{scope}
-
-          \end{scope}
-
-          \node at (1.25,-4) {Pattern 2};
-        \end{tikzpicture}
-      \end{minipage}
-
-    \end{tabular}
-    \caption{Case of $S[h-1..h+1] = tbt$}
-    \label{TTT_tunnelC_enter_usingTunnel}
-\end{figure}
+%\begin{figure}
+%  \centering
+%    \begin{tabular}{cc}
+%      
+%      \begin{minipage}{0.48\hsize}
+%      \centering
+%        \begin{tikzpicture}
+%
+%          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];
+%          
+%          \foreach \theta in {60,-60,120,-120,180}{
+%            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+%          }
+%
+%          \fill[blue](0:1) circle [radius=0.05];
+%          \draw[->, blue] (0:0.1)--(0:0.9);
+%
+%          \node[below] at (-60:1) {$n_4$};
+%
+%          \begin{scope}[shift=(0:2)]
+%            \fill[blue](0,0) circle [radius=0.05];
+%
+%            
+%            \foreach \theta in {120,60,-60,0}{
+%             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+%            }
+%
+%            \draw[->, blue] (180:0.9)--(180:0.1);
+%            \draw[->, blue] (-120:0.1)--(-120:0.9);
+%
+%            \node[below] at (180:1) {$w_{[h-1]}$};
+%            \node[above] at (0:0) {$w_{[h]}$};
+%            \node[below] at (-120:1) {$w_{[h+1]}$};
+%
+%            \node[above] at (120:1) {$n_3$};
+%            \node[above] at (60:1) {$n_2$};
+%            \node[right] at (0:1) {$n_1$};
+%
+%            \begin{scope}[shift=(-120:1)]
+%              \fill[blue](0,0) circle [radius=0.05];
+%              \foreach \theta in {-120,-60}{
+%                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+%              }
+%
+%              \node[right] at (-120:1) {$n_5$};
+%              \node[right] at (-60:1) {$n_6$};
+%            \end{scope}
+%            
+%          \end{scope}
+%
+%          \node at (1.2,-2.5) {Pattern 1};
+%        \end{tikzpicture}
+%      \end{minipage}
+%
+%      \begin{minipage}{0.48\hsize}
+%      \centering
+%        \begin{tikzpicture}
+%
+%          \fill(0,0) circle [radius=0.1];
+%          
+%          \foreach \theta in {60,0,120,-120,180}{
+%            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+%          }
+%
+%          \draw[->, blue] (-60:0.1)--(-60:0.9);
+%
+%
+%          \begin{scope}[shift=(-60:1),shift=(0:1)]
+%            \fill[blue](0,0) circle [radius=0.05];
+%            \fill[blue](180:1) circle [radius=0.05];
+%
+%            
+%            \foreach \theta in {120,60,0,-60}{
+%              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+%            }
+%
+%            \draw[->, blue] (180:0.9)--(180:0.1);
+%            \draw[->, blue] (-120:0.1)--(-120:0.9);
+%
+%            \node[below] at (180:1) {$w_{[h-1]}$};
+%            \node[above] at (0:0) {$w_{[h]}$};
+%            \node[below] at (-120:1) {$w_{[h+1]}$};
+%
+%            \node[above right] at (120:1) {$n_3$};
+%            \node[right] at (60:1) {$n_2$};
+%            \node[right] at (0:1) {$n_1$};
+%
+%            \begin{scope}[shift=(-120:1)]
+%              \fill(0,0) circle [radius=0.05];
+%              \foreach \theta in {180,-120,-60}{
+%                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+%              }
+%
+%              \node[left] at (180:1) {$n_4$};
+%              \node[right] at (-120:1) {$n_5$};
+%              \node[right] at (-60:1) {$n_6$};
+%            \end{scope}
+%            
+%          \end{scope}
+%
+%          \node at (1.25,-4) {Pattern 2};
+%        \end{tikzpicture}
+%      \end{minipage}
+%
+%      
+%      
+%    \end{tabular}
+%    \caption{Case of $S[h-1..h+1] = tbt$}
+%    \label{TTT_tunnelC_enter_usingTunnel}
+%\end{figure}
 
@@
 
-\proof{Proof of Tunnel Troll Theorem}
 %Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
@@
 %\end{lemma}
+
+\proof{Proof of Tunnel Troll Theorem}
 
@@
 
-Next, we consider the case of $\delta = 2, \alpha = 1$. We assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and $S[i+2] \in \{ t_s, t_o \} $.
-Then, all $S[i+1..j]$ do not contain $t_o$; otherwise $S[i+1..j]$ contain $\blacksquare$.
-Therefore according to Lemma~\ref{TTT_entrance_Tab}, $\#bc(C_{i-1}) > \#bc(C_{i})$ and moreover that, according to Lemma~\ref{TTT_exit}, $\#bc(C_{i}) \geq \#bc(C_{j})$.
+Next, we consider the case of $\delta = 2, \alpha = 1$. We assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and all $S[i+2..j]$ are  $ t_s$ or  $t_o$.
+According to Lemma~\ref{TTT_entrance_Tab}, $\#bc(C_{i-1}) > \#bc(C_{i})$ and moreover that, according to Lemma~\ref{TTT_exit}, $\#bc(C_{i}) \geq \#bc(C_{j})$.
+Thus, binding capability of the conformation decrease per a subsequence $bt_s$ or $bt_o$.
 
-On the other hand, we assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and $S[i+2] = t_a$.
+On the other hand, we assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and there is a element of $S[i+2..j]$ such that it is $t_a$.
+All $S[i+3..j]$ do not contain $t_o$; otherwise $S[i+4..j+1]$ contain $\blacksquare$.
+Therefore, $S[i+2] = t_a$.
+According to Lemma~\ref{TTT_exit}, on statement 1, 2, $\#bc(C_{i-2}) > \#bc(C_{i+2})$ and if $i \leq j - 3$, $\#bc(C_{i+2}) \geq \#bc(C_{j})$.
+Thus, binding capability of the conformation decrease per a subsequence $bt_a$ unless $w[i]$ does not consumes any bond.
+If $w[i]$ does not consumes any bond and $S[i] = t_a$, that is, $S[i-1..i+2] = bt_abt_a$, then $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
+In this case, two subsequences of $bt_a$ collaborate decreasing binding capability but eventually, two subsequences decrease two bond.
+That is, one subsequence decrease binding capability.
 
-Let us consider that $w[i]$ supplies two bonds (that is, $S[i] = t$).
-If $S[i] \in \{ t_s, t_o \}$, $\#bc(C_{i-2}) \geq \#bc(C_{i})$ because of Lemma~\ref{TTT_exit}.
-Therefore,
-
-if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of Lemma~\ref{TTT_exit}.
-Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.
-
+Hence, if $S[i..j]$ contain n's subsequences of $bt$, $\#bc(C_{i-2}) - \#bc(C_{j}) \geq n$
 \qed
@@
 
-\begin{figure}[tb]
- \centering
-    \begin{tikzpicture}
-	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (0:1) {$n_0$};
-
-	\foreach \theta in {0,60,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-    \end{tikzpicture}
-    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
-    \label{TTT_a4_lemma_fig}
-\end{figure}
+%\begin{figure}[tb]
+% \centering
+%    \begin{tikzpicture}
+%	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
+%      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+%      
+%      \draw[->] (180:0.9) -- (180:0.1);
+%
+%	\node[above] at (180:1) {$w_{[i-2]}$};
+%	\node[below] at (180:0) {$w_{[i-1]}$};
+%	\node[above] at (0:1) {$n_0$};
+%
+%	\foreach \theta in {0,60,-60,120,-120}{
+%   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
+%  	}
+% 	\node[above] at (60:1) {$n_1$};
+%	\node[below] at (-60:1) {$n_2$};
+%	\node[above] at (120:1) {$n_3$};
+%	\node[below] at (-120:1) {$n_4$};
+%    \end{tikzpicture}
+%    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
+%    \label{TTT_a4_lemma_fig}
+%\end{figure}
 
@@
 Consider the moment when a bead $b$ is stabilized outside $\hexagon_O^n$ for the first time. 
-See Fig.~\ref{TTT_a4_first}
+See Fig.~\ref{TTT_a4_first}.
 There is only one bead available to stabilize $b$ there, which is $b_1$. 
@@
 \begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $O(n)$.
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $2n + 14$.
 \end{theorem}
@@
 
+\begin{figure}
+  \begin{center}
+  \begin{tabular}{c c}
+  \begin{minipage}{0.48\hsize}
+  \centering
+    \begin{tikzpicture}
+      	\fill (0,0) circle [radius=0.1];
+        \fill[blue] (60:1) circle [radius=0.05];
+         \fill[blue] (120:1) circle [radius=0.05];
+        \fill (0:1) circle [radius=0.1];
+
+      \draw[dashed] (180:2) -- (0:2);
+      \draw[dashed, shift=(60:1)] (180:2.5) -- (0:1.5);
+       \draw[dashed, shift=(60:2)] (180:3) -- (0:1);
+      \draw[->, blue] (60:0.1) -- (60:0.9);
+      \draw[->, blue, shift=(60:1)] (180:0.1) -- (180:0.9);
+
+	\node[above] at (180:1) {$p_1$};
+	\node[above] at (60:2) {$p_2$};
+	\node[above,shift=(120:1)]at (60:1) {$p_3$};
+	\node[above]at (0:1) {$p_4$};
+
+	\draw (180:1) circle [radius=0.05];
+	\draw (60:2) circle [radius=0.05];
+	\draw[shift=(120:1)] (60:1) circle [radius=0.05];
+
+	\node at (0:2.5) {$n$};
+	\node[shift=(60:1)] at (0:2) {$n+1$};
+	\node[shift=(60:2)] at (0:1.5) {$n+2$};
+
+	\node[below] at (0:0) {$w[i-1]$};
+	\node[above] at (60:1) {$w[i]$};
+	\node[above] at (120:1) {$w[i+1]$};
+	\end{tikzpicture}
+    \end{minipage}
+
+    \begin{minipage}{0.48\hsize}
+    \begin{tikzpicture}
+      	\fill (0,0) circle [radius=0.1];
+        \fill[blue] (60:1) circle [radius=0.05];
+         \fill[blue,shift=(0:1)] (60:1) circle [radius=0.05];
+        \fill (0:1) circle [radius=0.1];
+
+      \draw[dashed] (180:2) -- (0:2);
+      \draw[dashed, shift=(60:1)] (180:2.5) -- (0:1.5);
+       \draw[dashed, shift=(60:2)] (180:3) -- (0:1);
+      \draw[->, blue] (60:0.1) -- (60:0.9);
+      \draw[->, blue, shift=(60:1)] (0:0.1) -- (0:0.9);
+
+	\node[above] at (180:1) {$p_1$};
+	\node[above] at (60:2) {$p_2$};
+	\node[above, shift=(120:1)]at (60:1) {$p_3$};
+	\node[above]at (0:1) {$p_4$};
+
+	\draw (180:1) circle [radius=0.05];
+	\draw (60:2) circle [radius=0.05];
+	\draw[shift=(120:1)] (60:1) circle [radius=0.05];
+
+	\node at (0:2.5) {$n$};
+	\node[shift=(60:1)] at (0:2) {$n+1$};
+	\node[shift=(60:2)] at (0:1.5) {$n+2$};
+
+	\node[below] at (0:0) {$w[i-1]$};
+	\node[above] at (60:1) {$w[i]$};
+	\node[above, shift=(0:1)] at (60:1) {$w[i+1]$};
+	\end{tikzpicture}
+    \end{minipage}
+    \end{tabular}
+    \caption{The bead $w[i]$  the first bead outside $\hexagon^n_0$: $w[i+1]$ elongated to west (left), $w[i+1]$ elongated to east (right)}
+    \label{fig:ttt_d2}
+  \end{center}
+\end{figure}
+
 \begin{theorem}[$\delta= 1, \alpha=2$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation.
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation in $w[27n^2 + 9n + 1]$.
 \end{theorem}
@@
 \begin{proof}
-By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
+ We assume $w[i]$ is the first bead outside $\hexagon^n_0$
+ See Fig.~\ref{fig:ttt_d2}.
+ If $w[i+1]$ elongated to west and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_3$; otherwise $w[i+2]$ forms two bonds.
+ If $w[i+1]$ elongated to west and $w[i+2]$ is stabilized at $p_3$, $w[i+1..]$ form a zig-zag conformation.
+  If $w[i+1]$ elongated to east and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_2$; otherwise $w[i+2]$ forms two bonds.
+ If $w[i+1]$ elongated to east and $w[i+2]$ is stabilized at $p_2$, $w[i+1..]$ is zig-zag conformation.
+ Thus, if $w[i]$ is the first bead outside $\hexagon^k_0$ for some $k \geq n$, $\#bc(C_i) > \#bc(C_{i+1})$ or $w[i+1..]$ form a zig-zag conformation.
+
+ We assume $w[l]$ is the first bead outside $\hexagon^k_0$ and $w[m]$ is the first bead outside $\hexagon^{k+1}_0$ for some $k,l,m$ with $k<3n$.
+Let $s$ be a element of $S[l+1..m-1]$.
+If $s = b$, $s$ does not increase binding capability.
+ If $s=t$, $s$ is a element of a subsequence $bt^+b$.
+This subsequence does not increase binding capability according to Theorem~\ref{TTT}.
+Thus, $\#bc(C_l) > \#bc(C_{m})$ or $w[l..]$ form a zig-zag conformation.
+
+ The seed $\sigma$ provides at most $2n$ binding capability, that is, $\#bc(C_0) \leq 2n$.
+ Thus,  if  $w[i]$ is the first bead outside $\hexagon^{3n}_0$, then this conformation has no hand without $w[i-1]$ and $w[i]$.
+ Hence, $w[27n^2 + 9n + 1..]$ form a zig-zag conformation.
+\end{proof}
+
+%By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
 If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$.
@@
 Therefore formula \ref{TTT_only_bond} hold.
-
-\begin{eqnarray}
-  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
-  \label{TTT_only_bond}
-\end{eqnarray}
-
-Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
-
-Let us consider the case of $v_k$ is $o$.
+%
+%\begin{eqnarray}
+%  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
+%  \label{TTT_only_bond}
+%\end{eqnarray}
+%
+%
+%Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
+%
+%
+%Let us consider the case of $v_k$ is $o$.
 See Fig.\ref{TTT_case_of_o}.
@@
 
-\end{proof}
-
-\begin{eqnarray}
-  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
-  \label{TTT_only_a}
-\end{eqnarray}
-
-\begin{eqnarray}
-  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
-  \label{TTT_structure}
-\end{eqnarray}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-
-      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
-
-      \fill[blue](0:0) circle [radius=0.05];
-      \fill[blue](0:1) circle [radius=0.05];
-      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
-
-      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
-      \draw[->, blue] (0:0.1) -- (0:0.9);
-      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
-
-      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-
-      \node[below] at (-120:1) {$w[i-2]$};
-      \node[above] at (0:0) {$w[i-1]$};
-      \node[below] at (0:1) {$w[i]$};
-      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
-
-      \node[above] at (60:1) {$n_1$};
-      \node[below] at (-60:1) {$n_2$};
-
-    \end{tikzpicture}
-    \caption{Case of $S[i]$}
-    \label{TTT_case_of_o}
-  \end{center}
-\end{figure}
+%
+%
+%\begin{eqnarray}
+%  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
+%  \label{TTT_only_a}
+%\end{eqnarray}
+%
+%\begin{eqnarray}
+%  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
+%  \label{TTT_structure}
+%\end{eqnarray}
+%
+%\begin{figure}
+%  \begin{center}
+%    \begin{tikzpicture}
+%      
+%      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
+%      
+%      \fill[blue](0:0) circle [radius=0.05];
+%      \fill[blue](0:1) circle [radius=0.05];
+%      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
+%
+%      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
+%      \draw[->, blue] (0:0.1) -- (0:0.9);
+%      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
+%      
+%      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
+%      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
+%      
+%      \node[below] at (-120:1) {$w[i-2]$};
+%      \node[above] at (0:0) {$w[i-1]$};
+%      \node[below] at (0:1) {$w[i]$};
+%      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
+%
+%      \node[above] at (60:1) {$n_1$};
+%      \node[below] at (-60:1) {$n_2$};
+%        
+%    \end{tikzpicture}
+%    \caption{Case of $S[i]$}
+%    \label{TTT_case_of_o}
+%  \end{center}
+%\end{figure}
+%

### 2018-12-05 tt_theorem.tex
12/5 morning

@@
 \begin{proof}
-We consider cases which $w[i-1]$ is two distances away from the singular point.
-Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is, when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
-Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$.
-Suppose $w[i]$ were able to be stabilized with using one hand in each cases.
-
-% Then, $w[i]$ can be also stabilized at $n_3$.
-
-\begin{paragraph}{Case of straight}
-\begin{itemize}
-\item[-] Case of $n_3$ is free\\
-The bead $w[i-2]$ must not have bonds because $w[i]$ is stabilized deterministically so that five neighbors of $w[i-2]$ must be occupied.
-Therefore $n_5$ must be occupied.
-We can continue this argument in clockwise manner to fill the neighbors of $n_3$ until $n_1$.
-However, two neighbors of $n_1$ must be free because they are $n_3$ and the point of $w[i]$, contradict.
-
-\item[-] Otherwise\\
-Both $n_3$ and $n_4$ are occupied.
-One of $n_1$ and $n_2$ must be free because $S[i] = b$.
-We assume $n_1$ is free, then all neighbors of $n_1$ must be occupied because $n_3$ is occupied.
-However, one of neighbors $n_1$ is a point which $w[i]$ is stabilized, contradict.
-\end{itemize}
-
-Therefore, this case contradict assumption.
-\end{paragraph}
-
-\begin{paragraph}{Case of obtuse}
-\begin{itemize}
-\item[-] Case of $n_3$ is free\\
-Any neighbors of $n_3$ have to be occupied but the point which $w[i]$ is stabilized is free. Thus $n_3$ has to be occupied.
-\item[-] Case of $n_4$ is free\\
-The point $n_2$ must be occupied because $n_4$ is free and $n_5$ must be occupied.
-Therefore $n_0$ is occupied.
-The bead $w[i]$ forms just one bond so that one of $n_0, n_3$ leave some hands or both of them do not leave any bonds.\\
-If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied. 
-We can continue this argument in clockwise manner to fill the neighbors of $w[i]$.
-That is, $S[i] = \blacksquare$, contradict.
-
-If $n_3$ has some hands, then $n_0$ does not have any hands so that neighbors of $w[i]$ are occupied. In the same previous way, contradict.\\
-If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied.
+In this proof, we shall verify the claim that when the bead $w[i]$ is stabilized with $S[i] = b$ and $S[i+1] \neq \blacksquare$, if the circle of radius 2 centered at its predecessor $w[i-1]$ is free from the singular point, then $w[i]$ must form at least 2 bonds.
+Recall that the circle of radius 2 centered at the origin $O$, where the only candidate of singularity is, consists of 19 points including $O$. 
+In order for the bead at $O$ to be singular, its $\alpha+1 = 4$ neighbors must be occupied. 
+This means that there are at most 14 points where a bead find a singular bead within 2 points. 
+Therefore, the claim, once proved, and the Tunnel Troll Theorem imply that all but at most 14 beads strictly decrease the binding capability. 
+The binding capability of the seed is at most $3n$. 
+Consequently, this theorem holds.
+
+Now let us verify the claim. 
+Suppose $w[i]$ were stabilized by just one bond. 
+There are three cases to be considered as depicted in Fig.~\ref{TTT_a3_w}, depending on the relative position of $w[i]$ to $w[i-2]$ and $w[i-1]$. 
+Since $S[i] = b$, at least one of the four neighbors of $w[i-1]$ must be empty. 
+If $w_3$ is free, then $w[i-2]$ must have used up all of its hands; otherwise, $w[i]$ would be stabilized also at $n_3$ nondeterministically, a contradiction. 
+Thus, $\alpha + 2 = 5$ neighbors of $w[i-2]$, that is, all of its neighbors, must be occupied. 
+Hence, $n_5$ is occupied. 
+(All the remaining arguments are based on this ``merry-go-round'' occupation. This works only if the circle of radius 2 around $w[i-1]$ is free from the singular bead). 
+In the same way, all the neighbors of $n_3$ turned out to be occupied in the clockwise order, but eventually, we would encounter a neighbor that is adjacent to also the point where $w[i]$ is supposed to go.
+Thus, $n_3$ must be occupied (in the left and middle cases). 
+In the left case, $n_4$ is symmetric to $n_3$, and hence, it must be occupied, too. 
+Since $S[i] = b$, $n_1$ or $n_2$ must be free; assume $n_1$ is. 
+Going clockwise around $n_1$ implies that $n_{-1}$ is occupied, but the bead at $n_1$ has a free hand and would cause a nondeterminism.
+
+Let us focus on the remaining cases: middle and right. 
+Suppose that among the 5 neighbors of $w[i]$ at which $w[i-1]$ is not, only one can be occupied. 
+Otherwise, a bead without any hand is found at one of them, and staring from the point, merry-go-round occupies all the neighbors, but then $w[i+1]$ would lose its way to go. 
+In the middle case, this means $n_0$ is free. 
+Since $n_{-1}$ is free, so must be $n_2$. 
+Repeating this, we get that both $n_4$ and $n_5$ are free, but then $w[i-2]$ would have a free hand and a free neighbor, attract $w[i]$, and cause a nondeterminism. 
+Even in the right case, the points $n_1, n_0, n_2, n_4$ turn out to be free one after another likewise, but then $w[i-2]$ would have a free hand and neighbor, a contradiction. 
+\qed
+
+\end{proof}
+
+%We consider cases which $w[i-1]$ is two distances away from the singular point.
+%Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is, when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
+%Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$.
+%Suppose $w[i]$ were able to be stabilized with using one hand in each cases.
+%
+%% Then, $w[i]$ can be also stabilized at $n_3$. 
+%
+%\begin{paragraph}{Case of straight}
+%\begin{itemize}
+%\item[-] Case of $n_3$ is free\\
+%The bead $w[i-2]$ must not have bonds because $w[i]$ is stabilized deterministically so that five neighbors of $w[i-2]$ must be occupied.
+%Therefore $n_5$ must be occupied.
+%We can continue this argument in clockwise manner to fill the neighbors of $n_3$ until $n_1$.
+%However, two neighbors of $n_1$ must be free because they are $n_3$ and the point of $w[i]$, contradict.
+%
+%\item[-] Otherwise\\
+%Both $n_3$ and $n_4$ are occupied.
+%One of $n_1$ and $n_2$ must be free because $S[i] = b$.
+%We assume $n_1$ is free, then all neighbors of $n_1$ must be occupied because $n_3$ is occupied.
+%However, one of neighbors $n_1$ is a point which $w[i]$ is stabilized, contradict.
+%\end{itemize}
+%
+%Therefore, this case contradict assumption.
+%\end{paragraph}
+%
+%\begin{paragraph}{Case of obtuse}
+%\begin{itemize}
+%\item[-] Case of $n_3$ is free\\
+%Any neighbors of $n_3$ have to be occupied but the point which $w[i]$ is stabilized is free. Thus $n_3$ has to be occupied.
+%\item[-] Case of $n_4$ is free\\
+%The point $n_2$ must be occupied because $n_4$ is free and $n_5$ must be occupied.
+%Therefore $n_0$ is occupied.
+%The bead $w[i]$ forms just one bond so that one of $n_0, n_3$ leave some hands or both of them do not leave any bonds.\\
+%If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied. 
+%We can continue this argument in clockwise manner to fill the neighbors of $w[i]$.
+%That is, $S[i] = \blacksquare$, contradict.
+%
+%If $n_3$ has some hands, then $n_0$ does not have any hands so that neighbors of $w[i]$ are occupied. In the same previous way, contradict.\\
+%If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied.
 If one of $n_{-1}, n_{-3}$ has some hands, the other does not have any hands so that $n_{-2}$ is occupied.
 If both of $n_{-1}, n_{-3}$ do not have any hands, $n_{-2}$ has to be occupied and $n_{-2}$ has some hands, contradict.
-\item[-] Case of $n_2$ is free\\
-Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied.
+%\item[-] Case of $n_2$ is free\\
+%Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied.
 Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free.
 Thus $n_2$ has to be occupied.
-\item[-] Case of $n_0$ is free\\
-Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied.
+%\item[-] Case of $n_0$ is free\\
+%Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied.
 Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
 Thus $n_0$ has to be occupied.
-\end{itemize}
-\end{paragraph}
-
-\begin{paragraph}{Case of acute}
-\begin{itemize}
-\item[-] Case of $n_4$ is free\\
-The point $n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some bonds.
-However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
-\item[-] Case of $n_2$ is free\\
-The point $n_0$ has to be occupied. The point $n_1$ has to be also occupied because five neighbors of $n_0$ must be occupied.
-We consider this case just like case of obtuse and that $n_4$ is free.
+%\end{itemize}
+%\end{paragraph}
+%
+%
+%
+%\begin{paragraph}{Case of acute}
+%\begin{itemize}
+%\item[-] Case of $n_4$ is free\\
+%The point $n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some bonds.
+%However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
+%\item[-] Case of $n_2$ is free\\
+%The point $n_0$ has to be occupied. The point $n_1$ has to be also occupied because five neighbors of $n_0$ must be occupied.
+%We consider this case just like case of obtuse and that $n_4$ is free.
 Then if $w[i-2]$ binds $w[i]$, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
@@
 Therefore, $w[i+1]$ cannot be provided.
-\item[-] Case of $n_0$ is free\\
-Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied.
+%\item[-] Case of $n_0$ is free\\
+%Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied.
 Any neighbors of $n_{1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
 Thus $n_0$ has to be occupied.
-\item[-] Case of $n_1$ is free\\
-Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied.
+%\item[-] Case of $n_1$ is free\\
+%Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied.
 Any neighbors of $n_{-1}$ except $n_1$ have to be also occupied but the point which is stabilized $w[i]$ is free.
 Thus $n_1$ has to be occupied.
-\end{itemize}
-
-Therefore, any situations contradict $S[i] = b$.
-\end{paragraph}\\
-
-Hence, $w[i]$ uses at least two bonds if $w[i-1]$ is at least two distances away the singular point.
-The size of $ \hexagon^2_0 = 19$ and this number contain the singular point, its successor and its three neighbors which is it binds to.
+%\end{itemize}
+%
+%Therefore, any situations contradict $S[i] = b$.
+%\end{paragraph}\\
+%
+%
+%Hence, $w[i]$ uses at least two bonds if $w[i-1]$ is at least two distances away the singular point.
+%The size of $ \hexagon^2_0 = 19$ and this number contain the singular point, its successor and its three neighbors which is it binds to.
 Therefore 14 times  $w[i]$ can be stabilized by forming one bond.
-Therefore, a deterministic unary oritatami system at $\delta = 1$ and $\alpha = 3$ can yield only finite conformation of length is $2n + 14$.
-\end{proof}
+%Therefore, a deterministic unary oritatami system at $\delta = 1$ and $\alpha = 3$ can yield only finite conformation of length is $2n + 14$.
 

### 2018-12-05 tt_theorem.tex
12/5 morning

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{lemma}
+\label{TTT_entrance_Tab}
+Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$, arity $\alpha =2$. 
+Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $S[i+1] = b$ and $S[i+2] \in \{ t_s, t_o \} $, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
+\end{lemma}
+
+\begin{proof}%[lemma \ref{TTT_entrance_Tab}]
+See Fig.\ref{TTT_tunnel_direction}.
+$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section of type $S$ or $O$.
+Thus,  its predecessor $w[i+1]$ must be inside the tunnel section, that is, $n_1$ and $n_2$ must be occupied.
+Free bonds of $w[i]$, if any, cannot be used in future by another bead $w[j]$ because otherwise the part of transcript $w[i..j]$ and the bond between $w[i]$ and $w[j]$ would form a closed curve and the curve would cross the path of $C_{i-1}$ between $n_1$ and $n_2$, contradiction.
+%Binding capabilities that $w[i]$ supplies are inactive according to Jordan curve theorem on $n_1$, $n_2$, and $w[i]$.
+Therefore, if $w[i]$ forms a bond at its stabilization $\#bc(C_{i-1}) > \#bc(C_{i})$ holds.
+We now prove that $w[i]$ must form a bond.
+
+Suppose $w[i]$ were stabilized without any bond, that is, by a tunnel.
+For that the two points that are a neighbor of both $w[i-1]$ and $w[i]$ must be occupied already.
+In addition, at least one of the neighbors of $w[i]$ must be free because $S[i+1] = b$.
+Thus, only the case to be considered is Fig.~\ref{TTT_tunnel_direction} (middle) with $n_5$ being occupied (that is, $n_4$ is free).
+In this case, before $w[i]$ is stabilized, at lest three neighbors of $n_2$ were free and hence, a bead at $n_2$ was provided with one free bond and could form a bond with $w[i]$. \qed
+
+\end{proof}
 
@@
             \foreach \theta in {120,-120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
             }
@@
             \foreach \theta in {180,-120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
             }
@@
             \foreach \theta in {180,-120,120}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
             }
 
-            \draw[->, blue] (60:1.1)--(60:0.1);
+            \draw[->, blue] (60:0.9)--(60:0.1);
             \draw[->, blue] (0:0.1)--(0:1.1);
@@
     \end{tabular}
-    \caption{Direction into a entrance}
+    \caption{Direction into an entrance of a tunnel: (Left) straight, (Middle) obtuse, (Right) acute. The bead $w[i]$ is stabilized at an entrance and $w[i+1]$ is stabilized inside a tunnel.}
     \label{TTT_tunnel_direction}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{lemma}
-\label{TTT_entrance_Tab}
-Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$, arity $\alpha =2$. 
-Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $S[i+1] = b$ and $S[i+2] \in \{ t_s, t_o \} $, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
+\label{TTT_exit}
+Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$ and arity $\alpha =2$.
+%Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
+If $S[i+1..j+1] = bt^{(j-i-1)}b$ for some $i,j$ with $i \leq j-2$ and $S[j] \in \{ t_s, t_o\}$, then $\#bc(C_{j-2}) \geq \#bc(C_j)$, and hence, $\#bc(C_{i}) \geq \#bc(C_j)$.
+If $i \leq j-3$, then the second inequality is strengthened as $\#bc(C_{i}) > \#bc(C_{j})$.
+%if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
 \end{lemma}
 
-\begin{proof}%[lemma \ref{TTT_entrance_Tab}]
-See Fig.\ref{TTT_tunnel_direction}.
-$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section of type $S$ or $O$.
-Thus,  its predecessor $w[i+1]$ must be inside the tunnel section, that is, $n_1$ and $n_2$ must be occupied.
-Free bonds of $w[i]$, if any, cannot be used in future by another bead $w[j]$ because otherwise the part of transcript $w[i..j]$ and the bond between $w[i]$ and $w[j]$ would form a closed curve and the curve would cross the path of $C_{i-1}$ between $n_1$ and $n_2$, contradiction.
-%Binding capabilities that $w[i]$ supplies are inactive according to Jordan curve theorem on $n_1$, $n_2$, and $w[i]$.
-Therefore, if $w[i]$ forms a bond at its stabilization $\#bc(C_{i-1}) > \#bc(C_{i})$ holds.
-We now prove that $w[i]$ must form a bond.
+\begin{proof}%[Lemma~ \ref{TTT_exit}]
+Since the binding capability never increases inside a tunnel, we just need to consider the exit of a tunnel.
+See Fig.\ref{TTT_tunnel_exit}. 
+At least one of points $n_1$ or $n_2$ must be free because otherwise $w[j]$ would be inside of a tunnel, that is, $S[j+1]$ would not be $b$.
 
-Suppose $w[i]$ were stabilized without any bond, that is, by a tunnel.
-For that the two points that are a neighbor of both $w[i-1]$ and $w[i]$ must be occupied already.
-In addition, at least one of the neighbors of $w[i]$ must be free because $S[i+1] = b$.
-Thus, only the case to be considered is Fig.~\ref{TTT_tunnel_direction} (middle) with $n_5$ being occupied (that is, $n_4$ is free).
-In this case, before $w[i]$ is stabilized, at lest three neighbors of $n_2$ were free and hence, a bead at $n_2$ was provided with one free bond and could form a bond with $w[i]$. \qed
+Let $m$ be the number of bonds $w[j-1]$ forms, that is, $\#bc(C_{j-2}) - \#bc(C_{j-1}) = m$.
+We claim $\#bc(C_{j}) - \#bc(C_{j-1}) \leq m$.
+Indeed, if both $n_1$ and $n_2$ are free (see Fig.~\ref{TTT_tunnel_exit}), the predecessor $w[j-1]$ must be bound to both beads at $n_3$ and at $n_4$ because both of them still have a free hand.
+Hence, $m \geq 2$.
+Since $\#bc(C_{j}) - \#bc(C_{j-1})$ is less than the arity, this difference is at most $m$.
+
+If $n_1$ is occupied, then $n_2$ is free.
+The predecessor $w[j-1]$ must be bound $n_4$.
+Hence,  $m \geq 1$.
+The bead $w[j]$ can increase the binding capability at most by 1 because one of its free neighbors would, $n_0$ or $n_2$, is to be occupied by the successor $w[j+1]$.
+Therefore, $\#bc(C_{j}) - \#bc(C_{j-1}) \leq m$.
+
+Thus,$\#bc(C_{j-2}) \geq \#bc(C_j)$ , and hence, $\#bc(C_{i}) \geq \#bc(C_j)$.
+If $i \leq j-3$, then the second inequality is strengthened as $\#bc(C_{i}) > \#bc(C_{j})$ because $S[i+1] = b$, that is, $\#bc(C_{i}) > \#bc(C_{i+1})$ and $\#bc(C_{i+1}) \geq \#bc(C_j)$. \qed
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}[tb]
@@
             \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];            }
             \draw (-60:1) circle [radius=0.05];
@@
 
-          \node at (0,-2) {Point $n_1$ and $n_2$ are free};
         \end{tikzpicture}
@@
         \begin{tikzpicture}
+
+	\draw[white] (0:0) -- (120:1);
+	\draw[white] (0:0) -- (-60:1);
 	\draw[white] (0:0) -- (0:1);
-	\draw[white] (0:0) -- (120:1);
-	\draw[white] (0:0) -- (-90:2);
 
@@
             \foreach \theta in {0}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
             }
@@
 
-          \node at (0,-2) {Point $n_1$ is occupied};
         \end{tikzpicture}
@@
     \end{tabular}
-    \caption{Exit of Tunnel}
+    \caption{Two kinds of exit of a tunnel: (Left) Both $n_1$ and $ n_2$ are free, (Right) One of $n_1$ and $n_2$ is occupied.}
     \label{TTT_tunnel_exit}
@@
 
-\begin{lemma}
-\label{TTT_exit}
-Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$ and arity $\alpha =2$.
-%Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
-If $S[i+1..j+1] = bt^{(j-i-1)}b$ for some $i,j$ with $i \leq j-2$ and $S[j] \in \{ t_s, t_o\}$, then $\#bc(C_{j-2}) \geq \#bc(C_j)$, and hence, $\#bc(C_{i}) \geq \#bc(C_j)$.
-If $i \leq j-3$, then the second inequality is strengthened as $\#bc(C_{i}) > \#bc(C_{j})$.
-%if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
-\end{lemma}
-
-\begin{proof}%[Lemma~ \ref{TTT_exit}]
-Since the binding capability never increases inside a tunnel, we just need to consider the exit of a tunnel.
-See Fig.\ref{TTT_tunnel_exit}. 
-At least one of points $n_1$ or $n_2$ must be free because otherwise $w[j]$ would be inside of a tunnel, that is, $S[j+1]$ would not be $b$.
-
-%If $i - h > 1$ and $j$ is such that $h \leq j<i$, then $\#bc(C_{j-1}) \geq \#bc(C_{j})$ because all neighbors of $w[j]$ are occupied by beads forming the tunnel so that any $w[i+1..]$ cannot reach neighbors of $w[j]$.
-%Thus, inside this tunnel, binding capabilities never increased.
-
-Let $m$ be the number of bonds $w[j-1]$ forms, that is, $\#bc(C_{j-2}) - \#bc(C_{j-1}) = m$.
-We claim $\#bc(C_{j}) - \#bc(C_{j-1}) \leq m$.
-Indeed, if both $n_1$ and $n_2$ are free (see Fig.~\ref{TTT_tunnel_exit}), the predecessor $w[j-1]$ must be bound to both beads at $n_3$ and at $n_4$ because both of them still have a free hand.
-Hence, $m \geq 2$.
-Since $\#bc(C_{j}) - \#bc(C_{j-1})$ is less than the arity, this difference is at most $m$.
-
-If $n_1$ is occupied, then $n_2$ is free.
-The predecessor $w[j-1]$ must be bound $n_4$.
-Hence,  $m \geq 1$.
-The bead $w[j]$ can increase the binding capability at most by 1 because one of its free neighbors would, $n_0$ or $n_2$, is to be occupied by the successor $w[j+1]$.
-Therefore, $\#bc(C_{j}) - \#bc(C_{j-1}) \leq m$.
-
-Thus,$\#bc(C_{j-2}) \geq \#bc(C_j)$ , and hence, $\#bc(C_{i}) \geq \#bc(C_j)$.
-If $i \leq j-3$, then the second inequality is strengthened as $\#bc(C_{i}) > \#bc(C_{j})$ because $S[i+1] = b$, that is, $\#bc(C_{i}) > \#bc(C_{i+1})$ and $\#bc(C_{i+1}) \geq \#bc(C_j)$. \qed
-
-\end{proof}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{figure}
-  \begin{center}
-        \begin{tikzpicture}
-        \draw[->,white] (-70:0.1) -- (-70:3);
-          \foreach \theta in {60,-60,120,0}{
-            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-          }
-
-          \fill[blue](180:1) circle [radius=0.05];
-          \fill[blue](0:0) circle [radius=0.05];
-
-          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
-          \draw[->, blue] (180:0.9) -- (180:0.1);
-          \draw[->, blue] (-120:0.1) -- (-120:0.9);
-
-          \node[below left] at (180:1) {$w[i]$};
-          \node[above] at (0:0) {$w[i+1]$};
-          \node[below] at (-120:1) {$w[i+2]$};
-
-          \node[right] at (120:1) {$n_3$};
-          \node[right] at (60:1) {$n_2$};
-          \node[right] at (0:1) {$n_1$};
-
-          \begin{scope}[shift=(-120:1)]
-            \fill[blue](0,0) circle [radius=0.05];
-            \foreach \theta in {-120,-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-            }
-
-          \end{scope}
-        \end{tikzpicture}
-    \caption{Case of $S[h-1..h+1] = bbt$}
-    \label{TTT_tunnelC_enter_usingBond}
-  \end{center}
-\end{figure}
 
@@
 \begin{proof}
-%	The bead $w[i+1]$ consumes one hand and provide nothing, that is, $\#bc(C_{i}) \geq \#bc(C_{i+1})$.
-%	The bead $w[i]$ consumes bond because $S[i] = b$.
-%	See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
-%	The bead $w[i+2]$ is stabilized at a point of neighbors of $w[i]$.
-%	If $w[i]$ consumes just one hand, $w[i]$ leaves a hand, that is, $\#bc(C_{i-1}) \geq \#bc(C_{i})$.
-%	Then, $w[i+2]$ consumes $w[i]$'s hand.
-%	Thus, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
-%	On the other hand, if $w[i]$ forms two bonds, then even if $w[i+2]$ provides two free hands, $\#bc(C_{i-1}) - \#bc(C_{i}) = \#bc(C_{i+1}) - \#bc(C_{i+2})$.
-%	Thus, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
-%	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.
 
@@
 
-%\begin{lemma}
-%\label{TTT_tunnelC_lemma}
-%Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
-We assume $S[h..i+1] = bt^{(i-h)}b \quad (1<h<i)$.
-If at least one of $w[h+1..i]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_i)$.
-%\end{lemma}
+\begin{figure}[tb]
+  \begin{center}
+        \begin{tikzpicture}
+        \draw[->,white] (-70:0.1) -- (-70:3);
+          \foreach \theta in {60,-60,120,0}{
+            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+          }
 
-%\begin{proof}[Lemma~ \ref{TTT_tunnelC_lemma}]
-%Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
-%Assume $S[h..i+1] = bt^{i-h}b (h<i)$.
-If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$, with $h+2 \leq g \leq i$ is stabilized by tunnel $C$, $C_g$ is a terminal.
-%
-%
-%Let us consider stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ as follows.
-In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
-In addition according to Lemma~\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$.
-Thus, $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_{i})$.
-%\\
-%
-%\subsubsection{Case of $S[h-1..h+1] = bbt$}
-%See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
-%If $w[h-1]$ forms one bond, then it leaves one free bond, but it is consumed by $w[h+1]$.
-%In addition, $w[h]$ has to bound.
-%Thus, in this cases, binding capability decreases by 1.
-%If $w[h-1]$ forms two bonds, then it does not leave any bond.
-%In addition, $w[h]$ has to be bound.
-%Thus, in this case, even if $w[h+1]$ supplies two free bonds, binding capability decreases by 1.
+          \fill[blue](180:1) circle [radius=0.05];
+          \fill[blue](0:0) circle [radius=0.05];
 
-%\subsubsection{Case of $S[h-1..h+1] = tbt_a$}
-%Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
-%
-%%\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
-%  In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$.
-Moreover, $w[h]$ has to bind to one of $n_1, n_2, n_3$ in order to stabilize deterministically.
-On the other hand, $w[h+1]$ can supply two bindings but has only two free neighbors.
-One of them is occupied by a successor.
-Therefore $w[h+1]$ can only bind one of $n_5, n_6$, that is, $w[h+1]$ supplies at most one binding.
-Thus, this case $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
-%
-%  These cases are divided on number of capabilities that $w[h-1]$ consumes.
-%  \begin{itemize}
-%  \item[-]{$w[h-1]$ does not consume any bindings}\\
-%  According to Lemma~\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
-%    $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
-%    $w[h+1]$ has to be bound to $w[h-1]$ because $w[h-1]$ has bindings, that is, $w[h+1]$ consumes at least one hand and supplies at most one hand so that $\#bc(C_{h}) \geq \#bc(C_{h+1})$.
-Thus, in this cases $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
-%%     This time, let us consider either $n_4$ is occupied or not.
-If $n_4$ is occupied, then $w[h-1]$ has no active bindings that is this situation consumes some binding capabilities.
-If $n_4$ is free and $w[h+2]$ is stabilized in $n_4$, then $w[h-1]$ has to bind $w[h+2]$.
-Therefore, In this case, stabilization of $w[h-1..h+2]$ consumes some bindings.
-If $n_4$ is free and $w[h+2]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[h+2]$.
-Therefore, in this case consumes some bindings.
-Thus in this cases $\#bc(C_{h-1}) > \#bc(C_{h+2})$.
-%
-%  \item[-]{$w[h-1]$ consumes one binding}\\
-%    In this case, $w_{h}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[h-1]$ and $w[h+1]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
-%  \item[-]{$w[h-1]$ consumes two bindings}\\
-%    In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies two bindings. Thus, in this cases $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
-%   
-%  \end{itemize}
+          \draw[transform canvas={shift=(180:1)}, blue] (105:1) edge[bend right] (105:0);
+          \draw[->, blue] (180:0.9) -- (180:0.1);
+          \draw[->, blue] (-120:0.1) -- (-120:0.9);
 
-%\begin{figure}
-%  \centering
-%    \begin{tabular}{cc}
-%      
-%      \begin{minipage}{0.48\hsize}
-%      \centering
-%        \begin{tikzpicture}
-%
-%          \fill[transform canvas={shift=(0:0)}](0,0) circle [radius=0.1];
-%          
-%          \foreach \theta in {60,-60,120,-120,180}{
-%            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-%          }
-%
-%          \fill[blue](0:1) circle [radius=0.05];
-%          \draw[->, blue] (0:0.1)--(0:0.9);
-%
-%          \node[below] at (-60:1) {$n_4$};
-%
-%          \begin{scope}[shift=(0:2)]
-%            \fill[blue](0,0) circle [radius=0.05];
-%
-%            
-%            \foreach \theta in {120,60,-60,0}{
-%             \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-%            }
-%
-%            \draw[->, blue] (180:0.9)--(180:0.1);
-%            \draw[->, blue] (-120:0.1)--(-120:0.9);
-%
-%            \node[below] at (180:1) {$w_{[h-1]}$};
-%            \node[above] at (0:0) {$w_{[h]}$};
-%            \node[below] at (-120:1) {$w_{[h+1]}$};
-%
-%            \node[above] at (120:1) {$n_3$};
-%            \node[above] at (60:1) {$n_2$};
-%            \node[right] at (0:1) {$n_1$};
-%
-%            \begin{scope}[shift=(-120:1)]
-%              \fill[blue](0,0) circle [radius=0.05];
-%              \foreach \theta in {-120,-60}{
-%                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-%              }
-%
-%              \node[right] at (-120:1) {$n_5$};
-%              \node[right] at (-60:1) {$n_6$};
-%            \end{scope}
-%            
-%          \end{scope}
-%
-%          \node at (1.2,-2.5) {Pattern 1};
-%        \end{tikzpicture}
-%      \end{minipage}
-%
-%      \begin{minipage}{0.48\hsize}
-%      \centering
-%        \begin{tikzpicture}
-%
-%          \fill(0,0) circle [radius=0.1];
-%          
-%          \foreach \theta in {60,0,120,-120,180}{
-%            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-%          }
-%
-%          \draw[->, blue] (-60:0.1)--(-60:0.9);
-%
-%
-%          \begin{scope}[shift=(-60:1),shift=(0:1)]
-%            \fill[blue](0,0) circle [radius=0.05];
-%            \fill[blue](180:1) circle [radius=0.05];
-%
-%            
-%            \foreach \theta in {120,60,0,-60}{
-%              \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
-%            }
-%
-%            \draw[->, blue] (180:0.9)--(180:0.1);
-%            \draw[->, blue] (-120:0.1)--(-120:0.9);
-%
-%            \node[below] at (180:1) {$w_{[h-1]}$};
-%            \node[above] at (0:0) {$w_{[h]}$};
-%            \node[below] at (-120:1) {$w_{[h+1]}$};
-%
-%            \node[above right] at (120:1) {$n_3$};
-%            \node[right] at (60:1) {$n_2$};
-%            \node[right] at (0:1) {$n_1$};
-%
-%            \begin{scope}[shift=(-120:1)]
-%              \fill(0,0) circle [radius=0.05];
-%              \foreach \theta in {180,-120,-60}{
-%                \draw[transform canvas={shift=(\theta:1)}](-0.05,-0.05) rectangle (0.05,0.05);
-%              }
-%
-%              \node[left] at (180:1) {$n_4$};
-%              \node[right] at (-120:1) {$n_5$};
-%              \node[right] at (-60:1) {$n_6$};
-%            \end{scope}
-%            
-%          \end{scope}
-%
-%          \node at (1.25,-4) {Pattern 2};
-%        \end{tikzpicture}
-%      \end{minipage}
-%
-%      
-%      
-%    \end{tabular}
-%    \caption{Case of $S[h-1..h+1] = tbt$}
-%    \label{TTT_tunnelC_enter_usingTunnel}
-%\end{figure}
+          \node[below left] at (180:1) {$w[i]$};
+          \node[above] at (0:0) {$w[i+1]$};
+          \node[below] at (-120:1) {$w[i+2]$};
 
-%\end{proof}
+          \node[right] at (120:1) {$n_3$};
+          \node[right] at (60:1) {$n_2$};
+          \node[right] at (0:1) {$n_1$};
+
+          \begin{scope}[shift=(-120:1)]
+            \fill[blue](0,0) circle [radius=0.05];
+            \foreach \theta in {-120,-60,180}{
+              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
+            }
+
+          \end{scope}
+        \end{tikzpicture}
+    \caption{Case of $S[i+2] = t_a$.}
+    \label{TTT_tunnelC_enter_usingBond}
+  \end{center}
+\end{figure}
 
@@
 
-%\begin{figure}[tb]
-% \centering
-%    \begin{tikzpicture}
-%	\fill[shift=(180:1)] (0,0) circle [radius=0.1];
-%      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-%      
-%      \draw[->] (180:0.9) -- (180:0.1);
-%
-%	\node[above] at (180:1) {$w_{[i-2]}$};
-%	\node[below] at (180:0) {$w_{[i-1]}$};
-%	\node[above] at (0:1) {$n_0$};
-%
-%	\foreach \theta in {0,60,-60,120,-120}{
-%   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-%  	}
-% 	\node[above] at (60:1) {$n_1$};
-%	\node[below] at (-60:1) {$n_2$};
-%	\node[above] at (120:1) {$n_3$};
-%	\node[below] at (-120:1) {$n_4$};
-%    \end{tikzpicture}
-%    \caption{$\alpha = 4$: when $w[i]$ is stabilized}
-%    \label{TTT_a4_lemma_fig}
-%\end{figure}
+\begin{theorem}[$\delta = 1, \alpha = 4$]
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite conformation of length is $3n^2  + 3n + 1$.
+\end{theorem}
 
-%\begin{lemma}
-%\label{TTT_a4_2b_lemma}
-%Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$.
-%When a bead is stabilized by bond, it forms at least two bonds.
-%\end{lemma}
-%
-%\begin{proof}%[proof of lemma]
-%Suppose $w[i]$ were stabilized by only one bond.
-See Fig.~\ref{TTT_a4_lemma_fig}.
-If $n_3$ is free, $w[i-2]$ still has some bonds because of arity $\alpha = 4$.
-Thus, $n_4$ must be occupied; otherwise, $w[i]$ would be stabilized nondeterministically at $n_3$ and $n_4$.
-Moreover, also $n_2$ has to be occupied for deterministic and also $n_0, n_1$.
-$n_1$ has some hands because $n_3$ is free.
-Therefore, $w[i]$ is stabilized at $n_3$ and it has to use at least two hands.
-It contradict assumption.
-%\end{proof}
+\begin{proof}
+Consider the moment when a bead $b$ is stabilized outside $\hexagon_O^n$ for the first time. 
+See Fig.~\ref{TTT_a4_first}.
+There is only one bead available to stabilize $b$ there, which is $b_1$. 
+In order for $b$ to avoid nondeterminism, hence, none of the beads around should not attract $b$.
+
+The point $p_1$ must be empty because a bead there would have at least two free neighbors and hence is provided with a free hand. 
+If there is a bead at $p_2$, $n$ must be at least 2 so that the bead is not singular. 
+Since $p_1$ is empty, this bead has at least one free hand, a contradiction. 
+Thus, $p_2$ must be also empty. 
+In the same way, we can easily show that the point $p_3$ must not be occupied by a non-singular bead. 
+Suppose $p_3 = O$. 
+The point $p_4$ must not be empty; otherwise the singular bead, at $O$, would have a free hand. 
+However, then a bead at $p_4$ would be provided with a free hand, a contradiction. 
+\qed
+\end{proof}
 
@@
     \end{tikzpicture}
-    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
+    \caption{The first bead out of $\hexagon_{w[-n+1]}^n$}
     \label{TTT_a4_first}
@@
 
-\begin{theorem}[$\delta = 1, \alpha = 4$]
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite conformation of length is $3n^2  + 3n + 1$.
-\end{theorem}
-
-\begin{proof}
-Consider the moment when a bead $b$ is stabilized outside $\hexagon_O^n$ for the first time. 
-See Fig.~\ref{TTT_a4_first}.
-There is only one bead available to stabilize $b$ there, which is $b_1$. 
-In order for $b$ to avoid nondeterminism, hence, none of the beads around should not attract $b$.
-
-The point $p_1$ must be empty because a bead there would have at least two free neighbors and hence is provided with a free hand. 
-If there is a bead at $p_2$, $n$ must be at least 2 so that the bead is not singular. 
-Since $p_1$ is empty, this bead has at least one free hand, a contradiction. 
-Thus, $p_2$ must be also empty. 
-In the same way, we can easily show that the point $p_3$ must not be occupied by a non-singular bead. 
-Suppose $p_3 = O$. 
-The point $p_4$ must not be empty; otherwise the singular bead, at $O$, would have a free hand. 
-However, then a bead at $p_4$ would be provided with a free hand, a contradiction. 
-\qed
-\end{proof}
-
-%\begin{lemma}
-%\label{TTT_a3_2b_lemma}
-%Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. 
-%If $S[i] = t$ or $t^\times$ and $S[i+1] \neq \blacksquare$, then the bead $w[i]$ consumes also at least one bond. 
-%% Let $p$ be a point whose neighbors is occupied at least two point.
-If $w[i]$ is not stabilized and $w[i-1]$ includes neighbors of $p$, then $w[i]$ is stabilized at $p$ with at least one bond, $w[i]$ is stabilized at another point of $p$ otherwise with at least two bond except any neighbors of $p$ is occupied.
-%\end{lemma}
-%
-%\begin{proof}%[proof of lemma]
-%Both $n_3$ and $n_4$ are occupied because $S[i] = t$ or $t^\times$.
-%Suppose $w[i]$ were stabilized without any bond.
-%Then, all neighbors of $n_3$ must be occupied as long as the bead at $n_3$ is not singular; otherwise, a bead at $n_3$ would be capable of forming a bond with $w[i]$.
-%That is, $n_1$ is occupied.
-%We can continue this argument in clockwise manner to fill the neighbors of $w[i]$ until a singular bead is encountered, if any.
-%If needed, the same argument is applied starting from $n_4$ in counter-clockwise manner.
-%Thus, all neighbors of $w[i]$ must be occupied but then $S[i+1] = \blacksquare$, contradiction. \qed
-%\end{proof}
-
-\begin{figure} [tb]
-  \begin{center}
-  \begin{tabular}{c c c}
- \begin{minipage}{0.3\hsize}
- \centering
-    \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](0:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (0:0.1) -- (0:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (0:1) {$w_{[i]}$};
-
-	\foreach \theta in {60,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	 \draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
-	  \draw [shift=(180:1),shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
- 	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
-	\node[above, shift=(180:1)] at (120:1) {$n_5$};
-    \end{tikzpicture}
-    \end{minipage}
-
-    \begin{minipage}{0.3\hsize}
-    \centering
-     \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](60:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (60:0.1) -- (60:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (60:1) {$w_{[i]}$};
-
-	\foreach \theta in {0,-60,120,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	\draw [shift=(60:1)] (0.95,-0.05) rectangle (1.05,0.05);
-	\draw [shift=(60:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(60:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	  \draw [shift=(180:1),shift=(-120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-
- 	\node[right] at (0:1) {$n_0$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[above] at (120:1) {$n_3$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(60:1)] at (0:1) {$n_{-1}$};
-	\node[above, shift=(60:1)] at (60:1) {$n_{-2}$};
-	\node[above, shift=(60:1)] at (120:1) {$n_{-3}$};
-	\node[below, shift=(180:1)] at (-120:1) {$n_5$};
-    \end{tikzpicture}
-    \end{minipage}
-
-    \begin{minipage}{0.3\hsize}
-        \centering
-     \begin{tikzpicture}
-
-      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
-      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
-
-      \fill[blue](120:1) circle [radius=0.05];
-
-      \draw[->] (180:0.9) -- (180:0.1);
-      \draw[->, blue] (120:0.1) -- (120:0.9);
-
-	\node[above] at (180:1) {$w_{[i-2]}$};
-	\node[below] at (180:0) {$w_{[i-1]}$};
-	\node[above] at (120:1) {$w_{[i]}$};
-
-	\foreach \theta in {0,60,-60,-120}{
-   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-  	}
-	\draw [shift=(120:1), shift=(60:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(120:1), shift=(120:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-	\draw [shift=(120:1), shift=(180:1)] (-0.05,-0.05) rectangle (0.05,0.05);
-
- 	\node[right] at (0:1) {$n_0$};
-	\node[above] at (60:1) {$n_1$};
-	\node[below] at (-60:1) {$n_2$};
-	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(120:1)] at (60:1) {$n_{-1}$};
-	\node[above, shift=(120:1)] at (120:1) {$n_{-2}$};
-	\node[above, shift=(120:1)] at (180:1) {$n_{-3}$};
-    \end{tikzpicture}
-    \end{minipage}
-    \end{tabular}
-    \caption{All possible directions of $w[i]$: straight, obtuse, acute.}
-    \label{TTT_a3_w}
-  \end{center}
-\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $2n + 14$.
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $4n + 14$.
 \end{theorem}
@@
 
-%We consider cases which $w[i-1]$ is two distances away from the singular point.
-%Let us show that $\#bc(C_{i-1}) > \#bc(C_i)$, that is, when $w[i]$ is stabilized, $w[i]$ uses at least two hands.
-%Fig.\ref{TTT_a3_w} exhibits all the three kinds of possibility of stabilized $w[i]$.
-%Suppose $w[i]$ were able to be stabilized with using one hand in each cases.
-%
-%% Then, $w[i]$ can be also stabilized at $n_3$. 
-%
-%\begin{paragraph}{Case of straight}
-%\begin{itemize}
-%\item[-] Case of $n_3$ is free\\
-%The bead $w[i-2]$ must not have bonds because $w[i]$ is stabilized deterministically so that five neighbors of $w[i-2]$ must be occupied.
-%Therefore $n_5$ must be occupied.
-%We can continue this argument in clockwise manner to fill the neighbors of $n_3$ until $n_1$.
-%However, two neighbors of $n_1$ must be free because they are $n_3$ and the point of $w[i]$, contradict.
-%
-%\item[-] Otherwise\\
-%Both $n_3$ and $n_4$ are occupied.
-%One of $n_1$ and $n_2$ must be free because $S[i] = b$.
-%We assume $n_1$ is free, then all neighbors of $n_1$ must be occupied because $n_3$ is occupied.
-%However, one of neighbors $n_1$ is a point which $w[i]$ is stabilized, contradict.
-%\end{itemize}
-%
-%Therefore, this case contradict assumption.
-%\end{paragraph}
-%
-%\begin{paragraph}{Case of obtuse}
-%\begin{itemize}
-%\item[-] Case of $n_3$ is free\\
-%Any neighbors of $n_3$ have to be occupied but the point which $w[i]$ is stabilized is free. Thus $n_3$ has to be occupied.
-%\item[-] Case of $n_4$ is free\\
-%The point $n_2$ must be occupied because $n_4$ is free and $n_5$ must be occupied.
-%Therefore $n_0$ is occupied.
-%The bead $w[i]$ forms just one bond so that one of $n_0, n_3$ leave some hands or both of them do not leave any bonds.\\
-%If $n_0$ has some hands, then $n_3$ does not have any hands so that $n_{-3}$ is occupied. 
-%We can continue this argument in clockwise manner to fill the neighbors of $w[i]$.
-%That is, $S[i] = \blacksquare$, contradict.
-%
-%If $n_3$ has some hands, then $n_0$ does not have any hands so that neighbors of $w[i]$ are occupied. In the same previous way, contradict.\\
-%If both of $n_0, n_3$ do not have any hands, then both of $n_{-1}, n_{-3}$ are occupied.
-If one of $n_{-1}, n_{-3}$ has some hands, the other does not have any hands so that $n_{-2}$ is occupied.
-If both of $n_{-1}, n_{-3}$ do not have any hands, $n_{-2}$ has to be occupied and $n_{-2}$ has some hands, contradict.
-%\item[-] Case of $n_2$ is free\\
-%Any neighbors of $n_2$ have to be occupied so that $n_0$ is occupied.
-Any neighbors of $n_0$ except $n_2$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_2$ has to be occupied.
-%\item[-] Case of $n_0$ is free\\
-%Any neighbors of $n_0$ have to be occupied so that $n_{-1}$ is occupied.
-Any neighbors of $n_{-1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_0$ has to be occupied.
-%\end{itemize}
-%\end{paragraph}
-%
-%
-%
-%\begin{paragraph}{Case of acute}
-%\begin{itemize}
-%\item[-] Case of $n_4$ is free\\
-%The point $n_4$ and a point which is stabilized $w[i]$ are free so that  $w[i-2]$ has some bonds.
-%However, $w[i]$ can be also stabilized $n_4$ in this case. Thus, $n_4$ has to be occupied.
-%\item[-] Case of $n_2$ is free\\
-%The point $n_0$ has to be occupied. The point $n_1$ has to be also occupied because five neighbors of $n_0$ must be occupied.
-%We consider this case just like case of obtuse and that $n_4$ is free.
-Then if $w[i-2]$ binds $w[i]$, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
-If $n_1$ binds $w[i]$, this case is same.
-Also if $n_1$ and $w[i-2]$ do not have any hand, any $n_{-1}, n_{-2}, n_{-3}$ are occupied.
-Therefore, $w[i+1]$ cannot be provided.
-%\item[-] Case of $n_0$ is free\\
-%Any neighbors of $n_0$ have to be occupied so that $n_{1}$ is occupied.
-Any neighbors of $n_{1}$ except $n_0$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_0$ has to be occupied.
-%\item[-] Case of $n_1$ is free\\
-%Any neighbors of $n_1$ have to be occupied so that $n_{-1}$ is occupied.
-Any neighbors of $n_{-1}$ except $n_1$ have to be also occupied but the point which is stabilized $w[i]$ is free.
-Thus $n_1$ has to be occupied.
-%\end{itemize}
-%
-%Therefore, any situations contradict $S[i] = b$.
-%\end{paragraph}\\
-%
-%
-%Hence, $w[i]$ uses at least two bonds if $w[i-1]$ is at least two distances away the singular point.
-%The size of $ \hexagon^2_0 = 19$ and this number contain the singular point, its successor and its three neighbors which is it binds to.
-Therefore 14 times  $w[i]$ can be stabilized by forming one bond.
-%Therefore, a deterministic unary oritatami system at $\delta = 1$ and $\alpha = 3$ can yield only finite conformation of length is $2n + 14$.
+\begin{figure} [tb]
+  \begin{center}
+  \begin{tabular}{c c c}
+ \begin{minipage}{0.3\hsize}
+ \centering
+    \begin{tikzpicture}
 
-\begin{figure}
+      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \fill[blue](0:1) circle [radius=0.05];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+      \draw[->, blue] (0:0.1) -- (0:0.9);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (0:1) {$w_{[i]}$};
+
+	\foreach \theta in {60,-60,120,-120}{
+   	   \draw [shift=(\theta:1)] (0:0) circle [radius=0.05];
+  	}
+	 \draw [shift=(60:1), ] (0:1) circle [radius=0.05];
+	  \draw [shift=(180:1),shift=(120:1)] (0:0) circle [radius=0.05];
+ 	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[below] at (-120:1) {$n_4$};
+	\node[above, shift=(0:1)] at (60:1) {$n_{-1}$};
+	\node[above, shift=(180:1)] at (120:1) {$n_5$};
+    \end{tikzpicture}
+    \end{minipage}
+
+    \begin{minipage}{0.3\hsize}
+    \centering
+     \begin{tikzpicture}
+
+      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \fill[blue](60:1) circle [radius=0.05];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+      \draw[->, blue] (60:0.1) -- (60:0.9);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (60:1) {$w_{[i]}$};
+
+	\foreach \theta in {0,-60,120,-120}{
+   	   \draw [shift=(\theta:1)](0:0) circle [radius=0.05];
+  	}
+	\draw [shift=(60:1)] (0:1) circle [radius=0.05];
+	\draw [shift=(60:1), shift=(60:1)] (0:0) circle [radius=0.05];
+	\draw [shift=(60:1), shift=(120:1)] (0:0) circle [radius=0.05];
+	  \draw [shift=(180:1),shift=(-120:1)] (0:0) circle [radius=0.05];
+
+ 	\node[right] at (0:1) {$n_0$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[above] at (120:1) {$n_3$};
+	\node[below] at (-120:1) {$n_4$};
+	\node[above, shift=(60:1)] at (0:1) {$n_{-1}$};
+	\node[above, shift=(60:1)] at (60:1) {$n_{-2}$};
+	\node[above, shift=(60:1)] at (120:1) {$n_{-3}$};
+	\node[below, shift=(180:1)] at (-120:1) {$n_5$};
+    \end{tikzpicture}
+    \end{minipage}
+
+    \begin{minipage}{0.3\hsize}
+        \centering
+     \begin{tikzpicture}
+
+      \fill[shift=(180:1)] (0,0) circle [radius=0.1];
+      \fill[shift=(180:0)] (0,0) circle [radius=0.1];
+
+      \fill[blue](120:1) circle [radius=0.05];
+
+      \draw[->] (180:0.9) -- (180:0.1);
+      \draw[->, blue] (120:0.1) -- (120:0.9);
+
+	\node[above] at (180:1) {$w_{[i-2]}$};
+	\node[below] at (180:0) {$w_{[i-1]}$};
+	\node[above] at (120:1) {$w_{[i]}$};
+
+	\foreach \theta in {0,60,-60,-120}{
+   	   \draw [shift=(\theta:1)] (0:0) circle [radius=0.05];
+  	}
+	\draw [shift=(120:1), shift=(60:1)] (0:0) circle [radius=0.05];
+	\draw [shift=(120:1), shift=(120:1)] (0:0) circle [radius=0.05];
+	\draw [shift=(120:1), shift=(180:1)] (0:0) circle [radius=0.05];
+
+ 	\node[right] at (0:1) {$n_0$};
+	\node[above] at (60:1) {$n_1$};
+	\node[below] at (-60:1) {$n_2$};
+	\node[below] at (-120:1) {$n_4$};
+	\node[above, shift=(120:1)] at (60:1) {$n_{-1}$};
+	\node[above, shift=(120:1)] at (120:1) {$n_{-2}$};
+	\node[above, shift=(120:1)] at (180:1) {$n_{-3}$};
+    \end{tikzpicture}
+    \end{minipage}
+    \end{tabular}
+    \caption{All possible directions of $w[i]$: straight, obtuse, acute.}
+    \label{TTT_a3_w}
+  \end{center}
+\end{figure}
+
+\begin{theorem}[$\delta= 1, \alpha=2$]
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation in $w[27n^2 + 9n + 1]$.
+\end{theorem}
+
+\begin{proof}
+ We assume $w[i]$ is the first bead outside $\hexagon^n_0$
+ See Fig.~\ref{fig:ttt_d2}.
+ If $w[i+1]$ elongated to west and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_3$; otherwise $w[i+2]$ forms two bonds.
+ If $w[i+1]$ elongated to west and $w[i+2]$ is stabilized at $p_3$, $w[i+1..]$ form a zig-zag conformation.
+  If $w[i+1]$ elongated to east and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_2$; otherwise $w[i+2]$ forms two bonds.
+ If $w[i+1]$ elongated to east and $w[i+2]$ is stabilized at $p_2$, $w[i+1..]$ is zig-zag conformation.
+ Thus, if $w[i]$ is the first bead outside $\hexagon^k_0$ for some $k \geq n$, $\#bc(C_i) > \#bc(C_{i+1})$ or $w[i+1..]$ form a zig-zag conformation.
+
+ We assume $w[l]$ is the first bead outside $\hexagon^k_0$ and $w[m]$ is the first bead outside $\hexagon^{k+1}_0$ for some $k,l,m$ with $k<3n$.
+Let $s$ be a element of $S[l+1..m-1]$.
+If $s = b$, $s$ does not increase binding capability.
+ If $s=t$, $s$ is a element of a subsequence $bt^+b$.
+This subsequence does not increase binding capability according to Theorem~\ref{TTT}.
+Thus, $\#bc(C_l) > \#bc(C_{m})$ or $w[l..]$ form a zig-zag conformation.
+
+ The seed $\sigma$ provides at most $2n$ binding capability, that is, $\#bc(C_0) \leq 2n$.
+ Thus,  if  $w[i]$ is the first bead outside $\hexagon^{3n}_0$, then this conformation has no hand without $w[i-1]$ and $w[i]$.
+ Hence, $w[27n^2 + 9n + 1..]$ form a zig-zag conformation.
+\end{proof}
+
+\begin{figure}[tb]
   \begin{center}
@@
     \end{tabular}
-    \caption{The bead $w[i]$  the first bead outside $\hexagon^n_0$: $w[i+1]$ elongated to west (left), $w[i+1]$ elongated to east (right)}
+    \caption{The bead $w[i]$  the first bead outside $\hexagon^n_0$: (Left) $w[i+1]$ elongated to west, (Right) $w[i+1]$ elongated to east.}
     \label{fig:ttt_d2}
@@
 \end{figure}
-
-\begin{theorem}[$\delta= 1, \alpha=2$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation in $w[27n^2 + 9n + 1]$.
-\end{theorem}
-
-\begin{proof}
- We assume $w[i]$ is the first bead outside $\hexagon^n_0$
- See Fig.~\ref{fig:ttt_d2}.
- If $w[i+1]$ elongated to west and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_3$; otherwise $w[i+2]$ forms two bonds.
- If $w[i+1]$ elongated to west and $w[i+2]$ is stabilized at $p_3$, $w[i+1..]$ form a zig-zag conformation.
-  If $w[i+1]$ elongated to east and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_2$; otherwise $w[i+2]$ forms two bonds.
- If $w[i+1]$ elongated to east and $w[i+2]$ is stabilized at $p_2$, $w[i+1..]$ is zig-zag conformation.
- Thus, if $w[i]$ is the first bead outside $\hexagon^k_0$ for some $k \geq n$, $\#bc(C_i) > \#bc(C_{i+1})$ or $w[i+1..]$ form a zig-zag conformation.
-
- We assume $w[l]$ is the first bead outside $\hexagon^k_0$ and $w[m]$ is the first bead outside $\hexagon^{k+1}_0$ for some $k,l,m$ with $k<3n$.
-Let $s$ be a element of $S[l+1..m-1]$.
-If $s = b$, $s$ does not increase binding capability.
- If $s=t$, $s$ is a element of a subsequence $bt^+b$.
-This subsequence does not increase binding capability according to Theorem~\ref{TTT}.
-Thus, $\#bc(C_l) > \#bc(C_{m})$ or $w[l..]$ form a zig-zag conformation.
-
- The seed $\sigma$ provides at most $2n$ binding capability, that is, $\#bc(C_0) \leq 2n$.
- Thus,  if  $w[i]$ is the first bead outside $\hexagon^{3n}_0$, then this conformation has no hand without $w[i-1]$ and $w[i]$.
- Hence, $w[27n^2 + 9n + 1..]$ form a zig-zag conformation.
-\end{proof}
-
-%By Tunnel Troll Theorem, any tunnel sections which represented in $bbt^+$ or $bt^+bt^+$ consume binding capabilities.
-If the sequence $S$ is free from any subsequence of the form $bt^+bt^+$, then it can factorize as $S = u_1 u_2 u_3 \cdots$ for some $u_1 , u_2 , u_3 , \cdots \in \{b\} \cup bbt^+$.
-Assume the length of $\sigma$ is $n$, seed supplies at most $2n$ binding capabilities.
-Therefore formula \ref{TTT_only_bond} hold.
-%
-%\begin{eqnarray}
-%  \exists i \in \mathbb{N} \quad s.t. \quad u_{i-1} , u_i , u_{i+1} , u_{i+2} , \cdots \in \{ b \}
-%  \label{TTT_only_bond}
-%\end{eqnarray}
-%
-%
-%Let us represent $S$ as $S[i.i+1...] = v_i v_{i+1} v_{i+2} \cdots$ for some $v_i, v_{i+1}, v_{i+2}, \cdots \in \{ a, o\}$ where if $v_k$ is $a$, then $v_{k+1}$ is bound to $v_{k-1}$, if $v_k$ is $o$, then $v_{k+1}$ is NOT bound to $v_{k-1}$.
-%
-%
-%Let us consider the case of $v_k$ is $o$.
-See Fig.\ref{TTT_case_of_o}.
-$w[i-1]$ consumes some binding capabilities because $v_{i-1}$ is $b$.
-If the number of $w[i-1]$'s bindings is one binding, then $w[i+1]$ has to be bound except $n_1$ or $n_2$ so that $w[i+1]$ must consumes two bindings except the case of $n_1$ and $n_2$ are occupied and $w[i]$ consumes at least one binding.
-If $n_1$ and $n_2$ are occupied, then $w[i-1]$'s bindings are inactive, that is, $w[i-1]$ consumes two binding capabilities.
-Therefore, this case consumes binding capabilities.
-If $w[i-1]$ dose Not have any bindings, then $w[i-1]$ already consumes two bindings.
-In addition, $w[i]$ and $w[i+1]$ consume at least one binding.
-Therefore this case consumes binding capabilities.
-Thus, the formula \ref{TTT_only_a} hold and according to the formula \ref{TTT_only_bond} and the formula \ref{TTT_only_a}, the formula \ref{TTT_structure} is hold.
-Thus, in this case, oritatami system can yield infinite structures but they are only zig-zag conformation.
-
-%
-%
-%\begin{eqnarray}
-%  \exists j \in \mathbb{N} \quad s.t. \quad u_j , u_{j+1} , u_{j+2} , \cdots \in \{ a \}
-%  \label{TTT_only_a}
-%\end{eqnarray}
-%
-%\begin{eqnarray}
-%  | S | > \forall m \in \mathbb{N} \quad \to \quad \exists n \in \mathbb{N} \quad s.t. \quad S[n], S[n+1], \cdots \in \{ a \}
-%  \label{TTT_structure}
-%\end{eqnarray}
-%
-%\begin{figure}
-%  \begin{center}
-%    \begin{tikzpicture}
-%      
-%      \fill[transform canvas={shift=(-120:1)}](0,0) circle [radius=0.1];
-%      
-%      \fill[blue](0:0) circle [radius=0.05];
-%      \fill[blue](0:1) circle [radius=0.05];
-%      \fill[shift=(0:1), blue](40:1) circle [radius=0.05];
-%
-%      \draw[->, blue] (-120:1) edge[bend left] (-120:0.1);
-%      \draw[->, blue] (0:0.1) -- (0:0.9);
-%      \draw[->,transform canvas={shift=(0:1.2)}, blue] (50:0) -- (47:0.8);
-%      
-%      \draw[shift=(60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-%      \draw[shift=(-60:1)](-0.05,-0.05) rectangle (0.05,0.05);
-%      
-%      \node[below] at (-120:1) {$w[i-2]$};
-%      \node[above] at (0:0) {$w[i-1]$};
-%      \node[below] at (0:1) {$w[i]$};
-%      \node[right, shift=(0:1)] at (40:1) {$w[i+1]$};
-%
-%      \node[above] at (60:1) {$n_1$};
-%      \node[below] at (-60:1) {$n_2$};
-%        
-%    \end{tikzpicture}
-%    \caption{Case of $S[i]$}
-%    \label{TTT_case_of_o}
-%  \end{center}
-%\end{figure}
-%

### 2018-12-05 arity1.tex
Update arity1.tex

@@
         \draw (0.0, 1.732) -- (-0.5, 0.866);
-        \draw [dotted] [red] (0.0, 1.732) -- (0.5, 0.866);
-        \draw [dotted] [red] (0.0, 0.0) -- (-0.5, 0.866);
+        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
+        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
       \end{tikzpicture}
@@
         \draw (0.0, 1.732) -- (0.5, 0.866);
-        \draw [dotted] [red] (0.0, 0.0) -- (0.5, 0.866);
-        \draw [dotted] [red] (0.0, 1.732) -- (-0.5, 0.866);
+        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
+        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
       \end{tikzpicture}
@@
 There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}.
-However, if it makes three bonds once, such as in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
+If there are beads having a free hand at (1,0) and (-1,0), there will be at least two possibilities in Fig.~\ref{fig:beadi-1} when a bead $i-1$ is fixed at (0,0).
+It is nondeterministic and beads $i-1, i, i+1$ needs to make three hydrogen bonds to prevent from it.
+That is, it is impossible to put beads having a free hand at (-1,0), (0,0) and (1,0).
+It is impossible to realize (b) and (e) in Fig.~\ref{fig:3bonds}.
+(d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
+If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
 Similarly to case 1.
-in the previous section, (a), (b) and (c)in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a first corner of $\hexagon_p^n$ and  (e) in Fig.~\ref{fig:3bonds} become nondeterministic finally, as in Fig.~\ref{fig:hexcorner}, when it reaches a second corner of $\hexagon_p^n$.
-(d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
+in the previous section, (a) and (c) in Fig.~\ref{fig:3bonds} become nondeterministic finally when it reaches a first corner of $\hexagon_p^n$.
 
@@
   \begin{center}
-    \begin{tabular}{ccc}
+    \begin{tabular}{ccccc}
       \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
@@
         \draw (1.5, 0.866) -- (2.5, 0.866);
-        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
         \fill (1.5, -0.5) node [below] {(a)};
@@
         \draw (-0.5, 0.866) -- (-1.5, 0.866);
-        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dotted] [red] (-0.5, 0.866) -- (-1.0, 0.0);
-        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (-0.5, 0.866) -- (-1.0, 0.0);
+        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
         \fill (-0.5, -0.5) node [below] {(b)};
-      \end{tikzpicture}\\
+      \end{tikzpicture}
 
@@
         \draw (-0.5, 0.866) -- (-1.5, 0.866);
-        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
-        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
+        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
         \fill (-0.5, -0.5) node [below] {(c)};
@@
         \draw (-0.5, 0.866) -- (-1.5, 0.866);
-        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
-        \draw [dotted] [red] (-1.5, 0.866) -- (-2.0, 0.0);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
+        \draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
         \fill (-0.5, -0.5) node [below] {(d)};
@@
         \draw (-0.5, 0.866) -- (-1.5, 0.866);
-        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dotted] [red] (-0.5, 0.866) -- (0.0, 0.0);
-        \draw [dotted] [red] (-1.5, 0.866) -- (-1.0, 0.0);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
+        \draw [dashed] [red] (-1.5, 0.866) -- (-1.0, 0.0);
         \fill (-0.5, -0.5) node [below] {(e)};
@@
   \begin{center}
-    \begin{tabular}{ccc}
+    \begin{tabular}{cc}
+
       \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
         \fill (1.0, 0.0) circle [radius = 0.1];
-        \fill (2.0, 0.0) circle [radius = 0.1];
-        \fill (3.0, 0.0) circle [radius = 0.1];
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (-1.0, 0.0) circle [radius = 0.1];
         \fill (0.5, 0.866) circle [radius = 0.1];
-        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
-        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
-        \fill [blue] (3.5, 0.866) circle [radius = 0.1];
-        \draw [blue] (0.5, 0.866) -- (1.5, 0.866);
-        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
-        \draw [blue] (2.5, 0.866) -- (3.5, 0.866);
-        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
-        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
-        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (0.5, 0.866) node [above] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (-0.5, 0.866);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
       \end{tikzpicture}
@@
         \fill (1.0, 0.0) circle [radius = 0.1];
-        \fill (2.0, 0.0) circle [radius = 0.1];
-        \fill (3.0, 0.0) circle [radius = 0.1];
+        \fill (0.0, 0.0) circle [radius = 0.1];
+        \fill (-1.0, 0.0) circle [radius = 0.1];
         \fill (0.5, 0.866) circle [radius = 0.1];
-        \fill [blue] (1.5, 0.866) circle [radius = 0.1];
-        \fill [blue] (2.5, 0.866) circle [radius = 0.1];
-        \fill [blue] (1.0, 1.732) circle [radius = 0.1];
-        \draw [blue] (0.5, 0.866) -- (1.0, 1.732);
-        \draw [blue] (1.5, 0.866) -- (1.0, 1.732);
-        \draw [blue] (1.5, 0.866) -- (2.5, 0.866);
-        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
-        \draw [dashed] (3.5, -0.866) -- (3.0, 0.0);
-        \draw [dashed] (0.5, 0.0) -- (3.0, 0.0);
+        \fill (-0.5, 0.866) circle [radius = 0.1];
+        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+        \fill (0.5, 0.866) node [above] {$(1, 1)$};
+        \draw (0.0, 0.0) -- (0.5, 0.866);
+        \draw (0.5, 0.866) -- (-0.5, 0.866);
+        \draw [dashed] [red] (-1.0, 0.0) -- (0.0, 0.0);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
       \end{tikzpicture}
@@
     \end{tabular}
-    \caption{Being nondeterministic when reaching a corner of $\hexagon_p^n$}
-    \label{fig:hexcorner}
+    \caption{When a bead$i-1$ is fixed at (0,0)}
+    \label{fig:beadi-1}
   \end{center}
@@
         \fill (0.5, 0.866) node [left] {$(1, 1)$};
+        \fill (1.0, 0.0) node [below] {$(1, 0)$};
         \draw (0.0, 0.0) -- (0.5, 0.866);
@@
         \draw (1.0, 1.732) -- (1.5, 0.866);
-        \draw [dotted] [red] (1.5, 0.866) -- (1.0, 0.0);
-        \draw [dotted] [red] (1.0, 1.732) -- (0.5, 0.866);
-        \draw [dotted] [red] (1.0, 1.732) -- (0.5, 0.866);
+        \draw [dashed] [red] (1.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
+        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
       \end{tikzpicture}
@@
         \fill (-0.5, 0.866) node [left] {$(0, 1)$};
+        \fill (1.0, 0.0) node [below] {$(1, 0)$};
         \draw (0.0, 0.0) -- (-0.5, 0.866);
@@
         \draw (0.0, 1.732) -- (0.5, 0.866);
-        \draw [dotted] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dotted] [red] (0.0, 1.732) -- (-0.5, 0.866);
+        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
+        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
       \end{tikzpicture}
@@
   \begin{center}
-    \begin{tabular}{ccc}
+    \begin{tabular}{cc}
 
@@
         \draw (2.5, 0.866) -- (3.5, 0.866);
-        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
-        \draw [dotted] [red] (3.5, 0.866) -- (4.0, 0.0);
+        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
         \fill (1.5, -0.5) node [below] {(a)};
@@
         \draw (2.5, 0.866) -- (3.5, 0.866);
-        \draw [dotted] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dotted] [red] (2.5, 0.866) -- (3.0, 0.0);
-        \draw [dotted] [red] (3.5, 0.866) -- (4.0, 0.0);
+        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
+        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
+        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
         \fill (1.5, -0.5) node [below] {(b)};

### 2018-12-05 arity1.tex
Update arity1.tex

@@
 \subsection{$\alpha = 1$, unary}
+\label{sec:unary}
 
@@
 
-\subsubsection{$\delta = 2$\\}
+\subsubsection{\ref{sec:unary}.1 \ \ $\delta = 2$\\}
 
@@
 
-\subsubsection{$\delta = 3$\\}
+\subsubsection{\ref{sec:unary}.2 \ \ $\delta = 3$\\}
 
-\textbf{A.} First, let us assume that a fixed bead on a side of $\hexagon_p^n$ has a free hand, and bead $i$ binds to it.
+\begin{enumerate}
+\item Let us discuss that a fixed bead on a side of $\hexagon_p^n$ has a free hand, and bead $i$ binds to it.
 If the most stable conformation formed by beads $i, i+1, i+2$ has only two hydrogen bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}.
@@
 \end{figure}
-
-There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}.
-If there are beads having a free hand at (1,0) and (-1,0), there will be at least two possibilities in Fig.~\ref{fig:beadi-1} when a bead $i-1$ is fixed at (0,0).
-It is nondeterministic and beads $i-1, i, i+1$ needs to make three hydrogen bonds to prevent from it.
-That is, it is impossible to put beads having a free hand at (-1,0), (0,0) and (1,0).
-It is impossible to realize (b) and (e) in Fig.~\ref{fig:3bonds}.
-(d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
-If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
-Similarly to case 1.
-in the previous section, (a) and (c) in Fig.~\ref{fig:3bonds} become nondeterministic finally when it reaches a first corner of $\hexagon_p^n$.
 
@@
 
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{cc}
+There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}.
+There are beads having a free hand at (1,0) and (-1,0) to realize (b) and (e) in Fig.~\ref{fig:3bonds} before a bead $i-1$ is fixed at (0,0).
+One of these two beads may be a predecessor of a bead $i-1$, but at least one bead is not.
+A bead $i-1$ makes a hydrogen bond with one of these two beads which is not its predecessor when it is fixed at (0,0).
+That is, it is impossible to put three beads having a free hand at (-1,0), (0,0) and (1,0) when a bead $i$ is fixed, and then, to realize (b) and (e) in Fig.~\ref{fig:3bonds}.
+(d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
+If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
+Similarly to case 1.
+in the previous section, (a) and (c) in Fig.~\ref{fig:3bonds} become nondeterministic finally when it reaches a first corner of $\hexagon_p^n$.
 
-      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-        \fill (1.0, 0.0) circle [radius = 0.1];
-        \fill (0.0, 0.0) circle [radius = 0.1];
-        \fill (-1.0, 0.0) circle [radius = 0.1];
-        \fill (0.5, 0.866) circle [radius = 0.1];
-        \fill (-0.5, 0.866) circle [radius = 0.1];
-        \fill (0.0, 0.0) node [below] {$(0, 0)$};
-        \fill (0.5, 0.866) node [above] {$(1, 1)$};
-        \draw (0.0, 0.0) -- (0.5, 0.866);
-        \draw (0.5, 0.866) -- (-0.5, 0.866);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
-      \end{tikzpicture}
-
-      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-        \fill (1.0, 0.0) circle [radius = 0.1];
-        \fill (0.0, 0.0) circle [radius = 0.1];
-        \fill (-1.0, 0.0) circle [radius = 0.1];
-        \fill (0.5, 0.866) circle [radius = 0.1];
-        \fill (-0.5, 0.866) circle [radius = 0.1];
-        \fill (0.0, 0.0) node [below] {$(0, 0)$};
-        \fill (0.5, 0.866) node [above] {$(1, 1)$};
-        \draw (0.0, 0.0) -- (0.5, 0.866);
-        \draw (0.5, 0.866) -- (-0.5, 0.866);
-        \draw [dashed] [red] (-1.0, 0.0) -- (0.0, 0.0);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-      \end{tikzpicture}
-
-    \end{tabular}
-    \caption{When a bead$i-1$ is fixed at (0,0)}
-    \label{fig:beadi-1}
-  \end{center}
-\end{figure}
-
-\textbf{B.} Next, let us assume that bead $i$'s predecessor at (0,0) has no free hand and that there is a bead at (1,0) which has a free hand.
+\item Let us discuss that bead $i$'s predecessor at (0,0) has no free hand.
+Let us assume that there is a bead at (1,0) which has a free hand.
 If there is a bead at (1,0) and beads $i, i+1, i+2$ make only two hydrogen bonds, it will become nondeterministic as in Fig.~\ref{fig:beadat(1,0)}.
 That is, beads $i, i+1, i+2$ need to make three bonds to stabilize $i$.
-If they make three hydrogen bonds, the situation is analogous to \textbf{A}.
-There should not be any bead having a free hand at (1,0) or (-1,0) to prevent from becoming \textbf{A}.
+If they make three hydrogen bonds, the situation is analogous to (a) and (c) in Fig.~\ref{fig:3bonds}.
+There are not any bead having a free hand at (1,0) or (-1,0) to prevent from being (a) and (c) in Fig.~\ref{fig:3bonds}.
 Let us discuss the moment after bead $i$ is fixed outside $\hexagon_p^n$.
-Now bead $i$ has a free hand.
-If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such structures, as in Fig.~\ref{fig:beadi2}.
+Now bead $i$ has a free hand because there are no beads having a free hand at (1,0) or (-1,0).
+If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such conformations, as in Fig.~\ref{fig:beadi2}.
 Hence, they need to form three bonds to deterministically stabilize, such as in Fig.~\ref{fig:3bonds2}.
-(a) in Fig~\ref{fig:3bonds2} becomes \textbf{A} because it makes three hydrogen bonds.
+(a) in Fig~\ref{fig:3bonds2} becomes (a) in Fig.~\ref{fig:3bonds}.
 (b) in Fig.~\ref{fig:3bonds2} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (1,0).\\
@@
 \end{figure}
+
+\end{enumerate}
+
+It can yield finite conformation and the length is $3n^2+n^2+1$.

### 2018-12-05 tt_theorem.tex

@@
 \item At arity $\alpha \geq 3$, if $S[i] = t$ (i.e. the tunnel that stabilizes $w[i]$ is not singular) and $S[i+1] \neq \blacksquare$, then $\#bc(C_{i-1}) > \#bc(C_i)$.
-\item At arity $\alpha = 2$, if $n$ is the number of $bt$ in $S[i..j]$ for some $i,j$ such that $S[i] = b$ and $i < j$, then $\#bc(C_{i-2}) - \#bc(C_{j}) \geq n$.
+\item At arity $\alpha = 2$, if $m$ is the number of occurrences of $bt$ as a factor in $S[1..k]$ for an index $k$, then $\#bc(C_{0}) - m \geq \#bc(C_{k})$.
 \end{enumerate}
 \end{theorem}
+
+In order to prove this Tunnel Troll Theorem, we use the following three lemmas.
+%Let us introduce some lemmas for proving Tunnel Troll Theorem.
 
@@
 \item If $w[i]$ forms at least one bond, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
-\item If $w[i]$ does not consumes any bond and $S[i] \in \{t_s, t_o \}$, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
-\item If $w[i]$ does not consumes any bond and $S[i] = t_a$, $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
+\item If $w[i]$ does not consume any bond and $S[i] \in \{t_s, t_o \}$, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
+\item If $w[i]$ does not consume any bond and $S[i] = t_a$, $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
 \end{enumerate}
@@
 
-	We consider each statements. First we prove statement 1.
-	The bead $w[i+1]$ consumes one hand and provide nothing.
+	We consider each statement. First we prove Statement 1.
+	The bead $w[i+1]$ consumes one hand and provides nothing.
 	If $w[i]$ forms two bonds, then even if $w[i+2]$ provides two free hands, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
@@
 
-	Next we prove statement 2.
+	Let us proceed to Statement 2.
 	See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
@@
 
-	Finally, we prove statement 3.
-	Consider the case when $w[i]$ is stabilized by a tunnel section of type $A$ and $w[i]$ does not consumes any bond.
-	Then, $w[i-2]$ must consume two bonds; otherwise $w[i-2]$'s hands is used by $w[i]$.
-	The bead $w[i-1]$ consumes one hand and provide nothing.
+	Finally, we prove Statement 3.
+	%Consider the case when $w[i]$ is stabilized by a tunnel section of type $A$ and $w[i]$ does not consumes any bond.
+	In order for $w[i]$ not to bind, $w[i-2]$ must have already used up its hands.
+	% The bead $w[i-2]$ must consume two bonds ; otherwise $w[i-2]$'s hands is used by $w[i]$.
+	The bead $w[i-1]$ consumes one hand and provides nothing.
 	Thus,  $\#bc(C_{i-3}) - 1 \geq \#bc(C_{i})$.
-	Moreover, the bead $w[i+1]$ consumes one hand and provide nothing and $w[i]$'s hands is used by $w[i+2]$, and hence, $w[i+2]$ does not increase the binding capability.
-	Therefore, $\#bc(C_{i-3}) > \#bc(C_{i+2})$.
-	This argument actually work also for the case when $w[i]$ is stabilized rather by binding.
+	The bead $w[i+1]$ consumes one hand and provides nothing.
+	Finally, $w[i+2]$ uses one hand of $w[i]$, and hence, does not increase the binding capability.
+	Therefore, $\#bc(C_{i-3}) -2 \geq \#bc(C_{i+2})$.
+	This argument actually works also for the case when $w[i]$ is stabilized rather by binding. \qed
 \end{proof}
@@
   \begin{center}
+  \begin{tabular} {c c}
+  \begin{minipage}{0.48\hsize}
+  \centering
         \begin{tikzpicture}
-        \draw[->,white] (-70:0.1) -- (-70:3);
+        \draw[->, white, shift=(180:1), shift=(120:1)] (120:0.9) -- (120:0.1);
           \foreach \theta in {60,-60,120,0}{
@@
             \fill[blue](0,0) circle [radius=0.05];
-            \foreach \theta in {-120,-60,180}{
-              \draw[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.05];
-            }
 
@@
         \end{tikzpicture}
-    \caption{Case of $S[i+2] = t_a$.}
+
+	\end{minipage}
+
+	\begin{minipage}{0.48\hsize}     
+        \begin{tikzpicture}
+         \draw[->, white, shift=(180:1), shift=(120:1)] (120:0.9) -- (120:0.1);
+          \foreach \theta in {60,-60,120,0}{
+            \fill[transform canvas={shift=(\theta:1)}](0,0) circle [radius=0.1];
+          }
+
+          \foreach \theta in {60,60,120,180}{
+            \fill[transform canvas={shift=(\theta:1)}, shift=(180:1)](120:1) circle [radius=0.1];
+          }
+
+          \fill[blue](180:1) circle [radius=0.05];
+          \fill[blue](0:0) circle [radius=0.05];
+          \fill[blue, shift=(180:1), shift=(120:1)](0:0) circle [radius=0.05];
+          \fill[blue, shift=(180:1), shift=(120:1)](-120:1) circle [radius=0.05];
+
+          \draw[->, blue] (180:0.9) -- (180:0.1);
+          \draw[->, blue] (-120:0.1) -- (-120:0.9);
+          \draw[->, blue, shift=(180:1), shift=(120:1)] (-60:0.1) -- (-60:0.9);
+           \draw[->, blue, shift=(180:1), shift=(120:1)] (-120:0.9) -- (-120:0.1);
+
+          \node[below] at (180:1) {$w[i]$};
+          \node[above] at (0:0) {$w[i+1]$};
+          \node[below] at (-120:1) {$w[i+2]$};
+          \node[below left] at (-180:2) {$w[i-2]$};
+
+          \node[right] at (120:1) {$n_3$};
+          \node[right] at (60:1) {$n_2$};
+          \node[right] at (0:1) {$n_1$};
+
+          \begin{scope}[shift=(-120:1)]
+            \fill[blue](0,0) circle [radius=0.05];
+
+          \end{scope}
+        \end{tikzpicture}
+        \end{minipage}
+        \end{tabular}
+    \caption{Case of $S[i] = t_a$ and $S[i+2] = t_a$: (Right) Moreover $w[i]$ does not consume any bond.}
     \label{TTT_tunnelC_enter_usingBond}
@@
 
-Next, we consider the case of $\delta = 2, \alpha = 1$. We assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and all $S[i+2..j]$ are  $ t_s$ or  $t_o$.
-According to Lemma~\ref{TTT_entrance_Tab}, $\#bc(C_{i-1}) > \#bc(C_{i})$ and moreover that, according to Lemma~\ref{TTT_exit}, $\#bc(C_{i}) \geq \#bc(C_{j})$.
-Thus, binding capability of the conformation decrease per a subsequence $bt_s$ or $bt_o$.
+Next, we consider the case of $\delta = 2, \alpha = 1$. We assume there are indices $i$, $j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$.
+If $S[i+2]$ is $ t_s$ or  $t_o$, then Lemma~\ref{TTT_entrance_Tab} implies $\#bc(C_{i-1}) > \#bc(C_{i})$ and  Lemma~\ref{TTT_exit} implies $\#bc(C_{i}) \geq \#bc(C_{j})$.
+Thus, binding capability decreases by 1 per a factor $bt_s$ or $bt_o$.
 
-On the other hand, we assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and there is a element of $S[i+2..j]$ such that it is $t_a$.
-All $S[i+3..j]$ do not contain $t_o$; otherwise $S[i+4..j+1]$ contain $\blacksquare$.
-Therefore, $S[i+2] = t_a$.
-According to Lemma~\ref{TTT_exit}, on statement 1, 2, $\#bc(C_{i-2}) > \#bc(C_{i+2})$ and if $i \leq j - 3$, $\#bc(C_{i+2}) \geq \#bc(C_{j})$.
+Now, we assume $S[i+2] = t_a$.
+%All $S[i+3..j]$ do not contain $t_a$; otherwise $S[i+4..j+1]$ contain $\blacksquare$.
+%Therefore, $S[i+2] = t_a$.
+According to Lemma~\ref{TTT_tunnelC_lemma}, on statement 1, 2, $\#bc(C_{i-2}) > \#bc(C_{i+2})$ and if $i \leq j - 3$, $\#bc(C_{i+2}) \geq \#bc(C_{j})$.
 Thus, binding capability of the conformation decrease per a subsequence $bt_a$ unless $w[i]$ does not consumes any bond.
@@
 
-Hence, if $S[i..j]$ contain n's subsequences of $bt$, $\#bc(C_{i-2}) - \#bc(C_{j}) \geq n$
+Hence, if $S[i..j]$ contain n's subsequences of $bt$, $\#bc(C_{i-2}) - n \geq \#bc(C_{j})$
 \qed

### 2018-12-05 arity1.tex
Update arity1.tex
Pyramid with numbers again
I don't know why the previous changes do not show up. I tried this like
3 times already and to me it showed that it worked. In any case, here
goes the numbered pyramid again.
Small change

@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{./Fig/chichenBig}
-	\caption{Quadratic length transcript folding deterministically into pyramid shape.
-Seed: thick black path.
-Transcript: thin blue path.
-Bonds: dashed red lines.
-Beads: '$0$' black, '$1$' red, '$2$' red with black contour, '$3$' green, '$4$' green with black contour.}
+	\includegraphics[width=0.9\linewidth]{./Fig/CI_Numbers}
+	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. }
 	\label{CI:big}
@@
 		\includegraphics[width=0.9\linewidth]{./Fig/hexagonOut2}
-		\caption{}
+		\caption{When bead $i+2+m$ is fixed}
 		\label{fig:hexagonout2}
@@
 
-	\caption{}
+	\caption{When bead $i+1$ is fixed at (0,1)}
 	\label{fig:hexagonOut2}
@@
     \end{tabular}
-    \caption{Two conformations when a bead $i-1$ at (0,0) has a free hand}
+    \caption{Two conformations when bead $i-1$ at (0,0) has a free hand}
     \label{fig:beadi}
@@
 
-It can yield finite conformation and the length is $3n^2+n^2+1$.
+It can yield only finite conformation and the length is $3n^2+n^2+1$.

### 2018-12-05 arity1.tex
Update arity1.tex

@@
 There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}.
-There are beads having a free hand at (1,0) and (-1,0) to realize (b) and (e) in Fig.~\ref{fig:3bonds} before a bead $i-1$ is fixed at (0,0).
-One of these two beads may be a predecessor of a bead $i-1$, but at least one bead is not.
+There are beads having a free hand at (1,0) and (-1,0) to realize (b) and (e) in Fig.~\ref{fig:3bonds} before bead $i-1$ is fixed at (0,0).
+One of these two beads may be a predecessor of bead $i-1$, but at least one bead is not.
 A bead $i-1$ makes a hydrogen bond with one of these two beads which is not its predecessor when it is fixed at (0,0).

### 2018-12-05 tt_theorem.tex

@@
 
-Now, we assume $S[i+2] = t_a$.
 %All $S[i+3..j]$ do not contain $t_a$; otherwise $S[i+4..j+1]$ contain $\blacksquare$.
 %Therefore, $S[i+2] = t_a$.
-According to Lemma~\ref{TTT_tunnelC_lemma}, on statement 1, 2, $\#bc(C_{i-2}) > \#bc(C_{i+2})$ and if $i \leq j - 3$, $\#bc(C_{i+2}) \geq \#bc(C_{j})$.
-Thus, binding capability of the conformation decrease per a subsequence $bt_a$ unless $w[i]$ does not consumes any bond.
-If $w[i]$ does not consumes any bond and $S[i] = t_a$, that is, $S[i-1..i+2] = bt_abt_a$, then $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
-In this case, two subsequences of $bt_a$ collaborate decreasing binding capability but eventually, two subsequences decrease two bond.
-That is, one subsequence decrease binding capability.
+Now, we assume $S[i+2] = t_a$.
+Then, we have to make sure that one troll is not double-counted.
+If $w[i]$ forms a bond, Lemmas~\ref{TTT_exit} and \ref{TTT_tunnelC_lemma} imply that binding capability decreases through this tunnel.
 
-Hence, if $S[i..j]$ contain n's subsequences of $bt$, $\#bc(C_{i-2}) - n \geq \#bc(C_{j})$
-\qed
+Assume $w[i]$ forms no bond.
+If $S[i] \in \{t_s, t_o\}$, Lemmas~\ref{TTT_exit} and \ref{TTT_tunnelC_lemma} imply $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
+Observe that the bead $w[i-1]$ is at the entrance of the previous tunnel or inside.
+It is when a bead is stabilized at the entrance of a tunnel that the troll of the tunnel decreases binding capability.
+Thus, the inequality does not rely on the troll of previous tunnel.
+If $S[i] = t_a$, Lemma~\ref{TTT_tunnelC_lemma} implies $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
+The previous tunnel must be indeed a tunnel section of type A (see Fig.~\ref{TTT_tunnelC_enter_usingBond}).
+That is, this inequality involves two tunnels but its difference 2 enables us to consider that binding capability decreases by 1 through this tunnel. \qed
+%According to Lemma~\ref{TTT_tunnelC_lemma}, on Statement 1, 2, $\#bc(C_{i-2}) > \#bc(C_{i+2})$ and if $i \leq j - 3$, $\#bc(C_{i+2}) \geq \#bc(C_{j})$.
+%Thus, binding capability of the conformation decrease per a subsequence $bt_a$ unless $w[i]$ does not consumes any bond.
+%If $w[i]$ does not consumes any bond and $S[i] = t_a$, that is, $S[i-1..i+2] = bt_abt_a$, then $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
+%In this case, two subsequences of $bt_a$ collaborate decreasing binding capability but eventually, two subsequences decrease two bond.
+%That is, one subsequence decrease binding capability.
 

### 2018-12-05 tt_theorem.tex
lateset

@@
 
-\begin{theorem}[$\delta= 1, \alpha=2$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation in $w[27n^2 + 9n + 1]$.
-\end{theorem}
-
-\begin{proof}
- We assume $w[i]$ is the first bead outside $\hexagon^n_0$
- See Fig.~\ref{fig:ttt_d2}.
- If $w[i+1]$ elongated to west and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_3$; otherwise $w[i+2]$ forms two bonds.
- If $w[i+1]$ elongated to west and $w[i+2]$ is stabilized at $p_3$, $w[i+1..]$ form a zig-zag conformation.
-  If $w[i+1]$ elongated to east and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_2$; otherwise $w[i+2]$ forms two bonds.
- If $w[i+1]$ elongated to east and $w[i+2]$ is stabilized at $p_2$, $w[i+1..]$ is zig-zag conformation.
- Thus, if $w[i]$ is the first bead outside $\hexagon^k_0$ for some $k \geq n$, $\#bc(C_i) > \#bc(C_{i+1})$ or $w[i+1..]$ form a zig-zag conformation.
-
- We assume $w[l]$ is the first bead outside $\hexagon^k_0$ and $w[m]$ is the first bead outside $\hexagon^{k+1}_0$ for some $k,l,m$ with $k<3n$.
-Let $s$ be a element of $S[l+1..m-1]$.
-If $s = b$, $s$ does not increase binding capability.
- If $s=t$, $s$ is a element of a subsequence $bt^+b$.
-This subsequence does not increase binding capability according to Theorem~\ref{TTT}.
-Thus, $\#bc(C_l) > \#bc(C_{m})$ or $w[l..]$ form a zig-zag conformation.
-
- The seed $\sigma$ provides at most $2n$ binding capability, that is, $\#bc(C_0) \leq 2n$.
- Thus,  if  $w[i]$ is the first bead outside $\hexagon^{3n}_0$, then this conformation has no hand without $w[i-1]$ and $w[i]$.
- Hence, $w[27n^2 + 9n + 1..]$ form a zig-zag conformation.
-\end{proof}
-
 \begin{figure}[tb]
@@
 
-	\node[above] at (180:1) {$p_1$};
-	\node[above] at (60:2) {$p_2$};
-	\node[above,shift=(120:1)]at (60:1) {$p_3$};
-	\node[above]at (0:1) {$p_4$};
+      \draw[dotted, shift = (60:1)] (0:0) -- (-60:1);
 
-	\draw (180:1) circle [radius=0.05];
-	\draw (60:2) circle [radius=0.05];
+	\node[above,shift=(120:1)]at (60:1) {$p$};
+
 	\draw[shift=(120:1)] (60:1) circle [radius=0.05];
@@
       \draw[->, blue, shift=(60:1)] (0:0.1) -- (0:0.9);
+       \draw[dotted, shift = (60:1)] (0:0) -- (-60:1);
 
-	\node[above] at (180:1) {$p_1$};
-	\node[above] at (60:2) {$p_2$};
-	\node[above, shift=(120:1)]at (60:1) {$p_3$};
-	\node[above]at (0:1) {$p_4$};
+	\node[above] at (60:2) {$p$};
 
-	\draw (180:1) circle [radius=0.05];
 	\draw (60:2) circle [radius=0.05];
-	\draw[shift=(120:1)] (60:1) circle [radius=0.05];
 
@@
     \end{tabular}
-    \caption{The bead $w[i]$  the first bead outside $\hexagon^n_0$: (Left) $w[i+1]$ elongated to west, (Right) $w[i+1]$ elongated to east.}
+    \caption{The moment when the transcript steps outside $\hexagon^n_0$.}
     \label{fig:ttt_d2}
@@
 \end{figure}
+
+\begin{theorem}[$\delta= 1, \alpha=2$]
+Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation in $w[27n^2 + 9n + 1]$.
+\end{theorem}
+
+\begin{proof}
+ We assume $w[i]$ is the first bead stabilized outside $\hexagon^n_0$.
+ See Fig.~\ref{fig:ttt_d2}.
+ The next bead $w[i+1]$ is to be bound for stabilization.
+ Hence, it goes to the west  or to the east (Fig.~\ref{fig:ttt_d2}).
+ Once $w[i+2]$ is stabilized at $p$, the remaining transcript folds into the zig-zag conformation.
+ In order to avoid this or nondeterminism, $w[i+2]$ must form two bonds; it thus decreases binding capability by 1.
+ Until when a bead is stabilized outside $\hexagon^{n+1}_0$, binding capability never increases because of arity being 2 and of the Tunnel Troll Theorem.
+ This means that, only at most $\#bc(C_0) \leq 2n$ times we can thus expand that hexagonal region.
+ In other words, outside $\hexagon^{3n}_0$ the transcript cannot help but fold into the zig-zag conformation. \qed
+
+% 
+% If $w[i+1]$ elongated to west and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_3$; otherwise $w[i+2]$ forms two bonds.
+% If $w[i+1]$ elongated to west and $w[i+2]$ is stabilized at $p_3$, $w[i+1..]$ form a zig-zag conformation.
+%  If $w[i+1]$ elongated to east and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_2$; otherwise $w[i+2]$ forms two bonds.
+% If $w[i+1]$ elongated to east and $w[i+2]$ is stabilized at $p_2$, $w[i+1..]$ is zig-zag conformation.
+% Thus, if $w[i]$ is the first bead outside $\hexagon^k_0$ for some $k \geq n$, $\#bc(C_i) > \#bc(C_{i+1})$ or $w[i+1..]$ form a zig-zag conformation.
+% 
+% We assume $w[l]$ is the first bead outside $\hexagon^k_0$ and $w[m]$ is the first bead outside $\hexagon^{k+1}_0$ for some $k,l,m$ with $k<3n$.
+Let $s$ be a element of $S[l+1..m-1]$.
+If $s = b$, $s$ does not increase binding capability.
+% If $s=t$, $s$ is a element of a subsequence $bt^+b$.
+This subsequence does not increase binding capability according to Theorem~\ref{TTT}.
+Thus, $\#bc(C_l) > \#bc(C_{m})$ or $w[l..]$ form a zig-zag conformation.
+% 
+% The seed $\sigma$ provides at most $2n$ binding capability, that is, $\#bc(C_0) \leq 2n$.
+% Thus,  if  $w[i]$ is the first bead outside $\hexagon^{3n}_0$, then this conformation has no hand without $w[i-1]$ and $w[i]$.
+% Hence, $w[27n^2 + 9n + 1..]$ form a zig-zag conformation.
+
+\end{proof}

### 2018-12-05 arity1.tex

@@
 \subsubsection{\ref{sec:unary}.2 \ \ $\delta = 3$\\}
-
+As before, let us assume that the last bead stabilized within $\hexagon_p^n$ is at point $(0,0)$ and the next bead is the first to be stabilized outside $\hexagon_p^n$ at point $(1,1)$.
+Depending on whether bead $i-1$ at point (0,0) has a free hand to form a bond or not, we distinguish two cases.
 \begin{enumerate}
-\item Let us discuss that a fixed bead on a side of $\hexagon_p^n$ has a free hand, and bead $i$ binds to it.
-If the most stable conformation formed by beads $i, i+1, i+2$ has only two hydrogen bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}.
-Therefore, it needs to make three hydrogen bonds to deterministically stabilize $i$.\\
+\item  Bead $i-1$ at (0,0) has a free hand.\\ If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}.
+Therefore, it needs to make three new bonds to deterministically stabilize $i$.\\
 
@@
 
-There are the five cases in which beads $i, i+1, i+2$ can have three bonds, see Fig.~\ref{fig:3bonds}.
-There are beads having a free hand at (1,0) and (-1,0) to realize (b) and (e) in Fig.~\ref{fig:3bonds} before bead $i-1$ is fixed at (0,0).
-One of these two beads may be a predecessor of bead $i-1$, but at least one bead is not.
-A bead $i-1$ makes a hydrogen bond with one of these two beads which is not its predecessor when it is fixed at (0,0).
-That is, it is impossible to put three beads having a free hand at (-1,0), (0,0) and (1,0) when a bead $i$ is fixed, and then, to realize (b) and (e) in Fig.~\ref{fig:3bonds}.
-(d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
+There are five possible cases in which beads $i, i+1, i+2$ can add three bonds, see Fig.~\ref{fig:3bonds}.
+In the cases (b) and (e) in Fig.~\ref{fig:3bonds}, there are beads having a free hand at (1,0) and (-1,0) already stabilized before bead $i-1$ is fixed at (0,0).
+One of these two beads may be a predecessor of bead $i-1$, but at least one of them is not.
+When bead $i-1$ is fixed at (0,0), it makes a bond with the one of these two beads which is not its predecessor.
+This means that it is impossible to have three beads at (-1,0), (0,0) and (1,0), each with a free hand, when bead $i$ is fixed, and consequently, cases (b) and (e) in Fig.~\ref{fig:3bonds} cannot occur.
+Case (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
 If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
 Similarly to case 1.
-in the previous section, (a) and (c) in Fig.~\ref{fig:3bonds} become nondeterministic finally when it reaches a first corner of $\hexagon_p^n$.
+in the previous section, cases (a) and (c) in Fig.~\ref{fig:3bonds} lead to nondeterministism eventually, when the transcript reaches a first corner of $\hexagon_p^n$.
 
-\item Let us discuss that bead $i$'s predecessor at (0,0) has no free hand.
-Let us assume that there is a bead at (1,0) which has a free hand.
-If there is a bead at (1,0) and beads $i, i+1, i+2$ make only two hydrogen bonds, it will become nondeterministic as in Fig.~\ref{fig:beadat(1,0)}.
-That is, beads $i, i+1, i+2$ need to make three bonds to stabilize $i$.
-If they make three hydrogen bonds, the situation is analogous to (a) and (c) in Fig.~\ref{fig:3bonds}.
-There are not any bead having a free hand at (1,0) or (-1,0) to prevent from being (a) and (c) in Fig.~\ref{fig:3bonds}.
+\item Bead $i-1$ at (0,0) does not have a free hand.\\
+(i) First, let us assume that there is a bead at (1,0) which has a free hand.
+If there is a bead at (1,0) and beads $i, i+1, i+2$ add only two bonds, we instantly get nondeterministism as in Fig.~\ref{fig:beadat(1,0)}.
+Hence, beads $i, i+1, i+2$ need to make three bonds to stabilize $i$, but if they make three hydrogen bonds, the situation is analogous to (a) and (c) in Fig.~\ref{fig:3bonds}.
+
+%There are not any bead having a free hand at (1,0) or (-1,0) to prevent from being (a) and (c) in Fig.~\ref{fig:3bonds}. 
+(ii) Now consider when there is no bead at (1,0) or there is one, but with no free hand.
 Let us discuss the moment after bead $i$ is fixed outside $\hexagon_p^n$.
-Now bead $i$ has a free hand because there are no beads having a free hand at (1,0) or (-1,0).
+Now bead $i$ has a free hand because it cannot bind to (1,0).
 If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such conformations, as in Fig.~\ref{fig:beadi2}.
 Hence, they need to form three bonds to deterministically stabilize, such as in Fig.~\ref{fig:3bonds2}.
-(a) in Fig~\ref{fig:3bonds2} becomes (a) in Fig.~\ref{fig:3bonds}.
-(b) in Fig.~\ref{fig:3bonds2} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (1,0).\\
+Case (a) in Fig.~\ref{fig:3bonds2}.
+becomes the same as case (a) in Fig.~\ref{fig:3bonds}.
+Case (b) in Fig.~\ref{fig:3bonds2} becomes nondeterministic already when bead $i$ is fixed because bead $i$ could also be fixed at (1,0).\\
 
@@
 
-It can yield only finite conformation and the length is $3n^2+n^2+1$.
+We have shown that at $\alpha=1$ and  $\delta=3$, unary oritatami systems can only fold finite length transcripts deterministically, and the length of that transcript is bounded by the size of the regular hexagon of radius $n+1$ surrounding the first bead of the transcript.
+This gives us the upper bound $|\hexagon_p^{n+1}|=3(n+1)^2+(n+1)^2+1$,  where $n$ is the length of the seed.

### 2018-12-05 paper.tex

@@
 Szil\'{a}rd Zsolt Fazekas\inst{1} \and 
-Kohei Maruyama \and
+Kohei Maruyama\thanks{Primary corresponding author (\email{k.maruyama@uec.ac.jp})} \and
 Reoto Morita \and \\
-Shinnosuke Seki\inst{2}\thanks{Corresponding author (\email{s.seki@uec.ac.jp})}}
+Shinnosuke Seki\inst{2}\thanks{Secondary corresponding author (\email{s.seki@uec.ac.jp})}
+}
 \institute{
@@
 \end{proof}
+
 \begin{theorem}\label{thm:OS_to_2dTM}
-	There is an algorithm that simulates any oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$. 
+	There is an algorithm that simulates any deterministic oritatami system $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ in time $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$. 
 \end{theorem}
@@
 \begin{corollary}
-	For fixed $\delta$ and $\alpha$, the class of problems solvable by oritatami systems $(\Sigma, R, \delta, \alpha, \sigma, w)$ is included in $\mathrm{DTIME}(n^3)$.
+	For fixed $\delta$ and $\alpha$, the class of problems solvable by deterministic oritatami systems $(\Sigma, R, \delta, \alpha, \sigma, w)$ is included in $\mathrm{DTIME}(n^3)$.
 \end{corollary}

### 2018-12-05 paper.tex
Ack
Acknowledgements for Yo-Sub added.
Intro is in a good shape
Intro is done. I may add something more, but not needed.

@@
 
-\begin{figure}[tb]
-\begin{tikzpicture}
-
-\node (origin) at (0, 0) {};
-
-\draw[-latex] (origin) -- ++(0:5) node[below] {$\delta$}; 
-\node at (2, -0.2) {1};
-\node at (4, -0.2) {2 and 3};
-\draw[-latex] (origin) -- ++(90:5) node[left] {$\alpha$}; 
-\node at (-0.2, 1) {1};
-\node at (-0.2, 2) {2};
-\node at (-0.2, 3) {3};
-\node at (-0.2, 4) {4};
-
-%Results
-\node at (2, 4) {$3n(n+1)+1$};
-\node at (2, 3) {$4n+14$};
-\node at (2, 2) {$9n(3n+1)+1$};
-\node at (2, 1) {$10n$ \cite{DHOPRSST2018}};
-
-\node at (4, 1) {$O(n^2)$};
-
-\end{tikzpicture}
-\caption{Summary of the results.}
-\label{fig:summary}
-\end{figure}
-
 Closely related is the question of where not to look for universal systems, i.e., what are the limitations of simple oritatami system. 
@@
 
-Results on this problem are summarized in Fig.~\ref{fig:summary}.
+\begin{figure}[tb]
+  \begin{center}
+    \begin{tikzpicture}
+      \fill (0,0) circle[radius = 0.1];
+      \fill (1.5,0) circle[radius = 0.1];
+      \fill (3,0) circle[radius = 0.1];
+      \fill (4.5,0) circle[radius = 0.1];
+      \fill (6,0) circle[radius = 0.1];
+
+      \draw[dashed] (0,0)--(1.5,0);
+      \draw[dashed] (1.5,0)--(3,0);
+      \draw[dashed] (3,0)--(4.5,0);
+      \draw[dashed] (4.5,0)--(6,0);
+      \draw[->] (0,0)--(60:0.75);
+      \draw[->] (1.5,0)--++(60:0.75);
+      \draw[->] (3,0)--++(60:0.75);
+      \draw[->] (4.5,0)--++(60:0.75);
+      \draw (0,0)--(60:1.5);
+      \draw (1.5,0)--++(60:1.5);
+      \draw (3,0)--++(60:1.5);
+      \draw (4.5,0)--++(60:1.5);
+
+      \begin{scope}[shift=(60:1.5)]
+        \fill (0,0) circle[radius = 0.1];
+        \fill (1.5,0) circle[radius = 0.1];
+        \fill (3,0) circle[radius = 0.1];
+        \fill (4.5,0) circle[radius = 0.1];
+        \draw[dashed] (0,0)--(1.5,0);
+        \draw[dashed] (1.5,0)--(3,0);
+        \draw[dashed] (3,0)--(4.5,0);
+        \draw[->] (0,0)--(-60:0.75);
+        \draw[->] (1.5,0)--++(-60:0.75);
+        \draw[->] (3,0)--++(-60:0.75);
+        \draw[->] (4.5,0)--++(-60:0.75);
+
+        \draw (0,0)--(-60:1.5);
+        \draw (1.5,0)--++(-60:1.5);
+        \draw (3,0)--++(-60:1.5);
+        \draw (4.5,0)--++(-60:1.5);
+      \end{scope}
+
+    \end{tikzpicture}
+    \caption{The zig-zag conformation. This is the only one infinite conformation foldable deterministically by an unary oritatami ssytem at delay 1 and arity 2.}
+    \label{TTT_zigzag}
+  \end{center}
+\end{figure}
+
+\begin{figure}[tb]
+\centering
+\begin{tikzpicture}
+
+\node (origin) at (0, 0) {};
+
+\draw[-latex] (origin) -- ++(0:10) node[below] {$\delta$}; 
+\node at (2, -0.2) {1};
+\node at (4, -0.2) {2 and 3};
+\node at (6, -0.2) {4 and larger}; 
+\draw[-latex] (origin) -- ++(90:5) node[left] {$\alpha$}; 
+\node at (-0.2, 1) {1};
+\node at (-0.2, 2) {2};
+\node at (-0.2, 3) {3};
+\node at (-0.2, 4) {4};
+
+%Results
+\node at (2, 4) {$3n(n{+}1){+}1$};
+\node at (2, 3) {$4n{+}14$};
+\node at (2, 2.2) {$\infty$ but zigzag after};
+\node at (2, 1.8) {$(27n^2{+}9n{+}1)$-th bead};
+\node at (2, 1) {$10n$ \cite{DHOPRSST2018}};
+
+\node at (4, 1) {$3n^2{+}4n{+}1$};
+
+\end{tikzpicture}
+\caption{Upper bounds on the length of a conformation foldable by a deterministic unary oritatami system at delay $\delta$ and arity $\alpha$.
+At any combination of delay and arity without anything written, no upper bound is known yet.
+}
+\label{fig:summary}
+\end{figure}
+In this paper, we will solve this problem partially at arity 1 in Sect.~\ref{sect:arity1} and completely at delay 1 in Sect.~\ref{sect:delay1}. 
+Concretely speaking, we will prove that at arity 1 and delay 2 or 3, the upper bound is $(3n+1)(n+1)$. 
+Upper bounds for longer delays remain open. 
+At delay 1, we will provide a quadratic upper bound $3n(n+1)+1$ for the case of arity being 4, while a linear upper bound $4n+14$ for arity 3. 
+At the delay 1 and arity 2, one infinite structure turns out to be foldable deterministically, which is the zigzag conformation shown in Fig.~\ref{TTT_zigzag}. 
+These results as well as known upper bounds are summarized in Fig.~\ref{fig:summary}. 
+As shown at the end of Sect.~\ref{sec:preliminaries}, the stabilization of first $t$ beads of transcript by a determinisitc oritatami system can be simulated by a deterministic Turing machine within $t^3$ steps (Corollary~\ref{cor:DTIME3}).
+Thus, the above mentioned upper bounds show that at delay 1 and arity 1, 3, or 4, or at delay 2 or 3 and arity 1, the class of deterministic unary oritatami systems is not Turing universal. 
+The Turing universal oritatami system by Geary et al. \cite{GeMeScSe2018} employs more than 500 types of beads. 
+Thus, this weakness result is not surprising at all. 
+The unary oritatami system might not be practical very much, though one bead may abstarct an oligonucleotide (a short sequence of nucleotides), and in that case, unary transcript can be a repetitive but nonunary sequence, which is not so unrealistic in experiments (see \cite{GearyAndersen2014}).
+Nevertheless, this paper makes a first considerable step towards the characterization of non-Turing-universal oritatami systems.
 
@@
 
-\begin{corollary}
-	For fixed $\delta$ and $\alpha$, the class of problems solvable by deterministic oritatami systems $(\Sigma, R, \delta, \alpha, \sigma, w)$ is included in $\mathrm{DTIME}(n^3)$.
+\begin{corollary}\label{cor:DTIME3}
+	For fixed $\delta$, the class of problems solvable by deterministic oritatami systems $(\Sigma, R, \delta, \alpha, \sigma, w)$ is included in $\mathrm{DTIME}(|w|^3)$.
 \end{corollary}
@@
 
-\section{Case of arity $1$}
+\section{Case of arity $1$}\label{sect:arity1}
 
@@
 
-\section{Case of delay $1$}
+\section{Case of delay $1$}\label{sect:delay1}
 \input{tt_intro}
 \input{tt_theorem}
+
+\subsection*{Acknowledgements}
+We thank Yo-Sub Han for his valuable comments on the contents of this paper.
 

### 2018-12-05 tt_theorem.tex
latest
12/5 evening

@@
 See Fig.\ref{TTT_tunnel_direction}.
-$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section of type $S$ or $O$.
+$S[i+2] \in \{ t_s, t_o \} $ means that $w[i+2]$ is stabilized by a tunnel section of type S or O.
 Thus,  its predecessor $w[i+1]$ must be inside the tunnel section, that is, $n_1$ and $n_2$ must be occupied.
@@
             \draw[->, blue] (60:0.9)--(60:0.1);
-            \draw[->, blue] (0:0.1)--(0:1.1);
+            \draw[->, blue] (0:0.1)--(0:0.9);
 
@@
 	See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
-	Consider the case when $w[i]$ is stabilized by a tunnel section of type $S$ or $O$.
-	As prove in Lemma~\ref{TTT_exit}, $\#bc(C_{i-2}) \geq \#bc(C_{i})$.%the increase of binding capability by $w[i-1]$ and $w[i]$ is at most 0.
-	The bead $w[i]$ leaves two free hand, it will be used by $w[i+2]$, and hence, $w[i+2]$ does not increase the binding capability.
+	Consider the case when $w[i]$ is stabilized by a tunnel section of type S or O.
+	As prove in Lemma~\ref{TTT_exit}, $\#bc(C_{i-2}) \geq \#bc(C_{i})$.	The bead $w[i]$ leaves two free hand, it will be used by $w[i+2]$, and hence, $w[i+2]$ does not increase the binding capability.
 	Thus, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
@@
 	Finally, we prove Statement 3.
-	%Consider the case when $w[i]$ is stabilized by a tunnel section of type $A$ and $w[i]$ does not consumes any bond.
 	In order for $w[i]$ not to bind, $w[i-2]$ must have already used up its hands.
-	% The bead $w[i-2]$ must consume two bonds ; otherwise $w[i-2]$'s hands is used by $w[i]$.
 	The bead $w[i-1]$ consumes one hand and provides nothing.
@@
           \node[below] at (-120:1) {$w[i+2]$};
-
-          \node[right] at (120:1) {$n_3$};
-          \node[right] at (60:1) {$n_2$};
-          \node[right] at (0:1) {$n_1$};
-
           \begin{scope}[shift=(-120:1)]
@@
 
-          \node[right] at (120:1) {$n_3$};
-          \node[right] at (60:1) {$n_2$};
-          \node[right] at (0:1) {$n_1$};
-
           \begin{scope}[shift=(-120:1)]
@@
         \end{tabular}
-    \caption{Case of $S[i] = t_a$ and $S[i+2] = t_a$: (Right) Moreover $w[i]$ does not consume any bond.}
+    \caption{The bead $w[i+2]$ is stabilized by a tunnel of type A. (Right) Moreover $S[i] = t_a$.}
     \label{TTT_tunnelC_enter_usingBond}
@@
     \end{tikzpicture}
-    \caption{The first bead out of $\hexagon_{w[-n+1]}^n$}
+    \caption{The first bead out of $\hexagon_{O}^n$}
     \label{TTT_a4_first}
@@
 \end{theorem}
-
-%Both $n_3$ and $n_4$ are occupied because $S[i] = t$ or $t^\times$.
-%Suppose $w[i]$ were stabilized without any bond.
-%Then, all neighbors of $n_3$ must be occupied as long as the bead at $n_3$ is not singular; otherwise, a bead at $n_3$ would be capable of forming a bond with $w[i]$.
-%That is, $n_1$ is occupied.
-%We can continue this argument in clockwise manner to fill the neighbors of $w[i]$ until a singular bead is encountered, if any.
-%If needed, the same argument is applied starting from $n_4$ in counter-clockwise manner.
-%Thus, all neighbors of $w[i]$ must be occupied but then $S[i+1] = \blacksquare$, contradiction. \qed
 
@@
     \begin{tikzpicture}
+      \draw[white] (0:0)-- (60:2);
 
@@
     \end{tabular}
-    \caption{The moment when the transcript steps outside $\hexagon^n_0$.}
+    \caption{The moment when the transcript steps outside $\hexagon^n_O$.}
     \label{fig:ttt_d2}
@@
 \begin{proof}
- We assume $w[i]$ is the first bead stabilized outside $\hexagon^n_0$.
+ We assume $w[i]$ is the first bead stabilized outside $\hexagon^n_O$.
  See Fig.~\ref{fig:ttt_d2}.
@@
  In order to avoid this or nondeterminism, $w[i+2]$ must form two bonds; it thus decreases binding capability by 1.
- Until when a bead is stabilized outside $\hexagon^{n+1}_0$, binding capability never increases because of arity being 2 and of the Tunnel Troll Theorem.
+ Until when a bead is stabilized outside $\hexagon^{n+1}_O$, binding capability never increases because of arity being 2 and of the Tunnel Troll Theorem.
  This means that, only at most $\#bc(C_0) \leq 2n$ times we can thus expand that hexagonal region.
- In other words, outside $\hexagon^{3n}_0$ the transcript cannot help but fold into the zig-zag conformation. \qed
-
-% 
-% If $w[i+1]$ elongated to west and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_3$; otherwise $w[i+2]$ forms two bonds.
-% If $w[i+1]$ elongated to west and $w[i+2]$ is stabilized at $p_3$, $w[i+1..]$ form a zig-zag conformation.
-%  If $w[i+1]$ elongated to east and $w[i+2]$ forms one bond, then $w[i+2]$ is stabilized at $p_2$; otherwise $w[i+2]$ forms two bonds.
-% If $w[i+1]$ elongated to east and $w[i+2]$ is stabilized at $p_2$, $w[i+1..]$ is zig-zag conformation.
-% Thus, if $w[i]$ is the first bead outside $\hexagon^k_0$ for some $k \geq n$, $\#bc(C_i) > \#bc(C_{i+1})$ or $w[i+1..]$ form a zig-zag conformation.
-% 
-% We assume $w[l]$ is the first bead outside $\hexagon^k_0$ and $w[m]$ is the first bead outside $\hexagon^{k+1}_0$ for some $k,l,m$ with $k<3n$.
-Let $s$ be a element of $S[l+1..m-1]$.
-If $s = b$, $s$ does not increase binding capability.
-% If $s=t$, $s$ is a element of a subsequence $bt^+b$.
-This subsequence does not increase binding capability according to Theorem~\ref{TTT}.
-Thus, $\#bc(C_l) > \#bc(C_{m})$ or $w[l..]$ form a zig-zag conformation.
-% 
-% The seed $\sigma$ provides at most $2n$ binding capability, that is, $\#bc(C_0) \leq 2n$.
-% Thus,  if  $w[i]$ is the first bead outside $\hexagon^{3n}_0$, then this conformation has no hand without $w[i-1]$ and $w[i]$.
-% Hence, $w[27n^2 + 9n + 1..]$ form a zig-zag conformation.
+ In other words, outside $\hexagon^{3n}_O$ the transcript cannot help but fold into the zig-zag conformation. \qed
 

### 2018-12-05 tt_intro.tex
fig.16..
Jordan curve added
I added an explanation of Jordan curve theorem in Section 3.

@@
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}
-      \fill (0,0) circle[radius = 0.1];
-      \fill (1.5,0) circle[radius = 0.1];
-      \fill (3,0) circle[radius = 0.1];
-      \fill (4.5,0) circle[radius = 0.1];
-      \fill (6,0) circle[radius = 0.1];
-
-      \draw[dashed] (0,0)--(1.5,0);
-      \draw[dashed] (1.5,0)--(3,0);
-      \draw[dashed] (3,0)--(4.5,0);
-      \draw[dashed] (4.5,0)--(6,0);
-      \draw[->] (0,0)--(60:0.75);
-      \draw[->] (1.5,0)--++(60:0.75);
-      \draw[->] (3,0)--++(60:0.75);
-      \draw[->] (4.5,0)--++(60:0.75);
-      \draw (0,0)--(60:1.5);
-      \draw (1.5,0)--++(60:1.5);
-      \draw (3,0)--++(60:1.5);
-      \draw (4.5,0)--++(60:1.5);
-
-      \begin{scope}[shift=(60:1.5)]
-        \fill (0,0) circle[radius = 0.1];
-        \fill (1.5,0) circle[radius = 0.1];
-        \fill (3,0) circle[radius = 0.1];
-        \fill (4.5,0) circle[radius = 0.1];
-        \draw[dashed] (0,0)--(1.5,0);
-        \draw[dashed] (1.5,0)--(3,0);
-        \draw[dashed] (3,0)--(4.5,0);
-        \draw[->] (0,0)--(-60:0.75);
-        \draw[->] (1.5,0)--++(-60:0.75);
-        \draw[->] (3,0)--++(-60:0.75);
-        \draw[->] (4.5,0)--++(-60:0.75);
-
-        \draw (0,0)--(-60:1.5);
-        \draw (1.5,0)--++(-60:1.5);
-        \draw (3,0)--++(-60:1.5);
-        \draw (4.5,0)--++(-60:1.5);
-      \end{scope}
-
-    \end{tikzpicture}
-    \caption{zig-zag conformation}
-    \label{TTT_zigzag}
-  \end{center}
-\end{figure}
-
 In this section, we consider Problem~\ref{prob:det_unary_length} at delay 1.
@@
           \begin{scope}[xshift=2cm, yshift=2cm]
+
+            \draw[white] (60:1) -- (0:0);
+            \draw[white] (-60:1) -- (0:0);
             \draw(0,0) circle [radius=0.05];
@@
           \begin{scope}[xshift=2cm, yshift=2cm]
+            \draw[white] (60:1) -- (0:0);
+            \draw[white] (-60:1) -- (0:0);
             \draw(0,0) circle [radius=0.05];
@@
 
+\begin{figure}[tb]
+\centering
+\includegraphics[width=0.5\linewidth]{Fig/jordan_curve.png}
+\caption{}
+\label{fig:Jordan}
+\end{figure}
+
 %We say that point $p$ is reachable from a conformation $C$ if there exists a directed path $P^\prime$ from the last point of $C$ that does not cross the path of $C$. 
-We say that a neighbor of a point $p$ is reachable from a conformation $C$ if there exists an elongation of $C$ in which a bead occupies the neighbor and it binds with a bead at $p$. 
+We say that a neighbor of a point $p$ is \textit{reachable} from a conformation $C$ if there exists an elongation of $C$ in which a bead occupies the neighbor and it binds with a bead at $p$. 
+For example, in Fig.~\ref{fig:Jordan}, the transcript $w$ is about to step into a tunnel. 
+The wall beads $w[i-\ell]$ and $w[i-k]$ are both older than the bead at the entrance, $w[i]$. 
+Even if $w[i]$ leaves a free neighbor, the neighbor is not reachable because the the path of a conformation must be non-self-intersecting, and its subpath between these two wall beads divides the plane into two regions, one of which includes the entrance of the tunnel and the other of which includes the exit (Jordan curve theorem \cite{Hales2007}).
 Taking this reachability into account, we define the \textit{binding capability} of a conformation as the number of free bonds of its beads available geometrically for elongations of $C$.

### 2018-12-05 arity1.tex
Added theorem and lemmas to delay 2 arity 1

@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{./Fig/CI_Numbers}
+	\includegraphics[width=0.8\linewidth]{./Fig/CI_Numbers}
 	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. }
@@
 
+In subsections~\ref{sec:unary}.1 and \ref{sec:unary}.2, we will argue that unary systems at arity $1$ and delay $2$ and $3$, respectively, cannot fold infinite transcripts deterministically.
+As we will see, in fact, the length of transcripts deterministically foldable by these systems has an upper bound quadratic in the length of the seed.
+The main result is the following theorem, which is a direct consequence of Lemma x and Lemma y from the next two subsections.
+\begin{theorem}[$\delta\in\{ 2,3\}, \alpha = 1$]\label{thm:d23a1}
+	Let $\Xi$ be a unary oritatami system of $\delta \in \{2,3\}$ and $\alpha = 1$. Starting with a seed of length $n$, $\Xi$ can yield only finite structures of size at most $3n^2+4n+2$.
+\end{theorem}
+
+Let us fix some common starting points for the next two subsections.
 Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|+1$.
@@
 Let this be the $i$th bead of the transcript.
-Without loss of generality, we can translate the origin $(0,0)$ to the coordinates of bead $i-1$ (which is still in $\hexagon_p^n$), and we can assume that the bead outside the hexagon is fixed at $(1,1)$ (see Fig.~\ref{fig:hexagonOut}).
+Without loss of generality, we can translate the origin $(0,0)$ to the coordinates of bead $i-1$ (which is still in $\hexagon_p^n$), and we can assume that bead $i$ is fixed at $(1,1)$ (see Fig.~\ref{fig:hexagonOut}).
 \begin{figure}
@@
 \subsubsection{\ref{sec:unary}.1 \ \ $\delta = 2$\\}
+\begin{lemma}[$\delta=2, \alpha =1$]\label{lem:d2a1}
+	Let $\Xi$ be a unary oritatami system of $\delta=2$ and $\alpha = 1$. Starting with a seed of length $n$, $\Xi$ can yield only finite structures of size at most $3n^2+4n+2$.
+\end{lemma}
+\begin{proof}
 
@@
 This is analogous to case 1.
-below.%as in Fig.~\ref{fig:hexagonOut1}.
+below, with the only difference being that the bond between (1,1) and (1,0) is missing.%as in Fig.~\ref{fig:hexagonOut1}.
 	\begin{figure}
@@
 This means that there is a bead at $(1,0)$, which bonds to bead $i$, otherwise there are other conformations in which beads $i$ and $i+1$ add one bond to the conformation, making the behavior nondeterministic.
-
+Because of the above, we need only consider the case when $i$ binds to a bead at (1,0).
 The next bead, $i+1$, can be fixed at $(2,1)$ or at $(0,1)$ as all other possibilities result in nondeterministic behavior immediately, so we have two cases.
@@
 \begin{enumerate}
-	\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$.
+	\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$ (see Fig.~\ref{fig:hexagonOut2}).
 Now consider bead $i+2$.
@@
 The only possibility is that there is a bead at $(3,0)$ and $i+2$ can bond with it when placed at $(3,1)$.
-We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by active beads, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$.
-Such an $m$ exists, and it is not greater than $n$.
+We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by beads with free hands, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$.
+Such an $m$ exists, and it is not greater than $n$, because those beads are all stabilized along the same side of $\hexagon_p^n$.
 Then, bead $i+\ell$ is fixed at $(\ell+1,1)$ and bonds with $(\ell+1,0)$.
 However, bead $i+2+m$ cannot be fixed anywhere, because $i+2+m$ and $i+3+m$ can only add one bond to the conformation, and that is possible either with $i+2+m \rightarrow (2+m,1)$, $i+3+m \rightarrow (3+m,1)$ or with $i+2+m \rightarrow (2+m,2)$, $i+3+m \rightarrow (2+m,1)$.
-	\begin{figure}
+Intuitively, when we reach a corner of the hexagon $\hexagon_p^n$, the next bead of the transcript cannot deterministically stabilize, as depicted in Fig.~\ref{fig:hexagonOut2}.
+In this case, the size of the transcript which was deterministically stabilized is bounded by the size of $\hexagon_p^n$ plus the length of one side of $\hexagon_p^{n+1}$, so by $(3n^2+3n+1)+(n+1)=3n^2+4n+2$.
+	\begin{figure}[h]
 		\centering
@@
 		\caption{When bead $i+2+m$ is fixed}
-		\label{fig:hexagonout2}
+		\label{fig:hexagonOut2}
 	\end{figure}
@@
 	\begin{enumerate}
-		\item there is an inactive bead at $(-1,0)$ and an active one at $(-2,0)$. This case is symmetrical to (1).
+		\item there is an inactive bead at $(-1,0)$ and one with a free hand one at $(-2,0)$. This case is symmetrical to (1).
 		\item there is no bead at $(-1,0)$, bead $i+1$ can bond with bead $i-1$ at $(0,0)$ and the bead $i+2$ can be placed at $(-1,0)$ where it can bond with $(-2,0)$, $(-2,-1)$ or $(-1,-1)$.
-This leads to nondeterminism, because bead $i$ at $(-1,0)$ and bead $i+1$ at $(0,1)$ has two bonds, just as the original conformation.
+This leads to nondeterminism, because placing bead $i$ at $(-1,0)$ and bead $i+1$ at $(0,1)$ would yield two bonds, just as the original conformation.
 		\item there is a bead at $(-1,0)$ and bead $i+1$ can bond with that or with bead $i-1$ at $(0,0)$.
@@
 	\caption{When bead $i+1$ is fixed at (0,1)}
-	\label{fig:hexagonOut2}
+	\label{fig:hexagonOut3}
 \end{figure}
 
+Case 2.(a) gives the same upper bound as case 1. Cases 2.(b)-(c) give the smaller upper bound $|\hexagon_p^n|+1$, thereby concluding the proof.
+\end{proof}
+
 \subsubsection{\ref{sec:unary}.2 \ \ $\delta = 3$\\}
+
+\begin{lemma}[$\delta=3, \alpha =1$]\label{lem:d3a1}
+	Let $\Xi$ be a unary oritatami system of $\delta=3$ and $\alpha = 1$. Starting with a seed of length $n$, $\Xi$ can yield only finite structures of size at most $3n^2+4n+2$.
+\end{lemma}
+\begin{proof}
+We will argue similarly to the $\delta=2$ case: when we stabilize beads outside $\hexagon_p^n$, we can only do so at points right next to one of the sides and even there only until we reach a corner.
+This yields the upper bound immediately.
+
 As before, let us assume that the last bead stabilized within $\hexagon_p^n$ is at point $(0,0)$ and the next bead is the first to be stabilized outside $\hexagon_p^n$ at point $(1,1)$.
@@
 
-We have shown that at $\alpha=1$ and  $\delta=3$, unary oritatami systems can only fold finite length transcripts deterministically, and the length of that transcript is bounded by the size of the regular hexagon of radius $n+1$ surrounding the first bead of the transcript.
-This gives us the upper bound $|\hexagon_p^{n+1}|=3(n+1)^2+(n+1)^2+1$,  where $n$ is the length of the seed.
+\end{proof}
+
+We have shown that at $\alpha=1$ and  $\delta\in\{2,3\}$, unary oritatami systems can only fold finite length transcripts deterministically, and the length of that transcript is bounded by the size of the regular hexagon of radius $n$ plus the length of one side of the surrounding hexagon.
+This gives us the upper bound $|\hexagon_p^{n}|+(n+1)=3n^2+4n+2$,  where $n$ is the length of the seed, concluding the proof of Theorem~\ref{thm:d23a1}.

### 2018-12-05 tt_theorem.tex
12/5 evening..

@@
 If $S[i] = t_a$, Lemma~\ref{TTT_tunnelC_lemma} implies $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
-The previous tunnel must be indeed a tunnel section of type A (see Fig.~\ref{TTT_tunnelC_enter_usingBond}).
-That is, this inequality involves two tunnels but its difference 2 enables us to consider that binding capability decreases by 1 through this tunnel. \qed
-%According to Lemma~\ref{TTT_tunnelC_lemma}, on Statement 1, 2, $\#bc(C_{i-2}) > \#bc(C_{i+2})$ and if $i \leq j - 3$, $\#bc(C_{i+2}) \geq \#bc(C_{j})$.
-%Thus, binding capability of the conformation decrease per a subsequence $bt_a$ unless $w[i]$ does not consumes any bond.
-%If $w[i]$ does not consumes any bond and $S[i] = t_a$, that is, $S[i-1..i+2] = bt_abt_a$, then $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
-%In this case, two subsequences of $bt_a$ collaborate decreasing binding capability but eventually, two subsequences decrease two bond.
-%That is, one subsequence decrease binding capability.
+%The previous tunnel must be indeed a tunnel section of type A (see Fig.~\ref{TTT_tunnelC_enter_usingBond}).
+This inequality involves two tunnels but its difference 2 enables us to consider that binding capability decreases by 1 through this tunnel. \qed
 
@@
     \begin{tikzpicture}
-      \draw[white] (0:0)-- (60:2);
+      \draw[white] (60:2) circle [radius=0.05];
+      \node[above, white] at (60:2) {$n_adj$};
 

### 2018-12-05 tt_theorem.tex
12/5 evening...

@@
 
-	Finally, we prove Statement 3.
+	We finalize this proof by showing Statement 3.
 	In order for $w[i]$ not to bind, $w[i-2]$ must have already used up its hands.
@@
 
-\proof{Proof of Tunnel Troll Theorem}
+Now we are ready to prove the Tunnel Troll Theorem.
 
+\begin{proof}%{Proof of Tunnel Troll Theorem}
 Let us first consider cases of $\delta \geq 3, \alpha = 1$. 
@@
 This inequality involves two tunnels but its difference 2 enables us to consider that binding capability decreases by 1 through this tunnel. \qed
+\end{proof}
 
@@
 \begin{theorem}[$\delta = 1, \alpha = 4$]
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite conformation of length is $3n^2  + 3n + 1$.
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite conformation of length $3n^2  + 3n + 1$.
 \end{theorem}
@@
 \begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length is $4n + 14$.
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length $4n + 14$.
 \end{theorem}
@@
 \begin{theorem}[$\delta= 1, \alpha=2$]
-Let $\Xi$ be a unary oritatami system of $\delta = 1, \alpha = 2$. It can yield infinite structures but they are only zig-zag conformation in $w[27n^2 + 9n + 1]$.
+Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 2$.
+It can yield an infinite structure, but the transcript folds into the zig-zag conformation after its ($27n^2 + 9n +1$)-th bead.
 \end{theorem}

### 2018-12-05 arity1.tex
made the section a bit more concise

@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{./Fig/CI_Numbers}
+	\includegraphics[width=0.7\linewidth]{./Fig/CI_Numbers}
 	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. }
@@
 
-\begin{enumerate}
-	\item bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$ (see Fig.~\ref{fig:hexagonOut2}).
+%\begin{enumerate}
+\noindent\textbf{Case 1.} bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$ (see Fig.~\ref{fig:hexagonOut2}).
 Now consider bead $i+2$.
@@
 
-	\item bead $i+1$ is fixed at $(0,1)$. This is only possible if
-	\begin{enumerate}
+\vspace{0.2cm}
+
+\noindent\textbf{Case 2.} bead $i+1$ is fixed at $(0,1)$. This is only possible if
+	\begin{enumerate}[label=(\alph*)]
 		\item there is an inactive bead at $(-1,0)$ and one with a free hand one at $(-2,0)$. This case is symmetrical to (1).
@@
 	\end{enumerate}
-\end{enumerate}
+%\end{enumerate}
 
@@
 Depending on whether bead $i-1$ at point (0,0) has a free hand to form a bond or not, we distinguish two cases.
-\begin{enumerate}
-\item  Bead $i-1$ at (0,0) has a free hand.\\ If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}.
+%\begin{enumerate}
+\noindent\textbf{Case 1.}  Bead $i-1$ at (0,0) has a free hand.\\ If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}.
 Therefore, it needs to make three new bonds to deterministically stabilize $i$.\\
@@
 
-\item Bead $i-1$ at (0,0) does not have a free hand.\\
+\noindent\textbf{Case 2.} Bead $i-1$ at (0,0) does not have a free hand.\\
 (i) First, let us assume that there is a bead at (1,0) which has a free hand.
@@
 \begin{figure}
+	\begin{minipage}{.45\textwidth}
+
   \begin{center}
@@
     \end{tabular}
-    \caption{Two conformations when a bead at (1,0) has a free hand}
+    \caption{Two conformations when a bead at (1,0) has a free hand.}
     \label{fig:beadat(1,0)}
   \end{center}
-\end{figure}
-
-\begin{figure}
+	\end{minipage}%	
+\hspace{1cm}\begin{minipage}{.45\textwidth}
 		\begin{center}
@@
 		\end{center}
+	\end{minipage}
+
 \end{figure}
+
+%
+%\begin{figure}
+%  \begin{center}
+%    \begin{tabular}{cc}
+%      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
+%        \fill (0.0, 0.0) circle [radius = 0.1];
+%        \fill (0.5, 0.866) circle [radius = 0.1];
+%        \fill (-0.5, 0.866) circle [radius = 0.1];
+%        \fill (0.0, 1.732) circle [radius = 0.1];
+%        \fill (0.0, 0.0) node [below] {$(1, 1)$};
+%        \draw (0.0, 0.0) -- (0.5, 0.866);
+%        \draw (0.5, 0.866) -- (-0.5, 0.866);
+%        \draw (0.0, 1.732) -- (-0.5, 0.866);
+%        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
+%        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
+%      \end{tikzpicture}
+%
+%      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
+%        \fill (0.0, 0.0) circle [radius = 0.1];
+%        \fill (-0.5, 0.866) circle [radius = 0.1];
+%        \fill (0.5, 0.866) circle [radius = 0.1];
+%        \fill (0.0, 1.732) circle [radius = 0.1];
+%        \fill (0.0, 0.0) node [below] {$(1, 1)$};
+%        \draw (0.0, 0.0) -- (-0.5, 0.866);
+%        \draw (-0.5, 0.866) -- (0.5, 0.866);
+%        \draw (0.0, 1.732) -- (0.5, 0.866);
+%        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
+%        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
+%      \end{tikzpicture}
+%
+%    \end{tabular}
+%    \caption{Two conformations when a bead $i$ at (1,1) has a free hand}
+%    \label{fig:beadi2}
+%  \end{center}
+%\end{figure}
 
@@
 
-\end{enumerate}
+%\end{enumerate}
 

### 2018-12-05 tt_theorem.tex
12/5 evening....

@@
 
-In order to prove this Tunnel Troll Theorem, we use the following three lemmas.
+In order to prove this theorem, we use the following three lemmas.
 %Let us introduce some lemmas for proving Tunnel Troll Theorem.
@@
 \label{TTT_entrance_Tab}
-Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$, arity $\alpha =2$. 
+Let $\Xi$ be a deterministic unary oritatami system at delay $\delta = 1$ and arity $\alpha =2$. 
 Assume $\Xi$ stabilizes the transcript until $w[i-1]$. If $S[i+1] = b$ and $S[i+2] \in \{ t_s, t_o \} $, then $\#bc(C_{i-1}) > \#bc(C_{i})$.
@@
 \label{TTT_tunnelC_lemma}
-Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
+Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$ and arity $\alpha = 2$.
 If $S[i+2] = t_a$, the following statements hold.
@@
 
-\subsection{On structures provided by a unary and $\delta = 1$ oritatami system}
+\subsection{Upper bounds on the length of conformation foldable deterministically at delay $\delta = 1$.}
 

### 2018-12-05 tt_intro.tex
Technical commit

@@
 In this section, we consider Problem~\ref{prob:det_unary_length} at delay 1. 
-Our result, cases of arity 1 and 3 can only yield finite structures of size $O (n)$, and cases of arity 4 and more can only yield finite structures which is size of $O (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.~\ref{TTT_zigzag}.
-
-%In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 2 deterministically and moreover that the only infinite conformations which its oritatami system can yield is only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.
-
 Let $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ be a deterministic oritatami system of delay 1. 
@@
 \includegraphics[width=0.5\linewidth]{Fig/jordan_curve.png}
-\caption{}
+\caption{A tunnel divides the world into two. 
+Getting through the tunnel leads us to another world. 
+}
 \label{fig:Jordan}

### 2018-12-05 arity1.tex
Add files via upload

@@
 As before, let us assume that the last bead stabilized within $\hexagon_p^n$ is at point $(0,0)$ and the next bead is the first to be stabilized outside $\hexagon_p^n$ at point $(1,1)$.
-Depending on whether bead $i-1$ at point (0,0) has a free hand to form a bond or not, we distinguish two cases.
+Depending on whether bead $i-1$ at point (0,0) has a free hand to form a bond or not, we distinguish two cases.\\
 %\begin{enumerate}
-\noindent\textbf{Case 1.}  Bead $i-1$ at (0,0) has a free hand.\\ If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities, see Fig.~\ref{fig:beadi}.
+\noindent\textbf{Case 1.}  Bead $i-1$ at (0,0) has a free hand.\\ If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities (see Fig.~\ref{fig:beadi2}, except it starts from (0,0) not (1,1)).
 Therefore, it needs to make three new bonds to deterministically stabilize $i$.\\
 
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{cc}
-      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-        \fill (0.0, 0.0) circle [radius = 0.1];
-        \fill (0.5, 0.866) circle [radius = 0.1];
-        \fill (-0.5, 0.866) circle [radius = 0.1];
-        \fill (0.0, 1.732) circle [radius = 0.1];
-        \fill (0.0, 0.0) node [below] {$(0, 0)$};
-        \draw (0.0, 0.0) -- (0.5, 0.866);
-        \draw (0.5, 0.866) -- (-0.5, 0.866);
-        \draw (0.0, 1.732) -- (-0.5, 0.866);
-        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
-        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
-      \end{tikzpicture}
-
-      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-        \fill (0.0, 0.0) circle [radius = 0.1];
-        \fill (-0.5, 0.866) circle [radius = 0.1];
-        \fill (0.5, 0.866) circle [radius = 0.1];
-        \fill (0.0, 1.732) circle [radius = 0.1];
-        \fill (0.0, 0.0) node [below] {$(0, 0)$};
-        \draw (0.0, 0.0) -- (-0.5, 0.866);
-        \draw (-0.5, 0.866) -- (0.5, 0.866);
-        \draw (0.0, 1.732) -- (0.5, 0.866);
-        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
-        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
-      \end{tikzpicture}
-
-    \end{tabular}
-    \caption{Two conformations when bead $i-1$ at (0,0) has a free hand}
-    \label{fig:beadi}
-  \end{center}
-\end{figure}
+%\begin{figure}
+%  \begin{center}
+%    \begin{tabular}{cc}
+%      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
+%        \fill (0.0, 0.0) circle [radius = 0.1];
+%        \fill (0.5, 0.866) circle [radius = 0.1];
+%        \fill (-0.5, 0.866) circle [radius = 0.1];
+%        \fill (0.0, 1.732) circle [radius = 0.1];
+%        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+%        \draw (0.0, 0.0) -- (0.5, 0.866);
+%        \draw (0.5, 0.866) -- (-0.5, 0.866);
+%        \draw (0.0, 1.732) -- (-0.5, 0.866);
+%        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
+%        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
+%      \end{tikzpicture}
+%
+%      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
+%        \fill (0.0, 0.0) circle [radius = 0.1];
+%        \fill (-0.5, 0.866) circle [radius = 0.1];
+%        \fill (0.5, 0.866) circle [radius = 0.1];
+%        \fill (0.0, 1.732) circle [radius = 0.1];
+%        \fill (0.0, 0.0) node [below] {$(0, 0)$};
+%        \draw (0.0, 0.0) -- (-0.5, 0.866);
+%        \draw (-0.5, 0.866) -- (0.5, 0.866);
+%        \draw (0.0, 1.732) -- (0.5, 0.866);
+%        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
+%        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
+%      \end{tikzpicture}
+%
+%    \end{tabular}
+%    \caption{Two conformations when bead $i-1$ at (0,0) has a free hand}
+%    \label{fig:beadi}
+%  \end{center}
+%\end{figure}
 
@@
     \end{tabular}
-    \caption{When beads $i, i+1, i+2$ make three hydrogen bonds \newline (c) there is an inactive bead at (-1,0). \newline (d) there is no bead at (-1,0).}
+    \caption{When beads $i, i+1, i+2$ make three hydrogen bonds (c) there is an inactive bead at (-1,0).  (d) there is no bead at (-1,0).}
     \label{fig:3bonds}
@@
     \end{tabular}
-    \caption{When beads $i+1, i+2, i+3$ make three hydrogen bonds \newline (a) there is an inactive bead at (1,0). \newline (b) there is no bead at (1,0).}
+    \caption{When beads $i+1, i+2, i+3$ make three hydrogen bonds (a) there is an inactive bead at (1,0). (b) there is no bead at (1,0).}
     \label{fig:3bonds2}
@@
 
-%\end{enumerate}
-
+\qed
 \end{proof}

### 2018-12-05 tt_theorem.tex
12/5 evening.....

@@
     \end{tabular}
-    \caption{Direction into an entrance of a tunnel: (Left) straight, (Middle) obtuse, (Right) acute. The bead $w[i]$ is stabilized at an entrance and $w[i+1]$ is stabilized inside a tunnel.}
+    \caption{The three ways to enter a tunnel: (Left) straight, (Middle) obtuse, (Right) acute. The bead $w[i]$ is stabilized at the entrance and $w[i+1]$ is stabilized inside.}
     \label{TTT_tunnel_direction}

### 2018-12-05 arity1.tex
Add files via upload
Succinctness, succinctness

@@
 	\end{minipage}
-	\caption{}
+	\caption{Transcript of pyramid-like conformation at delay $2$, arity $1$.}
 	\label{table:transcript}
@@
 
-In subsections~\ref{sec:unary}.1 and \ref{sec:unary}.2, we will argue that unary systems at arity $1$ and delay $2$ and $3$, respectively, cannot fold infinite transcripts deterministically.
+In this section we will argue that unary systems at arity $1$ and delay $2$ and $3$, respectively, cannot fold infinite transcripts deterministically.
 As we will see, in fact, the length of transcripts deterministically foldable by these systems has an upper bound quadratic in the length of the seed.
-The main result is the following theorem, which is a direct consequence of Lemma x and Lemma y from the next two subsections.
+The main result is the following theorem, which is a direct consequence of Lemma~\ref{lem:d2a1}  and Lemma~\ref{lem:d3a1} which follow.
 \begin{theorem}[$\delta\in\{ 2,3\}, \alpha = 1$]\label{thm:d23a1}
@@
 
-\subsubsection{\ref{sec:unary}.1 \ \ $\delta = 2$\\}
+%\subsubsection{\ref{sec:unary}.1 \ \ $\delta = 2$\\}
 \begin{lemma}[$\delta=2, \alpha =1$]\label{lem:d2a1}
@@
 
-\noindent\textbf{Case 2.} bead $i+1$ is fixed at $(0,1)$. This is only possible if
-	\begin{enumerate}[label=(\alph*)]
-		\item there is an inactive bead at $(-1,0)$ and one with a free hand one at $(-2,0)$. This case is symmetrical to (1).
-		\item there is no bead at $(-1,0)$, bead $i+1$ can bond with bead $i-1$ at $(0,0)$ and the bead $i+2$ can be placed at $(-1,0)$ where it can bond with $(-2,0)$, $(-2,-1)$ or $(-1,-1)$.
-This leads to nondeterminism, because placing bead $i$ at $(-1,0)$ and bead $i+1$ at $(0,1)$ would yield two bonds, just as the original conformation.
-		\item there is a bead at $(-1,0)$ and bead $i+1$ can bond with that or with bead $i-1$ at $(0,0)$.
+\noindent\textbf{Case 2.} bead $i+1$ is fixed at $(0,1)$. This is only possible if\\
+\textbf{(a)} there is an inactive bead at $(-1,0)$ and one with a free hand one at $(-2,0)$. This case is symmetrical to (1).
+there is no bead at $(-1,0)$, bead $i+1$ can bond with bead $i-1$ at $(0,0)$ and the bead $i+2$ can be placed at $(-1,0)$ where it can bond with $(-2,0)$, $(-2,-1)$ or $(-1,-1)$.
+This leads to nondeterminism, because placing bead $i$ at $(-1,0)$ and bead $i+1$ at $(0,1)$ would yield two bonds, just as the original conformation.\\
+\textbf{(b)	} there is a bead at $(-1,0)$ and bead $i+1$ can bond with that or with bead $i-1$ at $(0,0)$.
 However, this means that placing bead $i$ at $(0,1)$ at bead $i+1$ at $(1,1)$ creates the same number of hydrogen bonds, thus resulting in bead $i$ not being placed deterministically.
 
-	\end{enumerate}
 %\end{enumerate}
@@
 
-\subsubsection{\ref{sec:unary}.2 \ \ $\delta = 3$\\}
+%\subsubsection{\ref{sec:unary}.2 \ \ $\delta = 3$\\}
 
@@
 %\begin{enumerate}
-\noindent\textbf{Case 1.}  Bead $i-1$ at (0,0) has a free hand.\\ If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities (see Fig.~\ref{fig:beadi2}, except it starts from (0,0) not (1,1)).
-Therefore, it needs to make three new bonds to deterministically stabilize $i$.\\
-
-%\begin{figure}
-%  \begin{center}
-%    \begin{tabular}{cc}
-%      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-%        \fill (0.0, 0.0) circle [radius = 0.1];
-%        \fill (0.5, 0.866) circle [radius = 0.1];
-%        \fill (-0.5, 0.866) circle [radius = 0.1];
-%        \fill (0.0, 1.732) circle [radius = 0.1];
-%        \fill (0.0, 0.0) node [below] {$(0, 0)$};
-%        \draw (0.0, 0.0) -- (0.5, 0.866);
-%        \draw (0.5, 0.866) -- (-0.5, 0.866);
-%        \draw (0.0, 1.732) -- (-0.5, 0.866);
-%        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
-%        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
-%      \end{tikzpicture}
-%
-%      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-%        \fill (0.0, 0.0) circle [radius = 0.1];
-%        \fill (-0.5, 0.866) circle [radius = 0.1];
-%        \fill (0.5, 0.866) circle [radius = 0.1];
-%        \fill (0.0, 1.732) circle [radius = 0.1];
-%        \fill (0.0, 0.0) node [below] {$(0, 0)$};
-%        \draw (0.0, 0.0) -- (-0.5, 0.866);
-%        \draw (-0.5, 0.866) -- (0.5, 0.866);
-%        \draw (0.0, 1.732) -- (0.5, 0.866);
-%        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
-%        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
-%      \end{tikzpicture}
-%
-%    \end{tabular}
-%    \caption{Two conformations when bead $i-1$ at (0,0) has a free hand}
-%    \label{fig:beadi}
-%  \end{center}
-%\end{figure}
+\noindent\textbf{Case 1.}  Bead $i-1$ at (0,0) has a free hand.
+If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities (see Fig.~\ref{fig:beadi2}, except it starts from (0,0) not (1,1)).
+Therefore, it needs to make three new bonds to deterministically stabilize $i$.
+There are five possible cases in which beads $i, i+1, i+2$ can add three bonds, see Fig.~\ref{fig:3bonds}.
+In the cases (b) and (e) in Fig.~\ref{fig:3bonds}, there are beads having a free hand at (1,0) and (-1,0) already stabilized before bead $i-1$ is fixed at (0,0).
+One of these two beads may be a predecessor of bead $i-1$, but at least one of them is not.
+When bead $i-1$ is fixed at (0,0), it makes a bond with the one of these two beads which is not its predecessor.
+This means that it is impossible to have three beads at (-1,0), (0,0) and (1,0), each with a free hand, when bead $i$ is fixed, and consequently, cases (b) and (e) in Fig.~\ref{fig:3bonds} cannot occur.
+Case (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
+If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
+Similarly to case 1.
+in the previous section, cases (a) and (c) in Fig.~\ref{fig:3bonds} lead to nondeterministism eventually, when the transcript reaches a first corner of $\hexagon_p^n$.
 
@@
 
-There are five possible cases in which beads $i, i+1, i+2$ can add three bonds, see Fig.~\ref{fig:3bonds}.
-In the cases (b) and (e) in Fig.~\ref{fig:3bonds}, there are beads having a free hand at (1,0) and (-1,0) already stabilized before bead $i-1$ is fixed at (0,0).
-One of these two beads may be a predecessor of bead $i-1$, but at least one of them is not.
-When bead $i-1$ is fixed at (0,0), it makes a bond with the one of these two beads which is not its predecessor.
-This means that it is impossible to have three beads at (-1,0), (0,0) and (1,0), each with a free hand, when bead $i$ is fixed, and consequently, cases (b) and (e) in Fig.~\ref{fig:3bonds} cannot occur.
-Case (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
-If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
-Similarly to case 1.
-in the previous section, cases (a) and (c) in Fig.~\ref{fig:3bonds} lead to nondeterministism eventually, when the transcript reaches a first corner of $\hexagon_p^n$.
-
 \noindent\textbf{Case 2.} Bead $i-1$ at (0,0) does not have a free hand.\\
@@
 %There are not any bead having a free hand at (1,0) or (-1,0) to prevent from being (a) and (c) in Fig.~\ref{fig:3bonds}. 
-(ii) Now consider when there is no bead at (1,0) or there is one, but with no free hand.
+\noindent (ii) Now consider when there is no bead at (1,0) or there is one, but with no free hand.
 Let us discuss the moment after bead $i$ is fixed outside $\hexagon_p^n$.
@@
 \end{figure}
-
-\qed
-\end{proof}
-
 We have shown that at $\alpha=1$ and  $\delta\in\{2,3\}$, unary oritatami systems can only fold finite length transcripts deterministically, and the length of that transcript is bounded by the size of the regular hexagon of radius $n$ plus the length of one side of the surrounding hexagon.
 This gives us the upper bound $|\hexagon_p^{n}|+(n+1)=3n^2+4n+2$,  where $n$ is the length of the seed, concluding the proof of Theorem~\ref{thm:d23a1}.
+\end{proof}

### 2018-12-05 tt_theorem.tex
12/5 latest

@@
 	\node[left] at (-120:1) {$p_2$};
-	\node[left] at (-60:1) {$p_3$};
 	\node[left, shift=(-120:1)] at (-60:1) {$p_3$};
+	\node[right] at (-60:1) {$p_4$};
 
@@
 Since $S[i] = b$, at least one of the four neighbors of $w[i-1]$ must be empty. 
-If $w_3$ is free, then $w[i-2]$ must have used up all of its hands; otherwise, $w[i]$ would be stabilized also at $n_3$ nondeterministically, a contradiction. 
+If $n_3$ is free, then $w[i-2]$ must have used up all of its hands; otherwise, $w[i]$ would be stabilized also at $n_3$ nondeterministically, a contradiction. 
 Thus, $\alpha + 2 = 5$ neighbors of $w[i-2]$, that is, all of its neighbors, must be occupied. 
@@
       \draw[white] (60:2) circle [radius=0.05];
-      \node[above, white] at (60:2) {$n_adj$};
+      \node[right, white] at (60:2) {$n_{adj}$};
 
@@
      \begin{tikzpicture}
-
+	\node[right, shift=(60:1), white] at (60:1) {$n_{adj}$};
       \fill[shift=(180:1)] (0,0) circle [radius=0.1];
@@
 	\node[above, shift=(60:1)] at (0:1) {$n_{-1}$};
-	\node[above, shift=(60:1)] at (60:1) {$n_{-2}$};
-	\node[above, shift=(60:1)] at (120:1) {$n_{-3}$};
 	\node[below, shift=(180:1)] at (-120:1) {$n_5$};
@@
  	\node[right] at (0:1) {$n_0$};
-	\node[above] at (60:1) {$n_1$};
+	\node[right] at (60:1) {$n_1$};
 	\node[below] at (-60:1) {$n_2$};
 	\node[below] at (-120:1) {$n_4$};
-	\node[above, shift=(120:1)] at (60:1) {$n_{-1}$};
-	\node[above, shift=(120:1)] at (120:1) {$n_{-2}$};
-	\node[above, shift=(120:1)] at (180:1) {$n_{-3}$};
+	\node[right, shift=(120:1)] at (60:1) {$n_{-1}$};
     \end{tikzpicture}

### 2018-12-05 arity1pyramid.tex
Add files via upload

--- 2018-12-05 arity1.tex
@@
 \end{figure}
-
-\subsection{$\alpha = 1$, unary}
-\label{sec:unary}
-
-In this section we will argue that unary systems at arity $1$ and delay $2$ and $3$, respectively, cannot fold infinite transcripts deterministically.
-As we will see, in fact, the length of transcripts deterministically foldable by these systems has an upper bound quadratic in the length of the seed.
-The main result is the following theorem, which is a direct consequence of Lemma~\ref{lem:d2a1}  and Lemma~\ref{lem:d3a1} which follow.
-\begin{theorem}[$\delta\in\{ 2,3\}, \alpha = 1$]\label{thm:d23a1}
-	Let $\Xi$ be a unary oritatami system of $\delta \in \{2,3\}$ and $\alpha = 1$. Starting with a seed of length $n$, $\Xi$ can yield only finite structures of size at most $3n^2+4n+2$.
-\end{theorem}
-
-Let us fix some common starting points for the next two subsections.
-Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|+1$.
-We will argue about the situation when the first bead is stabilized outside $\hexagon_p^n$ (a hexagon of radius $n$).
-Let this be the $i$th bead of the transcript.
-Without loss of generality, we can translate the origin $(0,0)$ to the coordinates of bead $i-1$ (which is still in $\hexagon_p^n$), and we can assume that bead $i$ is fixed at $(1,1)$ (see Fig.~\ref{fig:hexagonOut}).
-\begin{figure}
-	\centering
-	\includegraphics[width=0.3\linewidth]{./Fig/hexagonOut}
-	\caption{$\hexagon_p^n$ and the position $(1,1)$ of the first bead fixed outside of it.}
-	\label{fig:hexagonOut}
-\end{figure}
-
-%\subsubsection{\ref{sec:unary}.1 \ \ $\delta = 2$\\}
-\begin{lemma}[$\delta=2, \alpha =1$]\label{lem:d2a1}
-	Let $\Xi$ be a unary oritatami system of $\delta=2$ and $\alpha = 1$. Starting with a seed of length $n$, $\Xi$ can yield only finite structures of size at most $3n^2+4n+2$.
-\end{lemma}
-\begin{proof}
-
-In the elongation that places bead $i$ at $(1,1)$ there are two possibilities:
-\begin{itemize}
-	\item $i$ forms a bond with a bead at $(1,0)$.
-	\item  $i$ does not bond to anything and $i+1$ is at $(2,1)$ bonding with a bead at $(2,0)$.
-If there is no bead at $(1,0)$, then placing $i$ at $(1,0)$ instead of $(1,1)$ results in the same number of bonds, leading to nondeterminism.
-Therefore, there has to be a bead at $(1,0)$ and it is inactive, otherwise it would bond to $i$.
-This is analogous to case 1.
-below, with the only difference being that the bond between (1,1) and (1,0) is missing.%as in Fig.~\ref{fig:hexagonOut1}.
-	\begin{figure}
-		\centering
-		\includegraphics[width=0.2\linewidth]{./Fig/hexagonOut1}
-		%\caption{}
-		\label{fig:hexagonOut1}
-	\end{figure}
-
-\end{itemize}
-
-%The only position with which $(1,1)$ can form a bond is $(1,0)$.
-This means that there is a bead at $(1,0)$, which bonds to bead $i$, otherwise there are other conformations in which beads $i$ and $i+1$ add one bond to the conformation, making the behavior nondeterministic.
-Because of the above, we need only consider the case when $i$ binds to a bead at (1,0).
-The next bead, $i+1$, can be fixed at $(2,1)$ or at $(0,1)$ as all other possibilities result in nondeterministic behavior immediately, so we have two cases.
-
-%\begin{enumerate}
-\noindent\textbf{Case 1.} bead $i+1$ is fixed at $(2,1)$ and can bond with a bead at $(2,0)$ (see Fig.~\ref{fig:hexagonOut2}).
-Now consider bead $i+2$.
-For $i+1$ to be fixed at $(2,1)$, $i+2$ needs to form a bond somewhere, otherwise $i+2$ could go to $(2,1)$ forming the bond with the bead at $(2,0)$ and there would be two conformations with the maximal $1$ bond.
-The only possibility is that there is a bead at $(3,0)$ and $i+2$ can bond with it when placed at $(3,1)$.
-We can apply the same argument inductively: there is some $m\geq 0$ such that grid points $(\ell,0)$ are occupied by beads with free hands, for all $\ell\in \{2,\dots,2+m\}$, and there is no bead at $(3+m,0)$.
-Such an $m$ exists, and it is not greater than $n$, because those beads are all stabilized along the same side of $\hexagon_p^n$.
-Then, bead $i+\ell$ is fixed at $(\ell+1,1)$ and bonds with $(\ell+1,0)$.
-However, bead $i+2+m$ cannot be fixed anywhere, because $i+2+m$ and $i+3+m$ can only add one bond to the conformation, and that is possible either with $i+2+m \rightarrow (2+m,1)$, $i+3+m \rightarrow (3+m,1)$ or with $i+2+m \rightarrow (2+m,2)$, $i+3+m \rightarrow (2+m,1)$.
-Intuitively, when we reach a corner of the hexagon $\hexagon_p^n$, the next bead of the transcript cannot deterministically stabilize, as depicted in Fig.~\ref{fig:hexagonOut2}.
-In this case, the size of the transcript which was deterministically stabilized is bounded by the size of $\hexagon_p^n$ plus the length of one side of $\hexagon_p^{n+1}$, so by $(3n^2+3n+1)+(n+1)=3n^2+4n+2$.
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.9\linewidth]{./Fig/hexagonOut2}
-		\caption{When bead $i+2+m$ is fixed}
-		\label{fig:hexagonOut2}
-	\end{figure}
-
-\vspace{0.2cm}
-
-\noindent\textbf{Case 2.} bead $i+1$ is fixed at $(0,1)$. This is only possible if\\
-\textbf{(a)} there is an inactive bead at $(-1,0)$ and one with a free hand one at $(-2,0)$. This case is symmetrical to (1).
-there is no bead at $(-1,0)$, bead $i+1$ can bond with bead $i-1$ at $(0,0)$ and the bead $i+2$ can be placed at $(-1,0)$ where it can bond with $(-2,0)$, $(-2,-1)$ or $(-1,-1)$.
-This leads to nondeterminism, because placing bead $i$ at $(-1,0)$ and bead $i+1$ at $(0,1)$ would yield two bonds, just as the original conformation.\\
-\textbf{(b)	} there is a bead at $(-1,0)$ and bead $i+1$ can bond with that or with bead $i-1$ at $(0,0)$.
-However, this means that placing bead $i$ at $(0,1)$ at bead $i+1$ at $(1,1)$ creates the same number of hydrogen bonds, thus resulting in bead $i$ not being placed deterministically.
-
-%\end{enumerate}
-
-\begin{figure}
-	\centering
-	%\includegraphics[width=0.3\linewidth]{./hexagonOut1}
-	%\hspace{10mm} %
-	\includegraphics[width=0.8\linewidth]{./Fig/hexagonOut3n}
-
-	\caption{When bead $i+1$ is fixed at (0,1)}
-	\label{fig:hexagonOut3}
-\end{figure}
-
-Case 2.(a) gives the same upper bound as case 1. Cases 2.(b)-(c) give the smaller upper bound $|\hexagon_p^n|+1$, thereby concluding the proof.
-\end{proof}
-
-%\subsubsection{\ref{sec:unary}.2 \ \ $\delta = 3$\\}
-
-\begin{lemma}[$\delta=3, \alpha =1$]\label{lem:d3a1}
-	Let $\Xi$ be a unary oritatami system of $\delta=3$ and $\alpha = 1$. Starting with a seed of length $n$, $\Xi$ can yield only finite structures of size at most $3n^2+4n+2$.
-\end{lemma}
-\begin{proof}
-We will argue similarly to the $\delta=2$ case: when we stabilize beads outside $\hexagon_p^n$, we can only do so at points right next to one of the sides and even there only until we reach a corner.
-This yields the upper bound immediately.
-
-As before, let us assume that the last bead stabilized within $\hexagon_p^n$ is at point $(0,0)$ and the next bead is the first to be stabilized outside $\hexagon_p^n$ at point $(1,1)$.
-Depending on whether bead $i-1$ at point (0,0) has a free hand to form a bond or not, we distinguish two cases.\\
-%\begin{enumerate}
-\noindent\textbf{Case 1.}  Bead $i-1$ at (0,0) has a free hand.
-If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities (see Fig.~\ref{fig:beadi2}, except it starts from (0,0) not (1,1)).
-Therefore, it needs to make three new bonds to deterministically stabilize $i$.
-There are five possible cases in which beads $i, i+1, i+2$ can add three bonds, see Fig.~\ref{fig:3bonds}.
-In the cases (b) and (e) in Fig.~\ref{fig:3bonds}, there are beads having a free hand at (1,0) and (-1,0) already stabilized before bead $i-1$ is fixed at (0,0).
-One of these two beads may be a predecessor of bead $i-1$, but at least one of them is not.
-When bead $i-1$ is fixed at (0,0), it makes a bond with the one of these two beads which is not its predecessor.
-This means that it is impossible to have three beads at (-1,0), (0,0) and (1,0), each with a free hand, when bead $i$ is fixed, and consequently, cases (b) and (e) in Fig.~\ref{fig:3bonds} cannot occur.
-Case (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
-If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
-Similarly to case 1.
-in the previous section, cases (a) and (c) in Fig.~\ref{fig:3bonds} lead to nondeterministism eventually, when the transcript reaches a first corner of $\hexagon_p^n$.
-
-\begin{figure}
-	\begin{center}
-		\begin{tabular}{ccccc}
-			\begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-			\fill (0.0, 0.0) circle [radius = 0.1];
-			\fill (1.0, 0.0) circle [radius = 0.1];
-			\fill (2.0, 0.0) circle [radius = 0.1];
-			\fill (3.0, 0.0) circle [radius = 0.1];
-			\fill (0.5, 0.866) circle [radius = 0.1];
-			\fill (1.5, 0.866) circle [radius = 0.1];
-			\fill (2.5, 0.866) circle [radius = 0.1];
-			\fill (0.0, 0.0) node [below] {$(0, 0)$};
-			\fill (0.5, 0.866) node [above] {$(1, 1)$};
-			\draw (0.0, 0.0) -- (0.5, 0.866);
-			\draw (0.5, 0.866) -- (1.5, 0.866);
-			\draw (1.5, 0.866) -- (2.5, 0.866);
-			\draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-			\draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
-			\draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
-			\fill (1.5, -0.5) node [below] {(a)};
-			\end{tikzpicture}
-
-			\begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-			\fill (1.0, 0.0) circle [radius = 0.1];
-			\fill (0.0, 0.0) circle [radius = 0.1];
-			\fill (-1.0, 0.0) circle [radius = 0.1];
-			\fill (-2.0, 0.0) circle [radius = 0.1];
-			\fill (0.5, 0.866) circle [radius = 0.1];
-			\fill (-0.5, 0.866) circle [radius = 0.1];
-			\fill (-1.5, 0.866) circle [radius = 0.1];
-			\fill (0.0, 0.0) node [below] {$(0, 0)$};
-			\fill (0.5, 0.866) node [above] {$(1, 1)$};
-			\draw (0.0, 0.0) -- (0.5, 0.866);
-			\draw (0.5, 0.866) -- (-0.5, 0.866);
-			\draw (-0.5, 0.866) -- (-1.5, 0.866);
-			\draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-			\draw [dashed] [red] (-0.5, 0.866) -- (-1.0, 0.0);
-			\draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
-			\fill (-0.5, -0.5) node [below] {(b)};
-			\end{tikzpicture}
-
-			\begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-			\fill (1.0, 0.0) circle [radius = 0.1];
-			\fill (0.0, 0.0) circle [radius = 0.1];
-			\fill (-1.0, 0.0) circle [radius = 0.1];
-			\fill (-2.0, 0.0) circle [radius = 0.1];
-			\fill (0.5, 0.866) circle [radius = 0.1];
-			\fill (-0.5, 0.866) circle [radius = 0.1];
-			\fill (-1.5, 0.866) circle [radius = 0.1];
-			\fill (0.0, 0.0) node [below] {$(0, 0)$};
-			\fill (0.5, 0.866) node [above] {$(1, 1)$};
-			\draw (0.0, 0.0) -- (0.5, 0.866);
-			\draw (0.5, 0.866) -- (-0.5, 0.866);
-			\draw (-0.5, 0.866) -- (-1.5, 0.866);
-			\draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-			\draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
-			\draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
-			\fill (-0.5, -0.5) node [below] {(c)};
-			\end{tikzpicture}
-
-			\begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-			\fill (1.0, 0.0) circle [radius = 0.1];
-			\fill (0.0, 0.0) circle [radius = 0.1];
-			\fill (-2.0, 0.0) circle [radius = 0.1];
-			\fill (0.5, 0.866) circle [radius = 0.1];
-			\fill (-0.5, 0.866) circle [radius = 0.1];
-			\fill (-1.5, 0.866) circle [radius = 0.1];
-			\fill (0.0, 0.0) node [below] {$(0, 0)$};
-			\fill (0.5, 0.866) node [above] {$(1, 1)$};
-			\draw (0.0, 0.0) -- (0.5, 0.866);
-			\draw (0.5, 0.866) -- (-0.5, 0.866);
-			\draw (-0.5, 0.866) -- (-1.5, 0.866);
-			\draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-			\draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
-			\draw [dashed] [red] (-1.5, 0.866) -- (-2.0, 0.0);
-			\fill (-0.5, -0.5) node [below] {(d)};
-			\end{tikzpicture}
-
-			\begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-			\fill (1.0, 0.0) circle [radius = 0.1];
-			\fill (0.0, 0.0) circle [radius = 0.1];
-			\fill (-1.0, 0.0) circle [radius = 0.1];
-			\fill (0.5, 0.866) circle [radius = 0.1];
-			\fill (-0.5, 0.866) circle [radius = 0.1];
-			\fill (-1.5, 0.866) circle [radius = 0.1];
-			\fill (0.0, 0.0) node [below] {$(0, 0)$};
-			\fill (0.5, 0.866) node [above] {$(1, 1)$};
-			\draw (0.0, 0.0) -- (0.5, 0.866);
-			\draw (0.5, 0.866) -- (-0.5, 0.866);
-			\draw (-0.5, 0.866) -- (-1.5, 0.866);
-			\draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-			\draw [dashed] [red] (-0.5, 0.866) -- (0.0, 0.0);
-			\draw [dashed] [red] (-1.5, 0.866) -- (-1.0, 0.0);
-			\fill (-0.5, -0.5) node [below] {(e)};
-			\end{tikzpicture}\\
-
-		\end{tabular}
-		\caption{When beads $i, i+1, i+2$ make three hydrogen bonds (c) there is an inactive bead at (-1,0).  (d) there is no bead at (-1,0).}
-		\label{fig:3bonds}
-	\end{center}
-\end{figure}
-
-\noindent\textbf{Case 2.} Bead $i-1$ at (0,0) does not have a free hand.\\
-(i) First, let us assume that there is a bead at (1,0) which has a free hand.
-If there is a bead at (1,0) and beads $i, i+1, i+2$ add only two bonds, we instantly get nondeterministism as in Fig.~\ref{fig:beadat(1,0)}.
-Hence, beads $i, i+1, i+2$ need to make three bonds to stabilize $i$, but if they make three hydrogen bonds, the situation is analogous to (a) and (c) in Fig.~\ref{fig:3bonds}.
-
-%There are not any bead having a free hand at (1,0) or (-1,0) to prevent from being (a) and (c) in Fig.~\ref{fig:3bonds}. 
-\noindent (ii) Now consider when there is no bead at (1,0) or there is one, but with no free hand.
-Let us discuss the moment after bead $i$ is fixed outside $\hexagon_p^n$.
-Now bead $i$ has a free hand because it cannot bind to (1,0).
-If beads $i+1, i+2, i+3$ can form only two bonds, it will be nondeterministic because there are at least two possible such conformations, as in Fig.~\ref{fig:beadi2}.
-Hence, they need to form three bonds to deterministically stabilize, such as in Fig.~\ref{fig:3bonds2}.
-Case (a) in Fig.~\ref{fig:3bonds2}.
-becomes the same as case (a) in Fig.~\ref{fig:3bonds}.
-Case (b) in Fig.~\ref{fig:3bonds2} becomes nondeterministic already when bead $i$ is fixed because bead $i$ could also be fixed at (1,0).\\
-
-\begin{figure}
-	\begin{minipage}{.45\textwidth}
-
-  \begin{center}
-    \begin{tabular}{cc}
-      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-        \fill (0.0, 0.0) circle [radius = 0.1];
-        \fill (1.0, 0.0) circle [radius = 0.1];
-        \fill (0.5, 0.866) circle [radius = 0.1];
-        \fill (1.5, 0.866) circle [radius = 0.1];
-        \fill (1.0, 1.732) circle [radius = 0.1];
-        \fill (0.0, 0.0) node [below] {$(0, 0)$};
-        \fill (0.5, 0.866) node [left] {$(1, 1)$};
-        \fill (1.0, 0.0) node [below] {$(1, 0)$};
-        \draw (0.0, 0.0) -- (0.5, 0.866);
-        \draw (0.5, 0.866) -- (1.5, 0.866);
-        \draw (1.0, 1.732) -- (1.5, 0.866);
-        \draw [dashed] [red] (1.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
-        \draw [dashed] [red] (1.0, 1.732) -- (0.5, 0.866);
-      \end{tikzpicture}
-
-      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-        \fill (0.0, 0.0) circle [radius = 0.1];
-        \fill (1.0, 0.0) circle [radius = 0.1];
-        \fill (-0.5, 0.866) circle [radius = 0.1];
-        \fill (0.5, 0.866) circle [radius = 0.1];
-        \fill (0.0, 1.732) circle [radius = 0.1];
-        \fill (0.0, 0.0) node [below] {$(0, 0)$};
-        \fill (-0.5, 0.866) node [left] {$(0, 1)$};
-        \fill (1.0, 0.0) node [below] {$(1, 0)$};
-        \draw (0.0, 0.0) -- (-0.5, 0.866);
-        \draw (-0.5, 0.866) -- (0.5, 0.866);
-        \draw (0.0, 1.732) -- (0.5, 0.866);
-        \draw [dashed] [red] (0.5, 0.866) -- (1.0, 0.0);
-        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
-      \end{tikzpicture}
-
-    \end{tabular}
-    \caption{Two conformations when a bead at (1,0) has a free hand.}
-    \label{fig:beadat(1,0)}
-  \end{center}
-	\end{minipage}%	
-\hspace{1cm}\begin{minipage}{.45\textwidth}
-		\begin{center}
-			\begin{tabular}{cc}
-				\begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-				\fill (0.0, 0.0) circle [radius = 0.1];
-				\fill (0.5, 0.866) circle [radius = 0.1];
-				\fill (-0.5, 0.866) circle [radius = 0.1];
-				\fill (0.0, 1.732) circle [radius = 0.1];
-				\fill (0.0, 0.0) node [below] {$(1, 1)$};
-				\draw (0.0, 0.0) -- (0.5, 0.866);
-				\draw (0.5, 0.866) -- (-0.5, 0.866);
-				\draw (0.0, 1.732) -- (-0.5, 0.866);
-				\draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
-				\draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
-				\end{tikzpicture}
-
-				\begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-				\fill (0.0, 0.0) circle [radius = 0.1];
-				\fill (-0.5, 0.866) circle [radius = 0.1];
-				\fill (0.5, 0.866) circle [radius = 0.1];
-				\fill (0.0, 1.732) circle [radius = 0.1];
-				\fill (0.0, 0.0) node [below] {$(1, 1)$};
-				\draw (0.0, 0.0) -- (-0.5, 0.866);
-				\draw (-0.5, 0.866) -- (0.5, 0.866);
-				\draw (0.0, 1.732) -- (0.5, 0.866);
-				\draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
-				\draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
-				\end{tikzpicture}
-
-			\end{tabular}
-			\caption{Two conformations when a bead $i$ at (1,1) has a free hand}
-			\label{fig:beadi2}
-		\end{center}
-	\end{minipage}
-
-\end{figure}
-
-%
-%\begin{figure}
-%  \begin{center}
-%    \begin{tabular}{cc}
-%      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-%        \fill (0.0, 0.0) circle [radius = 0.1];
-%        \fill (0.5, 0.866) circle [radius = 0.1];
-%        \fill (-0.5, 0.866) circle [radius = 0.1];
-%        \fill (0.0, 1.732) circle [radius = 0.1];
-%        \fill (0.0, 0.0) node [below] {$(1, 1)$};
-%        \draw (0.0, 0.0) -- (0.5, 0.866);
-%        \draw (0.5, 0.866) -- (-0.5, 0.866);
-%        \draw (0.0, 1.732) -- (-0.5, 0.866);
-%        \draw [dashed] [red] (0.0, 1.732) -- (0.5, 0.866);
-%        \draw [dashed] [red] (0.0, 0.0) -- (-0.5, 0.866);
-%      \end{tikzpicture}
-%
-%      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-%        \fill (0.0, 0.0) circle [radius = 0.1];
-%        \fill (-0.5, 0.866) circle [radius = 0.1];
-%        \fill (0.5, 0.866) circle [radius = 0.1];
-%        \fill (0.0, 1.732) circle [radius = 0.1];
-%        \fill (0.0, 0.0) node [below] {$(1, 1)$};
-%        \draw (0.0, 0.0) -- (-0.5, 0.866);
-%        \draw (-0.5, 0.866) -- (0.5, 0.866);
-%        \draw (0.0, 1.732) -- (0.5, 0.866);
-%        \draw [dashed] [red] (0.0, 0.0) -- (0.5, 0.866);
-%        \draw [dashed] [red] (0.0, 1.732) -- (-0.5, 0.866);
-%      \end{tikzpicture}
-%
-%    \end{tabular}
-%    \caption{Two conformations when a bead $i$ at (1,1) has a free hand}
-%    \label{fig:beadi2}
-%  \end{center}
-%\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{cc}
-
-      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-        \fill (0.0, 0.0) circle [radius = 0.1];
-        \fill (1.0, 0.0) circle [radius = 0.1];
-        \fill (2.0, 0.0) circle [radius = 0.1];
-        \fill (3.0, 0.0) circle [radius = 0.1];
-        \fill (4.0, 0.0) circle [radius = 0.1];
-        \fill (0.5, 0.866) circle [radius = 0.1];
-        \fill (1.5, 0.866) circle [radius = 0.1];
-        \fill (2.5, 0.866) circle [radius = 0.1];
-        \fill (3.5, 0.866) circle [radius = 0.1];
-        \fill (0.0, 0.0) node [below] {$(0, 0)$};
-        \fill (0.5, 0.866) node [above] {$(1, 1)$};
-        \draw (0.0, 0.0) -- (0.5, 0.866);
-        \draw (0.5, 0.866) -- (1.5, 0.866);
-        \draw (1.5, 0.866) -- (2.5, 0.866);
-        \draw (2.5, 0.866) -- (3.5, 0.866);
-        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
-        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
-        \fill (1.5, -0.5) node [below] {(a)};
-      \end{tikzpicture}
-
-      \begin{tikzpicture}[thick,scale=0.8, every node/.style={scale=0.8}]
-        \fill (0.0, 0.0) circle [radius = 0.1];
-        \fill (2.0, 0.0) circle [radius = 0.1];
-        \fill (3.0, 0.0) circle [radius = 0.1];
-        \fill (4.0, 0.0) circle [radius = 0.1];
-        \fill (0.5, 0.866) circle [radius = 0.1];
-        \fill (1.5, 0.866) circle [radius = 0.1];
-        \fill (2.5, 0.866) circle [radius = 0.1];
-        \fill (3.5, 0.866) circle [radius = 0.1];
-        \fill (0.0, 0.0) node [below] {$(0, 0)$};
-        \fill (0.5, 0.866) node [above] {$(1, 1)$};
-        \draw (0.0, 0.0) -- (0.5, 0.866);
-        \draw (0.5, 0.866) -- (1.5, 0.866);
-        \draw (1.5, 0.866) -- (2.5, 0.866);
-        \draw (2.5, 0.866) -- (3.5, 0.866);
-        \draw [dashed] [red] (1.5, 0.866) -- (2.0, 0.0);
-        \draw [dashed] [red] (2.5, 0.866) -- (3.0, 0.0);
-        \draw [dashed] [red] (3.5, 0.866) -- (4.0, 0.0);
-        \fill (1.5, -0.5) node [below] {(b)};
-      \end{tikzpicture}\\
-
-    \end{tabular}
-    \caption{When beads $i+1, i+2, i+3$ make three hydrogen bonds (a) there is an inactive bead at (1,0). (b) there is no bead at (1,0).}
-    \label{fig:3bonds2}
-  \end{center}
-\end{figure}
-We have shown that at $\alpha=1$ and  $\delta\in\{2,3\}$, unary oritatami systems can only fold finite length transcripts deterministically, and the length of that transcript is bounded by the size of the regular hexagon of radius $n$ plus the length of one side of the surrounding hexagon.
-This gives us the upper bound $|\hexagon_p^{n}|+(n+1)=3n^2+4n+2$,  where $n$ is the length of the seed, concluding the proof of Theorem~\ref{thm:d23a1}.
-\end{proof}

### 2018-12-05 arity1upper.tex
Add files via upload

--- 2018-12-05 arity1.tex
@@
-\subsection{$\alpha = 1$, arbitrary alphabets}
-First we present a lower bound construction for arity $1$ systems.
-At $\alpha=1$, having delay $\delta=2$ allows the deterministic folding of quadratic length transcripts compared with $\delta=1$, where, as stated before, the maximum length is linear in the length of the seed.
-We demonstrate this with an infinite family of OS, which fold deterministically a transcript of length $\frac{(n-1)^2}{4}$ starting from a given seed of length $n$.
-
-Consider the following $\delta=2$, $\alpha=1$ system with bead types $\{0,1,2,3,4\}$ and attraction rules $\{(1,1),(2,2), (3,3),(4,4)\}$.
-Let the seed $\sigma$ be a conformation of a $4k+1$ long bead sequence of the form $(1020)^k0$, such that bead $\sigma[i]$ of the seed is stabilized at point $(i,0)$, for all $1\leq i\leq 4k-1$.
-Bead $4k$ is at $(4k-1,-1)$ and bead $4k+1$ is at $(4k,0)$.
-\vspace{0.1cm}
-
-The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where $\mathrm{row}_\ell$, for $\ell\in \{1,\dots, 2k\}$ is given in the table of Fig.~\ref{table:transcript}.
-\begin{figure}[h]
-	\begin{minipage}{.49\textwidth}
-		%\centering
-		\begin{tabular}{l|l}
-			\multicolumn{2}{c}{Transcript $w$}\\
-			\multicolumn{2}{c}{}  \\
-			$k$ odd & \hspace{0.3cm} $k$ even\\\hline
-			& \\
-			$(2413)^{k-1}241$\hspace{0.3cm} & \hspace{0.3cm} $(2413)^{k-1}241$\\
-			$(4231)^{k-1}4$   &  \hspace{0.3cm} $(4231)^{k-1}4$  \\
-			$(1324)^{k-2}132$ &  \hspace{0.3cm} $(1324)^{k-2}132$\\
-			$(3142)^{k-2}3$   &  \hspace{0.3cm} $(3142)^{k-2}3$ \\
-			\vdots			 &  \hspace{0.3cm} \vdots\\
-			$(1324)^1 132$	 &  \hspace{0.3cm} $(2413)^{1} 241$\\
-			$(3142)^1 3$		 & \hspace{0.3cm} $(4231)^1 4$\\
-			$(2413)^0 241$	 &  \hspace{0.3cm} $(1324)^0 132$\\
-			$(4231)^0 4$		 & \hspace{0.3cm} $(3142)^0 3$\\
-		\end{tabular}
-	\end{minipage}
-	%\scriptsize
-	\begin{minipage}{.49\textwidth}
-		%\centering
-		\begin{tabular}{|l|c|}
-			\hline
-			\hspace{1.2cm}row $\ell$ & $\ell\mod 4$ \\\hline
-			 & \\
-			\hspace{0.1cm}$(2413)^{k-\lfloor (\ell+1)/2\rfloor}241$ \hspace{0.1cm} &  $\textrm{ }\ell\equiv 1\mod 4\textrm{ }$\\
-			\hspace{0.1cm}$(4231)^{k-\lfloor (\ell+1)/2\rfloor}4$   &  $\textrm{ }\ell\equiv 2 \mod 4\textrm{ }$ \\
-			\hspace{0.1cm}$(1324)^{k-\lfloor (\ell+1)/2\rfloor}132$ &  $\textrm{ }\ell\equiv 3 \mod 4\textrm{ }$ \\
-			\hspace{0.1cm}$(3142)^{k-\lfloor (\ell+1)/2\rfloor}3$   &  $\textrm{ }\ell\equiv 4 \mod 4\textrm{ }$ \\\hline
-		\end{tabular}
-
-	\end{minipage}
-	\caption{Transcript of pyramid-like conformation at delay $2$, arity $1$.}
-	\label{table:transcript}
-\end{figure}
-
-The transcript above is written in rows which correspond to beads in the conformation stabilized along the same row on the grid.
-To simplify the argument we will use \textit{row} both for the transcript above and for the conformation it stabilizes in (note that in the figure the row index grows from bottom to top).
-
-Row $1$ is of length $4k-1$ and row $\ell+1$ is two beads shorter than row $\ell$, so the length of the whole transcript is $|w|=4k^2=\frac{(4k+1-1)^2}{4}=\frac{(|\sigma|-1)^2}{4}$.
-As an example, see Fig.~\ref{CI:big}, where $k=5$, so the length of the seed is $4k+1=21$ and the transcript is $4k^2 = 100$ beads long.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{./Fig/CI_Numbers}
-	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. }
-	\label{CI:big}
-\end{figure}
-
-Stabilizing the first bead of row $j$ goes as follows (see Fig.~\ref{CI:turn}):
-%\begin{itemize}
-%	\item $\bf j\equiv 1\mod 4$: the first two beads are $24$, and the preceding bead is stabilized at $(4k-\frac{j-1}{2}, j-1)$.
-The $2$ can only bind to the $2$ which occurred two beads before at $(4k-\frac{j+1}{2}, j-1)$, and $4$ cannot bind anywhere, so the $2$ is stabilized at $(4k-\frac{j-1}{2},j)$.
-%\end{itemize}
-
-\begin{center}
-	\begin{tabular}{|c|c|c|c|c|@{}m{0pt}@{}}
-		%\renewcommand{\arraystretch}{2}
-	$j\mod 4$					& first bead 	& predecessor at		& first bead binds to		& first stabilizes at\\
-						\hline
-	$\equiv 1$	& 2		& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$& $\mathrm{ }$\newline $\mathrm{ }$\\
-	\hline
-	$\equiv 2$	& 4				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$\\
-	\hline
-	$\equiv 3$	& 1				& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
-	\hline
-	$\equiv 4$	& 3				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
-	\hline		
-	\end{tabular}
-\end{center}
-
-%The first bead of the transcript is type $2$ and it has to be fixed next to $(4k,0)$.
-The second bead is type $4$, which cannot form a bond with anything in the conformation so far.
-The only possibility of forming a bond is if the $2$-bead is placed at $(4k,1)$ and it bonds with the $2$-bead of the seed at $(4k-1,0)$.
-The next to be stabilized is a $4$-bead, and since it cannot form any bond, the conformation with the highest number of bonds is when the one after, a $1$-bead, is at $(4k-2,1)$ bonding with $(4k-3,0)$, which stabilizes the preceding $4$-bead at $(4k-1,1)$ (see Fig.~\ref{CI:1-4}, (a)-(b)).
-
-\begin{figure}
-	\begin{minipage}{.35\textwidth}
-		\centering
-		\includegraphics[align=c,height=1in]{./Fig/CI_1n}\\
-		\bigskip
-
-		(a) First transcript bead
-	\end{minipage}%
-	\begin{minipage}{.2\textwidth}
-		\centering
-		\includegraphics[align=c,height=0.7in]{./Fig/CI_2n}\\
-		\bigskip
-
-		(b) Second bead
-	\end{minipage}
-	\begin{minipage}{.4\textwidth}
-		\centering
-		\includegraphics[align=c,height=0.5in]{./Fig/CI_3n}
-		\bigskip
-		\vspace{0.1in}
-		\includegraphics[align=c,height=0.5in]{./Fig/CI_4n}
-		\bigskip
-
-		(c) Portions of row $1$
-	\end{minipage}
-	\caption{Fixing transcript beads in odd rows}
-	\label{CI:1-4}
-\end{figure}
-
-As for the other beads, in rows $j\equiv 1,3\mod 4$, beads of type $1$ and $3$ bind to a bead in row $j-1$.
-In rows $j\equiv 2,4\mod 4$ beads of type $2$ and $4$ can bind to a bead in row $j-1$.
-This is true for row $1$, because beads of type $1$ and $3$ from row $1$ can only bind to every second bead of the seed, whereas beads of type $2$ and $4$ from row $1$ cannot bind to anything (Fig.~\ref{CI:1-4}, (c)).
-Once this dynamic holds for a row, it holds inductively for the next, as a bead that binds to another loses its only free hand at arity $1$.
-
-Within one row of the transcript, no bead can bind to a preceding bead, because if there is a previous bead of the same type in that row, it is stabilized at a distance of four and the system has delay $2$.
-
-By the arguments above, the beads in row $i$ of the transcript are stabilized along row $i$ on the grid, forming the pyramid-like conformation from Fig.~\ref{CI:big}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{./Fig/CI_turnn}
-	\caption{Beads $4k, 8k-2, \dots$ stabilize at turning points because the bead two positions before is the same type and has a free hand.}
-	\label{CI:turn}
-\end{figure}
-
 \subsection{$\alpha = 1$, unary}

### 2018-12-05 paper.tex
Enumitem
Added
wrapfig
added
Reorganization paper.tex

@@
 \documentclass[runningheads]{llncs}
+
+\usepackage{enumitem}
 
@@
 \usepackage{comment}
+
+\usepackage{wrapfig}
 
@@
 
+As a result of independent significance, we show that increasing the delay from 1 to 2 enables an oritatami system to yield a conformation of quadratic length in $n$ as long as 5 types of beads are available.
+
 %------------------------------------------------------
@@
 
-\section{Case of arity $1$}\label{sect:arity1}
+\section{Quadratic lower bound for delay 2, arity 1}\label{sect:lower}
 
-\input{arity1}
+\input{arity1pyramid}
 
-\section{Case of delay $1$}\label{sect:delay1}
+%\section{Case of arity $1$}\label{sect:arity1}
+
+%\input{arity1}
+
+%\section{Case of delay $1$}\label{sect:delay1}
+
+\section{Upper bounds for delay 1 or arity 1}
+
+\input{arity1upper}
 \input{tt_intro}

### 2018-12-05 paper.tex
Intro modified

@@
 \end{figure}
-In this paper, we will solve this problem partially at arity 1 in Sect.~\ref{sect:arity1} and completely at delay 1 in Sect.~\ref{sect:delay1}. 
-Concretely speaking, we will prove that at arity 1 and delay 2 or 3, the upper bound is $(3n+1)(n+1)$. 
-Upper bounds for longer delays remain open. 
+In this paper, we will solve this problem  completely at delay 1and partially at arity 1 in Sect.~\ref{sect:upper}. 
 At delay 1, we will provide a quadratic upper bound $3n(n+1)+1$ for the case of arity being 4, while a linear upper bound $4n+14$ for arity 3. 
 At the delay 1 and arity 2, one infinite structure turns out to be foldable deterministically, which is the zigzag conformation shown in Fig.~\ref{TTT_zigzag}. 
-These results as well as known upper bounds are summarized in Fig.~\ref{fig:summary}. 
+At arity 1, we will prove that at delay 2 or 3, the upper bound is $(3n+1)(n+1)$. 
+Upper bounds for longer delays remain open. These results as well as known upper bounds are summarized in Fig.~\ref{fig:summary}. 
 As shown at the end of Sect.~\ref{sec:preliminaries}, the stabilization of first $t$ beads of transcript by a determinisitc oritatami system can be simulated by a deterministic Turing machine within $t^3$ steps (Corollary~\ref{cor:DTIME3}).
@@
 
-\section{Upper bounds for delay 1 or arity 1}
+\section{Upper bounds for determinisitc unary oritatami systems at delay 1 or arity 1}\label{sect:upper}
 
-\input{arity1upper}
 \input{tt_intro}
 \input{tt_theorem}
+\input{arity1upper}
 

### 2018-12-06 paper.tex
space was missing
Time hierarchy

@@
 \end{figure}
-In this paper, we will solve this problem  completely at delay 1and partially at arity 1 in Sect.~\ref{sect:upper}. 
+In this paper, we will solve this problem  completely at delay 1 and partially at arity 1 in Sect.~\ref{sect:upper}. 
 At delay 1, we will provide a quadratic upper bound $3n(n+1)+1$ for the case of arity being 4, while a linear upper bound $4n+14$ for arity 3. 
@@
 Upper bounds for longer delays remain open. These results as well as known upper bounds are summarized in Fig.~\ref{fig:summary}. 
-As shown at the end of Sect.~\ref{sec:preliminaries}, the stabilization of first $t$ beads of transcript by a determinisitc oritatami system can be simulated by a deterministic Turing machine within $t^3$ steps (Corollary~\ref{cor:DTIME3}).
+As shown at the end of Sect.~\ref{sec:preliminaries}, the stabilization of the first $t$ beads of transcript by a deterministic oritatami system can be simulated by a deterministic Turing machine within $t^3$ steps (Corollary~\ref{cor:DTIME3}).
 Thus, the above mentioned upper bounds show that at delay 1 and arity 1, 3, or 4, or at delay 2 or 3 and arity 1, the class of deterministic unary oritatami systems is not Turing universal. 
@@
 Thus, this weakness result is not surprising at all. 
-The unary oritatami system might not be practical very much, though one bead may abstarct an oligonucleotide (a short sequence of nucleotides), and in that case, unary transcript can be a repetitive but nonunary sequence, which is not so unrealistic in experiments (see \cite{GearyAndersen2014}).
+The unary oritatami system might not be practical very much, though one bead may abstract an oligonucleotide (a short sequence of nucleotides), and in that case, unary transcript can be a repetitive but nonunary sequence, which is not so unrealistic in experiments (see \cite{GearyAndersen2014}).
 Nevertheless, this paper makes a first considerable step towards the characterization of non-Turing-universal oritatami systems.
@@
 This conformation $C$ is \textit{$R$-valid} if all of its bonds are $R$-valid. 
-For an integer $\alpha \ge 1$, $C$ is \textit{of arity $\alpha$} if it contains a bead that forms $\alpha$ bonds but none of its bead forms more. 
+For an integer $\alpha \ge 1$, $C$ is \textit{of arity $\alpha$} if it contains a bead that forms $\alpha$ bonds but none of its beads forms more. 
 By $\mathcal{C}_{\le \alpha}(\Sigma)$, we denote the set of all conformations over $\Sigma$ whose arity is at most $\alpha$; its argument $\Sigma$ is omitted whenever $\Sigma$ is clear from the context.
@@
 
-Because of the time hierarchy theorems, we know that $\mathrm{P}\subsetneq \mathrm{EXP}$, so we can conclude that OS which cannot deterministically fold transcripts of length exponential in the length of the seed are not computationally universal.
+Considering the following decision problem: given an oritatami system, integer $i$, and a point $p$, decides whether the bead $w[i]$ is stabilized at $p$. 
+By Corollary~\ref{cor:DTIME3}, this problem is in $\mathrm{P}$ for a fixed delay $\delta$.
+Because of the time hierarchy theorems, we know that $\mathrm{P}\subsetneq \mathrm{EXP}$ (see, e.g., \cite{AroraBarak2009}), so we can conclude that OS which cannot deterministically fold transcripts of length exponential in the length of the seed are not computationally universal.
 

### 2018-12-06 arity1upper.tex
fix pyramid pic

@@
 Let us fix some common starting points for the next two subsections.
-Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|+1$.
+Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|$.
 We will argue about the situation when the first bead is stabilized outside $\hexagon_p^n$ (a hexagon of radius $n$).
@@
 Case (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1).
-If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic.
-Similarly to case 1.
-in the previous section, cases (a) and (c) in Fig.~\ref{fig:3bonds} lead to nondeterministism eventually, when the transcript reaches a first corner of $\hexagon_p^n$.
+If three consecutive beads make three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, then each consecutive triple from here on will need to make three bonds to be deterministic.
+Therefore, similarly to case 1.
+in the previous section, cases (a) and (c) in Fig.~\ref{fig:3bonds} lead to nondeterminism eventually, when the transcript reaches a first corner of $\hexagon_p^n$.
 

### 2018-12-06 tt_theorem.tex
Thm 5 minor fix

@@
 Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 2$.
-It can yield an infinite structure, but the transcript folds into the zig-zag conformation after its ($27n^2 + 9n +1$)-th bead.
+It can yield an infinite structure, but the transcript folds into the zig-zag conformation after its $(27n^2 + 9n +1)$-th bead.
 \end{theorem}
@@
  This means that, only at most $\#bc(C_0) \leq 2n$ times we can thus expand that hexagonal region.
- In other words, outside $\hexagon^{3n}_O$ the transcript cannot help but fold into the zig-zag conformation. \qed
+ In other words, outside $\hexagon^{3n}_O$ the transcript cannot help but fold zig-zag. \qed
 

### 2018-12-06 arity1upper.tex
Technical problems fixed

--- 2018-12-05 arity1upper.tex
@@
-\subsection{$\alpha = 1$, unary}
+\subsection{Quadratic upper bounds for arity 1 and delay 2 or 3}
 \label{sec:unary}
@@
 In this section we will argue that unary systems at arity $1$ and delay $2$ and $3$, respectively, cannot fold infinite transcripts deterministically.
-As we will see, in fact, the length of transcripts deterministically foldable by these systems has an upper bound quadratic in the length of the seed.
-The main result is the following theorem, which is a direct consequence of Lemma~\ref{lem:d2a1}  and Lemma~\ref{lem:d3a1} which follow.
+As we will see, in fact, the length of transcripts deterministically foldable by these systems has an upper bound quadratic in the length $n$ of the seed.
+The main result is the following theorem, which is a direct consequence of Lemmas~\ref{lem:d2a1}  and \ref{lem:d3a1} which follow.
 \begin{theorem}[$\delta\in\{ 2,3\}, \alpha = 1$]\label{thm:d23a1}
-	Let $\Xi$ be a unary oritatami system of $\delta \in \{2,3\}$ and $\alpha = 1$. Starting with a seed of length $n$, $\Xi$ can yield only finite structures of size at most $3n^2+4n+2$.
+	A deterministic unary oritatami system at arity $\alpha = 1$ and delay $\delta \in \{2,3\}$ can fold into a terminal conformation of length at most $3n^2+4n+2$.
 \end{theorem}
 
-Let us fix some common starting points for the next two subsections.
+%\begin{figure}
+\begin{wrapfigure}{r}{0.5\linewidth}
+	\centering
+	\includegraphics[width=0.4\linewidth]{./Fig/hexagonOut}
+	\caption{$\hexagon_p^n$ and the position $(1,1)$ of the first bead fixed outside of it.}
+	\label{fig:hexagonOut}
+\end{wrapfigure}
+%\end{figure}
+
+Let us fix some common starting points for Lemmas~\ref{lem:d2a1} and \ref{lem:d3a1}.
 Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|+1$.
@@
 Without loss of generality, we can translate the origin $(0,0)$ to the coordinates of bead $i-1$ (which is still in $\hexagon_p^n$), and we can assume that bead $i$ is fixed at $(1,1)$ (see Fig.~\ref{fig:hexagonOut}).
-\begin{figure}
-	\centering
-	\includegraphics[width=0.3\linewidth]{./Fig/hexagonOut}
-	\caption{$\hexagon_p^n$ and the position $(1,1)$ of the first bead fixed outside of it.}
-	\label{fig:hexagonOut}
-\end{figure}
 
@@
 \begin{lemma}[$\delta=2, \alpha =1$]\label{lem:d2a1}
-	Let $\Xi$ be a unary oritatami system of $\delta=2$ and $\alpha = 1$. Starting with a seed of length $n$, $\Xi$ can yield only finite structures of size at most $3n^2+4n+2$.
+	A deterministic unary oritatami system of $\delta=2$ and $\alpha = 1$ can fold into a conformation of length at most $3n^2+4n+2$.
 \end{lemma}
 \begin{proof}
-
-In the elongation that places bead $i$ at $(1,1)$ there are two possibilities:
+In the elongation that places bead $i$ at $(1,1)$ there are two possibilities. 
 \begin{itemize}
@@
 below, with the only difference being that the bond between (1,1) and (1,0) is missing.%as in Fig.~\ref{fig:hexagonOut1}.
+\end{itemize}
+
 	\begin{figure}
@@
 	\end{figure}
-
-\end{itemize}
 
@@
 
-\begin{figure}
+\begin{figure}[tb]
 	\centering
@@
 Case 2.(a) gives the same upper bound as case 1. Cases 2.(b)-(c) give the smaller upper bound $|\hexagon_p^n|+1$, thereby concluding the proof.
+\qed
 \end{proof}
@@
 \begin{lemma}[$\delta=3, \alpha =1$]\label{lem:d3a1}
-	Let $\Xi$ be a unary oritatami system of $\delta=3$ and $\alpha = 1$. Starting with a seed of length $n$, $\Xi$ can yield only finite structures of size at most $3n^2+4n+2$.
+	A deterministic unary oritatami system of $\delta=3$ and $\alpha = 1$ can fold into a terminal conformation of length at most $3n^2+4n+2$.
 \end{lemma}

### 2018-12-06 tt_intro.tex
Technical problems fixed

@@
-In this section, we consider Problem~\ref{prob:det_unary_length} at delay 1. 
+In this section, we consider Problem~\ref{prob:det_unary_length} at delay 1 first and then at arity 1. 
 Let $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ be a deterministic oritatami system of delay 1. 
@@
 \caption{A tunnel divides the world into two. 
-Getting through the tunnel leads us to another world. 
+%Getting through the tunnel leads us to another world. 
 }
@@
 We call a bead \textit{singular} if it is surrounded by only $\alpha+1$ beads but forms $\alpha$ bonds. 
-Any bead but $w[1]$ can be singular because of their predecessor and successor. 
+No bead but $w[1]$ can be singular because of their predecessor and successor. 
 A tunnel is \textit{singular} if its entrance or exit is next to $w[1]$ that is singular. 

### 2018-12-06 tt_theorem.tex
Technical problems fixed

@@
 \begin{theorem}[$\delta = 1, \alpha = 4$]
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 4$. It can yield only finite conformation of length $3n^2  + 3n + 1$.
+The terminal conformation of a deterministic unary oritatami system of $\delta = 1, \alpha = 4$ is of length at most $3n^2  + 3n + 1$.
 \end{theorem}
@@
 \begin{proof}
-Consider the moment when a bead $b$ is stabilized outside $\hexagon_O^n$ for the first time. 
-See Fig.~\ref{TTT_a4_first}.
-There is only one bead available to stabilize $b$ there, which is $b_1$. 
-In order for $b$ to avoid nondeterminism, hence, none of the beads around should not attract $b$.
+Consider the moment when a bead, say $b$, is stabilized outside $\hexagon_O^n$ for the first time.
+The bead must be bound a bead at the periphery of $\hexagon_O^n$ as depicted in Fig.~\ref{TTT_a4_first}.
+%There is only one bead available to stabilize $b$ there, which is $b_1$. 
+In order to avoid nondeterminism, the bead $b$ must not be attracted anyhow else by beads around.
 
@@
         \fill (0:1) circle [radius=0.1];
+
+	\draw[dotted, thick] (1, 0) -- ++(120:1);
 
@@
 \begin{theorem}[$\delta = 1, \alpha = 3$]
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 3$. It can yield only finite conformations of length $4n + 14$.
+The terminal conformation of a deterministic unary oritatami system of $\delta = 1, \alpha = 3$ is of length at most $4n + 14$.
 \end{theorem}
@@
 
-      \draw[dotted, shift = (60:1)] (0:0) -- (-60:1);
+      \draw[dotted, thick, shift = (60:1)] (0:0) -- (-60:1);
 
@@
       \draw[->, blue, shift=(60:1)] (0:0.1) -- (0:0.9);
-       \draw[dotted, shift = (60:1)] (0:0) -- (-60:1);
+       \draw[dotted, thick, shift = (60:1)] (0:0) -- (-60:1);
 
@@
 \begin{theorem}[$\delta= 1, \alpha=2$]
-Let $\Xi$ be a deterministic unary oritatami system of $\delta = 1, \alpha = 2$.
-It can yield an infinite structure, but the transcript folds into the zig-zag conformation after its $(27n^2 + 9n +1)$-th bead.
+A deterministic unary oritatami system of $\delta = 1, \alpha = 2$ can fold into an infinite conformation, but its transcript folds into the zig-zag conformation (Fig.~\ref{TTT_zigzag}) after its $(27n^2 + 9n +1)$-th bead.
 \end{theorem}

### 2018-12-06 arity1pyramid.tex
Intro modified
fix pyramid pic
Add files via upload

@@
-\subsection{$\alpha = 1$, arbitrary alphabets}
+%\subsection{$\alpha = 1$, arbitrary alphabets}
 First we present a lower bound construction for arity $1$ systems.
@@
 
-Consider the following $\delta=2$, $\alpha=1$ system with bead types $\{0,1,2,3,4\}$ and attraction rules $\{(1,1),(2,2), (3,3),(4,4)\}$.
-Let the seed $\sigma$ be a conformation of a $4k+1$ long bead sequence of the form $(1020)^k0$, such that bead $\sigma[i]$ of the seed is stabilized at point $(i,0)$, for all $1\leq i\leq 4k-1$.
+Consider the following $\delta=2$, $\alpha=1$ system with bead types $\{0,1,\dots,8\}$ and attraction rules $\{(i,i) \mid 1\leq i\leq 8\}$.
+Let the seed $\sigma$ be a conformation of a $4k+1$ long bead sequence of the form $(10205060)^{k/2}0$ and $(10205060)^{(k-1)/2}(1020)0$, for $k$ even and odd, respectively.
+Bead $\sigma[i]$ of the seed is stabilized at point $(i,0)$, for all $1\leq i\leq 4k-1$.
 Bead $4k$ is at $(4k-1,-1)$ and bead $4k+1$ is at $(4k,0)$.
@@
 
-The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where $\mathrm{row}_\ell$, for $\ell\in \{1,\dots, 2k\}$ is given in the table of Fig.~\ref{table:transcript}.
-\begin{figure}[h]
-	\begin{minipage}{.49\textwidth}
-		%\centering
-		\begin{tabular}{l|l}
-			\multicolumn{2}{c}{Transcript $w$}\\
-			\multicolumn{2}{c}{}  \\
-			$k$ odd & \hspace{0.3cm} $k$ even\\\hline
-			& \\
-			$(2413)^{k-1}241$\hspace{0.3cm} & \hspace{0.3cm} $(2413)^{k-1}241$\\
-			$(4231)^{k-1}4$   &  \hspace{0.3cm} $(4231)^{k-1}4$  \\
-			$(1324)^{k-2}132$ &  \hspace{0.3cm} $(1324)^{k-2}132$\\
-			$(3142)^{k-2}3$   &  \hspace{0.3cm} $(3142)^{k-2}3$ \\
-			\vdots			 &  \hspace{0.3cm} \vdots\\
-			$(1324)^1 132$	 &  \hspace{0.3cm} $(2413)^{1} 241$\\
-			$(3142)^1 3$		 & \hspace{0.3cm} $(4231)^1 4$\\
-			$(2413)^0 241$	 &  \hspace{0.3cm} $(1324)^0 132$\\
-			$(4231)^0 4$		 & \hspace{0.3cm} $(3142)^0 3$\\
-		\end{tabular}
-	\end{minipage}
-	%\scriptsize
-	\begin{minipage}{.49\textwidth}
-		%\centering
-		\begin{tabular}{|l|c|}
-			\hline
-			\hspace{1.2cm}row $\ell$ & $\ell\mod 4$ \\\hline
-			 & \\
-			\hspace{0.1cm}$(2413)^{k-\lfloor (\ell+1)/2\rfloor}241$ \hspace{0.1cm} &  $\textrm{ }\ell\equiv 1\mod 4\textrm{ }$\\
-			\hspace{0.1cm}$(4231)^{k-\lfloor (\ell+1)/2\rfloor}4$   &  $\textrm{ }\ell\equiv 2 \mod 4\textrm{ }$ \\
-			\hspace{0.1cm}$(1324)^{k-\lfloor (\ell+1)/2\rfloor}132$ &  $\textrm{ }\ell\equiv 3 \mod 4\textrm{ }$ \\
-			\hspace{0.1cm}$(3142)^{k-\lfloor (\ell+1)/2\rfloor}3$   &  $\textrm{ }\ell\equiv 4 \mod 4\textrm{ }$ \\\hline
-		\end{tabular}
+The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where 
+\begin{itemize}
+	\item $\mathrm{row}_1=(24136857)^{(k-1)/2}241$ if $k$ is odd, and $\mathrm{row}_1=(68572413)^{k/2-1}6857241$ if $k$ is even;
+	\item $\mathrm{row}_{i+1}=(\mathrm{row}_i[2..|\mathrm{row}_i|-1])^r$ for $i\in \{1,\dots, 2k-1\}$, that is each row is the reverse of the previous without the first and last bead.
+\end{itemize}
 
-	\end{minipage}
-	\caption{Transcript of pyramid-like conformation at delay $2$, arity $1$.}
-	\label{table:transcript}
-\end{figure}
+%The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where $\mathrm{row}_\ell$, for $\ell\in \{1,\dots, 2k\}$ is given in the table of Fig.~\ref{table:transcript}.
+%\begin{figure}[h]
+%%	\begin{minipage}{.49\textwidth}
+%%		%\centering
+%%		\begin{tabular}{l|l}
+%%			\multicolumn{2}{c}{Transcript $w$}\\
+%%			\multicolumn{2}{c}{}  \\
+%%			$k$ odd & \hspace{0.3cm} $k$ even\\\hline
+%%			& \\
+%%			$(24136857)^{(k-1)/2}241$\hspace{0.3cm} & \hspace{0.3cm} $(2413)^{k-1}241$\\
+%%			$42(75863142)^{k-1}314$   &  \hspace{0.3cm} $(4231)^{k-1}4$  \\
+%%			$13(68572413)^{k-2}2$ &  \hspace{0.3cm} $(1324)^{k-2}132$\\
+%%			$(3142)^{k-2}3$   &  \hspace{0.3cm} $(3142)^{k-2}3$ \\
+%%			\vdots			 &  \hspace{0.3cm} \vdots\\
+%%			$(1324)^1 132$	 &  \hspace{0.3cm} $(2413)^{1} 241$\\
+%%			$(3142)^1 3$		 & \hspace{0.3cm} $(4231)^1 4$\\
+%%			$(2413)^0 241$	 &  \hspace{0.3cm} $(1324)^0 132$\\
+%%			$(4231)^0 4$		 & \hspace{0.3cm} $(3142)^0 3$\\
+%%		\end{tabular}
+%%	\end{minipage}
+%	%\scriptsize
+%	\begin{minipage}{.99\textwidth}
+%		\centering
+%		\begin{tabular}{|l|c|}
+%			\hline
+%			\hspace{1.2cm}row $\ell$ & $\ell\mod 4$ \\\hline
+%			 & \\
+%			\hspace{0.1cm}$(24136857)^{k-\lfloor (\ell+1)/2\rfloor}241$ \hspace{0.1cm} &  $\textrm{ }\ell\equiv 1\mod 4\textrm{ }$\\
+%			\hspace{0.1cm}$(4231)^{k-\lfloor (\ell+1)/2\rfloor}4$   &  $\textrm{ }\ell\equiv 2 \mod 4\textrm{ }$ \\
+%			\hspace{0.1cm}$(1324)^{k-\lfloor (\ell+1)/2\rfloor}132$ &  $\textrm{ }\ell\equiv 3 \mod 4\textrm{ }$ \\
+%			\hspace{0.1cm}$(3142)^{k-\lfloor (\ell+1)/2\rfloor}3$   &  $\textrm{ }\ell\equiv 4 \mod 4\textrm{ }$ \\\hline
+%		\end{tabular}
+%	
+%	\end{minipage}
+%	\caption{Transcript of pyramid-like conformation at delay $2$, arity $1$.}
+%	\label{table:transcript}
+%\end{figure}
 
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{./Fig/CI_Numbers}
+	\includegraphics[width=0.7\linewidth]{./Fig/CI_NumbersNew}
 	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. }

### 2018-12-06 arity1upper.tex
arity1upper
Assumpation of n removed
Thm and Lemma statements fixed
The original was a bit informal, saying "can yield" or something like
that.

@@
 \begin{theorem}[$\delta\in\{ 2,3\}, \alpha = 1$]\label{thm:d23a1}
-	A deterministic unary oritatami system at arity $\alpha = 1$ and delay $\delta \in \{2,3\}$ can fold into a terminal conformation of length at most $3n^2+4n+2$.
+	The terminal conformation of a deterministic unary oritatami system at arity $\alpha = 1$ and delay $\delta \in \{2,3\}$ is of length at most $3n^2+4n+2$.
 \end{theorem}
@@
 Let us fix some common starting points for Lemmas~\ref{lem:d2a1} and \ref{lem:d3a1}.
-Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|+1$.
+Let the point where the first transcript bead was fixed be $p$.
 We will argue about the situation when the first bead is stabilized outside $\hexagon_p^n$ (a hexagon of radius $n$).
@@
 \begin{lemma}[$\delta=2, \alpha =1$]\label{lem:d2a1}
-	A deterministic unary oritatami system of $\delta=2$ and $\alpha = 1$ can fold into a conformation of length at most $3n^2+4n+2$.
+	The terminal conformation of a deterministic unary oritatami system of $\delta=2$ and $\alpha = 1$ is of length at most $3n^2+4n+2$.
 \end{lemma}
@@
 \begin{lemma}[$\delta=3, \alpha =1$]\label{lem:d3a1}
-	A deterministic unary oritatami system of $\delta=3$ and $\alpha = 1$ can fold into a terminal conformation of length at most $3n^2+4n+2$.
+	The terminal conformation of a deterministic unary oritatami system of $\delta=3$ and $\alpha = 1$ is of length at most $3n^2+4n+2$.
 \end{lemma}

### 2018-12-06 arity1pyramid.tex
Add files via upload

@@
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{./Fig/CI_NumbersNew}
+	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. }
+	\label{CI:big}
+\end{figure}
+
 %\subsection{$\alpha = 1$, arbitrary alphabets}
@@
 	\item $\mathrm{row}_1=(24136857)^{(k-1)/2}241$ if $k$ is odd, and $\mathrm{row}_1=(68572413)^{k/2-1}6857241$ if $k$ is even;
-	\item $\mathrm{row}_{i+1}=(\mathrm{row}_i[2..|\mathrm{row}_i|-1])^r$ for $i\in \{1,\dots, 2k-1\}$, that is each row is the reverse of the previous without the first and last bead.
+	\item $\mathrm{row}_{i+1}=(\mathrm{row}_i[2..|\mathrm{row}_i|-1])^r$ for $i\in \{1,\dots, 2k-1\}$, where $w^r$ is the reverse of $w$.
+In other words, each row is the reverse of the previous without its first and last bead.
 \end{itemize}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{./Fig/CI_NumbersNew}
-	\caption{Quadratic length transcript folding deterministically into pyramid shape. Seed: thick black path. Transcript: thin blue path. Bonds: dashed red lines. }
-	\label{CI:big}
-\end{figure}
-
-Stabilizing the first bead of row $j$ goes as follows (see Fig.~\ref{CI:turn}):
+Stabilizing the first bead of a row goes by binding to the penultimate bead of the previous row, as they are of the same type according to how we constructed the transcript, and they have free hands (see Fig.~\ref{CI:turn}).
 %\begin{itemize}
@@
 
-\begin{center}
-	\begin{tabular}{|c|c|c|c|c|@{}m{0pt}@{}}
-		%\renewcommand{\arraystretch}{2}
-	$j\mod 4$					& first bead 	& predecessor at		& first bead binds to		& first stabilizes at\\
-						\hline
-	$\equiv 1$	& 2		& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$& $\mathrm{ }$\newline $\mathrm{ }$\\
-	\hline
-	$\equiv 2$	& 4				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$\\
-	\hline
-	$\equiv 3$	& 1				& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
-	\hline
-	$\equiv 4$	& 3				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
-	\hline		
-	\end{tabular}
-\end{center}
+%\begin{center}
+%	\begin{tabular}{|c|c|c|c|c|@{}m{0pt}@{}}
+%		%\renewcommand{\arraystretch}{2}
+%	$j\mod 4$					& first bead 	& predecessor at		& first bead binds to		& first stabilizes at\\
+%						\hline
+%	$\equiv 1$	& 2		& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$& $\mathrm{ }$\newline $\mathrm{ }$\\
+%	\hline
+%	$\equiv 2$	& 4				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$\\
+%	\hline
+%	$\equiv 3$	& 1				& $(4k-\frac{j-1}{2}, j-1)$		& $(4k-\frac{j+1}{2}, j-1)$	& $(4k-\frac{j+1}{2}, j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
+%	\hline
+%	$\equiv 4$	& 3				& $(\frac{3j}{2}-1,j-1)$		& $(\frac{3j}{2},j-1)$		& $(\frac{3j}{2},j)$ & $\mathrm{ }$\newline $\mathrm{ }$ \\
+%	\hline		
+%	\end{tabular}
+%\end{center}
 
@@
 	\end{minipage}
-	\caption{Fixing transcript beads in odd rows}
+	\caption{Fixing transcript beads in first row, when $k$ is odd}
 	\label{CI:1-4}
@@
 
-As for the other beads, in rows $j\equiv 1,3\mod 4$, beads of type $1$ and $3$ bind to a bead in row $j-1$.
-In rows $j\equiv 2,4\mod 4$ beads of type $2$ and $4$ can bind to a bead in row $j-1$.
-This is true for row $1$, because beads of type $1$ and $3$ from row $1$ can only bind to every second bead of the seed, whereas beads of type $2$ and $4$ from row $1$ cannot bind to anything (Fig.~\ref{CI:1-4}, (c)).
+As for the other beads, in rows $j\equiv 1,3\mod 4$, beads of type $1,2,5,6$ bind to a bead in row $j-1$.
+In rows $j\equiv 2,4\mod 4$ beads of type $3,4,7,8$ can bind to a bead in row $j-1$.
+This is true for row $1$, because beads of type $1,2,5,6$ from row $1$ can only bind to every second bead of the seed, whereas the other beads of row $1$ cannot bind to anything (Fig.~\ref{CI:1-4}, (c)).
 Once this dynamic holds for a row, it holds inductively for the next, as a bead that binds to another loses its only free hand at arity $1$.
 
-Within one row of the transcript, no bead can bind to a preceding bead, because if there is a previous bead of the same type in that row, it is stabilized at a distance of four and the system has delay $2$.
+Within one row of the transcript, no bead $i$ can bind to a preceding bead, because if there is a previous bead of the same type in that row, it is stabilized at a distance of at least $6$ from any point where $i$ could be placed.
 

### 2018-12-06 paper.tex
QED
Pyramid enlarged
For not to challenge readers' eyes.

@@
 
-As a result of independent significance, we show that increasing the delay from 1 to 2 enables an oritatami system to yield a conformation of quadratic length in $n$ as long as 5 types of beads are available.
+As a result of independent significance, in Sect.~\ref{sect:lower}, we show that increasing the delay from 1 to 2 enables an oritatami system to yield a conformation of quadratic length in $n$ as long as 9 types of beads are available.
 
@@
 	Checking the condition in 2. can be done in $\mathcal{O}(|H|)$ time for any reasonable representation of $H$, hence the whole process takes $\mathcal{O}(|w|\cdot|H|)$ time.
+	\qed
 \end{proof}
@@
 Therefore, the total running time is $2^{\mathcal{O}(\delta)}\cdot |R|\cdot|w|$.
+	\qed
 \end{proof}
@@
 	The claim follows from Theorem~\ref{thm:OS_to_2dTM} and the fact that $|R|$ is implicitly bounded by $|w|^2$.
+	\qed
 \end{proof}

### 2018-12-06 paper.tex
Submitted
Done!!

@@
 \usepackage{wrapfig}
+
+\usepackage{hyperref}
 
@@
 \begin{abstract}
-We investigate simple oritatami systems in an attempt to establish lower bounds on the size and complexity of computationally universal systems. 
-In particular, we look at oritatami systems, where the folding sequence consists of a number of beads of the same type and show that under reasonable assumptions, these systems are not universal.
+An oritatami system is a novel mathematical model of RNA cotranscriptional folding, which has recently proven extremely significant in information processing in organisms and also controllable artificially in a test tube to construct an artificial structure by folding an RNA sequence.
+This model has turned out to be Turing universal. 
+One next step is to simplify the Turing universal oritatami system and another is to characterize weaker oritatami systems as we may not need Turing universality for applications. 
+%We investigate simple oritatami systems in an attempt to establish lower bounds on the size and complexity of computationally universal systems. 
+In this paper, we look at oritatami systems that folds a unary sequence, and show that under reasonable assumptions, these systems are not universal.
 \end{abstract}
@@
 (Right) an abstraction of its product, i.e., an RNA tile, as a configuration of an oritatami system. 
-A dot $\bullet$ in the figure on the right represents a sequence of 3-4 nucleotides, and the solid arrow and dashed lines represent its RNA transcript and interactions (respectively) based on hydrogen bonds between nucleotides.
+A dot $\bullet$ in the figure on the right represents a sequence of 3-4 nucleotides (oligonucleotides). 
+The solid arrow and dashed lines represent respectively its RNA transcript and interactions based on hydrogen bonds between nucleotides.
 }
@@
 
-Transcription is the first essential step of gene expression, in which a DNA template sequence is copied into a single stranded RNA sequence by a `molecular Xerox' called RNA polymerase, letter by letter according to the complimentarity relation ${\tt A} \rightarrow {\tt U}$, ${\tt G} \rightarrow {\tt C}$, ${\tt C} \rightarrow {\tt G}$, and ${\tt T} \rightarrow {\tt A}$.
+Transcription is the first essential step of gene expression, in which a DNA template sequence is copied into a single stranded RNA sequence of nucleotides {\tt A}, {\tt C}, {\tt G}, and {\tt U}  (letter of RNA alphabet) by a `molecular Xerox' called RNA polymerase, nucleotide by nucleotide according to the complimentarity relation ${\tt A} \rightarrow {\tt U}$, ${\tt G} \rightarrow {\tt C}$, ${\tt C} \rightarrow {\tt G}$, and ${\tt T} \rightarrow {\tt A}$.
 The copied RNA sequence is called \textit{transcript}. 
-The transcript starts folding upon itself into intricate structures immediately after it emerges from the polymerase, as illustrated in Fig.~\ref{fig:rna_origami} (Left).
+The transcript does NOT remain single-stranded until it is fully synthesized. 
+It rather starts folding upon itself into intricate stable conformations (structures) primarily via hydrogen bonds, immediately after it emerges from the polymerase, as illustrated in Fig.~\ref{fig:rna_origami} (Left).
 
@@
 As demonstrated in laboratory, this method, called RNA Origami, makes it possible to cotranscriptionally self-assemble a unique RNA rectangular tile highly probably (see Fig.~\ref{fig:rna_origami} (Left)).
+This breakthrough and the design of RNA tile has encouraged the research on the nano-scale RNA structure self-assembly so that several successful attempts to self-assemble artificial structures by folding a single-stranded RNA sequence \cite{EKOMSSSO2018,YanYin2017}.
 Geary et al.~\cite{GeMeScSe2016} proposed a mathematical model for this process, called oritatami system. 
-In this model, an RNA structure is abstracted as a directed path with information on hydrogen-based interaction (bonds) over the triangular grid graph $\mathbb{T}$ as illustrated in Fig.~\ref{fig:rna_origami}.
+In this model, an oligonucleotide (a short sequence of RNA nucleotides) is considered to be a bead and an RNA structure is abstracted as a directed path with information on hydrogen-based interaction (bonds) between beads over the triangular grid graph $\mathbb{T}$ as illustrated in Fig.~\ref{fig:rna_origami}.
 An oritatami system folds a transcript of abstract molecules (beads) of finite number of types over $\mathbb{T}$. 
@@
     \end{tikzpicture}
-    \caption{The zig-zag conformation. This is the only one infinite conformation foldable deterministically by an unary oritatami ssytem at delay 1 and arity 2.}
+    \caption{The zig-zag conformation. This is the only one infinite conformation foldable deterministically by an unary oritatami system at delay 1 and arity 2.}
     \label{TTT_zigzag}
@@
 Then we say that the bead $w[i+1]$ and the bonds it forms are \textit{stabilized} according to $C_{i+1}$. 
+The easiest way to understand this stabilization process should be the video available at \href{https://www.dailymotion.com/video/x3cdj35}{\tt https://www.dailymotion.com/video/x3cdj35}, in which the Turing universal oritatami system by Geary et al.
+\cite{GeMeScSe2018}, whose delay is 3, is running.
 Note that an arity-$\alpha$ oritatami system cannot fold any conformation of arity larger than $\alpha$. 
